### 2018-08-12 paper/SI.tex
Draft version 20180812

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}

%manuscript=suppinfo

% \usepackage{minted}
% \usepackage{graphicx}
%\usepackage{float}
%\usepackage{xcolor}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{fontspec}
%\renewcommand{\figurename}{}

\setkeys{acs}{usetitle = true}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{footnote}
\renewcommand{\sfdefault}{cmr}

%\renewcommand{\thefigure}{Supplementary Figure \arabic{figure}}
\usepackage{float}

\renewcommand{\figurename}{\bf Supplementary Figure}
\renewcommand{\tablename}{\bf Supplementary Table}
%\renewcommand{\bibname}{Supplementary References}

\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{D. H. and T. T. Contributed equally to this work}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich, Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{D. H. and T. T. Contributed equally to this work}

\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}

\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}

\author{Jonathan N. Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}

\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}

\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\keywords{two-dimensional materials, dielectric constant, first-principles calculation, band gap, binding energy}
\date{}

\title{Supplementary Information: \\
Universal Understanding of the Dielectric Constants of Two-Dimensional Materials}
\begin{document}

%\newpage{}

\pagebreak{}

\section{Table of Contents}

1. Supplementary Note 1: 2D-Moss relations at different levels of theory: PBE, $G_{\rm 0}W_{\rm 0}$ \\ 
%
2. Supplementary Figure 1: Simulations using PBE functional. \\
%
3. Supplementary Figure 2: Simulations using many-body $G_{\rm 0}W_{\rm 0}$ approach \\ 
%
4. Supplementary Figure 3: Model predictions at PBE level  \\ 
% 
5. Supplementary Figure 4: Hybrid functional versus many-body band gaps  \\ 
%
6. Supplementary Note 2: Additional discussions on Moss' description of photoconductivity \\
%
7. Supplementary Figure 5: Normalization of band gaps using $E_g/\varepsilon_{\parallel}^2$ \\ 
%
8. Supplementary Note 3: Linking excitonic binding energies and dielectric constants  \\
%
9. Supplementary Figure 6: Scaling relations between dielectric constants and excitonic binding energies \\ 
%
%Include here the part from main text. 
10. Supplementary Figure 7: A second model to extract dielectric constants \\
%
11. Supplementary Note 4: Multiscale calculations between monolayer and bulk \\ 
%
12. Supplementary Figure 8: Relationship between the 2D and 3D dielectric constants \\ 
%
%13. Supplementary Note 5: Derivation of  $\varepsilon^{\mathrm{2D}} =   \displaystyle 1 + \frac{1}{4 \pi \varepsilon_{0}}
 %                     \frac{4 e^2 \pi \hbar^2}{m_e^2 E_g^2} J_{cv} P_{cv}^{2}$ \\
%
13. Supplementary Figure 9: Quantum capacitance over valence states \\
%
14. Supplementary Table 1: Comparison between dielectric constants of 2D materials and 3D materials \\ 
%
15. Supplementary Table 2: Fitting parameters for $C_{Q}$ \\ 
%
16. Supplementary Table 3: Database of \textit{Ab initio} calculations using HSE06 hybrid functional \\
%
17. Supplementary Figures 10-61: DOS-calculation results using HSE06 functional plus self-consistent spin-orbit coupling \\
%
18. Supplementary References \\

%4. Figure S4: Comparison between $\varepsilon_{\parallel}$ from HSE06 method and estimated from $E_{\mathrm{g}}$ \\

\pagebreak{}

%\subsubsection{Supplementary Figure 1: Summary of systems studied and group separation}

%{\bf Figure S1: Summary of systems studied and group separation}

%\begin{figure}[H]
%\centering
%\includegraphics[width=0.80\linewidth]{fig1_v122017_ink.pdf}
%\caption{\label{fig-S1} 
%{\bf 2D geometries and periodic table. a}, Schematic of the geometries of the 2D materials included in our database. 
%Compounds include monochalcogenides, dichalcogenides at the most common phases, such as  
%2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group); 
%graphene derivatives (graphane, f-graphene); phosphorene, h-BN, 
%halides (CdX$_2$) and popular organic-inorganic perovskites (CH$_3$NH$_3$PbBr$_3$). 
%{\bf b}, Periodic table showing the main elements utilized in our high-throughput screening, and the classification of the groups accordingly to their scaling relationships. Several materials have resulted 
%to be metals (group 5, 7, 8, 9, 11) with dichalcogenide formula, which were not included here.  
%}
%\end{figure}
%
%
%\pagebreak{}

\subsubsection{Supplementary Note 1: 2D-Moss relations at different levels of theory: PBE, $G_{\rm 0}W_{\rm 0}$}

%Figure S2: PBE results for \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) versus band gaps}

To demonstrate the validity of the Moss relation for 2D materials we have performed calculations 
at different levels of theory, such as using plain PBE functional (Supplementary Figure \ref{fig-S2}), HSE06 hybrid functional (Figure 1) and many-body $G_{\rm 0}W_{\rm 0}$ (Supplementary Figure \ref{fig-S3}). Despite of the method utilized all three approaches resulted in clear dependence of $\varepsilon_{\parallel}$ as a 
function of band gaps, and no-dependence of $\varepsilon_{\perp}$. Slight variations of the fitting parameters are observed, which are expected due to the different levels of treatment of the electronic and dielectric properties of the layers. It is worth mentioning however that better accuracy between calculated magnitudes of $\varepsilon_{\parallel}$ and $\varepsilon_{\perp}$ 
are obtained at HSE06 and $G_{\rm 0}W_{\rm 0}$.

%It should be noted that simulations carried out at the level of PBE functional resulted in considerably larger differences between the model predictions and calculated \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) (see Supplementary Figure \ref{fig-S4}). Deviations from either a purely linear fitting without a finite cumulative factor at the model, or magnitudes that differ by more than $\sim$24\% between simulations and scaling relations are observed.

\begin{figure}[H]
\centering
\includegraphics[width=1.05\linewidth]{figure1S_v010318ink.pdf}
\caption{\label{fig-S2}
{\bf Simulations using PBE functional. a-b}, PBE results for the in-plane $\varepsilon_{\parallel}$ and out-of-plane $\varepsilon_{\perp}$  
dielectric constants, respectively, for monolayer materials as a function of the electronic band gap. 
Similar classification of the 2D materials as in {\bf Figure 1}  
is used for comparison: linear (green circles) and power (orange squares) groups. 
Orange and green lines are fits 
to $\varepsilon_{\parallel}=3.36/E_{g}^{0.71}$ and 
$\varepsilon_{\parallel}=7.79-2.15E_{g}$, respectively, in {\bf a}. 
The original 3D-Moss relation, $\varepsilon_{\parallel}=9.74/E_{g}^{0.50}$, 
between the dielectric constant of bulk semiconductors and band gap 
is shown as faint blue line.  
Dataset for $\varepsilon_{\perp}$ in {\bf b} are fitted using straight lines, 
$\varepsilon_{\perp}=1.21+(0.05)E_{g}$ (green) and $\varepsilon_{\perp}=1.60-(0.12)E_{g}$ (orange). 
The inset in {\bf b} shows the spatial definition of both $\varepsilon_{\perp}$ and $\varepsilon_{\parallel}$. 
}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=1.05\linewidth]{figureS_GW_gap_moss_v021218ink.pdf}
\caption{\label{fig-S3}
{\bf Simulations using many-body $G_{\rm 0}W_{\rm 0}$ approach. a-b}, $G_{\rm 0}W_{\rm 0}$ results for the in-plane $\varepsilon_{\parallel}$ and out-of-plane $\varepsilon_{\perp}$  
dielectric constants, respectively, for monolayer materials as a function of the electronic band gap. 
Similar classification of the 2D materials as in {\bf Figure 1}
is used for comparison: linear (green circles) and power (orange squares) groups. 
Orange and green lines are fits 
to $\varepsilon_{\parallel}=4.41/E_{g}^{0.52}$ and 
$\varepsilon_{\parallel}=8.20-1.48E_{g}$, respectively, in {\bf a}. 
The original 3D-Moss relation, $\varepsilon_{\parallel}=9.74/E_{g}^{0.50}$, 
between the dielectric constant of bulk semiconductors and band gap 
is shown as faint blue line.  
Dataset for $\varepsilon_{\perp}$ in {\bf b} are fitted using straight lines, 
$\varepsilon_{\perp}=1.14+(0.05)E_{g}$ (green) and $\varepsilon_{\perp}=1.31-(0.02)E_{g}$ (orange). 
The inset in {\bf b} shows the spatial definition of both $\varepsilon_{\perp}$ and $\varepsilon_{\parallel}$. 
}
\end{figure}

\pagebreak{}

%\subsubsection{Figure S3: Model predictions at PBE level}

%It should be noted that simulations carried out at the level of PBE functional resulted in considerably larger 
%differences between the model predictions and calculated \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) 
%as shown in Figure \ref{fig-S3}. Deviations from either a purely linear fitting without a finite cumulative 
%factor at the model, or magnitudes that differ by more than $\sim$24\% between simulations 
%and scaling relations are observed.

\begin{figure}[H]
\centering
\includegraphics[width=1.01\linewidth]{figure2S_v010218ink.pdf}
\caption{\label{fig-S4}
{\bf Model predictions using PBE results. a,b}, Comparison of PBE-calculated \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) 
and model predictions, respectively. The scaling relationships of PBE in-plane ($\varepsilon_{\parallel}=3.36/E_{g}^{0.71}$ and $\varepsilon_{\parallel}=7.79-2.15E_{g}$) 
and out of plane ($\varepsilon_{\perp}=1.21+(0.05)E_{g}$ 
and $\varepsilon_{\perp}=1.60-(0.12)E_{g}$) were utilized 
with $E_{g}$ as the only external parameter. Power- and linear-law materials are organized following 
the same classification in {\bf Figure 1}. PBE results are fitted using the solid blue line with a comparison with HSE06 fitted line shown in orange in {\bf a}. A linear line with an unitary slope $y=x$ is shown in {\bf b}. 
}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=1.01\linewidth]{hse06_gw_gaps_v010918.pdf}
\caption{\label{fig-S4a}
{\bf Hybrid functional versus many-body band gaps.} Comparison between band gaps at HSE06 (x-axis) and those calculated using many-body techniques (y-axis), such as $G_{\rm 0}W_{\rm 0}$ and $G_{\rm 0}W_{\rm 0}$-BSE. 
Power- and linear-law materials are organized following 
the same classification in {\bf Figure 1} in the main text. 
A linear fitting with an unitary slope $y=x$ is shown through the solid black line.}
\end{figure}

\pagebreak{}

\subsection*{Supplementary Note 2: Additional discussions on Moss' description of photoconductivity}

One of the main differences between 
the 2D-Moss relation (Eq.3) and that for 
3D bulk materials (Eq.1)
is the magnitude of the constant relating E$_{g}$ and \(\varepsilon_{\parallel}\). 
Its value was initially set based on the analysis of several 
photoconductors\cite{Moss_1950_relation}, and subsequently for several 
other semiconductors\cite{Moss-book1} with slightly different magnitudes. 
This energy constant can be interpreted 
as a scaling factor for the energy to raise an electron from the ground state into an 
excited state. According to Moss\cite{Moss_1950_relation,Moss52book,Moss59book,Moss_1985_n_Eg}, 
the absorption of a quantum excitation will raise an electron to an excited state rather than freeing it 
from the crystal. Thermal fluctuations will then move this electron into the conduction 
band from the lattice. These excitation points, which can can occur at different lattice sites, 
would behave similarly as in an isolated atom subjected to the 
dielectric constant of the host material\cite{Moss52book,Moss59book}. 
This results that the energy levels of this electron 
at this {\it hydrogenic} system are scaled down by $1/\varepsilon_{\parallel}^{2}$, 
which is equivalent 
to the Moss relation at different dimensionalities (Eq. 1 and 3). 
It is worth mentioning the resemblance of the energy coefficient in Eq.3 in the form of 
$E_g=13.55\varepsilon^{2}$ to the hydrogen ionization energy or Rydberg 
constant $hcR_{\infty}=13.60~eV$ 
for a hydrogenic description of electron-hole excitations 
using a single-particle approach.   
The similarity in this coefficient may suggest that 
photo-electrons stem from the same type of photo-process to the different types of 
hydrogen-like excitation centers. This energy defines the threshold 
wavelength $\lambda_{c}$ shown in Eq.4.

Moreover, if we carried out the band gap normalization via $E_{g}/\varepsilon_{\parallel}^{2}$ 
over the entire set of materials, as it is displayed 
in Supplementary Figure \ref{fig-S5}, we observe that most of the compounds follow similar threshold. 
Interestingly, monolayers with different electronic band gaps, 
such as 1T-NiO$_2$ (3.17 eV) and 2H-HfS$_2$ (1.89 eV), assume similar magnitudes of 
$E_{g}/\varepsilon^{2}$. Conversely, materials at both extremes of the dataset, e.g. 
1T-NiS$_2$ ($E_{g}=1.12$ eV, $\varepsilon_{\parallel}=6.16$) and 1T-HfO$_2$ ($E_{g}=6.49$ eV, 
$\varepsilon_{\parallel}=1.67$), exhibit roughly asymmetric trends on the electronic properties. 
That is, 1T-HfO$_2$ is a well-known insulator material in bulk\cite{Robertson:2004aa} 
but at the monolayer limit it may not 
give desirable dielectric properties because of its low dielectric constant, as it has recently been 
measured\cite{Zhang:2015aa}. 1T-NiS$_2$ in turn 
can develop different metallic or semiconducting properties\cite{Townsend:1971aa,Molla:2016aa} but its high-dielectric constant could be used as a reasonable dielectric. 
This indicates a plethora of potential combinations using band gaps and dielectric constants as key descriptors.

\begin{figure}[H]
\centering
\includegraphics[width=1.08\linewidth]{gap_normalization_divided_e2_v020918ink.pdf}
\caption{\label{fig-S5}
{\bf Normalization of band gaps using $E_g/\varepsilon_{\parallel}^2$.} Normalization of HSE06 band gaps $E_g$ by $1/\varepsilon_{\parallel}^{2}$ over the entire material 
dataset. The average value of $<E_{g}/\varepsilon_{\parallel}^{2}>=$ 0.54 indicates materials where  
the screening contribution is removed almost entirely to the band gap. Deviations from it would indicate 
larger or smaller contributions of the electronic screening to the band edges. 
}
\end{figure}

%%%%%%%%%%%%%%From Main text%%%%%%%%%%%%%

\subsubsection{Supplementary Note 3: Linking excitonic binding energies and dielectric constants}

The band gap may not be the only material property that \(\varepsilon\)
links to. The Claussius-Mossotti equation which
connects the dielectric constant and the molecular polarizability \(\alpha\), is
dependent on \(q\) in strictly 2D systems
\cite{Cudazzo_2011_screening_2D}:

\begin{equation}
\label{eq:Claussius-Mossotti-2D}
\varepsilon(q)^{2D} = 1 + 2\pi \alpha q
\end{equation}

The \(q\)-independent \(\varepsilon\) averaged over the \(q\)-space 
can be derived as\cite{Olsen_2016_hydrogen}:

\begin{equation}
\label{eq:eps-Olsen}
\varepsilon^{\mathrm{2D}}(\alpha, \mu) = 1/2 (1 + \sqrt{1 + 32\pi e^2/3\hbar^2 \alpha \mu})
%\varepsilon^{2D}(\alpha, \mu) = \frac{1}{2}(1 + \sqrt{1 + 32\pi \alpha \mu /3})
\end{equation}
where \(\mu=(m_{\mathrm{n}}^{-1} + m_{\mathrm{p}}^{-1})^{-1}\) is the
effective mass of the exciton. This equation 
establishes a direct relation between dielectric properties 
and specific details on the band structures of a given material. 
Using different values of $\mu$ and $\alpha$ for different classes of layered crystals
we can compare results obtained using Supplementary Eq.\ref{eq:eps-Olsen} with those calculated 
using HSE06 as indicated in Supplementary Figure \ref{fig-4}{\bf a}.  %The values of \(\alpha\) and \(\mu\) of the selected 2D materials are adapted from the results in Ref. \citenum{Rasmussen_2015_database}. 
There is a sound agreement between both approaches with most of the data points within 
the prediction margin of 90\% fidelity as shown in the violet stripe. 
Interestingly, we find that the two sets of data show almost a
linear correlation, with a linearly fitted slope of 0.95. Such results
indicate that \(\varepsilon\) does indeed relate to the internal band structures
of 2D materials, which are reflected by \(\alpha\) and \(\mu\). We also
notice that almost all the data points of the \(\varepsilon\) from the
polarizability model lie above the line \(y=x\), with a fitted
$y$-intercept of 1.39. The difference between the model predicted values of 
$\varepsilon^{2D}(\alpha, \mu)$ and our calculations 
may be due to the existence of long-range
Coulombic interactions $1/r$ in the Hartree-Fock exact 
exchange functional $E_{xc}^{HSE}$ even with a void
distance as large as 2 nm out of the plane, which results in \(\varepsilon_{\perp}\)
slightly higher than 1. 
The dielectric screening along the 
z-direction is not included in Supplementary Eq.\ref{eq:eps-Olsen} which is also derived assuming 
an average screening felt by the exciton. Even though such limitations are present, 
a mean prediction error of less than 1.5 is observed. With the implementation 
of a truncated Coulombic interaction function in the HSE06 
calculations\cite{Hueser_2013_2Dvs3D},
the discrepancy between both approximations may be even reduced.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.780\linewidth]{fig_biding_energy_v121917.pdf}
\caption{\label{fig-4}{\bf Scaling relations between dielectric constants and excitonic binding energies}
{\bf a}, \(\varepsilon_{\parallel}\)($\mu, \alpha$) from the 2D polarizability model (Supplementary Eq.\ref{eq:eps-Olsen}) compared with the \(\varepsilon_{\parallel}\) calculated at the HSE06 level. Dashed-orange line is the best fitting curve, with the linear $y=x$ in solid-blue. The violet area defines a prediction margin of 90\% fidelity of the model. Different data points are labeled in groups accordingly to Fig. {\bf 1b}. 
{\bf b}, Exciton binding energies \(E_{\mathrm{b}}\)$^{2D}$ of selected 2D materials calculated from \(\varepsilon_{\parallel}\)$^{\rm HSE06}$ (Supplementary Eq.\ref{eq:Wannier-2D}) compared with \(E_{\mathrm{b}}\) calculated by $G_0W_0-BSE$. 
The best fitting curve is displayed by dashed-orange line, with the linear $y=x$ in solid-blue. 
The coefficient of determination $R^2$ is shown in both panels. The violet areas define a 
prediction margin of 90\% fidelity of the model. Group labels follow those in {\bf a}. 
}
\end{figure}

%There is a recent revival of relating exciton binding energies with other quantities, e.g. band gaps\cite{Choi_linear_2015,Jiang_2017_Eg_Eb}.

Other important quantity that is related to the dielectric constant and in general with the screening 
properties is the exciton binding energy. From the Wannier
model of exciton in strictly 2D systems, the binding energy
\(E_{\mathrm{b}}\) is scaled by \(\varepsilon^{2}\) \cite{Yang_1991}:

\begin{equation}
\label{eq:Wannier-2D}
E_{\mathrm{b}}^{\mathrm{2D}} = \frac{2 \mu e^4}{\varepsilon^2 \hbar^2 }
%E_{\mathrm{b}}^{\mathrm{2D}} = \frac{2 \mu}{\varepsilon^{2}}
\end{equation}
which indicates that the accuracy on $\varepsilon$ is the key factor apart from the 
established limitations of the model. If accurate values of $\varepsilon$ are utilized
from HSE06 simulations we can bridge this simple model to 
higher-levels of theory, 
such as using many-body Green's function method ($GW$) together 
with the Bethe-Salpeter equation (BSE) which is a routine but expensive scheme to 
estimate \(E_{\mathrm{b}}\) for different 2D materials. Supplementary Figure \ref{fig-4}{\bf b} shows that this correlation does exist. 
Two regimes can be found comparing both sets of data: when
\(E_{\mathrm{b}}\) from $GW$ is smaller than 0.75 eV, both
\(E_{\mathrm{b}}\) values are close and lie along \(y=x\); while
\(E_{\mathrm{b}}\) from $GW$ is large than 0.75 eV, the model predicted
values give larger deviation and higher overestimation. This can be
explained by the limitation of the current model: the 2D Wannier model
neglects the contribution from higher quantum numbers, and is more
accurate for materials with higher \(\alpha\) (hence lower
\(E_{\mathrm{b}}\)) \cite{Olsen_2016_hydrogen}. We note that the 2D
exciton model works relatively well for group 6 and 10 TMDCs, while
for group 14 materials the deviation is relatively larger. The
validity of the 2D Wannier exciton model has its practical importance:
calculation of the exciton binding energy usually involves virtual
orbitals and solving BSE self-consistently, which requires much
more computation resources than ground state DFT calculations. The
relationship between the exciton binding energies and 
dielectric constants favors bidirectional
prediction of both quantities: \(\varepsilon\) can be estimated from \(E_{\mathrm{b}}\) assessed by
spectroscopy experiments, and the computationally-expensive
\(E_{\mathrm{b}}\) can also be predicted by facile obtainable \(\varepsilon\). 
In fact, one alternative to this framework 
would be the estimation of $\varepsilon$ using 
the scaling relationships in Eqs. 3 and 5, 
and then Supplementary Eq.\ref{eq:Wannier-2D} for the binding energies. The only external parameter 
in this scheme would be band gap, which considerably reduce the number of 
unknown variables.

Considering the similarity between the \(\varepsilon-E_{\mathrm{g}}\) and
\(\varepsilon-E_{\mathrm{b}}\) relations, that both are scaled with
1/\(\varepsilon^{2}\), one may guess whether such scaling relation between \(\varepsilon\)
and the atomistic energies are of similar origin. In fact, recent
quantum chemistry studies reveal the existence of a linear
relation between \(E_{\mathrm{g}}\) and the exciton binding energy
\(E_{\mathrm{b}}\) in 2D materials
\cite{Choi_linear_2015,Jiang_2017_Eg_Eb}, which is distinct for the 
bulk systems where the effective mass also plays a role. Important in these predictions 
is the close relation between the 2D polarizability \(\alpha\)$^{2D}$ and 
\(E_{\mathrm{g}}\). Indeed, when \(\alpha\)$^{2D}$ is large, it gives 
$\alpha_{\mathrm{2D}} = N_{\mathrm{g}} e^{2} / 8 \pi^2 \epsilon_{0}^2 E_{\mathrm{g}}$, where
\(N_{\mathrm{g}}\) is the degeneracy of the bands and normally assumed
to be 6 for hexagonal symmetry\cite{Jiang_2017_Eg_Eb}. 
Combining this with Supplementary Eq.\ref{eq:eps-Olsen} we get 
the relation between \(\varepsilon\) and \(E_{\mathrm{g}}\):

\begin{equation}
\label{eq:eps-Eg-derive}
\varepsilon(\varepsilon - 1) = \frac{N_{\mathrm{g}} e^4 \mu}{3 \pi \hbar^2 \varepsilon_{0}^{2} E_{\mathrm{g}}}
%\varepsilon (\varepsilon - 1) = \frac{4 N_{\mathrm{g}} \mu}{3 E_{\mathrm{g}}}
\end{equation}
\\
and in the small band gap regime it may be simplified as 
$\varepsilon = \sqrt{\frac{N_{\mathrm{g}} e^4 \mu}{3 \pi \hbar^2 \epsilon_{0}^{2} E_{\mathrm{g}}}}$, 
which is also
equivalent to plugging the linear relation between \(E_{\mathrm{g}}\)
and \(E_{\mathrm{b}}\), with \(E_{\mathrm{b}} = 3 E_{\mathrm{g}} / 2
N_{\mathrm{g}}\), into the 2D Wannier model in Supplementary Eq.\ref{eq:Wannier-2D}. 
The inverse-square relation between \(\varepsilon\)
and \(E_{\mathrm{g}}\) is thus restored. A comparison between the
\(\varepsilon\) from Supplementary Eq.\ref{eq:eps-Eg-derive} and the calculated HSE06 magnitudes, 
can be seen in Supplementary Figure \ref{fig-S7}. 
We note a larger deviation using this model than the
magnitudes extracted from Supplementary Eq. \ref{eq:eps-Olsen} as 
show in Supplementary Figure \ref{fig-4}{\bf a}, 
as the accumulated error in all the
assumptions used in such model. Nevertheless, using the quantum
perturbation theory, it is possible to reveal the general
inverse-square law between \(E_{\mathrm{b}}-\varepsilon\) and
\(E_{\mathrm{g}} - \varepsilon\).

\begin{figure}[H]
\centering
\includegraphics[width=0.90\linewidth]{SI_figs/figureS3_v010318.pdf}
\caption{{\bf A second model to extract dielectric constants.} Comparison between the HSE06-calculated $\varepsilon_{\parallel}$ and those 
using Supplementary Eq.9 from the band gap \(E_{\mathrm{g}}\) and exciton mass \(\mu\) as 
$\varepsilon_{\parallel}(\varepsilon_{\parallel}-1)=\frac{4N_{g} \mu}{3E_g}$. 
Different data points are labeled accordingly in groups 
from Fig.1b. Fitting curve is show in orange dashed line, with linear 
slope curve $y=x$ in blue. Mean square error is highlighted with 
R$^2$=0.67. The exciton mass data were taken from Supplementary Refs. \citenum{Rasmussen_2015_2D, Olsen_2016}. 
}
\label{fig-S7}
\end{figure}

\subsubsection{Supplementary Note 4: Multiscale calculations between monolayer and bulk}

With the insight that a single descriptor can link electronic and dielectric features in 2D materials, 
we are able to generate a simple model that describes the ability 
to predict \(\varepsilon_{\parallel}\) in two-dimensions from the details 
of the electronic structure of the 3D-bulk. Therefore, we shift our focus to a 
multiscale approach to this problem as this is more relevant for a 
unification of the concepts from monolayer materials to thin films. 
The close relation between the real part of the dielectric function 
and its imaginary component can be used to this goal. 
The Lindhard theory gives the wave vector \(q\)-dependency of dielectric
functions in both 2D and 3D systems \cite{Dressel:2002aa}:
%
%
%
%\begin{multline}
%\label{eq:eps1-2D}
%\varepsilon(q,\omega) = 1 -\Psi(q) \sum_{k,l,l'}   \frac{f(k+q,l') - f(k,l)}{E_{k+q,l'} - E_{k,l} -\hbar \omega - i\delta } \times \\
%                                       |<k+q,l'|e^{iqr}|k,l> |^{2}  
%\end{multline} 
%
%
%\begin{equation}
%\label{eq:eps1-2D}
%\begin{array}{lll}
%&\varepsilon(q,\omega) &= 1 -\Psi(q) \sum_{k,l,l'}   \frac{f(k+q,l') - f(k,l)}{E_{k+q,l'} - E_{k,l} -\hbar \omega - i\delta } \\
%   &                                    & |<k+q,l'|e^{iqr}|k,l> |^{2}  
%\end{array}
%\end{equation} 
%
%
%\begin{widetext}
\begin{equation}
\label{eq:Lindhard-all}
\varepsilon(q, \omega) =  1 - \Psi(q) \sum_{k, l, l'} \frac{f(k+q, l') - f(k, l)}{E_{k+q, l'} - E_{k, l} -
                                         \hbar \omega - i\delta} |<k+q,l'|e^{iqr}|k, l>|^{2}   
\end{equation}
%\end{widetext}
%
%
%
where \(\Psi\) is the Coulombic potential, \(E\) is the energy of the
state, and \(f\) is the Fermi-Dirac distribution function. For
semiconductors, the state $| k+q,l'>$ is in the valence band (VB), and state $|k, l>$ is
in the conduction band (CB). Using the relation \(\sum_{k,l,l'} (E_{k+q, l'} - E_{k,l})
\vert <k+q, l' \vert e^{iqr} \vert k, l > \vert ^{2} \approx 2 N_{e}
E_{q}\) \cite{Slyom_2008_fundBook}, where \(N_{e}\) is the electron density
of the bands, and \(E_{q}=\hbar^{2} q^{2} / 2 \mu\) is the energy at
wavevector \(q\). The Lindhard dielectric function at the long
wavelength limit (\(q \to 0\)) can be rewritten as:
%
\begin{equation}
\label{eq:Lindhard-derived}
\varepsilon(q, \omega) = 1 + \frac{\Psi(q)}{E_{\mathrm{g}}^{2}}{}2 N_{e} E_{q}
\end{equation}
%
The difference between the dimensions is reflected by the difference
in the form of \(\Psi(q)\): the Fourier-transformation of Coulombic
interaction potential in 2D and 3D systems give:
%
\begin{eqnarray}
\label{eq:Psi-2D-3D}
\Psi^{\mathrm{3D}}(q) = \frac{e^2}{\epsilon_{0} q^{2} \Omega^{\mathrm{3D}}}  \\ 
\Psi^{\mathrm{2D}}(q) = \frac{e^2}{2\epsilon_{0} q \Omega^{\mathrm{2D}}}
% \Psi^{\mathrm{3D}}(q) &= \displaystyle \frac{4 \pi e^{2}}{q^{2} \Omega^{\mathrm{3D}}} \\
% \Psi^{\mathrm{2D}}(q) &= \displaystyle \frac{2 \pi e^{2}}{q \Omega^{\mathrm{2D}}}
\end{eqnarray}
%
where \(\Omega^{\mathrm{3D}}\) and \(\Omega^{\mathrm{2D}}\) are unit
volumes in 3D and 2D systems, respectively. The transition energy from
VB to CB in semiconductors, \(E_{k+q, l'}-E_{k, l}\), can be
approximated by the band gap \(E_{\mathrm{g}}\). When \(\omega \to 0\), we
have:
%
\begin{eqnarray}
\label{eq:eps-Lindhard-3D}
\varepsilon^{\mathrm{3D}}(q) &= 1 + \displaystyle \frac{q^{2} e^{2} N_{e}}{4 \pi \epsilon_0 \mu \Omega^{\mathrm{3D}}} \frac{E_{q}}{E_{\mathrm{g}}^{2}}
                          &= 1 + (\displaystyle \frac{\hbar \omega^{\mathrm{3D}}_{p}}{E_{\mathrm{g}}})^{2} \\
\label{eq:eps-Lindhard-2D}
\varepsilon^{\mathrm{2D}}(q) &= 1 + \displaystyle \frac{q e^{2} N_{e}}{4 \pi \mu \Omega^{\mathrm{2D}}} \frac{E_{q}}{E_{\mathrm{g}}^{2}}&= 1 + (\displaystyle \frac{\hbar \omega^{\mathrm{2D}}_{p}(q)}{E_{\mathrm{g}}})^{2} 
\end{eqnarray}
%
where \(\omega^{3D}\) and \(\omega^{\mathrm{2D}}\) are the plasma
frequencies in 3D and 2D (\(q\)-dependent), respectively.  We therefore
arrives at the conclusion of \(q\)-dependent dielectric response of 2D
systems. For a 3D material 
which is composed of stacks of 2D materials with inter-layer 
distance L (see Supplementary Figure \ref{fig-6}{\bf a}), it is 
straightforward comparing Supplementary Eq.\ref{eq:eps-Lindhard-3D} and
Supplementary Eq.\ref{eq:eps-Lindhard-2D}, that the 2D and 3D dielectric constants are related as:
%
%
\begin{equation}
\label{eq:relation-2D-3D}
\begin{aligned}
\varepsilon^{\mathrm{2D}}(q) &= 1 + \frac{\Omega^{\mathrm{3D}}}{2 \Omega^{\mathrm{2D}}} (\varepsilon^{\mathrm{3D}} - 1)q \\
                          &= 1 + \frac{L}{2}(\varepsilon^{\mathrm{3D}} - 1)q
\end{aligned}
\end{equation}
Using a relation between the molecular polarizability \(\alpha\)$^{2D}$ and \(\varepsilon^{\mathrm{3D}}\), through
 \(\alpha^{\mathrm{2D}}= L/4\pi (\varepsilon^{\mathrm{3D}} - 1)\)\cite{Cudazzo_2010_screen2D}, where $L$ is the layer thickness, and 
$\varepsilon^{\mathrm{2D}}(\alpha, \mu) = 1/2 (1 + \sqrt{1 + 32\pi e^2/3\hbar^2 \alpha \mu})$\cite{Olsen_2016_hydrogen}, 
where \(\mu=(m_{\mathrm{n}}^{-1} + m_{\mathrm{p}}^{-1})^{-1}\) is the
effective mass of the exciton, we finally get the relation between the high-frequency 2D dielectric constant and its 3D counterpart:
%
\begin{equation}
\label{eq:eps-2D-3D-final}
%\varepsilon^{\mathrm{2D}} = \frac{1}{2}(1 + \sqrt{1 + \frac{8 e^2 L \mu}{3 \hbar^2 (\varepsilon^{\mathrm{3D}} - 1)}})  %new Eq.
%\varepsilon^{\mathrm{2D}} = \displaystyle \sqrt{\frac{2}{3} (\varepsilon^{\mathrm{3D}} - 1) \mu L} %old Eq. 
\varepsilon^{\mathrm{2D}} = \sqrt{\frac{2 e^2 L \mu^{2}}{3\hbar^{2}} (\varepsilon^{\mathrm{3D}} - 1)} %old Eq. w/ SI units
\end{equation}
%
Such relation is relatively simple yet strong, showing that the 2D and
3D dielectric constants are bridged by the bulk electronic structure 
(reflected by \(\mu\)). This relation can be tested for 21 layered materials with reported
magnitudes of \(\varepsilon\) in both 2D and 3D (see Supplementary Table 1) relative to the 
HSE06 hybrid calculations as shown in Supplementary Figure \ref{fig-6}{\bf b}. 
Strikingly, the two sets of data show
a good agreement with a small mean average error (MAE) of
0.448. All 2D-compounds analyzed follow the linear trending curve, 
and many fall in the limit of fidelity of 95\% of the prediction 
despite of geometry and the nature of the band gap. Undoubtedly, 
the existence of such universal relation between
\(\varepsilon^{\mathrm{2D}}\) and \(\varepsilon^{\mathrm{3D}}\) greatly
facilitates the understanding of the dielectric constants of a broad variety of 2D
materials, giving prediction values with reasonable accuracy from its 3D-bulk analogue.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.90\linewidth]{fig6_v122317_vertical.pdf}
\caption{\label{fig-6}
{\bf Relationship between the 2D and 3D dielectric constants.} {\bf a}, Schematic illustration of the structures of a monolayer (left) and its bulk material (right) as a layered stack of 2D materials. The 2D dielectric constant shows strong \(q\)-dependency, while the 3D dielectric constant has macroscopic features. 
{\bf b}, Comparison between the \(\varepsilon^{\mathrm{2D}}\) predicted 
from \(\varepsilon^{\mathrm{3D}}\) (Supplementary Eq. \ref{eq:eps-2D-3D-final}) 
and \(\varepsilon^{\mathrm{2D}}\) from HSE06 hybrid calculations. 
}
\end{figure}

%This is a significant step toward an unified understanding of both 
%class of materials where a simple dimensionality model can provide a useful foundation 
%for easily evaluating the often scarce dielectric constants of layered compounds.

%%%%%%%%%%%%%%%%END%%%%%%%%%%%%%%%%%%

\pagebreak{}

\pagebreak{}

%\subsection{Figure S5: Correlation between $\varepsilon_{\parallel}$ and $C_{\mathrm{Q}}$ from VB}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=1.02\linewidth]{SI_figs/FigS2.pdf}
    \caption{{\bf Quantum capacitance over valence states.} Correlation between (\textbf{a}), $\varepsilon_{\parallel}$ and
    $C_{\mathrm{Q}}$ and (\textbf{b}),
    $C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}$ from VB. Differently from the
    nearly linear relation within each group in Figure 3,
    $\varepsilon_{\parallel}$ show almost no linear relation with
    $C_{\mathrm{Q}}$ retrieved from the VB of a 2D material.}
\label{fig-S9}
\end{figure}

\pagebreak{}

%\pagebreak{}

\subsection{Supplementary Table 1: Comparison between dielectric constants of 2D materials and 3D materials}
\input{2D_3D_20180205tian.tex}

\subsection{Supplementary Table 2: Fitting parameters for $C_{Q}$ }

We performed linear fitting on the dataset in Figure 3 via $y=ax+b$
for each group of 2D materials, and plotted the prediction margin as stripe shaders. 
The fitting parameters $a$, $b$, the coefficient of determination $R^2$ 
and the half-span of prediction margin $\Delta b$, can be found in Supplementary Table 2.

\begin{table}
\begin{center}
  \begin{tabular}{l|cccc|cccc}
    \hline
    &  \multicolumn{4}{c|}{$\varepsilon$ vs $C_{\mathrm{Q}}$} &
    \multicolumn{4}{c}{$\varepsilon$ vs $C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}$}\\
    \hline
    Group & \(a\) & \(b\) & \(R^{2}\) & \(x\Delta b\) & \(a\) & \(b\) & \(R^{2}\) & \(\Delta b\)\\
    \hline
    Group 4-2H & 1.65$\times10^{-3}$ & 1.33 & 0.584 & 0.956 & 1.82$\times10^{-3}$ & 1.97 & 0.862 & 0.533\\
    Group 4-1T & 3.01$\times10^{-3}$ & 1.45 & 0.782 & 0.504 & 2.11$\times10^{-3}$ & 2.11 & 0.766 & 0.540\\
    Group 6-2H & 8.20$\times10^{-3}$ & 3.35 & 0.501 & 1.51 & 0.0152 & 3.50 & 0.813 & 0.970\\
    Group 10-1T & 0.0102 & 0.701 & 0.753 & 1.05 & 6.39$\times10^{-3}$ & 3.18 & 0.765 & 1.03\\
    Group 14-2H & 3.79$\times10^{-3}$ & 1.67 & 0.996 & 0.0282 & 8.87$\times10^{-3}$ & 1.75 & 0.999 & 0.0139\\
    Group 14-1T & 6.68$\times10^{-3}$ & 1.54 & 0.991 & 0.097 & 0.0133 & 1.813 & 0.967 & 0.165\\
    \hline
  \end{tabular}
  \caption{Fitting parameters of Figure 3a ($\varepsilon$ vs
    $C_{\mathrm{Q}}$) and Figure 3b ($\varepsilon$ vs
    $C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}$) for different 2D materials
    groups. The slope ($a$), y-axis intercept ($b$), coefficient of
    determination ($R^{2}$) and half width of regression span
    ($\Delta b$) are reported. In general, magnitudes of $R^{2}$ values are
    higher and $\Delta b$ are lower comparing to the regression of
    $\varepsilon$ vs $C_{\mathrm{Q}}$ with $\varepsilon$ vs
    $C_{\mathrm{Q}}/E_{\mathrm{g}}^2$, indicating a better fitting
    result of the latter model.}
\end{center}
\end{table}

\pagebreak{}

\subsection{Supplementary Table 3: Database of \textit{Ab initio} calculations using HSE06 hybrid functional}
%\subsection{Bandgap and dielectric tensors}
\input{table_raw_data_modified.tex}

\subsection{Supplementary Figures 10-61: DOS-calculation results using HSE06 functional plus self-consistent spin-orbit coupling}
\input{DOS_figs.tex}

\pagebreak{}

\renewcommand\refname{Supplementary References}
\bibliography{ref_SI_v071618}

%\begin{thebibliography}{ref_SI_v012418}
%
%%\section*{Supplementary References}
%
%\end{thebibliography}

\end{document}

### 2018-08-12 paper/paper.tex
Draft version 20180812

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
% \usepackage{minted}
% \usepackage{graphicx}
%\usepackage{float}
%\usepackage{xcolor}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{fontspec}
%\renewcommand{\figurename}{}

\setkeys{acs}{usetitle = true}
\renewcommand*{\bibnumfmt}[1]{#1.}
\usepackage{lineno}
\linenumbers
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage[T1]{fontenc}
\renewcommand{\sfdefault}{cmr}

\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{D. H. and T. T. Contributed equally to this work}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{D. H. and T. T. Contributed equally to this work}

\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}

\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}

\author{Jonathan N. Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}

\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}

\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\keywords{two-dimensional materials, dielectric constant, screening, first principles calculation, band gap, binding energy, scaling relationships, Moss relation}
\date{}

\title{Universal Understanding of the Dielectric Constants of Two-Dimensional Materials}
%Universal Understanding of the Dielectric Constants of Two-Dimensional Materials
%Unified Understanding of the Dielectric and Electronic Properties of Two-Dimensional Materials
%Unified Understanding of the Dielectric Constants of Two-Dimensional Materials
\begin{document}

%\newpage{}

\begin{abstract}
Dielectric constant, which defines the polarization of the media, is a key quantity in condensed matter. It describes to a large degree the electron-electron interaction, 
which has a crucial effect on band gaps, optical excitations, and screening. 
Despite its fundamental transcendence, the determination of such quantity 
in two-dimensional materials is a challenging task because 
their intrinsic low-dimensionality hampers accurate measurements.  
Here we show that, for the wide range of known layered crystals, 
a unifying framework for predicting dielectric constants using a 
single universal descriptor can be established. 
A set of scaling relations is found linking dielectric 
constants and band gaps which results in a general 
electronic structure despite of the chemical and physical properties of the layer. 
This points to a Moss-like behavior where novel descriptors 
for photoconductivity and quantum-capacitance appear naturally. 
Our results successfully rationalize the available empirical data and lay the foundation of 
future electronic-dielectric design strategies.

\end{abstract}

\section{Introduction}
\label{sec:orgb64aacb}

The dielectric constant (also known as the relative permittivity) 
which characterizes the screening of the electromagnetic field within
a medium, plays a crucial role in bridging various fundamental material
properties regarding electron-electron and electron-photon
interactions, such as electronic polarization, polarizability, optical
absorption, and exciton binding energy. 
The central place
of dielectric constant in physics drives the pursuit for a
unified model between electronic and dielectric or optical properties of materials. 
In fact, some pioneering works in the 50's discovered relationships between the dielectric
constants (high-frequency) $\varepsilon$ and other properties, in particular the bulk band gap
$E_g$. Moss\cite{Moss_1950_relation,Moss52book,Moss59book} 
showed that $E_g$ and $\varepsilon$ 
follow a semi-empirical relationship, known as the Moss relation
\cite{Moss_1950_relation,Moss52book,Moss59book,Moss_1985_n_Eg}:

\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} = 95~ eV
\end{equation}
which can be related to the high-frequency refractive index $n_{0}$, via $\varepsilon=n_{0}^{2}$,   
and the long wavelength threshold $\lambda_{c}$ which determines the photoconductivity properties\cite{Moss_1950_relation}:

\begin{equation}
\label{eq:Moss-wave}
n_{0}^{4} /\lambda_{c} = 77~ \mu m^{-1}
\end{equation}

Other similar
semi-empirical models for the relationship between \(\varepsilon\) and
\(E_{\mathrm{g}}\) were also proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. 
Despite the minute difference between the formulae used, it is clear that the
there exist certain general electronic relations in bulk
semiconductors, which are scaled by the dielectric constant and further
account for the variation in band gap between different
materials. The existence of such general relationship is also of high
practical importance: it is generally more straightforward to measure
the band gap \(E_{\mathrm{g}}\) than the dielectric constant \(\varepsilon\),
as the latter is strongly dependent on several critical 
details on the sample measurements, such as contamination, disorder, 
and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty starting from the magnitude of its band gap, 
as well as identify whether a compound is photoconductor. 
Indeed, the usage of such relations has spread out across 
the semiconductor community for more than 60 years.

Two-dimensional (2D) materials, the atomically-thin crystalline
layers, are known to have distinct electronic properties from their
bulk counterparts
\cite{Ando_1982_electron_2D,Stern_1967_polarizability_2DEG}. One
important feature of 2D materials is that the electric screening is
attenuated and anisotropic\cite{Das-Sarma:2011aa,Ando_1982_electron_2D}. 
The empirical
relations of dielectric constant in bulk materials, like the Moss
relation (Eq.\ref{eq:Moss-relations}), is thus invalid within the context of 2D materials, and has
to be modified. The quest for a general understanding of the
dielectric constant of 2D materials has even greater importance than
the bulk materials: the dielectric constant of a 2D material is
highly influenced by its surrounding environment
\cite{Keldysh_1979_eps_multi,Trolle_2017_eps_subst} and it has caused
considerable debate experimentally\cite{Raja:2017aa,Chernikov_2014_EB_MoS2_2D3D}. 
On the contrary, other
optoelectronic properties such as the band gap and binding energy can
be experimentally more easily assessed. 
The lack of both sufficient
data bank and sound experimental results requires the force from
computational chemistry to discover the underlying relation between
the dielectric constant and other properties of 2D materials.

Here we show that the dielectric constant provides a unique opportunity for 
the development of universal scaling relationships between electronic and 
dielectric properties of different 2D materials. The reduced screening features 
allow to observe the true nature of the electronic interactions in 
the 2D-world, which indicates a universal behavior despite the chemical 
and physical composition of the material. 
We explicitly obtained scaling 
relationships between dielectric constant and several 
other quantities, such as band gaps, and exciton binding 
energies, which describes a vast library of layered materials. 
This fundamental understanding can be further explored
looking for a new descriptor of photoconductivity, 
where 2D-photoconductors follow a similar pattern on refractive index 
and absorption edge.    
Moreover, using multiscale methods we unveil the close relation between quantum-capacitance and dielectric 
constants, which provides a map of the screening properties in terms of orbital decompositions.  
This framework is also used to successfully unify the concept of dielectric constant 
at different dimensionalities as its 2D-magnitude is obtained 
throughout the knowledge of few details of the 
3D-bulk electronic structure. The discovery of scaling relationships 
between electronic and dielectric properties in 
2D compounds introduces a new and general pathway for the exploration of their complex 
physical and chemical phenomena, and ultimately pushes the boundary 
of the understanding of electronic screening in two-dimensions.

\section{Results}
\label{sec:org93965d9}

\subsubsection{2D Moss relations}
We study several types of 2D materials of different electronic and optical properties, 
including transition metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (GaS, GaSe), cadmium halides (CdX$_2$, X=Cl, I), 
hexagonal boron nitride (hBN), graphene derivatives (fluorographene (f-graphene), graphane) 
thin layers of organic-inorganic perovskites (CH$_3$NH$_3$PbBr$_3$),  
and phosphorene as displayed in Figure \ref{fig-1}{\bf a}. For the TMDCs, we consider 
2 lattice phases, namely the 2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group). 
The elements contained in the materials involved in our 
simulations are summarized in the periodic table in Fig. \ref{fig-1}{\bf b}, 
which are grouped accordingly to their dielectric-electronic scaling 
relationships as discussed below. 
%%%Write here PBE data %%%%%%%
We calculate both the high-frequency dielectric constant tensor  
$\varepsilon_{\alpha,\beta}$ 
and band gaps $E_{g}$ at the level of 
hybrid density functional theory (DFT) using the Heyd-Scuseria-Ernzerhof
hybrid functionals (HSE06) including spin-orbit 
coupling to avoid limitations on the description of band gaps 
and dielectric constants (see {\it Methods} for details). 
We have also utilized different 
functionals (e.g. PBE) and approximations, 
such as many-body $G_0W_0$, which resulted in similar conclusions. 
See Supplementary Note 1 and Supplementary Figures 1-3 for details.

The in-plane $\varepsilon_{\parallel}$ and out-of-plane $\varepsilon_{\perp}$ 
components of the dielectric tensor as functions of E$_{g}$
are plotted in Figure \ref{fig-2}{\bf a-b}, respectively. 
For the $\varepsilon_{\parallel}-E_{g}$ relation, we notice two distinguished 
behaviors: a linear (green circles) and a power law (orange squares) 
variations of $\varepsilon_{\parallel}$ with $E_{g}$. Interestingly, such division 
is also element-dependent: the
TMDCs of group 4 and 14, hBN, graphene derivatives, and phosphorene
belong to the power group, while TMDCs of group 6 and 10, GaS, GaSe,
and CdI\(_{\text{2}}\) following the linear law (see Fig. \ref{fig-1}{\bf b}). 
The best fitting of the power group gives the relation:

\begin{equation}
\label{Moss-2D-power}
\varepsilon_{\parallel}=3.68/E_{g}^{0.50}
\end{equation}
or in term of the refractive index and long-wavelength:

\begin{equation}
\label{Moss-2D-power-lambda}
n_{0}^{4}/\lambda_{c} = 10.92~ \mu m^{-1}
\end{equation}

The linear group is well fitted with:

\begin{equation}
\label{Moss-2D-linear}
\varepsilon_{\parallel}=7.50-1.37{\rm E}_{g} 
\end{equation}

We notice that the power law of 2D layers (Eq. \ref{Moss-2D-power}) 
resembles the 3D Moss relation (Eq. \ref{eq:Moss-relations})
for bulk materials, however with a much smaller constant, 
as seen in the comparison in Fig. \ref{fig-2}{\bf a} using Eq. \ref{eq:Moss-relations}. 
The linear law in turn 
differs from the original Moss relation, but it is close to other approaches \cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}.
Conversely, $\varepsilon_{\perp}-E_{g}$ relations show much less
variation than the in-plane component: most of the values of 
$\varepsilon_{\perp}$ are within 1.2 and 1.6, indicating
that the dielectric screening perpendicular to the 2D plane is greatly
attenuated. The scattered dots of the power group and the linear group
overlap with each other in Figure \ref{fig-2}{\bf b}, showing that
the $\varepsilon_{\perp}$ has almost no material dependence in terms of the band gap. 
Therefore, it is accurate to state that out-of-plane screening excitations in a monolayer 
would behave similarly despite of its electronic and optical structures.   
Moreover, our \emph{ab initio} calculation results show that the in-plane dielectric
constant of a 2D material is clearly related with its band gap through scaling relations, 
either linear or non-linear (power-law). %maybe a new paragraph %
It is worth mentioning very few experimental reports on either $\varepsilon_{\perp}$ or 
$\varepsilon_{\parallel}$ for 
monolayer materials\cite{BN-epsilon,Mos2-epsilon,In2Se3-epsilon}. 
Nevertheless, the available data 
follows our scaling relations as displayed in Fig. \ref{fig-2}{\bf a}.

The relations between $\varepsilon$ and E$_{g}$
distinguishes from the 3D Moss equation and other approaches\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev},  
which indicates that the underlying mechanism in 2D
materials may be different from their bulk counterparts. 
Nevertheless, the possibility to use universal scaling relationships
that accurately describe a vast library of layered compounds using 
a single parameter have not been previously demonstrated. We postulate 
that this is possible because of the reduced screening observed in monolayers, and,
therefore, the dielectric constant does not depend sensibly 
on the material geometry. 
To verify the precision of the $\varepsilon-E_{g}$ relations
discovered, we compare the dielectric constants computed from the
linear and power laws using only the \(E_{g}\) values as input, compared with
the \(\varepsilon\) obtained by time-consuming HSE06 simulations. 
Figure \ref{fig-3}{\bf a} demonstrates the excellent agreement between our 
model's predictions and calculated HSE06 \(\varepsilon_{\parallel}\) across a wide variety of 
2D crystals. The linear correlation of the two sets of
data show a slope of 0.9976, indicating that the model can 
represent well the relation between \(\varepsilon_{\parallel}\) and
\(E_{g}\) by a numerical error smaller than 0.2\%. 
We perform a similar analysis for the out-of-plane
dielectric constant $\varepsilon_{\perp}$ in Figure \ref{fig-3}{\bf b}. 
We notice that the \(\varepsilon_{\perp}\) calculated
using the model has larger deviation from the \(y=x\) line than
\(\varepsilon_{\parallel}\). However, the scale utilized corresponds to magnitudes 
in the range of 1.10 to 1.40, which is 20 times smaller than that at in-plane component. 
This indicates that the model's prediction for \(\varepsilon_{\parallel}\) would give magnitudes within 0.05-0.12 differences relative to HSE06 calculations, 
which is in the numerical accuracy of the simulations. 
The fact that \(\varepsilon_{\perp}\) has
less dependency on \(E_{g}\) clearly distinguishes from the 3D
Moss relation, as a result of the attenuated out-of-plane dielectric
screening in 2D materials. 
Considering this relatively small dispersion
of the out of plane component, we may
conclude that the in-plane dielectric constant of 2D materials has
much greater impact on other properties as normally assumed in 
optical measurements\cite{Chernikov_2014_EB_MoS2_2D3D}. 
For the rest of the discussions we
will focus on the relation between \(\varepsilon_{\parallel}\) with other
2D properties.
It should be noted that simulations carried out at the level of PBE functional resulted in considerably larger 
differences between the model predictions and calculated \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) (see Supplementary Figure 3). Deviations from either a purely linear fitting without a finite cumulative factor at the model, or 
magnitudes that differ by more than $\sim$24\% between simulations 
and scaling relations are observed. 
%We have also compared our HSE06 simulation results against 
%more robust but computationally involved methods, such as many-body 
%Green's function method ($G_0W_0$) and 
%Bethe-Salpeter (BSE) equation as show in Supplementary Figure 4. We observe that 
%some $G_0W_0$ band gaps are overestimated  relative to the HSE06 ones as they do not  
%not include the electron-hole corrections. Such corrections are included at the level of 
%$G_0W_0$-BSE which shows a sound agreement with the HSE06 magnitudes. This 
%fully justifies the choice of an accurate approximation such hybrids in the 
%description of the electronic-dielectric interplay in 2D materials.

%The model obtained 
%using such values give substantial differences from the 
%calculated PBE data (see (Figure S2 in the {\it Supplementary Information})). 
%%%

\subsubsection{A descriptor for photoconductivity in two-dimensional materials}

The generality of the Moss' relation was initially used to identify compounds that 
could develop photoconductivity\cite{Moss_1950_relation,Moss-book1}. 
One of the key reasons is the rough constant threshold of Eq.\ref{eq:Moss-wave} for a vast 
library of 3D-bulk materials. This indicates that materials that are photoconductors assume 
similar pattern over band gaps and dielectric constants. 
In practice the photoconductivity depends on several factors, such as optical absorption coefficient, 
mean-free-time, carrier mobility, and thickness. Figure \ref{fig-3}{\bf c} shows, however, 
that a comparable argument as that used by Moss 
holds for 2D materials in terms of  
the behavior of $n_{0}^{4}/\lambda_{c}$ over the entire dataset. 
We have not separated the materials where photoconductivity has been observed 
experimentally from those that would need further study. This incidentally could give different 
line threshold not shown here. It is clear that materials that are photoconductors display 
similar electronic-dielectric properties via close magnitudes of $ \langle n_{0}^{4}/\lambda_{c} \rangle$ 
as initially suggested by Moss\cite{Moss_1950_relation,Moss59book,Moss52book,Moss_1985_n_Eg}. 
On the power-law group, compounds like 2H-SnS$_2$, 
2H-HfS$_2$, 1T-HfS$_2$, 1T-SnSe$_2$, 1T-SnS$_2$, and phosphorene 
have been observed photo-conductivity response, even though different groups 
have reported distinct magnitudes\cite{photo-2Dmaterials,Andres15}. 
Similarly as observed in the 
linear-law compounds, the average value $ \langle n_{0}^{4}/\lambda_{c} \rangle=31.22~\mu m^{-1}$
is larger than that for power-law materials but most of the photoconductors 
assume close magnitudes of $n_{0}^{4}/\lambda_{c}$. Several layered systems 
shown in Fig. \ref{fig-3}{\bf c} are still to be explored experimentally 
to give a thorough picture of the photoconductivity in 2D. However, 
this simple relation between refractive index and 
long wavelength seems to give reliable power-prediction 
on potential layers that could develop such 
features (see Supplementary Note 2 and Supplementary Figure 5 for additional discussions).

%%%%%Tian you may start writing from here%%%%%%%%%

%%%%%%%%%%%

\subsubsection{Correlating quantum-capacitance and dielectric constants}

This multiscale approach can also be used to show that other macroscopic properties are directly
correlated with the dielectric constant, such as the quantum-capacitance. 
Similar arguments can be used to link dielectric constants at different dimensionalities, such as between 2D-monolayers and their 3D-bulk counterparts, as well as obtain relations between dielectric constants and details of the electronic structure and exciton biding energies. See Supplementary Notes 3-4 and Supplementary Figures 6-8 for detailed discussions.
The random phase approximation (RPA) describes the imaginary dielectric function \(\varepsilon_{2}\)
at long wavelength limit as \cite{Slyom_2008_fundBook,Dressel:2002aa}:

\begin{equation}
\label{eq:RPA-eps2}
\epsilon_{2}(\omega) = \frac{1}{4 \pi \epsilon_0} (\frac{2\pi e}{m_{e} \omega})^{2} \sum_{c, v} J_{cv}|P_{cv}|^{2}
%\varepsilon_{2}(\omega) = (\frac{2 \pi e}{m \omega})^{2} 
%                     \sum_{l,l'} J_{l,l'}(\omega) < l | \mathbf{\mathit{p}} | l' >^{2}
\end{equation}
where $m_e$ is the electron mass, \(\omega\) is frequency, \(c\) and \(v\)
denote the conduction and valence states, \(J_{cv}\) is the joint density
of states (JDOS) and $P_{cv}$ is the dipole operator. The
difference between the \(\varepsilon-E_{\mathrm{g}}\) relations actually
comes from the forms of JDOS in 2D and 3D systems \cite{Ha_2011_introductry}. 
For a 3D semiconductor, the JDOS is energy-dependent:

\begin{equation}
\label{eq:JDOS-3D}
J^{\mathrm{3D}}(\omega) = \frac{1}{2\pi^{2}} (\frac{2 \mu}{ \hbar ^{2}})^{\frac{3}{2}}
                        (\hbar \omega - E_{\mathrm{g}})^{\frac{1}{2}}
\end{equation}
while on strictly 2D, JDOS is a step function and independent of \(\omega\):

\begin{equation}
\label{eq:JDOS-2D}
J^{\mathrm{2D}}(\omega) = 
                        \begin{cases}
                        \displaystyle \frac{1}{\pi} \frac{\mu}{\hbar^{2}} & \omega > E_{\mathrm{g}} \\
                        0                                   & 0 < \omega < E_{\mathrm{g}}
                        \end{cases}
\end{equation}

The real dielectric function can be derived using the Kramers-Kronig
relation \cite{Adachi_1987_dielGaP}:

\begin{equation}
\label{eq:KKR}
\varepsilon_{1}(\omega) = 1 + \frac{2}{\pi} \int_{0}^{\infty}
                     \frac{\omega' \varepsilon_{2}(\omega')}{\omega'^{2} - \omega^{2}} d\omega'
\end{equation}
in the \(\omega \to 0\) limit, and assuming that the dipole transition
matrix $P_{cv}$ is constant we have:

\begin{equation}
\label{eq:eps1-3D}
\varepsilon_1^{\mathrm{3D}}(\omega \to 0) = 1 + \frac{e^2 (2 \mu) ^{\frac{3}{2}}}{8\pi \epsilon_0 m_{e}^{2} \hbar^{2}}E_{\mathrm{g}}^{-\frac{3}{2}}P_{cv}^{2}
%\varepsilon_{1}^{\mathrm{2D}}(\omega \to 0) = 1 + \frac{e^{2} (2 \mu)^{\frac{3}{2}}}{2 m^{2} \hbar}
%                                  E_{\mathrm{g}}^{-\frac{3}{2}} P^{2}
\end{equation}
and
\begin{equation}
  \label{eq:Dressel-eps1}
  \begin{array}{lll}
  \varepsilon_{1}^{\mathrm{2D}}(\omega \to 0) &= \displaystyle 1 + \frac{2}{\pi} \frac{1}{4 \pi \varepsilon_{0}}
                         \frac{4 \pi^2  e^2}{m_{e}^{2}}
                         \frac{\mu}{\pi \hbar^2} P_{cv}^2
                         \int_{E_{g}/\hbar}^{\infty}
                      \frac{1}{\omega'(\omega'^{2} - \omega^{2})} \mathrm{d} \omega' \\
                    &= \displaystyle 1 + \frac{1}{4 \pi \epsilon_{0}} \frac{8 e^2 \pi}{m_{e}^{2}}
                      \frac{\mu}{\pi \hbar^{2}} \frac{1}{2 \omega^{2}} P_{cv}^{2}
                      \ln(1 - \frac{\omega^{2}}{\omega'^{2}}) \Big|_{E_{g}/\hbar}^{\infty} \\
                    &\approx \displaystyle 1 + \frac{1}{4 \pi \varepsilon_{0}}
                      \frac{4e^2 \pi}{m_{e}^2} \frac{\mu}{\pi \hbar^2}
                      \frac{\hbar^2 \omega^2}{\omega^2 E_{g}^2} P_{cv}^2\\
                    &= \displaystyle 1 + \frac{1}{4 \pi \varepsilon_{0}}
                      \frac{4 e^2 \pi \hbar^2}{m_e^2 E_g^2} J_{cv} P_{cv}^{2}
  \end{array}
\end{equation}
\\
It shows that, unlike in the 3D system, the 2D dielectric constant
has direct relation to JDOS and \(E_{\mathrm{g}}\). The JDOS in a free-electron model can be
written as the combined effect of the density of states (DOS) at both
conduction and valence bands: $J(E)^{-n} = \mathrm{DOS}_{\mathrm{C}}(E- E_{\mathrm{g}})^{-n} + \mathrm{DOS}_{\mathrm{V}}(E- E_{\mathrm{g}})^{-n}$, where n=2/3 for 3D case and n=1 for 2D case. 
Note that DOS is essentially the
quantum capacitance (\(C_{\mathrm{Q}}\)) of a material:
\(C_{\mathrm{Q}}(E) = \mathrm{DOS}(E) e^{2}\). Indeed, it is natural to look
into the relation between \(C_{\mathrm{Q}}\) and \(\varepsilon\), which is
also a characteristic of a material's capacitance.

In order to extract the \(C_{\mathrm{Q}}\) values, we calculated the DOS of each 2D
material by averaging the values at a band edge charge cutoff of 5 x10$^{13}$ $e/cm^2$ (see {\it Methods} for details). 
We first plot \(\varepsilon_{\parallel}\) as a function of \(C_{\mathrm{Q}}\) in the CB for 
various MX$_2$ materials studied here, as shown in Figure \ref{fig-5}{\bf a}.  Although the   %%%%%%%%%%%%%%%%%%
dispersion seems too wide to get a universal relation when considering
all the data together, we find that when categorizing the data by the
metal element group and lattice type, each $\varepsilon - C_Q$ dataset seems to be following linear
relations. We therefore performed linear fitting via $y=ax+b$
for each group of 2D
materials, and plotted the prediction margin as stripe shaders in
Fig. \ref{fig-5}{\bf a}. By varying $b$, we also show the 
prediction margin of each group as stripe shader. 
The fitting parameters $a$, $b$, the coefficient of determination $R^2$ 
and the half-span of prediction margin $\Delta b$, can be found in Supplementary Table 2.

%Interestingly, although the coefficient of determination
%vary among the groups (group 14-1T and group 14-2T show \(R^{2}\) higher
%than 0.95, while group 4-2H and group 6-2H show \(R^{2}\) less than
%0.8), they all show a similar intercept of ca. 1.70.
%%\begin{center}
%\fbox{
%\begin{minipage}[c]{.8\linewidth}
%\textbf{\textsf{\textsc{TODO}}} Add the data sheet in SI
%
%\end{minipage}
%}
%\end{center}
When \(C_{\mathrm{Q}}\) decays to 0 the 2D materials display an universal dielectric
constant. The discrepancy between the value of the intercept may
also be caused by the existence of long-range Coulombic interactions
in the calculations, similar to the phenomenon seen in Figure
\ref{fig-4}{\bf a}. The slope of the \(\varepsilon-C_{\mathrm{Q}}\) curve in each
group indicates that the materials with metals of the same group, have
similar values of dipole transition matrix \(P\). 
Note that in Eq.\ref{eq:Dressel-eps1}, \(E_{\mathrm{g}}\) also serves as a variable apart from
JDOS, we therefore compare the relation between \(\varepsilon_{\parallel}\)
and \(C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}\), as shown in Figure
\ref{fig-5}{\bf b}. Better regression results can be observed for almost all
groups compared with the \(\varepsilon_{\parallel}-C_{\mathrm{Q}}\)
relations. The slopes are also higher than the corresponding groups in
the \(\varepsilon-C_{\mathrm{Q}}\) relations, since the majority of the
materials we studied has \(E_{\mathrm{g}} > 1\) eV. The better
regression results using \(C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}\) indicates
the validity of Eq.\ref{eq:Dressel-eps1} in predicting the 2D dielectric constant. 
Unlike the relation we found for
\(\varepsilon-E_{\mathrm{g}}\), \(\varepsilon-\alpha\) and
\(\varepsilon-E_{\mathrm{b}}\), a universal scaling relation between
\(\varepsilon\) and \(C_{\mathrm{Q}}\) or \(C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}\)
does not seem to exist, instead the relation is found to be more
element-specific. We have also examined the \(\varepsilon\) as a function
of \(C_{\mathrm{Q}}\) or \(C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}\) in the VB,
as shown in Supplementary Figure 9. However a similar scaling relation seems 
inexistent. Such difference between the \(C_{\mathrm{Q}}\) in CB and VB
may imply that the unoccupied orbitals have more influence on the
dielectric constant of 2D materials.

%%%%%%%%%%Include tian's text herein 
Note that most the materials studied here have similar geometry, such
similarity between the $\varepsilon$ and $C_{\mathrm{Q}}$ (or
$C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}$) may be explained by the orbitals
close to the Fermi level. For instance, comparing TMDCs with metal
atoms from different groups, the change of orbital near the Fermi
level is mainly due to shift of $d$-orbitals, while the $\sigma$ and
$\sigma^*$ orbitals with mainly $s$ and $p$ components, show relatively
less change\cite{Liang84,Kuc14}. Figure \ref{fig-5}\textbf{c} show the
relative shift of orbitals in group 4, 6 and 10 (semiconducting)
TMDCs. The $d_{z^2}$ orbital which has a sharp increase of DOS and
contributes mainly to the CB in group 4, shifts below the Fermi
level in group 6, with the $d_{xy}$ and $d_{x^2-y^2}$ orbitals
with a slower DOS increment as the mainly-contributing orbital in the
CB. When the $d$-orbital occupation number further increases in group
10, all $d$-orbitals shift below the Fermi level, leaving the
$\sigma^*$ orbital as the major component of the CB. The shift of the
$d$-orbital due to increasing occupation has direct effect on the DOS
shape of CB. As seen in Figure \ref{fig-5}\textbf{d}, the two group 6
TMDCs (MoS$_{2}$ and WS$_{2}$) show a plateau with relative low DOS of
0.1 states/eV$^{3}$ at the CB edge, while the group 4 (ZrS$_{2}$
and HfS$_{2}$) show a much higher DOS plateau of $\sim$0.5 states/eV$^3$. 
On the other hand, all materials show similar DOS
shapes at the VB edge. Therefore, the apparent distinction between the states at the
CB edge can be explained by the shift of $d$-orbital as stated above, which is 
also consistent with the fact that the slope of regression between
$\varepsilon$ and $C_{\mathrm{Q}}$ in group 6 is much larger than that in
group 4. The atomic orbital analysis provides a good explanation for grouped
behavior of the $\varepsilon$-$C_{\mathrm{Q}}$ regression relations, and
provides more insights into the origin of the dielectric constant of
2D materials.

%%%Elton's comments%%%%%%%%%%
%Performing an orbital-based analysis on the states responsible 
%for the dielectric screening we observe that most 
%of the $d$-states for group 4, 6 and 10 shift down below the Fermi level with increasing 
%of the occupation number as displayed schematic in Figure \ref{fig-5}{\bf c}. 
%The higher DOS at CB for group 4 may be contributed by 
%the $dz^2$ orbitals; on the other hand the low CB DOS 
%of group 6 and group 10 may be contributed by other 
%orbitals with smoother edges. A comparison between group 4 and 6 in terms of a normalized 
%DOS by $E_g^2$ for illustrative materials (Figure \ref{fig-5}{\bf d}) 
%reveals the main features at CB for both groups. 
%Indeed, group 4 has a more continuous CB edge that extends 
%for several tenths of meV's and larger DOS. This can be translated 
%in higher magnitudes of \(C_{\mathrm{Q}}\) 
%over the accumulated charge density $\sigma (E)$ (see {\it Methods} for details), and therefore 
%less abrupt variation of $\varepsilon_{\parallel}$ as 
%function of \(C_{\mathrm{Q}}/E_{\mathrm{g}}^{2}\) (Fig. \ref{fig-5}{\bf b}).  
%Group 6 in its turn shows a step-edge with a small DOS relative to group 4 at the same energy range, which consequently imply low magnitudes of \(C_{\mathrm{Q}}\) and a sudden dependence of 
%$\varepsilon_{\parallel}$. Group 10 seems to follow a similar description not show here. 
%Overall this analysis suggests a close correlation between DOS and $\varepsilon_{\parallel}$ 
%throughout the quantum capacitance, which seems not established so far for 2D-materials.

%%%%%%%%%%

\section{Discussion}
\label{sec:org621792b}

In summary, our findings reveal a fundamental knowledge of the close link between 
dielectric, optical and electronic properties of 2D materials. The scaling relationships found
between dielectric constants and several other important quantities, such band gaps, 
excitonic binding energies, and quantum capacitance imply that such correlation is unique 
in the 2D-world. Physical magnitudes apparently with a no 
clear interdependence in 3D-bulk display a strong connection, which seems to be universal 
to different types of 2D crystals. One of the main driving 
forces for such unusual behavior is the reduced screening 
features present in layered materials, which is not present 
in bulk compounds.

We have shown that a 2D-analogous of the famous Moss' 
relation between band gaps and 
dielectric constants indeed exists with a similar functional 
form but different energy constants. 
Different compounds can also display different scaling relationships, 
which are accurate enough to reproduce computationally 
expensive hybrid HSE06 calculations at precisions 
near 99\% of the simulations just using a single descriptor. 
This allows to use efficient scaling schemes to quickly explore untouched physical
properties (e.g. photoconductivity) searching for new descriptors 
that could help in their identification.

An in-depth analysis of the dielectric function within the random phase approximation allowed to 
create a direct relation between quantum capacitance and dielectric constants 
using band gaps as a scaling parameter. Several materials throughout different 
groups of the periodic table follow a systematic pattern over the orbital states near the Fermi level, 
which explains most of the features of the model. A direct inter-relation between 
dielectric constants at 2D and 3D bulk is found based on the Lindhard formalism. 
This equation is used to promptly determine the dielectric constant of any 
2D material using simple arguments from the band structures of its bulk 
counterpart. This is a clear step towards new methods of materials screening using bulk properties. 
Our findings pave the way to understand and engineer 
the electronic and dielectric properties of a large library of vdW materials 
for different technological applications in an unified and unprecedented way.

%The computational screening performed at the level of HSE06 functional is an instrumental tool 
%for a reliable description of band gaps and dielectric constants, and consequently crossovers between physical variables. 
% 
%
%The methods presented herein are meant to quickly determine the 
%dielectric constant of any 2D-material using simple scaling relationships based 
%on the knowledge of the band gap.

\section{Methods}
\label{sec:org3881bef}

\subsubsection{Density functional theory calculations}
All first-principles density functional theory (DFT) calculations 
were performed using the VASP code\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2}. 
Projector Augmented Wave (PAW) approach\cite{Kresse_1999_pseudopotentials,PAW-1} 
using the new optimized GW potentials were utilized. Electronic and dielectric properties 
were initially calculated using generalized gradient approximation 
using PBE functional\cite{PBE}. The self-consistent field (SCF) convergence was set to 1.0x10$^{-8}$ eV. We also took into account a fractional component of the exact
exchange $E_x$ from the Hartree-Fock (HF) theory hybridized with the DFT 
exchange-correlation functional at the level of the range-separated HSE06 hybrid
functional\cite{HSE03,HSE06}. The exchange-correlation energy is given by:

\begin{equation}
E_{xc}^{HSE}=\alpha E_{x}^{HF, SR} (\omega) + (1-\alpha) E_{x}^{\omega PBE, SR}(\omega) + E_{x}^{\omega PBE, LR} (\omega) + E_c^{PBE}
\end{equation}
where $E_{x}^{HF, SR}(\omega)$ is the short-range (SR) HF exchange; $E_{x}^{\omega PBE, SR}(\omega)$ and $E_{x}^{\omega PBE, LR}(\omega)$ are the short and long range (LR) components of the PBE 
exchange functional, respectively; $\omega= 0.20~\AA^{-1}$ is the screening parameter, 
which defines the separation of the SR and LR exchange energies, and $\alpha$ is the 
HF mixing factor that controls the amount of exact Fock exchange energy 
in the functional.\cite{HSE03,HSE06} Note that HSE functional with $\alpha =0$ becomes the
PBE functional.\cite{PBE} Therefore, any limitation of the exchange and correlation functional in the chemical and physical description of the two-dimensional systems 
is improved. It is important to point out that 
such approach is considerably more expensive than 
the PBE functional, which makes our dataset valuable for 
further modeling analysis (see Supplementary Table 3). 
Spin-orbit coupling (SOC) was explicitly included in the calculations.

The geometries were converged both in cell
parameters and ionic positions, with forces below 0.001~eV/$\AA$. 
A vacuum spacing of at least 25 $\AA$ was used for each material. 
A {\bf k}-point grid of \(7\times7\times1\) was used to relax, with an initial relaxation
carried out at PBE level and a subsequent relaxation carried out at
HSE06, allowing both cell parameters and ionic positions to
relax each time. In VASP, the tag {\sc PREC=High} was used, giving a plane
wave kinetic energy cutoff of 30\% greater than the highest given in
the pseudopotentials used in each material, guaranteeing that absolute
energies were converged to a few meV. A default plane-wave cutoff of 800 eV 
was used in all simulations. A final HSE06 calculation with SOC was then carried out
using a \(21\times21\times1\) {\bf k}-point in the unit cell for each system.

Density functional perturbation theory (DFPT) is used to calculate the ion clamped
static dielectric tensor showed in the manuscript as\cite{Gajdos:2006aa}:

\begin{equation}  
\varepsilon_{\infty}=1/\varepsilon^{-1}_{\alpha,\beta}(0,0) \equiv 1/\lim_{q \to 0}[\varepsilon^{-1} (\mathbf{q},\mathbf{q+G})]
\end{equation}
with $\mathbf{G}=0$. Off-diagonal components of $\varepsilon_{\alpha, \beta}$ ($\alpha \neq \beta$) generally assume 
negligible magnitudes, with the diagonal components $\varepsilon_{\alpha, \beta}$ ($\alpha = \beta$) being 
similar in-plane, e.g. $xx=yy$. 
We assume that the ions do not relax in the
external electric field at optical frequencies and hence the ionic
contribution to the dielectric constant is negligible. 
In fact, this is the case for 2D-materials as recently found\cite{relax-epsilon}. 
Local field effect corrections are included at the exchange-correlation 
potential $V_{xc}$ at either PBE or HSE06 levels.

%\subsubsection{Many-body $G_0W_0$ and $G_0W_0-BSE$ calculations}
%
%To benchmark the calculations of band gaps using the HSE06 functional, 
%we have performed simulations at the level of many-body $G_0W_0$ approximations 
%plus Bethe-Salpeter equation (BSE). 10 occupied and 86 unoccupied bands were included in the 
%calculations with SOC included.

%\begin{equation}
%\varepsilon = 1-\upsilon_{c} \chi_{0} (1-f_{xc} \chi_{0})^{-1}
%\end{equation}
%where $\upsilon_{c}$ is the 
%
%$f_{xc}$ is the functional derivative of $V_{xc}$ with respect to the electron density as: 
%
%\begin{equation}
%f_{xc}(1,2)=\frac{\delta V_{xc}(1)}{\delta \rho(2)}
%\end{equation}

\subsubsection{Quantum capacitance}
For quantum capacitance analysis, the quantum capacitance
$C_{\mathrm{Q}}(E)$ at certain energy level $E$ is calculated using
the relation $C_{\mathrm{Q}}(E)=\mathrm{DOS}(E)e^{2}$, where
$\mathrm{DOS}(E)$ is the density of states (averaged by cell
area). The DOS value is calculated at the energy level with a charge
cutoff such that
$|\sigma(E)| = 5 \times 10^{13}\ e\cdot\mathrm{cm}^{-2}$, calculated by
the relation of accumulated charge $\sigma(E)$ at CB or VB:

\begin{equation}
  \label{eq:method-2}
  |\sigma(E)| = \left|\int_{E_{\mathrm{BE}}}^{E} \mathrm{DOS}(E')e dE' \right|
\end{equation}
where $E_{\mathrm{BE}}$ is the energy of the CB or VB band edge. 
The DOS's used for the calculation of $C_{\mathrm{Q}}$ 
for all 2D-materials using HSE06 hybrid functional is shown in Supplementary Figure 8-59.

%\subsection{Additional information}

\subsubsection{Data Availability}

The data that support the findings of this study 
are available within the paper and its Supplementary Information.

\subsubsection{Competing interests}
The Authors declare no conflict of interests.

%{\bf Supplementary Information} accompanies this paper at
%http://www.nature.com/naturecommunications

\subsubsection{Acknowledgments}
We acknowledge valuable discussions with Fritz B. Prinz, and Andres Castellanos-Gomez. C.J.S. and T.T. are grateful for financial support from ETH startup funding. L.H.L. thanks the financial support from Australian Research Council (ARC) via Discovery Early Career Researcher Award (DE160100796). E.J.G.S. acknowledges the use of computational resources from the UK national high performance computing service (ARCHER) for which access was obtained via the UKCP consortium (EPSRC grant ref EP/K013564/1); the UK Materials and Molecular Modelling Hub for access to THOMAS supercluster, which is partially funded by EPSRC (EP/P020194/1). The Queen's Fellow Award through the grant number M8407MPH, the Enabling Fund (A5047TSL), and the Department for the Economy (USI 097) are also acknowledged.

\subsubsection{Author Contributions}
E.J.G.S. designed the research and suggested the 2D-Moss' relation. 
D.H. and E.J.G.S. performed the first-principles simulations 
and data analytics. T.T. and C.J.S. developed the capacitor model. L.H.L. and J.C. 
performed numerical analysis and contributed to the discussions together with M.C.
E.J.G.S. and T.T. co-wrote the manuscript with inputs from all authors. 
All authors contributed to this work, read the manuscript, discussed 
the results, and all agree to the contents of the manuscript.

\bibliography{refv030318}

%\clearpage 
\pagebreak{}

%\section{Figures}

\label{sec:org01da3bf}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.91\linewidth]{fig1_v122017_ink.pdf}
\caption{\label{fig-1} {\bf Schematic of the studied 2D systems 
and their separation in power- and linear-law materials.}
{\bf a}, Schematic of the geometries of the 2D materials included in our database. 
From dichalcogenides at the most common phases, such as  
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group), up to different graphene derivatives, phosphorene, h-BN, CdCl$_2$ and popular organic-inorganic perovskites (CH$_3$NH$_3$PbBr$_3$). 
{\bf b}, Periodic table showing the main elements utilized in our high-throughput screening, and the classification of the groups accordingly to their scaling relationships. 
}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.67\linewidth]{fig1_v121217dielectric_xx_zz_ink.pdf}
\caption{\label{fig-2} {\bf 2D Moss relation between dielectric constants and band gaps.} 
{\bf a-b}, Calculated in-plane $\varepsilon_{\parallel}$ and out-of-plane $\varepsilon_{\perp}$  
dielectric constants for monolayer vdW materials as a function of the electronic band gap, respectively. 
The 2D materials are categorized into the linear group (green circles) and the 
power group (orange squares). Experimental values of dielectric 
constants and band gaps are show by 
blue squares for comparison\cite{BN-epsilon,Mos2-epsilon,Chernikov_2014_EB_MoS2_2D3D,In2Se3-epsilon}. 
Orange and green lines are fits to $\varepsilon_{\parallel}=3.68/E_{g}^{0.50}$ and 
$\varepsilon_{\parallel}=7.50-1.37E_{g}$, respectively, in {\bf a}. The original 3D-Moss relation, $\varepsilon_{\parallel}=9.74/E_{g}^{0.50}$, between the dielectric constant of bulk semiconductors and band gap is shown as faint blue line. The visible range between 1.7-3.3 eV is highlighted in both panels. 
Dataset for $\varepsilon_{\perp}$ in {\bf b} follows both straight lines, 
$\varepsilon_{\perp}=1.34-(0.00068)E_{g}$ (green) and $\varepsilon_{\perp}=1.28-(0.02)E_{g}$ (orange), 
with small dispersion around $\sim$1.30. The inset in {\bf b} shows the spatial definition of both $\varepsilon_{\perp}$ and $\varepsilon_{\parallel}$. All calculations are at hybrid functional HSE06 level. 
}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figure3_v011218ink.pdf}
\caption{\label{fig-3} {\bf Model prediction and a photoconductivity descriptor.}
{\bf a,b}, Comparison of HSE06-calculated \(\varepsilon_{\parallel}\) and \(\varepsilon_{\perp}\) 
and model predictions, respectively. The scaling relationships of in-plane ($\varepsilon_{\parallel}=3.68/E_{g}^{0.50}$ and $\varepsilon_{\parallel}=7.50-1.37E_{g}$) and out of plane ($\varepsilon_{\perp}=1.34-(0.00068)E_{g}$ and $\varepsilon_{\perp}=1.28-(0.02)E_{g}$) were utilized with $E_{g}$ as the only external parameter.  
{\bf c}, Calculated $n_{0}^{4}/\lambda_{c}$ for all materials considered in power- and linear-law (inset). The dashed blue and violet (in the inset) lines shows the average over the entire set of materials at each group. 
The back dashed line corresponds to Eq.\ref{Moss-2D-power-lambda}. 
Materials that have shown photoconductivity experimentally are marked with the red star\cite{Andres15,photo-2Dmaterials}. 
All calculations are using HSE06 hybrid functional. 
}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{fig4_121917_ink.pdf}
\caption{\label{fig-5}
{\bf The relation between \(\varepsilon_{\parallel}\) and \(C_{\mathrm{Q}}\) in the CB.} {\bf a} \(\varepsilon_{\parallel}\) as a function of \(C_{\mathrm{Q}}\), and {\bf b}, \(\varepsilon_{\parallel}\) as a function of \(C_{\mathrm{Q}}\)/$E_{g}^{2}$ for the 2D materials studied. Linear fitting is performed for materials of the metal element group and lattice type. The prediction margin of each group is shown in shader. {\bf c}, Scheme of the DOS obtained for each material groups highlighting the main stater near the Fermi level $E_F$. {\bf d}, Calculated DOS/$E_{g}^{2}$ using HSE06 hybrid functional for sample layers from group 4 (2H-ZrS$_2$, 2H-HfS$_2$) and group 6 (2H-MoS$_2$, 2H-WS$_2$). Valence band states (VB) and conduction band states (CB) are marked in faint red and green.
}
\end{figure}

%%%%%%% Only figures %%%%%%%%%%%

%\label{sec:org01da3bf}

%\setcounter{figure}{0}
%\begin{figure}[htbp]
%\centering
%\includegraphics[width=1.0\linewidth]{fig1_v122017_ink.pdf}
%\caption{\label{fig-1}
%}
%\end{figure}

%%\setcounter{figure}{0}
%\begin{figure}[htbp]
%\centering
%\includegraphics[width=0.850\linewidth]{fig1_v121217dielectric_xx_zz_ink.pdf}
%\caption{\label{fig-2}
% }
%\end{figure}

%\begin{figure}[htbp]
%\centering
%\includegraphics[width=1.1\linewidth]{figure3_v011218ink.pdf}
%\caption{\label{fig-3}
%}
%\end{figure}

%\begin{figure}[htbp]
%\centering
%\includegraphics[width=0.90\linewidth]{fig_biding_energy_v121917.pdf}
%\caption{\label{fig-4}
%}
%\end{figure}

%\begin{figure}[htbp]
%\centering
%\includegraphics[width=0.90\linewidth]{fig6_v122317_vertical.pdf}
%\caption{\label{fig-6}}
%\end{figure}

%\begin{figure}[htbp]
%\centering
%\includegraphics[width=1.1\linewidth]{fig4_121917_ink.pdf}
%\caption{\label{fig-5}
%}
%\end{figure}

\end{document}

### 2018-08-12 convert.py
add first analysis

@@ -1,0 +1,68 @@
+import re
+import os, os.path
+import shutil
+import glob
+import subprocess
+import multiprocessing
+from multiprocessing import Pool
+import warnings
+
+
+
+# color definition
+class TColors:
+    HEADER = '\033[95m'
+    OKBLUE = '\033[94m'
+    OKGREEN = '\033[92m'
+    WARNING = '\033[93m'
+    FAIL = '\033[91m'
+    ENDC = '\033[0m'
+    BOLD = '\033[1m'
+    UNDERLINE = '\033[4m'
+
+def convert_pdf(infile, outdir="./img"):
+    # Convert svg to pdf
+    base_name = os.path.basename(infile)
+    infile = os.path.join(PATH, base_name)
+    outfile = os.path.join(os.path.abspath(outdir), base_name)
+    outfile = outfile.replace(".svg", ".pdf")
+    print(outfile)
+    program = "inkscape"
+    params = ["--without-gui", "--export-area-drawing",
+    ]
+    io = ["--file={}".format(infile),
+          "--export-pdf={}".format(outfile)]
+    
+    success = subprocess.call([program, *params, *io])
+    if success != 0:
+        warnings.warn(TColors.FAIL + "File {} cannot be converted!".format(infile) + TColors.ENDC)
+    else:
+        print(TColors.OKGREEN +
+              "File {} converted successfully on thread {}.".format(infile, multiprocessing.current_process())
+              +TColors.ENDC)
+
+# Convert all the pdf files
+PATH = os.path.abspath("./img")
+
+if __name__ == "__main__":
+    import sys
+    try:
+        img_path = sys.argv[1]
+    except IndexError:
+        img_path = None
+    file_list = []
+    # TeX process
+    # for ifile in glob.glob("*.tex"):
+        # tex_process(ifile)
+        # print(TColors.OKBLUE + "Converted TeX file: {}".format(ifile) + TColors.ENDC)
+
+    # PDF Process 
+    for ifile in glob.glob(os.path.join(PATH, "*.svg")):
+        if img_path is None:
+            file_list.append((ifile))
+        else:
+            file_list.append((ifile, img_path))
+    N_cores = multiprocessing.cpu_count()
+    # multicore
+    with Pool(N_cores) as p:
+        p.map(convert_pdf, file_list)

### 2018-08-12 src/gpaw_analysis/alpha_relation.py

@@ -1,0 +1,95 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+import os, os.path
+
+db_file = "../../data/gpaw_data/c2db.db"
+if not os.path.exists(db_file):
+    warnings.warn(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db")
+    return
+
+db = ase.db.connect(db_file)
+
+materials = []
+alpha_x = []
+alpha_z = []
+Eg_HSE = []
+Eg_GW = []
+Eg_PBE = []
+thick = []
+
+def get_thick(atom_row):
+    pos = atom_row.positions[:, -1]
+    diff = covalent_radii[atom_row.numbers]
+    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
+    return zmax
+
+candidates = db.select(selection="gap_gw>0.5")
+
+
+for mol in candidates:
+    if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
+        continue
+    print("{0}-{1}".format(mol.formula, mol.prototype))
+    togo = True
+    for attrib in ("gap", "gap_hse",
+                   "gap_gw", "alphax", "alphaz"):
+        if not hasattr(mol, attrib):
+            warnings.warn("{0} doesn't have attribute {1}!".format(mol.formula,
+                                                                   attrib))
+            togo = False
+    if togo is not True:
+        warnings.warn("{0} not calculated!".format(mol.formula))
+        continue
+    materials.append("{0}-{1}".format(mol.formula, mol.prototype))
+    alpha_x.append(mol.alphax)
+    alpha_z.append(mol.alphaz)
+    Eg_HSE.append(mol.gap_hse)
+    Eg_GW.append(mol.gap_gw)
+    Eg_PBE.append(mol.gap)
+    thick.append(get_thick(mol))
+
+print(len(alpha_x))
+alpha_x = numpy.array(alpha_x)
[…]

### 2018-08-12 src/gpaw_analysis/alpha_relation_subset.py

@@ -1,0 +1,106 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+import os, os.path
+
+db_file = "../../data/gpaw_data/c2db.db"
+if not os.path.exists(db_file):
+    warnings.warn(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db")
+    return
+
+subset = [l.strip() for l in open("list.txt").readlines() if l != "\n"]
+
+db = ase.db.connect(db_file)
+
+materials = []
+alpha_x = []
+alpha_z = []
+Eg_HSE = []
+Eg_GW = []
+Eg_PBE = []
+thick = []
+
+def get_thick(atom_row):
+    pos = atom_row.positions[:, -1]
+    diff = covalent_radii[atom_row.numbers]
+    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
+    return zmax
+
+candidates = db.select(selection="gap_gw>0.5")
+
+for mol in candidates:
+    if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
+        continue
+    if mol.formula not in subset:
+        continue
+    print("{0}-{1}".format(mol.formula, mol.prototype))
+    togo = True
+    for attrib in ("gap", "gap_hse",
+                   "gap_gw", "alphax", "alphaz"):
+        if not hasattr(mol, attrib):
+            warnings.warn("{0} doesn't have attribute {1}!".format(mol.formula,
+                                                                   attrib))
+            togo = False
+    if togo is not True:
+        warnings.warn("{0} not calculated!".format(mol.formula))
+        continue
+    materials.append("{0}-{1}".format(mol.formula, mol.prototype))
+    alpha_x.append(mol.alphax)
+    alpha_z.append(mol.alphaz)
+    Eg_HSE.append(mol.gap_hse)
[…]

### 2018-08-13 src/gpaw_analysis/alpha_relation.py
Change plot scripts for gpaw`

@@ -5,12 +5,13 @@ import matplotlib.pyplot as plt
 from ase.data import covalent_radii
 from scipy.stats import linregress
 import os, os.path
+from scipy.constants import pi, epsilon_0
 
 db_file = "../../data/gpaw_data/c2db.db"
 if not os.path.exists(db_file):
-    warnings.warn(("Please download the c2db data into ../../data/gpaw_data/ folder,"
-                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db")
-    return
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
 
 db = ase.db.connect(db_file)
 
@@ -66,30 +67,30 @@ plt.style.use("science")
 
 plt.figure(figsize=(7, 3.5))
 plt.subplot(121)
-plt.plot(Eg_HSE, alpha_x, "o", alpha=0.5)
+plt.plot(Eg_HSE, alpha_x * 4 * pi, "o", alpha=0.5)
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{xx}$ ($\\AA$)")
+plt.ylabel("$\\alpha_{xx}/\\varepsilon_0$ ($\\AA$)")
 
 plt.subplot(122)
-plt.plot(Eg_HSE, alpha_z, "o", alpha=0.5)
+plt.plot(Eg_HSE, alpha_z * 4 * pi, "o", alpha=0.5)
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{zz}$ ($\\AA$)")
+plt.ylabel("$\\alpha_{zz} / \\varepsilon_0$ ($\\AA$)")
 
 plt.tight_layout()
 plt.savefig(os.path.join(img_path, "alpha_Eg_original.svg"))
 
 # x-direction
 plt.figure(figsize=(3.5, 3.5))
-plt.plot(1 / Eg_HSE, alpha_x, "o", alpha=0.5)
+plt.plot(1 / Eg_HSE, alpha_x * 4 * pi, "o", alpha=0.5)
 print(linregress(x=1/Eg_HSE, y=alpha_x))
 plt.xlabel("$1/E_{\\rm{g}}$ (1/eV)")
[…]

### 2018-08-13 src/gpaw_analysis/alpha_relation_subset.py

@@ -5,12 +5,13 @@ import matplotlib.pyplot as plt
 from ase.data import covalent_radii
 from scipy.stats import linregress
 import os, os.path
+from scipy.constants import pi, epsilon_0
 
 db_file = "../../data/gpaw_data/c2db.db"
 if not os.path.exists(db_file):
-    warnings.warn(("Please download the c2db data into ../../data/gpaw_data/ folder,"
-                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db")
-    return
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
 
 subset = [l.strip() for l in open("list.txt").readlines() if l != "\n"]
 
@@ -69,38 +70,38 @@ plt.style.use("science")
 
 plt.figure(figsize=(7, 3.5))
 plt.subplot(121)
-plt.plot(Eg_HSE, alpha_x, "o", alpha=0.5)
+plt.plot(Eg_HSE, alpha_x * 4 * pi, "o", alpha=0.5)
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{xx}$ ($\\AA$)")
+plt.ylabel("$\\alpha_{xx} / \\epsilon_0$ ($\\AA$)")
 
 plt.subplot(122)
-plt.plot(Eg_HSE, alpha_z, "o", alpha=0.5)
+plt.plot(Eg_HSE, alpha_z * 4 * pi, "o", alpha=0.5)
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{zz}$ ($\\AA$)")
+plt.ylabel("$\\alpha_{zz} / \\epsilon_0$ ($\\AA$)")
 
 plt.tight_layout()
 plt.savefig(os.path.join(img_path, "alpha_Eg_subset.svg"))
 
 # x-direction
 plt.figure(figsize=(3.5, 3.5))
-plt.plot(1 / Eg_HSE, alpha_x, "o", alpha=0.5)
-res = linregress(x=1/Eg_HSE, y=alpha_x)
+plt.plot(1 / Eg_HSE, alpha_x * 4 * pi, "o", alpha=0.5)
[…]

### 2018-08-13 src/distance/fit_funct.py
Add model description

@@ -1,0 +1,72 @@
+import numpy
+from scipy.optimize import curve_fit
+import os, os.path
+import matplotlib.pyplot as plt
+from scipy.constants import pi
+plt.style.use("science")
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+names = next(g)[1]
+for i, item in enumerate(g):
+    for f in item[2]:
+        f_path = os.path.join(item[0], f)
+        if "agr" not in f_path:
+            continue
+        print(f_path)
+        data = numpy.genfromtxt(f_path,
+                                delimiter=" "
+                                # skip_header=297,
+                                # skip_footer=2
+         )
+        data = data[1: , :]
+        L = data[:, 0]
+        eps_SL = data[:, 1]
+        if "par" in f_path:
+            alpha_SL = L * (data[:, 1] - 1) 
+        elif "perp" in f_path:
+            alpha_SL = L * (data[:, 1] - 1) / (data[:, 1])
+        fig = plt.figure(figsize=(3, 3))
+        ax = fig.add_subplot(111)
+        ax2 = ax.twinx()
+        ax.plot(L, eps_SL, "o-")
+        ax2.plot(L, alpha_SL, "o-")
+
+        ax.set_xlabel("$L$ ($\\AA$)")
+        if "par" in f_path:
+            param, _ = curve_fit(fit_para, L, eps_SL,
+                                 p0=(5, 10),
+                                 bounds=((0.5, 1.0),
+                                         (10, 50))
+            )
+            LL = numpy.linspace(10, 70)
+            # ax.plot(LL, fit_para(LL, *param), "--")
+            # ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{d}}={0:.3f}$".format(*param, names[i]))
+            # ax.set_ylabel("$\\epsilon_{\\parallel}$")
+            ax.set_title("{} parallel".format(names[i]))
+            ax.set_ylabel("$\\epsilon_{\\parallel}$")
+            ax2.set_ylabel("$\\alpha_{\\parallel}/\\epsilon_0 (\\AA)$")
+            # ax.set_ylim(0, 12)
[…]

### 2018-08-13 src/gpaw_analysis/alpha_relation_subset_conflict-20180813-120552.py

@@ -89,7 +89,7 @@ res = linregress(x=1/Eg_HSE, y=alpha_x * 4 * pi)
 xx = numpy.linspace(min(1/Eg_HSE), max(1/Eg_HSE))
 yy = res.slope * xx + res.intercept
 plt.plot(xx, yy, "--")
-plt.text(x=0.8, y=4, s="$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
+plt.text(x=0.6, y=40, s="$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
 plt.xlabel("$1/E_{\\rm{g}}$ (1/eV)")
 plt.ylabel("$\\alpha_{xx} / \\epsilon_0$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "alpha_xx_1_Eg_subset.svg"))
@@ -101,7 +101,7 @@ res = linregress(x=thick, y=alpha_z * 4 * pi)
 xx = numpy.linspace(min(thick), max(thick))
 yy = res.slope * xx + res.intercept
 plt.plot(xx, yy, "--")
-plt.text(x=2.5, y=0.40, s="$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
+plt.text(x=2.5, y=5, s="$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
 plt.xlabel("Thickness ($\\AA$)")
 plt.ylabel("$\\alpha_{zz} / \\epsilon_0$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "alpha_zz_thick_subset.svg"))

### 2018-10-01 src/VASP_HSE/alpha_EG_PBE.py
Change figures for second version

@@ -49,4 +49,23 @@ plt.xlabel("$E_{\\mathrm{g}}$ (eV)")
 plt.ylabel("$(4 \\pi \\varepsilon_0) / \\alpha^{\parallel}$ ($\\AA^{-1}$)")
 plt.legend()
 plt.savefig("../../tmp_img/compare_alpha_Eg.svg")
+
+
+plt.figure(figsize=(3.5, 3))
+plt.style.use("science")
+direct_diff = (data[:, 1] - data[:, 2]) / 1
+l =  plt.scatter(data[:, 0], 1 / data[:, -2], marker="o",
+                     alpha=0.5, c=direct_diff, cmap="rainbow")
+k, b, r, *_ = linregress(data[:, 0], 1/data[:, -2])
+print(k, b, r)
+plt.plot(xx, k * xx + b, "--")
+cb = plt.colorbar(shrink=0.5)
+cb.ax.set_ylabel("$E_{\\mathrm{g}}^{\\mathrm{direct}} - E_{\\mathrm{g}}^{\\mathrm{min}}$ (eV)")
+
+plt.ylim(0, 1.24)
+
+plt.xlabel("$E_{\\mathrm{g}}$ (eV)")
+plt.ylabel("$(4 \\pi \\varepsilon_0) / \\alpha^{\parallel}$ ($\\AA^{-1}$)")
+plt.tight_layout()
+plt.savefig("../../tmp_img/compare_alpha_HSE_direct_sepa.svg")
     

### 2018-10-01 src/VASP_HSE/polarizability_histo.py

@@ -35,13 +35,14 @@ ax = [a[0] for e, a, n in res]
 az = [a[1] for e, a, n in res]
 Eg = [e for e, a, n in res]
 
-xx = numpy.arange(0, len(maters)) - 0.5
+xx = numpy.arange(0, len(maters))
 
 ax2.plot(Eg, "o-", markersize=6)
 ax1.bar(xx, ax, color="#FFCC00", alpha=0.7)
 ax1.bar(xx, az, color="#FF5555", alpha=0.5)
-ax1.set_xticks(range(0, 50))
-ax1.set_xticklabels(maters, rotation="vertical")
+ax1.set_xticks(range(0, len(maters)))
+mnames = [n[0] + n[1:].replace("2", "$_{2}$") for n in maters]
+ax1.set_xticklabels(mnames, rotation="vertical")
 plt.tight_layout()
 plt.savefig("../../tmp_img/all_data.svg")
 

### 2018-10-01 src/VASP_HSE/relation_2D3D.py

@@ -67,7 +67,7 @@ for row in reader:
     if row[4] != "":
         name, proto = row[: 2]
         print(name, proto)
-        L, E, ex, ey, ez = map(float, row[2:])
+        L, E, ex, ey, ez, *_ = map(float, row[2:])
         if ez < ex:
             e_xy = numpy.sqrt(ex * ey)
             ax = (e_xy - 1) / (4 * pi) * L
@@ -110,6 +110,8 @@ def fit_func(x, a,b):
 
 
 # x-direction
+MAE=numpy.mean(numpy.abs(eps_x_3D[:, 1][eps_x_3D[:, 0] < 30] - eps_x_3D[:, 0][eps_x_3D[:, 0]<30]))
+print(MAE)
 plt.figure(figsize=(3, 2.8))
 plt.scatter(eps_x_3D[:, 1], eps_x_3D[:, 0],
             c=Eg_HSE,

### 2018-10-01 src/VASP_HSE/relation_alpha.py

@@ -42,7 +42,7 @@ for row in reader:
     if row[4] != "":
         name, proto = row[: 2]
         print(name, proto)
-        L, E, ex, ey, ez = map(float, row[2:])
+        L, E, ex, ey, ez, *_ = map(float, row[2:])
         if ez < ex:
             eps_z.append(ez)
             materials.append("-".join((name, proto)))
@@ -69,7 +69,7 @@ thick = thick[cond]
 
 colors = {"MoS2": "#AA0000", "CdI2": "#2C5AA0",
           "GaS": "#FFCC00", "BN": "#A05A2C",
-          "P": "#447821"}
+          "P": "#447821", "CH": "#FF6600"}
 
 cs = [colors[mat.split("-")[-1]] for mat in materials]
 
@@ -78,21 +78,31 @@ plt.style.use("science")
 
 plt.figure(figsize=(7, 3.5))
 plt.subplot(121)
-plt.scatter(Eg_HSE, alpha_x * 4 * pi, marker="o", alpha=0.5, c=cs)
+plt.scatter(Eg_HSE, alpha_x, marker="o", alpha=0.5, c=cs)
+def fit_func(x, a,b):
+    return b / x
+
+fit_param, cov = curve_fit(fit_func,
+                      xdata=Eg_HSE, ydata=alpha_x,
+                      p0=(0, 10))
+print(fit_param)
+xx = numpy.linspace(0.5, 8)
+yy = fit_func(xx, *fit_param)
+plt.plot(xx, yy, "--")
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{xx}/\\varepsilon_0$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 
 plt.subplot(122)
-plt.scatter(Eg_HSE, alpha_z * 4 * pi, marker="o", alpha=0.5, c=cs)
+plt.scatter(Eg_HSE, alpha_z, marker="o", alpha=0.5, c=cs)
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$\\alpha_{zz} / \\varepsilon_0$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\perp} / (4 \pi \\varepsilon_0)$ ($\\AA$)")
 
 plt.tight_layout()
[…]

### 2018-10-01 src/distance/fit_funct.py

@@ -1,74 +1,0 @@
-import numpy
-from scipy.optimize import curve_fit
-import os, os.path
-import matplotlib.pyplot as plt
-from scipy.constants import pi
-plt.style.use("science")
-
-def fit_para(L, d, eps_2D):
-    return (eps_2D - 1) * d / L  + 1
-
-def fit_vert(L, d, eps_2D):
-    return 1 / (d / L * (1 / eps_2D - 1) + 1)
-
-root = "../../data/distance/"
-g = os.walk(root)
-names = next(g)[1]
-for i, item in enumerate(g):
-    if "old" in item:
-        continue
-    for f in item[2]:
-        f_path = os.path.join(item[0], f)
-        if "agr" not in f_path:
-            continue
-        print(f_path)
-        data = numpy.genfromtxt(f_path,
-                                delimiter=" "
-                                # skip_header=297,
-                                # skip_footer=2
-         )
-        # data = data[1: , :]
-        L = data[:, 0]
-        eps_SL = data[:, 1]
-        if "parallel.agr" in f_path:
-            alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
-        elif "perpendicular.agr" in f_path:
-            alpha_SL = L * (data[:, 1] - 1) / (data[:, 1]) / (4 * pi)
-        fig = plt.figure(figsize=(2.5, 2.5))
-        ax = fig.add_subplot(111)
-        ax2 = ax.twinx()
-        ax.plot(L, eps_SL, "o-", color="#00AAD4")
-        ax2.plot(L, alpha_SL, "o-", color="#FF6600")
-
-        ax.set_xlabel("$L$ ($\\AA$)")
-        if "par" in f_path:
-            param, _ = curve_fit(fit_para, L, eps_SL,
-                                 p0=(5, 10),
-                                 bounds=((0.5, 1.0),
-                                         (10, 50))
-            )
-            LL = numpy.linspace(10, 70)
-            # ax.plot(LL, fit_para(LL, *param), "--")
-            # ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{d}}={0:.3f}$".format(*param, names[i]))
-            # ax.set_ylabel("$\\epsilon_{\\parallel}$")
-            ax.set_title("{} parallel".format(names[i]))
[…]

### 2018-10-01 src/gpaw_analysis/alpha_mass.py

@@ -81,28 +81,28 @@ plt.xlim(0.05, 1.5)
 
 l2, *_ = plt.plot(emass, alpha_x, "o", alpha=0.4)
 plt.xlabel("$m_{e}^{*}/m_0$ ")
-plt.ylabel("$\\alpha_{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphaxx_emass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(hmass, alpha_x, "o", alpha=0.4)
 plt.xlabel("$m_{h}^{*}/m_0$ ")
-plt.ylabel("$\\alpha_{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphaxx_hmass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(emass, alpha_z, "o", alpha=0.4)
 plt.xlabel("$m_{e}^{*}/m_0$ ")
-plt.ylabel("$\\alpha_{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphazz_emass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(hmass, alpha_z, "o", alpha=0.4)
 plt.xlabel("$m_{h}^{*}/m_0$ ")
-plt.ylabel("$\\alpha_{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphazz_hmass.svg"))
 
 

### 2018-10-01 SI.tex
Change manuscript

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{float}

\SectionNumbersOn{}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S\arabic{equation}}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

\date{}

\title{Universal Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

\section{Hypothetical 2D dielectric constant rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}

From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric constant
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text and
other studies\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D},
the definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials. Here we show that, in
addition to the ambiguous definition of the 2D dielectric constant,
such approach requires the precise determination of the 2D layer
thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

In brief, the hypothetical 2D dielectric constant
$\varepsilon_{\mathrm{2D}}$ comes from the planar limit of the
Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f (\varepsilon_{\mathrm{2D}}^{\perp})^{-1} + (1-f)
\end{eqnarray}
where $f=\delta_{\mathrm{2D}}/L$ is the volume fraction of the 2D
material in the superlattice. The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$,
which is not well defined for a 2D material. To eliminate the modeling
error caused by the \texttt{a priori} parameter selection of
$\delta_{\mathrm{2D}}$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$, and use
least-square fitting to extract both $\varepsilon_{\mathrm{2D}}$ and
$\delta_{\mathrm{2D}}$, as shown in Figure \ref{fig:rescale-prb}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta_{\mathrm{2D}}$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

As can be seen from the fitted results in Figure
\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}$ extracted
from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
{\AA}. Notably, the $\delta_{\mathrm{2D}}$ values are generally 10\%
smaller than the interlayer distance in corresponding bulk materials
$L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
other hand, the extracted $\delta_{\mathrm{2D}}$ values are closer to
the covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ as
described in the main text, with a difference generally smaller than
5\%. Our results indicate that the conventional estimation of the 2D
layer thickness by its bulk interlayer distance
\cite{Matthes_2016,Laturia_2018}, will always lead to
overestimation. On the contrary, the out-of-plane polarizability
$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness nature
of 2D materials.

\begin{table}[htbp]
  \centering
  \begin{tabular}[htbp]{lccccc}
  \hline{}
  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha^{\perp}/\varepsilon_{0}$ ({\AA})\\
  \hline{}
  2H-MoS$_{2}$ & 5.76 & 5.49 & 6.15 & 5.22 & 4.98\\
  2H-MoSe$_{2}$ & 5.98 & 5.92 & 6.46 &  5.73 & 5.60\\
  2H-MoTe$_{2}$ & 6.43 & 6.85 & 6.98 & 6.37 & 6.12\\
  2H-WS$_{2}$ & 5.63 & 5.49 & 6.15 & 5.20 & 5.00\\
  2H-WSe$_{2}$ & 5.84 & 5.92 & 6.49 & 5.75 & 5.42\\
  2H-WTe$_{2}$ & 6.32 & 6.58 & 7.06 & 6.38 & 6.33\\
  \hline{}
\end{tabular}

\caption{Calculated $\delta_{\mathrm{2D}}$ from
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$, compared with the interlayer
  distance of corresponding bulk material $L_{\mathrm{SL}}$, the
  covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
  $\alpha^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
\label{tab:delta-L-DFt}
\end{table}

Another drawback of the 2D dielectric constant approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\linewidth]{img/SI-eps-alpha-error.pdf}
  \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
    function of the difference between $\delta_{\mathrm{2D}}$ and
    $\alpha^{\perp}/\varepsilon_{0}$. A small change of
    $\alpha^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
    the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
    which is apparently unphysical}
  \label{fig:eps-alpha-error}
\end{figure}

which indicate that the characteristic length
$\alpha^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
$\alpha^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
\item $\alpha$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
\item $\alpha$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.

\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha$.
\end{enumerate}

\section{Further analysis of the 2D polarizability}
\label{sec:pol-2D}

In this section we will provide more analysis on the 2D polarizability
in addition to the main text.

\subsection{Dependence of superlattice size}
\label{sec:pol-2D-1}

We study the polarizabilties of group 6 TMDCs to demonstrate the
dependency between the 2D polarizability $\alpha$ and the superlattice
length $L$, which is shown in Figure \ref{fig:eps-L-all} \todo{Which
  method?}.  In all cases, we observe that the calculated
polarizability converges when $L>$15 \AA{}, in good agreement with our
conclusion in main text. The lower bound of $L_{\mathrm{min}}$ for the
convergence of $\alpha$ can be viewed as the minimal distance that
overlap of induced charge density from image layers is negligible. In
practice, any superlattice size larger than $L_{\mathrm{min}}$ can be
used for calculating the intrinsic 2D dielectric nature through the
polarizability, however to reduce the computational cost, especially
at the HSE level, we typically choose a superlattice size no larger
than 35 \AA{}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-eps-L-all.pdf} 
  \caption{Calculated value of $\varepsilon_{\mathrm{SL}}^{\parallel}$
    (top left axis), $\varepsilon_{\mathrm{SL}}^{\perp}$ (bottom left
    axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
    (bottom right axis) of various group 6 TMDCs. In all cases, the
    polarizability  converges when $L>$15 \AA{}}
  \label{fig:eps-L-all}
\end{figure}

\subsection{Depdence of bandgap}
\label{sec:pol-2D-2}

In this section we further look into the bandgap dependency of the 2D
polarizability. Figure \ref{fig:SI-raw-HSE} shows $\alpha^{\parallel}$
and $\alpha^{\perp}$ as functions of $E_{\mathrm{g}}$ of the 2D
materials studied here. We observe that $\alpha^{\parallel}$ can be
approximated by a reciprocal function of $E_{\mathrm{g}}$, that
$\alpha^{\parallel}\sim{} 7.295(E_{\mathrm{g}})^{-1}$. On the other
hand, the plot of $\alpha^{\perp}$ against $E_{\mathrm{g}}$ shows no
apparent correlation.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
  \caption{$E_{\mathrm{g}}$-dependence of    \textbf{a} $\alpha^{\parallel}$ and
    \textbf{b} $\alpha^{\perp}$ for the 2D materials investigated here.}
  \label{fig:SI-raw-HSE}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
  \caption{Relation between $1/\alpha^{\parallel}$ and various choices
    of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
    from PBE (orange) and direct gap from PBE (green). The linear
    regression results are shown as broken lines.}
  \label{fig:alpha-Eg-diff}
\end{figure}

We also investigate the relation of 2D polarizabilities with
difference choices of \textit{ab initio} bandgaps. It is widely
accepted that the PBE method, while gives quantitative predictions of
the dielectric response of 2D and layered materials, tends to
underestimate the bangap
\cite{Kumar_2016_PRB,Kumar_2016_jpcc}. \todo{complete the discussion
  for HSE?}  Indeed, changing the choice of $E_{\mathrm{g}}$ yields
different regression relation with $1/\alpha^{\parallel}$, as shown in
Figure \ref{fig:alpha-Eg-diff}. We see that due to the underestimation
of PBE bandgap, the slope of linear regression is larger than that
from HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
relation is better presented by using the minimal HSE bandga than the
minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
the former. We note that the higher $R^{2}$ coefficient observed using
the direct PBE bandgap than the minimal PBE bandgap may be solely
caused by the fact that the direct bandgap of 2D materials on the PBE
level is closer to the HSE bandgap. From the random phase
approximation theory of dielectric response, the polarizability is
contributed by all possible transition between valence and conduction
bands, with the minimal bandgap as the least possible transition. In
this sense, $\alpha^{\parallel}$ is mostly like to be associated with
the minimal, not direct bandgap, as also observed in the original Moss
relation. We also examine the validity of such statement based on the
analysis of the Computational 2D Materials Database (C2DB)
\cite{Haastrup_2018}, as will be discussed in the following sections.

\section{Validation on the C2DB 2D materials database}
\label{sec:gpaw}
\subsection{Validation of the universal description of 2D polarizabilities}
\label{sec:gpaw-1}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ on the C2DB
    2D material database. }
  \label{fig:gpaw-alpha-relation}
\end{figure}

Due to the high computation complexity of dielectric response
calculations on the HSE level, our 2D material database is limited to
about 50 types of materials. It is desirable to validate our proposed
relations on a even larger scale database. \todo{Add comments for the
  C2DB database}. We select 210 semiconducting 2D materials from the
C2DB database with a HSE bandgap larger than 0.5 eV and extracted the
2D polarizabilities calculated on the PBE level. The propsed linear
relations between $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
and $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ are also
valid, as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent
linear correlation is observed in both cases, with the $R^{2}$
coefficient larger than 0.9, indicating the existence of the universal
description of 2D dielectric nature through the proposed relations
with the 2D polarizabilities. We note that the slope of linear
regression is slightly different from the our proposed relation from
the dielectric response on HSE level, due to the fact that the
macroscopic dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated
on the PBE level is about 5\% lower. Despite the minor deviation of
the slope of linear regression, the analysis on the C2DB database
supports our understanding of the universal dielectric nature of 2D
materials.

\subsection{Choice of bandgap}
\label{sec:gpaw-2}

Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
regression of $\alpha^{\parallel}-E_{\mathrm{g}}$ relation. Figure
\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha^{\parallel}$ from the
C2DB database as a function of minimal and direct bandgap calculated
on PBE, HSE and GW levels.\todo{to be more specific?} We observe,
although the regression $R^{2}$ coefficient in all cases are around
0.9, the $\alpha^{\parallel}-E_{\mathrm{g}}$ is better described using
the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
using indirect or minimal bandgaps on the same level gives almost
identical regression slope. The observations are in good agreement
with our calculations on the HSE level discussed in Section
\ref{sec:pol-2D-2}. In combination with the physical contribution of
$E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
minimal bandgap should be used for quantitative prediction of the
in-plane 2D polarizability. The prediction is greatly improved when
more accurate theory level for bandgap is used (for instance, HSE and GW).

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
  \caption{$\alpha^{\parallel}$ as funtion of minimal and direct
    $E_{\mathrm{g}}$ calculated on different theoretical levels:
    \textbf{a} PBE, \textbf{b} HSE and \textbf{c} GW of the C2DB
    database.}
  \label{fig:SI-gpaw-alpha-Eg-all}
\end{figure}

\subsection{Relation between 2D polarizabilities and other physical quantities}
\label{sec:gpaw-3}

The relatively large size of the C2DB 2D materials database allows us
to examine the relation between 2D polarizabilities and other physical
quantities. We choose the following quantities for comparison,
corresponding to Figures \ref{fig:gpaw-2D-quantities-1} to
\ref{fig:gpaw-2D-quantities-3}:
\begin{enumerate}
\item The effective carrier mass for electron $m_{e}^{*}$ and hole $m_{h}^{*}$

\item The quantum capacitance at the conduction band edge
  $C_{\mathrm{Q}}^{\mathrm{C}}$ and valence band edge
  ($C_{\mathrm{Q}}^{\mathrm{V}}$).

\item The total atomic polarizabilities per area $\alpha^{\mathrm{sum}}$.
\end{enumerate}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\linewidth]{img/SI-gpaw-alpha-emass.pdf}
  \caption{Relation between 2D polarizabilities and the effective
    carrier mass from the C2DB 2D material
    database. \textbf{a}. $\alpha^{\parallel}$ as a function of the
    electron mass $m_{e}^{*}$.  \textbf{b}. $\alpha^{\parallel}$ as a
    function of the hole mass
    $m_{h}^{*}$. \textbf{c}. $\alpha^{\perp}$ as a function of the
    electron mass $m_{e}^{*}$.  \textbf{d}. $\alpha^{\perp}$ as a
    function of the hole mass $m_{h}^{*}$. No apparent correlation
    between the 2D polarizabilities and the effective carrier masses
    is observed.}
  \label{fig:gpaw-2D-quantities-1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\linewidth]{img/SI-quantum-capacitance.pdf}
  \caption{Relation between the 2D polarizabilities with the quantum
    capacitance. \textbf{a} $\alpha^{\parallel}$ (top) and
    $\alpha^{\perp}$ (bottom) as functions of the quantum capacitance
    of the conduction band edge,
    $C_{\mathrm{Q}}^{\mathrm{C}}$. \textbf{b} $\alpha^{\parallel}$
    (top) and $\alpha^{\perp}$ (bottom) as functions of the quantum
    capacitance of the valence band edge,
    $C_{\mathrm{Q}}^{\mathrm{V}}$. Similar to the case of effective
    carrier mass, no apparent correlation between 2D polarizabilities
    and the quantum capacitance can be found.}
  \label{fig:gpaw-2D-quantities-2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\linewidth]{img/SI-gpaw-alpha-atomic-polarizability.pdf}
  \caption{Relation between the 2D polarizabilities
    (\textbf{a}. $\alpha^{\parallel}$ and
    \textbf{b}. $\alpha^{\perp}$) with the total atomic polarizability per area.}
  \label{fig:gpaw-2D-quantities-3}
\end{figure}

The quantum capacitance
$C_{\mathrm{Q}}(E)$ at certain energy level $E$ is calculated using
the relation $C_{\mathrm{Q}}(E)=\mathrm{DOS}(E)e^{2}$, where
$\mathrm{DOS}(E)$ is the density of states at the conduction or valence band edge (averaged by cell
area). The DOS value is calculated at the energy level with a charge
cutoff such that
$|n_{\mathrm{2D}}(E)| = 5 \times 10^{13}\ \mathrm{cm}^{-2}$, calculated by
the relation of accumulated charge $n_{\mathrm{2D}}(E)$ at CB or VB:
\begin{equation}
  \label{eq:CQ-method}
  |n_{\mathrm{2D}}(E)| = \left|\int_{E_{\mathrm{BE}}}^{E} \mathrm{DOS}(E') dE' \right|
\end{equation}
where $E_{\mathrm{BE}}$ is the energy of the CB or VB band edge.

The total polarizability $\alpha^{\mathrm{sum}}$ is calculated by the
summation of the atomic polarizabilities $\alpha^{\mathrm{atom}}$
\cite{Gould_2016_jctc} of individual atoms per area $A$, such that:
\begin{equation}
  \label{eq:atom-polar}
  \alpha^{\mathrm{sum}} = \frac{\sum_{i} \alpha^{\mathrm{atom}}_{i}}{A}
\end{equation}

From Figures \ref{fig:gpaw-2D-quantities-1} to
\ref{fig:gpaw-2D-quantities-3} we can see that none of the above
quantities have apparent relation with the 2D polarizabilities, as
compared with the bandgap and covalent thickness proposed in the main
text. \todo{add some more explanation}

\section{More theoretical analysis}
\label{eq:MG-effect-1}

\subsection{Detailed derivations from Eq. 10}
\label{sec:theory-1}

Here we will first show how Eq. 10 in the main text is
derived. Treating the in-plane wavefunctions as plane wave with form
$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
element of
$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
  &= \frac{1}{A} \int dx \int dy
  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
  \end{aligned}
\end{equation}
Note that the states perpendicular are bound, the integral is
meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
performing the Taylor expansion of
$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
   \end{aligned}
\end{equation}
plug this into Eq. 7 in main text and express the summation over
$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
arrive at Eq. 10 in main text.

Although the exact form for $\psi^{\perp}$ depends on the exact
distribution of $V(z)$, without loss of generality we can assume the
electrons are confined in a potential well of width $\delta$, which is
the typical treatment for semiconductor QWs
\cite{ihn_semiconductor_2009}. The allowed bound states inside the
confined region generally has wave vector
$k_{z} \propto n \pi / \delta$. With the total energy
$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
the effective masses parallel and perpendicular to the 2D
plane. Therefore the denominator of Eq. 10 becomes independent of
$\mathbf{k}$, that
$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
hand, the numerator
$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
is proportional to the confinement length $\delta$ (can be seen using
particle-in-box solution\cite{davies_physics_1997}). In combination,
the individual terms of the summation in the right hand of Eq. 10 is
independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
$\alpha^{\perp}$ is independent of the band gap.

Finally we will show the $\alpha^{\perp}$ is related to the
confinement length $\delta$, or equivalent the thickness of the 2D
material. For simplicity we assume $\psi^{\parallel}$ is the solution
of a particle confined inside an infinite potential well of width
$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
K, the only non-zero contribution for the transition between band
$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
\begin{equation}
  \begin{aligned}
    \alpha^{\perp} &\propto \delta^{4} m^{\perp} \int
    d^{2}\mathbf{k}_{\rho}
    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
      n_{\mathrm{v}}^{2}}\\
    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
        n_{\mathrm{v}}^{2}}
  \end{aligned}
\end{equation}
Since the Fermi wave vector for band \textit{i} follows
${\displaystyle
  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
    \delta^{2}}} = E_{\mathrm{F}}$, we have
$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
model, the energy levels for a sub-nm QW will be at the order of 10
eV, which allows only few states inside the QW. Combine with the fact
that the strongest transition comes from the lowest bands
\cite{davies_physics_1997}, we can finally show:
\begin{equation}
  \label{eq:alpha-perp-L}
  \alpha^{\perp} \propto m^{\parallel} \delta^{2}
\end{equation}
Apart from the power of $\delta$, this explains our observation
$\alpha^{\perp}$ is related with the thickness of a 2D material. We
note the power law of $\delta^{2}$ instead of $\delta$ is
inevitable. The atomic polarizabilities of free particles inside a 1D
infinite QW, finite QW or harmonic QW all show dependency with
$\delta^{4}$, where $\delta$ is the length of confinement or effective
harmonic length of the QW \cite{Fowler_1984,Maize_2011}. Since the 2D
polarizability is the molecular polarizability divided by the area,
such approach will always yield $\alpha^{\perp} \propto \delta^{2}$
regardless of the Hamiltonian used. To accurately model the
$\alpha^{\perp}$ we need a better model for the confinement in
z-direction than simple square potential well, which may be
tedious. Nevertheless the simple model presented here still captures
the bandgap-indepent and thickness-related feature of
$\alpha^{\perp}$, supporting our findings in the main text.

\subsection{Detailed discussion for main text Eq. 14 }
\label{sec:theory-2}

Eq. 14 is the detailed form of Eq. 6 considering wavefunctions in all
directions are periodic which can be written in the form of Block
waves. The solution for Eq. 14 in main text is derived as follows. For
simplicity we consider that the effective mass $m^{*}$ is uniform,
which is generally a good assumption for bulk materials. Considering
only one pair of valence-conduction transition, and take the result
from \cite{Jiang_2017_Eg_Eb}, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:eps-bulk}
    \varepsilon_{\mathrm{bulk}} - 1 &\propto \int d^{3}\mathbf{k}
    {\displaystyle \frac{1}{(E_{\mathrm{g}} + {\displaystyle
          \frac{\hbar^{2} k^{2}}{m^{*}}})^{2}}}\\
    &= \int_{0}^{k_{\mathrm{BZ}}} {\displaystyle
      \frac{4 \pi k^{2}}{(E_{\mathrm{g}} + {\displaystyle \frac{\hbar^{2}
            k^{2}}{m^{*}}})^{2}}} dk
  \end{aligned}
\end{equation}
where $k_{\mathrm{BZ}}$ is the boundary for the Brillouin Zone. The
last step in Eq. \ref{eq:eps-bulk} assumes the integral within the
Brillouin Zone is equivalent to integral inside a sphere of
k-space. Let $\hbar^{2}/(2 m^{*})=A$, the integral becomes:
\begin{equation}
  \begin{aligned}
    \label{eq:integral-BZ-bulk}
    \alpha^{\perp} &\propto {\displaystyle \frac{2 \pi
        \mathrm{arctan}(\sqrt{Ak^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}}A^{3}}}
        - \frac{2\pi k}{A(A+E_{\mathrm{g}}k^{2})}
      } \bigg\rvert_{0}^{k_{\mathrm{BZ}}}\\
      &\propto \sqrt{\frac{m^{*}}{E_{\mathrm{g}}}}
  \end{aligned}
\end{equation}
since generally
$\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg E_{\mathrm{g}}$. When
$\varepsilon_{\mathrm{bulk}} \gg 1$ and assuming the difference
between $m^{*}$ in different semiconductors is small
\cite{Finkenrath_1988}, it is the Moss relation of bulk semiconductors.

\subsection{Static 2D polarizability and 2D plasma frequency}
\label{sec:omega-p}

A common approach for describing the bulk dielectric function of bulk
semiconductors is via the Lorentz oscillator model, where the
dielectric function is dominated by the plasma frequencies
$\omega_{\mathrm{3D}}^{\mathrm{p}}$ and bandgap $E_{\mathrm{g}}$ of
individual oscillators \cite{ketterson_physics_2016}. At zero optical
frequency and the static limit, the dielectric constant for single
oscillator is:
\begin{equation}
  \label{eq:eps-plas-3D}
  \varepsilon_{\mathrm{3D}} = 1 +
  \frac{\hbar^{2} (\omega_{\mathrm{3D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{equation}
where
$\omega_{\mathrm{3D}}^{\mathrm{p}} = {\displaystyle \sqrt{\frac{e^{2}
      n_{\mathrm{3D}}}{\varepsilon_{0} m_{e}}}}$, where
$n_{\mathrm{3D}}$ is the 3D number density of valence
electrons. Combine Eq. \ref{eq:eps-plas-3D} with Eq. 3 in main text,
we get:
\begin{equation}
  \begin{aligned}
  \label{eq:alpha-plas}
  \alpha^{\parallel} &= \frac{e^{2} n_{\mathrm{3D}} L}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \frac{e^{2} n_{\mathrm{2D}}}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \varepsilon_{0} \frac{\hbar^{2}
    (\omega_{\mathrm{2D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{aligned}
\end{equation}
where $n_{\mathrm{2D}} =n_{\mathrm{3D}} L$ is the 2D number density of
valence electrons and
$\omega_{\mathrm{2D}}^{p}=\omega_{\mathrm{3D}}^{p}\sqrt{L}$ is the 2D
plasma frequency at static limit \cite{Nazarov_2015_2D_3D}, as
discussed in the main text. Apparently $n_{\mathrm{2D}}$ and
$\omega_{\mathrm{2D}}^{p}$ defines the superlattice-independent 2D
quantity $\alpha^{\parallel}$, while its 3D counterpart
$\varepsilon_{\mathrm{3D}}$ is dependent on $L$. By defining the 2D
valence charge density
$\sigma_{\mathrm{2D}}^{\mathrm{v}}=n_{\mathrm{2D}}e$, we have also
calculated $\alpha^{\parallel}$ as a function of
$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the C2DB database, as shown in Figure \ref{fig:plasma}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.65\linewidth]{img/SI-lorentz-model.pdf}
  \caption{Calculated$\alpha^{\parallel}$ as a function of
    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the
    C2DB database. The broken line shows the theoretical prediction
    from single-oscillator model.}
  \label{fig:plasma}
\end{figure}
It can be seen that, a large number of materials are close to the
theoretical value of
$\alpha^{\parallel} = \frac{e^{2} n_{\mathrm{3D}} L}{m_{e}
  E_{\mathrm{g}}^{2}}$ (broken line). However there are also many
violations to this simple relation, making such model not suitable for
quantitative prediction of the 2D dielectric nature, due to the
oversimplification of single Lorentz oscillator. Nevertheless, this
example shows excellently how the quantities in both dimensions are
related to each other.

\section{Raw data from first principles calculations}
\label{sec:raw}

TBD.

\section*{}
\label{sec:ref}
\bibliography{ref}

\end{document}

### 2018-10-01 paper.tex
Change manuscript

% Created 2018-09-26 Wed 21:07
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage{times}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

\newpage{}

\section{Introduction}
\label{sec:org2ea169d}

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relationships between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relationship, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relationship between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that the
there exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on dependent on several critical details on the sample measurements,
such as contamination, disorder, and model interpretation. With the
Moss relationship or other similar models, it is feasible to predict
the dielectric constant of a bulk semiconductor with a reasonable
degree of certainty.

While the relation between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
relation still exists in low-dimensional materials. For instance,
two-dimensional (2D) materials, the atomically-thin crystalline layers
\cite{Novoselov_2016}, are known to have distinct electronic
\cite{Mak_2010,Tran_2014} and dielectric properties
\cite{Keldysh_1979_eps_multi,Sharma_1985} compared with their bulk
counterparts, making the empirical relations of dielectric constant in
bulk materials, like the Moss relation invalid within the context of
2D materials. More critically, the static dielectric constant, a
quantity associated with the macroscopic dielectric property and
commonly obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe the microscopic and anisotropic dielectric nature of 2D
materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for the 2D Moss-like relations. Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation of over 50 kinds of monolayer 2D materials, we reveal the
long-sought universal dielectric scale relation in the 2D world: the
in-plane polarizability $\alpha^{\parallel}$ is inversely proportional
to the minimal bandgap $E_{\mathrm{g}}$, while the out-of-plane
polarizability $\alpha^{\perp}$ is closely related with the intrinsic
thickness of 2D materials. The anisotropy of the 2D polarizability is
further explained by a confined quantum model. The universal relations
provide quantitative prediction of the dielectric properties of 2D
materials, which leads to better design and understanding of
electronic devices based on 2D materials and their heterostructures
. Furthermore, such relations bridge the gap between the 2D and 3D
properties, and ultimately pushes the boundary of the understanding of
electronic screening in both dimensions.

\section{Results}
\label{sec:org752ca78}

\subsection{Dielectric Nature of 2D Materials}
\label{sec:2d}

To get the correct description between the dielectric properties of a
2D material with other physical quantities, an accurate description of
the dielectric nature must first be established. As shown in Figure
\ref{fig-1}a, in first principles calculations, an isolated 2D
material needs to be placed in a periodically repeating superlattice
(SL) with a certain length $L$ in the out-of-plane direction to
prevent the interaction from periodic images. The macroscopic
dielectric constant from the superlattice, is the combined effect of
the intrinsic 2D dielectric properties and the vacuum spacing inside
the superlattice. From the classical electrostatics, we know that the
dielectric tensor $\varepsilon_{\alpha \beta}$, is determined by the
response of dipole density $\mathbf{P}_{\alpha}$ under small
perturbative external field $\mathbf{E}_{\beta}$, such that:
\begin{equation}
  \label{eq:def-eps}
  \begin{aligned}
    \varepsilon_{\alpha \beta} &= \kappa_{\alpha \beta} +
    \frac{\partial \mathbf{P}_{\alpha}}{\varepsilon_{0} \partial \mathbf{E}_{\beta}} \\
    &= \kappa_{\alpha \beta} + {\displaystyle \frac{\partial {\displaystyle
          \int_{\mathrm{SL}} \rho(\mathbf{r})\mathbf{r}_{\alpha} d^{3}\mathbf{r}}}{\Omega \varepsilon_{0} \partial \mathbf{E}_{\beta}}}
  \end{aligned}
\end{equation}
where $\alpha$, $\beta$ are the directions in $(x, y, z)$,
$\kappa_{\alpha\beta}$ is the dielectric tensor of the environment
(equals 1 if the environment is vacuum), $\rho$ is the spatial charge
density, $\Omega$ is the volume of the superlattice and
$\varepsilon_{0}$ is vacuum permittivity. For 2D semiconductors, the
off-diagonal elements of the dielectric tensor ($\alpha \neq \beta$)
is always 0. Therefore we can distinguish two components of the
SL dielectric constant, namely the in-plane
($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constant, where
$\varepsilon_{\mathrm{SL}}^{\parallel} =
(\varepsilon_{\mathrm{SL}}^{xx} + \varepsilon_{\mathrm{SL}}^{yy})/2$
and
$\varepsilon_{\mathrm{SL}}^{\perp} =
\varepsilon_{\mathrm{SL}}^{zz}$. Consider the volume $\Omega=AL$,
where $A$ is the area of SL in the xy-plane, and $\kappa \equiv 1$, we
see that both $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ depends on the superlattice length
$L$. On the other hand, the induced dipole of the 2D to an external
field is localized within a confined region near the 2D plane. We show
this by plot the charge density change
$\Delta \rho=\rho(\mathbf{E}) - \rho(\mathbf{E}=0)$ along the z-axis
for an isolated 2H-MoS$_{2}$ layer under
$|\mathbf{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$, as illustrated in Figure
\ref{fig-1}b. The induced dipole only extends to ~12 \AA{} in the
z-direction. Combining the two effects discussed above, it is
erroneous to use directly use the value $\varepsilon_{\mathrm{SL}}$
to present the dielectric nature of a 2D material. We need to find the
$L$-independent quantity to present the intrinsic dielectric
properties of the 2D material. By multiplying $\mathbf{P}$ with $L$,
we get the sheet polarization density $\mathbf{\mu}$, such that
$\mathbf{\mu}=\int_{\mathrm{SL}} \rho(\mathbf{r})rd^{3} \mathbf{r}/A$,
independent of the superlattice size. Similar to the definition of
molecular polarizability, the sheet polarization density
$\mathbf{\mu}$ is associated with the 2D polarizability $\alpha$ by:
$\mathbf{\mu} = \alpha \mathbf{E}_{\mathrm{loc}}$, where
$E_{\mathrm{loc}}$ is the local electric field. In the in-plane
direction, the continuity of electric field gives
$\mathbf{E}^{\parallel}_{\mathrm{loc}}=\mathbf{E}^{\parallel}$
\cite{Markel_2016}. Perpendicular to the 2D plane, the dipole
screening yields $\mathbf{E}_{\mathrm{loc}}=\mathbf{E}+\mathbf{\mu}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eq. \ref{eq:def-eps}, we get the expressions for the in-plane and
out-of-plane 2D polarizabilities, $\alpha^{\parallel}$ and
$\alpha^{\perp}$, respectively:
\begin{eqnarray}
  \label{eq:alpha-para-def}
  \alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
  \label{eq:alpha-perp-def}
    \alpha^{\perp} &= \varepsilon_{0}\left(1 - \frac{1}{\varepsilon_{\mathrm{SL}}^{\parallel}}\right)L
\end{eqnarray}
The $L$-dependence presented in $\varepsilon$ is then removed in the
2D polarizabilities.  We note that although both scaling relations
have been proposed in individual studies
\cite{Cudazzo_2011_screening_2D,Kumar_2016_jpcc,Kumar_2016_PRB}, the
work presented here is the first attempt of unifying the dielectric
properties of 2D materials by both the in- and out-of-plane
polarizabilities, which provides a universal description of dielectric
nature from strict 2D system to the  3D world. Next we examine
how good the 2D polarizability can present its dielectric
nature. Figure \ref{fig-1}c and \ref{fig-1}d show the
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$ of a
2H-MoS$_{2}$ monolayer. As expected the $\varepsilon_{\mathrm{SL}}$
decreases with $L$ in both cases and does not converge even when the
SL size is as large as 60 \AA{}. On the contrary, the
$\alpha^{\parallel}$ and $\alpha^{\perp}$ calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, remain
almost constant when $L>$15 \AA{}. We have further examined the
$\alpha-L$ relation for other group 6 transitional metal
dichalcogenides (TMDCs), including 2H-MoSe$_{2}$, 2H-MoTe$_{2}$,
2H-WS$_{2}$, 2H-WSe$_{2}$, 2H-WTe$_{2}$ (details see Supplementary
Section XX \todo{TBD}). All materials exhibit constant $\alpha$ for
$L>$15 \AA{}, confirming that $\alpha$ is the true descriptor for the
dielectric nature of 2D materials. The calculation of $\alpha$ from
first principles dielectric response does not require the \textit{a
  priori} determination of the thickness of the 2D material, a
quantity which is not well defined. On the other hand, the widely-used
method of treating the 2D material as a dielectric slab with thickness
$\delta$ and uniform dielectric constant $\varepsilon_{\mathrm{2D}}$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Trolle_2017_eps_subst},
tends to give nonphysical pictures of the 2D dielectric properties due
to the ambiguity of $\delta$ (details see Supplementary Section XX
\todo{TBD}). In the following sections, we will pursue the universal
description for the dielectric nature of 2D materials starting from
the 2D polarizability.

\subsection{Universal Relations for 2D Polarizabilities}
\label{sec:first-principles}

In this letter, We study several types of 2D materials of different
electronic and optical properties, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)) and phosphorene (P$4$).
For the TMDCs, we consider 2 lattice phases, namely the 2H
(P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The elements
involved in this study and the structures of the 2D materials are
shown in Figure \ref{fig-2}a and \ref{fig-2}b, respectively. The
static 2D polarizabilities are calculated from the static dielectric
response of the selected 2D materials using density functional theory
(DFT) with Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) in the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions. Further details for the first principle
calculations please refer to \textit{Methods}.

Figure \ref{fig-3}a shows the calculated $E_{\mathrm{g}}$ (blue dots)
and polarizabilities (bar plots) of all the 2D materials investigated,
covering a wide bandgap range of over 6 eV. The 2D polarizability
$\alpha $has the unit of Farad, and is more intuitive to be expressed
in the form $\alpha/(4 \pi \varepsilon_{0})$, which has the unit of
[Length] (similar to the molecular polarizability, which has the unit
of $4\pi \varepsilon_{0}\times$[Volume] \cite{Israelachvili_2011}). We
find that $\alpha^{\parallel}$ has a general descending trend when
$E_{\mathrm{g}}$ increases. On the other hand, no apparent trend
between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
details see Supplementary Figure SXX \todo{TBD}). Recently, it is
found that the exciton binding energy $E_{\mathrm{b}}$ of 2D materials
exhibits universal linear relation with $E_{\mathrm{g}}$
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. Combine
with the fact that the $E_{\mathrm{b}}$ is roughly inversely
proportional to $\alpha^{\parallel}$ \cite{Pulci_2014}, it is
reasonable to guess that a general linear correlation between
$E_{\mathrm{g}}$ and $1/\alpha^{\parallel}$ may exist for 2D
materials. Figure \ref{fig-3}c shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investigated, with a
linear regression slope of ~0.166 and $R^{2}$ of 0.84. We observe that
materials with lower $E_{\mathrm{g}}$ (<4 eV) generally lie close to
the regression line, while the deviation becomes greater for materials
with $E_{\mathrm{g}}>$4 eV, which has also been observed in the
$E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of 2D materials
\cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also observe that
$E_{\mathrm{g}}$ calculated on the HSE06 level shows better linear
correlation with $1/\alpha^{\parallel}$ compared with the bandgap
calculated using the Perdew–Burke–Ernzerhof (PBE) method (details see
Supplementary Information SXX \todo{TBD}). This can be explained by
the fact that the HSE06 hybrid functionals generally have a better
prediction for the bandgap of a material than the PBE method
\todo{some reference?}. It should be noted that although even more
accurate estimation of both $\varepsilon$ and $E_{\mathrm{g}}$ can be
achieved via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D} (see Supplementary Section SXX
\todo{}). Combining the accuracy, computational effort and
convergence, the choice of the HSE06 hybrid functional may be most
suitable to present the true relationship between $\alpha^{\parallel}$
and $E_{\mathrm{g}}$.

On the other hand, $\alpha^{\perp}$ is observed to be almost
independent of $E_{\mathrm{g}}$. Similar behavior is also observed for
molecular \cite{T_bik_2004} and carbon nanotube \cite{Benedict_1995}
systems when the polarizability is in the direct perpendicular to the
$\pi$ electron cloud. Meanwhile, while $\alpha^{\perp}$ is much
smaller than $\alpha^{\parallel}$, its magnitude can still span over 5
times among different materials, and generally larger for materials
with more atoms in the z-direction (such as Ga$_{2}$S$_{2}$) than
single-atom materials (such as BN). Starting from this observation and
the fact that 2D polarizability has unit of
$4\pi\epsilon\times$[Length], $\alpha^{\perp}$ may actually be related
to a characteristic length in the z-direction of a 2D material. Figure
\ref{fig-3}c shows $\alpha^{\perp}$ as a function of the covalent
thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$. The covalent
thickness is defined as the longest distance in the z-direction
between any two atom nuclei plus their covalent radii, such that:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{2D}}^{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i, as illustrated in Figure
\ref{fig-delta}. Surprisingly, $\alpha^{\perp}$ shows excellent linear
correlation with $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$. In other words, the
quantity $\alpha^{\perp}/\varepsilon_{0}$ can be regarded as the
long-sought-for characteristic thickness of 2D materials. In short, we
have revealed the 2D analog of the Moss relation for both polarization
direction: $\alpha^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
characteristic thickness of the 2D material. The existence of such
universal scaling relation is confirmed by examining using the
recently-published C2DB database \cite{Haastrup_2018}, with the
dielectric properties of over 200 2D semiconductors calculated on the
PBE level (details see Supplementary Section SXX \todo{TBD}).  We have
further tested the potential relation between the 2D polarizabilities
with other physical quantities, including the effective carrier mass,
quantum capacitance and total atomic polarizabilities while no
apparent correlations are found (details see Supplementary Section SXX
\todo{note}). In the next section, we will show the theoretical
backgrounds of such universal relations of 2D polarizabilities.

\subsection{Theoretical Explanations}
\label{sec:theory}

Similar to the treatment of quantum wells (QW), the wavefunction of an
isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
and out-of-plane components \cite{davies_physics_1997}
$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
the in-plane coordinate. According to the Bloch theorem, the periodic
in-plane wavefunction can be further expressed as
$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
in-plane wave vector and $u(\rho)$ is periodic function in the
xy-plane. According to the random phase approximation theory
\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ can be calculated by
taking the $\mathbf{q} \to 0$ and $\omega \to 0$ limits of the
non-interacting dielectric function $\varepsilon(\mathbf{q}, \omega)$,
where $\mathbf{q}$ is the momentum transfer and $\omega$ is the
frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \varepsilon_{\mathrm{SL}}(\mathbf{q} \to 0)
  = 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}}))\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $f$ is the Fermi-Dirac distribution, $E$ is the eigenenergy of
individual bands, and $f$ is the Fermi-Dirac distribution. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore $\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. For
$\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent of
$z$. Further combining with the Bloch wave representation and the k-p
theory\cite{Jiang_2017_Eg_Eb}, we have:
\begin{equation}
  \label{eq:alpha_para_RPA}
  \alpha^{\parallel} = \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
the final expression for Eq. \ref{eq:alpha_para_RPA} is shown to be
$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$ by
Ref. \citenum{Jiang_2017_Eg_Eb}, where $N$ is degeneracy of bands
associated with the minimal bandgap. This explains the linear
correlation we observe between $1/\alpha^{\parallel}$ and
$E_{\mathrm{g}}$. When $\alpha^{\parallel}$ is measured in
$(4 \pi \varepsilon_{0})\cdot \mathrm{\AA}$ and $E_{\mathrm{g}}$
measured in eV, the linear regression slope in Figure \ref{fig-3}b is
predicted to be
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$. The
observed value of $\sim$0.166 corresponds to $N$ between 2 and 3,
which is reasonable for the 2D materials studied.

On the other hand, the $E_{\mathrm{g}}$ independence and correlation
with the covalent thickness of $\alpha^{\perp}$, can also be explained
using the same quantum framework. Generally speaking, $\psi^{\perp}$
follows the Hamiltonian in z-direction, such that:
\begin{equation}
  \label{eq:Hamil-z}
  \left[-\frac{\hbar^{2}}{2 m^{\perp}}\nabla^{2} + V(z)\right] \psi^{\perp}(z) = E \psi^{\perp}
\end{equation}
where $\hbar$ is the reduced Planck constant and $m^{\perp}$ is the
effective mass in the perpendicular direction. $V(z)$ is the potential
created by the 2D material, and confined within a region of length
$\delta$. For simplicity we use plane wave to model the in-plane
wavefunction, that
$\psi^{\parallel}(\mathbf{\rho}) \propto
e^{i\mathbf{k\rho}}$. Inserting into Eq. \ref{eq:alpha-RPA} and
perform the Taylor expansion of $e^{-i\mathbf{qr}}$, we can eliminate
the contribution from the in-plane
wavefunctions\cite{davies_physics_1997} and get:
\begin{equation}
  \label{eq:alpha_perp_RPA}
  \alpha^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
  \sum_{\mathrm{c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k}>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the integration over $\mathbf{k}$ is done in the $k_{x}-k_{y}$
part of the Brillouin Zone. In a confined 1D system, the matrix
element
$<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>$ is
usually proportional to the length of confinement $\delta$, while the
eigenenergy difference $E_{\mathrm{c}}-E_{\mathrm{v}}$ is correlated
with $\delta^{-2}$, while independent of
$\mathbf{k}$\cite{Benedict_1995}. Therefore the integrated
$\alpha^{\perp}$ is also independent of the bandgap $E_{\mathrm{g}}$,
which would instead greatly influence $\alpha^{\parallel}$. Using a
simplified particle-in-box model, we evaluated the integration of
Eq. \ref{eq:alpha_perp_RPA} and show that $\alpha^{\parallel}$ is
related with the geometric parameter $\delta$ (details see Supplementary Section SXX \todo{add note}), the confinement of
electrons in the z-direction, which nicely explains our finding of
correlation between $\alpha^{\perp}$ and
$\delta^{\mathrm{cov}}_{\mathrm{2D}}$.

Based on unit analysis of the 2D polarizability, its in- and
out-of-plane components can be described as the characteristic
lengthes in both directions. In fact, such characteristic length is
just the dielectric screening length. The potential from a point
charge inside the 2D material generates an in-plane potential
$V(\rho)$ as function of distance $\rho$ from the point charge, in the
Keldysh form \cite{Keldysh_1979_eps_multi,Pulci_2014}:
\begin{equation}
  \label{eq:Keldysh}
  V(\rho) = \frac{e}{4 \alpha^{\parallel}}
  \left[H_{0}(\frac{2\varepsilon_{0}\rho}{\alpha^{\parallel}})
    - Y_{0}(2 \varepsilon_{0}\frac{\rho}{\alpha^{\parallel}})\right]
\end{equation}
The length $r^{\parallel}_{0} = \alpha^{\parallel}/(2\varepsilon_{0})$
determines the degree of in-plane dielectric screening: the charges
feel strong screening when $\rho/r^{\parallel}_{0} \ll 1$ while the
screening for $\rho/r^{\parallel}_{0} \gg 1$ reduces to the case of
vacuum. In other words, the quantity
$\alpha^{\parallel}/(2\varepsilon_{0})$ characterizes the radius of
localized in-plane screened potential. Combining with the result that
the thickness of 2D material is characterized by
$\alpha^{\perp}/\varepsilon_{0}$, we have drawn a generalized picture
of the dielectric nature of 2D materials via the 2D polarizability:
the dielectric screening of a point charge sitting in the middle of a
2D material can be viewed as an ellipsoid with the length of
principle axes to be $\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively. Beyond the
boundary the ellipsoid the dielectric screening gradually reduced to
the vacuum situation. Note such radius is not essentially the 2D
exciton radius, which is still related with the effective mass
\cite{Chernikov_2014_EB_MoS2_2D3D}. Nevertheless, with the universal
relation between $\alpha^{\parallel}-E_{\mathrm{g}}$ and
$\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ for 2D materials,
we are able to quantitatively predict and design the dielectric nature
of a new 2D material by engineering the bandgap and geometry, which
can greatly enhance our understanding and application of 2D materials.

\subsection{Bridging the 2D and 3D Dielectric Properties}
\label{sec:2D-3D}

Apart from the universal relations we propose for the 2D materials, it
is also of high theoretical interest to model the transition of
dielectric properties from the 2D world to the 3D world. In other
words, can we describe the dielectric constants of a bulk layered
material from the polarizabilities of the monolayer (see Figure
\ref{fig-4}a)? The static dielectric constants
$\varepsilon_{\mathrm{bulk}}$ for a bulk material with equilibrium
interlayer distance $L_{\mathrm{bulk}}$, can be expressed using the
polarizabilities of the individual layers in the bulk material
$\alpha_{\mathrm{bulk}}$:
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{bulk}} &= \left(1 - \frac{\alpha_{\mathrm{bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{bulk}}}\right)^{-1}
\end{eqnarray}
Note that $\alpha_{\mathrm{bulk}}$ may not essentially be the same as
$\alpha$ of isolated layer. Nevertheless we will first see how good
the predictions can be made when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. Figure \ref{fig-4}b and \ref{fig-4}c
show the comparison between the
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, respectively. We observe that
such approach provides good estimation of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$, with the mean average error
(MAE) of 1.35. On the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. Such results means that the
$\alpha^{\parallel}$ in a bulk layered material can generally be
estimated from its 2D counterpart, while $\alpha^{\perp}$ differs from
the values of monolayer, as also observed in other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. Two factors contribute
to the discrepancy: (i) the overlap between induced dipoles is larger
perpendicular to the plane than parallel to the plane, and (ii) the
interlayer coupling is larger for 2D materials with smaller
bandgap. If we have an accuracy approach to model
$\alpha_{\mathrm{bulk}}$ as function of $\alpha$ and the degree of
interlayer coupling $\eta$ \cite{Tkatchenko_2012}, the dielectric
transition from 2D to 3D would be smoothly described.

Next we will show how the relation between dielectric properties
transforms from 2D to 3D. Extend the approach for modeling
$\alpha^{\parallel}$ in Eq. \ref{eq:alpha_perp_RPA} to the bulk
material, and use the Bloch presentation for wavefunctions in all
dimensions, we get:
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \varepsilon_{\mathrm{bulk}} = 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
Using a similar treatment for
$|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}$ as in
Ref. \citenum{Jiang_2017_Eg_Eb} we end up with the relation
$\alpha_{\mathrm{bulk}} \propto 1/\sqrt{E_{\mathrm{g}}}$ (details see
Supplementary Section SXX \todo{note}), which recovers the Moss
relation under rigorous treatment \cite{Finkenrath_1988}. Therefore,
the universal $\alpha^{\perp}-E_{\mathrm{g}}$ relation is indeed the
Moss relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is dominated by the confinement
perpendicular to the 2D plane.

Finally, we would like to comment on the generality of the dielectric
nature between the 2D and 3D worlds. As schematically shown in Figure
\ref{fig-2D-3D}, the physical quantities related to the dielectric
properties can be categorized into (i) strictly 2D (microscopic), (ii)
strictly 3D (macroscopic) and (iii) valid both 2D and 3D.  $\alpha$
and $\varepsilon$ are the starting point for the strictly 2D and 3D
quantities, which require distinct definitions when dimensionality
changes. Such quantities include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
  details see Supplementary Section SXX \todo{TBD}).

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.

\section{Conclusion}
\label{sec:org5fd1f1a}

To sum up, using first principles calculation for over 50 kinds of 2D
materials, we reveal the universal relation between the dielectric
nature of 2D materials and other physical quantities via the 2D
polarizability. The in-plane polarizability of a 2D material is found
to be inversely proportional to the minimal bandgap, while the
out-of-plane polarizability is the characteristic thickness of the 2D
material. Such universal scaling relation is explained by a quantum
mechanical model combining the polarizability in both directions. Our
universal scaling relation bridges the gap between 2D and 3D
dielectric properties with good accuracy of prediction.  Our numerical
findings and theoretical analysis pave the way to understand and
engineer the electronic and dielectric properties of a large library
of 2D materials for different technological applications in an
unified and unprecedented way.

\section{Theoretical Methods}
\label{sec:org8457dbb}

All results calculated for this paper were the result of \emph{ab initio}
simulations carried out using plane-wave Density Functional Theory
package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the
Projector Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Hybrid functional HSE06, with Spin Orbit Coupling
explicitly included. The geometries were converged both in cell
parameters and ionic positions, with forces below 0.04 eV/Å. A vacuum
spacing of at least 12 Å was used for each material. A K-Point grid of
\(7\times7\times1\) was used to relax, with an initial relaxation
carried out at PBE level and a subsequent relaxation carried out at
HSE06 level, allowing both cell parameters and ionic positions to
relax each time. In VASP, the tag PREC=High was used, giving a plane
wave kinetic energy cutoff of 30\% greater than the highest given in
the pseudopotentials used in each material, guaranteeing that absolute
energies were converged to a few meV and the stress tensor to within a
few kBar. A final HSE06 calculation with SOC was then carried out
using a 14x14x1 K-Point grid, from which the density of states was
taken.
\todo{add more notes here}

\bibliography{ref}

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.90\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} The macroscopic dielectric constant and
  microscopic polarizability of a 2D material. \textbf{a}. Left: 2D
  material in a superlattice with length $L$ in the z-direction. The
  periodic images of the 2D material are shown below and above the
  superlattice. Right: simplied presentation of the dielectric
  constants $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ of the superlattice as a
  combined effect of the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ and the vacuum. \textbf{b}. Change of spatial
  charge density $\Delta \rho(z)$ in the z-direction for a layer of
  2H-MoS$_{2}$ under external eletric field of 0.01 V/\AA{}. The green
  and red regions represent negative and positive induced charges,
  respectively. \textbf{c}. $\varepsilon^{\parallel}_{\mathrm{SL}}$
  (left) and $\alpha_{\mathrm{SL}}^{\parallel}$ (right) as functions
  of $L$ for a 2H-MoS$_{2}$
  layer. \textbf{d}. $\varepsilon^{\perp}_{\mathrm{SL}}$ (left) and
  $\alpha_{\mathrm{SL}}^{\perp}$ (right) as functions of $L$ for a
  2H-MoS$_{2}$ layer. The polarizabilities in \textbf{c} and
  \textbf{d} are constant when $L>$15 \AA{}.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
\caption{\label{fig-2} The 2D materials investigated. \textbf{a}. The
  elements that involved in this study. \textbf{b} 3D structures of
  the 2D materials investigated in this study.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
\caption{\label{fig-3} The universal scaling relation of the
  dielectric nature of 2D materials. \textbf{a}. $\alpha^{\parallel}$,
  $\alpha^{\perp}$ (bar plots) and $E_{\mathrm{g}}$ (blue dots) for
  all the 2D materials studied.  $\alpha^{\parallel}$ is observed to
  descend with increasing $E_{\mathrm{g}}$, while no apparent relation
  between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of the covalent thickness, showing a perfect
  linear relation with slope very close to $1/4\pi$. The materials in
  \textbf{b} and \textbf{c} are grouped by their prototyes, including
  1T-TMDCs and cadmium halide (1T-MX$_{2}$), 2H-TMDCs (2H-MX$_{2}$),
  boron nitride (BN), phosphorene (P), monochalcogenides (GaS) and
  graphene derivatives (CH).}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
\caption{\label{fig-delta} Scheme for the determination of the
  covalent thickness of one-atom-thick (left) and few-atom-thick
  (right) 2D materials.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} Transition of dielectric properties from 2D to
  3D systems. \textbf{a}. Scheme for the 2D-3D transition. $\alpha$ in
  the 2D material is essentially equivalent to $\varepsilon$ in its
  bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. }
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
  both 2D (red circle) and 3D (cyan circle) systems. The
  dimension-dependent quantities can be related with $\alpha$ and
  $\varepsilon$, respectively. The intersection between the circles
  present the quantities are well-defined in both dimensions, but may have a
  different scaling relation with others quantities.}
\end{figure}
\end{document}

### 2018-10-01 BS_figures.tex
Add SI figures for raw data

% \documentclass{article}

% \usepackage{graphicx}
% \usepackage{float}

% \begin{document}
\maxdeadcycles=200
\begin{figure}[htbp]
  \centering
  {\bfseries \sffamily 1T-TiO$_{2}$}\\
  % \vskip -2cm
  \includegraphics[width=0.45\linewidth, angle=-90, trim={3cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-TiO2.eps}
\end{figure}

\begin{figure}[htbp]
  \centering
  {\bfseries \sffamily 2H-TiO$_{2}$}\\
  % \vskip -2cm
  \includegraphics[width=0.45\linewidth, angle=-90, trim={3cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-TiO2.eps}
\end{figure}

\begin{figure}[htbp]
  \centering
  {\bfseries \sffamily 2H-TiS$_{2}$}\\
  % \vskip -2cm
  \includegraphics[width=0.45\linewidth, angle=-90, trim={3cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-TiS2.eps}
\end{figure}

\begin{figure}[htbp]
  \centering
  {\bfseries \sffamily 2H-TiSe$_{2}$}\\
  % \vskip -2cm
  \includegraphics[width=0.45\linewidth, angle=-90, trim={3cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-TiSe2.eps}
\end{figure}

\begin{figure}[htbp]
  \centering
  {\bfseries \sffamily 1T-ZrO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-ZrO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-ZrS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-ZrS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-ZrSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-ZrSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-ZrO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-ZrO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-ZrSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-ZrSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-ZrTe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-ZrTe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-HfO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-HfO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-HfS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-HfS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-HfSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-HfSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-HfO4$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-HfO2.eps}
\end{figure}

% \begin{figure}[htbp]
% \centering
% {\bfseries \sffamily 2H-HfS$_{2}$}\\
% \includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-HfS2.eps}
% \end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-HfSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-HfSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-HfTe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-HfTe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-GeO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-GeO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-GeS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-GeS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-GeO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-GeO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-SnO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-SnO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-SnS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-SnS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-SnSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-SnSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-SnO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-SnO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-SnS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-SnS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PbO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PbO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily BN}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/hBN.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily C$_{2}$F$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/FGraph.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily P$_{4}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/Phosphorene.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily C$_{2}$H$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/Graphane.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-NiO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-NiO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PdO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PdO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PdS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PdS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PtO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PtO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PtS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PtS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PdSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PdSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-NiS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-NiS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 1T-PtSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/1T-PtSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily Ga$_{2}$Se$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/GaSe.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily Ga$_{2}$S$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/GaS.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily CdI$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/CdI2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-MoS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-MoS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-WS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-WS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-WSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-WSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-WO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-WO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-MoO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-MoO2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-MoTe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-MoTe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-WTe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-WTe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-CrS$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-CrS2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-CrSe$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-CrSe2.eps}
\end{figure}

\begin{figure}[htbp]
\centering
{\bfseries \sffamily 2H-CrO$_{2}$}\\
\includegraphics[width=0.45\linewidth, angle=-90, trim={2.9cm, 0cm, 2cm, 0cm}, clip]{img/SI_figs/BS/2H-CrO2.eps}
\end{figure}

% \end{document}

### 2018-10-01 DOS_figs.tex
Add SI figures for raw data

\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-TiO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-TiO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-TiS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-TiSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-ZrO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-ZrS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-ZrSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-ZrO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-ZrSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-ZrTe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-HfO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-HfS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-HfSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-HfO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-HfS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-HfSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-HfTe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-GeO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-GeS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-GeO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-SnO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-SnS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-SnSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-SnO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-SnS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PbO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/hBN-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/FGraph-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/Phosphorene-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/Graphane-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-NiO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PdO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PdS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PtO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PtS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PdSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-NiS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/1T-PtSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/GaSe-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/GaS-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/CdI2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-MoS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-WS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-WSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-WO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-MoO2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-MoTe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-WTe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-CrS2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-CrSe2-DOS.pdf}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{img/SI_figs/2H-CrO2-DOS.pdf}
\end{center}

### 2018-10-01 src/distance/fit_func.py

@@ -1,0 +1,74 @@
+import numpy
+from scipy.optimize import curve_fit
+import os, os.path
+import matplotlib.pyplot as plt
+from scipy.constants import pi
+plt.style.use("science")
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+names = next(g)[1]
+for i, item in enumerate(g):
+    if "old" in item:
+        continue
+    for f in item[2]:
+        f_path = os.path.join(item[0], f)
+        if "agr" not in f_path:
+            continue
+        print(f_path)
+        data = numpy.genfromtxt(f_path,
+                                delimiter=" "
+                                # skip_header=297,
+                                # skip_footer=2
+         )
+        # data = data[1: , :]
+        L = data[:, 0]
+        eps_SL = data[:, 1]
+        if "parallel.agr" in f_path:
+            alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
+        elif "perpendicular.agr" in f_path:
+            alpha_SL = L * (data[:, 1] - 1) / (data[:, 1]) / (4 * pi)
+        fig = plt.figure(figsize=(2.5, 2.5))
+        ax = fig.add_subplot(111)
+        ax2 = ax.twinx()
+        ax.plot(L, eps_SL, "o-", color="#00AAD4")
+        ax2.plot(L, alpha_SL, "o-", color="#FF6600")
+
+        ax.set_xlabel("$L$ ($\\AA$)")
+        if "par" in f_path:
+            param, _ = curve_fit(fit_para, L, eps_SL,
+                                 p0=(5, 10),
+                                 bounds=((0.5, 1.0),
+                                         (10, 50))
+            )
+            LL = numpy.linspace(10, 70)
+            # ax.plot(LL, fit_para(LL, *param), "--")
+            # ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{d}}={0:.3f}$".format(*param, names[i]))
+            # ax.set_ylabel("$\\epsilon_{\\parallel}$")
+            ax.set_title("{} parallel".format(names[i]))
[…]

### 2018-10-01 src/distance/fit_func_PRB.py

@@ -1,0 +1,75 @@
+import numpy
+from scipy.optimize import curve_fit
+import os, os.path
+import matplotlib.pyplot as plt
+from scipy.constants import pi
+plt.style.use("science")
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+names = next(g)[1]
+tags = {
+    "mos2": "MoS$_{2}$",
+    "mose2": "MoSe$_{2}$",
+    "mote2": "MoTe$_{2}$",
+    "ws2": "WS$_{2}$",
+    "wse2": "WSe$_{2}$",
+    "wte2": "WTe$_{2}$",
+}
+for i, item in enumerate(g):
+    if "old" in item:
+        continue
+    for f in item[2]:
+        f_path = os.path.join(item[0], f)
+        if "agr" not in f_path:
+            continue
+        print(f_path)
+        data = numpy.genfromtxt(f_path,
+                                delimiter=" "
+                                # skip_header=297,
+                                # skip_footer=2
+         )
+        # data = data[1: , :]
+        L = data[:, 0]
+        eps_SL = data[:, 1]
+        fig = plt.figure(figsize=(2.5, 2.5))
+        ax = fig.add_subplot(111)
+        # ax2 = ax.twinx()
+        ax.plot(L, eps_SL, "o")
+        # ax2.plot(L, alpha_SL, "o-", color="#FF6600")
+
+        ax.set_xlabel("$L$ ($\\AA$)")
+        if "par" in f_path:
+            param, _ = curve_fit(fit_para, L[1:], eps_SL[1:],
+                                 p0=(5, 10),
+                                 bounds=((0.5, 1.0),
+                                         (10, 50))
+            )
+            LL = numpy.linspace(10, 70)
+            ax.plot(LL, fit_para(LL, *param), "--")
+            ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{d}}={0:.3f}\\ \\AA$".format(*param, tags[names[i]]))
+            ax.set_ylabel("$\\epsilon_{\\parallel}$")
+            # ax.set_title("{} parallel".format(names[i]))
[…]

### 2018-10-01 src/post_processing/plot_2D_eps.py

@@ -1,0 +1,16 @@
+import matplotlib.pyplot as plt
+import numpy
+from scipy.constants import pi, epsilon_0
+
+plt.figure(figsize=(3.5, 3.5))
+plt.style.use("science")
+alpha = 5
+delta = numpy.linspace(4.5, 5.5, 1000)
+eps = 1 / (1 - alpha / delta)
+# print(eps)
+plt.plot((delta - alpha)/alpha * 100, eps, "o", markersize=2)
+plt.axhline(y=1, ls="--")
+plt.ylim(-100, 100)
+plt.xlabel("Difference between $\\delta_{\\mathrm{2D}}$ and $\\alpha^{\\perp}/\\varepsilon_{0}$ (%)")
+plt.ylabel("Calculated $\\varepsilon_{\\mathrm{2D}}^{\\perp}$")
+plt.savefig("../../tmp_img/scale_error.svg")

### 2018-10-01 src/gpaw_analysis/alpha_relation_subset_conflict-20180813-120552.py
Delete unnecessary files

@@ -1,107 +1,0 @@
-import ase.db
-import warnings
-import numpy
-import matplotlib.pyplot as plt
-from ase.data import covalent_radii
-from scipy.stats import linregress
-import os, os.path
-from scipy.constants import pi, epsilon_0
-
-db_file = "../../data/gpaw_data/c2db.db"
-if not os.path.exists(db_file):
-    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
-                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
-
-
-subset = [l.strip() for l in open("list.txt").readlines() if l != "\n"]
-
-db = ase.db.connect(db_file)
-
-materials = []
-alpha_x = []
-alpha_z = []
-Eg_HSE = []
-Eg_GW = []
-Eg_PBE = []
-thick = []
-
-def get_thick(atom_row):
-    pos = atom_row.positions[:, -1]
-    diff = covalent_radii[atom_row.numbers]
-    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
-    return zmax
-
-candidates = db.select(selection="gap_gw>0.5")
-
-for mol in candidates:
-    if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
-        continue
-    if mol.formula not in subset:
-        continue
-    print("{0}-{1}".format(mol.formula, mol.prototype))
-    togo = True
-    for attrib in ("gap", "gap_hse",
-                   "gap_gw", "alphax", "alphaz"):
-        if not hasattr(mol, attrib):
-            warnings.warn("{0} doesn't have attribute {1}!".format(mol.formula,
-                                                                   attrib))
-            togo = False
-    if togo is not True:
-        warnings.warn("{0} not calculated!".format(mol.formula))
-        continue
-    materials.append("{0}-{1}".format(mol.formula, mol.prototype))
-    alpha_x.append(mol.alphax)
[…]

### 2018-10-09 paper.tex
minor change for manuscript

@@
 
-All results calculated for this paper were the result of \emph{ab initio}
-simulations carried out using plane-wave Density Functional Theory
-package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the
-Projector Augmented Wave (PAW) approach with Kresse’s mainly GW
+All results calculated for this paper were the result of \emph{ab
+  initio} simulations carried out using plane-wave Density Functional
+Theory (DFT) package VASP
+\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
+Augmented Wave (PAW) approach with Kresse’s mainly GW
 Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
-calculated using the Hybrid functional HSE06, with Spin Orbit Coupling
-explicitly included. The geometries were converged both in cell
-parameters and ionic positions, with forces below 0.04 eV/Å. A vacuum
-spacing of at least 12 Å was used for each material. A K-Point grid of
-\(7\times7\times1\) was used to relax, with an initial relaxation
-carried out at PBE level and a subsequent relaxation carried out at
-HSE06 level, allowing both cell parameters and ionic positions to
-relax each time. In VASP, the tag PREC=High was used, giving a plane
-wave kinetic energy cutoff of 30\% greater than the highest given in
-the pseudopotentials used in each material, guaranteeing that absolute
-energies were converged to a few meV and the stress tensor to within a
-few kBar. A final HSE06 calculation with SOC was then carried out
-using a 14x14x1 K-Point grid, from which the density of states was
-taken.
-\todo{add more notes here}
+calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
+\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
+included. The geometries were converged both in cell parameters and
+ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
+of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
+used. A k-point grid of \(7\times7\times1\) was used to relax the
+superlattice, with an initial relaxation carried out at the
+Perdew-Burke-Ernzerhof
+(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
+exchange-correlation functional level and a subsequent relaxation
+carried out at HSE06 level, allowing both cell parameters and ionic
+positions to relax each time. In VASP, the tag PREC=High was used,
+giving a plane wave kinetic energy cutoff of 30\% greater than the
+highest given in the pseudopotentials used in each material,
+guaranteeing that absolute energies were converged to a few meV and
+the stress tensor to within a few kBar.  Calculation of the
+macroscopic ion-clamped dielectric tensor were carried out with an
+18$\times$18$\times$1 k-grid and electric field strength of 0.001
+eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
+length of corresponding monolayer material with the interlayer van der
+Waals (vdW) interactions calculated by non-local vdW correlation
+functional\cite{Lee_2010_vdFD2}. The dielectric properties of bulk
+layered materials were calculated at PBE level with
+18$\times$18$\time$6 k-grid with same parameter as for monolayer.
 

### 2018-10-09 src/VASP_HSE/DOS.py

@@ -18,7 +18,8 @@ for m in materials:
 data = numpy.array(data)
 # plt.plot(data[:, 0], data[:, 2], "o")  # 2D
 # plt.plot(data[:, 2], data[:, 1], "o")  # 2D
-plt.plot(data[:, 3] ** -1, data[:, 1], "o")  # 2D
+plt.plot(data[:, 3], data[:, 1], "o")  # 2D
+plt.yscale("log")
 # plt.xlim(0, 2)
 
 plt.savefig("../../tmp_img/test_alpha_QC.pdf")

### 2018-10-09 src/distance/fit_func_all.py
All plots for eps and alpha done for fig1

@@ -1,0 +1,88 @@
+import numpy
+from scipy.optimize import curve_fit
+import os, os.path
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+from scipy.constants import pi
+from model_eps import plot_eps_para, plot_eps_perp
+plt.style.use("science")
+
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+names = next(g)[1]
+gs = GridSpec(3, 1)
+fig1 = plt.figure(figsize=(3, 3))
+fig2 = plt.figure(figsize=(3, 3))
+ax1_r = fig1.add_subplot(gs[0])
+ax1 = fig1.add_subplot(gs[1: ])
+ax2_r = fig2.add_subplot(gs[0])
+ax2 = fig2.add_subplot(gs[1: ])
+
+plot_eps_para(ax1, alpha_0=8.5, dev=4)
+plot_eps_perp(ax2, alpha_0=0.47, dev=0.15)
+
+for i, item in enumerate(g):
+    if "old" in item:
+        continue
+    for f in item[2]:
+        f_path = os.path.join(item[0], f)
+        if "agr" not in f_path:
+            continue
+        print(f_path)
+        data = numpy.genfromtxt(f_path,
+                                delimiter=" "
+                                # skip_header=297,
+                                # skip_footer=2
+         )
+        # data = data[1: , :]
+        L = data[:, 0]
+        eps_SL = data[:, 1]
+        if "parallel.agr" in f_path:
+            alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
+            l, *_ = ax1.plot(L, eps_SL, "o-",
+                             label=names[i],
+                             markersize=4)
+            ax1_r.plot(L, alpha_SL, "o-",
+                       markersize=4,
+                       color=l.get_c())
+        elif "perpendicular.agr" in f_path:
[…]

### 2018-10-09 src/distance/model_eps.py

@@ -1,0 +1,43 @@
+import numpy
+import matplotlib.pyplot as plt
+from scipy.constants import epsilon_0, pi
+
+def eps_para(alpha, L):
+    return 1 + 4 * pi * alpha / L
+
+def eps_perp(alpha, L):
+    return 1 / (1 - 4 * pi * alpha / L)
+
+def plot_eps_para(ax, alpha_0, dev, trans=0.7):
+    L = numpy.linspace(10, 60, 100)
+    [ax.plot(L, eps_para(a, L), c="#839abf",
+             alpha=(1 - abs(a - alpha_0) / dev) * trans) \
+     for a in numpy.linspace(alpha_0 - dev * 0.999,
+                             alpha_0 + dev * 0.999)]
+    return
+
+def plot_eps_perp(ax, alpha_0, dev, trans=0.7):
+    L = numpy.linspace(10, 60, 100)
+    [ax.plot(L, eps_perp(a, L), c="#cca384",
+             alpha=(1 - abs(a - alpha_0) / dev) * trans) \
+     for a in numpy.linspace(alpha_0 - dev * 0.999,
+                             alpha_0 + dev * 0.999)]
+    return
+
+plt.style.use("science")
+fig = plt.figure(figsize=(6, 2.5))
+ax = fig.add_subplot(121)
+ax2 = fig.add_subplot(122)
+L = numpy.linspace(10, 60, 100)
+#color plots
+[ax.plot(L, eps_para(a, L), c="#839abf", alpha=(1 - abs(a - 9.0) / 4)) for a in numpy.linspace(5, 13, 100)]
+ax.set_title("$\\alpha^{\\parallel} = 9 \\pm 4$")
+ax.set_xlabel("L")
+ax.set_ylabel("Model $\\varepsilon^{\\parallel}$")
+# 
+[ax2.plot(L, eps_perp(a, L), c="#cca384", alpha=(1 - abs(a - 0.5) / 0.1)) for a in numpy.linspace(0.4, 0.6, 100)]
+ax2.set_title("$\\alpha^{\\perp} = 0.5 \\pm 0.1$")
+ax2.set_xlabel("L")
+ax2.set_ylabel("Model $\\varepsilon^{\\perp}$")
+fig.tight_layout()
+fig.savefig("../../tmp_img/model_eps_parallel.svg")

### 2018-10-10 src/VASP_HSE/gpaw_data.py
figure 1-3 version 20181010

@@ -1,0 +1,158 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+import os, os.path
+from scipy.constants import pi, epsilon_0
+
+db_file = "../../data/gpaw_data/c2db.db"
+if not os.path.exists(db_file):
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
+
+db = ase.db.connect(db_file)
+valence = numpy.load("../post_processing/valence.npy")
+pol = numpy.load("../post_processing/valence.npy")
+
+
+def get_thick(atom_row):
+    pos = atom_row.positions[:, -1]
+    diff = covalent_radii[atom_row.numbers]
+    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
+    vals = valence[atom_row.numbers]  # valence electrons
+    atom_pol = pol[atom_row.numbers]
+    A = atom_row.cell_area
+    return zmax, sum(vals) / A, sum(atom_pol) / A
+
+
+def get_data():
+    candidates = db.select(selection="gap_gw>0.5")
+    materials = []
+    alpha_x = []
+    alpha_z = []
+    Eg_HSE = []
+    Eg_GW = []
+    Eg_PBE = []
+    thick = []
+    n_2D = []
+    polar = []
+
+    for mol in candidates:
+        if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
+            continue
+        print("{0}-{1}".format(mol.formula, mol.prototype))
+        togo = True
+        for attrib in ("gap", "gap_hse",
+                       "gap_gw", "alphax", "alphaz"):
+            if not hasattr(mol, attrib):
+                warnings.warn("{0} doesn't have attribute {1}!".format(mol.formula,
+                                                                       attrib))
+                togo = False
+        if togo is not True:
[…]

### 2018-10-12 src/VASP_HSE/polarizability_histo.py
Changes to Figs 1-4 to include the comparison between bulk and mono

@@ -5,6 +5,9 @@ from scipy.constants import pi, k, epsilon_0, e
 
 data = json.load(open("../../data/HSE-data/all_data.json", "r"))
 
+def model_alpha(x, ratio=0.1657):
+    return 1 / ( ratio * x - 0.0243)
+
 maters = []
 alpha = []
 Eg = []
@@ -31,11 +34,16 @@ ax2 = ax1.twinx()
 
 res = sorted(zip(Eg, alpha, maters))
 maters = [n for e, a, n in res]
-ax = [a[0] for e, a, n in res]
+ax = [max(a[0], 1/1.2) for e, a, n in res]
 az = [a[1] for e, a, n in res]
 Eg = [e for e, a, n in res]
 
 xx = numpy.arange(0, len(maters))
+
+for r in numpy.linspace(0.12, 0.20, 100):
+    a_model = model_alpha(numpy.array(Eg), r)
+    ax1.plot(xx +0.5, a_model, color="cyan",
+             alpha=0.2)
 
 ax2.plot(Eg, "o-", markersize=6)
 ax1.bar(xx, ax, color="#FFCC00", alpha=0.7)
@@ -43,6 +51,7 @@ ax1.bar(xx, az, color="#FF5555", alpha=0.5)
 ax1.set_xticks(range(0, len(maters)))
 mnames = [n[0] + n[1:].replace("2", "$_{2}$") for n in maters]
 ax1.set_xticklabels(mnames, rotation="vertical")
+ax1.set_ylim(0, 13)
 plt.tight_layout()
 plt.savefig("../../tmp_img/all_data.svg")
 

### 2018-10-12 src/VASP_HSE/relation_2D3D.py

@@ -16,10 +16,7 @@ import csv
 Extract the alpha from the HSE xlsx files
 """
 
-db_file = "../../data/gpaw_data/c2db.db"
-if not os.path.exists(db_file):
-    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
-                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+db_file = "../../data/2D-bulk/bulk.db"
 
 
 db = ase.db.connect(db_file)
@@ -41,25 +38,42 @@ def get_thick(atom_row):
     zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
     return zmax
 
-def get_bulk(name, proto):
+def get_bulk(name, proto, id=None):
     # Get bulk properties
-    dir_root = os.path.join("../../data/2D-bulk/{}-{}".format(name, proto))
-    gpw_file = os.path.join(dir_root, "gs.gpw")
-    traj_file = os.path.join(dir_root, "{}-{}_relax.traj".format(name, proto))
-    eps_file = os.path.join(dir_root, "eps_df.npz")
-    if (not os.path.exists(gpw_file)) or (not os.path.exists(eps_file)):
-        return None
-    else:
-        try:
-            d = Trajectory(traj_file)[-1].cell[-1][-1]
-        except Exception:
+    if id is None:
+        res = list(db.select(formula=name, prototype=proto))
+        if len(res) == 0:
             return None
-            # calc = GPAW(gpw_file)
-            # d = calc.get_atoms().cell[-1][-1]
-        f = numpy.load(eps_file)
-        eps_xx = f["eps_x"][0].real
-        eps_zz = f["eps_z"][0].real
-        return d, eps_xx, eps_zz
+        r = res[0]
+    else:
+        r = db.get(id)    
+    try:
+        L = r.bulk_L
+        eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
+        eps_perp = r.bulk_eps_z
+        if eps_para < 0 or eps_perp < 0:
+            return None
+    except Exception:
+        return None
+    return L, eps_para, eps_perp
+    
[…]

### 2018-10-12 src/VASP_HSE/relation_alpha.py

@@ -7,6 +7,7 @@ from scipy.stats import linregress
 from scipy.optimize import curve_fit
 import os, os.path
 from scipy.constants import pi, epsilon_0
+from gpaw_data import get_data
 import scipy
 import csv
 
@@ -49,6 +50,7 @@ for row in reader:
             e_xy = numpy.sqrt(ex * ey)
             ax = (e_xy - 1) / (4 * pi) * L
             az = (1 - 1/ez) * L / (4 * pi)
+            ax = max(1 / 1.2, ax)
             eps_x.append(e_xy); eps_z.append(ez)
             alpha_x.append(ax); alpha_z.append(az)
             Eg_HSE.append(E)
@@ -81,7 +83,7 @@ plt.subplot(121)
 plt.scatter(Eg_HSE, alpha_x, marker="o", alpha=0.5, c=cs)
 def fit_func(x, a,b):
     return b / x
-
+'''
 fit_param, cov = curve_fit(fit_func,
                       xdata=Eg_HSE, ydata=alpha_x,
                       p0=(0, 10))
@@ -113,39 +115,54 @@ yy = fit_func(xx, *fit_param)
 plt.plot(Eg_HSE, alpha_x, "o", alpha=0.5)
 plt.plot(xx, yy, "--")
 plt.savefig(os.path.join(img_path, "alpha_fit_naive.pdf"))
+'''
 
-
+gp_data = get_data()
 
 # x-direction
-plt.figure(figsize=(3.5, 3.5))
-plt.scatter(Eg_HSE, 1 / (alpha_x), marker="o",
+fig = plt.figure(figsize=(3, 3))
+ax = fig.add_subplot(111)
+# gpaw
+ax.scatter(gp_data[2], 1 / gp_data[0], marker="s", alpha=0.1,
+           c="#7289af")
+# hse
+ax.scatter(Eg_HSE, 1 / (alpha_x), marker="o",
             edgecolors=None, alpha=0.5,
             c=cs)
 res = linregress(x=Eg_HSE, y=1 / (alpha_x))
 print(res)
-xx = numpy.linspace(min(Eg_HSE), max(Eg_HSE))
+xx = numpy.linspace(min(gp_data[2]), max(gp_data[2]))
 yy = res.slope * xx + res.intercept
[…]

### 2018-10-12 src/distance/fit_func_all.py

@@ -16,17 +16,28 @@ def fit_vert(L, d, eps_2D):
 
 root = "../../data/distance/"
 g = os.walk(root)
+# print(g)
 names = next(g)[1]
-gs = GridSpec(3, 1)
-fig1 = plt.figure(figsize=(3, 3))
-fig2 = plt.figure(figsize=(3, 3))
-ax1_r = fig1.add_subplot(gs[0])
-ax1 = fig1.add_subplot(gs[1: ])
-ax2_r = fig2.add_subplot(gs[0])
-ax2 = fig2.add_subplot(gs[1: ])
+# print(names)
+# names = sorted(names)
+gs = GridSpec(7, 1, hspace=0.3)
+fig1 = plt.figure(figsize=(3, 3.2))
+fig2 = plt.figure(figsize=(3, 3.2))
+ax1_r = fig1.add_subplot(gs[:2])
+ax1 = fig1.add_subplot(gs[2: ])
+ax2_r = fig2.add_subplot(gs[:2])
+ax2 = fig2.add_subplot(gs[2: ])
 
-plot_eps_para(ax1, alpha_0=8.5, dev=4)
-plot_eps_perp(ax2, alpha_0=0.47, dev=0.15)
+colors = {"mos2": "#1f77b4",
+          "mose2": "#ff7f0e",
+          "mote2": "#2ca02c",
+          "ws2": "#d62728",
+          "wse2": "#9467bd",
+          "wte2": "#8c564b",
+}
+
+# plot_eps_para(ax1, alpha_0=8.5, dev=4)
+# plot_eps_perp(ax2, alpha_0=0.47, dev=0.15)
 
 for i, item in enumerate(g):
     if "old" in item:
@@ -48,7 +59,9 @@ for i, item in enumerate(g):
             alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
             l, *_ = ax1.plot(L, eps_SL, "o-",
                              label=names[i],
-                             markersize=4)
+                             markersize=4,
+                             color=colors[names[i]]
+            )
             ax1_r.plot(L, alpha_SL, "o-",
                        markersize=4,
                        color=l.get_c())
@@ -56,7 +69,9 @@ for i, item in enumerate(g):
             alpha_SL = L * (data[:, 1] - 1) / (data[:, 1]) / (4 * pi)
[…]

### 2018-10-12 src/distance/model_eps.py

@@ -25,19 +25,22 @@ def plot_eps_perp(ax, alpha_0, dev, trans=0.7):
     return
 
 plt.style.use("science")
-fig = plt.figure(figsize=(6, 2.5))
+fig = plt.figure(figsize=(4, 2))
 ax = fig.add_subplot(121)
 ax2 = fig.add_subplot(122)
 L = numpy.linspace(10, 60, 100)
 #color plots
-[ax.plot(L, eps_para(a, L), c="#839abf", alpha=(1 - abs(a - 9.0) / 4)) for a in numpy.linspace(5, 13, 100)]
-ax.set_title("$\\alpha^{\\parallel} = 9 \\pm 4$")
-ax.set_xlabel("L")
-ax.set_ylabel("Model $\\varepsilon^{\\parallel}$")
-# 
-[ax2.plot(L, eps_perp(a, L), c="#cca384", alpha=(1 - abs(a - 0.5) / 0.1)) for a in numpy.linspace(0.4, 0.6, 100)]
-ax2.set_title("$\\alpha^{\\perp} = 0.5 \\pm 0.1$")
-ax2.set_xlabel("L")
-ax2.set_ylabel("Model $\\varepsilon^{\\perp}$")
+plot_eps_para(ax, alpha_0=8.5, dev=4)
+plot_eps_perp(ax2, alpha_0=0.47, dev=0.155)
+
+# [ax.plot(L, eps_para(a, L), c="#839abf", alpha=(1 - abs(a - 9.0) / 4)) for a in numpy.linspace(5, 13, 100)]
+# ax.set_title("$\\alpha^{\\parallel} = 9 \\pm 4$")
+# ax.set_xlabel("L")
+# ax.set_ylabel("Model $\\varepsilon^{\\parallel}$")
+
+# [ax2.plot(L, eps_perp(a, L), c="#cca384", alpha=(1 - abs(a - 0.5) / 0.1)) for a in numpy.linspace(0.4, 0.6, 100)]
+# ax2.set_title("$\\alpha^{\\perp} = 0.5 \\pm 0.1$")
+# ax2.set_xlabel("L")
+# ax2.set_ylabel("Model $\\varepsilon^{\\perp}$")
 fig.tight_layout()
 fig.savefig("../../tmp_img/model_eps_parallel.svg")

### 2018-10-15 src/VASP_HSE/gpaw_data.py
Support selection of database

@@ -30,6 +30,7 @@ def get_thick(atom_row):
 
 def get_data():
     candidates = db.select(selection="gap_gw>0.5")
+    candidates = db.select(selection="gap_gw>0.05")
     materials = []
     alpha_x = []
     alpha_z = []

### 2018-10-15 src/VASP_HSE/relation_2D3D.py

@@ -38,7 +38,7 @@ def get_thick(atom_row):
     zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
     return zmax
 
-def get_bulk(name, proto, id=None):
+def get_bulk(name, proto, id=None, method="gpaw"):
     # Get bulk properties
     if id is None:
         res = list(db.select(formula=name, prototype=proto))
@@ -48,9 +48,17 @@ def get_bulk(name, proto, id=None):
     else:
         r = db.get(id)    
     try:
-        L = r.bulk_L
-        eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
-        eps_perp = r.bulk_eps_z
+        if method.lower() == "gpaw":
+            L = r.bulk_L
+            eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
+            eps_perp = r.bulk_eps_z
+        # VASP version below:
+        elif method.lower() == "vasp":
+            L = r.bulk_L_vasp
+            eps_para = (r.bulk_eps_x_vasp + r.bulk_eps_y_vasp) / 2
+            eps_perp = r.bulk_eps_z_vasp
+        else:
+            return None
         if eps_para < 0 or eps_perp < 0:
             return None
     except Exception:
@@ -86,7 +94,7 @@ for row in reader:
             e_xy = numpy.sqrt(ex * ey)
             ax = (e_xy - 1) / (4 * pi) * L
             az = (1 - 1/ez) * L / (4 * pi)
-            bulk_res = get_bulk(name, proto)
+            bulk_res = get_bulk(name, proto, method="vasp")
             if bulk_res is not None:
                 materials.append("-".join((name, proto)))
                 eps_x.append(e_xy); eps_z.append(ez)
@@ -121,7 +129,7 @@ for db_id in range(1, db.count() + 1):  # db index starts with 1
     try:
         ax = (mol.alphax +  mol.alphay) / 2
         az = mol.alphaz
-        L, ex, ez = get_bulk(None, None, db_id)
[…]

### 2018-10-15 src/post_processing/update_gpaw_vasp.py

@@ -1,0 +1,36 @@
+import ase, ase.db
+import numpy
+from scipy.constants import pi, e, epsilon_0
+
+db = ase.db.connect("../../data/2D-bulk/bulk.db")
+
+csv_file = "../../data/gpaw_data/gpaw_vasp_aa.csv"
+
+with open(csv_file, "r", encoding="utf-8") as f:
+    while True:
+        line = f.readline()
+        if len(line) == 0:
+            break
+        sys, gap, L, ex, ey, ez = line.strip().split(",")
+        if any(len(s) == 0 for s in [ex, ey, ez]):  # bad results, discard
+            continue
+        try:
+            gap = float(gap); L = float(L)
+            ex = float(ex); ey = float(ey); ez = float(ez)
+        except ValueError:
+            continue
+        formula, proto = sys.split("-")
+        # print(sys.encode("utf8"), gap, L, ex, ey, ez)
+        res = list(db.select(formula=formula, prototype=proto))
+        
+        if len(res) == 0:
+            continue
+        mol = res[0]
+        db_id = mol.id
+        db.update(db_id, bulk_L_vasp=L,
+                  bulk_gap_vasp=gap,
+                  bulk_eps_x_vasp=ex,
+                  bulk_eps_y_vasp=ey,
+                  bulk_eps_z_vasp=ez)
+        print(sys, "Suscessful!")
+

### 2018-10-16 src/gpaw_analysis/gen_vasp.py
Minor change to figure 4

@@ -1,0 +1,80 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from ase.calculators.vasp import Vasp
+from ase.atoms import Atoms
+from scipy.stats import linregress
+import os, os.path
+import shutil
+from scipy.constants import pi, epsilon_0
+
+db_file = "../../data/gpaw_data/c2db.db"
+if not os.path.exists(db_file):
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
+
+db = ase.db.connect(db_file)
+
+valence = numpy.load("../post_processing/valence.npy")
+pol = numpy.load("../post_processing/valence.npy")
+
+def get_thick(atom_row):
+    pos = atom_row.positions[:, -1]
+    diff = covalent_radii[atom_row.numbers]
+    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
+    vals = valence[atom_row.numbers]  # valence electrons
+    atom_pol = pol[atom_row.numbers]
+    A = atom_row.cell_area
+    return zmax, sum(vals) / A, sum(atom_pol) / A
+
+candidates = db.select(selection="gap_gw>0.5")
+
+
+root_dir = "../../VASP/"
+curr_dir = os.path.dirname(os.path.abspath(__file__))
+for mol in candidates:
+    if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
+        continue
+    thick, *_ = get_thick(mol)
+    start_guess = thick + 0.25            #Start guess of thickness
+    tag = "{0}-{1}".format(mol.formula, mol.prototype)
+    print(tag)
+    togo = True
+    for attrib in ("alphax", "alphaz"):
+        if not hasattr(mol, attrib):
+            warnings.warn("{0} doesn't have attribute {1}!".format(mol.formula,
+                                                                   attrib))
+            togo = False
+    if togo is not True:
+        warnings.warn("{0} not calculated!".format(mol.formula))
+        continue
+    base_dir = os.path.join(root_dir, tag)
+    if os.path.exists(base_dir) is not True:
+        os.makedirs(base_dir)
+    os.chdir(base_dir)
+    calc = Vasp(restart=None,
+                xc="vdw-df2",
+                encut=800,
+                kpts={"gamma":True,
+                      "density":5.0},
[…]

### 2018-10-16 paper.tex
Change section 1 of main text

@@
 \cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
-the minor difference between the formulae used, it is clear that the
-there exists certain general electronic relations in bulk
+the minor difference between the formulae used, it is clear that there
+exists certain general electronic relations in bulk
 semiconductors. The existence of such general relationship is also of
@@
 dielectric constant $\varepsilon$, as the latter is strongly dependent
-on dependent on several critical details on the sample measurements,
-such as contamination, disorder, and model interpretation. With the
-Moss relationship or other similar models, it is feasible to predict
-the dielectric constant of a bulk semiconductor with a reasonable
-degree of certainty.
+on several critical details on the sample measurements, such as
+contamination, disorder, and model interpretation. With the Moss
+relationship or other similar models, it is feasible to predict the
+dielectric constant of a bulk semiconductor with a reasonable degree
+of certainty.
 
@@
 accurate description of the 2D dielectric nature is the prerequisite
-for the 2D Moss-like relations. Here we show that instead of the
+for a 2D Moss-like relation. Here we show that instead of the
 dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
@@
 in-plane and out-of-plane polarizations. Based on first principles
-simulation of over 50 kinds of monolayer 2D materials, we reveal the
-long-sought universal dielectric scale relation in the 2D world: the
-in-plane polarizability $\alpha^{\parallel}$ is inversely proportional
-to the minimal bandgap $E_{\mathrm{g}}$, while the out-of-plane
-polarizability $\alpha^{\perp}$ is closely related with the intrinsic
-thickness of 2D materials. The anisotropy of the 2D polarizability is
-further explained by a confined quantum model. The universal relations
-provide quantitative prediction of the dielectric properties of 2D
-materials, which leads to better design and understanding of
-electronic devices based on 2D materials and their heterostructures
-. Furthermore, such relations bridge the gap between the 2D and 3D
-properties, and ultimately pushes the boundary of the understanding of
-electronic screening in both dimensions.
+simulation of over 50 kinds \todo{some more?} of monolayer 2D
+materials, we reveal the long-sought universal dielectric scale
+relation in the 2D world: the in-plane polarizability
+$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
+$E_{\mathrm{g}}$, while the out-of-plane polarizability
+$\alpha^{\perp}$ is closely related with the intrinsic thickness of 2D
+materials. The anisotropy of the 2D polarizability is further
+explained by a confined quantum model. The universal relations provide
+quantitative prediction of the dielectric properties of 2D materials,
+which leads to better design and understanding of electronic devices
+based on 2D materials and their heterostructures. Furthermore, such
+relations bridge the dielectric properties between the 2D materials
+and their 3D counterparts, and ultimately pushes the boundary of the
+understanding of electronic screening in both dimensions.
 
@@
 
-To get the correct description between the dielectric properties of a
-2D material with other physical quantities, an accurate description of
-the dielectric nature must first be established. As shown in Figure
-\ref{fig-1}a, in first principles calculations, an isolated 2D
-material needs to be placed in a periodically repeating superlattice
-(SL) with a certain length $L$ in the out-of-plane direction to
-prevent the interaction from periodic images. The macroscopic
-dielectric constant from the superlattice, is the combined effect of
-the intrinsic 2D dielectric properties and the vacuum spacing inside
-the superlattice. From the classical electrostatics, we know that the
-dielectric tensor $\varepsilon_{\alpha \beta}$, is determined by the
-response of dipole density $\mathbf{P}_{\alpha}$ under small
-perturbative external field $\mathbf{E}_{\beta}$, such that:
-\begin{equation}
-  \label{eq:def-eps}
-  \begin{aligned}
-    \varepsilon_{\alpha \beta} &= \kappa_{\alpha \beta} +
-    \frac{\partial \mathbf{P}_{\alpha}}{\varepsilon_{0} \partial \mathbf{E}_{\beta}} \\
-    &= \kappa_{\alpha \beta} + {\displaystyle \frac{\partial {\displaystyle
-          \int_{\mathrm{SL}} \rho(\mathbf{r})\mathbf{r}_{\alpha} d^{3}\mathbf{r}}}{\Omega \varepsilon_{0} \partial \mathbf{E}_{\beta}}}
-  \end{aligned}
-\end{equation}
-where $\alpha$, $\beta$ are the directions in $(x, y, z)$,
-$\kappa_{\alpha\beta}$ is the dielectric tensor of the environment
-(equals 1 if the environment is vacuum), $\rho$ is the spatial charge
-density, $\Omega$ is the volume of the superlattice and
-$\varepsilon_{0}$ is vacuum permittivity. For 2D semiconductors, the
-off-diagonal elements of the dielectric tensor ($\alpha \neq \beta$)
-is always 0. Therefore we can distinguish two components of the
-SL dielectric constant, namely the in-plane
+In persuit of the Moss-like relation of 2D materials, a accurate
+description of the dielectric properties of 2D materials needs to be
+established. One known issue is that the concept of macroscopic
+dielectric constant is ill-defined for 2D materials
+\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
+shown in Figure \ref{fig-1}a \todo{I'll change upon your change of Fig
+  1a}, in first principles calculations, an isolated 2D material is
+placed at the xy-plane of a periodically repeating superlattice (SL)
+with a length $L$ along the z-direction large enough to prevent the
+interactions between periodic images. The macroscopic dielectric
+tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, from
+fundamental electrostatics, is determined by the response of
+volumetric dipole density $\boldsymbol{P}^{p}$, under small perturbative
+external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the
+directions in $(x, y, z)$,such that:
+\begin{subequations}
+  \begin{eqnarray}
+      \label{eq:def-eps-1}
+    &\varepsilon^{p} &= \kappa^{pq} +
+                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
+                                 {\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
+          \label{eq:def-eps-2}
+    &\boldsymbol{P}^{p} &=  {\displaystyle \frac{\boldsymbol{u}^{p}}{\Omega}}
+                          = {\displaystyle \frac{{\displaystyle
+          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}
+                          {AL}}
+  \end{eqnarray}
+\end{subequations}
+$\kappa$ is the dielectric tensor of the environment, $\boldsymbol{u}$
+is the total dipole moments of the SL, $\rho$ is the spatial charge
+density, $\Omega=AL$ is the volume of the SL, $A$ is the xy-plane area
+of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
+majority of 2D semiconductors, the off-diagonal elements of the
+dielectric tensor ($p \neq q$) tend to be negligible.  Consider that
+the 2D material is placed in vacuum, such that $\kappa^{pp} \equiv 1$
+and $\kappa^{pq} \equiv 0$, we can distinguish two components of the
+SL dielectric tensor, namely the in-plane
 ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
-($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constant, where
+($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
 $\varepsilon_{\mathrm{SL}}^{\parallel} =
@@
 and
-$\varepsilon_{\mathrm{SL}}^{\perp} =
-\varepsilon_{\mathrm{SL}}^{zz}$. Consider the volume $\Omega=AL$,
-where $A$ is the area of SL in the xy-plane, and $\kappa \equiv 1$, we
-see that both $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ depends on the superlattice length
-$L$. On the other hand, the induced dipole of the 2D to an external
-field is localized within a confined region near the 2D plane. We show
-this by plot the charge density change
-$\Delta \rho=\rho(\mathbf{E}) - \rho(\mathbf{E}=0)$ along the z-axis
-for an isolated 2H-MoS$_{2}$ layer under
-$|\mathbf{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$, as illustrated in Figure
-\ref{fig-1}b. The induced dipole only extends to ~12 \AA{} in the
-z-direction. Combining the two effects discussed above, it is
-erroneous to use directly use the value $\varepsilon_{\mathrm{SL}}$
-to present the dielectric nature of a 2D material. We need to find the
-$L$-independent quantity to present the intrinsic dielectric
-properties of the 2D material. By multiplying $\mathbf{P}$ with $L$,
-we get the sheet polarization density $\mathbf{\mu}$, such that
-$\mathbf{\mu}=\int_{\mathrm{SL}} \rho(\mathbf{r})rd^{3} \mathbf{r}/A$,
+$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$
+\todo{geometry or numerical average?}. Due to the absence of bonding
+along the z-direction, the induced charge density of a 2D material is
+highly confined. Figure \ref{fig-1}a demonstrates the charge density
+difference between zero and finite electric fields,
+$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ along the
+z-axis for an isolated 2H-MoS$_{2}$ layer under
+$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which only
+extends to ~12 \AA{} along the z-direction inside the SL. When $L$ is
+large enough that the induced dipoles from periodic images do not
+overlap, the total dipole moments $\boldsymbol{u}$ of the SL in
+Eq. \ref{eq:def-eps-2} is independent of $L$. As a consequence, we can
+see from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
+$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on the SL length $L$. We
+show this by plotting $\epsilon^{\parallel}_{\mathrm{SL}}$ and
+$\epsilon^{\perp}_{\mathrm{SL}}$ as functions of $L$ for 2H-type group
+6 transitional metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo,
+W and X=S, Se, Te), in the top panels of Figure \ref{fig-1}b and
+\ref{fig-1}c \todo{change order!}, respectively. We can also observe
+that neither $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
+$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with the superlattice
+length $L$ due to fact that the long-range Coulomb interaction could
+not be completed screened, which is computationally unpractical
+\cite{Hueser_2013_2Dvs3D}. The $L$-dependency of macroscopic
+dielectric constant makes it erroneous to use
+$\varepsilon_{\mathrm{SL}}$ to present the dielectric nature of a 2D
+material. Therefore, we need to find a $L$-independent quantity to
+present the intrinsic dielectric properties of the 2D materials. As
+discussed previous, since the total dipole moments $\mathbf{u}$ remain
+constant with $L$, we can define the surface or sheet polarization
+density matrix $\boldsymbol{\mu}$, by multiplying
+Eq. \ref{eq:def-eps-2} with $L$, that
+$\boldsymbol{\mu}^{p} = \boldsymbol{P}_{p}L = \int_{\mathrm{SL}}
+\rho(\boldsymbol{r}) \boldsymbol{r}_{p}d^{3} \boldsymbol{r}/A$,
 independent of the superlattice size. Similar to the definition of
-molecular polarizability, the sheet polarization density
-$\mathbf{\mu}$ is associated with the 2D polarizability $\alpha$ by:
-$\mathbf{\mu} = \alpha \mathbf{E}_{\mathrm{loc}}$, where
+molecular polarizability \cite{Israelachvili_2011}, the sheet
+polarization density $\boldsymbol{\mu}$ is associated with the 2D
+polarizability tensor $\alpha$ through:
+$\boldsymbol{\mu}^{p} = \sum_{q} \alpha^{pq}
+\mathbf{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
 $E_{\mathrm{loc}}$ is the local electric field. In the in-plane
@@
 \cite{Markel_2016}. Perpendicular to the 2D plane, the dipole
-screening yields $\mathbf{E}_{\mathrm{loc}}=\mathbf{E}+\mathbf{\mu}/L$
+screening yields
+$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}^{\perp}/L$
 \cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
-Eq. \ref{eq:def-eps}, we get the expressions for the in-plane and
-out-of-plane 2D polarizabilities, $\alpha^{\parallel}$ and
-$\alpha^{\perp}$, respectively:
+Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we derive the
+expressions for the in-plane and out-of-plane 2D polarizabilities,
+$\alpha^{\parallel}$ and $\alpha^{\perp}$, respectively:
 \begin{eqnarray}
   \label{eq:alpha-para-def}
-  \alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
+  &\alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
   \label{eq:alpha-perp-def}
-    \alpha^{\perp} &= \varepsilon_{0}\left(1 - \frac{1}{\varepsilon_{\mathrm{SL}}^{\parallel}}\right)L
+    &\alpha^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
 \end{eqnarray}
-The $L$-dependence presented in $\varepsilon$ is then removed in the
-2D polarizabilities.  We note that although both scaling relations
-have been proposed in individual studies
-\cite{Cudazzo_2011_screening_2D,Kumar_2016_jpcc,Kumar_2016_PRB}, the
-work presented here is the first attempt of unifying the dielectric
-properties of 2D materials by both the in- and out-of-plane
-polarizabilities, which provides a universal description of dielectric
-nature from strict 2D system to the  3D world. Next we examine
-how good the 2D polarizability can present its dielectric
-nature. Figure \ref{fig-1}c and \ref{fig-1}d show the
+The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
+$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the TMDCs as functions of
+$L$, calculated using Eqs. \ref{eq:alpha-para-def} and
+\ref{eq:alpha-perp-def}. We observe that both $\alpha^{\parallel}$ and
+$\alpha^{\perp}$ remain almost constant when $L>$15 \AA{}. In
+addition, by varying the value of $\alpha^{\parallel}$ and
+$\alpha^{\perp}$, we can nicely reproduce the $L$-dependence of
 $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$ of a
-2H-MoS$_{2}$ monolayer. As expected the $\varepsilon_{\mathrm{SL}}$
-decreases with $L$ in both cases and does not converge even when the
-SL size is as large as 60 \AA{}. On the contrary, the
-$\alpha^{\parallel}$ and $\alpha^{\perp}$ calculated using
-Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, remain
-almost constant when $L>$15 \AA{}. We have further examined the
-$\alpha-L$ relation for other group 6 transitional metal
-dichalcogenides (TMDCs), including 2H-MoSe$_{2}$, 2H-MoTe$_{2}$,
-2H-WS$_{2}$, 2H-WSe$_{2}$, 2H-WTe$_{2}$ (details see Supplementary
-Section XX \todo{TBD}). All materials exhibit constant $\alpha$ for
-$L>$15 \AA{}, confirming that $\alpha$ is the true descriptor for the
-dielectric nature of 2D materials. The calculation of $\alpha$ from
-first principles dielectric response does not require the \textit{a
-  priori} determination of the thickness of the 2D material, a
-quantity which is not well defined. On the other hand, the widely-used
-method of treating the 2D material as a dielectric slab with thickness
-$\delta$ and uniform dielectric constant $\varepsilon_{\mathrm{2D}}$
-\cite{Sharma_1985,Cudazzo_2011_screening_2D,Trolle_2017_eps_subst},
-tends to give nonphysical pictures of the 2D dielectric properties due
-to the ambiguity of $\delta$ (details see Supplementary Section XX
-\todo{TBD}). In the following sections, we will pursue the universal
-description for the dielectric nature of 2D materials starting from
-the 2D polarizability.
+$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}b
+and \ref{fig-1}c insets). These findings indicate that the 2D
+polarizability, instead of the dielectric constant, is the true
+descriptor of the dielectric properties of 2D materials.
+
+We note that the dielectric properties of 2D materials are also often
+modeled using an effect medium approach, which treats the 2D material
+as a slab with effective permittivity $\varepsilon_{\mathrm{2D}}$ and
+thickness $\delta$
+\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
+methods require \textit{a priori} determination of $\delta$, a
+quantity with controversial definitions \cite{Mas_Ballest__2011}. In
+such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
+determined by fitting the $L$-dependent data of
+$\varepsilon_{\mathrm{SL}}$, which is not only computational
+expensive, but also fails to capture the anisotropy of the 2D
+dielectric properties (details see Supplementary Section S1). On the
+other hand, calculating 2D polarizabilities requires no knowledge of
+$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
+\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
+dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
+the polarizability as the true descriptor of 2D dielectric properties,
+we will reveal the universal Moss-like relation of 2D materials.
 
@@
 layered materials were calculated at PBE level with
-18$\times$18$\time$6 k-grid with same parameter as for monolayer.
+18$\times$18$\times$6 k-grid with same parameter as for monolayer.
 

### 2018-10-16 src/distance/fit_func_all.py
Panels reorder in Figure 1

@@ -23,10 +23,10 @@ names = next(g)[1]
 gs = GridSpec(7, 1, hspace=0.3)
 fig1 = plt.figure(figsize=(3, 3.2))
 fig2 = plt.figure(figsize=(3, 3.2))
-ax1_r = fig1.add_subplot(gs[:2])
-ax1 = fig1.add_subplot(gs[2: ])
-ax2_r = fig2.add_subplot(gs[:2])
-ax2 = fig2.add_subplot(gs[2: ])
+ax1_r = fig1.add_subplot(gs[5:])
+ax1 = fig1.add_subplot(gs[:5 ])
+ax2_r = fig2.add_subplot(gs[5:])
+ax2 = fig2.add_subplot(gs[:5 ])
 
 colors = {"mos2": "#1f77b4",
           "mose2": "#ff7f0e",
@@ -76,23 +76,23 @@ for i, item in enumerate(g):
                        markersize=4,
                        color=l.get_c())
 
-ax1.set_xlabel("$L$ ($\\AA$)")
+ax1_r.set_xlabel("$L$ ($\\AA$)")
 ax1_r.set_title("parallel")
 ax1.set_ylabel("$\\epsilon^{\\parallel}_{\mathrm{SL}}$")
 ax1_r.set_ylabel("$\\alpha^{\\parallel}/(4\\pi\\varepsilon_0) (\\AA)$")
 ax1_r.set_ylim(5, 13)
-ax1_r.set_xticklabels([])
+ax1.set_xticklabels([])
 # ax1_r.set_ylim(min(alpha_SL) * 0.75, max(alpha_SL)* 1.25)
 
     # ax.plot(LL, fit_vert(LL, *param), "--")
-ax2.set_xlabel("$L$ ($\\AA$)")
+ax2_r.set_xlabel("$L$ ($\\AA$)")
 ax2.set_ylabel("$\\epsilon^{\\perp}_{\mathrm{SL}}$")
 ax2_r.set_ylabel("$\\alpha^{\\perp}/(4\\pi \\varepsilon_0) (\\AA)$")
 ax2_r.set_title("perp")
 ax2.set_ylim(1, 4)
     # ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\perp}} }}={1:.3f}$ ${{d}}={0:.3f}$".format(*param, names[i]))
 ax2_r.set_ylim(0.3, 0.8)
-ax2_r.set_xticklabels([])
[…]

### 2018-10-16 src/VASP_HSE/relation_2D3D.py
Change 3D scheme of Figure 1

@@ -88,7 +88,7 @@ next(reader)                    # skip line1
 for row in reader:
     if row[4] != "":
         name, proto = row[: 2]
-        print(name, proto)
+        # print(name, proto)
         L, E, ex, ey, ez, *_ = map(float, row[2:])
         if ez < ex:
             e_xy = numpy.sqrt(ex * ey)
@@ -100,9 +100,10 @@ for row in reader:
                 eps_x.append(e_xy); eps_z.append(ez)
                 alpha_x.append(ax); alpha_z.append(az)
                 L_3D, ex_3D, ez_3D = bulk_res
-                print(L_3D, ex_3D, ez_3D)
+                # print(L_3D, ex_3D, ez_3D)
                 ex_simu = 1 + 4 * pi * ax / L_3D
                 ez_simu = 1 / (1 - 4 * pi * az / L_3D)
+                print(name, proto, ex_3D, ex_simu)
                 eps_x_3D.append((ex_3D, ex_simu))
                 eps_z_3D.append((ez_3D, ez_simu))
                 Eg_HSE.append(E)
@@ -153,15 +154,16 @@ plt.style.use("science")
 def fit_func(x, a,b):
     return a+b / x
 
-cond = numpy.where(eps_x_gpaw[:, 0] < 25)
-cond2 = numpy.where(eps_x_3D[:, 0] < 25)
+upper = 25
+cond = numpy.where(eps_x_gpaw[:, 0] < upper)
+cond2 = numpy.where(eps_x_3D[:, 0] < upper)
 
 # x-direction
 # MAE=numpy.mean(numpy.abs(eps_x_3D[:, 1][eps_x_3D[:, 0] < 30] - eps_x_3D[:, 0][eps_x_3D[:, 0]<30]))
 # print(MAE)
 # MAE=numpy.mean(numpy.abs(eps_x_3D[:, 1][eps_x_3D[:, 0] < 30] - eps_x_3D[:, 0][eps_x_3D[:, 0]<30]))
 # print(MAE)
-plt.figure(figsize=(3, 2.8))
+plt.figure(figsize=(2.8, 2.5))
 res = linregress(eps_x_gpaw[:, 1][cond], eps_x_gpaw[:, 0][cond])
 print(res)
[…]

### 2018-10-16 paper.tex
Shorten section of theory

@@
 
-In this letter, We study several types of 2D materials of different
-electronic and optical properties, including transition metal
-dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
-a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
-(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
-I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
-(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)) and phosphorene (P$4$).
-For the TMDCs, we consider 2 lattice phases, namely the 2H
-(P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The elements
-involved in this study and the structures of the 2D materials are
-shown in Figure \ref{fig-2}a and \ref{fig-2}b, respectively. The
-static 2D polarizabilities are calculated from the static dielectric
-response of the selected 2D materials using density functional theory
-(DFT) with Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) in the
-Vienna Ab Initio Simulation Package (VASP) including spin-orbit
-coupling to avoid limitations on the description of band gaps and
-dielectric functions. Further details for the first principle
-calculations please refer to \textit{Methods}.
+We study several types of 2D materials of different electronic and
+optical properties, including transition metal dichalcogenides (TMDCs,
+with the formula MX\(_{\text{2}}\), where M is a metal in group 4, 6,
+10 and X=O, S, Se, Te), metal monochalcogenides (Ga$_{2}$S$_{2}$,
+Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl, I), hexagonal boron
+nitride (BN), graphene derivatives (fluorographene (C$_{2}$F$_{2}$),
+graphane (C$_{2}$H$_{2}$)) and phosphorene (P$_{4}$).  For the TMDCs,
+we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2 space
+group) and 1T (P3m1 space group).  The structures and elements of the
+2D materials are shown in Figure \ref{fig-2}a and \ref{fig-2}b,
+respectively. The static 2D polarizabilities are calculated from the
+static dielectric response of the selected 2D materials using density
+functional theory (DFT) with the Heyd-Scuseria-Ernzerhof hybrid
+functionals (HSE06) using the Vienna Ab Initio Simulation Package (VASP)
+including spin-orbit coupling to avoid limitations on the description
+of band gaps and dielectric functions. Further details for the first
+principle calculations please refer to \textit{Methods}.
 
-Figure \ref{fig-3}a shows the calculated $E_{\mathrm{g}}$ (blue dots)
-and polarizabilities (bar plots) of all the 2D materials investigated,
-covering a wide bandgap range of over 6 eV. The 2D polarizability
-$\alpha $has the unit of Farad, and is more intuitive to be expressed
-in the form $\alpha/(4 \pi \varepsilon_{0})$, which has the unit of
-[Length] (similar to the molecular polarizability, which has the unit
-of $4\pi \varepsilon_{0}\times$[Volume] \cite{Israelachvili_2011}). We
-find that $\alpha^{\parallel}$ has a general descending trend when
-$E_{\mathrm{g}}$ increases. On the other hand, no apparent trend
-between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
-details see Supplementary Figure SXX \todo{TBD}). Recently, it is
-found that the exciton binding energy $E_{\mathrm{b}}$ of 2D materials
-exhibits universal linear relation with $E_{\mathrm{g}}$
-\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. Combine
-with the fact that the $E_{\mathrm{b}}$ is roughly inversely
-proportional to $\alpha^{\parallel}$ \cite{Pulci_2014}, it is
-reasonable to guess that a general linear correlation between
-$E_{\mathrm{g}}$ and $1/\alpha^{\parallel}$ may exist for 2D
-materials. Figure \ref{fig-3}c shows
-$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
-of $E_{\mathrm{g}}$ (in eV) for the 2D materials investigated, with a
-linear regression slope of ~0.166 and $R^{2}$ of 0.84. We observe that
-materials with lower $E_{\mathrm{g}}$ (<4 eV) generally lie close to
-the regression line, while the deviation becomes greater for materials
-with $E_{\mathrm{g}}>$4 eV, which has also been observed in the
-$E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of 2D materials
-\cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also observe that
-$E_{\mathrm{g}}$ calculated on the HSE06 level shows better linear
-correlation with $1/\alpha^{\parallel}$ compared with the bandgap
-calculated using the Perdew–Burke–Ernzerhof (PBE) method (details see
-Supplementary Information SXX \todo{TBD}). This can be explained by
-the fact that the HSE06 hybrid functionals generally have a better
-prediction for the bandgap of a material than the PBE method
+Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
+(blue dots) and polarizabilities (bar plots) of all the 2D materials
+investigated, covering a wide bandgap range from far infrared to
+ultraviolet. From dimension analysis, it is more intuitive to express
+the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
+of \AA. We find that $\alpha^{\parallel}$ has a general descending
+trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
+trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
+details see Supplementary Section S2.2).  Combining recent theoretical
+findings of the universal linear relation between exciton binding
+energy $E_{\mathrm{b}}$ and bandgap $E_{\mathrm{b}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
+a general Moss-like relation between $E_{\mathrm{g}}$ and
+$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
+the bandgap-independent relation of $\alpha^{\perp}$ resembles
+molecular polarizabilities of conjugate molecules \cite{Davies_1952},
+fullerenes \cite{Sabirov_2014} and carbon nanotubes
+\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
+we show that the universal Moss-like relations exist for both
+$\alpha^{\parallel}$ and $\alpha^{\perp}$.
+
+Similar to the treatment of quantum wells (QW), the wavefunction of an
+isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
+and out-of-plane components \cite{davies_physics_1997}
+$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
+$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
+the in-plane coordinate. Using the Bloch theorem, the periodic
+$\psi^{\parallel}(\mathbf{\rho})$ can be further expressed as
+$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
+in-plane wave vector and $u(\rho)$ is periodic function in the
+xy-planeAccording to the random phase approximation (RPA)
+theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
+$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
+dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
+$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
+\begin{equation}
+  \label{eq:RPA-eps2}
+  \varepsilon_{\mathrm{SL}}
+  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
+  \sum_{\mathrm{k, c, v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
+  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
+\end{equation}
+where $e$ is the unit charge, c, v are the conduction and valence
+bands, $E$ is the eigenenergy of individual bands, and $f$ is the
+Fermi-Dirac distribution function. Taking the limit that $L\to\infty$,
+when $\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
+$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
+(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Combine this with
+Eqs. \ref{eq:alpha-para-def}, \ref{eq:alpha-perp-def} and
+\ref{eq:RPA-eps2}, and taking the difference between the properties of
+in-plane and out-of-plane polarizabilities, we derive the expressions
+for $\alpha^{\parallel}$ and $\alpha^{\perp}$ under small perturbation
+(details see Supplementary Section SXX \todo{mark!}):
+\begin{subequations}
+  \begin{eqnarray}
+  \label{eq:alpha_para_RPA}
+  & \alpha^{\parallel} &= \frac{2e^{2}}
+  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
+  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
+                         {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
+  \label{eq:alpha_perp_RPA}
+  & \alpha^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
+  \sum_{\mathrm{c, v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+  \end{eqnarray}
+\end{subequations}
+where the integral is performed within the first Brillouin Zone (BZ)
+in the reciprocal $\mathbf{k}$-plane. Although they only differ by the
+numerator inside the integral, the distinct behaviors of $u(\rho)$
+(periodic function) and $\psi(z)$ (confined to the 2D material) give
+rise to the different relations of $\alpha^{\parallel}$ and
+$\alpha^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
+Eq. \ref{eq:alpha_para_RPA} is evaluated to be
+$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
+degeneracy associated with the minimal bandgap
+\cite{Jiang_2017_Eg_Eb}. On the contrary, $\psi(z)$ is the solution to
+the Schr\"{o}dinger equation Hamiltonian
+$\mathcal{H} = -\hbar^{2}/2m^{*} \nabla^{2} + V(z)$, where $\hbar$ is
+the reduced Planck constant, $m^{*}$ is reduced mass and $V(z)$ is the
+confined Coulombic potential along the z-direction created by the
+nuclei \cite{davies_physics_1997,ihn_semiconductor_2009}. Using a
+simple particle-in-well model, we show that both the numerator and
+denominator parts of Eq. \ref{eq:alpha_perp_RPA} are independent of
+$E_{g}$ but instead modulated by the size of the potential confinement
+(details see Supplementary Section SXX\todo{note}). We further prove,
+using both quantum mechanical and fundamental electrostatic models,
+that $\alpha^{\perp}$ is actually proportional to the size of
+potential confinement (details see Supplementary Section
+SXX\todo{note}), which we may relate with the thickness $\delta$ of
+the 2D material. Now we may finally propose the 2D analog of the Moss
+relation with both in- and out-of-plane polarizations:
+\begin{subequations}
+\begin{eqnarray}
+\label{eq:2D-Moss-para}
+  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
+  \label{eq:2D-Moss-perp}
+  &\alpha^{\perp} & \propto \delta
+\end{eqnarray}
+\end{subequations}
+which form the main conclusion of this work.
+
+Figure \ref{fig-3}c
+shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a
+function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
+investigated, with a linear regression slope of ~0.166 and $R^{2}$ of
+0.84. We observe that materials with lower $E_{\mathrm{g}}$ (<4 eV)
+generally lie close to the regression line, while the deviation
+becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
+also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
+2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
+observe that $E_{\mathrm{g}}$ calculated on the HSE06 level shows
+better linear correlation with $1/\alpha^{\parallel}$ compared with
+the bandgap calculated using the Perdew–Burke–Ernzerhof (PBE) method
+(details see Supplementary Information SXX \todo{TBD}). This can be
+explained by the fact that the HSE06 hybrid functionals generally have
+a better prediction for the bandgap of a material than the PBE method
 \todo{some reference?}. It should be noted that although even more
@@
 
+\iffalse
 \subsection{Theoretical Explanations}
@@
 can greatly enhance our understanding and application of 2D materials.
+
+\fi
 

### 2018-10-18 paper.tex
Modification for figure 3 main text

@@
 
-\subsection{Universal Relations for 2D Polarizabilities}
+\subsection{2D Moss Relations}
 \label{sec:first-principles}
@@
 
-Figure \ref{fig-3}c
-shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a
-function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
-investigated, with a linear regression slope of ~0.166 and $R^{2}$ of
-0.84. We observe that materials with lower $E_{\mathrm{g}}$ (<4 eV)
-generally lie close to the regression line, while the deviation
+We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
+using the polarizabilities calculated by first principle
+calculations. Figure \ref{fig-3}b shows
+$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
+of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle dots), with a
+linear regression slope of ~0.182 and $R^{2}$ of 0.84. From
+Ref. \cite{Jiang_2017_Eg_Eb}, the slope between
+$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
+$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
+yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
+studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
+eV) generally lie close to the regression line, while the deviation
 becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
@@
 2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
-observe that $E_{\mathrm{g}}$ calculated on the HSE06 level shows
-better linear correlation with $1/\alpha^{\parallel}$ compared with
-the bandgap calculated using the Perdew–Burke–Ernzerhof (PBE) method
-(details see Supplementary Information SXX \todo{TBD}). This can be
-explained by the fact that the HSE06 hybrid functionals generally have
-a better prediction for the bandgap of a material than the PBE method
-\todo{some reference?}. It should be noted that although even more
-accurate estimation of both $\varepsilon$ and $E_{\mathrm{g}}$ can be
-achieved via many-body Green’s function method (GW) together with the
-Bethe-Salpeter equation (BSE), the convergence of such method is known
-to be highly affected by the dielectric screening of 2D materials
-\cite{Hueser_2013_2Dvs3D} (see Supplementary Section SXX
-\todo{}). Combining the accuracy, computational effort and
-convergence, the choice of the HSE06 hybrid functional may be most
-suitable to present the true relationship between $\alpha^{\parallel}$
-and $E_{\mathrm{g}}$.
+discover that the linearity between
+$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
+better when the bandgap is calculated using the HSE06 hybrid
+functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
+exchange correlations (details see Supplementary Section S2 and
+Supplementary Figure S5), which can be explained by the fact that the
+electronic structure, in particular the bandgap, is generally better
+predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
+noted that although even more accurate estimation of both
+$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
+Green’s function method (GW) together with the Bethe-Salpeter
+equation (BSE), the convergence of such method is known to be highly
+affected by the dielectric screening of 2D materials
+\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
+effort and convergence, the choice of the HSE06 hybrid functional may
+be most suitable to present the true 2D Moss-like relationship between
+$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.
 
-On the other hand, $\alpha^{\perp}$ is observed to be almost
-independent of $E_{\mathrm{g}}$. Similar behavior is also observed for
-molecular \cite{T_bik_2004} and carbon nanotube \cite{Benedict_1995}
-systems when the polarizability is in the direct perpendicular to the
-$\pi$ electron cloud. Meanwhile, while $\alpha^{\perp}$ is much
-smaller than $\alpha^{\parallel}$, its magnitude can still span over 5
-times among different materials, and generally larger for materials
-with more atoms in the z-direction (such as Ga$_{2}$S$_{2}$) than
-single-atom materials (such as BN). Starting from this observation and
-the fact that 2D polarizability has unit of
-$4\pi\epsilon\times$[Length], $\alpha^{\perp}$ may actually be related
-to a characteristic length in the z-direction of a 2D material. Figure
-\ref{fig-3}c shows $\alpha^{\perp}$ as a function of the covalent
-thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$. The covalent
-thickness is defined as the longest distance in the z-direction
-between any two atom nuclei plus their covalent radii, such that:
+We further examine the relation between $\alpha^{\perp}$ and the
+thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
+we choose the thickness of as 2D material as its ``covalent''
+thickness $\delta_{\mathrm{cov}}$, which is
+defined as the longest distance along the z-direction between any two
+atom nuclei plus their covalent radii:
 \begin{equation}
   \label{eq:cov-thick}
-  \delta_{\mathrm{2D}}^{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
+  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
   + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
@@
 where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
-is the covalent radius of atom i, as illustrated in Figure
-\ref{fig-delta}. Surprisingly, $\alpha^{\perp}$ shows excellent linear
-correlation with $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, with
-$R^{2}=0.98$, and a slope very close to $1/4\pi$. In other words, the
-quantity $\alpha^{\perp}/\varepsilon_{0}$ can be regarded as the
-long-sought-for characteristic thickness of 2D materials. In short, we
-have revealed the 2D analog of the Moss relation for both polarization
-direction: $\alpha^{\parallel}$ is inversely proportional to the
-minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
-characteristic thickness of the 2D material. The existence of such
-universal scaling relation is confirmed by examining using the
-recently-published C2DB database \cite{Haastrup_2018}, with the
-dielectric properties of over 200 2D semiconductors calculated on the
-PBE level (details see Supplementary Section SXX \todo{TBD}).  We have
-further tested the potential relation between the 2D polarizabilities
-with other physical quantities, including the effective carrier mass,
-quantum capacitance and total atomic polarizabilities while no
-apparent correlations are found (details see Supplementary Section SXX
-\todo{note}). In the next section, we will show the theoretical
-backgrounds of such universal relations of 2D polarizabilities.
+is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
+Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
+shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
+with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
+to our theoretical predictions discussed above, the perfect linear
+correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
+its strong physical meaning. Similar to the molecular polarizability
+which characterizes the volume of electron cloud of an isolated
+molecule \cite{Israelachvili_2011}, the 2D polarizability also
+characterizes the volume of the electron cloud of a 2D material per
+unit area (from its definition), and naturally represents the
+thickness of the electron cloud of the 2D material. The fact that the
+thickness of the electron cloud of a 2D material can be approximated
+by the extension of valence states in the z-direction, explains the
+close match between the linear slope in Figure \ref{fig-3}c and
+$1/4\pi$. In other wordst, the universal scaling relation for
+$\alpha^{\perp}$ indicates the quantity
+$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
+thickness of a 2D material. We propose that the well-established
+experimental protocol for measuring the electronic polarizability of
+isolated molecules \cite{Antoine_1999}, can also be extended to
+measure $\alpha^{\perp}$ of a 2D material, as a direct estimation of
+it thickness, in comparison with the optical ellipsometry techniques
+\cite{Weber_2010} widely used to estimate the thickness of 2D
+materials, which requires empirical optical model and parameter
+fitting.
+
+To rule out the possibility that our conclusion is limited by the
+number of materials used, we further validate our proposed 2D
+Moss-like relations on the recently-published C2DB database
+\cite{Haastrup_2018}, from which we extracted the dielectric
+properties of over 230 2D materials calculated at the PBE level, and
+overlap them with our results in Figure \ref{fig-3}b and \ref{fig3-c}
+(further details see Supplementary Section S3). Althought the
+dielectric properties may be overestimated at PBE level due to
+underestimation of the bandgap compared with the more accurate HSE06
+functionals, apparent linear trends can be observed for both
+$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
+very close to the HSE06 results. Therefore, the proposed universal 2D
+Moss-like relations are confirmed.  We have also tested the potential
+relation between the 2D polarizabilities with other physical
+quantities, including the effective carrier mass, quantum capacitance
+and total atomic polarizabilities, while no apparent correlations are
+found (details see Supplementary Section S3).
+
+In short, we have revealed the 2D analog of the Moss relation for both
+polarization direction by using the 2D polarizability: $\alpha^{\parallel}$ is inversely proportional
+to the minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
+characteristic thickness of the 2D material.
 

### 2018-10-18 src/VASP_HSE/relation_2D3D.py

@@ -103,6 +103,7 @@ for row in reader:
                 # print(L_3D, ex_3D, ez_3D)
                 ex_simu = 1 + 4 * pi * ax / L_3D
                 ez_simu = 1 / (1 - 4 * pi * az / L_3D)
+                # ez_simu = 4 * pi * az / L_3D
                 print(name, proto, ex_3D, ex_simu)
                 eps_x_3D.append((ex_3D, ex_simu))
                 eps_z_3D.append((ez_3D, ez_simu))
@@ -119,6 +120,8 @@ Eg_HSE = numpy.array(Eg_HSE)
 
 eps_x_gpaw = []
 eps_z_gpaw = []
+alpha_z_gpaw = []
+L_gpaw = []
 for db_id in range(1, db.count() + 1):  # db index starts with 1
     mol = db.get(db_id)
     # if any(hasattr(mol, key) is False for key in ["alphax", "alphay", "alphaz",
@@ -133,12 +136,18 @@ for db_id in range(1, db.count() + 1):  # db index starts with 1
         L, ex, ez = get_bulk(None, None, db_id, method="gpaw")
         ex_simu = 1 + 4 * pi * ax / L
         ez_simu = 1 / (1 - 4 * pi * az / L)
+        # ez_simu = 4 * pi * az / L
         eps_x_gpaw.append((ex, ex_simu))
         eps_z_gpaw.append((ez, ez_simu))
+        alpha_z_gpaw.append(az)
+        L_gpaw.append(L)
     except Exception:
         continue
 eps_x_gpaw = numpy.array(eps_x_gpaw)
 eps_z_gpaw = numpy.array(eps_z_gpaw)
+alpha_z_gpaw = numpy.array(alpha_z_gpaw)
+L_gpaw = numpy.array(L_gpaw)
+print(eps_x_3D.shape)
 print(eps_x_gpaw.shape, eps_z_gpaw.shape)
 
 # cond = numpy.where(Eg_HSE > 0.6)
@@ -191,7 +200,7 @@ plt.savefig(os.path.join(img_path, "eps_3D_xx.svg"))
 
 # z-direction
 upper = 10
[…]

### 2018-10-19 paper.tex
Change contents for the theoretical part

@@
 $\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
-thickness of a 2D material. We propose that the well-established
-experimental protocol for measuring the electronic polarizability of
-isolated molecules \cite{Antoine_1999}, can also be extended to
-measure $\alpha^{\perp}$ of a 2D material, as a direct estimation of
-it thickness, in comparison with the optical ellipsometry techniques
-\cite{Weber_2010} widely used to estimate the thickness of 2D
-materials, which requires empirical optical model and parameter
-fitting.
+thickness of a 2D material. We propose that the experimental
+measurment of the electronic polarizability
+\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
+extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
+estimation of it thickness, in comparison with the optical
+ellipsometry techniques \cite{Weber_2010} widely used to estimate the
+thickness of 2D materials, which requires empirical optical model and
+parameter fitting.
 
@@
 properties of over 230 2D materials calculated at the PBE level, and
-overlap them with our results in Figure \ref{fig-3}b and \ref{fig3-c}
+overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
 (further details see Supplementary Section S3). Althought the
@@
 In short, we have revealed the 2D analog of the Moss relation for both
-polarization direction by using the 2D polarizability: $\alpha^{\parallel}$ is inversely proportional
-to the minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
-characteristic thickness of the 2D material.
-
-\iffalse
-\subsection{Theoretical Explanations}
-\label{sec:theory}
-
-Similar to the treatment of quantum wells (QW), the wavefunction of an
-isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
-and out-of-plane components \cite{davies_physics_1997}
-$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
-$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
-the in-plane coordinate. According to the Bloch theorem, the periodic
-in-plane wavefunction can be further expressed as
-$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
-in-plane wave vector and $u(\rho)$ is periodic function in the
-xy-plane. According to the random phase approximation theory
-\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ can be calculated by
-taking the $\mathbf{q} \to 0$ and $\omega \to 0$ limits of the
-non-interacting dielectric function $\varepsilon(\mathbf{q}, \omega)$,
-where $\mathbf{q}$ is the momentum transfer and $\omega$ is the
-frequency:
-\begin{equation}
-  \label{eq:RPA-eps2}
-  \varepsilon_{\mathrm{SL}}
-  = \varepsilon_{\mathrm{SL}}(\mathbf{q} \to 0)
-  = 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
-  \sum_{\mathrm{k, c, v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
-  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}}))\right]
-\end{equation}
-where $e$ is the unit charge, c, v are the conduction and valence
-bands, $f$ is the Fermi-Dirac distribution, $E$ is the eigenenergy of
-individual bands, and $f$ is the Fermi-Dirac distribution. Taking the
-limit that $L\to\infty$, when
-$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
-$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
-(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore $\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the same equation:
-\begin{equation}
-  \label{eq:alpha-RPA}
-  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-where the direction is determined by $\mathbf{q}$. For
-$\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent of
-$z$. Further combining with the Bloch wave representation and the k-p
-theory\cite{Jiang_2017_Eg_Eb}, we have:
-\begin{equation}
-  \label{eq:alpha_para_RPA}
-  \alpha^{\parallel} = \frac{2e^{2}}
-  {(2 \pi)^{2}} \int d^{2}\mathbf{k}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-the final expression for Eq. \ref{eq:alpha_para_RPA} is shown to be
-$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$ by
-Ref. \citenum{Jiang_2017_Eg_Eb}, where $N$ is degeneracy of bands
-associated with the minimal bandgap. This explains the linear
-correlation we observe between $1/\alpha^{\parallel}$ and
-$E_{\mathrm{g}}$. When $\alpha^{\parallel}$ is measured in
-$(4 \pi \varepsilon_{0})\cdot \mathrm{\AA}$ and $E_{\mathrm{g}}$
-measured in eV, the linear regression slope in Figure \ref{fig-3}b is
-predicted to be
-$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$. The
-observed value of $\sim$0.166 corresponds to $N$ between 2 and 3,
-which is reasonable for the 2D materials studied.
-
-On the other hand, the $E_{\mathrm{g}}$ independence and correlation
-with the covalent thickness of $\alpha^{\perp}$, can also be explained
-using the same quantum framework. Generally speaking, $\psi^{\perp}$
-follows the Hamiltonian in z-direction, such that:
-\begin{equation}
-  \label{eq:Hamil-z}
-  \left[-\frac{\hbar^{2}}{2 m^{\perp}}\nabla^{2} + V(z)\right] \psi^{\perp}(z) = E \psi^{\perp}
-\end{equation}
-where $\hbar$ is the reduced Planck constant and $m^{\perp}$ is the
-effective mass in the perpendicular direction. $V(z)$ is the potential
-created by the 2D material, and confined within a region of length
-$\delta$. For simplicity we use plane wave to model the in-plane
-wavefunction, that
-$\psi^{\parallel}(\mathbf{\rho}) \propto
-e^{i\mathbf{k\rho}}$. Inserting into Eq. \ref{eq:alpha-RPA} and
-perform the Taylor expansion of $e^{-i\mathbf{qr}}$, we can eliminate
-the contribution from the in-plane
-wavefunctions\cite{davies_physics_1997} and get:
-\begin{equation}
-  \label{eq:alpha_perp_RPA}
-  \alpha^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
-  \sum_{\mathrm{c, v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k}>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-where the integration over $\mathbf{k}$ is done in the $k_{x}-k_{y}$
-part of the Brillouin Zone. In a confined 1D system, the matrix
-element
-$<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>$ is
-usually proportional to the length of confinement $\delta$, while the
-eigenenergy difference $E_{\mathrm{c}}-E_{\mathrm{v}}$ is correlated
-with $\delta^{-2}$, while independent of
-$\mathbf{k}$\cite{Benedict_1995}. Therefore the integrated
-$\alpha^{\perp}$ is also independent of the bandgap $E_{\mathrm{g}}$,
-which would instead greatly influence $\alpha^{\parallel}$. Using a
-simplified particle-in-box model, we evaluated the integration of
-Eq. \ref{eq:alpha_perp_RPA} and show that $\alpha^{\parallel}$ is
-related with the geometric parameter $\delta$ (details see Supplementary Section SXX \todo{add note}), the confinement of
-electrons in the z-direction, which nicely explains our finding of
-correlation between $\alpha^{\perp}$ and
-$\delta^{\mathrm{cov}}_{\mathrm{2D}}$.
-
-Based on unit analysis of the 2D polarizability, its in- and
-out-of-plane components can be described as the characteristic
-lengthes in both directions. In fact, such characteristic length is
-just the dielectric screening length. The potential from a point
-charge inside the 2D material generates an in-plane potential
-$V(\rho)$ as function of distance $\rho$ from the point charge, in the
-Keldysh form \cite{Keldysh_1979_eps_multi,Pulci_2014}:
-\begin{equation}
-  \label{eq:Keldysh}
-  V(\rho) = \frac{e}{4 \alpha^{\parallel}}
-  \left[H_{0}(\frac{2\varepsilon_{0}\rho}{\alpha^{\parallel}})
-    - Y_{0}(2 \varepsilon_{0}\frac{\rho}{\alpha^{\parallel}})\right]
-\end{equation}
-The length $r^{\parallel}_{0} = \alpha^{\parallel}/(2\varepsilon_{0})$
-determines the degree of in-plane dielectric screening: the charges
-feel strong screening when $\rho/r^{\parallel}_{0} \ll 1$ while the
-screening for $\rho/r^{\parallel}_{0} \gg 1$ reduces to the case of
-vacuum. In other words, the quantity
-$\alpha^{\parallel}/(2\varepsilon_{0})$ characterizes the radius of
-localized in-plane screened potential. Combining with the result that
-the thickness of 2D material is characterized by
-$\alpha^{\perp}/\varepsilon_{0}$, we have drawn a generalized picture
-of the dielectric nature of 2D materials via the 2D polarizability:
-the dielectric screening of a point charge sitting in the middle of a
-2D material can be viewed as an ellipsoid with the length of
-principle axes to be $\alpha^{\parallel}/(2 \varepsilon_{0})$ and
-$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively. Beyond the
-boundary the ellipsoid the dielectric screening gradually reduced to
-the vacuum situation. Note such radius is not essentially the 2D
-exciton radius, which is still related with the effective mass
-\cite{Chernikov_2014_EB_MoS2_2D3D}. Nevertheless, with the universal
-relation between $\alpha^{\parallel}-E_{\mathrm{g}}$ and
-$\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ for 2D materials,
-we are able to quantitatively predict and design the dielectric nature
-of a new 2D material by engineering the bandgap and geometry, which
-can greatly enhance our understanding and application of 2D materials.
-
-\fi
+polarization direction by using the 2D polarizability:
+$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
+$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
+thickness of the 2D material. Although their apparent forms in
+Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
+will show the 2D Moss-like relations stem from the same origin. In
+merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
+both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
+$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
+characteristic lengthes in- and out-of-plane, respectively. The
+in-plane screened electrostatic potential $V(r)$ from a point charge
+in an 2D plane, as a function of distance $r$,
+\cite{Keldysh_1979_eps_multi,Pulci_2014}:
+$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
+\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
+      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
+      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$, where $H_{0}$
+is the Struve function and $Y_{0}$ is the Bessel function of second
+kind, is assciated with the in-plane screening radius
+$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
+$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
+potential in vacuum. Combining with the result that the thickness of
+2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
+have drawn a generalized picture of the dielectric nature of 2D
+materials via the 2D polarizability: the dielectric screening of a
+point charge sitting in the middle of a 2D material can be viewed as
+an ellipsoid with the length of principle axes to be
+$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
+$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
+polarizability ellipsoid picture of molecules used in spectroscopy
+\cite{Banwell_1994}. The in-plane screening length is generally larger
+for a smaller bandgap semiconductor, which qualitatively explains the
+inverse propotional relation between $\alpha^{\parallel}$ and
+$E_{\mathrm{g}}$, a 2D version of the Moss-relation.
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
-\caption{\label{fig-delta} Scheme for the determination of the
-  covalent thickness of one-atom-thick (left) and few-atom-thick
-  (right) 2D materials.}
-\end{figure}
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
+% \caption{\label{fig-delta} Scheme for the determination of the
+  % covalent thickness of one-atom-thick (left) and few-atom-thick
+  % (right) 2D materials.}
+% \end{figure}
 

### 2018-10-19 src/distance/fit_func_PRB.py
Change manuscript figures

@@ -38,7 +38,7 @@ for i, item in enumerate(g):
         # data = data[1: , :]
         L = data[:, 0]
         eps_SL = data[:, 1]
-        fig = plt.figure(figsize=(2.5, 2.5))
+        fig = plt.figure(figsize=(2, 2))
         ax = fig.add_subplot(111)
         # ax2 = ax.twinx()
         ax.plot(L, eps_SL, "o")
@@ -53,7 +53,7 @@ for i, item in enumerate(g):
             )
             LL = numpy.linspace(10, 70)
             ax.plot(LL, fit_para(LL, *param), "--")
-            ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{d}}={0:.3f}\\ \\AA$".format(*param, tags[names[i]]))
+            ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\parallel}} }}={1:.3f}$ ${{\\delta}}={0:.3f}\\ \\AA$".format(*param, tags[names[i]]))
             ax.set_ylabel("$\\epsilon_{\\parallel}$")
             # ax.set_title("{} parallel".format(names[i]))
             ax.set_ylabel("$\\epsilon^{\\parallel}_{\mathrm{SL}}$")
@@ -69,7 +69,7 @@ for i, item in enumerate(g):
             LL = numpy.linspace(10, 70)
             ax.plot(LL, fit_vert(LL, *param), "--")
             ax.set_ylabel("$\\epsilon^{\\perp}_{\mathrm{SL}}$")
-            ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\perp}} }}={1:.3f}$ ${{d}}={0:.3f}\\ \\AA$".format(*param, tags[names[i]]))
+            ax.set_title("{2}, ${{\\epsilon_{{2D}}^{{\\perp}} }}={1:.3f}$ ${{\\delta}}={0:.3f}\\ \\AA$".format(*param, tags[names[i]]))
             # ax.set_title("{} perp".format(names[i]))
             # ax.set_ylim(0, 1)
             fig.savefig(os.path.join(item[0], "{}-fit-perp-SL.svg".format(names[i])))

### 2018-10-19 src/distance/model_eps.py

@@ -25,7 +25,7 @@ def plot_eps_perp(ax, alpha_0, dev, trans=0.7):
     return
 
 plt.style.use("science")
-fig = plt.figure(figsize=(4, 2))
+fig = plt.figure(figsize=(5, 1.6))
 ax = fig.add_subplot(121)
 ax2 = fig.add_subplot(122)
 L = numpy.linspace(10, 60, 100)

### 2018-10-19 paper.tex
change slightly manuscript

@@
 $\alpha^{\parallel}$ and $\alpha^{\perp}$, respectively:
+\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\end{subequations}
 The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
@@
 $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}b
-and \ref{fig-1}c insets). These findings indicate that the 2D
-polarizability, instead of the dielectric constant, is the true
-descriptor of the dielectric properties of 2D materials.
+$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}d
+and \ref{fig-1}e). These findings indicate that the 2D polarizability,
+instead of the dielectric constant, is the true descriptor of the
+dielectric properties of 2D materials.
 
@@
 $E_{g}$ but instead modulated by the size of the potential confinement
-(details see Supplementary Section SXX\todo{note}). We further prove,
+(details see Supplementary Section S4). We further prove,
 using both quantum mechanical and fundamental electrostatic models,
@@
 potential confinement (details see Supplementary Section
-SXX\todo{note}), which we may relate with the thickness $\delta$ of
+S4), which we may relate with the thickness $\delta$ of
 the 2D material. Now we may finally propose the 2D analog of the Moss
@@
 
-Apart from the universal relations we propose for the 2D materials, it
-is also of high theoretical interest to model the transition of
-dielectric properties from the 2D world to the 3D world. In other
-words, can we describe the dielectric constants of a bulk layered
-material from the polarizabilities of the monolayer (see Figure
-\ref{fig-4}a)? The static dielectric constants
-$\varepsilon_{\mathrm{bulk}}$ for a bulk material with equilibrium
-interlayer distance $L_{\mathrm{bulk}}$, can be expressed using the
-polarizabilities of the individual layers in the bulk material
-$\alpha_{\mathrm{bulk}}$:
+Apart from the universal Moss-like relations we propose for the
+dielectric nature of 2D materials, it is also of high theoretical
+interest to model the 2D-3D transition of dielectric properties. In
+other words, can we describe the dielectric constants
+$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
+$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
+$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
+\ref{fig-4}a)? First, we see that the 2D polarizabilities for
+individual layers in the bulk materials
+$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
+$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
+Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
+becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
+dielectric constants of the bulk material are then expressed as:
+\begin{subequations}
 \begin{eqnarray}
   \label{eq:3D-para}
-  &\varepsilon^{\parallel}_{\mathrm{bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{bulk}}}}\\
+  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
   \label{eq:3D-perp}
-  &\varepsilon^{\perp}_{\mathrm{bulk}} &= \left(1 - \frac{\alpha_{\mathrm{bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{bulk}}}\right)^{-1}
+  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
 \end{eqnarray}
-Note that $\alpha_{\mathrm{bulk}}$ may not essentially be the same as
-$\alpha$ of isolated layer. Nevertheless we will first see how good
-the predictions can be made when assuming
-$\alpha_{\mathrm{bulk}}=\alpha$. Figure \ref{fig-4}b and \ref{fig-4}c
-show the comparison between the
+\end{subequations}
+Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
+$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
+$\alpha$ of isolated layer, but still quite close as seen in Figure
+\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
+we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
+$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
+$\alpha_{\mathrm{bulk}}=\alpha$. We compare
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
@@
 calculations compared with the values predicted using Eqs
-\ref{eq:3D-para} and \ref{eq:3D-perp}, respectively. We observe that
-such approach provides good estimation of
-$\varepsilon_{\mathrm{bulk}}^{\parallel}$, with the mean average error
-(MAE) of 1.35. On the other hand, we observe the predicted values of
+\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
+and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
+levels which give almost identical trends, indicating the generality
+of such approach. Note although the stacking order is not considered
+in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
+influence of stacking is minor (see Supplementary Figure SXX
+\todo{Wait for Declan's data}). We observe that the majority of
+predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
+the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
+0.97, indicating that such method indeed captures the transition from
+$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
+the other hand, we observe the predicted values of
 $\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
 values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
-when $E_{\mathrm{g}}$ reduces. Such results means that the
-$\alpha^{\parallel}$ in a bulk layered material can generally be
-estimated from its 2D counterpart, while $\alpha^{\perp}$ differs from
-the values of monolayer, as also observed in other studies
-\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. Two factors contribute
-to the discrepancy: (i) the overlap between induced dipoles is larger
-perpendicular to the plane than parallel to the plane, and (ii) the
-interlayer coupling is larger for 2D materials with smaller
-bandgap. If we have an accuracy approach to model
-$\alpha_{\mathrm{bulk}}$ as function of $\alpha$ and the degree of
-interlayer coupling $\eta$ \cite{Tkatchenko_2012}, the dielectric
-transition from 2D to 3D would be smoothly described.
+when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
+$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
+$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
+its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
+to interlayout coupling and overlap between induced dipoles, as also
+observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
+\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
+describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
+$\alpha^{\perp}$ and the degree of interlayer coupling $\eta$
+\cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
+be smoothly described.
 
-Next we will show how the relation between dielectric properties
-transforms from 2D to 3D. Extend the approach for modeling
-$\alpha^{\parallel}$ in Eq. \ref{eq:alpha_perp_RPA} to the bulk
-material, and use the Bloch presentation for wavefunctions in all
-dimensions, we get:
+As described in the previous section, the 2D Moss-like relation
+between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
+relation between $\varepsilon$ and $E_{g}$, with a different power
+law. Such difference in the power law can indeed be explained by
+modern theory of dielectric properties.  Extend the approach
+Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
+presentation for wavefunctions in all dimensions, we derive (detailed
+procedure see Supplementary Section S4):
 \begin{equation}
   \label{eq:alpha-Eg-3D}
-  \varepsilon_{\mathrm{bulk}} = 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
+  \begin{aligned}[t]
+  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
   \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
+  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
+\end{aligned}
 \end{equation}
-Using a similar treatment for
-$|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}$ as in
-Ref. \citenum{Jiang_2017_Eg_Eb} we end up with the relation
-$\alpha_{\mathrm{bulk}} \propto 1/\sqrt{E_{\mathrm{g}}}$ (details see
-Supplementary Section SXX \todo{note}), which recovers the Moss
-relation under rigorous treatment \cite{Finkenrath_1988}. Therefore,
-the universal $\alpha^{\perp}-E_{\mathrm{g}}$ relation is indeed the
-Moss relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
-independence of effective mass is dominated by the confinement
-perpendicular to the 2D plane.
+which recovers the 3D Moss relation. Therefore, the universal
+$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss relation
+in 2D world, while the power law of $E_{\mathrm{g}}$ and independence
+of effective mass is a result of the confinement perpendicular to the
+2D plane.
 
+\todo{First leave this part untouched}
 Finally, we would like to comment on the generality of the dielectric
@@
 
-To sum up, using first principles calculation for over 50 kinds of 2D
-materials, we reveal the universal relation between the dielectric
-nature of 2D materials and other physical quantities via the 2D
-polarizability. The in-plane polarizability of a 2D material is found
-to be inversely proportional to the minimal bandgap, while the
-out-of-plane polarizability is the characteristic thickness of the 2D
-material. Such universal scaling relation is explained by a quantum
-mechanical model combining the polarizability in both directions. Our
-universal scaling relation bridges the gap between 2D and 3D
-dielectric properties with good accuracy of prediction.  Our numerical
-findings and theoretical analysis pave the way to understand and
-engineer the electronic and dielectric properties of a large library
-of 2D materials for different technological applications in an
+To sum up, using first principles calculation for a large set of 2D
+materials, we reveal the universal relation of the dielectric nature
+of 2D materials using the 2D polarizability, as an analog to the Moss
+relation for bulk semiconductors. The in-plane polarizability of a 2D
+material is found to be inversely proportional to the minimal bandgap,
+while the out-of-plane polarizability is the characteristic thickness
+of the 2D material. Such universal scaling relation is explained by a
+quantum mechanical model combining the polarizability in both
+directions. Our universal scaling relation bridges the gap between 2D
+and 3D dielectric properties with good accuracy of prediction.  Our
+numerical findings and theoretical analysis pave the way to understand
+and engineer the electronic and dielectric properties of a large
+library of 2D materials for different technological applications in an
 unified and unprecedented way.
@@
 18$\times$18$\times$1 k-grid and electric field strength of 0.001
-eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
-length of corresponding monolayer material with the interlayer van der
-Waals (vdW) interactions calculated by non-local vdW correlation
+eV/\AA. The materials in C2DB database for comparison were choses with
+the GW bandgap larger than 0.05 eV. Bulk layered materials were
+constructed by relaxing the c-axis length of corresponding monolayer
+material with the interlayer van der Waals (vdW) interactions
+calculated by non-local vdW correlation
 functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
-layered materials were calculated at PBE level with
-18$\times$18$\times$6 k-grid with same parameter as for monolayer.
+layered materials using VASP were calculated at HSE06 level with
+18$\times$18$\times$6 k-grid with same parameter as for monolayer,
+while the dielectric properties of bulk counterparts of the C2DB
+database are calculated at PBE level with a k-point density of 10
+\AA$^{-1}$.
 
@@
 \centering
-\includegraphics[width=0.90\linewidth]{img/fig1.pdf}
-\caption{\label{fig-1} The macroscopic dielectric constant and
-  microscopic polarizability of a 2D material. \textbf{a}. Left: 2D
-  material in a superlattice with length $L$ in the z-direction. The
-  periodic images of the 2D material are shown below and above the
-  superlattice. Right: simplied presentation of the dielectric
-  constants $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-  $\varepsilon_{\mathrm{SL}}^{\perp}$ of the superlattice as a
-  combined effect of the 2D polarizabilities $\alpha^{\parallel}$ and
-  $\alpha^{\perp}$ and the vacuum. \textbf{b}. Change of spatial
-  charge density $\Delta \rho(z)$ in the z-direction for a layer of
-  2H-MoS$_{2}$ under external eletric field of 0.01 V/\AA{}. The green
-  and red regions represent negative and positive induced charges,
-  respectively. \textbf{c}. $\varepsilon^{\parallel}_{\mathrm{SL}}$
-  (left) and $\alpha_{\mathrm{SL}}^{\parallel}$ (right) as functions
-  of $L$ for a 2H-MoS$_{2}$
-  layer. \textbf{d}. $\varepsilon^{\perp}_{\mathrm{SL}}$ (left) and
-  $\alpha_{\mathrm{SL}}^{\perp}$ (right) as functions of $L$ for a
-  2H-MoS$_{2}$ layer. The polarizabilities in \textbf{c} and
-  \textbf{d} are constant when $L>$15 \AA{}.}
+\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
+\caption{\label{fig-1} \textbf{2D polarizability as the true
+    descriptor of the dielectric nature of 2D materials.}
+  \textbf{a}. 3D illustration of the spatial distribution of the
+  charge density change $\Delta \rho(z)$ along the z-direction for
+  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
+  eletric field of 0.01 V/\AA{}.  The green and red regions represent
+  negative and positive induced charges, respectively. The macroscopic
+  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
+  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
+  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
+  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
+  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
+  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
+  constant when $L>$15 \AA{}, compared with the $L$-dependence of
+  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
+  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
+  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
+  \ref{eq:alpha-perp-def}, respectively.}
 \end{figure}
@@
 \includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
-\caption{\label{fig-2} The 2D materials investigated. \textbf{a}. The
-  elements that involved in this study. \textbf{b} 3D structures of
-  the 2D materials investigated in this study.}
+\caption{\label{fig-2} The elements and 3D structures of the 2D
+  materials investigated in this study.}
 \end{figure}
@@
 \includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
-\caption{\label{fig-3} The universal scaling relation of the
-  dielectric nature of 2D materials. \textbf{a}. $\alpha^{\parallel}$,
-  $\alpha^{\perp}$ (bar plots) and $E_{\mathrm{g}}$ (blue dots) for
-  all the 2D materials studied.  $\alpha^{\parallel}$ is observed to
-  descend with increasing $E_{\mathrm{g}}$, while no apparent relation
-  between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
+\caption{\label{fig-3} \textbf{The universal scaling relation of the
+    dielectric nature of 2D
+    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
+  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
+  materials studied.  $\alpha^{\parallel}$ is observed to descend with
+  increasing $E_{\mathrm{g}}$, while no apparent relation between
+  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
   observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
-  (in \AA{}) as a function of $E_{\mathrm{g}}$, showing a linear
+  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
   correlation between each other. The energy range of visible light is
@@
   background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
-  \AA{}) as a function of the covalent thickness, showing a perfect
-  linear relation with slope very close to $1/4\pi$. The materials in
-  \textbf{b} and \textbf{c} are grouped by their prototyes, including
-  1T-TMDCs and cadmium halide (1T-MX$_{2}$), 2H-TMDCs (2H-MX$_{2}$),
-  boron nitride (BN), phosphorene (P), monochalcogenides (GaS) and
-  graphene derivatives (CH).}
+  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
+  schematically shown in the inset), showing a perfect linear relation
+  with slope very close to $1/4\pi$. The universal scaling relation is
+  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
+  and \textbf{c}.}
 \end{figure}
@@
 \includegraphics[width=\linewidth]{./img/fig4.pdf}
-\caption{\label{fig-4} Transition of dielectric properties from 2D to
-  3D systems. \textbf{a}. Scheme for the 2D-3D transition. $\alpha$ in
-  the 2D material is essentially equivalent to $\varepsilon$ in its
-  bulk counterpart. \textbf{b}
+\caption{\label{fig-4} \textbf{Transition of dielectric properties
+    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
+  transition. $\alpha$ in the 2D material is essentially equivalent to
+  $\varepsilon$ in its bulk counterpart. \textbf{b}
   $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
@@
   calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
-  coupling. }
+  coupling. The comparisons in \textbf{b} and \textbf{c} are made
+  based on both HSE06 (circles) and PBE (squares) levels.}
 \end{figure}

### 2018-10-20 SI.tex
Add SI figures for raw data
Add figures for SI

@@
 \documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
+\usepackage{times}
 \usepackage{amsmath}
@@
 \usepackage[T1]{fontenc}
-\usepackage{longtable}
+\usepackage{ltablex}
 \usepackage{footnote}
@@
 From literatures, it is often desired to extract the ``dielectric
-constant'' of a 2D material from the 3D macroscopic dielectric constant
-\cite{Matthes_2016,Laturia_2018}. As discussed in the main text and
-other studies\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D},
-the definition of the 2D ``dielectric constant'' (in particular, its
+constant'' of a 2D material from the 3D macroscopic dielectric
+constant of the superlattice, where the layers are periodic along of
+x,y directions but separated by a vacuum layer between its images
+\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
+definition of the 2D ``dielectric constant'' (in particular, its
 in-plane components) is questionable, due to the locality of
-electrostatic screening of the 2D materials. Here we show that, in
-addition to the ambiguous definition of the 2D dielectric constant,
-such approach requires the precise determination of the 2D layer
-thickness $\delta_{\mathrm{2D}}$, which makes it impractical.
+electrostatic screening of the 2D materials
+\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
+that, in addition to the ambiguous definition of the 2D dielectric
+constant, such approach requires the precise determination of the 2D
+layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.
 
 In brief, the hypothetical 2D dielectric constant
-$\varepsilon_{\mathrm{2D}}$ comes from the planar limit of the
+$\varepsilon$ comes from the planar limit of the
 Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
@@
   \label{eq:MG-effect-2}
-  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f (\varepsilon_{\mathrm{2D}}^{\perp})^{-1} + (1-f)
+  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
 \end{eqnarray}
-where $f=\delta_{\mathrm{2D}}/L$ is the volume fraction of the 2D
+where $f=\delta/L$ is the volume fraction of the 2D
 material in the superlattice. The major issue when using such rescale
-relations comes from the determination of $\delta_{\mathrm{2D}}$,
-which is not well defined for a 2D material. To eliminate the modeling
-error caused by the \texttt{a priori} parameter selection of
-$\delta_{\mathrm{2D}}$, we perform the calculation of
-$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$, and use
-least-square fitting to extract both $\varepsilon_{\mathrm{2D}}$ and
-$\delta_{\mathrm{2D}}$, as shown in Figure \ref{fig:rescale-prb}.
+relations comes from the determination of $\delta_{\mathrm{2D}}$. To
+eliminate the modeling error caused by the \textit{a priori} parameter
+selection of $\delta$, we perform the calculation of
+$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
+and use least-square fitting to extract both
+$\varepsilon$ and $\delta$, as shown in
+Figure \ref{fig:rescale-prb}.
 
@@
     WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
-    $\delta_{\mathrm{2D}}$ are shown in each subfigure.}
+    $\delta$ are shown in each subfigure.}
   \label{fig:rescale-prb}
@@
 dependency between the 2D polarizability $\alpha$ and the superlattice
-length $L$, which is shown in Figure \ref{fig:eps-L-all} \todo{Which
-  method?}.  In all cases, we observe that the calculated
+length $L$, which is shown in Figure \ref{fig:eps-L-all}.  In all cases, we observe that the calculated
 polarizability converges when $L>$15 \AA{}, in good agreement with our
@@
 polarizability, however to reduce the computational cost, especially
-at the HSE level, we typically choose a superlattice size no larger
+at the HSE06 level, we typically choose a superlattice size no larger
 than 35 \AA{}.
@@
     axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
-    (bottom right axis) of various group 6 TMDCs. In all cases, the
-    polarizability  converges when $L>$15 \AA{}}
+    (bottom right axis) of various group 6 TMDCs corresponding to
+    Figure 1 in main text. In all cases, the polarizability converges
+    when $L>$15 \AA{}}
   \label{fig:eps-L-all}
@@
 
-\subsection{Depdence of bandgap}
+\subsection{Dependence of bandgap}
 \label{sec:pol-2D-2}
@@
 difference choices of \textit{ab initio} bandgaps. It is widely
-accepted that the PBE method, while gives quantitative predictions of
-the dielectric response of 2D and layered materials, tends to
-underestimate the bangap
-\cite{Kumar_2016_PRB,Kumar_2016_jpcc}. \todo{complete the discussion
-  for HSE?}  Indeed, changing the choice of $E_{\mathrm{g}}$ yields
-different regression relation with $1/\alpha^{\parallel}$, as shown in
-Figure \ref{fig:alpha-Eg-diff}. We see that due to the underestimation
-of PBE bandgap, the slope of linear regression is larger than that
-from HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
+accepted that the PBE exchange correlation, tends to underestimate the
+bangap \cite{Heyd_2005,Kumar_2016_PRB,Kumar_2016_jpcc}.  Indeed,
+changing the choice of $E_{\mathrm{g}}$ yields different regression
+relation with $1/\alpha^{\parallel}$, as shown in Figure
+\ref{fig:alpha-Eg-diff}. We see that due to the underestimation of PBE
+bandgap, the slope of linear regression is larger than that from
+HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
 relation is better presented by using the minimal HSE bandga than the
@@
     $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
-    $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ on the C2DB
-    2D material database. }
+    $\alpha^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
+    database, corresponding to Figure 3b and 3c in main text.}
   \label{fig:gpaw-alpha-relation}
@@
 about 50 types of materials. It is desirable to validate our proposed
-relations on a even larger scale database. \todo{Add comments for the
-  C2DB database}. We select 210 semiconducting 2D materials from the
-C2DB database with a HSE bandgap larger than 0.5 eV and extracted the
-2D polarizabilities calculated on the PBE level. The propsed linear
-relations between $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
-and $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ are also
-valid, as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent
-linear correlation is observed in both cases, with the $R^{2}$
-coefficient larger than 0.9, indicating the existence of the universal
-description of 2D dielectric nature through the proposed relations
-with the 2D polarizabilities. We note that the slope of linear
-regression is slightly different from the our proposed relation from
-the dielectric response on HSE level, due to the fact that the
-macroscopic dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated
-on the PBE level is about 5\% lower. Despite the minor deviation of
-the slope of linear regression, the analysis on the C2DB database
-supports our understanding of the universal dielectric nature of 2D
-materials.
+relations on a even larger scale database. We select over 230
+semiconducting 2D materials from the C2DB database with a GW bandgap
+larger than 0.05 eV and extracted the 2D polarizabilities calculated
+on the PBE level. The propsed linear relations between
+$1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
+$\alpha^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
+as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
+correlation is observed in both cases, with the $R^{2}$ coefficient
+larger than 0.9, indicating the existence of the universal description
+of 2D dielectric nature through the proposed relations with the 2D
+polarizabilities. We note that the slope of linear regression is
+slightly different from the our proposed relation from the dielectric
+response on HSE06 level, due to the fact that the macroscopic
+dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated on the PBE
+level is about slightly difference. Despite the minor deviation of the
+slope of linear regression, the analysis on the C2DB database supports
+our understanding of the universal dielectric nature of 2D materials.
 
@@
 C2DB database as a function of minimal and direct bandgap calculated
-on PBE, HSE and GW levels.\todo{to be more specific?} We observe,
+on PBE, HSE06 and GW levels. We observe,
 although the regression $R^{2}$ coefficient in all cases are around
@@
 compared with the bandgap and covalent thickness proposed in the main
-text. \todo{add some more explanation}
+text.
 
@@
 
-\subsection{Detailed derivations from Eq. 10}
+\subsection{Detailed derivations for Eq. 5a and 5b}
 \label{sec:theory-1}
 
-Here we will first show how Eq. 10 in the main text is
-derived. Treating the in-plane wavefunctions as plane wave with form
-$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
-element of
+Here we will first show how Eq. 5a and 5b in the main text are
+derived. Taking the limit that $L\to\infty$, when
+$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
+$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
+(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
+$\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the
+same equation:
+\begin{equation}
+  \label{eq:alpha-RPA}
+  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+where the direction is determined by $\mathbf{q}$.
+
+For the in-plane component, $\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$
+is independent of $z$, therefore the integral in
+$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
+becomes the independent of $\psi^{\perp}$, due to the
+orthogonality. Present the summation of k-space into integral, and further
+combining with the Bloch wave representation and the k-p
+theory\cite{Jiang_2017_Eg_Eb}, we arrive at Eq. 5a.
+
+For Eq. 5b, treating the in-plane wavefunctions as plane wave with
+form $\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the
+matrix element of
 $<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
@@
 \end{equation}
-plug this into Eq. 7 in main text and express the summation over
+plug this into Eq. \ref{eq:alpha-RPA} and express the summation over
 $k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
-arrive at Eq. 10 in main text.
+arrive at Eq. 5b in main text.
 
@@
 particle-in-box solution\cite{davies_physics_1997}). In combination,
-the individual terms of the summation in the right hand of Eq. 10 is
+the individual terms of the summation in the right hand of Eq. 5b is
 independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
@@
   \label{eq:alpha-perp-L}
-  \alpha^{\perp} \propto m^{\parallel} \delta^{2}
+  \alpha^{\perp} \propto \delta^{2}
 \end{equation}
@@
 
-\subsection{Detailed discussion for main text Eq. 14 }
+The dependency of $\alpha^{\perp}$ on the thickness of a 2D material,
+can also be regarded using fundamental electrostatic model. Consider
+the smallest repeating unit of the 2D material with xy-plane area $A$,
+under small perturbation field $E$ along the z-direction.  Note that
+the surface bound charge $\sigma_{\mathrm{b}}=n e /A$, where $n$ is
+the number of unit charges contributes to the bound charges, comes
+only from the dipoles of the outer-most atoms, since the induced
+charges from inner atoms are cancel out (see Figure \ref{fig:classic-model}).
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\linewidth]{img/SI-classic.pdf}
+  \caption{Fundamental electrostatic model for the
+    thickness-dependency of $\alpha^{\perp}$, using 2H-MoS2 as an
+    example. Left: induced dipoles from individual atoms along the
+    z-direction. The positive and negative induced charges from inner
+    atoms cancel out. Right: simplied model for the thickness
+    dependency of $\alpha^{\perp}$, where the surface dipole density
+    $\boldsymbol{\mu}$ comes only from the outer-most atoms.}
+  \label{fig:classic-model}
+\end{figure}
+From the definition of
+$\alpha^{\perp}$, we have:
+\begin{equation}
+  \label{eq:alpha-classic}
+  \alpha^{\perp} = \frac{\boldsymbol{u}_{z}}{E_{\mathrm{loc}} A}
+  = \frac{(d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j}) \sigma_{\mathrm{b}}}{E}
+\end{equation}
+where $r_{\mathrm{cov}}^{i}$ and $r_{\mathrm{cov}}^{j}$ are the
+covalent radii of the outer-most atoms, the characteristic length of
+the dipole extension in z-direction, and $d_{\mathrm{max}}$ is the
+z-distance between the nuclei of such atoms.  The field $E$
+counterbalances the field from the surface bound charges and equals
+$E = \sigma_{\mathrm{b}}/\varepsilon_{0}$. Therefore we have:
+\begin{equation}
+  \label{eq:alpha-classic-2}
+  \alpha^{\perp} = (d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j})\varepsilon_{0}
+                = \delta_{\mathrm{cov}} \varepsilon_{0}
+\end{equation}
+which explains the linear relation seen in Figure 3c of main text. We
+can see that such simple model nicely captures the thickness feature
+of $\alpha^{\perp}$, and reproduces the right coefficient between
+$\delta_{\mathrm{cov}}$ and $\alpha^{\perp}$. Finally, the schematic
+drawing of the polarizability ellipsoid for a 2D material, is drawn in
+Figure \ref{fig:ellipsoid}.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.6\linewidth]{img/SI-ellipsoid.pdf}
+  \caption{Polarizability ellipsoid of a 2D material, the long axis
+    equals $\alpha^{\parallel}/2\varepsilon_{0}$ and the short axis
+    equals  $\alpha^{\perp}/2\varepsilon_{0}$}
+  \label{fig:ellipsoid}
+\end{figure}
+
+\subsection{Detailed discussion for main text Eq. 9}
 \label{sec:theory-2}
 
-Eq. 14 is the detailed form of Eq. 6 considering wavefunctions in all
+Eq. 9 is the detailed form of Eq. 6 considering wavefunctions in all
 directions are periodic which can be written in the form of Block
-waves. The solution for Eq. 14 in main text is derived as follows. For
+waves. The solution for Eq. 9 in main text is derived as follows. For
 simplicity we consider that the effective mass $m^{*}$ is uniform,
@@
     \label{eq:integral-BZ-bulk}
-    \alpha^{\perp} &\propto {\displaystyle \frac{2 \pi
+    \varepsilon_{\mathrm{Bulk}} &\propto {\displaystyle \frac{2 \pi
         \mathrm{arctan}(\sqrt{Ak^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}}A^{3}}}
@@
       } \bigg\rvert_{0}^{k_{\mathrm{BZ}}}\\
-      &\propto \sqrt{\frac{m^{*}}{E_{\mathrm{g}}}}
+      &\propto 1/\sqrt{E_{\mathrm{g}}}
   \end{aligned}
 \end{equation}
-since generally
+when $\varepsilon_{\mathrm{Bulk}} \gg 1$. since generally
 $\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg E_{\mathrm{g}}$. When
-$\varepsilon_{\mathrm{bulk}} \gg 1$ and assuming the difference
-between $m^{*}$ in different semiconductors is small
-\cite{Finkenrath_1988}, it is the Moss relation of bulk semiconductors.
+$\varepsilon_{\mathrm{bulk}} \gg 1$ \cite{Finkenrath_1988}, it is the
+Moss relation of bulk semiconductors.
 
@@
 \section{Raw data from first principles calculations}
+\subsection{Quantities from First Principles Calculation}
 \label{sec:raw}
 
-TBD.
+\input{raw_data}
 
+\subsection{Density of States (DOS) plots for the materials studied}
+\label{sec:DOS}
+
+\input{DOS_figs}
+
+\subsection{Bandstructures of 2D Materials Calculated}
+\label{sec:bs}
+
+\input{BS_figures}
+
+\clearpage{}
 \section*{}

### 2018-10-20 paper.tex
Minor changes to the manuscript

@@
 
-In persuit of the Moss-like relation of 2D materials, a accurate
+In persuit of the Moss-like relation of 2D materials, an accurate
 description of the dielectric properties of 2D materials needs to be
-established. One known issue is that the concept of macroscopic
+established. One challenge is that the concept of macroscopic
 dielectric constant is ill-defined for 2D materials
@@
   1a}, in first principles calculations, an isolated 2D material is
-placed at the xy-plane of a periodically repeating superlattice (SL)
-with a length $L$ along the z-direction large enough to prevent the
-interactions between periodic images. The macroscopic dielectric
+placed in the xy-plane of a periodically repeating superlattice (SL)
+with a length $L$ along the z-direction. The macroscopic dielectric
 tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, from
@@
 external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the
-directions in $(x, y, z)$,such that:
+directions in $(x, y, z)$, such that:
 \begin{subequations}
@@
 dielectric tensor ($p \neq q$) tend to be negligible.  Consider that
-the 2D material is placed in vacuum, such that $\kappa^{pp} \equiv 1$
-and $\kappa^{pq} \equiv 0$, we can distinguish two components of the
+the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
+and $\kappa^{pq} = 0$, we can distinguish two components of the
 SL dielectric tensor, namely the in-plane
@@
 $|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which only
-extends to ~12 \AA{} along the z-direction inside the SL. When $L$ is
+extends to ~12 \AA{} along the z-direction. When $L$ is
 large enough that the induced dipoles from periodic images do not
@@
 W and X=S, Se, Te), in the top panels of Figure \ref{fig-1}b and
-\ref{fig-1}c \todo{change order!}, respectively. We can also observe
+\ref{fig-1}c \todo{change order!}, respectively. We also observe
 that neither $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
@@
 Eq. \ref{eq:def-eps-2} with $L$, that
-$\boldsymbol{\mu}^{p} = \boldsymbol{P}_{p}L = \int_{\mathrm{SL}}
-\rho(\boldsymbol{r}) \boldsymbol{r}_{p}d^{3} \boldsymbol{r}/A$,
+$\boldsymbol{\mu}^{p} = \boldsymbol{P}^{p}L = \int_{\mathrm{SL}}
+\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$,
 independent of the superlattice size. Similar to the definition of
@@
 $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}d
-and \ref{fig-1}e). These findings indicate that the 2D polarizability,
+$\varepsilon_{\mathrm{SL}}^{\perp}$ of the TMDCs, as shown Figure \ref{fig-1}d
+and \ref{fig-1}e, respectively. These findings indicate that the 2D polarizability,
 instead of the dielectric constant, is the true descriptor of the
@@
   \varepsilon_{\mathrm{SL}}
-  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
+  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\boldsymbol{q}|^{2} \Omega}
   \sum_{\mathrm{k, c, v}}
@@
 for $\alpha^{\parallel}$ and $\alpha^{\perp}$ under small perturbation
-(details see Supplementary Section SXX \todo{mark!}):
+(details see Supplementary Section S4):
 \begin{subequations}
@@
 \cite{Jiang_2017_Eg_Eb}. On the contrary, $\psi(z)$ is the solution to
-the Schr\"{o}dinger equation Hamiltonian
+the Schr\"{o}dinger equation with Hamiltonian
 $\mathcal{H} = -\hbar^{2}/2m^{*} \nabla^{2} + V(z)$, where $\hbar$ is
@@
 $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
-of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle dots), with a
-linear regression slope of ~0.182 and $R^{2}$ of 0.84. From
-Ref. \cite{Jiang_2017_Eg_Eb}, the slope between
+of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle
+dots), with a linear regression slope of ~0.182 and $R^{2}$ of
+0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
 $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
@@
   \label{eq:cov-thick}
-  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
-  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
+  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
+  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
 \end{equation}
-where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
+where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
 is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
@@
 close match between the linear slope in Figure \ref{fig-3}c and
-$1/4\pi$. In other wordst, the universal scaling relation for
+$1/4\pi$. In other words, the universal scaling relation for
 $\alpha^{\perp}$ indicates the quantity
@@
 in-plane screened electrostatic potential $V(r)$ from a point charge
-in an 2D plane, as a function of distance $r$,
-\cite{Keldysh_1979_eps_multi,Pulci_2014}:
+in an 2D plane, as a function of distance $r$:
 $V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
@@
       r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
-      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$, where $H_{0}$
-is the Struve function and $Y_{0}$ is the Bessel function of second
-kind, is assciated with the in-plane screening radius
+      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
+\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
+function and $Y_{0}$ is the Bessel function of second kind, is
+assciated with the in-plane screening radius
 $r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
@@
 polarizability ellipsoid picture of molecules used in spectroscopy
-\cite{Banwell_1994}. The in-plane screening length is generally larger
-for a smaller bandgap semiconductor, which qualitatively explains the
-inverse propotional relation between $\alpha^{\parallel}$ and
-$E_{\mathrm{g}}$, a 2D version of the Moss-relation.
+\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
+screening length is generally larger for a smaller bandgap
+semiconductor, which qualitatively explains the inverse propotional
+relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
+version of the Moss-relation.
 

### 2018-10-20 convert.py

@@ -28,11 +28,10 @@ def convert_pdf(infile, outdir="./img"):
     outfile = outfile.replace(".svg", ".pdf")
     print(outfile)
     program = "inkscape"
-    params = ["--without-gui", "--export-area-drawing",
+    params = ["--without-gui", "--export-area-page",
     ]
     io = ["--file={}".format(infile),
           "--export-pdf={}".format(outfile)]
-    
     success = subprocess.call([program, *params, *io])
     if success != 0:
         warnings.warn(TColors.FAIL + "File {} cannot be converted!".format(infile) + TColors.ENDC)

### 2018-10-24 paper.tex
Change to paper up to 2D Moss relation

@@
 In fact, some pioneering work\cite{Moss_1950_relation} discovered
-relationships between the dielectric constant $\varepsilon$ and other
+relations between the dielectric constant $\varepsilon$ and other
 physical properties, in particular the band gap $E_{\mathrm{g}}$
@@
 that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
-relationship, known as the Moss relation:
+relation, known as the Moss relation:
 \begin{equation}
@@
 \end{equation}
-Other similar semi-empirical models for the relationship between
+Other similar semi-empirical models for the relations between
 $\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
@@
 
-While the relation between the electronic and dielectric properties
+While the relations between the electronic and dielectric properties
 for bulk semiconductors are well-established, it is unknown if such
-relation still exists in low-dimensional materials. For instance,
-two-dimensional (2D) materials, the atomically-thin crystalline layers
-\cite{Novoselov_2016}, are known to have distinct electronic
-\cite{Mak_2010,Tran_2014} and dielectric properties
-\cite{Keldysh_1979_eps_multi,Sharma_1985} compared with their bulk
-counterparts, making the empirical relations of dielectric constant in
-bulk materials, like the Moss relation invalid within the context of
-2D materials. More critically, the static dielectric constant, a
-quantity associated with the macroscopic dielectric property and
-commonly obtained by theoretical calculations of 2D materials
-\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
-describe the microscopic and anisotropic dielectric nature of 2D
-materials
+equation still exists in low-dimensional materials. One important
+feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
+the electric screening is attenuated and anisotropic
+\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
+makes the empirical relations of dielectric constants in bulk
+materials, like the Moss relation invalid within the context of 2D
+materials. More critically, the static dielectric constant, a quantity
+associated with the macroscopic dielectric and optoelectronic
+properties and commonly obtained by theoretical calculations of 2D
+materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
+not well describe this microscopic and anisotropic dielectric nature
+of 2D materials
 \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
 accurate description of the 2D dielectric nature is the prerequisite
-for a 2D Moss-like relation. Here we show that instead of the
+for a 2D Moss-like relation, which could be used to make predictions
+for less-investigated layered crystals and to create materials design
+rules at an accurate level.  Here we show that instead of the
 dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
@@
 in-plane and out-of-plane polarizations. Based on first principles
-simulation of over 50 kinds \todo{some more?} of monolayer 2D
-materials, we reveal the long-sought universal dielectric scale
-relation in the 2D world: the in-plane polarizability
-$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
-$E_{\mathrm{g}}$, while the out-of-plane polarizability
-$\alpha^{\perp}$ is closely related with the intrinsic thickness of 2D
-materials. The anisotropy of the 2D polarizability is further
-explained by a confined quantum model. The universal relations provide
-quantitative prediction of the dielectric properties of 2D materials,
-which leads to better design and understanding of electronic devices
-based on 2D materials and their heterostructures. Furthermore, such
-relations bridge the dielectric properties between the 2D materials
-and their 3D counterparts, and ultimately pushes the boundary of the
-understanding of electronic screening in both dimensions.
+simulation using highly accurate hybrid functionals and analytical
+models, we reveal the long-sought universal dielectric-scale relation
+in the 2D world: the in-plane polarizability $\alpha^{\parallel}$ is
+inversely proportional to the minimal bandgap $E_{\mathrm{g}}$, while
+the out-of-plane polarizability $\alpha^{\perp}$ is directly related
+with the intrinsic thickness of 2D materials. An analytical
+quantum-mechanical model is developed which give a sound background to
+the dielectric-scale relationships. Furthermore, such relations unify
+the dielectric properties between the 2D materials and their 3D
+counterparts in a natural manner, which ultimately pushes the boundary
+of the understanding of electronic screening in both dimensions. The
+discovery of scaling relationships between dielectric and electronic
+and structural properties in 2D compounds introduces a new and general
+pathway for the exploration of their complex physical and chemical
+phenomena well beyond the currently possible applications.
 
@@
 \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
-shown in Figure \ref{fig-1}a \todo{I'll change upon your change of Fig
-  1a}, in first principles calculations, an isolated 2D material is
-placed in the xy-plane of a periodically repeating superlattice (SL)
-with a length $L$ along the z-direction. The macroscopic dielectric
-tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, from
-fundamental electrostatics, is determined by the response of
-volumetric dipole density $\boldsymbol{P}^{p}$, under small perturbative
-external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the
-directions in $(x, y, z)$, such that:
+shown in Figure \ref{fig-1}a, in routine first principles
+calculations, an isolated 2D material is placed in the xy-plane of a
+periodically repeating superlattice (SL) with a length $L$ along the
+z-direction separating the cell images. The macroscopic dielectric
+tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, is
+determined through fundamental electrostatics by the response of the
+polarization density $\boldsymbol{P}^{p}$, under small
+perturbative external field $\boldsymbol{E}^{q}$, where $p$, $q$ are
+the directions in $(x, y, z)$, such that:
 \begin{subequations}
@@
 \end{subequations}
-$\kappa$ is the dielectric tensor of the environment, $\boldsymbol{u}$
-is the total dipole moments of the SL, $\rho$ is the spatial charge
-density, $\Omega=AL$ is the volume of the SL, $A$ is the xy-plane area
-of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
+where $\kappa$ is the dielectric tensor of the environment,
+$\boldsymbol{u}$ is the total dipole moments of the SL, $\rho$ is the
+spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
+area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
 majority of 2D semiconductors, the off-diagonal elements of the
-dielectric tensor ($p \neq q$) tend to be negligible.  Consider that
-the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
-and $\kappa^{pq} = 0$, we can distinguish two components of the
-SL dielectric tensor, namely the in-plane
+dielectric tensor ($p \neq q$) tend to be negligible.  Considering
+that the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
+and $\kappa^{pq} = 0$, we can distinguish two components of the SL
+dielectric tensor, namely the in-plane
 ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
@@
 and
-$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$
-\todo{geometry or numerical average?}. Due to the absence of bonding
-along the z-direction, the induced charge density of a 2D material is
-highly confined. Figure \ref{fig-1}a demonstrates the charge density
-difference between zero and finite electric fields,
+$\varepsilon_{\mathrm{SL}}^{\perp} =
+\varepsilon_{\mathrm{SL}}^{zz}$. Due to the absence of bonding along
+the z-direction, the induced charge density of a 2D material is highly
+confined in the xy-plane but delocalised along of the
+z-direction. Figure \ref{fig-1}a shows the charge density difference
+between zero and finite electric fields,
 $\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ along the
 z-axis for an isolated 2H-MoS$_{2}$ layer under
-$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which only
-extends to ~12 \AA{} along the z-direction. When $L$ is
-large enough that the induced dipoles from periodic images do not
-overlap, the total dipole moments $\boldsymbol{u}$ of the SL in
-Eq. \ref{eq:def-eps-2} is independent of $L$. As a consequence, we can
-see from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
+$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which extends to
+$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough, the
+induced dipoles from periodic images do not overlap, and the total
+dipole moments $\boldsymbol{u}$ of the SL in Eq. \ref{eq:def-eps-2} is
+independent of $L$. As a consequence, we can see from
+Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on the SL length $L$. We
-show this by plotting $\epsilon^{\parallel}_{\mathrm{SL}}$ and
-$\epsilon^{\perp}_{\mathrm{SL}}$ as functions of $L$ for 2H-type group
-6 transitional metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo,
-W and X=S, Se, Te), in the top panels of Figure \ref{fig-1}b and
-\ref{fig-1}c \todo{change order!}, respectively. We also observe
-that neither $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
-$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with the superlattice
-length $L$ due to fact that the long-range Coulomb interaction could
-not be completed screened, which is computationally unpractical
+$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$. We show this by
+plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
+theory (DFT) as functions of $L$ for P$\bar{6}$m2 (2H) transitional
+metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
+Te), in the top panels of Figure \ref{fig-1}b and \ref{fig-1}c,
+respectively. We observe that neither
+$\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
+$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
+that the long-range Coulomb interaction could not be completed
+screened within the range of magnitudes computationally accessible
 \cite{Hueser_2013_2Dvs3D}. The $L$-dependency of macroscopic
 dielectric constant makes it erroneous to use
-$\varepsilon_{\mathrm{SL}}$ to present the dielectric nature of a 2D
+$\varepsilon_{\mathrm{SL}}$ to represent the dielectric nature of a 2D
 material. Therefore, we need to find a $L$-independent quantity to
 present the intrinsic dielectric properties of the 2D materials. As
-discussed previous, since the total dipole moments $\mathbf{u}$ remain
-constant with $L$, we can define the surface or sheet polarization
-density matrix $\boldsymbol{\mu}$, by multiplying
-Eq. \ref{eq:def-eps-2} with $L$, that
+discussed previously, since the total dipole moments $\mathbf{u}$
+remain constant with $L$, we can define the surface or sheet
+polarization density matrix $\boldsymbol{\mu}$, by multiplying
+Eq. \ref{eq:def-eps-2} with $L$, such that
 $\boldsymbol{\mu}^{p} = \boldsymbol{P}^{p}L = \int_{\mathrm{SL}}
-\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$,
-independent of the superlattice size. Similar to the definition of
+\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$, which
+is independent of the superlattice size. Similar to the definition of
 molecular polarizability \cite{Israelachvili_2011}, the sheet
@@
 
-We note that the dielectric properties of 2D materials are also often
-modeled using an effect medium approach, which treats the 2D material
-as a slab with effective permittivity $\varepsilon_{\mathrm{2D}}$ and
-thickness $\delta$
+It is also worth mentioning that the dielectric properties of 2D
+materials are also often modeled using an effective medium approach,
+which treats the 2D material as a slab with effective permittivity
+$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
 \cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
@@
 expensive, but also fails to capture the anisotropy of the 2D
-dielectric properties (details see Supplementary Section S1). On the
+dielectric properties (see Supplementary Section S1). On the
 other hand, calculating 2D polarizabilities requires no knowledge of
@@
 We study several types of 2D materials of different electronic and
-optical properties, including transition metal dichalcogenides (TMDCs,
-with the formula MX\(_{\text{2}}\), where M is a metal in group 4, 6,
-10 and X=O, S, Se, Te), metal monochalcogenides (Ga$_{2}$S$_{2}$,
-Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl, I), hexagonal boron
-nitride (BN), graphene derivatives (fluorographene (C$_{2}$F$_{2}$),
-graphane (C$_{2}$H$_{2}$)) and phosphorene (P$_{4}$).  For the TMDCs,
-we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2 space
-group) and 1T (P3m1 space group).  The structures and elements of the
-2D materials are shown in Figure \ref{fig-2}a and \ref{fig-2}b,
-respectively. The static 2D polarizabilities are calculated from the
-static dielectric response of the selected 2D materials using density
-functional theory (DFT) with the Heyd-Scuseria-Ernzerhof hybrid
-functionals (HSE06) using the Vienna Ab Initio Simulation Package (VASP)
-including spin-orbit coupling to avoid limitations on the description
-of band gaps and dielectric functions. Further details for the first
-principle calculations please refer to \textit{Methods}.
+optical properties as show in Figure \ref{fig-2}, including transition
+metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
+where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
+monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
+(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
+(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
+phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
+(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
+2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
+2D polarizabilities are calculated from the static dielectric response
+of the selected 2D materials using density functional theory (DFT)
+with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
+Vienna Ab Initio Simulation Package (VASP) including spin-orbit
+coupling to avoid limitations on the description of band gaps and
+dielectric functions (see Methods for details).
 
@@
 (blue dots) and polarizabilities (bar plots) of all the 2D materials
-investigated, covering a wide bandgap range from far infrared to
+investigated, covering a wide spectrum range from far infrared to
 ultraviolet. From dimension analysis, it is more intuitive to express
@@
 trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
-trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
-details see Supplementary Section S2.2).  Combining recent theoretical
-findings of the universal linear relation between exciton binding
-energy $E_{\mathrm{b}}$ and bandgap $E_{\mathrm{b}}$ of 2D materials
+trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
+Supplementary Section S2.2).  Combining recent theoretical findings of
+the universal linear relation between exciton binding energy
+$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
 \cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
@@
 in-plane wave vector and $u(\rho)$ is periodic function in the
-xy-planeAccording to the random phase approximation (RPA)
+xy-plane. According to the random phase approximation (RPA)
 theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
@@
   \varepsilon_{\mathrm{SL}}
-  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\boldsymbol{q}|^{2} \Omega}
+  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
   \sum_{\mathrm{k, c, v}}

### 2018-10-25 src/VASP_HSE/alpha_alpha.py
Dielectric anisotropy diagram for 2D and 3D

@@ -1,0 +1,177 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+from scipy.optimize import curve_fit
+import os, os.path
+from scipy.constants import pi, epsilon_0
+from gpaw_data import get_data
+import scipy
+import csv
+
+"""
+Extract the alpha from the HSE xlsx files
+"""
+
+db_file = "../../data/gpaw_data/c2db.db"
+bulk_file = "../../data/2D-bulk/bulk.db"
+if not os.path.exists(db_file):
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
+def get_bulk(name, proto, id=None, method="gpaw"):
+    # Get bulk properties
+    if id is None:
+        res = list(db.select(formula=name, prototype=proto))
+        if len(res) == 0:
+            return None
+        r = res[0]
+    else:
+        r = db.get(id)    
+    try:
+        if method.lower() == "gpaw":
+            L = r.bulk_L
+            eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
+            eps_perp = r.bulk_eps_z
+            e = r.gap_hse
+        # VASP version below:
+        elif method.lower() == "vasp":
+            L = r.bulk_L_vasp
+            eps_para = (r.bulk_eps_x_vasp + r.bulk_eps_y_vasp) / 2
+            eps_perp = r.bulk_eps_z_vasp
+            if r.bulk_gap_vasp < 0:
+                r = r.gap_hse
+            else:
+                r = r.bulk_gap_vasep
+        else:
+            return None
+        if eps_para < 0 or eps_perp < 0:
+            return None
+    except Exception:
+        return None
+    return L, eps_para, eps_perp, e
+
+db = ase.db.connect(db_file)
+bulk_db = ase.db.connect(bulk_file)
+
+materials = []
+eps_x = []
+eps_z = []
[…]

### 2018-10-25 src/VASP_HSE/relation_2D3D.py

@@ -52,43 +52,30 @@ def get_bulk(name, proto, id=None, method="gpaw"):
             L = r.bulk_L
             eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
             eps_perp = r.bulk_eps_z
+            e = r.gap_hse
         # VASP version below:
         elif method.lower() == "vasp":
             L = r.bulk_L_vasp
             eps_para = (r.bulk_eps_x_vasp + r.bulk_eps_y_vasp) / 2
             eps_perp = r.bulk_eps_z_vasp
+            if r.bulk_gap < 0:
+                e = r.gap_hse
+            else:
+                e = r.bulk_gap
         else:
             return None
         if eps_para < 0 or eps_perp < 0:
             return None
     except Exception:
         return None
-    return L, eps_para, eps_perp
-    
-    # dir_root = os.path.join("../../data/2D-bulk/{}-{}".format(name, proto))
-    # gpw_file = os.path.join(dir_root, "gs.gpw")
-    # traj_file = os.path.join(dir_root, "{}-{}_relax.traj".format(name, proto))
-    # eps_file = os.path.join(dir_root, "eps_df.npz")
-    # if (not os.path.exists(gpw_file)) or (not os.path.exists(eps_file)):
-    #     return None
-    # else:
-    #     try:
-    #         d = Trajectory(traj_file)[-1].cell[-1][-1]
-    #     except Exception:
-    #         return None
-    #         # calc = GPAW(gpw_file)
-    #         # d = calc.get_atoms().cell[-1][-1]
-    #     f = numpy.load(eps_file)
-    #     eps_xx = f["eps_x"][0].real
-    #     eps_zz = f["eps_z"][0].real
-    #     return d, eps_xx, eps_zz
+    return L, eps_para, eps_perp, e
 
 reader = csv.reader(open("../../data/HSE-data/2D_HSE.csv", encoding="utf8"))
 next(reader)                    # skip line1
 for row in reader:
[…]

### 2018-10-26 paper.tex
Minor change to text

@@
 in-plane and out-of-plane polarizations. Based on first principles
-simulation using highly accurate hybrid functionals and analytical
-models, we reveal the long-sought universal dielectric-scale relation
-in the 2D world: the in-plane polarizability $\alpha^{\parallel}$ is
-inversely proportional to the minimal bandgap $E_{\mathrm{g}}$, while
-the out-of-plane polarizability $\alpha^{\perp}$ is directly related
-with the intrinsic thickness of 2D materials. An analytical
-quantum-mechanical model is developed which give a sound background to
-the dielectric-scale relationships. Furthermore, such relations unify
-the dielectric properties between the 2D materials and their 3D
-counterparts in a natural manner, which ultimately pushes the boundary
-of the understanding of electronic screening in both dimensions. The
+simulation using highly accurate hybrid functionals and quantum
+mechanical models, we reveal the long-sought universal
+dielectric-scale relation in the 2D world: the in-plane polarizability
+$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
+$E_{\mathrm{g}}$, while the out-of-plane polarizability
+$\alpha^{\perp}$ is directly related with the intrinsic thickness of
+2D materials. An analytical quantum-mechanical model is developed
+which give a sound background to the dielectric-scale
+relationships. Furthermore, such relations unify the dielectric
+properties between the 2D materials and their 3D counterparts in a
+natural manner, which ultimately pushes the boundary of the
+understanding of electronic screening in both dimensions. The
 discovery of scaling relationships between dielectric and electronic

### 2018-10-26 paper.tex
Reorder the theoretical part

@@
 expensive, but also fails to capture the anisotropy of the 2D
-dielectric properties (see Supplementary Section S1). On the
-other hand, calculating 2D polarizabilities requires no knowledge of
+dielectric properties (see Supplementary Section S1). On the other
+hand, calculating 2D polarizabilities requires no knowledge of
 $\delta$ (see Eqs. \ref{eq:alpha-para-def} and
@@
 the polarizability as the true descriptor of 2D dielectric properties,
-we will reveal the universal Moss-like relation of 2D materials.
+we will reveal the universal Moss-like relation of 2D materials from
+both theoretical and first principles studies.
 
-\subsection{2D Moss Relations}
-\label{sec:first-principles}
-
-We study several types of 2D materials of different electronic and
-optical properties as show in Figure \ref{fig-2}, including transition
-metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
-where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
-monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
-(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
-(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
-phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
-(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
-2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
-2D polarizabilities are calculated from the static dielectric response
-of the selected 2D materials using density functional theory (DFT)
-with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
-Vienna Ab Initio Simulation Package (VASP) including spin-orbit
-coupling to avoid limitations on the description of band gaps and
-dielectric functions (see Methods for details).
-
-Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
-(blue dots) and polarizabilities (bar plots) of all the 2D materials
-investigated, covering a wide spectrum range from far infrared to
-ultraviolet. From dimension analysis, it is more intuitive to express
-the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
-of \AA. We find that $\alpha^{\parallel}$ has a general descending
-trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
-trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
-Supplementary Section S2.2).  Combining recent theoretical findings of
-the universal linear relation between exciton binding energy
-$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
-\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
-fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
-$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
-a general Moss-like relation between $E_{\mathrm{g}}$ and
-$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
-the bandgap-independent relation of $\alpha^{\perp}$ resembles
-molecular polarizabilities of conjugate molecules \cite{Davies_1952},
-fullerenes \cite{Sabirov_2014} and carbon nanotubes
-\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
-we show that the universal Moss-like relations exist for both
-$\alpha^{\parallel}$ and $\alpha^{\perp}$.
-
-Similar to the treatment of quantum wells (QW), the wavefunction of an
-isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
-and out-of-plane components \cite{davies_physics_1997}
-$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
-$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
-the in-plane coordinate. Using the Bloch theorem, the periodic
-$\psi^{\parallel}(\mathbf{\rho})$ can be further expressed as
-$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
-in-plane wave vector and $u(\rho)$ is periodic function in the
-xy-plane. According to the random phase approximation (RPA)
+\subsection{Polarizability-Based Theoretical Model}
+In this section we theoretically investigate the existence of the 2D
+Moss-like relations, based on the 2D polarizability.  Due to its
+highly anisotropic nature, the wavefunction of an isolated 2D material
+$\psi(\mathbf{r})$ can be separated into the in- and out-of-plane
+components, similar to the treatment of quantum wells
+(QW),\cite{davies_physics_1997} such that
+$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
+$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
+is the in-plane coordinate. Using the Bloch theorem, the periodic
+$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
+$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
+  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
+in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
+in the xy-plane. According to the random phase approximation (RPA)
 theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
@@
 the Schr\"{o}dinger equation with Hamiltonian
-$\mathcal{H} = -\hbar^{2}/2m^{*} \nabla^{2} + V(z)$, where $\hbar$ is
-the reduced Planck constant, $m^{*}$ is reduced mass and $V(z)$ is the
-confined Coulombic potential along the z-direction created by the
+$\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where $\hbar$ is
+the reduced Planck constant, $m_{e}$ is electron mass and $V(z)$ is
+the confined Coulombic potential along the z-direction created by the
 nuclei \cite{davies_physics_1997,ihn_semiconductor_2009}. Using a
-simple particle-in-well model, we show that both the numerator and
+simple particle-in-box model, we show that both the numerator and
 denominator parts of Eq. \ref{eq:alpha_perp_RPA} are independent of
 $E_{g}$ but instead modulated by the size of the potential confinement
-(details see Supplementary Section S4). We further prove,
-using both quantum mechanical and fundamental electrostatic models,
-that $\alpha^{\perp}$ is actually proportional to the size of
-potential confinement (details see Supplementary Section
-S4), which we may relate with the thickness $\delta$ of
-the 2D material. Now we may finally propose the 2D analog of the Moss
-relation with both in- and out-of-plane polarizations:
+(details see Supplementary Section S4). We further prove, using both
+quantum mechanical and fundamental electrostatic models, that
+$\alpha^{\perp}$ is actually proportional to the size of potential
+confinement (details see Supplementary Section S4), which we may
+relate with the thickness $\delta$ of the 2D material. Now we may
+finally propose the 2D analog of the Moss relation with both in- and
+out-of-plane polarizations:
 \begin{subequations}
@@
 \end{subequations}
-which form the main conclusion of this work.
+which form the main conclusion of this work. Next, we will validate
+the proposed 2D Moss-like relations using first principle
+calculations.
+
+\subsection{2D Moss Relations}
+\label{sec:first-principles}
+We study several types of 2D materials of different electronic and
+optical properties as show in Figure \ref{fig-2}, including transition
+metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
+where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
+monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
+(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
+(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
+phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
+(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
+2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
+2D polarizabilities are calculated from the static dielectric response
+of the selected 2D materials using density functional theory (DFT)
+with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
+Vienna Ab Initio Simulation Package (VASP) including spin-orbit
+coupling to avoid limitations on the description of band gaps and
+dielectric functions (see Methods for details).
+
+Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
+(blue dots) and polarizabilities (bar plots) of all the 2D materials
+investigated, covering a wide spectrum range from far infrared to
+ultraviolet. From dimension analysis, it is more intuitive to express
+the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
+of \AA. We find that $\alpha^{\parallel}$ has a general descending
+trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
+trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
+Supplementary Section S2.2).  Combining recent theoretical findings of
+the universal linear relation between exciton binding energy
+$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
+a general Moss-like relation between $E_{\mathrm{g}}$ and
+$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
+the bandgap-independent relation of $\alpha^{\perp}$ resembles
+molecular polarizabilities of conjugate molecules \cite{Davies_1952},
+fullerenes \cite{Sabirov_2014} and carbon nanotubes
+\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
+we show that the universal Moss-like relations exist for both
+$\alpha^{\parallel}$ and $\alpha^{\perp}$.
 

### 2018-10-29 paper.tex
Add paragraph about dielectric anisotropy

@@
 investigated, covering a wide spectrum range from far infrared to
-ultraviolet. From dimension analysis, it is more intuitive to express
-the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
-of \AA. We find that $\alpha^{\parallel}$ has a general descending
-trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
-trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
-Supplementary Section S2.2).  Combining recent theoretical findings of
-the universal linear relation between exciton binding energy
-$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
-\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
-fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
-$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
-a general Moss-like relation between $E_{\mathrm{g}}$ and
-$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
-the bandgap-independent relation of $\alpha^{\perp}$ resembles
-molecular polarizabilities of conjugate molecules \cite{Davies_1952},
-fullerenes \cite{Sabirov_2014} and carbon nanotubes
-\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
-we show that the universal Moss-like relations exist for both
-$\alpha^{\parallel}$ and $\alpha^{\perp}$.
-
-We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
-using the polarizabilities calculated by first principle
-calculations. Figure \ref{fig-3}b shows
-$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
-of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle
-dots), with a linear regression slope of ~0.182 and $R^{2}$ of
-0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
-$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
+ultraviolet. Note from dimension analysis, it is more intuitive to
+express the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which
+has unit of \AA. We find that $\alpha^{\parallel}$ has a general
+descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
+no apparent trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
+observed (see Supplementary Section S2.2), which appears to be in good
+agreement with our polarizability-based theoretical model. We now
+validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
+polarizabilities calculated by first principle calculations. Figure
+\ref{fig-3}b shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in
+\AA{}) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
+investiaged (circle dots), with a linear regression slope of ~0.182
+and $R^{2}$ of 0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope
+between $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
 $8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
@@
 $\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
-Green’s function method (GW) together with the Bethe-Salpeter
-equation (BSE), the convergence of such method is known to be highly
-affected by the dielectric screening of 2D materials
+Green’s function method (GW) together with the Bethe-Salpeter equation
+(BSE), the convergence of such method is known to be highly affected
+by the dielectric screening of 2D materials
 \cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
@@
 We further examine the relation between $\alpha^{\perp}$ and the
-thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
-we choose the thickness of as 2D material as its ``covalent''
-thickness $\delta_{\mathrm{cov}}$, which is
-defined as the longest distance along the z-direction between any two
-atom nuclei plus their covalent radii:
+thickness of a 2D material proposed in
+Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
+$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
+longest distance along the z-direction between any two atom nuclei
+plus their covalent radii:
 \begin{equation}
@@
 where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
-is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
-Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
-shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
-with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
-to our theoretical predictions discussed above, the perfect linear
-correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
-its strong physical meaning. Similar to the molecular polarizability
-which characterizes the volume of electron cloud of an isolated
-molecule \cite{Israelachvili_2011}, the 2D polarizability also
-characterizes the volume of the electron cloud of a 2D material per
-unit area (from its definition), and naturally represents the
+is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
+in Figure \ref{fig-3}c, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$
+indeed shows an excellent linear correlation with
+$\delta_{\mathrm{cov}}$, with $R^{2}=0.98$, and the slope very close
+to $1/4\pi$. In addition to our theoretical predictions discussed
+above, the perfect linear correlation between $\alpha^{\perp}$ and
+$\delta_{\mathrm{cov}}$ has its strong physical meaning. Similar to
+the molecular polarizability which characterizes the volume of
+electron cloud of an isolated molecule \cite{Israelachvili_2011}, the
+2D polarizability also characterizes the volume of the electron cloud
+per unit area (from its definition), and naturally represents the
 thickness of the electron cloud of the 2D material. The fact that the
-thickness of the electron cloud of a 2D material can be approximated
-by the extension of valence states in the z-direction, explains the
-close match between the linear slope in Figure \ref{fig-3}c and
-$1/4\pi$. In other words, the universal scaling relation for
-$\alpha^{\perp}$ indicates the quantity
+thickness of the electron cloud can be approximated by the extension
+of valence states in the z-direction, explains the close match between
+the linear slope in Figure \ref{fig-3}c and $1/4\pi$ (see
+Supplementary Section S4.1). In other words, the universal scaling
+relation for $\alpha^{\perp}$ indicates the quantity
 $\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
@@
 
-To rule out the possibility that our conclusion is limited by the
-number of materials used, we further validate our proposed 2D
-Moss-like relations on the recently-published C2DB database
-\cite{Haastrup_2018}, from which we extracted the dielectric
+The universal relations of 2D polarizabilities are not
+coincidence. Combining recent theoretical findings of the linear
+relation between exciton binding energy $E_{\mathrm{b}}$ and
+$E_{\mathrm{g}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
+general Moss-like relation between $E_{\mathrm{g}}$ and
+$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
+2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
+molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
+carbon nanotubes \cite{Benedict_1995}, which are also shown to be
+geometry-dependent. To rule out the possibility that our conclusion is
+limited by the number of materials used, we further validate our
+proposed 2D Moss-like relations on the recently-published C2DB
+database \cite{Haastrup_2018}, from which we extracted the dielectric
 properties of over 230 2D materials calculated at the PBE level, and
@@
 
-In short, we have revealed the 2D analog of the Moss relation for both
-polarization direction by using the 2D polarizability:
+In short, we have revealed the 2D analog of the Moss relation by both
+theoretical modeling and first principles calculations:
 $\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
@@
 describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
-$\alpha^{\perp}$ and the degree of interlayer coupling $\eta$
-\cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
+$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
 be smoothly described.
 
+Although we have extensively shown that the treatment for the
+dielectric nature differs in 2D (polarizability) and 3D (dielectric
+constant) scenarios, a general picture of the dielectric properties in
+both dimensions can still be drawn by studying the dielectric
+anisotropy. The dielectric anisotropy index $\eta$ is defined as:
+\begin{equation}
+  \label{eq:anisotropy}
+  \begin{aligned}[t]
+    \eta =
+    \begin{cases}
+      {\displaystyle \min_{i \neq j}}
+      {\displaystyle
+        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
+      \ \mathrm{Bulk\ Materials}\\
+      {\displaystyle \min_{i \neq j}}
+      {\displaystyle
+        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
+      \ \mathrm{2D\ Materials}\\
+    \end{cases}
+  \end{aligned}
+\end{equation}
+$\eta=1$ indicates the material has isotropic dielectric properties
+while $\eta \to 0$ means the dielectric property is highly
+anisotropic. Figure XX \todo{TBD} shows the phase diagram of $\eta$ as
+function of $E_{\mathrm{g}}$ for 2D materials and their bulk
+counterparts. Interestingly, the 2D materials (\todo{marker shape})
+can be clearly distinguished from the layered bulk materials
+(\todo{marker shape}). The boundary separating the 2D and layered bulk
+materials is determined using an least-square support vector machine
+(LS-SVM) classification algorithm, and can be linearly approximated by
+the equation \todo{TBD}. The much lower $\eta$ values of 2D materials
+compared with their bulk counterparts indicates a high dielectric
+anisotropy, which is responsible for the unique 2D optoelectronic
+properties, such as electrostatic transparency
+\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
+\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
+also observe that $\eta$ of 2D materials increase almost linearly with
+$E_{\mathrm{g}}$, while such trend is absent for layered bulk
+materials. The observations above can be explained by the principles
+presented in thie work. As a result from the limited layer thickness
+(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
+varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
+\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
+$\eta$ of 2D materials. On the other hand, the fact that
+$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
+values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
+coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
+layered bulk materials compared with the corresponding monolayer, and
+making it possible to separate the 2D and layered bulk materials from
+the $\eta-E_{\mathrm{g}}$ phase diagram.
+
+\todo[inline]{I have some doubt how to handle the next paragraph, keep the status quo}
 As described in the previous section, the 2D Moss-like relation
@@
 which recovers the 3D Moss relation. Therefore, the universal
-$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss relation
-in 2D world, while the power law of $E_{\mathrm{g}}$ and independence
-of effective mass is a result of the confinement perpendicular to the
-2D plane.
+$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
+relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
+independence of effective mass is a result of the confinement
+perpendicular to the 2D plane.
 
@@
 \centering
-\includegraphics[width=\linewidth]{./img/fig4.pdf}
+\includegraphics[width=0.85\linewidth]{./img/fig4.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties

### 2018-10-29 src/VASP_HSE/alpha_alpha.py
Add polarizability data in other dimensions

@@ -134,6 +134,18 @@ A = 52.0; B = 18.2
 # cnt_r = numpy.linspace(2.0, 8.0, 8)
 # cnt_data = numpy.array([(eg, get_cnt(eg, r)) for eg in cnt_eg for r in cnt_r])
 
+def anisotropy(data):
+    a_max = numpy.max(data, axis=1)
+    a_min = numpy.min(data, axis=1)
+    return a_min / a_max
+
+def anis_from_file(file_name):
+    data = numpy.genfromtxt(file_name, delimiter=",",
+                            comments="#")  # csv ending
+    Eg = data[:, 1]
+    anis = anisotropy(data[:, 2:5])
+    return Eg, anis
+
 cnt_eg = numpy.sqrt(cnt_r * B / (cnt_x - A))
 # gpaw
 ax.scatter(gp_data[2], gp_data[1] / gp_data[0], marker="^", alpha=0.1,
@@ -158,9 +170,13 @@ ax.scatter(bulk.Eg_gpaw, numpy.min([bulk.eps_z_gpaw[:, 0] / bulk.eps_x_gpaw[:, 0
 
 # ax.scatter(cnt_data[:, 0], cnt_data[:, 1], alpha=0.5,
            # marker="*", label="CNT-1D")
-ax.scatter(cnt_eg, cnt_z / cnt_x, alpha=0.2,
-           marker="*", label="CNT-1D")
+# ax.scatter(cnt_eg, cnt_z / cnt_x, alpha=0.2,
+           # marker="*", label="CNT-1D")
 
+for f in ["CNT", "covalent", "polyacene", "molecule", "fullerene"]:
+    f_name = "../../data/other_dimension/{}.csv".format(f)
+    Eg, anis = anis_from_file(f_name)
+    ax.scatter(Eg, anis, label=f)
 
 xx = yy = numpy.linspace(0, 8, 100)
 ax.plot(xx, numpy.ones_like(xx), "--")

### 2018-10-29 src/VASP_HSE/alpha_alpha.py
Make anisotropy plot src more concise

@@ -15,124 +15,129 @@ import csv
 Extract the alpha from the HSE xlsx files
 """
 
-db_file = "../../data/gpaw_data/c2db.db"
-bulk_file = "../../data/2D-bulk/bulk.db"
-if not os.path.exists(db_file):
-    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
-                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+def get_2D3D():
+    aniso_data = "../../data/other_dimension/2D3D.npz"
+    if not os.path.exists(aniso_data):  # then need to create
+        db_file = "../../data/gpaw_data/c2db.db"
+        bulk_file = "../../data/2D-bulk/bulk.db"
+        if not os.path.exists(db_file):
+            raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                           "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
 
-def get_bulk(name, proto, id=None, method="gpaw"):
-    # Get bulk properties
-    if id is None:
-        res = list(db.select(formula=name, prototype=proto))
-        if len(res) == 0:
-            return None
-        r = res[0]
-    else:
-        r = db.get(id)    
-    try:
-        if method.lower() == "gpaw":
-            L = r.bulk_L
-            eps_para = (r.bulk_eps_x + r.bulk_eps_y) / 2
-            eps_perp = r.bulk_eps_z
-            e = r.gap_hse
-        # VASP version below:
-        elif method.lower() == "vasp":
-            L = r.bulk_L_vasp
-            eps_para = (r.bulk_eps_x_vasp + r.bulk_eps_y_vasp) / 2
-            eps_perp = r.bulk_eps_z_vasp
-            if r.bulk_gap_vasp < 0:
-                r = r.gap_hse
+        def get_bulk(name, proto, id=None, method="gpaw"):
+            # Get bulk properties
+            if id is None:
+                res = list(db.select(formula=name, prototype=proto))
+                if len(res) == 0:
+                    return None
+                r = res[0]
             else:
-                r = r.bulk_gap_vasep
-        else:
[…]

### 2018-10-30 src/VASP_HSE/alpha_alpha.py
Success with SVC

@@ -139,6 +139,20 @@ Eg_2D, Eg_3D, eta_2D, eta_3D = get_2D3D()
 ax.scatter(Eg_2D, eta_2D, marker="^", alpha=0.1)
 ax.scatter(Eg_3D, eta_3D, marker="s", alpha=0.1)
 
+# LinearSVM classification
+from sklearn.svm import LinearSVC
+svc = LinearSVC(C=1,
+                max_iter=100000,
+                class_weight={1:1, 2:3})
+class_feature = numpy.vstack([list(zip(Eg_2D, eta_2D)), list(zip(Eg_3D, eta_3D))])
+print(class_feature.shape)
+class_tag = numpy.append(1 * numpy.ones_like(Eg_2D), 2 * numpy.ones_like(Eg_3D))
+svc.fit(class_feature, class_tag)
+xx, yy = numpy.meshgrid(numpy.linspace(0, 8, 30), numpy.linspace(0, 1, 30))
+xy = numpy.vstack([xx.ravel(), yy.ravel()]).T
+zz = svc.decision_function(xy).reshape(xx.shape)
+ax.contour(xx, yy, zz, levels=[0])
+
 def anisotropy(data):
     a_max = numpy.max(data, axis=1)
     a_min = numpy.min(data, axis=1)
@@ -150,6 +164,7 @@ def anis_from_file(file_name):
     Eg = data[:, 1]
     anis = anisotropy(data[:, 2:5])
     return Eg, anis
+
 
 for f in ["CNT", "covalent", "polyacene", "molecule", "fullerene"]:
     f_name = "../../data/other_dimension/{}.csv".format(f)

### 2018-10-30 src/VASP_HSE/alpha_alpha.py
Add planar organic molecules for anisotropy comparison

@@ -136,8 +136,10 @@ fig = plt.figure(figsize=(3, 3))
 ax = fig.add_subplot(111)
 
 Eg_2D, Eg_3D, eta_2D, eta_3D = get_2D3D()
-ax.scatter(Eg_2D, eta_2D, marker="^", alpha=0.1)
-ax.scatter(Eg_3D, eta_3D, marker="s", alpha=0.1)
+ax.scatter(Eg_2D, eta_2D, marker="^", alpha=0.1, s=40,
+           linewidth=0)
+ax.scatter(Eg_3D, eta_3D, marker="s", alpha=0.1, s=40,
+           linewidth=0)
 
 # LinearSVM classification
 from sklearn.svm import LinearSVC
@@ -166,10 +168,18 @@ def anis_from_file(file_name):
     return Eg, anis
 
 
-for f in ["CNT", "covalent", "polyacene", "molecule", "fullerene"]:
+marks = {"CNT": "o",
+         "polyacene": "p",
+         "MPc": "<",
+         "covalent": ">",
+         "fullerene": "*"}
+for f in ["CNT", "covalent", "polyacene", "MPc", "fullerene"]:
     f_name = "../../data/other_dimension/{}.csv".format(f)
     Eg, anis = anis_from_file(f_name)
-    ax.scatter(Eg, anis, label=f)
+    ax.scatter(Eg, anis, label=f,
+               marker=marks[f], s=40,
+               alpha=0.6,
+               linewidth=0)
 
 xx = yy = numpy.linspace(0, 8, 100)
 ax.plot(xx, numpy.ones_like(xx), "--")

### 2018-10-30 paper.tex
Add paragraph discussing the 2D and 3D anisotropy

@@
 while $\eta \to 0$ means the dielectric property is highly
-anisotropic. Figure XX \todo{TBD} shows the phase diagram of $\eta$ as
-function of $E_{\mathrm{g}}$ for 2D materials and their bulk
-counterparts. Interestingly, the 2D materials (\todo{marker shape})
-can be clearly distinguished from the layered bulk materials
-(\todo{marker shape}). The boundary separating the 2D and layered bulk
-materials is determined using an least-square support vector machine
-(LS-SVM) classification algorithm, and can be linearly approximated by
-the equation \todo{TBD}. The much lower $\eta$ values of 2D materials
-compared with their bulk counterparts indicates a high dielectric
-anisotropy, which is responsible for the unique 2D optoelectronic
-properties, such as electrostatic transparency
+anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
+as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
+counterparts. Interestingly, the 2D materials (blue triangle) can be
+clearly distinguished from the bulk layered materials (orange
+square). The boundary separating the 2D and layered bulk materials is
+determined using an linear support vector machine (SVM) classification
+algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
+materials compared with their bulk counterparts indicates a high
+dielectric anisotropy, which is responsible for the unique 2D
+optoelectronic properties, such as electrostatic transparency
 \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
@@
 making it possible to separate the 2D and layered bulk materials from
-the $\eta-E_{\mathrm{g}}$ phase diagram.
+the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
+superimpose the dielectric anisotropy $\eta$ of common semiconducting
+materials in other dimensions (details see Supplementary Section SXX
+\todo{TBD}) on the phase diagram in Figure \ref{fig:aniso}. Bulk
+covalent materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$)
+show isotropic dielectric property, scattered on the line $\eta=1$. On
+the other hand, reduced dimensionality increases the dielectric
+anisotropy of materials such as planar organic semiconductor (OSc,
+1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
+e.g. polyacene). Interestingly, these materials also scatter along the
+boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
+2D (more anisotropic) and bulk layered materials (more isotropic) from
+the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
+dimensions. From the phase diagram, we can see that 2D and bulk
+layered materials (also including 2D van der Waals heterostructure
+(vdWH) \cite{Novoselov_2016}), provides more flexibility in
+controlling the dielectric and electronic properties, compared with semiconductors in other dimensions.
 
@@
   \centering
+  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
+  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
+      function of bandgap $E_{\mathrm{g}}$}. The
+    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
+    their bulk counterparts (orange square) can be distinguished by
+    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
+    semiconducting materials in other dimensions are also superimposed
+    for comparison. Isotropic dielectric property is observed for bulk
+    covalent materials (3D, red triangle) and fullerenes (0D, green
+    star), while reduced dimensional materials, including planar
+    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
+    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
+    scattered along the boundary line. The dimensionality and
+    structure of typical materials are shown along the axis on the
+    right. Compared with other materials, 2D materials and their bulk
+    counterparts provide more flexibility of controlling the
+    dielectric anisotropy.}
+  \label{fig:aniso}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
 \includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}

### 2018-10-30 paper.tex
Change the order for 2D-3D transition part

@@
 
-Apart from the universal Moss-like relations we propose for the
-dielectric nature of 2D materials, it is also of high theoretical
-interest to model the 2D-3D transition of dielectric properties. In
-other words, can we describe the dielectric constants
-$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
+The universal Moss-like relation shown in the previous sections
+provides general understanding of the dielectric nature of 2D
+materials. Moreover, the underlying physical mechanism allows us to
+further bridge the 2D and 3D dielectric and electronic properties. As
+described in the previous section, the 2D Moss-like relation between
+$\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss relation
+between $\varepsilon$ and $E_{g}$, with a different power law. Such
+difference in the power law can indeed be explained by modern theory
+of dielectric properties.  Extend the approach
+Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
+presentation for wavefunctions in all dimensions, we derive (detailed
+procedure see Supplementary Section S4):
+\begin{equation}
+  \label{eq:alpha-Eg-3D}
+  \begin{aligned}[t]
+  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
+  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
+  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
+\end{aligned}
+\end{equation}
+which recovers the 3D Moss relation. Therefore, the universal
+$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
+relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
+independence of effective mass is a result of the confinement
+perpendicular to the 2D plane.
+
+The relation between 2D polarizability and 3D dielectric constant
+shown in Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can
+be further used to reconstruct the dielectric
+constants $\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
 $\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
 $\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
-\ref{fig-4}a)? First, we see that the 2D polarizabilities for
+\ref{fig-4}a). First, we see that the 2D polarizabilities for
 individual layers in the bulk materials
@@
 controlling the dielectric and electronic properties, compared with semiconductors in other dimensions.
-
-\todo[inline]{I have some doubt how to handle the next paragraph, keep the status quo}
-As described in the previous section, the 2D Moss-like relation
-between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
-relation between $\varepsilon$ and $E_{g}$, with a different power
-law. Such difference in the power law can indeed be explained by
-modern theory of dielectric properties.  Extend the approach
-Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
-presentation for wavefunctions in all dimensions, we derive (detailed
-procedure see Supplementary Section S4):
-\begin{equation}
-  \label{eq:alpha-Eg-3D}
-  \begin{aligned}[t]
-  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
-  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
-\end{aligned}
-\end{equation}
-which recovers the 3D Moss relation. Therefore, the universal
-$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
-relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
-independence of effective mass is a result of the confinement
-perpendicular to the 2D plane.
 

### 2018-10-30 SI.tex
Add SI part to the anisotropy data

@@
 
+\subsection{Comparing dielectric anisotropy}
+The dielectric anisotropy $\eta$ proposed in the main text is also
+applied to other dimensions. Similar to the case of 2D and bulk
+layered materials, $\epsilon$ is used to compare the anisotropy when
+the material is periodic in all dimensions (bulk covalent materials),
+while the polarizability $\alpha$ is used for reduced dimensional
+materials.
+
+The following types materials are chosen for comparison:
+\begin{itemize}
+\item Bulk covalent materials.  \\
+  The list of materials and bandgap are chosen according to
+  Ref. \citenum{sze_appendix_2006}, including IV-IV, III-V, II-VI, and
+  IV-VI semiconductors. All these materials have isotropic dielectric
+  properties.
+\item Planar OSc \\
+  The planar OScs include metal phthanocyanines, disk-like polycyclic
+  aromatic hydrocarbon (PAHs), and benzene derivatives. The
+  dimensionality of these materials are close to 2D materials due to
+  their planar shape. The bandgap values (mostly at B3LYP density
+  functional with 6-31G** basis sets) are extracted from the NIST
+  Computational Chemistry Comparison and Benchmark Database
+  (http://cccdb.nist.gov, Release 19, April 2018) and the
+  polarizability values are obtained from
+  Refs. \citenum{Miller_1990,Ramprasad_2006}.
+\item Carbon nanotubes (CNT) \\
+  Like 2D materials, CNTs are periodic along the 1D directions, and
+  shoudl be treated in a similar way to get the polarizability
+  proportional to [Length]$^{2}$ \cite{Benedict_1995}. Semiconducting
+  zigzag and armchair CNTs are considered, with their electronic
+  properties obtained from Refs
+  \citenum{Benedict_1995,Matsuda_2010}. and dielectric properties
+  obtained from
+  Refs. \citenum{Benedict_1995,Jensen_2000,Brothers_2008}.
+\item Linear OSc \\
+  We choose the polyacenes (linear PAHs from benznene to nonacene) as
+  a model system of linear OScs. The bandgaps are obtained from
+  \citenum{Salzner_1998} and the polarizabilities are obtained from
+  \citenum{Hinchliffe_2005}.
+\item Fullerenes \\
+  The bandgap of fullerens (C$_{n}$ where $n=60*m^{2}$ where
+  $m=1\sim{}7$) are taken from \citenum{Lin_1994} and the
+  polarizabilities are taken from \citenum{Martin_2008}. All these
+  materials have isotropic polarizability due to the high symmetry.
+\end{itemize}
+
 \section{Raw data from first principles calculations}
-\subsection{Quantities from First Principles Calculation}
+\subsection{Quantities from first principles calculation}
 \label{sec:raw}
@@
 
-\subsection{Bandstructures of 2D Materials Calculated}
+\subsection{Bandstructures of 2D materials calculated}
 \label{sec:bs}

### 2018-10-30 paper.tex
Add SI part to the anisotropy data
Add implications for exp

@@
 superimpose the dielectric anisotropy $\eta$ of common semiconducting
-materials in other dimensions (details see Supplementary Section SXX
-\todo{TBD}) on the phase diagram in Figure \ref{fig:aniso}. Bulk
-covalent materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$)
-show isotropic dielectric property, scattered on the line $\eta=1$. On
-the other hand, reduced dimensionality increases the dielectric
-anisotropy of materials such as planar organic semiconductor (OSc,
-1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
+materials in other dimensions (details see Supplementary Section S4.5)
+on the phase diagram in Figure \ref{fig:aniso}. Bulk covalent
+materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$) show
+isotropic dielectric property, scattered on the line $\eta=1$. On the
+other hand, reduced dimensionality increases the dielectric anisotropy
+of materials such as planar organic semiconductor (OSc, 1D-2D,
+e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
 e.g. polyacene). Interestingly, these materials also scatter along the
@@
 (vdWH) \cite{Novoselov_2016}), provides more flexibility in
-controlling the dielectric and electronic properties, compared with semiconductors in other dimensions.
+controlling the dielectric and electronic properties, compared with
+semiconductors in other dimensions.
 
-\todo{First leave this part untouched}
-Finally, we would like to comment on the generality of the dielectric
-nature between the 2D and 3D worlds. As schematically shown in Figure
-\ref{fig-2D-3D}, the physical quantities related to the dielectric
-properties can be categorized into (i) strictly 2D (microscopic), (ii)
-strictly 3D (macroscopic) and (iii) valid both 2D and 3D.  $\alpha$
-and $\varepsilon$ are the starting point for the strictly 2D and 3D
-quantities, which require distinct definitions when dimensionality
-changes. Such quantities include (but not limited to):
+\subsection{Implications for Experiments}
+Finally, we would like to comment on the implications of this work for
+the experiments concerning the dielectric properties of 2D materials.
+As schematically shown in Figure \ref{fig-2D-3D}, the physical
+quantities related to the dielectric properties can be categorized
+into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
+(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
+starting point for the strictly 2D and 3D quantities, which require
+distinct definitions when dimensionality changes. Such quantities
+include (but not limited to):
 \begin{enumerate}
@@
   $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
-  details see Supplementary Section SXX \todo{TBD}).
+  details see Supplementary Section S4.4).
 
@@
 dimension-dependent and dimension-independent quantities.
+\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}
 
@@
 \label{sec:org5fd1f1a}
-
+\todo[inline]{To be changed later when everything fixed}
 To sum up, using first principles calculation for a large set of 2D

### 2018-11-12 paper.tex
Merge new fig1 and fig2 with the main text

@@
 \author{Manish Chhowalla}
-\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
+% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
+\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kindom}
 \author{Elton J. G. Santos}
@@
 \date{}
-\title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
+\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
+% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
 \begin{document}
@@
 
-\section{Introduction}
-\label{sec:org2ea169d}
+% \section{Introduction}
+% \label{sec:org2ea169d}
+\linenumbers{}
+
+{\bfseries Dielectric constant, which defines the polarization of the
+  media, is a key quantity in condensed matter. Here we show that
+  despite its fundamental transcendence, the dielectric constant does
+  not define unequivocally the dielectric properties of a
+  two-dimensional (2D) material. We found instead that the dielectric
+  polarizability correctly captures the dielectric nature of a 2D
+  material which is strongly dependent on the long-range
+  electron-electron interaction.  We reveal a long-sought universal
+  framework where electronic, geometrical and dielectric properties
+  are intrinsically correlated through the polarizability opening the
+  door to probe quantities yet not directly measurable, e.g. thickness
+  of an atom.  By using this framework, we unify the concept of
+  dielectric properties in any material dimension through a dielectric
+  anisotropy index which defines the degree of controllability of the
+  dielectric features of a compound. A universal boundary line
+  separates the 3D and 2D behaviors where materials likely to have
+  similar properties as layered materials collapsed onto.  }
 
@@
 relations between the dielectric constant $\varepsilon$ and other
-physical properties, in particular the band gap $E_{\mathrm{g}}$
-(minimal optical transition energy) of bulk
+physical properties, in particular the band gap $E_{\mathrm{g}}$ of bulk
 semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed

### 2018-11-12 paper.tex
Shorten the introduction part from Elton

@@
 model between the electronic and dielectric properties of materials.
-In fact, some pioneering work\cite{Moss_1950_relation} discovered
-relations between the dielectric constant $\varepsilon$ and other
-physical properties, in particular the band gap $E_{\mathrm{g}}$ of bulk
-semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
-that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
-relation, known as the Moss relation:
+% In fact, some pioneering work\cite{Moss_1950_relation} discovered
+% relations between the dielectric constant $\varepsilon$ and other
+% physical properties, in particular the band gap $E_{\mathrm{g}}$ of
+% bulk semiconductors.
+In fact, some pioneer
+work\cite{Moss_1950_relation,Moss_1985_n_Eg,Ravindra_1979_eps_Eg,Ravindra_2007_Eg_rev}
+proposed the empirical model between the energy bandgap
+$E_{\mathrm{g}}$ and dielectric constant $\varepsilon$ of bulk
+semiconductors, such as the famous Moss relation
+\cite{Moss_1950_relation,Moss_1985_n_Eg}:
 \begin{equation}
@@
 \end{equation}
-Other similar semi-empirical models for the relations between
-$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
-been proposed
-\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
-the minor difference between the formulae used, it is clear that there
-exists certain general electronic relations in bulk
-semiconductors. The existence of such general relationship is also of
-high practical importance: it is generally more straightforward and
-accurate to measure the band gap $E_{\mathrm{g}}$ than the static
-dielectric constant $\varepsilon$, as the latter is strongly dependent
-on several critical details on the sample measurements, such as
-contamination, disorder, and model interpretation. With the Moss
-relationship or other similar models, it is feasible to predict the
-dielectric constant of a bulk semiconductor with a reasonable degree
-of certainty.
-
-While the relations between the electronic and dielectric properties
-for bulk semiconductors are well-established, it is unknown if such
-equation still exists in low-dimensional materials. One important
-feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
-the electric screening is attenuated and anisotropic
-\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
-makes the empirical relations of dielectric constants in bulk
-materials, like the Moss relation invalid within the context of 2D
-materials. More critically, the static dielectric constant, a quantity
-associated with the macroscopic dielectric and optoelectronic
-properties and commonly obtained by theoretical calculations of 2D
-materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
-not well describe this microscopic and anisotropic dielectric nature
-of 2D materials
-\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
-accurate description of the 2D dielectric nature is the prerequisite
-for a 2D Moss-like relation, which could be used to make predictions
-for less-investigated layered crystals and to create materials design
-rules at an accurate level.  Here we show that instead of the
-dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
-correctly captures the dielectric nature of a 2D material for both
-in-plane and out-of-plane polarizations. Based on first principles
-simulation using highly accurate hybrid functionals and quantum
-mechanical models, we reveal the long-sought universal
-dielectric-scale relation in the 2D world: the in-plane polarizability
+Despite the minor difference between the empirical formulae proposed,
+such general relation  is of high
+practical importance for material design and engineering: with the
+Moss relationship or other similar models, it is feasible to predict
+the dielectric constant (and hence other parameters such as refractive
+index, Bohr radius, exciton binding energy, etc.) of a bulk material
+from the its bandgap with with a reasonable degree of certainty
+% The
+% existence of such general relationship is also of high practical
+% importance: it is generally more straightforward and accurate to
+% measure the band gap $E_{\mathrm{g}}$ than the static dielectric
+% constant $\varepsilon$ of a bulk material, as the latter is strongly
+% dependent on several critical details on the sample measurements, such
+% as contamination, disorder, and model interpretation.
+While the electronic-dielectric relation for bulk semiconductors is
+well-established, it is unknown if such equation still exists in
+atomically-thin two-dimensional (2D) materials \cite{Novoselov_2016},
+due to (i) the dielectric screening of a 2D material is attenuated and
+anisotropic
+\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}
+and (ii) the static dielectric constant, a quantity associated with
+the macroscopic dielectric and optoelectronic properties and commonly
+obtained by theoretical calculations of 2D materials
+\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
+describe this microscopic and anisotropic dielectric nature of 2D
+materials \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}.
+% Therefore, an
+% accurate description of the 2D dielectric nature is the prerequisite
+% for a 2D Moss-like relation, which could be used to make predictions
+% for less-investigated layered crystals and to create materials design
+% rules at an accurate level.
+Here we show that instead of the dielectric constant $\varepsilon$,
+the 2D polarizabilty $\alpha$ correctly captures the dielectric nature
+of a 2D material. Based on both theoretical model and first principle
+calculations, we reveal the long-sought universal dielectric scaling
+relations for 2D materials, depend both on the electronic and
+structural information: the in-plane polarizability
 $\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
@@
 $\alpha^{\perp}$ is directly related with the intrinsic thickness of
-2D materials. An analytical quantum-mechanical model is developed
-which give a sound background to the dielectric-scale
-relationships. Furthermore, such relations unify the dielectric
-properties between the 2D materials and their 3D counterparts in a
-natural manner, which ultimately pushes the boundary of the
-understanding of electronic screening in both dimensions. The
-discovery of scaling relationships between dielectric and electronic
-and structural properties in 2D compounds introduces a new and general
-pathway for the exploration of their complex physical and chemical
-phenomena well beyond the currently possible applications.
+2D materials. We further introduce the concept of dielectric
+anisotropy index, to unify 2D and 3D dielectric property. The proposed
+universal dielectric scaling relationships of 2D compounds introduce a
+general pathway for the exploration of their complex physical and
+chemical phenomena well beyond the currently possible applications.
+% Based on this
+% framework, we further unify the concept of dielectric properties of
+% any material dimension, by the dielectric anisotropy index, 
+% An analytical quantum-mechanical model is developed
+% which give a sound background to the dielectric-scale
+% relationships.
+% Using such unified relations unify the dielectric
+% properties between the 2D materials and their 3D counterparts in a
+% natural manner, which ultimately pushes the boundary of the
+% understanding of electronic screening in both dimensions.
+% The discovery of scaling relationships between dielectric and electronic
+% and structural properties in 2D compounds introduces a new and general
+% pathway for the exploration of their complex physical and chemical
+% phenomena well beyond the currently possible applications.
 
-\section{Results}
-\label{sec:org752ca78}
+% \section{Results}
+% \label{sec:org752ca78}
 

### 2018-11-12 paper.tex
Change section 2

@@
 % \label{sec:org2ea169d}
-\linenumbers{}
+% \linenumbers{}
 
@@
 $E_{\mathrm{g}}$, while the out-of-plane polarizability
-$\alpha^{\perp}$ is directly related with the intrinsic thickness of
-2D materials. We further introduce the concept of dielectric
-anisotropy index, to unify 2D and 3D dielectric property. The proposed
-universal dielectric scaling relationships of 2D compounds introduce a
-general pathway for the exploration of their complex physical and
-chemical phenomena well beyond the currently possible applications.
+$\alpha^{\perp}$ is directly related with the thickness
+$\delta$ of a 2D materials. We further introduce the concept of
+dielectric anisotropy index, to unify 2D and 3D dielectric
+property. The proposed universal dielectric scaling relationships of
+2D compounds introduce a general pathway for the exploration of their
+complex physical and chemical phenomena well beyond the currently
+possible applications.
 % Based on this
@@
 
-In persuit of the Moss-like relation of 2D materials, an accurate
-description of the dielectric properties of 2D materials needs to be
-established. One challenge is that the concept of macroscopic
-dielectric constant is ill-defined for 2D materials
+In pursuit of the Moss-like relation for 2D materials, an accurate
+description of their dielectric properties needs to be established,
+since the concept of macroscopic dielectric constant is ill-defined
+for 2D materials
 \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
@@
 z-direction separating the cell images. The macroscopic dielectric
-tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, is
+tensor from the superlattice $\varepsilon_{\mathrm{SL}}^{pq}$, is
 determined through fundamental electrostatics by the response of the
-polarization density $\boldsymbol{P}^{p}$, under small
-perturbative external field $\boldsymbol{E}^{q}$, where $p$, $q$ are
-the directions in $(x, y, z)$, such that:
+polarization density $\boldsymbol{P}^{p}$ under small perturbative
+external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the directions
+of polarization and electric field,
+respectively\cite{Dressel_2001_electrodynamics}:
 \begin{subequations}
@@
       \label{eq:def-eps-1}
-    &\varepsilon^{p} &= \kappa^{pq} +
+    &\varepsilon^{pq} &= \kappa^{pq} +
                                  {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
@@
 where $\kappa$ is the dielectric tensor of the environment,
-$\boldsymbol{u}$ is the total dipole moments of the SL, $\rho$ is the
-spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
-area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
-majority of 2D semiconductors, the off-diagonal elements of the
-dielectric tensor ($p \neq q$) tend to be negligible.  Considering
-that the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
-and $\kappa^{pq} = 0$, we can distinguish two components of the SL
-dielectric tensor, namely the in-plane
+$\boldsymbol{u} = {\displaystyle \int_{\mathrm{SL}}
+  \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}$ is the
+total dipole moments of the SL, $\rho$ is the spatial charge density,
+$\Omega=AL$ is the volume, $A$ is the xy-plane area of the SL and
+$\varepsilon_{0}$ is vacuum permittivity. For the majority of 2D
+semiconductors, the off-diagonal elements of the dielectric tensor
+($p \neq q$) tend to be negligible.  Considering that the 2D material
+is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
+distinguish two components, namely the in-plane
 ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
@@
 $\varepsilon_{\mathrm{SL}}^{\perp} =
-\varepsilon_{\mathrm{SL}}^{zz}$. Due to the absence of bonding along
-the z-direction, the induced charge density of a 2D material is highly
-confined in the xy-plane but delocalised along of the
-z-direction. Figure \ref{fig-1}a shows the charge density difference
+\varepsilon_{\mathrm{SL}}^{zz}$. The absense of bonding perpendicular
+to the 2D plane confines the induced dipoles along the
+\textit{z}-direction: as shown in Figure \ref{fig-1}a and
+Supplementary Figure SXX \todo{check}, the charge density difference
 between zero and finite electric fields,
@@
 z-axis for an isolated 2H-MoS$_{2}$ layer under
-$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which extends to
-$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough, the
-induced dipoles from periodic images do not overlap, and the total
-dipole moments $\boldsymbol{u}$ of the SL in Eq. \ref{eq:def-eps-2} is
-independent of $L$. As a consequence, we can see from
-Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
+$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$ only extends to
+$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough that
+the induced dipoles from periodic images do not interact,
+$\boldsymbol{u}$ equals the total dipole moments of a monolayer 2D
+materials and independent of the SL size. As a consequence, we can see
+from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
@@
 Te), in the top panels of Figure \ref{fig-1}b and \ref{fig-1}c,
-respectively. We observe that neither
-$\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
-$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
-that the long-range Coulomb interaction could not be completed
-screened within the range of magnitudes computationally accessible
-\cite{Hueser_2013_2Dvs3D}. The $L$-dependency of macroscopic
-dielectric constant makes it erroneous to use
-$\varepsilon_{\mathrm{SL}}$ to represent the dielectric nature of a 2D
-material. Therefore, we need to find a $L$-independent quantity to
-present the intrinsic dielectric properties of the 2D materials. As
-discussed previously, since the total dipole moments $\mathbf{u}$
-remain constant with $L$, we can define the surface or sheet
-polarization density matrix $\boldsymbol{\mu}$, by multiplying
-Eq. \ref{eq:def-eps-2} with $L$, such that
-$\boldsymbol{\mu}^{p} = \boldsymbol{P}^{p}L = \int_{\mathrm{SL}}
-\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$, which
-is independent of the superlattice size. Similar to the definition of
-molecular polarizability \cite{Israelachvili_2011}, the sheet
-polarization density $\boldsymbol{\mu}$ is associated with the 2D
-polarizability tensor $\alpha$ through:
-$\boldsymbol{\mu}^{p} = \sum_{q} \alpha^{pq}
-\mathbf{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
-$E_{\mathrm{loc}}$ is the local electric field. In the in-plane
-direction, the continuity of electric field gives
-$\mathbf{E}^{\parallel}_{\mathrm{loc}}=\mathbf{E}^{\parallel}$
+respectively.
+% We observe that neither
+% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
+% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
+% that the long-range Coulomb interaction could not be completed
+% screened within the range of magnitudes computationally accessible
+% \cite{Hueser_2013_2Dvs3D}.
+As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
+it impractical to represent the dielectric nature of a 2D material
+both theoretically and experimentally, because the size of vacuum
+layer must always be considered. To solve this problem, we need to
+find the $L$-independent alternative of
+$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
+Eq. \ref{eq:def-eps-2} with $L$ we get the sheet polarization density
+of a 2D material $\boldsymbol{\mu}_{\mathrm{2D}}$, such that
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \boldsymbol{P}^{p}L =
+\boldsymbol{u}^{p}/A$, which is dependent with $L$ due to the invariablity
+of $\boldsymbol{u}$ and $A$. Similar to the definition of molecular
+polarizability \cite{Israelachvili_2011},
+$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
+polarizability $\alpha_{\mathrm{2D}}$ through:
+$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
+\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
+$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. In the
+in-plane direction, the continuity of electric field gives
+$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
 \cite{Markel_2016}. Perpendicular to the 2D plane, the dipole
 screening yields
-$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}^{\perp}/L$
+$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
 \cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
@@
 expressions for the in-plane and out-of-plane 2D polarizabilities,
-$\alpha^{\parallel}$ and $\alpha^{\perp}$, respectively:
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$, respectively:
 \begin{subequations}
@@
   \label{eq:alpha-para-def}
-  &\alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
+  &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
   \label{eq:alpha-perp-def}
-    &\alpha^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
+  &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
 \end{eqnarray}
@@
 The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
-$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the TMDCs as functions of
-$L$, calculated using Eqs. \ref{eq:alpha-para-def} and
-\ref{eq:alpha-perp-def}. We observe that both $\alpha^{\parallel}$ and
-$\alpha^{\perp}$ remain almost constant when $L>$15 \AA{}. In
-addition, by varying the value of $\alpha^{\parallel}$ and
-$\alpha^{\perp}$, we can nicely reproduce the $L$-dependence of
-$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$ of the TMDCs, as shown Figure \ref{fig-1}d
-and \ref{fig-1}e, respectively. These findings indicate that the 2D polarizability,
-instead of the dielectric constant, is the true descriptor of the
-dielectric properties of 2D materials.
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+of the TMDCs as functions of $L$, calculated using
+Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
+that both $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ remain almost constant when $L>$15
+\AA{}. In addition, as shown Figure \ref{fig-1}d and \ref{fig-1}e,
+respectivel, the model-predicted
+$\varepsilon_{\mathrm{SL}}^{\parallel}-L$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}-L$ relations from Eqs.
+\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} nicely reproduce
+the trends from Figures \ref{fig-1}b and \ref{fig-1}c. These findings
+indicate that the 2D polarizability, instead of the dielectric
+constant, is the true descriptor of the dielectric properties of 2D
+materials. More discussion about the choice of the 2D polarizability
+and comparison with other methods can be find in Supplementary Section
+SXX \todo{xxx}.
 
-It is also worth mentioning that the dielectric properties of 2D
-materials are also often modeled using an effective medium approach,
-which treats the 2D material as a slab with effective permittivity
-$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
-\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
-methods require \textit{a priori} determination of $\delta$, a
-quantity with controversial definitions \cite{Mas_Ballest__2011}. In
-such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
-determined by fitting the $L$-dependent data of
-$\varepsilon_{\mathrm{SL}}$, which is not only computational
-expensive, but also fails to capture the anisotropy of the 2D
-dielectric properties (see Supplementary Section S1). On the other
-hand, calculating 2D polarizabilities requires no knowledge of
-$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
-\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
-dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
-the polarizability as the true descriptor of 2D dielectric properties,
-we will reveal the universal Moss-like relation of 2D materials from
-both theoretical and first principles studies.
+% It is also worth mentioning that the dielectric properties of 2D
+% materials are also often modeled using an effective medium approach,
+% which treats the 2D material as a slab with effective permittivity
+% $\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
+% \cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
+% methods require \textit{a priori} determination of $\delta$, a
+% quantity with controversial definitions \cite{Mas_Ballest__2011}. In
+% such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
+% determined by fitting the $L$-dependent data of
+% $\varepsilon_{\mathrm{SL}}$, which is not only computational
+% expensive, but also fails to capture the anisotropy of the 2D
+% dielectric properties (see Supplementary Section S1). On the other
+% hand, calculating 2D polarizabilities requires no knowledge of
+% $\delta$ (see Eqs. \ref{eq:alpha-para-def} and
+% \ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
+% dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
+% the polarizability as the true descriptor of 2D dielectric properties,
+% we will reveal the universal Moss-like relation of 2D materials from
+% both theoretical and first principles studies.
 
+\iffalse
 \subsection{Polarizability-Based Theoretical Model}
-In this section we theoretically investigate the existence of the 2D
-Moss-like relations, based on the 2D polarizability.  Due to its
-highly anisotropic nature, the wavefunction of an isolated 2D material
-$\psi(\mathbf{r})$ can be separated into the in- and out-of-plane
-components, similar to the treatment of quantum wells
-(QW),\cite{davies_physics_1997} such that
-$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
-$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
-is the in-plane coordinate. Using the Bloch theorem, the periodic
-$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
+\todo[inline]{In case of Nat. Nanotechnol., I would like to move all
+  theoretical information to SI}.
+Based on the 2D polarizability, we
+then theoretically investigate the potential existence of the
+Moss-like relations for 2D materials.  Due to its highly anisotropic
+nature, the wavefunction of an isolated 2D material $\psi(\mathbf{r})$
+can be separated into the in- and out-of-plane components, similar to
+the treatment of quantum wells (QW),\cite{davies_physics_1997} such
+that $\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such
+that $\psi=\psi^{\parallel}\psi^{\perp}$, where
+$\boldsymbol{\rho}=(x, y)$ is the in-plane coordinate. Using the Bloch
+theorem, the periodic $\psi^{\parallel}(\boldsymbol{\rho})$ can be
+further expressed as
 $\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
@@
 calculations.
+\fi
 
-\subsection{2D Moss Relations}
+\subsection{2D Moss Relations Based on 2D Polarizabilities}
 \label{sec:first-principles}
@@
 \centering
-\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
+\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
 \caption{\label{fig-1} \textbf{2D polarizability as the true
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
-\caption{\label{fig-2} The elements and 3D structures of the 2D
-  materials investigated in this study.}
-\end{figure}
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
+% \caption{\label{fig-2} The elements and 3D structures of the 2D
+  % materials investigated in this study.}
+% \end{figure}
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
+\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
 \centering
-\includegraphics[width=0.85\linewidth]{./img/fig4.pdf}
+\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties

### 2018-11-12 paper.tex
Change up to page 7

@@
 \cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
-Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we derive the
-expressions for the in-plane and out-of-plane 2D polarizabilities,
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$, respectively:
+Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
+\iffalse
 \begin{subequations}
@@
   &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
+\end{eqnarray}
+\end{subequations}
+\fi
+\begin{subequations}
+\begin{eqnarray}
+  \label{eq:alpha-para-def}
+  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
+  \label{eq:alpha-perp-def}
+  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
 \end{eqnarray}
@@
 
-\subsection{2D Moss Relations Based on 2D Polarizabilities}
+\subsection{2D Moss-like  Relations}
 \label{sec:first-principles}
-We study several types of 2D materials of different electronic and
-optical properties as show in Figure \ref{fig-2}, including transition
-metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
-where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
-monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
-(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
-(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
-phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
-(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
-2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
-2D polarizabilities are calculated from the static dielectric response
-of the selected 2D materials using density functional theory (DFT)
-with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
+Based on the 2D polarizabilities, we then investigate the potential
+Moss-like relations for 2D materials. By evaluating the expressions
+for $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
+theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
+treatment\cite{kittel_2005_introduction} (details see Supplementary
+Section SXX) \todo{note}, we show that
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+have simple relation with the electronic  and structural information of a 2D
+material, respectively:
+\begin{subequations}
+\begin{eqnarray}
+\label{eq:2D-Moss-para}
+  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
+  \label{eq:2D-Moss-perp}
+  &\alpha^{\perp} & \propto \delta
+\end{eqnarray}
+\end{subequations}
+where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
+material, and $\delta$ is its intrinsic
+thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
+the main conclusions of this work.
+
+To validate such relations, we study several types of 2D materials as
+show in Figure \ref{fig-3}a, including transition metal
+dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
+a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
+(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
+I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
+(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
+and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
+TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
+space group) and 1T (P3m1 space group).  The static 2D
+polarizabilities are calculated from the static dielectric response of
+the selected 2D materials using density functional theory (DFT) with
+the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
 Vienna Ab Initio Simulation Package (VASP) including spin-orbit
 coupling to avoid limitations on the description of band gaps and
-dielectric functions (see Methods for details).
-
-Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
-(blue dots) and polarizabilities (bar plots) of all the 2D materials
-investigated, covering a wide spectrum range from far infrared to
-ultraviolet. Note from dimension analysis, it is more intuitive to
-express the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which
-has unit of \AA. We find that $\alpha^{\parallel}$ has a general
+dielectric functions (see Methods for details). Figure \ref{fig-3}b
+shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
+(bar plots) of all the 2D materials investigated, covering a wide
+spectrum range from far infrared to ultraviolet. Note from dimension
+analysis, it is more intuitive to express the polarizability as
+$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
+\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
 descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
-no apparent trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
-observed (see Supplementary Section S2.2), which appears to be in good
-agreement with our polarizability-based theoretical model. We now
-validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
+no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
+$E_{\mathrm{g}}$ is observed (see Supplementary Section S2.2), which
+appears to be in good agreement with our polarizability-based
+theoretical model (Supplementary Section SXX \todo{note}). We then
+examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
 polarizabilities calculated by first principle calculations. Figure
-\ref{fig-3}b shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in
-\AA{}) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
-investiaged (circle dots), with a linear regression slope of ~0.182
-and $R^{2}$ of 0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope
-between $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
-$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
-yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
-studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
-eV) generally lie close to the regression line, while the deviation
-becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
-also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
-2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
-discover that the linearity between
-$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
-better when the bandgap is calculated using the HSE06 hybrid
-functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
-exchange correlations (details see Supplementary Section S2 and
-Supplementary Figure S5), which can be explained by the fact that the
-electronic structure, in particular the bandgap, is generally better
-predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
-noted that although even more accurate estimation of both
-$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
-Green’s function method (GW) together with the Bethe-Salpeter equation
-(BSE), the convergence of such method is known to be highly affected
-by the dielectric screening of 2D materials
+\ref{fig-3}b shows
+$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
+\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
+materials investiaged (circle dots), with a linear regression
+coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
+corresponds well with theoretical investigations
+\citenum{Jiang_2017_Eg_Eb} (details see Supplementary Section SXX
+\todo{format Jiang's paper into SI}).
+% From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
+% $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
+% $8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
+% yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
+% studied.
+% We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
+% eV) generally lie close to the regression line, while the deviation
+% becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
+% also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
+% 2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}.
+We also discover that the linearity between
+$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$
+(measured by the $R^{2}$ value) is higher when the bandgap is
+calculated using the HSE06 hybrid functionals, compared with that from
+the Perdew--Burk--Ernzerhof (PBE) exchange correlations (details see
+Supplementary Section S2 and Supplementary Figure S5), which can be
+explained by the fact that the electronic structure, in particular the
+bandgap, is generally better predicted at HSE06 level than PBE level
+\cite{Heyd_2005}. It should be noted that although even more accurate
+estimation of both dielectric properties and bandgap can be achieved
+via many-body Green’s function method (GW) together with the
+Bethe-Salpeter equation (BSE), the convergence of such method is known
+to be highly affected by the dielectric screening of 2D materials
 \cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
@@
 be most suitable to present the true 2D Moss-like relationship between
-$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$.
+\todo[inline]{check the values for optical bandgap}
 
@@
 is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
-in Figure \ref{fig-3}c, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$
-indeed shows an excellent linear correlation with
-$\delta_{\mathrm{cov}}$, with $R^{2}=0.98$, and the slope very close
-to $1/4\pi$. In addition to our theoretical predictions discussed
-above, the perfect linear correlation between $\alpha^{\perp}$ and
-$\delta_{\mathrm{cov}}$ has its strong physical meaning. Similar to
-the molecular polarizability which characterizes the volume of
-electron cloud of an isolated molecule \cite{Israelachvili_2011}, the
-2D polarizability also characterizes the volume of the electron cloud
-per unit area (from its definition), and naturally represents the
-thickness of the electron cloud of the 2D material. The fact that the
-thickness of the electron cloud can be approximated by the extension
-of valence states in the z-direction, explains the close match between
-the linear slope in Figure \ref{fig-3}c and $1/4\pi$ (see
-Supplementary Section S4.1). In other words, the universal scaling
-relation for $\alpha^{\perp}$ indicates the quantity
-$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
-thickness of a 2D material. We propose that the experimental
-measurment of the electronic polarizability
-\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
-extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
-estimation of it thickness, in comparison with the optical
-ellipsometry techniques \cite{Weber_2010} widely used to estimate the
-thickness of 2D materials, which requires empirical optical model and
-parameter fitting.
+in Figure \ref{fig-3}c,
+$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
+excellent linear correlation with $\delta_{\mathrm{cov}}$, with
+$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
+$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
+to $\delta_{\mathrm{cov}}$, which has its strong physical
+meaning. Similar to the molecular polarizability which characterizes
+the volume of electron cloud of an isolated molecule
+\cite{Israelachvili_2011},
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
+volume of the electron cloud per unit area (from its definition), and
+is naturally proportional to the electron cloud thickness of the 2D
+material (see Supplementary Section SXX). In fact, the universal
+scaling relation for $\alpha^{\perp}$ in Figure \ref{fig-3}c indicates
+that the quantity $\alpha^{\perp}/\varepsilon_{0}$ measurable via
+electronic approaches
+\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
+(dielectric) characteristic thickness of a 2D material, and can be
+used to resolve the long-existing controversy about the experimental
+thickness of 2D materials, such as graphene \cite{Shearer_2016}.
 
-The universal relations of 2D polarizabilities are not
-coincidence. Combining recent theoretical findings of the linear
-relation between exciton binding energy $E_{\mathrm{b}}$ and
-$E_{\mathrm{g}}$ of 2D materials
+\iffalse
+The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
+and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
+theoretical findings of the linear relation between exciton binding
+energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
 \cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
@@
 carbon nanotubes \cite{Benedict_1995}, which are also shown to be
-geometry-dependent. To rule out the possibility that our conclusion is
-limited by the number of materials used, we further validate our
-proposed 2D Moss-like relations on the recently-published C2DB
-database \cite{Haastrup_2018}, from which we extracted the dielectric
+geometry-dependent.
+\fi
+
+To rule out the possibility that our conclusion is limited by the
+number of materials used, we further validate our proposed 2D
+Moss-like relations on the recently-published C2DB database
+\cite{Haastrup_2018}, from which we extracted the dielectric
 properties of over 230 2D materials calculated at the PBE level, and
-overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
-(further details see Supplementary Section S3). Althought the
-dielectric properties may be overestimated at PBE level due to
-underestimation of the bandgap compared with the more accurate HSE06
-functionals, apparent linear trends can be observed for both
-$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
-very close to the HSE06 results. Therefore, the proposed universal 2D
-Moss-like relations are confirmed.  We have also tested the potential
-relation between the 2D polarizabilities with other physical
-quantities, including the effective carrier mass, quantum capacitance
-and total atomic polarizabilities, while no apparent correlations are
-found (details see Supplementary Section S3).
+superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
+(details see Supplementary Section S3). Althought the dielectric
+properties may be overestimated at PBE level due to underestimation of
+the bandgap compared with the more accurate HSE06 functionals
+\cite{Van_Dyck_2017}, similar linear trends can be observed for both
+$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
+with the linear coefficient very close to the HSE06 results. We have
+also tested the potential relation between the 2D polarizabilities
+with other physical quantities, including the effective carrier mass,
+quantum capacitance and total atomic polarizabilities, while no
+apparent correlations are found (details see Supplementary Section
+S3).
 
@@
 theoretical modeling and first principles calculations:
-$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
-$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
-thickness of the 2D material. Although their apparent forms in
-Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
-will show the 2D Moss-like relations stem from the same origin. In
-merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
-both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
-$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
-characteristic lengthes in- and out-of-plane, respectively. The
-in-plane screened electrostatic potential $V(r)$ from a point charge
-in an 2D plane, as a function of distance $r$:
+$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
+minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
+is the characteristic thickness of the 2D material. Next we show,
+despite their different forms, both 2D Moss-like relations stem from
+the same origin. In merit of the unit analysis,
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
+words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
+characteristic lengthes, respectively. The in-plane screened
+electrostatic potential $V(r)$ from a point charge in an 2D plane, as
+a function of distance $r$:
 $V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
@@
 function and $Y_{0}$ is the Bessel function of second kind, is
-assciated with the in-plane screening radius
-$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
-$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
-potential in vacuum. Combining with the result that the thickness of
-2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
-have drawn a generalized picture of the dielectric nature of 2D
-materials via the 2D polarizability: the dielectric screening of a
-point charge sitting in the middle of a 2D material can be viewed as
-an ellipsoid with the length of principle axes to be
-$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
-$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
-polarizability ellipsoid picture of molecules used in spectroscopy
-\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
-screening length is generally larger for a smaller bandgap
-semiconductor, which qualitatively explains the inverse propotional
-relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
-version of the Moss-relation.
+associated with the in-plane screening radius
+$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
+\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
+to the simple Coulombic potential in vacuum. Combining with the result
+that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
+thickness of a 2D material, we have drawn a generalized picture of the
+dielectric nature of 2D materials via the 2D polarizability: the
+dielectric screening of a point charge sitting in the middle of a 2D
+material can be viewed as an ellipsoid with the length of principle
+axes to be
+$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
+\varepsilon_{0})$ and
+$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
+respectively, analog to the polarizability ellipsoid picture of
+molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
+Figure S12). The polarizability ellipsoid for a 2D material is in
+general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
+can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
+Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
+bandgap semiconductor, which qualitatively explains the inverse
+propotional relation between $\alpha^{\parallel}$ and
+$E_{\mathrm{g}}$, a 2D version of the Moss-relation.
 
@@
   % \end{figure}
+\begin{table}[htbp]
+  \centering
+  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
+    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
+    selected 2D materials calculated from first principles
+    simulations. $r_{0}^{\parallel}$ is in general much larger than
+    $r_{0}^{\perp}$, which accounts for the highly anisotropic
+    dielectric nature of 2D materials.}
+  \label{tbl:radii}  
+  \begin{tabular}[htbp]{lcc}
+    \hline
+    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
+    \hline
+    2H-MoS$_{2}$ & 40.0 & 2.50 \\
+    2H-MoSe$_{2}$ & &  \\
+    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
+    2H-WS$_{2}$ & 35.7 & 2.46  \\
+    2H-WSe$_{2}$ & 41.0 & 2.71 \\
+    2H-WTe$_{2}$ & 53.5 &  3.17\\
+    \hline
+  \end{tabular}
+\end{table}
 

### 2018-11-13 paper.tex
Change until the anisotropy part

@@
 % \label{sec:org2ea169d}
-% \linenumbers{}
+\linenumbers{}
 
@@
 bandgap semiconductor, which qualitatively explains the inverse
-propotional relation between $\alpha^{\parallel}$ and
+propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
 $E_{\mathrm{g}}$, a 2D version of the Moss-relation.
@@
 materials. Moreover, the underlying physical mechanism allows us to
-further bridge the 2D and 3D dielectric and electronic properties. As
-described in the previous section, the 2D Moss-like relation between
-$\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss relation
-between $\varepsilon$ and $E_{g}$, with a different power law. Such
-difference in the power law can indeed be explained by modern theory
-of dielectric properties.  Extend the approach
-Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
-presentation for wavefunctions in all dimensions, we derive (detailed
-procedure see Supplementary Section S4):
-\begin{equation}
-  \label{eq:alpha-Eg-3D}
-  \begin{aligned}[t]
-  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
-  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
-\end{aligned}
-\end{equation}
-which recovers the 3D Moss relation. Therefore, the universal
-$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
-relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
-independence of effective mass is a result of the confinement
-perpendicular to the 2D plane.
+further bridge the 2D and 3D dielectric and electronic properties in
+various ways. Using the similar appraoch as we derive the 2D Moss-like
+relations, we show that the
+$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
+relation for a 2D material naturally transforms to
+$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
+semiconductor, which is the original Moss relation (details see
+Supplementary Section SXX \todo{note}). In other words, the proposed
+$\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is indeed
+the Moss relation in 2D world, while the different power law for
+$E_{\mathrm{g}}$ is caused by the electronic confinement.
 
-The relation between 2D polarizability and 3D dielectric constant
-shown in Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can
-be further used to reconstruct the dielectric
-constants $\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
-$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
-$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
-\ref{fig-4}a). First, we see that the 2D polarizabilities for
-individual layers in the bulk materials
-$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
-$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
-Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
-becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
-dielectric constants of the bulk material are then expressed as:
+% As described in the previous section, the 2D Moss-like relation
+% between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
+% relation between $\varepsilon$ and $E_{g}$, with a different power
+% law. Such difference in the power law can indeed be explained by
+% modern theory of dielectric properties.  Extend the approach
+% Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
+% presentation for wavefunctions in all dimensions, we derive (detailed
+% procedure see Supplementary Section S4):
+% \begin{equation}
+  % \label{eq:alpha-Eg-3D}
+  % \begin{aligned}[t]
+  % \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
+  % \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
+  % {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
+  % &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
+% \end{aligned}
+% \end{equation}
+% which recovers the 3D Moss relation.
+
+The dielectric constant $\varepsilon$, although not well-defined for
+monolayer 2D material, becomes applicable when the 2D layers are
+stacked. \todo[inline]{I would appreciate for polishing this sentence}
+In a bulk layered materil stacked by layers with equilibrium
+inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
+of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
+$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
+\ref{eq:alpha-perp-def}, the dielectric constants
+$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
+$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
+be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
+$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
 \begin{subequations}
-\begin{eqnarray}
+\begin{align}
   \label{eq:3D-para}
-  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
+  \varepsilon^{\parallel}_{\mathrm{Bulk}}
+  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
+  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
   \label{eq:3D-perp}
-  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
-\end{eqnarray}
+  \varepsilon^{\perp}_{\mathrm{Bulk}}
+  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
+  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
+\end{align}
 \end{subequations}
-Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
-$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
-$\alpha$ of isolated layer, but still quite close as seen in Figure
-\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
-we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
-$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
-$\alpha_{\mathrm{bulk}}=\alpha$. We compare
+The approximations come from the fact that
+$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
+seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
+that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
+and \ref{eq:3D-perp}. We compare the values of
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
-$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
-calculations compared with the values predicted using Eqs
-\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
-and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
-levels which give almost identical trends, indicating the generality
-of such approach. Note although the stacking order is not considered
-in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
-influence of stacking is minor (see Supplementary Figure SXX
-\todo{Wait for Declan's data}). We observe that the majority of
-predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
-the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
-0.97, indicating that such method indeed captures the transition from
-$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
-the other hand, we observe the predicted values of
-$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
-values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
-when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
+$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
+with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
+(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
+respectively, with data calculated at both HSE06 and PBE levels give
+almost identical trends. We observe that
+$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
+predicted by Eq. \ref{eq:3D-para} align along the line $y=x$ , with a
+linear regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
+$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
+Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
+$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
+$E_{\mathrm{g}}$ reduces. The difference for the prediction of
 $\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
@@
 its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
-to interlayout coupling and overlap between induced dipoles, as also
-observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
-\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
-describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
-$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
-be smoothly described.
+to interlayout coupling and overlap between induced
+dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
+in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
+$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha^{\perp}$ and
+the degree of interlayer coupling, the dielectric transition from 2D
+to 3D would be smoothly described.
 

### 2018-11-13 paper.tex
Change the anisotropic part

@@
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
-predicted by Eq. \ref{eq:3D-para} align along the line $y=x$ , with a
-linear regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
+predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
+regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
 $\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
@@
 $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
-$E_{\mathrm{g}}$ reduces. The difference for the prediction of
-$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
+$E_{\mathrm{g}}$ reduces. The above results indicate that
 $\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
@@
 in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
-$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha^{\perp}$ and
+$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
 the degree of interlayer coupling, the dielectric transition from 2D
@@
 
-Although we have extensively shown that the treatment for the
-dielectric nature differs in 2D (polarizability) and 3D (dielectric
-constant) scenarios, a general picture of the dielectric properties in
-both dimensions can still be drawn by studying the dielectric
-anisotropy. The dielectric anisotropy index $\eta$ is defined as:
+Finally, we show that a general picture of the dielectric properties in
+both dimensions can be drawn by studying the dielectric
+anisotropy. We define the dielectric anisotropy index $\eta$ as:
 \begin{equation}
@@
 counterparts. Interestingly, the 2D materials (blue triangle) can be
-clearly distinguished from the bulk layered materials (orange
-square). The boundary separating the 2D and layered bulk materials is
-determined using an linear support vector machine (SVM) classification
-algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
-materials compared with their bulk counterparts indicates a high
-dielectric anisotropy, which is responsible for the unique 2D
-optoelectronic properties, such as electrostatic transparency
-\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
-\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
-also observe that $\eta$ of 2D materials increase almost linearly with
-$E_{\mathrm{g}}$, while such trend is absent for layered bulk
-materials. The observations above can be explained by the principles
-presented in thie work. As a result from the limited layer thickness
-(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
-varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
-\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
-$\eta$ of 2D materials. On the other hand, the fact that
-$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
-values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
-coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
-layered bulk materials compared with the corresponding monolayer, and
-making it possible to separate the 2D and layered bulk materials from
-the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
-superimpose the dielectric anisotropy $\eta$ of common semiconducting
-materials in other dimensions (details see Supplementary Section S4.5)
-on the phase diagram in Figure \ref{fig:aniso}. Bulk covalent
-materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$) show
-isotropic dielectric property, scattered on the line $\eta=1$. On the
-other hand, reduced dimensionality increases the dielectric anisotropy
-of materials such as planar organic semiconductor (OSc, 1D-2D,
-e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
-e.g. polyacene). Interestingly, these materials also scatter along the
-boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
-2D (more anisotropic) and bulk layered materials (more isotropic) from
-the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
-dimensions. From the phase diagram, we can see that 2D and bulk
-layered materials (also including 2D van der Waals heterostructure
-(vdWH) \cite{Novoselov_2016}), provides more flexibility in
-controlling the dielectric and electronic properties, compared with
-semiconductors in other dimensions.
+clearly distinguished from the bulk layered materials (orange square)
+with the boundary line determined to be
+$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
+$\eta$ values for 2D materials compared with their bulk counterparts
+indicates a high dielectric anisotropy, which is responsible for the
+unique 2D optoelectronic properties, such as electrostatic
+transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
+binding energy
+\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
+Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
+\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
+$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
+$\eta$ for 2D materials increase almost linearly with
+$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
+\AA{}) of the 2D materials investigated varies much less than
+$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
+\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
+index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
+$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
+    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
+\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
+of corresponding 2D layer (details see Supplementary Section SXX
+\todo{note}), which is the basis for the separation of bulk and 2D
+regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
+we also superimpose the dielectric anisotropy indices $\eta$ of common
+semiconducting materials in other dimensions (details see
+Supplementary Section S4.5) on the phase diagram in Figure
+\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
+semiconductors show isotropic dielectric properties, scattered on the
+line $\eta=1$. On the other hand, reduced dimensionality increases the
+dielectric anisotropy of materials such as planar organic
+semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
+linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
+most of these materials also scatter along the boundary line
+separating the bulk and 2D regimes, indicating the criteria
+distinguishing 2D (more anisotropic) and bulk layered materials (more
+isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
+to other dimensions. From the phase diagram, we can see that 2D and
+bulk layered materials (also including 2D van der Waals
+heterostructure (vdWH) \cite{Novoselov_2016}), provides more
+flexibility in controlling the dielectric and electronic properties,
+compared with semiconductors in other dimensions.  \todo[inline]{I
+  leave this section to be freely modified}
 
 \subsection{Implications for Experiments}
+\todo[inline]{Wait for comments from JC and MC.}
+\iffalse
 Finally, we would like to comment on the implications of this work for
@@
 \todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}
+\fi
 
@@
 \label{sec:org34cbe74}
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
   % \end{figure}
-\begin{table}[htbp]
+\begin{table}[H]
   \centering
@@
   \label{tbl:radii}  
-  \begin{tabular}[htbp]{lcc}
+  \begin{tabular}{lcc}
     \hline
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering

### 2018-11-13 src/VASP_HSE/alpha_alpha.py
Add more data for anisotropy

@@ -172,8 +172,9 @@ marks = {"CNT": "o",
          "polyacene": "p",
          "MPc": "<",
          "covalent": ">",
-         "fullerene": "*"}
-for f in ["CNT", "covalent", "polyacene", "MPc", "fullerene"]:
+         "fullerene": "*",
+         "polyacetylene": "D"}
+for f in ["CNT", "covalent", "polyacene", "MPc", "fullerene", "polyacetylene"]:
     f_name = "../../data/other_dimension/{}.csv".format(f)
     Eg, anis = anis_from_file(f_name)
     ax.scatter(Eg, anis, label=f,

### 2018-11-13 src/gpaw_analysis/alpha_opt_gap.py
Add comparison with optical bandgap

@@ -1,0 +1,52 @@
+import ase.db
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+import os, os.path
+from scipy.constants import pi, epsilon_0
+
+db_file = "../../data/gpaw_data/c2db.db"
+if not os.path.exists(db_file):
+    raise FileExistsError(("Please download the c2db data into ../../data/gpaw_data/ folder,"
+                   "from https://cmr.fysik.dtu.dk/_downloads/c2db.db"))
+
+
+db = ase.db.connect(db_file)
+
+candidates = db.select(selection="bse_binding>0,dir_gap_gw>0,alphax>0")
+
+materials = []
+alpha_x = []
+E_opt = []
+
+for mol in candidates:
+    if "Cr" in mol.formula:     # CrS2 stuffs are not correct?
+        continue
+    print("{0}-{1}".format(mol.formula, mol.prototype))
+    materials.append("{0}-{1}".format(mol.formula, mol.prototype))
+    alpha_x.append((mol.alphax + mol.alphay) / 2)
+    E_opt.append(mol.dir_gap_gw - mol.bse_binding)
+
+alpha_x = numpy.array(alpha_x)
+E_opt = numpy.array(E_opt)
+
+img_path = "../../tmp_img/"
+plt.style.use("science")
+
+
+
+# x-direction
+plt.figure(figsize=(3.5, 3.5))
+plt.plot(E_opt, 1 / (alpha_x), "o", alpha=0.5)
+k, b, r, *_ = linregress(x=E_opt, y=1 / alpha_x)
+print(k, b, r)
+xx = numpy.linspace(0.0, 8)
+yy = k * xx + b
+plt.xlim(0, 8)
+plt.plot(xx, yy, "--")
+plt.xlabel("$E_{\\rm{g}}^{\\rm{opt}}$ (eV)")
+plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha_{\parallel}$ ($\\AA^{-1}$)")
+plt.savefig(os.path.join(img_path, "alpha_x_E_opt.svg"))
+

### 2018-11-13 src/VASP_HSE/plot_alpha_QC.py
Change all alpha to alpha_2D in the plotting scripts

@@ -24,28 +24,28 @@ plt.style.use("science")
 plt.figure(figsize=(3.5, 3.5))
 plt.plot(data[:, -2], data[:, 1], "o")
 plt.xlabel("$C_{\\mathrm{Q}}^{\mathrm{C}}$ ($\\mathrm{\\mu F} \\cdot \\mathrm{cm}^{-2}$)")
-plt.ylabel("$\\alpha^{\\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\parallel}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.xscale("log")
 plt.savefig("../../tmp_img/alpha_xx_QC_n.svg")
 
 plt.figure(figsize=(3.5, 3.5))
 plt.plot(data[:, -1], data[:, 1],"o")
 plt.xlabel("$C_{\\mathrm{Q}}^{\\mathrm{V}}$ ($\\mathrm{\\mu F} \\cdot  \\mathrm{cm}^{-2}$)")
-plt.ylabel("$\\alpha^{\\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\parallel}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.xscale("log")
 plt.savefig("../../tmp_img/alpha_xx_QC_p.svg")
 
 plt.figure(figsize=(3.5, 3.5))
 plt.plot(data[:, -2], data[:, 2],"o")
 plt.xlabel("$C_{\\mathrm{Q}}^{\mathrm{C}}$ ($\\mathrm{\\mu F} \\cdot \\mathrm{cm}^{-2}$)")
-plt.ylabel("$\\alpha^{\\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\perp}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.xscale("log")
 plt.savefig("../../tmp_img/alpha_zz_QC_n.svg")
 
 plt.figure(figsize=(3.5, 3.5))
 plt.plot(data[:, -1], data[:, 2],"o")
[…]

### 2018-11-13 src/gpaw_analysis/alpha_EG_compare.py

@@ -104,7 +104,7 @@ for i, data in enumerate((Eg_HSE, Eg_PBE, Eg_GW)):
     plt.plot(xx, yy, "--", color=l2.get_c())
     plt.xlabel("$E_{\\rm{g}}$ (eV)")
     plt.title(candidates[i])
-    plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha_{\parallel}$ ($\\AA^{-1}$)")
+    plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha^{\\parallel}_{\\rm{2D}}$ ($\\AA^{-1}$)")
     plt.legend()
     plt.savefig(os.path.join(img_path, "gpaw_alphaxx_all_Eg_{}.svg").format(candidates[i]))
 

### 2018-11-13 src/gpaw_analysis/alpha_mass.py

@@ -81,28 +81,28 @@ plt.xlim(0.05, 1.5)
 
 l2, *_ = plt.plot(emass, alpha_x, "o", alpha=0.4)
 plt.xlabel("$m_{e}^{*}/m_0$ ")
-plt.ylabel("$\\alpha^{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\parallel}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphaxx_emass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(hmass, alpha_x, "o", alpha=0.4)
 plt.xlabel("$m_{h}^{*}/m_0$ ")
-plt.ylabel("$\\alpha^{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\parallel}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphaxx_hmass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(emass, alpha_z, "o", alpha=0.4)
 plt.xlabel("$m_{e}^{*}/m_0$ ")
-plt.ylabel("$\\alpha^{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\perp}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphazz_emass.svg"))
 
 plt.figure(figsize=(3.5, 3.5))
 plt.xlim(0.05, 1.5)
 l2, *_ = plt.plot(hmass, alpha_z, "o", alpha=0.4)
 plt.xlabel("$m_{h}^{*}/m_0$ ")
-plt.ylabel("$\\alpha^{\perp}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
[…]

### 2018-11-13 src/gpaw_analysis/alpha_opt_gap.py

@@ -47,6 +47,6 @@ yy = k * xx + b
 plt.xlim(0, 8)
 plt.plot(xx, yy, "--")
 plt.xlabel("$E_{\\rm{g}}^{\\rm{opt}}$ (eV)")
-plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha_{\parallel}$ ($\\AA^{-1}$)")
+plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha^{\parallel}_{\\rm{2D}}$ ($\\AA^{-1}$)")
 plt.savefig(os.path.join(img_path, "alpha_x_E_opt.svg"))
 

### 2018-11-13 src/gpaw_analysis/alpha_relation.py

@@ -102,7 +102,7 @@ xx = numpy.linspace(0.3, 8)
 yy = k * xx + b
 plt.plot(xx, yy, "--")
 plt.xlabel("$E_{\\rm{g}}$ (eV)")
-plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha_{\parallel}$ ($\\AA^{-1}$)")
+plt.ylabel("$(4 \\pi \\varepsilon_0)/\\alpha^{\parallel}_{\\rm{2D}}$ ($\\AA^{-1}$)")
 plt.savefig(os.path.join(img_path, "alpha_xx_1_Eg.svg"))
 
 # z-direction
@@ -117,7 +117,7 @@ yy = k * xx + b
 plt.plot(xx, yy, "--")
 # plt.plot(xx, yyy, "--")
 plt.xlabel("Thickness ($\\AA$)")
-plt.ylabel("$\\alpha_{\\perp} / (4 \pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\perp}_{\\rm{2D}} / (4 \pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "alpha_zz_thick.svg"))
 
 #x-direction
@@ -131,9 +131,9 @@ plt.plot(polar, alpha_z, "o", alpha=0.5)
 # yyy = 1 / (4 * pi) * xx - 0.05
 # plt.plot(xx, yy, "--")
 # plt.plot(xx, yyy, "--")
-plt.text(x=2, y=10, s="$\\alpha^{\\perp} = \\frac{\\hbar^2 e^2 \\rho_e}{m_e E_{\mathrm{g}}^2}$")
+plt.text(x=2, y=10, s="$\\alpha^{\\perp}_{\\rm{2D}} = \\frac{\\hbar^2 e^2 \\rho_e}{m_e E_{\mathrm{g}}^2}$")
 plt.xlabel("Total Atomic Polarizability per Area (Bohr$^3$)")
-plt.ylabel("$\\alpha^{\\perp} / (4 \pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\\perp}_{\\rm{2D}} / (4 \pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "alpha_zz_polar.svg"))
 
 # z-direction with atomic polarizability
[…]

### 2018-11-13 src/gpaw_analysis/alpha_valence.py

@@ -80,7 +80,7 @@ xx = numpy.linspace(min(omega_Eg), max(omega_Eg))
 plt.plot(xx, 10.97 * xx, "--")
 plt.xlim(0, 5)
 plt.ylim(0, 20)
-plt.text(x=2, y=10, s="$\\alpha^{\\parallel}=\\frac{\\hbar^2 e^2 \\sigma_{\\mathrm{2D}}^{\\mathrm{V}}}{m_e E_{\mathrm{g}}^2}$")
+plt.text(x=2, y=10, s="$\\alpha^{\\parallel}_{\\rm{2D}}=\\frac{\\hbar^2 e^2 \\sigma_{\\mathrm{2D}}^{\\mathrm{V}}}{m_e E_{\mathrm{g}}^2}$")
 plt.xlabel("$\\sigma^{\mathrm{V}}_{\mathrm{2D}}/E_{\mathrm{g}}^{2}$ ($\\AA^{-2}$∙eV$^{-2}$) ")
-plt.ylabel("$\\alpha^{\parallel}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
+plt.ylabel("$\\alpha^{\parallel}_{\\rm{2D}}/(4 \\pi \\varepsilon_0)$ ($\\AA$)")
 plt.savefig(os.path.join(img_path, "gpaw_alphaxx_omega_Eg.svg"))

### 2018-11-15 SI.tex
Add optical bandgap in SI

@@
 \usepackage{times}
+\usepackage{float}
 \usepackage{amsmath}
@@
 
-\usepackage{float}
+\usepackage{xr}
+\externaldocument[main-]{paper}
 
@@
 
-\section{Hypothetical 2D dielectric constant rescaled from 3D dielectric constant}
+\newpage{}
+\section{Further Analysis of the 2D Polarizability Model}
+\label{sec:2D-pol}
+
+In this section, we discuss further topics about the 2D polarizability
+model proposed in the main text.
+
+\subsection{Profile of induced dipoles of 2D material}
+\label{sec:dipole-plot}
+Here we show in detail the
+$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
+the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}a. The
+density $\rho$ is calculated as the average value in the
+\textit{xy}-plane, and the value is shown in Figure
+\ref{fig:rho-profile}. As can be seen the induced charges on the
+MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
+SL size $L \gg$12 \AA{} as in the first principle calculations done in
+the main text, the induced dipoles from the periodic images do not
+interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
+  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
+    superlattice, corresponding to main text Figure
+    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
+    inside the SL separated by vacuum layer. The dielectric constant
+    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
+    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
+    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
+    MoS$_{2}$ layer, green and red parts corresponding to negative and
+    positive induced charges. The external electric field
+    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
+  \label{fig:rho-profile}
+\end{figure}
+
+\subsection{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
 \label{sec:2D-3D-rescale}
-
 From literatures, it is often desired to extract the ``dielectric
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{img/SI-rescale-PRB.pdf}
+  \includegraphics[width=0.85\linewidth]{img/SI-rescale-PRB.pdf}
   \caption{ Calculated (blue dots) and fitted
@@
   \hline{}
-  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha^{\perp}/\varepsilon_{0}$ ({\AA})\\
+  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
   \hline{}
@@
   covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
-  $\alpha^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
+  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
 \label{tab:delta-L-DFt}
@@
 smaller perpendicular to the 2D plane. In fact, combining
-Eq. \ref{eq:MG-effect-1} and the definition of $\alpha^{\perp}$, we
+Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
 have:
@@
   \label{eq:eps-alpha-perp}
-  \frac{\alpha^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
+  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
 \end{equation}
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{img/SI-eps-alpha-error.pdf}
+  \includegraphics[width=0.6\linewidth]{img/SI-eps-alpha-error.pdf}
   \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
     function of the difference between $\delta_{\mathrm{2D}}$ and
-    $\alpha^{\perp}/\varepsilon_{0}$. A small change of
-    $\alpha^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
+    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$. A small change of
+    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
     the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
@@
 which indicate that the characteristic length
-$\alpha^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
 than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
@@
 Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
-$\alpha^{\perp}/\varepsilon_{0}$ are close, slight change of the
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
 $\delta_{\mathrm{2D}}$ chosen may lead to divergence of
@@
 \begin{enumerate}
-\item $\alpha$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
-\item Calculating $\alpha$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
-\item $\alpha$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
-\item $\alpha$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.
+\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
+\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
+\item $\alpha_{\mathrm{2D}}$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
+\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.
 
@@
   choice of the thickness of 2D material, while such information is
-  intrinsically embedded in $\alpha$.
+  intrinsically embedded in $\alpha_{\mathrm{2D}}$.
 \end{enumerate}
 
-\section{Further analysis of the 2D polarizability}
-\label{sec:pol-2D}
-
-In this section we will provide more analysis on the 2D polarizability
-in addition to the main text.
-
-\subsection{Dependence of superlattice size}
-\label{sec:pol-2D-1}
-
-We study the polarizabilties of group 6 TMDCs to demonstrate the
-dependency between the 2D polarizability $\alpha$ and the superlattice
-length $L$, which is shown in Figure \ref{fig:eps-L-all}.  In all cases, we observe that the calculated
-polarizability converges when $L>$15 \AA{}, in good agreement with our
-conclusion in main text. The lower bound of $L_{\mathrm{min}}$ for the
-convergence of $\alpha$ can be viewed as the minimal distance that
-overlap of induced charge density from image layers is negligible. In
-practice, any superlattice size larger than $L_{\mathrm{min}}$ can be
-used for calculating the intrinsic 2D dielectric nature through the
-polarizability, however to reduce the computational cost, especially
-at the HSE06 level, we typically choose a superlattice size no larger
-than 35 \AA{}.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.95\linewidth]{img/SI-eps-L-all.pdf} 
-  \caption{Calculated value of $\varepsilon_{\mathrm{SL}}^{\parallel}$
-    (top left axis), $\varepsilon_{\mathrm{SL}}^{\perp}$ (bottom left
-    axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
-    (bottom right axis) of various group 6 TMDCs corresponding to
-    Figure 1 in main text. In all cases, the polarizability converges
-    when $L>$15 \AA{}}
-  \label{fig:eps-L-all}
-\end{figure}
-
-\subsection{Dependence of bandgap}
-\label{sec:pol-2D-2}
+\subsection{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
+\label{sec:pol-2D-Eg}
 
 In this section we further look into the bandgap dependency of the 2D
-polarizability. Figure \ref{fig:SI-raw-HSE} shows $\alpha^{\parallel}$
-and $\alpha^{\perp}$ as functions of $E_{\mathrm{g}}$ of the 2D
-materials studied here. We observe that $\alpha^{\parallel}$ can be
-approximated by a reciprocal function of $E_{\mathrm{g}}$, that
-$\alpha^{\parallel}\sim{} 7.295(E_{\mathrm{g}})^{-1}$. On the other
-hand, the plot of $\alpha^{\perp}$ against $E_{\mathrm{g}}$ shows no
+polarizability. Figure \ref{fig:SI-raw-HSE} shows the raw data of
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+as functions of $E_{\mathrm{g}}$ of the 2D materials investigated. We
+observe that $\alpha_{\mathrm{2D}}^{\parallel}$ can be approximated by
+a reciprocal function of $E_{\mathrm{g}}$, that
+$\alpha_{\mathrm{2D}}^{\parallel}\sim{}
+7.295(E_{\mathrm{g}})^{-1}$. On the other hand, the plot of
+$\alpha_{\mathrm{2D}}^{\perp}$ against $E_{\mathrm{g}}$ shows no
 apparent correlation.
@@
   \includegraphics[width=0.8\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
-  \caption{$E_{\mathrm{g}}$-dependence of    \textbf{a} $\alpha^{\parallel}$ and
-    \textbf{b} $\alpha^{\perp}$ for the 2D materials investigated here.}
+  \caption{$E_{\mathrm{g}}$-dependence of \textbf{a} $\alpha_{\mathrm{2D}}^{\parallel}$ and
+    \textbf{b} $\alpha_{\mathrm{2D}}^{\perp}$ for the 2D materials investigated here.}
   \label{fig:SI-raw-HSE}
@@
   \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
-  \caption{Relation between $1/\alpha^{\parallel}$ and various choices
+  \caption{Relation between $1/\alpha_{\mathrm{2D}}^{\parallel}$ and various choices
     of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
@@
 changing the choice of $E_{\mathrm{g}}$ yields different regression
-relation with $1/\alpha^{\parallel}$, as shown in Figure
+relation with $1/\alpha_{\mathrm{2D}}^{\parallel}$, as shown in Figure
 \ref{fig:alpha-Eg-diff}. We see that due to the underestimation of PBE
@@
 bands, with the minimal bandgap as the least possible transition. In
-this sense, $\alpha^{\parallel}$ is mostly like to be associated with
+this sense, $\alpha_{\mathrm{2D}}^{\parallel}$ is mostly like to be associated with
 the minimal, not direct bandgap, as also observed in the original Moss
@@
 \section{Validation on the C2DB 2D materials database}
-\label{sec:gpaw}
 \subsection{Validation of the universal description of 2D polarizabilities}
@@
   \caption{Validation the linear relation between \textbf{a}
-    $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
-    $\alpha^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
+    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
+    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
     database, corresponding to Figure 3b and 3c in main text.}
@@
 on the PBE level. The propsed linear relations between
-$1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
-$\alpha^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
+$1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
+$\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
 as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
@@
 Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
-regression of $\alpha^{\parallel}-E_{\mathrm{g}}$ relation. Figure
-\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha^{\parallel}$ from the
+regression of $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation. Figure
+\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha_{\mathrm{2D}}^{\parallel}$ from the
 C2DB database as a function of minimal and direct bandgap calculated
@@
 although the regression $R^{2}$ coefficient in all cases are around
-0.9, the $\alpha^{\parallel}-E_{\mathrm{g}}$ is better described using
+0.9, the $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ is better described using
 the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
@@
 with our calculations on the HSE level discussed in Section
-\ref{sec:pol-2D-2}. In combination with the physical contribution of
+\ref{sec:pol-2D-Eg}. In combination with the physical contribution of
 $E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
@@
   \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
-  \caption{$\alpha^{\parallel}$ as funtion of minimal and direct
+  \caption{$\alpha_{\mathrm{2D}}^{\parallel}$ as funtion of minimal and direct
     $E_{\mathrm{g}}$ calculated on different theoretical levels:
@@
   \label{fig:SI-gpaw-alpha-Eg-all}
+\end{figure}
+
+For 2D materials, the exciton effect plays an important role in
+determining the experimentally accessible bandgap
+\cite{Arnaud_2006_exc_hBN,Pulci_2014,Ramasubramaniam_2012,Chernikov_2014_EB_MoS2_2D3D}. The
+experimentally observed optical bandgap
+$E_{\mathrm{g}}^{\mathrm{opt}}$, is usually lower than the direct
+bandgap from bandstructure $E_{\mathrm{g}}^{\mathrm{dir}}$ by the
+exciton binding energy $E_{\mathrm{b}}$, which is at the 10$^{-1}$ to
+10$^{1}$ eV for different 2D materials due to the attenuated
+dielectric screening. Next we examine the relation between
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{\mathrm{opt}}$
+from the C2DB database, with
+$E_{\mathrm{g}}^{\mathrm{opt}}=E_{\mathrm{g}}^{\mathrm{dir,QP}}-E_{\mathrm{b}}^{\mathrm{BSE}}$,
+where $E_{\mathrm{g}}^{\mathrm{dir,QP}}$ is the direct quasi-particle
+bandgap calculated using G0W0 method and
+$E_{\mathrm{b}}^{\mathrm{BSE}}$ is the exciton binding energy
+calculated using the Bethe-Salpethe equation. Figure \ref{fig:opt}
+shows $(4\pi\varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ as a
+function of $E_{\mathrm{g}}^{\mathrm{opt}}$, with a linear regression
+slope of 0.154 and $R^{2}$ of 0.84, similar to the relation between
+$(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
+$E_{\mathrm{g}}$ (from HSE06 level, see Figures \ref{fig:SI-raw-HSE}
+and \ref{fig:SI-gpaw-alpha-Eg-all}). The roughly linear correlation
+between $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
+$E_{\mathrm{g}}^{\mathrm{opt}}$ is not coincidence: in fact,
+theoretical analysis shows that the binding energy $E_{\mathrm{b}}$ is
+proportional to the direct bandgap $E_{\mathrm{g}}$
+\cite{Jiang_2017_Eg_Eb}, taking into account that
+$(\alpha_{\mathrm{2D}}^{\parallel})^{-1} \propto E_{\mathrm{g}}$, we
+rationalize that
+$(\alpha_{\mathrm{2D}}^{\parallel})^{-1} \propto
+E_{\mathrm{g}}^{\mathrm{opt}}=E_{\mathrm{g}}^{\mathrm{dir}}-E_{\mathrm{b}}$. The
+slightly smaller linearity than the 2D Moss-like relation is caused
+from multiple approximations used. Nevertheless we show that
+$(4\pi\varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ can be
+equivalently predicted using the experimentally accessible optical
+bandgap.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.55\linewidth]{img/SI-alphax-Eg-opt.pdf}
+  \caption{$(4\pi\varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
+    $E_{\mathrm{g}}^{\mathrm{opt}}$ from the C2DB database.}
+  \label{fig:opt}
 \end{figure}
@@
 
-\item The total atomic polarizabilities per area $\alpha^{\mathrm{sum}}$.
+\item The total atomic polarizabilities per area $\alpha_{\mathrm{2D}}^{\mathrm{sum}}$.
 \end{enumerate}
@@
     carrier mass from the C2DB 2D material
-    database. \textbf{a}. $\alpha^{\parallel}$ as a function of the
-    electron mass $m_{e}^{*}$.  \textbf{b}. $\alpha^{\parallel}$ as a
+    database. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of the
+    electron mass $m_{e}^{*}$.  \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a
     function of the hole mass
-    $m_{h}^{*}$. \textbf{c}. $\alpha^{\perp}$ as a function of the
-    electron mass $m_{e}^{*}$.  \textbf{d}. $\alpha^{\perp}$ as a
+    $m_{h}^{*}$. \textbf{c}. $\alpha_{\mathrm{2D}}^{\perp}$ as a function of the
+    electron mass $m_{e}^{*}$.  \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}$ as a
     function of the hole mass $m_{h}^{*}$. No apparent correlation
@@
   \caption{Relation between the 2D polarizabilities with the quantum
-    capacitance. \textbf{a} $\alpha^{\parallel}$ (top) and
-    $\alpha^{\perp}$ (bottom) as functions of the quantum capacitance
+    capacitance. \textbf{a} $\alpha_{\mathrm{2D}}^{\parallel}$ (top) and
+    $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of the quantum capacitance
     of the conduction band edge,
-    $C_{\mathrm{Q}}^{\mathrm{C}}$. \textbf{b} $\alpha^{\parallel}$
-    (top) and $\alpha^{\perp}$ (bottom) as functions of the quantum
+    $C_{\mathrm{Q}}^{\mathrm{C}}$. \textbf{b} $\alpha_{\mathrm{2D}}^{\parallel}$
+    (top) and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of the quantum
     capacitance of the valence band edge,
@@
   \caption{Relation between the 2D polarizabilities
-    (\textbf{a}. $\alpha^{\parallel}$ and
-    \textbf{b}. $\alpha^{\perp}$) with the total atomic polarizability per area.}
+    (\textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ and
+    \textbf{b}. $\alpha_{\mathrm{2D}}^{\perp}$) with the total atomic polarizability per area.}
   \label{fig:gpaw-2D-quantities-3}
@@
 
-The total polarizability $\alpha^{\mathrm{sum}}$ is calculated by the
-summation of the atomic polarizabilities $\alpha^{\mathrm{atom}}$
+The total polarizability $\alpha_{\mathrm{2D}}^{\mathrm{sum}}$ is calculated by the
+summation of the atomic polarizabilities $\alpha_{\mathrm{2D}}^{\mathrm{atom}}$
 \cite{Gould_2016_jctc} of individual atoms per area $A$, such that:
@@
   \label{eq:atom-polar}
-  \alpha^{\mathrm{sum}} = \frac{\sum_{i} \alpha^{\mathrm{atom}}_{i}}{A}
+  \alpha_{\mathrm{2D}}^{\mathrm{sum}} = \frac{\sum_{i} \alpha^{\mathrm{atom}}_{i}}{A}
 \end{equation}
@@
 (\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
-$\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ at 0 K can be unified by the
 same equation:
@@
 
-For the in-plane component, $\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$
+For the in-plane component, $\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$
 is independent of $z$, therefore the integral in
@@
 independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
-$\alpha^{\perp}$ is independent of the band gap.
+$\alpha_{\mathrm{2D}}^{\perp}$ is independent of the band gap.
 
-Finally we will show the $\alpha^{\perp}$ is related to the
+Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
 confinement length $\delta$, or equivalent the thickness of the 2D
@@
   \begin{aligned}
-    \alpha^{\perp} &\propto \delta^{4} m^{\perp} \int
+    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
     d^{2}\mathbf{k}_{\rho}
@@
   \label{eq:alpha-perp-L}
-  \alpha^{\perp} \propto \delta^{2}
+  \alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}
 \end{equation}
 Apart from the power of $\delta$, this explains our observation
-$\alpha^{\perp}$ is related with the thickness of a 2D material. We
+$\alpha_{\mathrm{2D}}^{\perp}$ is related with the thickness of a 2D material. We
 note the power law of $\delta^{2}$ instead of $\delta$ is
@@
 polarizability is the molecular polarizability divided by the area,
-such approach will always yield $\alpha^{\perp} \propto \delta^{2}$
+such approach will always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$
 regardless of the Hamiltonian used. To accurately model the
-$\alpha^{\perp}$ we need a better model for the confinement in
+$\alpha_{\mathrm{2D}}^{\perp}$ we need a better model for the confinement in
 z-direction than simple square potential well, which may be
@@
 the bandgap-indepent and thickness-related feature of
-$\alpha^{\perp}$, supporting our findings in the main text.
+$\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main text.
 
-The dependency of $\alpha^{\perp}$ on the thickness of a 2D material,
+The dependency of $\alpha_{\mathrm{2D}}^{\perp}$ on the thickness of a 2D material,
 can also be regarded using fundamental electrostatic model. Consider
@@
   \caption{Fundamental electrostatic model for the
-    thickness-dependency of $\alpha^{\perp}$, using 2H-MoS2 as an
+    thickness-dependency of $\alpha_{\mathrm{2D}}^{\perp}$, using 2H-MoS2 as an
     example. Left: induced dipoles from individual atoms along the
@@
     atoms cancel out. Right: simplied model for the thickness
-    dependency of $\alpha^{\perp}$, where the surface dipole density
+    dependency of $\alpha_{\mathrm{2D}}^{\perp}$, where the surface dipole density
     $\boldsymbol{\mu}$ comes only from the outer-most atoms.}
@@
 From the definition of
-$\alpha^{\perp}$, we have:
+$\alpha_{\mathrm{2D}}^{\perp}$, we have:
 \begin{equation}
   \label{eq:alpha-classic}
-  \alpha^{\perp} = \frac{\boldsymbol{u}_{z}}{E_{\mathrm{loc}} A}
+  \alpha_{\mathrm{2D}}^{\perp} = \frac{\boldsymbol{u}_{z}}{E_{\mathrm{loc}} A}
   = \frac{(d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j}) \sigma_{\mathrm{b}}}{E}
@@
   \label{eq:alpha-classic-2}
-  \alpha^{\perp} = (d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j})\varepsilon_{0}
+  \alpha_{\mathrm{2D}}^{\perp} = (d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j})\varepsilon_{0}
                 = \delta_{\mathrm{cov}} \varepsilon_{0}
@@
 can see that such simple model nicely captures the thickness feature
-of $\alpha^{\perp}$, and reproduces the right coefficient between
-$\delta_{\mathrm{cov}}$ and $\alpha^{\perp}$. Finally, the schematic
+of $\alpha_{\mathrm{2D}}^{\perp}$, and reproduces the right coefficient between
+$\delta_{\mathrm{cov}}$ and $\alpha_{\mathrm{2D}}^{\perp}$. Finally, the schematic
 drawing of the polarizability ellipsoid for a 2D material, is drawn in
@@
   \caption{Polarizability ellipsoid of a 2D material, the long axis
-    equals $\alpha^{\parallel}/2\varepsilon_{0}$ and the short axis
-    equals  $\alpha^{\perp}/2\varepsilon_{0}$}
+    equals $\alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ and the short axis
+    equals  $\alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$}
   \label{fig:ellipsoid}
@@
   \label{eq:alpha-plas}
-  \alpha^{\parallel} &= \frac{e^{2} n_{\mathrm{3D}} L}{m_{e} E_{\mathrm{g}}^{2}} \\
+  \alpha_{\mathrm{2D}}^{\parallel} &= \frac{e^{2} n_{\mathrm{3D}} L}{m_{e} E_{\mathrm{g}}^{2}} \\
   &= \frac{e^{2} n_{\mathrm{2D}}}{m_{e} E_{\mathrm{g}}^{2}} \\
@@
 $\omega_{\mathrm{2D}}^{p}$ defines the superlattice-independent 2D
-quantity $\alpha^{\parallel}$, while its 3D counterpart
+quantity $\alpha_{\mathrm{2D}}^{\parallel}$, while its 3D counterpart
 $\varepsilon_{\mathrm{3D}}$ is dependent on $L$. By defining the 2D
@@
 $\sigma_{\mathrm{2D}}^{\mathrm{v}}=n_{\mathrm{2D}}e$, we have also
-calculated $\alpha^{\parallel}$ as a function of
+calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
 $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the C2DB database, as shown in Figure \ref{fig:plasma}.
@@
   \includegraphics[width=0.65\linewidth]{img/SI-lorentz-model.pdf}
-  \caption{Calculated$\alpha^{\parallel}$ as a function of
+  \caption{Calculated$\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
     $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the
@@
 theoretical value of
-$\alpha^{\parallel} = \frac{e^{2} n_{\mathrm{3D}} L}{m_{e}
+$\alpha_{\mathrm{2D}}^{\parallel} = \frac{e^{2} n_{\mathrm{3D}} L}{m_{e}
   E_{\mathrm{g}}^{2}}$ (broken line). However there are also many

### 2018-11-15 paper.tex
Add optical bandgap in SI

@@
 \usepackage{times}
+
+\usepackage{xr}
+\externaldocument[SI-]{SI}
 
@@
 % rules at an accurate level.
-Here we show that instead of the dielectric constant $\varepsilon$,
-the 2D polarizabilty $\alpha$ correctly captures the dielectric nature
+Here we show that instead of the dielectric constant,
+the 2D polarizabilty correctly captures the dielectric nature
 of a 2D material. Based on both theoretical model and first principle
@@
 structural information: the in-plane polarizability
-$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
+$\alpha^{\parallel}_{\mathrm{2D}}$ is inversely proportional to the minimal bandgap
 $E_{\mathrm{g}}$, while the out-of-plane polarizability
-$\alpha^{\perp}$ is directly related with the thickness
+$\alpha^{\perp}_{\mathrm{2D}}$ is directly related with the thickness
 $\delta$ of a 2D materials. We further introduce the concept of
@@
 where $\kappa$ is the dielectric tensor of the environment,
-$\boldsymbol{u} = {\displaystyle \int_{\mathrm{SL}}
-  \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}$ is the
-total dipole moments of the SL, $\rho$ is the spatial charge density,
-$\Omega=AL$ is the volume, $A$ is the xy-plane area of the SL and
-$\varepsilon_{0}$ is vacuum permittivity. For the majority of 2D
-semiconductors, the off-diagonal elements of the dielectric tensor
-($p \neq q$) tend to be negligible.  Considering that the 2D material
-is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
-distinguish two components, namely the in-plane
-($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
+$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is the
+spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
+area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
+majority of 2D semiconductors, the off-diagonal elements of the
+dielectric tensor ($p \neq q$) tend to be negligible.  Considering
+that the 2D material is placed in vacuum ($\kappa^{pp} = 1$ and
+$\kappa^{pq} = 0$), we can distinguish two components, namely the
+in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
 ($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
@@
 \textit{z}-direction: as shown in Figure \ref{fig-1}a and
-Supplementary Figure SXX \todo{check}, the charge density difference
+Supplementary Figure \ref{SI-fig:rho-profile}, the charge density difference
 between zero and finite electric fields,
@@
 and comparison with other methods can be find in Supplementary Section
-SXX \todo{xxx}.
-
-% It is also worth mentioning that the dielectric properties of 2D
-% materials are also often modeled using an effective medium approach,
-% which treats the 2D material as a slab with effective permittivity
-% $\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
-% \cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
-% methods require \textit{a priori} determination of $\delta$, a
-% quantity with controversial definitions \cite{Mas_Ballest__2011}. In
-% such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
-% determined by fitting the $L$-dependent data of
-% $\varepsilon_{\mathrm{SL}}$, which is not only computational
-% expensive, but also fails to capture the anisotropy of the 2D
-% dielectric properties (see Supplementary Section S1). On the other
-% hand, calculating 2D polarizabilities requires no knowledge of
-% $\delta$ (see Eqs. \ref{eq:alpha-para-def} and
-% \ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
-% dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
-% the polarizability as the true descriptor of 2D dielectric properties,
-% we will reveal the universal Moss-like relation of 2D materials from
-% both theoretical and first principles studies.
+\ref{SI-sec:2D-3D-rescale}.
 
@@
 no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
-$E_{\mathrm{g}}$ is observed (see Supplementary Section S2.2), which
-appears to be in good agreement with our polarizability-based
-theoretical model (Supplementary Section SXX \todo{note}). We then
-examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
-polarizabilities calculated by first principle calculations. Figure
-\ref{fig-3}b shows
+$E_{\mathrm{g}}$ is observed (see Supplementary Section
+\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
+our polarizability-based theoretical model (Supplementary Section SXX
+\todo{note}). We then examine Eqs. \ref{eq:2D-Moss-para} and
+\ref{eq:2D-Moss-perp} using the polarizabilities calculated by first
+principle calculations. Figure \ref{fig-3}b shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
@@
 We also discover that the linearity between
-$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$
-(measured by the $R^{2}$ value) is higher when the bandgap is
-calculated using the HSE06 hybrid functionals, compared with that from
-the Perdew--Burk--Ernzerhof (PBE) exchange correlations (details see
-Supplementary Section S2 and Supplementary Figure S5), which can be
+$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
+$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
+bandgap is calculated using the HSE06 hybrid functionals, compared
+with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
+(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
+Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
 explained by the fact that the electronic structure, in particular the
@@
 be most suitable to present the true 2D Moss-like relationship between
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$.
-\todo[inline]{check the values for optical bandgap}
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
+that the proposed relation behaves equivalently well when using the
+experimentally accessible optical bandgap of 2D materials (details see
+Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
+\ref{SI-fig:opt}).
 

### 2018-11-15 paper.tex
Change all alpha to alpha_2D in main

@@
 in-plane and out-of-plane polarizabilities, we derive the expressions
-for $\alpha^{\parallel}$ and $\alpha^{\perp}$ under small perturbation
+for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ under small perturbation
 (details see Supplementary Section S4):
@@
   \label{eq:alpha_para_RPA}
-  & \alpha^{\parallel} &= \frac{2e^{2}}
+  & \alpha_{\mathrm{2D}}^{\parallel} &= \frac{2e^{2}}
   {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
@@
   \label{eq:alpha_perp_RPA}
-  & \alpha^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
+  & \alpha_{\mathrm{2D}}^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
   \sum_{\mathrm{c, v}}
@@
 (periodic function) and $\psi(z)$ (confined to the 2D material) give
-rise to the different relations of $\alpha^{\parallel}$ and
-$\alpha^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
+rise to the different relations of $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
 Eq. \ref{eq:alpha_para_RPA} is evaluated to be
-$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
+$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
 degeneracy associated with the minimal bandgap
@@
 quantum mechanical and fundamental electrostatic models, that
-$\alpha^{\perp}$ is actually proportional to the size of potential
+$\alpha_{\mathrm{2D}}^{\perp}$ is actually proportional to the size of potential
 confinement (details see Supplementary Section S4), which we may
@@
 \label{eq:2D-Moss-para}
-  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
+  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
   \label{eq:2D-Moss-perp}
-  &\alpha^{\perp} & \propto \delta
+  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
 \end{eqnarray}
@@
 coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
-corresponds well with theoretical investigations
-\citenum{Jiang_2017_Eg_Eb} (details see Supplementary Section SXX
-\todo{format Jiang's paper into SI}).
+corresponds well with theoretical investigations (details see
+Supplementary Section SXX \todo{format Jiang's paper into SI}).
 % From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
@@
 
-We further examine the relation between $\alpha^{\perp}$ and the
+We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
 thickness of a 2D material proposed in
@@
 material (see Supplementary Section SXX). In fact, the universal
-scaling relation for $\alpha^{\perp}$ in Figure \ref{fig-3}c indicates
-that the quantity $\alpha^{\perp}/\varepsilon_{0}$ measurable via
+scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
+that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
 electronic approaches
@@
 fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
-$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
+$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
 general Moss-like relation between $E_{\mathrm{g}}$ and
-$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
-2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
+$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
+2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
 molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
@@
 a function of distance $r$:
-$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
+$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
 \left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
-      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
-      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
+      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
+      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
 \cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
@@
       {\displaystyle
-        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
+        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
       \ \mathrm{2D\ Materials}\\
@@
   $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
-  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
-  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
+  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
+  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
   $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
@@
     dielectric nature of 2D
-    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
+    materials}. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
   (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
-  materials studied.  $\alpha^{\parallel}$ is observed to descend with
+  materials studied.  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
   increasing $E_{\mathrm{g}}$, while no apparent relation between
-  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
-  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
+  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
+  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
   (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
@@
   shown in the
-  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
+  background. \textbf{c}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
   \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
@@
   (y-axis) compared with the predicted value from 2D
-  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
   $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
-  compared with the predicted value from 2D $\alpha^{\parallel}$
+  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
   (x-axis). The predicted value is in good aggreement with the DFT

### 2018-11-15 SI.tex
Move all theoretical part to SI

@@
 
-\section{More theoretical analysis}
-\label{eq:MG-effect-1}
-
-\subsection{Detailed derivations for Eq. 5a and 5b}
-\label{sec:theory-1}
-
-Here we will first show how Eq. 5a and 5b in the main text are
-derived. Taking the limit that $L\to\infty$, when
+\section{Theoretical Analysis}
+\label{sec:theory}
+\subsection{Polarizability-Based Theoretical Model}
+\label{ssec:theory-1}
+In this section we show in detail the polarizability-based theoretical
+framework that leads to the 2D Moss-like relations proposed in the
+main text.  Due to its highly anisotropic nature, the wavefunction of
+an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
+in- and out-of-plane components, similar to the treatment of quantum
+wells (QW),\cite{davies_physics_1997} such that
+$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
+$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
+is the in-plane coordinate. Using the Bloch theorem, the periodic
+$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
+$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
+  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
+in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
+in the xy-plane. According to the random phase approximation (RPA)
+theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
+$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
+dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
+$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
+\begin{equation}
+  \label{eq:RPA-eps2}
+  \varepsilon_{\mathrm{SL}}
+  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
+  \sum_{\mathrm{k, c, v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
+  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
+\end{equation}
+where $e$ is the unit charge, c, v are the conduction and valence
+bands, $E$ is the eigenenergy of individual bands, and $f$ is the
+Fermi-Dirac distribution function. Taking the
+limit that $L\to\infty$, when
 $\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
@@
 (\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ at 0 K can be unified by the
-same equation:
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+at 0 K can be unified by the same equation:
 \begin{equation}
@@
 \end{equation}
-where the direction is determined by $\mathbf{q}$.
+where the direction is determined by $\mathbf{q}$. Next we will show
+that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
+give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
+\ref{main-eq:2D-Moss-perp}.
 
-For the in-plane component, $\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$
-is independent of $z$, therefore the integral in
+\subsubsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-para}}
+\label{sssec:theory-1}
+
+In this section we show how main text Eq. \ref{main-eq:2D-Moss-para}
+is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
+$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
+of $z$, therefore the integral in
 $|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
-becomes the independent of $\psi^{\perp}$, due to the
-orthogonality. Present the summation of k-space into integral, and further
-combining with the Bloch wave representation and the k-p
-theory\cite{Jiang_2017_Eg_Eb}, we arrive at Eq. 5a.
+becomes the independent of $\psi^{\perp}$, due to the orthogonality
+and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
+only the cell-function $u(\mathbf{k})$ contributes to the final result
+of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
+that:
+\begin{equation}
+  \label{eq:alpha_para_RPA}
+  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
+  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
+  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+Present the summation of k-space into integral, and further combining
+with the Bloch wave representation and the
+$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
+at Eq. \ref{main-eq:2D-Moss-para}. Note that from
+Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
+$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
+$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
+where $N$ is the degeneracy associated with the minimal bandgap. Such
+relation predicts the linear correlation coefficient between
+$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
+\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
+$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From main
+text Figure \ref{main-fig-3}c, we have
+$(4 \pi \varepsilon_{0}\cdot \AA{})/\alpha_{\mathrm{2D}}^{\parallel}
+\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
+between 2 and 3, which is a reasonable result for the 2D materials
+studied.
 
-For Eq. 5b, treating the in-plane wavefunctions as plane wave with
-form $\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the
-matrix element of
+\subsubsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-perp}}
+\label{ssec:theory-2}
+For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
+wavefunctions as plane wave with form
+$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
+element of
 $<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
@@
   \begin{aligned}
-    \label{eq:matrix-z}
+    \label{eq:matrix-z-2}
     <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
@@
 $k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
-arrive at Eq. 5b in main text.
+arrive at:
+\begin{equation}
+\label{eq:alpha_perp_RPA}
+\alpha_{\mathrm{2D}}^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
+\sum_{\mathrm{c, v}}
+\frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
+{E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+The formalism is slightly different from Eq.\ref{eq:alpha_para_RPA}.
 
-Although the exact form for $\psi^{\perp}$ depends on the exact
-distribution of $V(z)$, without loss of generality we can assume the
-electrons are confined in a potential well of width $\delta$, which is
-the typical treatment for semiconductor QWs
-\cite{ihn_semiconductor_2009}. The allowed bound states inside the
-confined region generally has wave vector
+The out-of-plane wavefunction $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
+Hamiltonian $\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where
+$\hbar$ is the reduced Planck constant, $m_{e}$ is electron mass and
+$V(z)$ is the confined Coulombic potential along the z-direction
+created by the nuclei
+\cite{davies_physics_1997,ihn_semiconductor_2009}. Although the exact
+form for $\psi^{\perp}$ depends on the exact distribution of $V(z)$,
+without loss of generality we can assume the electrons are confined in
+a potential well of width $\delta$, which is the typical treatment for
+semiconductor QWs \cite{ihn_semiconductor_2009}. The allowed bound
+states inside the confined region generally has wave vector
 $k_{z} \propto n \pi / \delta$. With the total energy
@@
 eV, which allows only few states inside the QW. Combine with the fact
-that the strongest transition comes from the lowest bands
-\cite{davies_physics_1997}, we can finally show:
-\begin{equation}
-  \label{eq:alpha-perp-L}
-  \alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}
-\end{equation}
-Apart from the power of $\delta$, this explains our observation
-$\alpha_{\mathrm{2D}}^{\perp}$ is related with the thickness of a 2D material. We
-note the power law of $\delta^{2}$ instead of $\delta$ is
-inevitable. The atomic polarizabilities of free particles inside a 1D
-infinite QW, finite QW or harmonic QW all show dependency with
-$\delta^{4}$, where $\delta$ is the length of confinement or effective
-harmonic length of the QW \cite{Fowler_1984,Maize_2011}. Since the 2D
-polarizability is the molecular polarizability divided by the area,
-such approach will always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$
-regardless of the Hamiltonian used. To accurately model the
-$\alpha_{\mathrm{2D}}^{\perp}$ we need a better model for the confinement in
-z-direction than simple square potential well, which may be
-tedious. Nevertheless the simple model presented here still captures
-the bandgap-indepent and thickness-related feature of
-$\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main text.
+that the strongest transition mostly comes from the lowest bands
+\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
+be proportional to $\delta^{p}$, where the power index $p$ is 2. We
+note the different power law comes from the choice of the $V(z)$. The
+atomic polarizabilities of free particles inside a 1D infinite QW,
+finite QW or harmonic QW all show dependency with $\delta^{4}$, where
+$\delta$ is the length of confinement or effective harmonic length of
+the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
+the molecular polarizability divided by the area, such approach will
+always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
+accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
+model for the confinement in z-direction than simple square potential
+well, which may be tedious. Nevertheless the simple model presented
+here still captures the bandgap-indepent and thickness-related feature
+of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
+text. In the next section we will provide a simple explanation for the $\alpha \propto \delta$ relation from fundamental electrostatics theory.
 
-The dependency of $\alpha_{\mathrm{2D}}^{\perp}$ on the thickness of a 2D material,
-can also be regarded using fundamental electrostatic model. Consider
-the smallest repeating unit of the 2D material with xy-plane area $A$,
-under small perturbation field $E$ along the z-direction.  Note that
-the surface bound charge $\sigma_{\mathrm{b}}=n e /A$, where $n$ is
-the number of unit charges contributes to the bound charges, comes
-only from the dipoles of the outer-most atoms, since the induced
-charges from inner atoms are cancel out (see Figure \ref{fig:classic-model}).
+\subsubsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
+  from fundamental electrostatics}
+\label{sssec:theory-3}
+
+The dependency of $\alpha_{\mathrm{2D}}^{\perp}$ on the thickness
+$\delta$ of a 2D material, can also be regarded using fundamental
+electrostatic model. Consider the smallest repeating unit of the 2D
+material with xy-plane area $A$, under small perturbation field $E$
+along the z-direction.  Note that the surface bound charge
+$\sigma_{\mathrm{b}}=n e /A$, where $n$ is the number of unit charges
+contributes to the bound charges, comes only from the dipoles of the
+outer-most atoms, since the induced charges from inner atoms are
+cancel out (see Figure \ref{fig:classic-model}).
 \begin{figure}[htbp]
@@
 \end{equation}
-which explains the linear relation seen in Figure 3c of main text. We
-can see that such simple model nicely captures the thickness feature
-of $\alpha_{\mathrm{2D}}^{\perp}$, and reproduces the right coefficient between
-$\delta_{\mathrm{cov}}$ and $\alpha_{\mathrm{2D}}^{\perp}$. Finally, the schematic
-drawing of the polarizability ellipsoid for a 2D material, is drawn in
-Figure \ref{fig:ellipsoid}.
+which explains the linear relation seen in main text Figure
+\ref{main-fig-3}d. We can see that such simple model nicely captures
+the thickness feature of $\alpha_{\mathrm{2D}}^{\perp}$, and
+reproduces the right coefficient between $\delta_{\mathrm{cov}}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$. Finally, the schematic drawing of the
+polarizability ellipsoid for a 2D material, is drawn in Figure
+\ref{fig:ellipsoid}.
 \begin{figure}[htbp]
@@
 
-\subsection{Detailed discussion for main text Eq. 9}
+\subsection{}
 \label{sec:theory-2}

### 2018-11-15 paper.tex
Move all theoretical part to SI

@@
 
-\iffalse
-\subsection{Polarizability-Based Theoretical Model}
-\todo[inline]{In case of Nat. Nanotechnol., I would like to move all
-  theoretical information to SI}.
-Based on the 2D polarizability, we
-then theoretically investigate the potential existence of the
-Moss-like relations for 2D materials.  Due to its highly anisotropic
-nature, the wavefunction of an isolated 2D material $\psi(\mathbf{r})$
-can be separated into the in- and out-of-plane components, similar to
-the treatment of quantum wells (QW),\cite{davies_physics_1997} such
-that $\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such
-that $\psi=\psi^{\parallel}\psi^{\perp}$, where
-$\boldsymbol{\rho}=(x, y)$ is the in-plane coordinate. Using the Bloch
-theorem, the periodic $\psi^{\parallel}(\boldsymbol{\rho})$ can be
-further expressed as
-$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
-  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
-in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
-in the xy-plane. According to the random phase approximation (RPA)
-theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
-$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
-dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
-$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
-\begin{equation}
-  \label{eq:RPA-eps2}
-  \varepsilon_{\mathrm{SL}}
-  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
-  \sum_{\mathrm{k, c, v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
-  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
-\end{equation}
-where $e$ is the unit charge, c, v are the conduction and valence
-bands, $E$ is the eigenenergy of individual bands, and $f$ is the
-Fermi-Dirac distribution function. Taking the limit that $L\to\infty$,
-when $\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
-$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
-(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Combine this with
-Eqs. \ref{eq:alpha-para-def}, \ref{eq:alpha-perp-def} and
-\ref{eq:RPA-eps2}, and taking the difference between the properties of
-in-plane and out-of-plane polarizabilities, we derive the expressions
-for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ under small perturbation
-(details see Supplementary Section S4):
-\begin{subequations}
-  \begin{eqnarray}
-  \label{eq:alpha_para_RPA}
-  & \alpha_{\mathrm{2D}}^{\parallel} &= \frac{2e^{2}}
-  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
-                         {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
-  \label{eq:alpha_perp_RPA}
-  & \alpha_{\mathrm{2D}}^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
-  \sum_{\mathrm{c, v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
-  \end{eqnarray}
-\end{subequations}
-where the integral is performed within the first Brillouin Zone (BZ)
-in the reciprocal $\mathbf{k}$-plane. Although they only differ by the
-numerator inside the integral, the distinct behaviors of $u(\rho)$
-(periodic function) and $\psi(z)$ (confined to the 2D material) give
-rise to the different relations of $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
-Eq. \ref{eq:alpha_para_RPA} is evaluated to be
-$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
-degeneracy associated with the minimal bandgap
-\cite{Jiang_2017_Eg_Eb}. On the contrary, $\psi(z)$ is the solution to
-the Schr\"{o}dinger equation with Hamiltonian
-$\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where $\hbar$ is
-the reduced Planck constant, $m_{e}$ is electron mass and $V(z)$ is
-the confined Coulombic potential along the z-direction created by the
-nuclei \cite{davies_physics_1997,ihn_semiconductor_2009}. Using a
-simple particle-in-box model, we show that both the numerator and
-denominator parts of Eq. \ref{eq:alpha_perp_RPA} are independent of
-$E_{g}$ but instead modulated by the size of the potential confinement
-(details see Supplementary Section S4). We further prove, using both
-quantum mechanical and fundamental electrostatic models, that
-$\alpha_{\mathrm{2D}}^{\perp}$ is actually proportional to the size of potential
-confinement (details see Supplementary Section S4), which we may
-relate with the thickness $\delta$ of the 2D material. Now we may
-finally propose the 2D analog of the Moss relation with both in- and
-out-of-plane polarizations:
-\begin{subequations}
-\begin{eqnarray}
-\label{eq:2D-Moss-para}
-  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
-  \label{eq:2D-Moss-perp}
-  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
-\end{eqnarray}
-\end{subequations}
-which form the main conclusion of this work. Next, we will validate
-the proposed 2D Moss-like relations using first principle
-calculations.
-\fi
-
 \subsection{2D Moss-like  Relations}
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section SXX). In fact, the universal
+material (see Supplementary Section SXX \todo{note}). In fact, the universal
 scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
@@
 superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
-(details see Supplementary Section S3). Althought the dielectric
-properties may be overestimated at PBE level due to underestimation of
-the bandgap compared with the more accurate HSE06 functionals
-\cite{Van_Dyck_2017}, similar linear trends can be observed for both
-$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
-with the linear coefficient very close to the HSE06 results. We have
-also tested the potential relation between the 2D polarizabilities
-with other physical quantities, including the effective carrier mass,
-quantum capacitance and total atomic polarizabilities, while no
-apparent correlations are found (details see Supplementary Section
-S3).
+(details see Supplementary Section \ref{SI-sec:gpaw-1}). Althought the
+dielectric properties may be overestimated at PBE level due to
+underestimation of the bandgap compared with the more accurate HSE06
+functionals \cite{Van_Dyck_2017}, similar linear trends can be
+observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$, with the linear coefficient very close
+to the HSE06 results (details see Supplementary Section
+\ref{SI-sec:gpaw-2}). We have also tested the potential relation
+between the 2D polarizabilities with other physical quantities,
+including the effective carrier mass, quantum capacitance and total
+atomic polarizabilities, while no apparent correlations are found
+(details see Supplementary Section \ref{SI-sec:gpaw-3}).
 
@@
 \left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
-      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
+      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
+    \frac{2
       \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
@@
 molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
-Figure S12). The polarizability ellipsoid for a 2D material is in
-general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
-can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
-Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
-bandgap semiconductor, which qualitatively explains the inverse
-propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
+Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
+material is in general ultra flat, with
+$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
+TMDCs in Table \ref{tbl:radii}\todo{Lacks MoSe2}.  Moreover,
+$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
+semiconductor, which qualitatively explains the inverse propotional
+relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
 $E_{\mathrm{g}}$, a 2D version of the Moss-relation.

### 2018-11-15 SI.tex
Complete xr between SI and main for the theoretical alpha part

@@
 \label{ssec:theory-1}
+The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
+and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
+theoretical findings of the linear relation between exciton binding
+energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
+general Moss-like relation between $E_{\mathrm{g}}$ and
+$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
+2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
+molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
+carbon nanotubes \cite{Benedict_1995}, which are also shown to be
+geometry-dependent.
+
 In this section we show in detail the polarizability-based theoretical
@@
 
-\subsection{}
+\subsection{Comparing 2D and 3D Moss relations}
 \label{sec:theory-2}

### 2018-11-15 paper.tex
Complete xr between SI and main for the theoretical alpha part

@@
 treatment\cite{kittel_2005_introduction} (details see Supplementary
-Section SXX) \todo{note}, we show that
+Section \ref{SI-ssec:theory-1}), we show that
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
@@
 thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
-the main conclusions of this work.
+the main conclusions of this work.  \todo[inline]{I not sure if we
+  need to show the proportional coefficiens
+  here. $\alpha_{2D}^{\perp}$ is almost certain to be
+  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
+  a more complex coefficient.}
 
@@
 \ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
-our polarizability-based theoretical model (Supplementary Section SXX
-\todo{note}). We then examine Eqs. \ref{eq:2D-Moss-para} and
-\ref{eq:2D-Moss-perp} using the polarizabilities calculated by first
-principle calculations. Figure \ref{fig-3}b shows
+our polarizability-based theoretical model (Supplementary Section
+\ref{SI-ssec:theory-2}). We then examine Eqs. \ref{eq:2D-Moss-para}
+and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
+first principle calculations. Figure \ref{fig-3}b shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
@@
 corresponds well with theoretical investigations (details see
-Supplementary Section SXX \todo{format Jiang's paper into SI}).
-% From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
-% $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
-% $8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
-% yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
-% studied.
-% We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
-% eV) generally lie close to the regression line, while the deviation
-% becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
-% also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
-% 2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}.
-We also discover that the linearity between
+Supplementary Section \ref{SI-sssec:theory-1}).  We also discover that
+the linearity between
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
@@
 excellent linear correlation with $\delta_{\mathrm{cov}}$, with
-$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
-$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
-to $\delta_{\mathrm{cov}}$, which has its strong physical
-meaning. Similar to the molecular polarizability which characterizes
-the volume of electron cloud of an isolated molecule
-\cite{Israelachvili_2011},
+$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words, we
+propose
+$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
+\delta_{\mathrm{cov}}$, which has its strong physical meaning. Similar
+to the molecular polarizability which characterizes the volume of
+electron cloud of an isolated molecule \cite{Israelachvili_2011},
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section SXX \todo{note}). In fact, the universal
-scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
-that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
+material (see Supplementary Section \ref{SI-sssec:theory-3}). In fact,
+the universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
+Figure \ref{fig-3}c indicates that the quantity
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
 electronic approaches
@@
 thickness of 2D materials, such as graphene \cite{Shearer_2016}.
-
-\iffalse
-The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
-and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
-theoretical findings of the linear relation between exciton binding
-energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
-\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
-fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
-$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
-general Moss-like relation between $E_{\mathrm{g}}$ and
-$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
-2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
-molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
-carbon nanotubes \cite{Benedict_1995}, which are also shown to be
-geometry-dependent.
-\fi
 

### 2018-11-15 SI.tex
Add parts that deal with 2D - 3D transition

--- 2018-11-15 SI.tex
@@
 \label{ssec:theory-1}
+The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
+Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
+coincidence. Combining recent theoretical findings of the linear
+relation between exciton binding energy $E_{\mathrm{b}}$ and
+$E_{\mathrm{g}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
+to have a general Moss-like relation between
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
+the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
+resembles molecular polarizabilities of conjugate molecules
+\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
+nanotubes \cite{Benedict_1995}, which are also shown to be
+geometry-dependent.
+
 In this section we show in detail the polarizability-based theoretical
@@
 text Figure \ref{main-fig-3}c, we have
-$(4 \pi \varepsilon_{0}\cdot \AA{})/\alpha_{\mathrm{2D}}^{\parallel}
+$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
 \sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
@@
 
-\subsection{}
-\label{sec:theory-2}
+\subsection{Comparing 2D and 3D Moss relations}
+\label{ssec:theory-2}
 
-Eq. 9 is the detailed form of Eq. 6 considering wavefunctions in all
-directions are periodic which can be written in the form of Block
-waves. The solution for Eq. 9 in main text is derived as follows. For
-simplicity we consider that the effective mass $m^{*}$ is uniform,
-which is generally a good assumption for bulk materials. Considering
-only one pair of valence-conduction transition, and take the result
-from \cite{Jiang_2017_Eg_Eb}, we get:
+The 2D Moss-like relation $\alpha^{\parallel} \propto E_{g}^{-1}$ is
+similar to the 3D Moss relation $\varepsilon \propto E_{g}^{-1/2}$,
+with a different power law. Such difference in the power law can
+indeed be explained by modern theory of dielectric properties. From
+the 2D material to a bulk covalent semiconductor, the wavefunction
+becomes periodic in all directions. Considering only one pair of
+valence-conduction transition and uniform effective mass $m^{*}$,
+extending the approach Eq. \ref{eq:alpha_perp_RPA} to the bulk
+material, and using the Bloch presentation for wavefunctions in all
+dimensions, we get \cite{Jiang_2017_Eg_Eb}:
 \begin{equation}
@@
 Brillouin Zone is equivalent to integral inside a sphere of
-k-space. Let $\hbar^{2}/(2 m^{*})=A$, the integral becomes:
+k-space. Let $\hbar^{2}/(2 m^{*})=\beta$, the integral becomes:
 \begin{equation}
@@
     \varepsilon_{\mathrm{Bulk}} &\propto {\displaystyle \frac{2 \pi
-        \mathrm{arctan}(\sqrt{Ak^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}}A^{3}}}
-        - \frac{2\pi k}{A(A+E_{\mathrm{g}}k^{2})}
+        \mathrm{arctan}(\sqrt{\beta k^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}} \beta^{3}}}
+        - \frac{2\pi k}{\beta(\beta +E_{\mathrm{g}}k^{2})}
       } \bigg\rvert_{0}^{k_{\mathrm{BZ}}}\\
@@
 when $\varepsilon_{\mathrm{Bulk}} \gg 1$. since generally
-$\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg E_{\mathrm{g}}$. When
-$\varepsilon_{\mathrm{bulk}} \gg 1$ \cite{Finkenrath_1988}, it is the
-Moss relation of bulk semiconductors.
+$\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg
+E_{\mathrm{g}}$ \cite{Finkenrath_1988}. The final result $\varepsilon_{\mathrm{Bulk}} \propto E_{\mathrm{g}}^{-1/2}$ recovers the original Moss relation for bulk semiconductors.
 
 \subsection{Static 2D polarizability and 2D plasma frequency}
-\label{sec:omega-p}
+\label{ssec:omega-p}
 
@@
 \subsection{Comparing dielectric anisotropy}
+\label{ssec:aniso}
 The dielectric anisotropy $\eta$ proposed in the main text is also
@@
 
+\subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
+\label{sssec:aniso-1}
+
 \section{Raw data from first principles calculations}

### 2018-11-15 paper.tex
Add parts that deal with 2D - 3D transition

@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
-\iffalse
-\begin{subequations}
-\begin{eqnarray}
-  \label{eq:alpha-para-def}
-  &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
-  \label{eq:alpha-perp-def}
-  &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
-\end{eqnarray}
-\end{subequations}
-\fi
+% \begin{subequations}
+% \begin{eqnarray}
+  % \label{eq:alpha-para-def}
+  % &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
+  % \label{eq:alpha-perp-def}
+  % &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
+% \end{eqnarray}
+% \end{subequations}
 \begin{subequations}
@@
 semiconductor, which is the original Moss relation (details see
-Supplementary Section SXX \todo{note}). In other words, the proposed
-$\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is indeed
-the Moss relation in 2D world, while the different power law for
-$E_{\mathrm{g}}$ is caused by the electronic confinement.
-
-% As described in the previous section, the 2D Moss-like relation
-% between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
-% relation between $\varepsilon$ and $E_{g}$, with a different power
-% law. Such difference in the power law can indeed be explained by
-% modern theory of dielectric properties.  Extend the approach
-% Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
-% presentation for wavefunctions in all dimensions, we derive (detailed
-% procedure see Supplementary Section S4):
-% \begin{equation}
-  % \label{eq:alpha-Eg-3D}
-  % \begin{aligned}[t]
-  % \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
-  % \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
-  % {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
-  % &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
-% \end{aligned}
-% \end{equation}
-% which recovers the 3D Moss relation.
+Supplementary Section \ref{SI-ssec:theory-2}). In other words, the
+proposed $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is
+indeed the Moss relation in 2D world, while the different power law
+for $E_{\mathrm{g}}$ is caused by the electronic confinement.
+\todo[inline]{I shortened this paragraph since the derivation is
+  interesting but not so much related with other stuff like the
+  dielectric anisotropy.}
 
@@
 semiconducting materials in other dimensions (details see
-Supplementary Section S4.5) on the phase diagram in Figure
+Supplementary Section ) on the phase diagram in Figure
 \ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)

### 2018-11-15 SI.tex
Add analytical solution to anisotropy

@@
 \label{ssec:aniso}
+\subsubsection{Choice of materials}
+\label{sssec:aniso-1}
 The dielectric anisotropy $\eta$ proposed in the main text is also
@@
 \subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
-\label{sssec:aniso-1}
+\label{sssec:aniso-2}
+In this section we give an analytical explanation for the separation
+between the dielectric anisotropy indices of 2D and their bulk
+counterparts. From main text Eqs. \ref{main-eq:alpha-para-def},
+\ref{main-eq:alpha-perp-def} and \ref{main-eq:anisotropy},
+$\eta_{\mathrm{Bulk}}$ of a bulk layered material is expressed as:
+\begin{equation}
+  \label{eq:eta-bulk}
+  \begin{aligned}[t]
+    \eta_{\mathrm{Bulk}} &= \frac{\varepsilon_{\mathrm{Bulk}}^{\perp}}
+    {\varepsilon_{\mathrm{Bulk}}^{\parallel}}\\
+    &= \frac{1}{\left(1 + {\displaystyle
+          \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}L_{\mathrm{Bulk}}}}\right)
+      \left(1 - {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0}L_{\mathrm{Bulk}}}} \right)}\\
+    &= \frac{1}{ \left[1-\left( {\displaystyle
+            \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
+        \left(
+          {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}
+            L_{\mathrm{Bulk}}}} \right) \right]
+      \left[ 1 + \left(
+          {\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0}
+            L_{\mathrm{Bulk}}}} \right)\right]
+    }
+    % &= \frac{\left({\displaystyle \frac{\varepsilon_{0}L_{\mathrm{Bulk}}}{\alpha^{\parallel}_{\mathrm{Bulk}}}}\right)^{2}}
+    % {\left({\displaystyle \frac{\varepsilon_{0}L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}_{\mathrm{2D}}}}\right)^{2}    
+      % -\left({\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
+      % \left({\displaystyle \frac{\varepsilon_{0} L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
+      % + \left({\displaystyle \frac{\varepsilon_{0} L_{\mathrm{Bulk}}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)
+      % -\left({\displaystyle \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\alpha_{\mathrm{Bulk}}^{\parallel}}}\right)}
+  \end{aligned}
+\end{equation}
+Name take the fact that
+$\alpha_{\mathrm{Bulk}}^{\parallel} \approx
+\alpha^{\parallel}_{\mathrm{2D}}$ (main text Figure
+\ref{main-fig-4}b), we name
+$\alpha_{\mathrm{Bulk}}^{\parallel} /\epsilon_{0}L_{\mathrm{Bulk}}
+\approx \alpha_{\mathrm{2D}}^{\parallel}/
+\epsilon_{0}L_{\mathrm{Bulk}}$ as $\gamma$. Furthermore we name
+$\alpha_{\mathrm{Bulk}}^{\perp}/\alpha_{\mathrm{Bulk}}^{\parallel}$ as
+$\hat{\eta_{\mathrm{2D}}}$, that
+$\hat{\eta}_{\mathrm{2D}} =
+\alpha_{\mathrm{Bulk}}^{\perp}/\alpha_{\mathrm{Bulk}}^{\parallel} \geq
+\alpha_{\mathrm{2D}}^{\perp}/\alpha_{\mathrm{2D}}^{\parallel}=\eta_{\mathrm{2D}}$,
+and Eq. \ref{eq:eta-bulk} is reduced to:
+\begin{equation}
+  \label{eq:eta-bulk-2}
+  \eta_{\mathrm{Bulk}} = \frac{1}{(1 - \hat{\eta}_{\mathrm{2D}} \gamma) (1 + \gamma)}
+\end{equation}
+The minimal value for $\eta_{\mathrm{Bulk}}$ when $\gamma>0$ is obtained by solving:
+\begin{equation}
+  \label{eq:eta-bulk-min}
+  \frac{\partial \eta_{\mathrm{Bulk}}}{\partial \gamma}
+  = \frac{2 \hat{\eta}_{\mathrm{2D}} \gamma + \hat{\eta}_{\mathrm{2D}} - 1}
+  {(\gamma+1)^{2}(1 - \hat{\eta}_{\mathrm{2D}} \gamma)^{2}} = 0
+\end{equation}
+which gives that
+$\eta_{\mathrm{Bulk}} \geq \frac{4
+  \hat{\eta}_{\mathrm{2D}}}{(\hat{\eta}_{\mathrm{2D}} + 1)^{2}}$,
+where the minimal value is taken at
+$\gamma = \frac{1}{2}(\frac{1}{\hat{\eta}_{\mathrm{2D}}} - 1)$. Since
+$\frac{4 \hat{\eta}_{\mathrm{2D}}}{(\hat{\eta}_{\mathrm{2D}} +
+  1)^{2}}$ monotonically increases when
+$0 < \hat{\eta}_{\mathrm{2D}} < 1$, we get the comparison between the
+dielectric anisotropy indices between 2D materials and their bulk
+counterparts:
+\begin{equation}
+  \label{eq:aniso-final}
+\eta_{\mathrm{Bulk}} \geq \frac{4
+  \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}} + 1)^{2}} \geq
+\eta_{\mathrm{2D}} 
+\end{equation}
+Since $\gamma$ is actually $2r_{0}^{\parallel}/L_{\mathrm{Bulk}}$, the
+ratio between the in-plane screening length $r_{0}^{\parallel}$ and
+inter-plane distance $L_{\mathrm{Bulk}}$, and in general
+$r_{0}^{\parallel} \gg L_{\mathrm{Bulk}}$, we can conclude that the
+case when $\eta_{\mathrm{Bulk}} = \eta_{\mathrm{2D}}$ only happens
+when $\eta_{\mathrm{2D}}$ is much smaller than 1. Therefore the
+separation between the 2D and 3D regimes in the Figure
+\ref{main-fig:aniso} is explained.
+
+\section{}
 

### 2018-11-15 paper.tex
Add analytical solution to anisotropy

@@
     \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
-\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
-of corresponding 2D layer (details see Supplementary Section SXX
-\todo{note}), which is the basis for the separation of bulk and 2D
-regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
-we also superimpose the dielectric anisotropy indices $\eta$ of common
-semiconducting materials in other dimensions (details see
-Supplementary Section ) on the phase diagram in Figure
+\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
+index of corresponding 2D layer (details see Supplementary Section
+\ref{SI-sssec:aniso-2}), which is the basis for the separation of bulk
+and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
+comparison, we also superimpose the dielectric anisotropy indices
+$\eta$ of common semiconducting materials in other dimensions (details
+see Supplementary Section \ref{SI-sssec:aniso-1}) on the phase diagram in Figure
 \ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)

### 2018-11-15 SI.tex
Move 2D-3D graph to SI

@@
 \item Linear OSc \\
-  We choose the polyacenes (linear PAHs from benznene to nonacene) as
-  a model system of linear OScs. The bandgaps are obtained from
+  We choose the linear polyacenes (linear PAHs from benznene to
+  nonacene) and zigzag polyacetylene (1--9 repeating units) as model
+  systems of linear OScs. The bandgaps are obtained from
   \citenum{Salzner_1998} and the polarizabilities are obtained from
@@
 
-\section{}
+\subsection{The relation between 2D and 3D physical quantities}
+As schematically shown in Figure \ref{fig-2D-3D}, the physical
+quantities related to the dielectric properties can be categorized
+into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
+(iii) valid both 2D and 3D.  $\alpha_{\mathrm{2D}}$ and $\varepsilon$ are the
+starting point for the strictly 2D and 3D quantities, which require
+distinct definitions when dimensionality changes. Such quantities
+include (but not limited to):
+\begin{enumerate}
+\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
+  charge, polarization, electronic states, etc.
+
+\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
+  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (see
+  Section \ref{ssec:omega-p} and Figure \ref{fig:plasma}).
+
+\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
+  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
+\end{enumerate}
+These quantities have distinct units in both dimensions, and related
+by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
+plasma frequency), which requires prudent interpretation of
+theoretical and experimental results. For instance, the experimentally
+observed ``dielectric constant'' of monolayer 2D materials
+\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
+without considering the effect of mix ted medium. Instead, the 2D slab
+polarizability, either transformed from the vacuum-containing
+macroscopic dielectric constant, or predicted from the bandgap and
+geometry as proposed here, will be a better descriptor for the true 2D
+dielectric nature. On the other hand, there are also
+dimension-independent quantities that valid for both 2D and 3D
+systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
+energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
+as well as the Hamaker constant of van der Waals interaction
+$A_{\mathrm{H}}$. All these quantities are well-defined and can be
+measured in both dimensions, while their relation with the dielectric
+property varies with dimensionality. The well-known examples are the
+different Wannier-Mott laws for exciton binding energy
+\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
+proposed here, and the distinct power laws for van der Waals
+interactions \cite{Gobre_2013}. To get a accuracy description of
+dielectric-related properties of the 2D materials and their
+heterostructures, one has to distinguish between the 2D and 3D
+properties, and choose a suitable relation with the
+dimension-dependent and dimension-independent quantities.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
+\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
+  both 2D (red circle) and 3D (cyan circle) systems. The
+  dimension-dependent quantities can be related with $\alpha_{\mathrm{2D}}$ and
+  $\varepsilon$, respectively. The intersection between the circles
+  present the quantities are well-defined in both dimensions, but may have a
+  different scaling relation with others quantities.}
+\end{figure}
 
@@
 \label{sec:raw}
-
+\todo[inline]{I think showing the $\alpha$ values is enough since
+  whoever interested in calculating the $r_{0}$ values can simply
+  multiply them by $2 \pi$. }
 \input{raw_data}

### 2018-11-15 paper.tex
Move 2D-3D graph to SI

@@
 \todo[inline]{Wait for comments from JC and MC.}
-\iffalse
-Finally, we would like to comment on the implications of this work for
-the experiments concerning the dielectric properties of 2D materials.
-As schematically shown in Figure \ref{fig-2D-3D}, the physical
-quantities related to the dielectric properties can be categorized
-into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
-(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
-starting point for the strictly 2D and 3D quantities, which require
-distinct definitions when dimensionality changes. Such quantities
-include (but not limited to):
-\begin{enumerate}
-\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
-  charge, polarization, electronic states, etc.
-
-\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
-  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
-  details see Supplementary Section S4.4).
-
-\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
-  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
-\end{enumerate}
-These quantities have distinct units in both dimensions, and related
-by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
-plasma frequency), which requires prudent interpretation of
-theoretical and experimental results. For instance, the experimentally
-observed ``dielectric constant'' of monolayer 2D materials
-\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
-without considering the effect of mix ted medium. Instead, the 2D slab
-polarizability, either transformed from the vacuum-containing
-macroscopic dielectric constant, or predicted from the bandgap and
-geometry as proposed here, will be a better descriptor for the true 2D
-dielectric nature. On the other hand, there are also
-dimension-independent quantities that valid for both 2D and 3D
-systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
-energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
-as well as the Hamaker constant of van der Waals interaction
-$A_{\mathrm{H}}$. All these quantities are well-defined and can be
-measured in both dimensions, while their relation with the dielectric
-property varies with dimensionality. The well-known examples are the
-different Wannier-Mott laws for exciton binding energy
-\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
-proposed here, and the distinct power laws for van der Waals
-interactions \cite{Gobre_2013}. To get a accuracy description of
-dielectric-related properties of the 2D materials and their
-heterostructures, one has to distinguish between the 2D and 3D
-properties, and choose a suitable relation with the
-dimension-dependent and dimension-independent quantities.
-\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}
-\fi
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
-\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
-  both 2D (red circle) and 3D (cyan circle) systems. The
-  dimension-dependent quantities can be related with $\alpha$ and
-  $\varepsilon$, respectively. The intersection between the circles
-  present the quantities are well-defined in both dimensions, but may have a
-  different scaling relation with others quantities.}
-\end{figure}
 \end{document}

### 2018-11-15 SI.tex
Correct minor grammatic errors

@@
 % \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
-\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kindom}
+\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
 \author{Elton J. G. Santos}
@@
 
-\title{Universal Understanding of the Dielectric Nature of Two-Dimensional Materials}
+\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
 \begin{document}
@@
 \item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
-\item $\alpha_{\mathrm{2D}}$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
+\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
 \item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.
@@
 HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
-relation is better presented by using the minimal HSE bandga than the
+relation is better presented by using the minimal HSE bandgap than the
 minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
@@
 about 50 types of materials. It is desirable to validate our proposed
-relations on a even larger scale database. We select over 230
+relations on an even larger scale database. We select over 230
 semiconducting 2D materials from the C2DB database with a GW bandgap
 larger than 0.05 eV and extracted the 2D polarizabilities calculated
-on the PBE level. The propsed linear relations between
+on the PBE level. The proposed linear relations between
 $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
@@
   \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
-  \caption{$\alpha_{\mathrm{2D}}^{\parallel}$ as funtion of minimal and direct
+  \caption{$\alpha_{\mathrm{2D}}^{\parallel}$ as function of minimal and direct
     $E_{\mathrm{g}}$ calculated on different theoretical levels:
@@
 $E_{\mathrm{g}}^{\mathrm{opt}}$, is usually lower than the direct
-bandgap from bandstructure $E_{\mathrm{g}}^{\mathrm{dir}}$ by the
+bandgap from band structure $E_{\mathrm{g}}^{\mathrm{dir}}$ by the
 exciton binding energy $E_{\mathrm{b}}$, which is at the 10$^{-1}$ to
@@
 framework that leads to the 2D Moss-like relations proposed in the
-main text.  Due to its highly anisotropic nature, the wavefunction of
+main text.  Due to its highly anisotropic nature, the wave function of
 an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
@@
 For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
-wavefunctions as plane wave with form
+wave functions as plane wave with form
 $\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
@@
 
-The out-of-plane wavefunction $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
+The out-of-plane wave function $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
 Hamiltonian $\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where
 $\hbar$ is the reduced Planck constant, $m_{e}$ is electron mass and
-$V(z)$ is the confined Coulombic potential along the z-direction
+$V(z)$ is the confined Coulomb potential along the z-direction
 created by the nuclei
@@
 well, which may be tedious. Nevertheless the simple model presented
-here still captures the bandgap-indepent and thickness-related feature
+here still captures the bandgap-independent and thickness-related feature
 of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
@@
     z-direction. The positive and negative induced charges from inner
-    atoms cancel out. Right: simplied model for the thickness
+    atoms cancel out. Right: simplified model for the thickness
     dependency of $\alpha_{\mathrm{2D}}^{\perp}$, where the surface dipole density
@@
 indeed be explained by modern theory of dielectric properties. From
-the 2D material to a bulk covalent semiconductor, the wavefunction
+the 2D material to a bulk covalent semiconductor, the wave function
 becomes periodic in all directions. Considering only one pair of
@@
 extending the approach Eq. \ref{eq:alpha_perp_RPA} to the bulk
-material, and using the Bloch presentation for wavefunctions in all
+material, and using the Bloch presentation for wave functions in all
 dimensions, we get \cite{Jiang_2017_Eg_Eb}:
@@
 \item Planar OSc \\
-  The planar OScs include metal phthanocyanines, disk-like polycyclic
+  The planar OScs include metal phthalocyanines, disk-like polycyclic
   aromatic hydrocarbon (PAHs), and benzene derivatives. The
@@
   Like 2D materials, CNTs are periodic along the 1D directions, and
-  shoudl be treated in a similar way to get the polarizability
+  should be treated in a similar way to get the polarizability
   proportional to [Length]$^{2}$ \cite{Benedict_1995}. Semiconducting
@@
 \item Linear OSc \\
-  We choose the linear polyacenes (linear PAHs from benznene to
+  We choose the linear polyacenes (linear PAHs from benzene to
   nonacene) and zigzag polyacetylene (1--9 repeating units) as model
@@
 \item Fullerenes \\
-  The bandgap of fullerens (C$_{n}$ where $n=60*m^{2}$ where
+  The bandgap of fullerenes (C$_{n}$ where $n=60*m^{2}$ where
   $m=1\sim{}7$) are taken from \citenum{Lin_1994} and the
@@
 
-\subsection{Bandstructures of 2D materials calculated}
+\subsection{Band structures of 2D materials calculated}
 \label{sec:bs}

### 2018-11-15 paper.tex
Correct minor grammatic errors

@@
 index, Bohr radius, exciton binding energy, etc.) of a bulk material
-from the its bandgap with with a reasonable degree of certainty
+from the its bandgap with a reasonable degree of certainty
 % The
@@
 $\varepsilon_{\mathrm{SL}}^{\perp} =
-\varepsilon_{\mathrm{SL}}^{zz}$. The absense of bonding perpendicular
+\varepsilon_{\mathrm{SL}}^{zz}$. The absence of bonding perpendicular
 to the 2D plane confines the induced dipoles along the
@@
 \AA{}. In addition, as shown Figure \ref{fig-1}d and \ref{fig-1}e,
-respectivel, the model-predicted
+respectively, the model-predicted
 $\varepsilon_{\mathrm{SL}}^{\parallel}-L$ and
@@
 the main conclusions of this work.  \todo[inline]{I not sure if we
-  need to show the proportional coefficiens
+  need to show the proportional coefficients
   here. $\alpha_{2D}^{\perp}$ is almost certain to be
@@
 dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
-a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
+a metal in groups 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
 (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
@@
 \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
-materials investiaged (circle dots), with a linear regression
+materials investigated (circle dots), with a linear regression
 coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
@@
 estimation of both dielectric properties and bandgap can be achieved
-via many-body Green’s function method (GW) together with the
+via many-body Green's function method (GW) together with the
 Bethe-Salpeter equation (BSE), the convergence of such method is known
@@
 number of materials used, we further validate our proposed 2D
-Moss-like relations on the recently-published C2DB database
+Moss-like relations on the recently published C2DB database
 \cite{Haastrup_2018}, from which we extracted the dielectric
@@
 superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
-(details see Supplementary Section \ref{SI-sec:gpaw-1}). Althought the
+(details see Supplementary Section \ref{SI-sec:gpaw-1}). Although the
 dielectric properties may be overestimated at PBE level due to
@@
 $\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
-characteristic lengthes, respectively. The in-plane screened
+characteristic lengths, respectively. The in-plane screened
 electrostatic potential $V(r)$ from a point charge in an 2D plane, as
@@
 \varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
-to the simple Coulombic potential in vacuum. Combining with the result
+to the simple Coulomb potential in vacuum. Combining with the result
 that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
@@
 $r_{0}^{\parallel}$ is generally larger for a smaller bandgap
-semiconductor, which qualitatively explains the inverse propotional
+semiconductor, which qualitatively explains the inverse proportional
 relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
@@
 further bridge the 2D and 3D dielectric and electronic properties in
-various ways. Using the similar appraoch as we derive the 2D Moss-like
+various ways. Using the similar approach as we derive the 2D Moss-like
 relations, we show that the
@@
 stacked. \todo[inline]{I would appreciate for polishing this sentence}
-In a bulk layered materil stacked by layers with equilibrium
+In a bulk layered material stacked by layers with equilibrium
 inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
@@
 its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
-to interlayout coupling and overlap between induced
+to interlayer coupling and overlap between induced
 dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
@@
 \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
-Augmented Wave (PAW) approach with Kresse’s mainly GW
+Augmented Wave (PAW) approach with Kresse's mainly GW
 Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
@@
   $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
-  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
   the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
-  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
+  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
   the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
@@
     dielectric nature of 2D
-    materials}. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
+    materials}. \textbf{a}. The structures of the 2D materials investigated in this study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
   (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
@@
   $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
-  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
+  observed. \textbf{c}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
   (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
@@
   shown in the
-  background. \textbf{c}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
+  background. \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
   \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
@@
   with slope very close to $1/4\pi$. The universal scaling relation is
-  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
-  and \textbf{c}.}
+  also revealed using the C2DB database (squares), as superimposed on \textbf{c}
+  and \textbf{d}.}
 \end{figure}
@@
     their bulk counterparts (orange square) can be distinguished by
-    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
+    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
     semiconducting materials in other dimensions are also superimposed

### 2018-11-15 SI.tex
Fix missing cross-ref links

@@
   \caption{Validation the linear relation between \textbf{a}
-    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
-    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
-    database, corresponding to Figure 3b and 3c in main text.}
+    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
+    and \textbf{b}
+    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB
+    2D material database, corresponding to Figure \ref{main-fig-3}c
+    and \ref{main-fig-3}d in main text.}
   \label{fig:gpaw-alpha-relation}
@@
 $n_{\mathrm{3D}}$ is the 3D number density of valence
-electrons. Combine Eq. \ref{eq:eps-plas-3D} with Eq. 3 in main text,
-we get:
+electrons. Combine Eq. \ref{eq:eps-plas-3D} with main text
+Eq. \ref{main-eq:alpha-para-def}, we get:
 \begin{equation}

### 2018-12-15 paper_tian_20181214.tex
Implement changes from Elton 20181212

% Created 2018-09-26 Wed 21:07
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage{times}

%\usepackage{xr}
%\externaldocument{SI_v112818}
\usepackage{xr-hyper} 
%\usepackage{zref-xr}
\externaldocument{SI_v120518}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

\newpage{}

% \section{Introduction}
% \label{sec:org2ea169d}
\linenumbers{}

{\bfseries The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in describing electromagnetic interactions
  through screening plays a critical role in understanding fundamental
  molecular interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. We found instead that
  the electric  polarizability correctly
  captures the dielectric nature of a 2D material which is united to
  other physical quantities in an atomically thin layer. We reveal a
  long-sought universal formalism where electronic, geometrical and
  dielectric properties are intrinsically correlated through the
  polarizability opening the door to probe quantities yet not directly
  measurable including the real covalent thickness of a layer. We
  unify the concept of dielectric properties in any material dimension
  finding a global dielectric anisotropy index defining their
  controllability through dimensionality.  }

The dielectric constant $\varepsilon$ (also known as the relative
permittivity) plays a crucial role in bridging various fundamental
material properties, such as bandgaps, optical absorption, and
conductivities.  \todo{Add more citations} $\varepsilon$ characterizes
the ability to screen an electric field $\boldsymbol{E}$ which
classifies metals, semiconductors and insulators.  \todo[inline]{I
  shortened the sentences. However, can we really "classify" the
  material only by $varepsilon$? For instance HfO2 has large
  $\varepsilon$ but also large bandgap}
% Such definitions determine a broad range of
% condensed matter physics, as well as in related fields in chemistry
% and materials science.
The ability to compute and measure
$\varepsilon$ in bulk materials is well established via different
theoretical and experimental techniques of distinct flavors where the
probe of the dielectric properties is made through an external
electric field.
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or only an 
additional parameter from the bulk-counterparts. 
%%
%%
We approach this problem showing that the current definition of
$\varepsilon$ used in layered materials is ill defined as illustrated
in Figure \ref{fig-1}.  From the theoretical point of view, an
isolated 2D material is placed in the \textit{xy}-plane of a
periodically repeating superlattice (SL) with a length $L$ along the
\textit{z}-direction separating the cell images. The static macroscopic
dielectric tensor from the superlattice
$\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
electrostatics by the response of the polarization density
$\boldsymbol{P}^{p}$ under small perturbative external field
$\boldsymbol{E}^{q}$, where $p$, $q$ are the directions of
polarization and electric field,
respectively\cite{Dressel_2001_electrodynamics}:
\begin{subequations}
  \begin{eqnarray}
      \label{eq:def-eps-1}
    &\varepsilon^{pq} &= \kappa^{pq} +
                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
                                 {\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
          \label{eq:def-eps-2}
    &\boldsymbol{P}^{p} &=  {\displaystyle \frac{\boldsymbol{u}^{p}}{\Omega}}
                          = {\displaystyle \frac{{\displaystyle
          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}
                          {AL}}
  \end{eqnarray}
\end{subequations}
where $\kappa$ is the dielectric tensor of the environment,
$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is
the spatial charge density, $\Omega=AL$ is the volume of the
supercell, $A$ is the \textit{xy}-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. Here we only study the
electronic contribution to the dielectric constant where the dipole
$\boldsymbol{P}$ comes from the displacement of electron cloud under
external electric field. For the majority of 2D nonmetals, the
off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
negligible \todo[inline]{why only nonmetals?  Could you cite one
  reference?}.  Considering that the 2D material is placed in vacuum
($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
components, namely the in-plane
($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
$\varepsilon_{\mathrm{SL}}^{\parallel} =
(\varepsilon_{\mathrm{SL}}^{xx} + \varepsilon_{\mathrm{SL}}^{yy})/2$
and
$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$.
The absence of bonding perpendicular to the plane confines the induced
dipoles along the \textit{z}-direction as the charge density
difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$, at zero and
finite electric fields
($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf
  a}). When $L$ is large enough, the induced dipoles $\boldsymbol{u}$
from the periodic images do not interact mutually as the integral in
Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge
density at the layer.  However, we can see from
Eqs. \ref{eq:def-eps-1} that both
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
the cell $\Omega$.  Therefore, any calculation performed using such
definition will intrinsically depend on the magnitude of $L$ as an
additional parameter.  This dependence can be clearly demonstrated by
plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
theory (DFT) using hybrid functionals (see {\it Methods} for details)
as a function of $L$ for P$\bar{6}$m2 transitional metal
dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
(top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c},
respectively).  Despite of the magnitudes of $L$ both components of
the dielectric constant change systematically without a clear
convergence.
%
Simulations performed at higher levels of theory using many-body
techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}),
and also taking into account electron-hole excitations at the level of
the Bethe-Salpeter equation (BSE) for the frequency-dependent
$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
results (Supplementary Figure \ref{fig:S2}). Moreover, due to the long
range Coulomb interaction, variations of the quasi-particle energy
(and corresponding peak positions) with lattice constant $L$ at the
G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
SXX). Such results implicate that several other related quantities,
including the optical absorption and optical conductivity, suffer the
same deficiencies, which should be avoided in a fully first principles
theory.
%
%
%
%as the computation of the dielectric function is based on alike formalism\cite{Ehrenreich-Cohen paper}
% We can understand this behavior in terms of the electrostatic of the problem. 
%
%
%
%This result indicates that the use of the dielectric constant to represent 
%dielectric properties at the static limit of a 2D material is 
%ambiguous as the long-range correlations between the layers would only 
%be negligible at the limit of $L \rightarrow \infty$, which incidentally modify the magnitudes of 
%$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ in the convergence. 
%
It is worth mentioning that experimental dielectric results of 2D
materials generally need to define an ``effective thickness'' of the sheet
to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
extract information for the real part of the dielectric functions.  We
argue that such procedure may induce inevitably variations of the
results as the thickness is normally chosen by the interlayer spacing
of the respective bulk materials (details see Supplementary Section
\ref{sec:2D-3D-rescale}).
%
%%%
%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.
%
%
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 
%

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability
and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.

%\subsection*{Polarizability as the fundamental variable}
%\label{sec:first-principles}

%We consider

As a consequence of Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, we can demonstrate 
that other quantities are intrinsically related to the polarizability. 
Using random phase approximation (RPA)
theory \cite{Adler_1962} within the $\mathbf{k} \cdot \mathbf{p}$
formalism\cite{kittel_2005_introduction} (see Supplementary
Section \ref{sssec:theory-1} and  \ref{ssec:theory-2} for details), 
we can show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
can be written as: 
%
%
%
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \delta
\end{eqnarray}
\end{subequations}
%
%
%
%
where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf
  a}), and $C^{\parallel} = \frac{Ne^2}{2 \pi}$, where $N$ corresponds to
the degeneracy of the bands associated with $E_{\mathrm{g}}$, and
$C^{\perp} = {\varepsilon_{0}}$.  \todo[inline]{The previous
  expressions for the coefficients are wrong. Please see the version
  in SI.} Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
the polarizability and the electronic and structural properties for
any 2D material in a new framework.  We can show that these equations
are valid for the current library of known layered materials involving
different lattice symmetry, element composition, optical and
electronic properties.
%
A high-throughput screening performed on 
different families of TMDCs (MX\(_{\text{2}}\), where M is
a metal in groups 4, 6, 10, and X=O, S, Se, Te) and phases (P\(\bar{6}\)m2, P3m1), 
metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$) (Fig. \ref{fig-3}{\bf a}) 
shows that our method enables full correlation between these disparate variables. 
%%
%
%Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are the main conclusions of this work. 
%
% \todo[inline]{I not sure if we need to show the proportional coefficients
%  here. $\alpha_{2D}^{\perp}$ is almost certain to be
%  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
%  a more complex coefficient.}
%
%
%
%The static 2D
%polarizabilities are calculated from the static dielectric response of
%the selected 2D materials (see {\it Methods}). 
Figure \ref{fig-3}{\bf b} compares the calculated fundamental bandgap
$E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar
plots) of all the 2D materials investigated, covering a wide spectrum
range from far-infrared to ultraviolet.  Note from dimension analysis,
it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases, while no apparent
correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with
elements having large polarizabilities, such as Hf and Zr in
1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
for the layers with slightly variations between 1T and 2H phases. The
former normally shows larger values of
$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
\todo[inline]{sorry but I don't quite get the idea of this
  sentence. In fact HfO2 and ZrO2 have quite low in-plane
  polarizabilities compared with even TiO2. Shall we just remove these
  sentenses? }
%
% 
We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
first-principle calculations. 
Figure \ref{fig-3}{\bf c} shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investigated (circle dots).  
A linear regression coefficient of $R^{2}=0.84$ indicates a 
strong correlation between bandgaps and polarizabilities as predicted in 
Eq. \ref{eq:2D-Moss-para}. 
We also discover that
the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functional\cite{Heyd_2005} compared
with that from Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
(see Supplementary Section \ref{sec:pol-2D-Eg} and
Supplementary Figure \ref{fig:alpha-Eg-diff}) which suggests that higher levels 
of theory are needed to predict bandgaps as it is normally the case.   
We also show
that the proposed Eq. \ref{eq:2D-Moss-para}
behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{sec:gpaw-2} and Supplementary Figure
\ref{fig:opt}).

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
This results indicate that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
physical meaning through the geometry of the layer.  Similar to the
molecular polarizability which characterizes the volume of electron
cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section \ref{sssec:theory-3}). Indeed, the
universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
Figure \ref{fig-3}{\bf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic and optical approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
is in reality the (dielectric) characteristic thickness of a 2D
material, and can be used to resolve the long-existing controversy
about the experimental thickness of 2D materials, such as graphene
\cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
database\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\bf c} and
\ref{fig-3}{\bf d} (see details in Supplementary Section
\ref{sec:gpaw-1}). Although the dielectric properties may be
overestimated at PBE level due to underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results (see
details in Supplementary Section \ref{sec:gpaw-2}).

We have also searched for additional relations between the 2D
polarizabilities with other physical quantities, including the
effective carrier mass, quantum capacitance (density of states) and
total atomic polarizabilities with no apparent correlations being
found (Supplementary Section \ref{sec:gpaw-3}).  We found however that
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
connection with the screening properties of the layer.
%
In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], that is, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengths, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge as
a function of distance $r$: 
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively. This is analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure \ref{fig:ellipsoid}). The polarizability ellipsoid for a 2D
material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}.  Moreover,
$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse proportional
relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ seen in Eq. \ref{eq:2D-Moss-para}. 
This gives a geometrical interpretation of the bandgap in terms 
of the screening radius of the layer.

%\subsection{Bridging the 2D and 3D Dielectric Properties}
%\label{sec:2D-3D}

We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
%The dielectric constant $\varepsilon$, although not well-defined for
%a monolayer 2D material, becomes applicable when the 2D layers are
%stacked. 
%
%
%
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\bf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
These approximations assume that the strong interactions 
occur in-plane and the interlayer stacking is not a critical factor.
\todo{??}
The dielectric constant $\varepsilon$ although not well-defined for
a monolayer 2D material becomes applicable when the 2D layers are
put together. 
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

Finally, we show that a general picture of the dielectric properties in
any dimension can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
index of corresponding 2D layer (see additional details in Supplementary Section
\ref{sssec:aniso-2}), which is the basis for the separation of bulk
and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
comparison, we also superimpose the dielectric anisotropy indices
$\eta$ of common semiconducting materials in other dimensions 
(Supplementary Section \ref{sssec:aniso-1}) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.

%
%\subsection{Implications for Experiments}
%\todo[inline]{Wait for comments from JC and MC.}

%\section{Conclusion}
%\label{sec:org5fd1f1a}
%\todo[inline]{To be changed later when everything fixed}

Our results show that the 2D electric polarizability
$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
properties of 2D materials.  There exist well defined relationships
between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
electronic properties.  According to our analysis, simple scaling
equations involving bandgaps and layer thicknesses can be used to
describe both dielectric and electronic features at the same
footing. A dielectric anisotropy index is found relating any material
dimension with its controllability.  Thus, our results suggest that
the challenge of understanding the dielectric phenomena is in general
a geometrical problem mediated by the bandgap. We believe the
principles presented here will benefit both fundamental understanding
of 2D materials as well as rational device design and optimization.

\section{Theoretical Methods}
\label{sec:org8457dbb}

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse's mainly GW Pseudopotentials
\cite{Kresse_1999_pseudopotentials}. Band gaps were calculated using
the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. The materials from Ref. \citenum{Haastrup_2018} for comparison
were choses with the GW bandgap larger than 0.05 eV. Bulk layered
materials were constructed by relaxing the c-axis length of
corresponding monolayer material with the interlayer van der Waals
(vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of the C2DB
database are calculated at PBE level with a k-point density of 10
\AA$^{-1}$.

\bibliography{ref}

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
% \includegraphics[width=0.75\linewidth]{}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
% \caption{\label{fig-2} The elements and 3D structures of the 2D
  % materials investigated in this study.}
% \end{figure}

\begin{figure}[H]
\centering
% \includegraphics[width=0.70\linewidth]{}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. The structures of the 2D materials investigated in this study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{c}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{c}
  and \textbf{d}.}
\end{figure}

\begin{table}[H]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & &  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

\begin{figure}[H]
\centering
% \includegraphics[width=1.04\linewidth]{}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

\begin{figure}[H]
  \centering
  % \includegraphics[width=1.05\linewidth]{}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}

\end{document}

### 2018-12-15 src/VASP_HSE/polarizability_histo.py

@@ -26,7 +26,7 @@ for entry in data:
 # alpha = numpy.array(alpha)
 # Eg = numpy.array(Eg)
 
-fig = plt.figure(figsize=(6.5, 3.2))
+fig = plt.figure(figsize=(8, 4.0))
 plt.style.use("science")
 
 ax1 = fig.add_subplot(111)
@@ -40,10 +40,10 @@ Eg = [e for e, a, n in res]
 
 xx = numpy.arange(0, len(maters))
 
-for r in numpy.linspace(0.12, 0.20, 100):
-    a_model = model_alpha(numpy.array(Eg), r)
-    ax1.plot(xx +0.5, a_model, color="cyan",
-             alpha=0.2)
+# for r in numpy.linspace(0.12, 0.20, 100):
+    # a_model = model_alpha(numpy.array(Eg), r)
+    # ax1.plot(xx +0.5, a_model, color="cyan",
+             # alpha=0.2)
 
 ax2.plot(Eg, "o-", markersize=6)
 ax1.bar(xx, ax, color="#FFCC00", alpha=0.7)
@@ -51,7 +51,7 @@ ax1.bar(xx, az, color="#FF5555", alpha=0.5)
 ax1.set_xticks(range(0, len(maters)))
 mnames = [n[0] + n[1:].replace("2", "$_{2}$") for n in maters]
 ax1.set_xticklabels(mnames, rotation="vertical")
-ax1.set_ylim(0, 13)
+ax1.set_ylim(0, 11)
 plt.tight_layout()
 plt.savefig("../../tmp_img/all_data.svg")
 

### 2018-12-15 src/post_processing/compile_data.py

@@ -4,6 +4,7 @@ import numpy
 from ase.data import covalent_radii
 from ase.dft.bandgap import bandgap
 from ase.io.trajectory import Trajectory
+from ase.io import read
 from gpaw import GPAW
 from ase.dft.bandgap import bandgap
 import os, os.path
@@ -64,8 +65,10 @@ def get_bulk(name, proto):
             d = Trajectory(traj_file)[-1].cell[-1][-1]
         except Exception:
             print(Exception)
-            calc = GPAW(gpw_file)
-            d = calc.get_atoms().cell[-1][-1]
+            c_atoms = read(gpw_file)
+            # calc = GPAW(gpw_file)
+            d = c_atoms.cell[-1][-1]
+            # d = calc.get_atoms().cell[-1][-1]
         f = numpy.load(eps_file)
         eps_xx = f["eps_x"][0].real
         eps_zz = f["eps_z"][0].real
@@ -99,7 +102,11 @@ for row in reader:
         ax = (e_xy - 1) / (4 * pi) * L
         az = (1 - 1/ez) * L / (4 * pi)
         mol = list(db.select(formula=name, prototype=proto))[0]
-        delta, n_2D = get_thick(mol)
+        if proto == "ABX3":     # perovskite?
+            delta = 14.24
+            n_2D = None
+        else:
+            delta, n_2D = get_thick(mol)
         # 3D
         try:
             L_3D, epsx, epsz, E_3D = get_bulk(name, proto)

### 2018-12-15 src/distance/compare_GW_zero_freq.py
Add script for plot of GW results

@@ -1,0 +1,79 @@
+import numpy
+import matplotlib.pyplot as plt
+import os
+
+gw_in = numpy.array([[20, 1.4114],
+                     [30, 1.2706],
+                     [40, 1.2018],
+                     [50, 1.1599],
+                     [60, 1.1326]])
+
+gw_out = numpy.array([[20, 1.2103],
+                      [30, 1.1385],
+                      [40, 1.1031],
+                      [50, 1.0815],
+                      [60, 1.0671]])
+
+pbe_in = numpy.array([[20, 1.6458],
+                      [30, 1.4297],
+                      [40, 1.3225],
+                      [50, 1.257],
+                      [60, 1.2139]])
+
+pbe_out = numpy.array([[20, 1.2852],
+                       [30, 1.1892],
+                       [40, 1.1413],
+                       [50, 1.112],
+                       [60, 1.0925]])
+
+plt.style.use("science")
+
+plt.figure(figsize=(6, 3.5))
+
+plt.subplot(221)
+plt.xlabel("$L$ ($\\rm{\\AA}$)")
+plt.ylabel("$\\varepsilon_{\\rm{SL}}^{\parallel}$")
+L_pbe = pbe_in[:, 0]
+eps_pbe = pbe_in[:, 1]
+L_gw = gw_in[:, 0]
+eps_gw = gw_in[:, 1]
+plt.plot(L_pbe, eps_pbe, "-o", label="PBE")
+plt.plot(L_gw, eps_gw, "-o", label="G$_{0}$W$_{0}$")
+plt.legend()
+
+plt.subplot(222)
+plt.xlabel("$L$ ($\\rm{\AA}$)")
+plt.ylabel("$\\alpha_{\\rm{2D}}^{\parallel}/(4 \pi \\varepsilon_0)$ ($\\rm{\\AA}$)")
+alpha_pbe = (eps_pbe - 1) * L_pbe / (4 * numpy.pi)
+alpha_gw = (eps_gw - 1) * L_gw / (4 * numpy.pi)
+plt.plot(L_pbe, alpha_pbe, "-o", label="PBE")
+plt.plot(L_gw, alpha_gw, "-o", label="GW")
+plt.ylim(0.5, 1.2)
+
+
[…]

### 2018-12-15 src/distance/compare_eps_bse.py

@@ -1,0 +1,80 @@
+import numpy
+import os
+import matplotlib.pyplot as plt
+
+
+def calc_alpha_freq(L=20,
+                    direction="in_plane",
+                    method="BSE",):
+    assert direction in ("in_plane", "out_of_plane")
+    # assert method in ("PBE", "GW")
+    base_dir = os.path.join(os.path.dirname(__file__),
+                            "../../data/distance/GW/BSE/{0:d}/{1}/".format(L,
+                                                                        direction))
+    img_file = os.path.join(base_dir, "{}_imaginary_epsilon.dat".format(direction))
+    real_file = os.path.join(base_dir, "{}_real_epsilon.dat".format(direction))
+    img_data = numpy.genfromtxt(img_file)
+    real_data = numpy.genfromtxt(real_file)
+    freq = img_data[:, 0]
+    eps = real_data[:, 1] + 1j * img_data[:, 1]
+    if direction == "in_plane":
+        alpha = (eps - 1) * L / (numpy.pi * 4)
+    else:
+        alpha = (eps - 1) * L / (numpy.pi * 4)
+    return freq, alpha, eps
+
+def main(method="BSE", direction="in_plane"):
+    fig = plt.figure(figsize=numpy.array((6, 4)) * 1.2)
+    ax1 = fig.add_subplot(221)
+    ax2 = fig.add_subplot(222)
+    ax3 = fig.add_subplot(223)
+    ax4 = fig.add_subplot(224)
+    for ax in [ax1, ax2, ax3, ax4]:
+        ax.set_xlabel("Energy (eV)")
+    if method == "GW":
+        if direction == "in_plane":
+            lim = [8, 12]
+        else:
+            lim = [13, 17]
+    else:
+        if direction == "in_plane":
+            lim = [4, 8]
+        else:
+            lim = [8, 12]
+    # for ax in [ax3, ax4]:
+        # ax.set_xlim(6, )
+    # Set ylabel
+    if direction == "in_plane":
+        tag = "\\parallel"
+    else:
+        tag = "\\perp"
+        
+    ax1.set_ylabel("Re $\\varepsilon^{{{0}}}_{{\\rm{{SL}}}}(\\omega)$".format(tag))
[…]

### 2018-12-15 src/distance/compare_eps_freq.py

@@ -1,0 +1,81 @@
+import numpy
+import os
+import matplotlib.pyplot as plt
+
+
+def calc_alpha_freq(L=20,
+                    direction="in_plane",
+                    method="PBE",):
+    assert direction in ("in_plane", "out_of_plane")
+    assert method in ("PBE", "GW")
+    base_dir = os.path.join(os.path.dirname(__file__),
+                            "../../data/distance/GW/{0}/{1:d}/{2}/".format(method,
+                                                       L,
+                                                       direction))
+    img_file = os.path.join(base_dir, "{}_imaginary_epsilon.dat".format(direction))
+    real_file = os.path.join(base_dir, "{}_real_epsilon.dat".format(direction))
+    img_data = numpy.genfromtxt(img_file)
+    real_data = numpy.genfromtxt(real_file)
+    freq = img_data[:, 0]
+    eps = real_data[:, 1] + 1j * img_data[:, 1]
+    if direction == "in_plane":
+        alpha = (eps - 1) * L / (numpy.pi * 4)
+    else:
+        alpha = (eps - 1) * L / (numpy.pi * 4)
+    return freq, alpha, eps
+
+def main(method="PBE", direction="in_plane"):
+    fig = plt.figure(figsize=numpy.array((6, 4)) * 1.2)
+    ax1 = fig.add_subplot(221)
+    ax2 = fig.add_subplot(222)
+    ax3 = fig.add_subplot(223)
+    ax4 = fig.add_subplot(224)
+    for ax in [ax1, ax2, ax3, ax4]:
+        ax.set_xlabel("Energy (eV)")
+    if method == "GW":
+        if direction == "in_plane":
+            lim = [8, 12]
+        else:
+            lim = [13, 17]
+    else:
+        if direction == "in_plane":
+            lim = [4, 8]
+        else:
+            lim = [8, 12]
+    # for ax in [ax3, ax4]:
+        # ax.set_xlim(6, )
+    # Set ylabel
+    if direction == "in_plane":
+        tag = "\\parallel"
+    else:
+        tag = "\\perp"
+        
+    ax1.set_ylabel("Re $\\varepsilon^{{{0}}}_{{\\rm{{SL}}}}(\\omega)$".format(tag))
[…]

### 2018-12-15 src/VASP_HSE/relation_alpha.py
Change panels for figure 2

@@ -54,8 +54,11 @@ for row in reader:
             eps_x.append(e_xy); eps_z.append(ez)
             alpha_x.append(ax); alpha_z.append(az)
             Eg_HSE.append(E)
-            mol = list(db.select(formula=name, prototype=proto))[0]
-            thick.append(get_thick(mol))
+            if proto == "ABX3":
+                thick.append(10.58)
+            else:
+                mol = list(db.select(formula=name, prototype=proto))[0]
+                thick.append(get_thick(mol))
 
 print(len(alpha_x))
 alpha_x = numpy.array(alpha_x)
@@ -71,16 +74,19 @@ thick = thick[cond]
 
 colors = {"MoS2": "#AA0000", "CdI2": "#2C5AA0",
           "GaS": "#FFCC00", "BN": "#A05A2C",
-          "P": "#447821", "CH": "#FF6600"}
+          "P": "#447821", "CH": "#FF6600",
+          "ABX3": "#6600FF"}
 
+print(materials)
 cs = [colors[mat.split("-")[-1]] for mat in materials]
+print(cs)
 
 img_path = "../../tmp_img/"
 plt.style.use("science")
 
-plt.figure(figsize=(7, 3.5))
-plt.subplot(121)
-plt.scatter(Eg_HSE, alpha_x, marker="o", alpha=0.5, c=cs)
+# plt.figure(figsize=(7, 3.5))
+# plt.subplot(121)
+# plt.scatter(Eg_HSE, alpha_x, marker="o", alpha=0.5, c=cs)
 def fit_func(x, a,b):
     return b / x
 '''
@@ -160,6 +166,7 @@ xx = numpy.linspace(min(gp_data[3]), max(gp_data[3]))
 yy = res.slope * xx + res.intercept
 ax.plot(xx, yy, "--")
 # plt.colorbar()
+ax.set_ylim(0.12, 0.80)
 ax.set_title("$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
 ax.set_xlabel("Thickness ($\\AA$)")
 ax.set_ylabel("$\\alpha_{zz} / \\varepsilon_0$ ($\\AA$)")

### 2018-12-16 src/distance/compare_eps_bse.py
Update data on BSE

@@ -11,8 +11,8 @@ def calc_alpha_freq(L=20,
     base_dir = os.path.join(os.path.dirname(__file__),
                             "../../data/distance/GW/BSE/{0:d}/{1}/".format(L,
                                                                         direction))
-    img_file = os.path.join(base_dir, "{}_imaginary_epsilon.dat".format(direction))
-    real_file = os.path.join(base_dir, "{}_real_epsilon.dat".format(direction))
+    img_file = os.path.join(base_dir, "eps_imaginary_{}.dat".format(direction))
+    real_file = os.path.join(base_dir, "eps_real_{}.dat".format(direction))
     img_data = numpy.genfromtxt(img_file)
     real_data = numpy.genfromtxt(real_file)
     freq = img_data[:, 0]
@@ -38,9 +38,9 @@ def main(method="BSE", direction="in_plane"):
             lim = [13, 17]
     else:
         if direction == "in_plane":
-            lim = [4, 8]
+            lim = [6, 10]
         else:
-            lim = [8, 12]
+            lim = [11, 15]
     # for ax in [ax3, ax4]:
         # ax.set_xlim(6, )
     # Set ylabel
@@ -74,7 +74,8 @@ def main(method="BSE", direction="in_plane"):
 
 if __name__== "__main__":
     plt.style.use("science")
-    main("PBE", "in_plane")
+    main("BSE", "in_plane")
+    main("BSE", "out_of_plane")
     # main("PBE", "out_of_plane")
     # main("GW", "in_plane")
     # main("GW", "out_of_plane")

### 2018-12-16 src/VASP_HSE/relation_alpha.py
Add figures for BSE calculations`

@@ -55,7 +55,7 @@ for row in reader:
             alpha_x.append(ax); alpha_z.append(az)
             Eg_HSE.append(E)
             if proto == "ABX3":
-                thick.append(10.58)
+                thick.append(8.0)
             else:
                 mol = list(db.select(formula=name, prototype=proto))[0]
                 thick.append(get_thick(mol))

### 2018-12-16 SI.tex
Changes adapted from Elton 20181212

@@
 
-\usepackage{xr}
-\externaldocument[main-]{paper}
+%\usepackage{xr}
+%\externaldocument{paper_v112818}
+
+\usepackage{xr-hyper} 
+%\usepackage{xr}
+\externaldocument{paper_v120918fundamental}
 
@@
 
-\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
+\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
 \begin{document}
@@
 \newpage{}
-\section{Further Analysis of the 2D Polarizability Model}
-\label{sec:2D-pol}
-
-In this section, we discuss further topics about the 2D polarizability
-model proposed in the main text.
-
-\subsection{Profile of induced dipoles of 2D material}
-\label{sec:dipole-plot}
-Here we show in detail the
-$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
-the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}a. The
-density $\rho$ is calculated as the average value in the
-\textit{xy}-plane, and the value is shown in Figure
-\ref{fig:rho-profile}. As can be seen the induced charges on the
-MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
-SL size $L \gg$12 \AA{} as in the first principle calculations done in
-the main text, the induced dipoles from the periodic images do not
-interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
-  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
-    superlattice, corresponding to main text Figure
-    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
-    inside the SL separated by vacuum layer. The dielectric constant
-    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
-    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
-    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
-    MoS$_{2}$ layer, green and red parts corresponding to negative and
-    positive induced charges. The external electric field
-    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
-  \label{fig:rho-profile}
-\end{figure}
-
-\subsection{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
+%\section{Further Analysis of the 2D Polarizability Model}
+%\label{sec:2D-pol}
+
+%In this section, we discuss further topics about the 2D polarizability
+%model proposed in the main text.
+
+%\section{Profile of induced dipoles of 2D material}
+%\label{sec:dipole-plot}
+%Here we show in detail the
+%$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
+%the 2H-MoS$_{2}$ slab in main text Figure 1a. The
+%density $\rho$ is calculated as the average value in the
+%\textit{xy}-plane, and the value is shown in Figure
+%\ref{fig:rho-profile}. As can be seen the induced charges on the
+%MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
+%SL size $L \gg$12 \AA{} as in the first principle calculations done in
+%the main text, the induced dipoles from the periodic images do not
+%interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
+%
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
+%  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
+%    superlattice, corresponding to main text Figure
+%    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
+%    inside the SL separated by vacuum layer. The dielectric constant
+%    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
+%    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
+%    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
+%    MoS$_{2}$ layer, green and red parts corresponding to negative and
+%    positive induced charges. The external electric field
+%    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
+%  \label{fig:rho-profile}
+%\end{figure}
+
+\section{Table of Contents}
+
+1. Supplementary Figure \ref{fig:S1}:  Simulations of $\varepsilon_{\mathrm{SL}}$ using many-body $G_{\rm 0}W_{\rm 0}$   \\
+%
+%2. Supplementary Section \ref{epsilon-model}: $\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ dependence on $L$ \\ 
+%
+2. Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant \\
+%
+3. Supplementary Section \ref{ssec:theory-1}: Polarizability-Based Theoretical Model  \\ 
+%
+4. Supplementary Section \ref{sec:pol-2D-Eg}: Dependence of $\alpha_{\mathrm{2D}}$ on bandgap \\ 
+%
+5.
+
+\pagebreak{}
+
+\section{Calculations using many-body Green function method and frequency-dependent quantities $\alpha_{\mathrm{2D}}(\omega)$ and $\varepsilon_{\mathrm{SL}}(\omega)$}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/Fig-G0W0.pdf}
+  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
+calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
+}
+  \label{fig:S1}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
+  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
+Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
+many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
+with the only variable quantity being $L$. The systematic shift 
+}
+  \label{fig:S2}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ %\includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
+  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
+  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
+  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
+  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
+}
+  \label{fig:S3}
+\end{figure}
+
+%\section{$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ dependence on $L$}
+%\label{epsilon-model}
+%
+%Under an external electric field $\boldsymbol{E}$ the material forming the layer 
+%polarizes with a polarization $\mathcal{P}_{2D}=\chi_{2D}  \boldsymbol{E} $, where  
+%$\chi_{2D} $ is the electric susceptibility of the sheet. $\mathcal{P}_{2D}$ corresponds to a dipole moment 
+%in the 2D material 
+%of: 
+%
+%\begin{equation}
+%\label{P_2D}
+%\boldsymbol{u}_{2D}= \mathcal{P}_{2D} \Omega = (\chi_{2D}  \boldsymbol{E}) (A L)
+%\end{equation}
+%\\
+%From Eq. \ref{P_2D} we can calculate the dipole moment density  $\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$
+
+\pagebreak{}
+\section{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
 \label{sec:2D-3D-rescale}
@@
 where $f=\delta/L$ is the volume fraction of the 2D
-material in the superlattice. The major issue when using such rescale
+material in the superlattice and $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
+$\varepsilon_{\mathrm{2D}}^{\perp}$ are the corresponding dielectric constants for the 2D layer. 
+The major issue when using such rescale
 relations comes from the determination of $\delta_{\mathrm{2D}}$. To
@@
 
-\subsection{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
+%%%%%%\section{Theoretical Analysis}
+%%%%%%\label{sec:theory}
+\section{Polarizability-Based Theoretical Model}
+\label{ssec:theory-1}
+The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
+Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
+coincidence. Combining recent theoretical findings of the linear
+relation between exciton binding energy $E_{\mathrm{b}}$ and
+$E_{\mathrm{g}}$ of 2D materials
+\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
+fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
+$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
+to have a general Moss-like relation between
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
+the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
+resembles molecular polarizabilities of conjugate molecules
+\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
+nanotubes \cite{Benedict_1995}, which are also shown to be
+geometry-dependent.
+
+In this section we show in detail the polarizability-based theoretical
+framework that leads to the 2D Moss-like relations proposed in the
+main text.  Due to its highly anisotropic nature, the wave function of
+an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
+in- and out-of-plane components, similar to the treatment of quantum
+wells (QW),\cite{davies_physics_1997} such that
+$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
+$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
+is the in-plane coordinate. Using the Bloch theorem, the periodic
+$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
+$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
+  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
+in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
+in the xy-plane. According to the random phase approximation (RPA)
+theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
+$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
+dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
+$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
+\begin{equation}
+  \label{eq:RPA-eps2}
+  \varepsilon_{\mathrm{SL}}
+  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
+  \sum_{\mathrm{k, c, v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
+  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
+\end{equation}
+where $e$ is the unit charge, c, v are the conduction and valence
+bands, $E$ is the eigenenergy of individual bands, and $f$ is the
+Fermi-Dirac distribution function. Taking the
+limit that $L\to\infty$, when
+$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
+$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
+(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+at 0 K can be unified by the same equation:
+\begin{equation}
+  \label{eq:alpha-RPA}
+  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
+  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+where the direction is determined by $\mathbf{q}$. Next we will show
+that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
+give rise to the main text Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}.
+
+{\bf ES:} There is something weird with the cross-referencing for the equations 3a and 3b between the main text and 
+SI. They changed to 2a and 2b in the SI.
+
+\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-para-def} 3a}  %
+\label{sssec:theory-1}
+
+In this section we show how main text Eq. \ref{eq:alpha-para-def}
+is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
+$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
+of $z$, therefore the integral in
+$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
+becomes independent of $\psi^{\perp}$, due to the orthogonality
+and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
+only the cell-function $u(\mathbf{k})$ contributes to the final result
+of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
+that:
+\begin{equation}
+  \label{eq:alpha_para_RPA}
+  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
+  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
+  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
+  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+Present the summation of k-space into integral, and further combining
+with the Bloch wave representation and the
+$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
+at Eq. \ref{eq:alpha-para-def}. Note that from
+Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
+$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
+$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
+where $N$ is the degeneracy associated with the minimal bandgap. Such
+relation predicts the linear correlation coefficient between
+$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
+\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
+$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From Figure 2{\bf c}, we have
+$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
+\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
+between 2 and 3, which is a reasonable result for the 2D materials
+studied.
+
+{\bf ES:} Tian, please include more details in this section on the derivations!
+
+\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-perp-def}}
+\label{ssec:theory-2}
+
+For main text Eq. \ref{eq:alpha-perp-def}, treating the in-plane
+wave functions as plane wave with form
+$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
+element of
+$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
+when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
+\begin{equation}
+  \begin{aligned}
+    \label{eq:matrix-z}
+  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
+  &= \frac{1}{A} \int dx \int dy
+  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
+  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
+  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
+  \end{aligned}
+\end{equation}
+Note that the states perpendicular are bound, the integral is
+meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
+performing the Taylor expansion of
+$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
+\begin{equation}
+  \begin{aligned}
+    \label{eq:matrix-z-2}
+    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
+    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
+    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
+    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
+   \end{aligned}
+\end{equation}
+plug this into Eq. \ref{eq:alpha-RPA} and express the summation over
+$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
+arrive at:
+\begin{equation}
+\label{eq:alpha_perp_RPA}
+\alpha_{\mathrm{2D}}^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
+\sum_{\mathrm{c, v}}
+\frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
+{E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
+\end{equation}
+The formalism is slightly different from Eq.\ref{eq:alpha_para_RPA}.
+
+The out-of-plane wave function $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
+Hamiltonian $\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where
+$\hbar$ is the reduced Planck constant, $m_{e}$ is electron mass and
+$V(z)$ is the confined Coulomb potential along the z-direction
+created by the nuclei
+\cite{davies_physics_1997,ihn_semiconductor_2009}. Although the exact
+form for $\psi^{\perp}$ depends on the exact distribution of $V(z)$,
+without loss of generality we can assume the electrons are confined in
+a potential well of width $\delta$, which is the typical treatment for
+semiconductor QWs \cite{ihn_semiconductor_2009}. The allowed bound
+states inside the confined region generally have wave vector
+$k_{z} \propto n \pi / \delta$. With the total energy
+$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
+    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
+    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
+the effective masses parallel and perpendicular to the 2D
+plane. Therefore the denominator of Eq. \ref{eq:alpha_perp_RPA} becomes independent of
+$\mathbf{k}$, that
+$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
+(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
+  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
+hand, the numerator
+$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
+is proportional to the confinement length $\delta$ which can be seen using
+particle-in-box solution\cite{davies_physics_1997}. In combination,
+the individual terms of the summation in the right hand of Eq. \ref{eq:alpha_perp_RPA} is
+independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
+$\alpha_{\mathrm{2D}}^{\perp}$ is independent of the band gap.
+
+Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
+confinement length $\delta$, or equivalent the thickness of the 2D
+material. For simplicity we assume $\psi^{\parallel}$ is the solution
+of a particle confined inside an infinite potential well of width
+$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
+K, the only non-zero contribution for the transition between band
+$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
+vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
+$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
+\begin{equation}
+  \begin{aligned}
+    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
+    d^{2}\mathbf{k}_{\rho}
+    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
+      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
+      n_{\mathrm{v}}^{2}}\\
+    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
+      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
+        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
+        n_{\mathrm{v}}^{2}}
+  \end{aligned}
+\end{equation}
+Since the Fermi wave vector for band \textit{i} follows
+${\displaystyle
+  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
+{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
+    \delta^{2}}} = E_{\mathrm{F}}$, we have
+$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
+(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
+n_{\mathrm{v}}^{2}) {\displaystyle
+  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
+model, the energy levels for a sub-nm QW will be at the order of 10
+eV, which allows only few states inside the QW. Combine with the fact
+that the strongest transition mostly comes from the lowest bands
+\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
+be proportional to $\delta^{p}$, where the power index $p$ is 2. We
+note the different power law comes from the choice of the $V(z)$. The
+atomic polarizabilities of free particles inside a 1D infinite QW,
+finite QW or harmonic QW all show dependency with $\delta^{4}$, where
+$\delta$ is the length of confinement or effective harmonic length of
+the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
+the molecular polarizability divided by the area, such approach will
+always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
+accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
+model for the confinement in z-direction than simple square potential
+well, which may be explored further. Nevertheless the simple model presented
+here still captures the bandgap-independent and thickness-related feature
+of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
+text. In the next section we will provide a simple explanation for the $\alpha \propto \delta$ relation from fundamental electrostatics theory.
+
+\section{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
 \label{sec:pol-2D-Eg}
@@
   \centering
-  \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
+  \includegraphics[width=0.6\linewidth]{img/SI-compare_alpha_Eg.pdf}
   \caption{Relation between $1/\alpha_{\mathrm{2D}}^{\parallel}$ and various choices
@@
 
-\section{Theoretical Analysis}
-\label{sec:theory}
-\subsection{Polarizability-Based Theoretical Model}
-\label{ssec:theory-1}
-The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
-Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
-coincidence. Combining recent theoretical findings of the linear
-relation between exciton binding energy $E_{\mathrm{b}}$ and
-$E_{\mathrm{g}}$ of 2D materials
-\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
-fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
-$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
-to have a general Moss-like relation between
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
-the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
-resembles molecular polarizabilities of conjugate molecules
-\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
-nanotubes \cite{Benedict_1995}, which are also shown to be
-geometry-dependent.
-
-In this section we show in detail the polarizability-based theoretical
-framework that leads to the 2D Moss-like relations proposed in the
-main text.  Due to its highly anisotropic nature, the wave function of
-an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
-in- and out-of-plane components, similar to the treatment of quantum
-wells (QW),\cite{davies_physics_1997} such that
-$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
-$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
-is the in-plane coordinate. Using the Bloch theorem, the periodic
-$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
-$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
-  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
-in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
-in the xy-plane. According to the random phase approximation (RPA)
-theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
-$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
-dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
-$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
-\begin{equation}
-  \label{eq:RPA-eps2}
-  \varepsilon_{\mathrm{SL}}
-  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
-  \sum_{\mathrm{k, c, v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
-  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
-\end{equation}
-where $e$ is the unit charge, c, v are the conduction and valence
-bands, $E$ is the eigenenergy of individual bands, and $f$ is the
-Fermi-Dirac distribution function. Taking the
-limit that $L\to\infty$, when
-$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
-$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
-(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-at 0 K can be unified by the same equation:
-\begin{equation}
-  \label{eq:alpha-RPA}
-  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
-  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-where the direction is determined by $\mathbf{q}$. Next we will show
-that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
-give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
-\ref{main-eq:2D-Moss-perp}.
-
-\subsubsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-para}}
-\label{sssec:theory-1}
-
-In this section we show how main text Eq. \ref{main-eq:2D-Moss-para}
-is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
-$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
-of $z$, therefore the integral in
-$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
-becomes the independent of $\psi^{\perp}$, due to the orthogonality
-and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
-only the cell-function $u(\mathbf{k})$ contributes to the final result
-of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
-that:
-\begin{equation}
-  \label{eq:alpha_para_RPA}
-  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
-  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
-  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-Present the summation of k-space into integral, and further combining
-with the Bloch wave representation and the
-$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
-at Eq. \ref{main-eq:2D-Moss-para}. Note that from
-Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
-$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
-$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
-where $N$ is the degeneracy associated with the minimal bandgap. Such
-relation predicts the linear correlation coefficient between
-$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
-\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
-$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From main
-text Figure \ref{main-fig-3}c, we have
-$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
-\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
-between 2 and 3, which is a reasonable result for the 2D materials
-studied.
-
-\subsubsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-perp}}
-\label{ssec:theory-2}
-For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
-wave functions as plane wave with form
-$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
-element of
-$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
-when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
-\begin{equation}
-  \begin{aligned}
-    \label{eq:matrix-z}
-  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
-  &= \frac{1}{A} \int dx \int dy
-  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
-  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
-  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
-  \end{aligned}
-\end{equation}
-Note that the states perpendicular are bound, the integral is
-meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
-performing the Taylor expansion of
-$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
-\begin{equation}
-  \begin{aligned}
-    \label{eq:matrix-z-2}
-    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
-    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
-    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
-    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
-   \end{aligned}
-\end{equation}
-plug this into Eq. \ref{eq:alpha-RPA} and express the summation over
-$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
-arrive at:
-\begin{equation}
-\label{eq:alpha_perp_RPA}
-\alpha_{\mathrm{2D}}^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
-\sum_{\mathrm{c, v}}
-\frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
-{E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
-\end{equation}
-The formalism is slightly different from Eq.\ref{eq:alpha_para_RPA}.
-
-The out-of-plane wave function $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
-Hamiltonian $\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where
-$\hbar$ is the reduced Planck constant, $m_{e}$ is electron mass and
-$V(z)$ is the confined Coulomb potential along the z-direction
-created by the nuclei
-\cite{davies_physics_1997,ihn_semiconductor_2009}. Although the exact
-form for $\psi^{\perp}$ depends on the exact distribution of $V(z)$,
-without loss of generality we can assume the electrons are confined in
-a potential well of width $\delta$, which is the typical treatment for
-semiconductor QWs \cite{ihn_semiconductor_2009}. The allowed bound
-states inside the confined region generally has wave vector
-$k_{z} \propto n \pi / \delta$. With the total energy
-$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
-    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
-    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
-the effective masses parallel and perpendicular to the 2D
-plane. Therefore the denominator of Eq. 10 becomes independent of
-$\mathbf{k}$, that
-$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
-(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
-  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
-hand, the numerator
-$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
-is proportional to the confinement length $\delta$ (can be seen using
-particle-in-box solution\cite{davies_physics_1997}). In combination,
-the individual terms of the summation in the right hand of Eq. 5b is
-independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
-$\alpha_{\mathrm{2D}}^{\perp}$ is independent of the band gap.
-
-Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
-confinement length $\delta$, or equivalent the thickness of the 2D
-material. For simplicity we assume $\psi^{\parallel}$ is the solution
-of a particle confined inside an infinite potential well of width
-$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
-K, the only non-zero contribution for the transition between band
-$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
-vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
-$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
-\begin{equation}
-  \begin{aligned}
-    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
-    d^{2}\mathbf{k}_{\rho}
-    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
-      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
-      n_{\mathrm{v}}^{2}}\\
-    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
-      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
-        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
-        n_{\mathrm{v}}^{2}}
-  \end{aligned}
-\end{equation}
-Since the Fermi wave vector for band \textit{i} follows
-${\displaystyle
-  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
-{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
-    \delta^{2}}} = E_{\mathrm{F}}$, we have
-$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
-(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
-n_{\mathrm{v}}^{2}) {\displaystyle
-  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
-model, the energy levels for a sub-nm QW will be at the order of 10
-eV, which allows only few states inside the QW. Combine with the fact
-that the strongest transition mostly comes from the lowest bands
-\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
-be proportional to $\delta^{p}$, where the power index $p$ is 2. We
-note the different power law comes from the choice of the $V(z)$. The
-atomic polarizabilities of free particles inside a 1D infinite QW,
-finite QW or harmonic QW all show dependency with $\delta^{4}$, where
-$\delta$ is the length of confinement or effective harmonic length of
-the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
-the molecular polarizability divided by the area, such approach will
-always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
-accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
-model for the confinement in z-direction than simple square potential
-well, which may be tedious. Nevertheless the simple model presented
-here still captures the bandgap-independent and thickness-related feature
-of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
-text. In the next section we will provide a simple explanation for the $\alpha \propto \delta$ relation from fundamental electrostatics theory.
-
-\subsubsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
+%%%%%%pasted in 12/05/2018
+
+\subsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
   from fundamental electrostatics}
@@
 \subsection{Comparing 2D and 3D Moss relations}
-\label{ssec:theory-2}
-
+\label{ssec:theory-2D}
+%\label{ssec:theory-2}
 The 2D Moss-like relation $\alpha^{\parallel} \propto E_{g}^{-1}$ is
@@
 
+%%%%%%pasted!
+
 \section{Raw data from first principles calculations}
@@
 \label{sec:ref}
-\bibliography{ref}
+\bibliography{ref1}
 

### 2018-12-16 paper.tex
Fix missing cross-ref links
Changes adapted from Elton 20181212

@@
 
-\usepackage{xr}
-\externaldocument[SI-]{SI}
+%\usepackage{xr}
+%\externaldocument{SI_v112818}
+\usepackage{xr-hyper} 
+%\usepackage{zref-xr}
+\externaldocument{SI_v120518}
 
@@
 \author{Manish Chhowalla}
-% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
+%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
 \affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
@@
 \date{}
-\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
+\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
 % \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
@@
 
-{\bfseries Dielectric constant, which defines the polarization of the
-  media, is a key quantity in condensed matter. Here we show that
-  despite its fundamental transcendence, the dielectric constant does
-  not define unequivocally the dielectric properties of a
-  two-dimensional (2D) material. We found instead that the dielectric
-  polarizability correctly captures the dielectric nature of a 2D
-  material which is strongly dependent on the long-range
-  electron-electron interaction.  We reveal a long-sought universal
-  framework where electronic, geometrical and dielectric properties
-  are intrinsically correlated through the polarizability opening the
-  door to probe quantities yet not directly measurable, e.g. thickness
-  of an atom.  By using this framework, we unify the concept of
-  dielectric properties in any material dimension through a dielectric
-  anisotropy index which defines the degree of controllability of the
-  dielectric features of a compound. A universal boundary line
-  separates the 3D and 2D behaviors where materials likely to have
-  similar properties as layered materials collapsed onto.  }
+{\bfseries Dielectric constant, which defines the polarization of the media, is a key quantity in condensed matter.
+It determines several electronic and optoelectronic properties important for a plethora of modern technologies from computer memory to field effect transistors and communication circuits.
+Moreover, the importance of the dielectric constant in describing electromagnetic interactions through screening plays a critical role in understanding fundamental molecular interactions.
+Here we show that despite its fundamental transcendence, the dielectric constant does not define unequivocally the dielectric properties of two-dimensional (2D) materials due to the locality of their electrostatic screening.
+We found instead that the electric polarizability correctly captures the dielectric nature of a 2D material which is united to other physical quantities in an atomically thin layer.
+We reveal a long-sought universal formalism where electronic, geometrical and dielectric properties are intrinsically correlated through the polarizability opening the door to probe quantities yet not directly measurable including the real covalent thickness of a layer.
+We unify the concept of dielectric properties in any material dimension finding a global dielectric anisotropy index defining their controllability through dimensionality.
+}
 
-The central place of dielectric properties, especially the static
-dielectric constant in material research
-\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
-model between the electronic and dielectric properties of materials.
-% In fact, some pioneering work\cite{Moss_1950_relation} discovered
-% relations between the dielectric constant $\varepsilon$ and other
-% physical properties, in particular the band gap $E_{\mathrm{g}}$ of
-% bulk semiconductors.
-In fact, some pioneer
-work\cite{Moss_1950_relation,Moss_1985_n_Eg,Ravindra_1979_eps_Eg,Ravindra_2007_Eg_rev}
-proposed the empirical model between the energy bandgap
-$E_{\mathrm{g}}$ and dielectric constant $\varepsilon$ of bulk
-semiconductors, such as the famous Moss relation
-\cite{Moss_1950_relation,Moss_1985_n_Eg}:
-\begin{equation}
-\label{eq:Moss-relations}
-\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
-\end{equation}
-Despite the minor difference between the empirical formulae proposed,
-such general relation  is of high
-practical importance for material design and engineering: with the
-Moss relationship or other similar models, it is feasible to predict
-the dielectric constant (and hence other parameters such as refractive
-index, Bohr radius, exciton binding energy, etc.) of a bulk material
-from the its bandgap with a reasonable degree of certainty
-% The
-% existence of such general relationship is also of high practical
-% importance: it is generally more straightforward and accurate to
-% measure the band gap $E_{\mathrm{g}}$ than the static dielectric
-% constant $\varepsilon$ of a bulk material, as the latter is strongly
-% dependent on several critical details on the sample measurements, such
-% as contamination, disorder, and model interpretation.
-While the electronic-dielectric relation for bulk semiconductors is
-well-established, it is unknown if such equation still exists in
-atomically-thin two-dimensional (2D) materials \cite{Novoselov_2016},
-due to (i) the dielectric screening of a 2D material is attenuated and
-anisotropic
-\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}
-and (ii) the static dielectric constant, a quantity associated with
-the macroscopic dielectric and optoelectronic properties and commonly
-obtained by theoretical calculations of 2D materials
-\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
-describe this microscopic and anisotropic dielectric nature of 2D
-materials \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}.
-% Therefore, an
-% accurate description of the 2D dielectric nature is the prerequisite
-% for a 2D Moss-like relation, which could be used to make predictions
-% for less-investigated layered crystals and to create materials design
-% rules at an accurate level.
-Here we show that instead of the dielectric constant,
-the 2D polarizabilty correctly captures the dielectric nature
-of a 2D material. Based on both theoretical model and first principle
-calculations, we reveal the long-sought universal dielectric scaling
-relations for 2D materials, depend both on the electronic and
-structural information: the in-plane polarizability
-$\alpha^{\parallel}_{\mathrm{2D}}$ is inversely proportional to the minimal bandgap
-$E_{\mathrm{g}}$, while the out-of-plane polarizability
-$\alpha^{\perp}_{\mathrm{2D}}$ is directly related with the thickness
-$\delta$ of a 2D materials. We further introduce the concept of
-dielectric anisotropy index, to unify 2D and 3D dielectric
-property. The proposed universal dielectric scaling relationships of
-2D compounds introduce a general pathway for the exploration of their
-complex physical and chemical phenomena well beyond the currently
-possible applications.
-% Based on this
-% framework, we further unify the concept of dielectric properties of
-% any material dimension, by the dielectric anisotropy index, 
-% An analytical quantum-mechanical model is developed
-% which give a sound background to the dielectric-scale
-% relationships.
-% Using such unified relations unify the dielectric
-% properties between the 2D materials and their 3D counterparts in a
-% natural manner, which ultimately pushes the boundary of the
-% understanding of electronic screening in both dimensions.
-% The discovery of scaling relationships between dielectric and electronic
-% and structural properties in 2D compounds introduces a new and general
-% pathway for the exploration of their complex physical and chemical
-% phenomena well beyond the currently possible applications.
-
-% \section{Results}
-% \label{sec:org752ca78}
-
-\subsection{Dielectric Nature of 2D Materials}
-\label{sec:2d}
-
-In pursuit of the Moss-like relation for 2D materials, an accurate
-description of their dielectric properties needs to be established,
-since the concept of macroscopic dielectric constant is ill-defined
-for 2D materials
-\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
-shown in Figure \ref{fig-1}a, in routine first principles
-calculations, an isolated 2D material is placed in the xy-plane of a
+The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
+plays a crucial role in bridging various fundamental material
+properties, such as bandgaps, optical absorption, and conductivities,   
+with elemental interactions, e.g. the electron-electron forces. 
+The central place of $\varepsilon$ in physics drives the analysis of several phenomena 
+where is common to classify a material accordingly to its ability to screen an electric field $\boldsymbol{E}$ 
+in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
+condensed matter physics, as well as in related fields in chemistry and materials science. 
+The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
+theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
+is made through an external electric field. 
+%
+Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
+electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
+%
+%
+The confined nature of the electrons in such atomically thin space associated with the 
+attenuated and anisotropic character of the dielectric screening of 2D crystals 
+\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
+have generated long-standing debates whether the dielectric constant 
+may represent their dielectric features or it can be used as an 
+additional parameter from the bulk-counterparts. 
+%%
+%%
+We approach to this problem showing 
+that the current definition used in layered materials is ill defined as illustrated in Figure \ref{fig-1}.  
+From the theoretical point of view, 
+an isolated 2D material is placed in the xy-plane of a  %cutting started here! 
 periodically repeating superlattice (SL) with a length $L$ along the
-z-direction separating the cell images. The macroscopic dielectric
+z-direction separating the cell images. The static macroscopic dielectric
 tensor from the superlattice $\varepsilon_{\mathrm{SL}}^{pq}$, is
@@
 $\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is the
-spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
+spatial charge density, $\Omega=AL$ is the volume of the supercell, $A$ is the xy-plane
 area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
-majority of 2D semiconductors, the off-diagonal elements of the
+majority of 2D nonmetals, the off-diagonal elements of the
 dielectric tensor ($p \neq q$) tend to be negligible.  Considering
@@
 $\varepsilon_{\mathrm{SL}}^{\perp} =
-\varepsilon_{\mathrm{SL}}^{zz}$. The absence of bonding perpendicular
-to the 2D plane confines the induced dipoles along the
-\textit{z}-direction: as shown in Figure \ref{fig-1}a and
-Supplementary Figure \ref{SI-fig:rho-profile}, the charge density difference
-between zero and finite electric fields,
-$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ along the
-z-axis for an isolated 2H-MoS$_{2}$ layer under
-$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$ only extends to
-$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough that
-the induced dipoles from periodic images do not interact,
-$\boldsymbol{u}$ equals the total dipole moments of a monolayer 2D
-materials and independent of the SL size. As a consequence, we can see
-from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
+\varepsilon_{\mathrm{SL}}^{zz}$. 
+The absence of bonding perpendicular
+to the plane confines the induced dipoles along the
+\textit{z}-direction as the charge density difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$,
+at zero and finite electric fields ($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) 
+extends to $\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a}). When $L$ is large enough,   
+the induced dipoles $\boldsymbol{u}$ from the periodic images do not interact mutually 
+as the integral in Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge density at the layer. 
+However, we can see from Eqs. \ref{eq:def-eps-1} that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$. We show this by
+$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of the cell $\Omega$. 
+Therefore, any calculation performed using such definition will intrinsically depend on the magnitude of $L$ as an additional parameter. 
+This dependence can be clearly demonstrated by
 plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
-theory (DFT) as functions of $L$ for P$\bar{6}$m2 (2H) transitional
-metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
-Te), in the top panels of Figure \ref{fig-1}b and \ref{fig-1}c,
-respectively.
+theory (DFT) using hybrid functionals (see {\it Methods} for details) as a function 
+of $L$ for P$\bar{6}$m2 transitional metal dichalcogenides 
+(TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
+Te (top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}, respectively). 
+Despite of the magnitudes of $L$ both components of the dielectric constant 
+change systematically without a clear convergence.  
+%
+Simulations performed at higher levels of theory using 
+many-body techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}), 
+and also taking into account  electron-hole excitations at the level of the Bethe-Salpeter equation 
+at the frequency-dependent versions of $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$
+invariably give alike results (Supplementary Figure \ref{fig:S2}). 
+Indeed, the variations observed in peak positions at different values of $\omega(eV)$ 
+implicate that several other related quantities, such as, the optical absorption and 
+optical conductivity, suffer the same deficiencies. In a fully first-principles theory 
+such intrinsic dependence on $L$ should not be present. 
+%
+%
+%
+%as the computation of the dielectric function is based on alike formalism\cite{Ehrenreich-Cohen paper}
+% We can understand this behavior in terms of the electrostatic of the problem. 
+%
+%
+%
+%This result indicates that the use of the dielectric constant to represent 
+%dielectric properties at the static limit of a 2D material is 
+%ambiguous as the long-range correlations between the layers would only 
+%be negligible at the limit of $L \rightarrow \infty$, which incidentally modify the magnitudes of 
+%$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ in the convergence. 
+%
+It is worth mentioning that experimental results also need to define an effective thickness of the sheet 
+to interpret ellipsometry data \cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, 
+reflectance or transmission spectra \cite{Li_2014, Yoffe-Wilson69} in 
+order to extract information for the real part of the dielectric functions. 
+We argue that such procedure may induce inevitably variations of the results as the 
+thickness is normally chosen by the interlayer spacing of the 
+respective bulk materials (Supplementary Section \ref{sec:2D-3D-rescale} gives an exhaustive analysis).  
+%
+%%%
+%
 % We observe that neither
@@
 % screened within the range of magnitudes computationally accessible
-% \cite{Hueser_2013_2Dvs3D}.
-As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
-it impractical to represent the dielectric nature of a 2D material
-both theoretically and experimentally, because the size of vacuum
-layer must always be considered. To solve this problem, we need to
+%.
+%
+%
+%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
+%it impractical to represent the dielectric nature of a 2D material
+%both theoretically and experimentally, because the size of vacuum
+%layer must always be considered. 
+%
+
+To solve this problem, we need to
 find the $L$-independent alternative of
 $\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
-Eq. \ref{eq:def-eps-2} with $L$ we get the sheet polarization density
-of a 2D material $\boldsymbol{\mu}_{\mathrm{2D}}$, such that
-$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \boldsymbol{P}^{p}L =
-\boldsymbol{u}^{p}/A$, which is dependent with $L$ due to the invariablity
-of $\boldsymbol{u}$ and $A$. Similar to the definition of molecular
+Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
+$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
+which is independent of $L$ due to the locality 
+of $\boldsymbol{u}$ and $A$. 
+%
+Similar to the definition of molecular
 polarizability \cite{Israelachvili_2011},
@@
 \boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
-$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. In the
-in-plane direction, the continuity of electric field gives
+$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
+Using electrostatic boundary conditions, 
+the continuity of the electric field along the
+in-plane direction gives
 $\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
-\cite{Markel_2016}. Perpendicular to the 2D plane, the dipole
+\cite{Markel_2016}. For the out-of-plane component, the dipole
 screening yields
@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
-% \begin{subequations}
-% \begin{eqnarray}
-  % \label{eq:alpha-para-def}
-  % &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
-  % \label{eq:alpha-perp-def}
-  % &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
-% \end{eqnarray}
-% \end{subequations}
+%
+%
 \begin{subequations}
@@
 \end{subequations}
+%
+%
 The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-of the TMDCs as functions of $L$, calculated using
+of the selected TMDCs as a function of $L$, calculated using
 Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
-that both $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ remain almost constant when $L>$15
-\AA{}. In addition, as shown Figure \ref{fig-1}d and \ref{fig-1}e,
-respectively, the model-predicted
-$\varepsilon_{\mathrm{SL}}^{\parallel}-L$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}-L$ relations from Eqs.
-\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} nicely reproduce
-the trends from Figures \ref{fig-1}b and \ref{fig-1}c. These findings
-indicate that the 2D polarizability, instead of the dielectric
-constant, is the true descriptor of the dielectric properties of 2D
-materials. More discussion about the choice of the 2D polarizability
-and comparison with other methods can be find in Supplementary Section
-\ref{SI-sec:2D-3D-rescale}.
+that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
+convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
+%
+%
+Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
+to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
+for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
+a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
+and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
+A similar curve profile is obtained in both components of the dielectric constant including the much 
+abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
+interlayer interactions.  Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
+the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
+%
+% 
+% 
+% 
+% 
+These findings provide that the 2D polarizability captures the essence of the dielectric properties 
+of layered materials as the microscopic quantity in describing the 
+atomic interactions present in the layers. Its local nature removes any dependence on size effects 
+present in the calculations.  
+More discussions about the choice of the 2D polarizability
+and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.
 
-\subsection{2D Moss-like  Relations}
-\label{sec:first-principles}
-Based on the 2D polarizabilities, we then investigate the potential
-Moss-like relations for 2D materials. By evaluating the expressions
-for $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
-theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
-treatment\cite{kittel_2005_introduction} (details see Supplementary
-Section \ref{SI-ssec:theory-1}), we show that
+%\subsection*{Polarizability as the fundamental variable}
+%\label{sec:first-principles}
+
+%We consider
+
+As a consequence of Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, we can demonstrate 
+that other quantities are intrinsically related to the polarizability. 
+Using random phase approximation (RPA)
+theory \cite{Adler_1962} within the $\mathbf{k} \cdot \mathbf{p}$
+formalism\cite{kittel_2005_introduction} (see Supplementary
+Section \ref{sssec:theory-1} and  \ref{ssec:theory-2} for details), 
+we can show that
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-have simple relation with the electronic  and structural information of a 2D
-material, respectively:
+can be written as: 
+%
+%
+%
 \begin{subequations}
@@
 \label{eq:2D-Moss-para}
-  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
+  &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
   \label{eq:2D-Moss-perp}
-  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
+  &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \delta
 \end{eqnarray}
 \end{subequations}
-where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
-material, and $\delta$ is its intrinsic
-thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
-the main conclusions of this work.  \todo[inline]{I not sure if we
-  need to show the proportional coefficients
-  here. $\alpha_{2D}^{\perp}$ is almost certain to be
-  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
-  a more complex coefficient.}
-
-To validate such relations, we study several types of 2D materials as
-show in Figure \ref{fig-3}a, including transition metal
-dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
-a metal in groups 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
+%
+%
+%
+%
+where $E_{\mathrm{g}}$ is the minimal electronic bandgap, 
+$\delta$ is the intrinsic or covalent thickness of the layer (Fig.
+\ref{fig-1}{\bf a}), and $C^{\parallel} = {8\pi^{2}\varepsilon_0\AA}/{eN}$, where $N$ corresponds to the degeneracy of the bands associated with $E_{\mathrm{g}}$,
+and $C^{\perp} = {1}/{4\pi}$.  Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, 
+they generalize a direct relationship between the polarizability and the electronic and structural properties for any 
+2D material in a new framework. 
+We can show that these equations are valid for the current library of known layered materials 
+involving different lattice symmetry, element composition, optical and electronic properties. 
+%
+A high-throughput screening performed on 
+different families of TMDCs (MX\(_{\text{2}}\), where M is
+a metal in groups 4, 6, 10, and X=O, S, Se, Te) and phases (P\(\bar{6}\)m2, P3m1), 
+metal monochalcogenides
 (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
@@
 (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
-and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
-TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
-space group) and 1T (P3m1 space group).  The static 2D
-polarizabilities are calculated from the static dielectric response of
-the selected 2D materials using density functional theory (DFT) with
-the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
-Vienna Ab Initio Simulation Package (VASP) including spin-orbit
-coupling to avoid limitations on the description of band gaps and
-dielectric functions (see Methods for details). Figure \ref{fig-3}b
+and thin layer organic-inorganic perovskites (ABX$_{3}$) (Fig. \ref{fig-3}{\bf a}) 
+showed that our method enables full correlation between these disparate variables. 
+%%
+%
+%Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are the main conclusions of this work. 
+%
+% \todo[inline]{I not sure if we need to show the proportional coefficients
+%  here. $\alpha_{2D}^{\perp}$ is almost certain to be
+%  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
+%  a more complex coefficient.}
+%
+%
+%
+%The static 2D
+%polarizabilities are calculated from the static dielectric response of
+%the selected 2D materials (see {\it Methods}). 
+Figure \ref{fig-3}{\bf b}
 shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
 (bar plots) of all the 2D materials investigated, covering a wide
-spectrum range from far infrared to ultraviolet. Note from dimension
+spectrum range from far-infrared to ultraviolet at HSE06 level. 
+Note from dimension
 analysis, it is more intuitive to express the polarizability as
@@
 \AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
-descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
+descending trend when $E_{\mathrm{g}}$ increases, while 
 no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
 $E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
-our polarizability-based theoretical model (Supplementary Section
-\ref{SI-ssec:theory-2}). We then examine Eqs. \ref{eq:2D-Moss-para}
+\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with elements 
+having large polarizabilities, such as Hf and Zr in 1T-HfO$_2$ or 1T-ZrO$_2$, 
+respectively, also transfer alike features for the layers with slightly variations between 
+1T and 2H phases. The former normally shows larger values of $\alpha_{\mathrm{2D}}^{\parallel}$ 
+than the latter. 
+%
+% 
+We then examine Eqs. \ref{eq:2D-Moss-para}
 and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
-first principle calculations. Figure \ref{fig-3}b shows
+first-principle calculations. 
+Figure \ref{fig-3}{\bf c} shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
 \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
-materials investigated (circle dots), with a linear regression
-coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
-corresponds well with theoretical investigations (details see
-Supplementary Section \ref{SI-sssec:theory-1}).  We also discover that
+materials investigated (circle dots).  
+A linear regression coefficient of $R^{2}=0.84$ indicates a 
+strong correlation between bandgaps and polarizabilities as predicted in 
+Eq. \ref{eq:2D-Moss-para}. 
+We also discover that
 the linearity between
@@
 $E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
-bandgap is calculated using the HSE06 hybrid functionals, compared
-with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
-(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
-Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
-explained by the fact that the electronic structure, in particular the
-bandgap, is generally better predicted at HSE06 level than PBE level
-\cite{Heyd_2005}. It should be noted that although even more accurate
-estimation of both dielectric properties and bandgap can be achieved
-via many-body Green's function method (GW) together with the
-Bethe-Salpeter equation (BSE), the convergence of such method is known
-to be highly affected by the dielectric screening of 2D materials
-\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
-effort and convergence, the choice of the HSE06 hybrid functional may
-be most suitable to present the true 2D Moss-like relationship between
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
-that the proposed relation behaves equivalently well when using the
+bandgap is calculated using the HSE06 hybrid functional\cite{Heyd_2005} compared
+with that from Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
+(see Supplementary Section \ref{sec:pol-2D-Eg} and
+Supplementary Figure \ref{fig:alpha-Eg-diff}) which suggests that higher levels 
+of theory are needed to predict bandgaps as it is normally the case.   
+We also show
+that the proposed Eq. \ref{eq:2D-Moss-para}
+behaves equivalently well when using the
 experimentally accessible optical bandgap of 2D materials (details see
-Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
-\ref{SI-fig:opt}).
+Supplementary Section \ref{sec:gpaw-2} and Supplementary Figure
+\ref{fig:opt}).
 
@@
 plus their covalent radii:
+%
+%
 \begin{equation}
@@
 where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
-is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
-in Figure \ref{fig-3}c,
-$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
+is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
+%
+%
+$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
 excellent linear correlation with $\delta_{\mathrm{cov}}$, with
-$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words, we
-propose
-$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
-\delta_{\mathrm{cov}}$, which has its strong physical meaning. Similar
+$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure \ref{fig-3}{\bf d}). 
+This results that $\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
+\delta_{\mathrm{cov}}$ has a strong physical meaning through the geometry of the layer. 
+Similar
 to the molecular polarizability which characterizes the volume of
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section \ref{SI-sssec:theory-3}). In fact,
+material (see Supplementary Section \ref{sssec:theory-3}). Indeed,
 the universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
-Figure \ref{fig-3}c indicates that the quantity
+Figure \ref{fig-3}{\bf d} indicates that the quantity
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
 electronic approaches
-\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
+\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is in reality the
 (dielectric) characteristic thickness of a 2D material, and can be
@@
 thickness of 2D materials, such as graphene \cite{Shearer_2016}.
-
-To rule out the possibility that our conclusion is limited by the
-number of materials used, we further validate our proposed 2D
-Moss-like relations on the recently published C2DB database
-\cite{Haastrup_2018}, from which we extracted the dielectric
-properties of over 230 2D materials calculated at the PBE level, and
-superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
-(details see Supplementary Section \ref{SI-sec:gpaw-1}). Although the
+%
+To rule out the possibility that our conclusion are limited by the
+number of materials used at HSE06, we further 
+validate Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
+using a different database\cite{Haastrup_2018}, from which we extracted the dielectric
+properties of over 230 compounds calculated at the PBE level, and
+superimpose with our results in Figure \ref{fig-3}{\bf c} and \ref{fig-3}{\bf d}
+(see details in Supplementary Section \ref{sec:gpaw-1}). Although the
 dielectric properties may be overestimated at PBE level due to
@@
 observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$, with the linear coefficient very close
-to the HSE06 results (details see Supplementary Section
-\ref{SI-sec:gpaw-2}). We have also tested the potential relation
+$\alpha_{\mathrm{2D}}^{\perp}$ with the linear coefficient very close
+to the HSE06 results (see details in Supplementary Section
+\ref{sec:gpaw-2}).
+
+We have also searched for additional relations
 between the 2D polarizabilities with other physical quantities,
 including the effective carrier mass, quantum capacitance and total
-atomic polarizabilities, while no apparent correlations are found
-(details see Supplementary Section \ref{SI-sec:gpaw-3}).
-
-In short, we have revealed the 2D analog of the Moss relation by both
-theoretical modeling and first principles calculations:
-$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
-minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
-is the characteristic thickness of the 2D material. Next we show,
-despite their different forms, both 2D Moss-like relations stem from
-the same origin. In merit of the unit analysis,
+atomic polarizabilities with no apparent correlations being found
+(Supplementary Section \ref{sec:gpaw-3}). 
+We found however that Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} 
+have a natural connection with the screening properties of the layer. 
+%
+In merit of the unit analysis,
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
-words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
+both have unit of $4\pi\varepsilon_{0} \cdot$[Length], that is, $\alpha_{\mathrm{2D}}^{\parallel}$ and
 $\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
 characteristic lengths, respectively. The in-plane screened
-electrostatic potential $V(r)$ from a point charge in an 2D plane, as
+electrostatic potential $V(r)$ from a point charge as
 a function of distance $r$: 
@@
 $r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
-respectively, analog to the polarizability ellipsoid picture of
+respectively. This is analog to the polarizability ellipsoid picture of
 molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
-Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
+Figure \ref{fig:ellipsoid}). The polarizability ellipsoid for a 2D
 material is in general ultra flat, with
 $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
-TMDCs in Table \ref{tbl:radii}\todo{Lacks MoSe2}.  Moreover,
+TMDCs in Table \ref{tbl:radii}.  Moreover,
 $r_{0}^{\parallel}$ is generally larger for a smaller bandgap
@@
 relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$E_{\mathrm{g}}$, a 2D version of the Moss-relation.
+$E_{\mathrm{g}}$ seen in Eq. \ref{eq:2D-Moss-para}. 
+This gives a geometrical interpretation of the bandgap in terms 
+of the screening radius of the layer.
 
-\subsection{Bridging the 2D and 3D Dielectric Properties}
-\label{sec:2D-3D}
+%\subsection{Bridging the 2D and 3D Dielectric Properties}
+%\label{sec:2D-3D}
 
-The universal Moss-like relation shown in the previous sections
-provides general understanding of the dielectric nature of 2D
-materials. Moreover, the underlying physical mechanism allows us to
-further bridge the 2D and 3D dielectric and electronic properties in
-various ways. Using the similar approach as we derive the 2D Moss-like
-relations, we show that the
-$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
-relation for a 2D material naturally transforms to
-$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
-semiconductor, which is the original Moss relation (details see
-Supplementary Section \ref{SI-ssec:theory-2}). In other words, the
-proposed $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is
-indeed the Moss relation in 2D world, while the different power law
-for $E_{\mathrm{g}}$ is caused by the electronic confinement.
-\todo[inline]{I shortened this paragraph since the derivation is
-  interesting but not so much related with other stuff like the
-  dielectric anisotropy.}
-
-The dielectric constant $\varepsilon$, although not well-defined for
-monolayer 2D material, becomes applicable when the 2D layers are
-stacked. \todo[inline]{I would appreciate for polishing this sentence}
+We next show that the underlying physical mechanism linking 
+polarizability to bandgaps allows us to further bridge 
+the dielectric properties between 2D materials and 
+their 3D bulk counterparts in a remarkable way. 
+%The dielectric constant $\varepsilon$, although not well-defined for
+%a monolayer 2D material, becomes applicable when the 2D layers are
+%stacked. 
+%
+%
+%
 In a bulk layered material stacked by layers with equilibrium
@@
 $\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
-$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
+$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
 be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
-$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
+$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\bf a}) as:
+%
+%
 \begin{subequations}
@@
 \end{subequations}
-The approximations come from the fact that
-$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
-seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
-that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
-and \ref{eq:3D-perp}. We compare the values of
+%
+%
+These approximations assume that the strong interactions 
+occur in-plane and the interlayer stacking is not a critical factor. 
+The dielectric constant $\varepsilon$ although not well-defined for
+a monolayer 2D material becomes applicable when the 2D layers are
+putted together. 
+%
+We compare the values of
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
@@
 with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
-(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
-respectively, with data calculated at both HSE06 and PBE levels give
-almost identical trends. We observe that
+(x-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
+Both HSE06 and PBE datasets give almost identical results.  
+%
+We observe that
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
 predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
-regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
+regression slope of 1.01 and $R^2$ of 0.97. Conversely,
 $\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
@@
 its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
-to interlayer coupling and overlap between induced
-dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
-in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
-$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
-the degree of interlayer coupling, the dielectric transition from 2D
-to 3D would be smoothly described.
+to the interlayer coupling and overlap between induced
+dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
+%With a better model describing
+%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
+%the degree of interlayer coupling, the dielectric transition from 2D
+%to 3D would be smoothly described.
 
 Finally, we show that a general picture of the dielectric properties in
-both dimensions can be drawn by studying the dielectric
+any dimension can be drawn by studying the dielectric
 anisotropy. We define the dielectric anisotropy index $\eta$ as:
@@
 \eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
-index of corresponding 2D layer (details see Supplementary Section
-\ref{SI-sssec:aniso-2}), which is the basis for the separation of bulk
+index of corresponding 2D layer (see additional details in Supplementary Section
+\ref{sssec:aniso-2}), which is the basis for the separation of bulk
 and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
 comparison, we also superimpose the dielectric anisotropy indices
-$\eta$ of common semiconducting materials in other dimensions (details
-see Supplementary Section \ref{SI-sssec:aniso-1}) on the phase diagram in Figure
+$\eta$ of common semiconducting materials in other dimensions 
+(Supplementary Section \ref{sssec:aniso-1}) on the phase diagram in Figure
 \ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
@@
 flexibility in controlling the dielectric and electronic properties,
-compared with semiconductors in other dimensions.  \todo[inline]{I
-  leave this section to be freely modified}
+compared with semiconductors in other dimensions.
 
-\subsection{Implications for Experiments}
-\todo[inline]{Wait for comments from JC and MC.}
+%
+%\subsection{Implications for Experiments}
+%\todo[inline]{Wait for comments from JC and MC.}
 
-\section{Conclusion}
-\label{sec:org5fd1f1a}
-\todo[inline]{To be changed later when everything fixed}
-To sum up, using first principles calculation for a large set of 2D
-materials, we reveal the universal relation of the dielectric nature
-of 2D materials using the 2D polarizability, as an analog to the Moss
-relation for bulk semiconductors. The in-plane polarizability of a 2D
-material is found to be inversely proportional to the minimal bandgap,
-while the out-of-plane polarizability is the characteristic thickness
-of the 2D material. Such universal scaling relation is explained by a
-quantum mechanical model combining the polarizability in both
-directions. Our universal scaling relation bridges the gap between 2D
-and 3D dielectric properties with good accuracy of prediction.  Our
-numerical findings and theoretical analysis pave the way to understand
-and engineer the electronic and dielectric properties of a large
-library of 2D materials for different technological applications in an
-unified and unprecedented way.
+%\section{Conclusion}
+%\label{sec:org5fd1f1a}
+%\todo[inline]{To be changed later when everything fixed}
+
+Our results show that the electric polarizability $\alpha$ is a local 
+variable determining the dielectric properties of 2D materials. 
+There exist well defined relationships between $\alpha$ and 
+other quantities hidden in the electronic properties.  
+According to our analysis, simple 
+scaling equations involving bandgaps and layer thicknesses 
+can be used to describe both dielectric and electronic 
+features at the same footing. A dielectric anisotropy index is 
+found relating any material dimension with its controllability.  
+Thus, our results suggest that the challenge of understanding the 
+dielectric phenomena is in general a geometrical problem 
+mediated by the bandgap.
 
@@
 
-\bibliography{ref}
+\bibliography{ref1}
 
@@
 \centering
-\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
+\includegraphics[width=0.70\linewidth]{img/fig2_v110418.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
 
-% \begin{figure}[htbp]
-% \centering
-% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
-% \caption{\label{fig-delta} Scheme for the determination of the
-  % covalent thickness of one-atom-thick (left) and few-atom-thick
-  % (right) 2D materials.}
-  % \end{figure}
 \begin{table}[H]
@@
 \centering
-\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
+\includegraphics[width=1.04\linewidth]{./img/fig4_v111618ii.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
+  \includegraphics[width=1.05\linewidth]{img/fig5.pdf}
   \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as

### 2018-12-16 SI.tex
Add figures for paper and SI

@@
 
-%\usepackage{xr}
-%\externaldocument{paper_v112818}
-
 \usepackage{xr-hyper} 
 %\usepackage{xr}
-\externaldocument{paper_v120918fundamental}
+\externaldocument{paper}
 
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/Fig-G0W0.pdf}
+ \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
   \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
@@
 }
-  \label{fig:S1}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
- \includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
+  \label{fig:GW-PBE-alpha}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
   \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
@@
 }
-  \label{fig:S2}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
- %\includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
+  \label{fig:GW-omega-in}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
+  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
+Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
+many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
+with the only variable quantity being $L$. The systematic shift 
+}
+  \label{fig:GW-omega-out}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
+  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
+Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
+many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
+with the only variable quantity being $L$. The systematic shift 
+}
+  \label{fig:GW-omega-in}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
+  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
+Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
+many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
+with the only variable quantity being $L$. The systematic shift 
+}
+  \label{fig:GW-omega-out}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
   \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
@@
 }
-  \label{fig:S3}
+  \label{fig:BSE-omega-in}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
+  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
+  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
+  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
+  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
+}
+  \label{fig:BSE-omega-out}
 \end{figure}
@@
 \label{sec:ref}
-\bibliography{ref1}
+\bibliography{ref}
 

### 2018-12-16 paper.tex
Add figures for paper and SI

@@
 %\usepackage{xr}
-%\externaldocument{SI_v112818}
 \usepackage{xr-hyper} 
-%\usepackage{zref-xr}
-\externaldocument{SI_v120518}
+\externaldocument{SI}
 
@@
 
-{\bfseries Dielectric constant, which defines the polarization of the media, is a key quantity in condensed matter.
-It determines several electronic and optoelectronic properties important for a plethora of modern technologies from computer memory to field effect transistors and communication circuits.
-Moreover, the importance of the dielectric constant in describing electromagnetic interactions through screening plays a critical role in understanding fundamental molecular interactions.
-Here we show that despite its fundamental transcendence, the dielectric constant does not define unequivocally the dielectric properties of two-dimensional (2D) materials due to the locality of their electrostatic screening.
-We found instead that the electric polarizability correctly captures the dielectric nature of a 2D material which is united to other physical quantities in an atomically thin layer.
-We reveal a long-sought universal formalism where electronic, geometrical and dielectric properties are intrinsically correlated through the polarizability opening the door to probe quantities yet not directly measurable including the real covalent thickness of a layer.
-We unify the concept of dielectric properties in any material dimension finding a global dielectric anisotropy index defining their controllability through dimensionality.
-}
+{\bfseries The dielectric constant, which defines the polarization of
+  the media, is a key quantity in condensed matter. It determines
+  several electronic and optoelectronic properties important for a
+  plethora of modern technologies from computer memory to field effect
+  transistors and communication circuits. Moreover, the importance of
+  the dielectric constant in describing electromagnetic interactions
+  through screening plays a critical role in understanding fundamental
+  molecular interactions. Here we show that despite its fundamental
+  transcendence, the dielectric constant does not define unequivocally
+  the dielectric properties of two-dimensional (2D) materials due to
+  the locality of their electrostatic screening. We found instead that
+  the electric  polarizability correctly
+  captures the dielectric nature of a 2D material which is united to
+  other physical quantities in an atomically thin layer. We reveal a
+  long-sought universal formalism where electronic, geometrical and
+  dielectric properties are intrinsically correlated through the
+  polarizability opening the door to probe quantities yet not directly
+  measurable including the real covalent thickness of a layer. We
+  unify the concept of dielectric properties in any material dimension
+  finding a global dielectric anisotropy index defining their
+  controllability through dimensionality.  }
 
-The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
-plays a crucial role in bridging various fundamental material
-properties, such as bandgaps, optical absorption, and conductivities,   
-with elemental interactions, e.g. the electron-electron forces. 
-The central place of $\varepsilon$ in physics drives the analysis of several phenomena 
-where is common to classify a material accordingly to its ability to screen an electric field $\boldsymbol{E}$ 
-in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
-condensed matter physics, as well as in related fields in chemistry and materials science. 
-The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
-theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
-is made through an external electric field. 
+The dielectric constant $\varepsilon$ (also known as the relative
+permittivity) plays a crucial role in bridging various fundamental
+material properties, such as bandgaps, optical absorption, and
+conductivities.  \todo{Add more citations} $\varepsilon$ characterizes
+the ability to screen an electric field $\boldsymbol{E}$ which
+classifies metals, semiconductors and insulators.  \todo[inline]{I
+  shortened the sentences. However, can we really "classify" the
+  material only by $varepsilon$? For instance HfO2 has large
+  $\varepsilon$ but also large bandgap}
+% Such definitions determine a broad range of
+% condensed matter physics, as well as in related fields in chemistry
+% and materials science.
+The ability to compute and measure
+$\varepsilon$ in bulk materials is well established via different
+theoretical and experimental techniques of distinct flavors where the
+probe of the dielectric properties is made through an external
+electric field.
 %
@@
 have generated long-standing debates whether the dielectric constant 
-may represent their dielectric features or it can be used as an 
+may represent their dielectric features or only an 
 additional parameter from the bulk-counterparts. 
@@
 %%
-We approach to this problem showing 
-that the current definition used in layered materials is ill defined as illustrated in Figure \ref{fig-1}.  
-From the theoretical point of view, 
-an isolated 2D material is placed in the xy-plane of a  %cutting started here! 
+We approach this problem showing that the current definition of
+$\varepsilon$ used in layered materials is ill defined as illustrated
+in Figure \ref{fig-1}.  From the theoretical point of view, an
+isolated 2D material is placed in the \textit{xy}-plane of a
 periodically repeating superlattice (SL) with a length $L$ along the
-z-direction separating the cell images. The static macroscopic dielectric
-tensor from the superlattice $\varepsilon_{\mathrm{SL}}^{pq}$, is
-determined through fundamental electrostatics by the response of the
-polarization density $\boldsymbol{P}^{p}$ under small perturbative
-external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the directions
-of polarization and electric field,
+\textit{z}-direction separating the cell images. The static macroscopic
+dielectric tensor from the superlattice
+$\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
+electrostatics by the response of the polarization density
+$\boldsymbol{P}^{p}$ under small perturbative external field
+$\boldsymbol{E}^{q}$, where $p$, $q$ are the directions of
+polarization and electric field,
 respectively\cite{Dressel_2001_electrodynamics}:
@@
 where $\kappa$ is the dielectric tensor of the environment,
-$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is the
-spatial charge density, $\Omega=AL$ is the volume of the supercell, $A$ is the xy-plane
-area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
-majority of 2D nonmetals, the off-diagonal elements of the
-dielectric tensor ($p \neq q$) tend to be negligible.  Considering
-that the 2D material is placed in vacuum ($\kappa^{pp} = 1$ and
-$\kappa^{pq} = 0$), we can distinguish two components, namely the
-in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
+$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is
+the spatial charge density, $\Omega=AL$ is the volume of the
+supercell, $A$ is the \textit{xy}-plane area of the SL and
+$\varepsilon_{0}$ is vacuum permittivity. Here we only study the
+electronic contribution to the dielectric constant where the dipole
+$\boldsymbol{P}$ comes from the displacement of electron cloud under
+external electric field. For the majority of 2D nonmetals, the
+off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
+negligible \todo[inline]{why only nonmetals?  Could you cite one
+  reference?}.  Considering that the 2D material is placed in vacuum
+($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
+components, namely the in-plane
+($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
 ($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
@@
 and
-$\varepsilon_{\mathrm{SL}}^{\perp} =
-\varepsilon_{\mathrm{SL}}^{zz}$. 
-The absence of bonding perpendicular
-to the plane confines the induced dipoles along the
-\textit{z}-direction as the charge density difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$,
-at zero and finite electric fields ($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) 
-extends to $\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a}). When $L$ is large enough,   
-the induced dipoles $\boldsymbol{u}$ from the periodic images do not interact mutually 
-as the integral in Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge density at the layer. 
-However, we can see from Eqs. \ref{eq:def-eps-1} that both
+$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$.
+The absence of bonding perpendicular to the plane confines the induced
+dipoles along the \textit{z}-direction as the charge density
+difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$, at zero and
+finite electric fields
+($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
+$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf
+  a}). When $L$ is large enough, the induced dipoles $\boldsymbol{u}$
+from the periodic images do not interact mutually as the integral in
+Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge
+density at the layer.  However, we can see from
+Eqs. \ref{eq:def-eps-1} that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of the cell $\Omega$. 
-Therefore, any calculation performed using such definition will intrinsically depend on the magnitude of $L$ as an additional parameter. 
-This dependence can be clearly demonstrated by
+$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
+the cell $\Omega$.  Therefore, any calculation performed using such
+definition will intrinsically depend on the magnitude of $L$ as an
+additional parameter.  This dependence can be clearly demonstrated by
 plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
-theory (DFT) using hybrid functionals (see {\it Methods} for details) as a function 
-of $L$ for P$\bar{6}$m2 transitional metal dichalcogenides 
-(TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
-Te (top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}, respectively). 
-Despite of the magnitudes of $L$ both components of the dielectric constant 
-change systematically without a clear convergence.  
+theory (DFT) using hybrid functionals (see {\it Methods} for details)
+as a function of $L$ for P$\bar{6}$m2 transitional metal
+dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
+(top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c},
+respectively).  Despite of the magnitudes of $L$ both components of
+the dielectric constant change systematically without a clear
+convergence.
 %
-Simulations performed at higher levels of theory using 
-many-body techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}), 
-and also taking into account  electron-hole excitations at the level of the Bethe-Salpeter equation 
-at the frequency-dependent versions of $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$
-invariably give alike results (Supplementary Figure \ref{fig:S2}). 
-Indeed, the variations observed in peak positions at different values of $\omega(eV)$ 
-implicate that several other related quantities, such as, the optical absorption and 
-optical conductivity, suffer the same deficiencies. In a fully first-principles theory 
-such intrinsic dependence on $L$ should not be present. 
+Simulations performed at higher levels of theory using many-body
+techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}),
+and also taking into account electron-hole excitations at the level of
+the Bethe-Salpeter equation (BSE) for the frequency-dependent
+$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
+results (Supplementary Figure \ref{fig:S2}). Moreover, due to the long
+range Coulomb interaction, variations of the quasi-particle energy
+(and corresponding peak positions) with lattice constant $L$ at the
+G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
+SXX). Such results implicate that several other related quantities,
+including the optical absorption and optical conductivity, suffer the
+same deficiencies, which should be avoided in a fully first principles
+theory.
 %
@@
 %
-It is worth mentioning that experimental results also need to define an effective thickness of the sheet 
-to interpret ellipsometry data \cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, 
-reflectance or transmission spectra \cite{Li_2014, Yoffe-Wilson69} in 
-order to extract information for the real part of the dielectric functions. 
-We argue that such procedure may induce inevitably variations of the results as the 
-thickness is normally chosen by the interlayer spacing of the 
-respective bulk materials (Supplementary Section \ref{sec:2D-3D-rescale} gives an exhaustive analysis).  
+It is worth mentioning that experimental dielectric results of 2D
+materials generally need to define an ``effective thickness'' of the sheet
+to interpret ellipsometry data
+\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
+transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
+extract information for the real part of the dielectric functions.  We
+argue that such procedure may induce inevitably variations of the
+results as the thickness is normally chosen by the interlayer spacing
+of the respective bulk materials (details see Supplementary Section
+\ref{sec:2D-3D-rescale}).
 %
@@
 and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
-A similar curve profile is obtained in both components of the dielectric constant including the much 
-abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
-interlayer interactions.  Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
+% A similar curve profile is obtained in both components of the dielectric constant including the much 
+% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
+% interlayer interactions.
+\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true.
+I think it is better not to explicitly mention this.}
+Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
 the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
@@
 %
-where $E_{\mathrm{g}}$ is the minimal electronic bandgap, 
-$\delta$ is the intrinsic or covalent thickness of the layer (Fig.
-\ref{fig-1}{\bf a}), and $C^{\parallel} = {8\pi^{2}\varepsilon_0\AA}/{eN}$, where $N$ corresponds to the degeneracy of the bands associated with $E_{\mathrm{g}}$,
-and $C^{\perp} = {1}/{4\pi}$.  Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, 
-they generalize a direct relationship between the polarizability and the electronic and structural properties for any 
-2D material in a new framework. 
-We can show that these equations are valid for the current library of known layered materials 
-involving different lattice symmetry, element composition, optical and electronic properties. 
+where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
+the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf
+  a}), and $C^{\parallel} = \frac{Ne^2}{2 \pi}$, where $N$ corresponds to
+the degeneracy of the bands associated with $E_{\mathrm{g}}$, and
+$C^{\perp} = {\varepsilon_{0}}$.  \todo[inline]{The previous
+  expressions for the coefficients are wrong. Please see the version
+  in SI.} Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
+\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
+the polarizability and the electronic and structural properties for
+any 2D material in a new framework.  We can show that these equations
+are valid for the current library of known layered materials involving
+different lattice symmetry, element composition, optical and
+electronic properties.
 %
@@
 and thin layer organic-inorganic perovskites (ABX$_{3}$) (Fig. \ref{fig-3}{\bf a}) 
-showed that our method enables full correlation between these disparate variables. 
+shows that our method enables full correlation between these disparate variables. 
 %%
@@
 %the selected 2D materials (see {\it Methods}). 
-Figure \ref{fig-3}{\bf b}
-shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
-(bar plots) of all the 2D materials investigated, covering a wide
-spectrum range from far-infrared to ultraviolet at HSE06 level. 
-Note from dimension
-analysis, it is more intuitive to express the polarizability as
+Figure \ref{fig-3}{\bf b} compares the calculated fundamental bandgap
+$E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar
+plots) of all the 2D materials investigated, covering a wide spectrum
+range from far-infrared to ultraviolet.  Note from dimension analysis,
+it is more intuitive to express the polarizability as
 $\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
 \AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
-descending trend when $E_{\mathrm{g}}$ increases, while 
-no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
+descending trend when $E_{\mathrm{g}}$ increases, while no apparent
+correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
 $E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with elements 
-having large polarizabilities, such as Hf and Zr in 1T-HfO$_2$ or 1T-ZrO$_2$, 
-respectively, also transfer alike features for the layers with slightly variations between 
-1T and 2H phases. The former normally shows larger values of $\alpha_{\mathrm{2D}}^{\parallel}$ 
-than the latter. 
+\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with
+elements having large polarizabilities, such as Hf and Zr in
+1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
+for the layers with slightly variations between 1T and 2H phases. The
+former normally shows larger values of
+$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
+\todo[inline]{sorry but I don't quite get the idea of this
+  sentence. In fact HfO2 and ZrO2 have quite low in-plane
+  polarizabilities compared with even TiO2. Shall we just remove these
+  sentenses? }
 %
@@
 excellent linear correlation with $\delta_{\mathrm{cov}}$, with
-$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure \ref{fig-3}{\bf d}). 
-This results that $\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
-\delta_{\mathrm{cov}}$ has a strong physical meaning through the geometry of the layer. 
-Similar
-to the molecular polarizability which characterizes the volume of
-electron cloud of an isolated molecule \cite{Israelachvili_2011},
+$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
+\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
+This results indicate that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
+physical meaning through the geometry of the layer.  Similar to the
+molecular polarizability which characterizes the volume of electron
+cloud of an isolated molecule \cite{Israelachvili_2011},
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section \ref{sssec:theory-3}). Indeed,
-the universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
+material (see Supplementary Section \ref{sssec:theory-3}). Indeed, the
+universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
 Figure \ref{fig-3}{\bf d} indicates that the quantity
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
-electronic approaches
-\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is in reality the
-(dielectric) characteristic thickness of a 2D material, and can be
-used to resolve the long-existing controversy about the experimental
-thickness of 2D materials, such as graphene \cite{Shearer_2016}.
+electronic and optical approaches
+\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
+is in reality the (dielectric) characteristic thickness of a 2D
+material, and can be used to resolve the long-existing controversy
+about the experimental thickness of 2D materials, such as graphene
+\cite{Shearer_2016}.
 %
 To rule out the possibility that our conclusion are limited by the
-number of materials used at HSE06, we further 
-validate Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
-using a different database\cite{Haastrup_2018}, from which we extracted the dielectric
+number of materials used at HSE06, we further validate
+Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
+database\cite{Haastrup_2018}, from which we extracted the dielectric
 properties of over 230 compounds calculated at the PBE level, and
-superimpose with our results in Figure \ref{fig-3}{\bf c} and \ref{fig-3}{\bf d}
-(see details in Supplementary Section \ref{sec:gpaw-1}). Although the
-dielectric properties may be overestimated at PBE level due to
-underestimation of the bandgap compared with the more accurate HSE06
-functionals \cite{Van_Dyck_2017}, similar linear trends can be
-observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ with the linear coefficient very close
-to the HSE06 results (see details in Supplementary Section
-\ref{sec:gpaw-2}).
+superimpose with our results in Figure \ref{fig-3}{\bf c} and
+\ref{fig-3}{\bf d} (see details in Supplementary Section
+\ref{sec:gpaw-1}). Although the dielectric properties may be
+overestimated at PBE level due to underestimation of the bandgap
+compared with the more accurate HSE06 functionals
+\cite{Van_Dyck_2017}, similar linear trends can be observed for both
+$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+with the linear coefficient very close to the HSE06 results (see
+details in Supplementary Section \ref{sec:gpaw-2}).
 
-We have also searched for additional relations
-between the 2D polarizabilities with other physical quantities,
-including the effective carrier mass, quantum capacitance and total
-atomic polarizabilities with no apparent correlations being found
-(Supplementary Section \ref{sec:gpaw-3}). 
-We found however that Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} 
-have a natural connection with the screening properties of the layer. 
+We have also searched for additional relations between the 2D
+polarizabilities with other physical quantities, including the
+effective carrier mass, quantum capacitance (density of states) and
+total atomic polarizabilities with no apparent correlations being
+found (Supplementary Section \ref{sec:gpaw-3}).  We found however that
+Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
+connection with the screening properties of the layer.
 %
@@
 occur in-plane and the interlayer stacking is not a critical factor.
+\todo{??}
 The dielectric constant $\varepsilon$ although not well-defined for
 a monolayer 2D material becomes applicable when the 2D layers are
-putted together. 
+put together. 
 %
@@
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
-$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
+$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
 with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
-(x-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
+(\textit{x}-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
 Both HSE06 and PBE datasets give almost identical results.  
@@
 
-Our results show that the electric polarizability $\alpha$ is a local 
-variable determining the dielectric properties of 2D materials. 
-There exist well defined relationships between $\alpha$ and 
-other quantities hidden in the electronic properties.  
-According to our analysis, simple 
-scaling equations involving bandgaps and layer thicknesses 
-can be used to describe both dielectric and electronic 
-features at the same footing. A dielectric anisotropy index is 
-found relating any material dimension with its controllability.  
-Thus, our results suggest that the challenge of understanding the 
-dielectric phenomena is in general a geometrical problem 
-mediated by the bandgap.
+Our results show that the 2D electric polarizability
+$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
+properties of 2D materials.  There exist well defined relationships
+between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
+electronic properties.  According to our analysis, simple scaling
+equations involving bandgaps and layer thicknesses can be used to
+describe both dielectric and electronic features at the same
+footing. A dielectric anisotropy index is found relating any material
+dimension with its controllability.  Thus, our results suggest that
+the challenge of understanding the dielectric phenomena is in general
+a geometrical problem mediated by the bandgap. We believe the
+principles presented here will benefit both fundamental understanding
+of 2D materials as well as rational device design and optimization.
 
@@
 \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
-Augmented Wave (PAW) approach with Kresse's mainly GW
-Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
-calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
+Augmented Wave (PAW) approach with Kresse's mainly GW Pseudopotentials
+\cite{Kresse_1999_pseudopotentials}. Band gaps were calculated using
+the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
 \cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
@@
 18$\times$18$\times$1 k-grid and electric field strength of 0.001
-eV/\AA. The materials in C2DB database for comparison were choses with
-the GW bandgap larger than 0.05 eV. Bulk layered materials were
-constructed by relaxing the c-axis length of corresponding monolayer
-material with the interlayer van der Waals (vdW) interactions
-calculated by non-local vdW correlation
+eV/\AA. The materials from Ref. \citenum{Haastrup_2018} for comparison
+were choses with the GW bandgap larger than 0.05 eV. Bulk layered
+materials were constructed by relaxing the c-axis length of
+corresponding monolayer material with the interlayer van der Waals
+(vdW) interactions calculated by non-local vdW correlation
 functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
@@
 
-\bibliography{ref1}
+\bibliography{ref}
 
@@
 \centering
-\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
+\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
 \caption{\label{fig-1} \textbf{2D polarizability as the true
@@
 \centering
-\includegraphics[width=0.70\linewidth]{img/fig2_v110418.pdf}
+\includegraphics[width=0.70\linewidth]{img/fig2.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
 \centering
-\includegraphics[width=1.04\linewidth]{./img/fig4_v111618ii.pdf}
+\includegraphics[width=1.04\linewidth]{img/fig4.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties

### 2018-12-16 paper.tex
Add HSE datasheet into manuscript and SI

@@
     2H-MoS$_{2}$ & 40.0 & 2.50 \\
-    2H-MoSe$_{2}$ & &  \\
+    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
     2H-MoTe$_{2}$ & 58.1 & 3.07  \\

### 2018-12-17 SI.tex
First change of manuscriot and figures

@@
 \usepackage{footnote}
+\usepackage{braket}
 \usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}
@@
 %\usepackage{xr}
-\externaldocument{paper}
+\externaldocument[main-]{paper}
 
@@
 \newpage{}
-%\section{Further Analysis of the 2D Polarizability Model}
-%\label{sec:2D-pol}
-
-%In this section, we discuss further topics about the 2D polarizability
-%model proposed in the main text.
-
-%\section{Profile of induced dipoles of 2D material}
-%\label{sec:dipole-plot}
-%Here we show in detail the
-%$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
-%the 2H-MoS$_{2}$ slab in main text Figure 1a. The
-%density $\rho$ is calculated as the average value in the
-%\textit{xy}-plane, and the value is shown in Figure
-%\ref{fig:rho-profile}. As can be seen the induced charges on the
-%MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
-%SL size $L \gg$12 \AA{} as in the first principle calculations done in
-%the main text, the induced dipoles from the periodic images do not
-%interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
-%
-%\begin{figure}[htbp]
-%  \centering
-%  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
-%  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
-%    superlattice, corresponding to main text Figure
-%    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
-%    inside the SL separated by vacuum layer. The dielectric constant
-%    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
-%    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
-%    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
-%    MoS$_{2}$ layer, green and red parts corresponding to negative and
-%    positive induced charges. The external electric field
-%    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
-%  \label{fig:rho-profile}
-%\end{figure}
-
-\section{Table of Contents}
+
+\section*{Table of Contents}
 
@@
 
-\section{Calculations using many-body Green function method and frequency-dependent quantities $\alpha_{\mathrm{2D}}(\omega)$ and $\varepsilon_{\mathrm{SL}}(\omega)$}
-
+\section{Further analysis on the dielectric properties of 2D materials}
+
+In this section we provide more analysis on the dielectric properties
+of 2D materials, with focus on the dielectric properties calculated
+using many-body Green function method (G$_0$W$_0$) and the
+frequency-dependency of the superlattice dielectric functions and 2D
+polarizabilities.
+
+\subsection{Profile of induced dipoles of 2D material}
+\label{sec:dipole-plot}
+Here we show in detail the
+$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
+the 2H-MoS$_{2}$ slab in main text Figure 1a. The
+density $\rho$ is calculated as the average value in the
+\textit{xy}-plane, and the value is shown in Figure
+\ref{fig:rho-profile}. As can be seen the induced charges on the
+MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
+SL size $L \gg$12 \AA{} as in the first principle calculations done in
+the main text, the induced dipoles from the periodic images do not
+interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
+
+\begin{figure}[htbp]
+ \centering
+ \includegraphics[width=0.5\linewidth]{img/SI-dipole-MoS2.pdf}
+ \caption{$\Delta \rho$ as a function of $z$ around the
+   MoS$_{2}$ layer, corresponding to main text Figure
+   \ref{main-fig-1}a. Green and red parts corresponding to negative and
+   positive induced charges. The external electric field
+   $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
+ \label{fig:rho-profile}
+\end{figure}
+
+\subsection{Dielectric properties calculated using many-body Green function method and frequency dependency}
+\label{ssec:gw}
+
+Here we will show the results of dielectric properties calculated
+using higher level of many-body Green function method (G$_0$W$_{0}$)
+and with electron-hole interaction. We first compare the case of a
+layer of hBN within an superlattice with varying size with the
+dielectric properties calculated using PBE and G$_{0}$W$_{0}$ methods,
+as shown in Figure
+\ref{fig:GW-PBE-alpha}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$, shown in
+Figure \ref{fig:GW-PBE-alpha}a and \ref{fig:GW-PBE-alpha}b,
+respectively, do not converge with $L$, while the corresponding 2D
+polarizabilities in Figure \ref{fig:GW-PBE-alpha}c and
+\ref{fig:GW-PBE-alpha}d are almost $L$-independent. It is worthnoting
+that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than PBE method.
 \begin{figure}[htbp]
@@
  \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
-  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
-calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
-}
+ \caption{Variation of dielectric properties and
+   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
+   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.
+   \textbf{a}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ as function of
+   $L$. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as function of
+   $L$ corresponding to
+   \textbf{b}. \textbf{c}. $\varepsilon_{\mathrm{SL}}^{\perp}$ as
+   function of $L$.  \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}$ as
+   function of $L$. In all cases the values obtained using
+   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
+   better estimation of the bandgap.}
   \label{fig:GW-PBE-alpha}
@@
 
-\begin{figure}[htbp]
+Next we will investigate the frequency-dependent dielectric properties of the 2D materials using various methods.
+The imaginary part of the frequency-dependent dielectric function of an periodic system is calculated using the following relation:
+
+\begin{equation}
+\begin{aligned}
+  \label{eq:dft-dielectric}
+\varepsilon_{\alpha\beta}^{(2)}(\omega)=\frac{4\pi e^2}{\Omega}\lim\limits_{q\rightarrow 0}\frac{1}{q^2}\sum_{v,c,\mathbf{k}}&2\omega_\mathbf{k}\delta(\epsilon_{c\mathbf{k}}-\epsilon_{v\mathbf{k}}-\omega) \\
+&\times\braket{u_{c\mathbf{k}+q\mathbf{e}_\alpha}|u_{v\mathbf{k}}}\braket{u_{v\mathbf{k}}|u_{c\mathbf{k}+q\mathbf{e}_\beta}}
+\end{aligned}
+\end{equation}
+Through the Kramers-Kronig transformation the real part of the dielectric function can be obtained as:
+
+\begin{equation}
+  \varepsilon_{\alpha\beta}^{(1)}(\omega)=1+\frac{2}{\pi}\int_0^\infty\frac{\varepsilon_{\alpha\beta}^{(2)}(\omega')\omega'}{\omega'^2-\omega^2}d\omega'
+\end{equation}
+
+We calculate the frequency-dependent dielectric properties of hBN with
+varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$
+with electron-hole interaction (G$_{0}$W$_{0}$+BSE). As shown in
+Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out}, the
+intensities of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
+throughout the whole frequency range. The $L$-dependency can also be
+removed using Eqs. \ref{main-eq:alpha-para-def} and
+\ref{main-eq:alpha-perp-ref}, yielding lattice-independent
+polarizabilities throughout the frequency domain.
+
+\begin{figure}[H]
   \centering
  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
-  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
-Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
-many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
-with the only variable quantity being $L$. The systematic shift 
+ \caption{Dependence of in-plane dielectric properties on $L$ for
+   monolayer BN calculated using PBE method: \textbf{a} Real part of
+   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{b} Real part of
+   $\alpha_{\mathrm{2D}}^{\parallel}$, \textbf{c} Imaginary part of
+   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part of
+   $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling is used
+   in all simulations with the only variable quantity being $L$. }
+  \label{fig:PBE-omega-in}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
+   \caption{Dependence of out-of-plane dielectric properties on $L$ for
+   monolayer BN calculated using PBE method: \textbf{a} Real part of
+   $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{b} Real part of
+   $\alpha_{\mathrm{2D}}^{\perp}$, \textbf{c} Imaginary part of
+   $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{d} Imaginary part of
+   $\alpha_{\mathrm{2D}}^{\perp}$.  The same {\bf k}-sampling is used
+   in all simulations with the only variable quantity being $L$. }
+  \label{fig:PBE-omega-out}
+\end{figure}
+
+We note that the result may change slightly when G$_{0}$W$_{0}$ method
+is used. As shown in Figures \ref{fig:GW-omega-in} and
+\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
+functions change with $L$, but also the peak positions. As a result
+the obtained polarizabilities also show $L$-dependent peak shift. This
+can be explained by the long-range nature of Coulomb interactions. In
+fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
+\begin{equation}
+  \label{eq:GW-formula}
+  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
+\end{equation}
+where $G$ is the non-interacting Green function, and $\nu$ is the
+Coulomb interaction. Since the dielectric constant $\varepsilon$
+changes with $L$, the self energy as well quasi-particle energies of
+the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
+higher peak energy of the dielectric spectrum when $L$ increases. Such
+peculiar $L$-dependency can be minimized when adding electron-hole
+interaction through the Bethe-Salpethe equation (BSE), as shown in
+Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
+polarizabilities again becomes lattice-independent due to the
+localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.
+
+Combining the accuray of bandgap estimation, reproducible results of
+frequency-dependent dielectric properties and calculation efforts, the
+choice of HSE06 hybrid functional seems used in the main text provides
+best tradeoff between all aspects.
+
+\begin{figure}[H]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
+  \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated using G$_{0}$W$_{0}$ method. Peak shift can be observed in the dielectric function spectra.
 }
@@
 
-\begin{figure}[htbp]
-  \centering
- \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
-  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
-Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
-many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
-with the only variable quantity being $L$. The systematic shift 
-}
+\begin{figure}[H]
+  \centering
+ \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
+ \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
+   using G$_{0}$W$_{0}$ method. Peak shift can be observed in the
+   dielectric function spectra.}
   \label{fig:GW-omega-out}
@@
 
-\begin{figure}[htbp]
-  \centering
- \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
-  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
-Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
-many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
-with the only variable quantity being $L$. The systematic shift 
-}
-  \label{fig:GW-omega-in}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
- \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
-  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
-Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
-many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
-with the only variable quantity being $L$. The systematic shift 
-}
-  \label{fig:GW-omega-out}
-\end{figure}
-
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering
  \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
-  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
+  \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into account electron-hole interactions at the level of 
   the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
-  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
-  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
+  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$.
 }
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering
  \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
-  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
+  \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into account electron-hole interactions at the level of 
   the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
-  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
-  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
+  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
 }

### 2018-12-17 paper.tex
First change of manuscriot and figures

@@
 \usepackage{xr-hyper} 
-\externaldocument{SI}
+\externaldocument[SI-]{SI}
 
@@
 permittivity) plays a crucial role in bridging various fundamental
-material properties, such as bandgaps, optical absorption, and
-conductivities.  \todo{Add more citations} $\varepsilon$ characterizes
-the ability to screen an electric field $\boldsymbol{E}$ which
-classifies metals, semiconductors and insulators.  \todo[inline]{I
-  shortened the sentences. However, can we really "classify" the
-  material only by $varepsilon$? For instance HfO2 has large
-  $\varepsilon$ but also large bandgap}
+material properties, such as bandgaps
+\cite{Moss_1950_relation,Moss_1985_n_Eg}, optical absorption
+\cite{kittel_2005_introduction}, and conductivities
+\cite{Dressel_2001_electrodynamics}. $\varepsilon$ characterizes the
+ability to screen an electric field $\boldsymbol{E}$ which classifies
+metals, semiconductors and insulators.  \todo[inline]{I shortened the
+  sentences. However, can we really "classify" the material only by
+  $\varepsilon$? For instance HfO2 has large $\varepsilon$ but also
+  large bandgap}
 % Such definitions determine a broad range of
@@
 ($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
-$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf
-  a}). When $L$ is large enough, the induced dipoles $\boldsymbol{u}$
-from the periodic images do not interact mutually as the integral in
-Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge
-density at the layer.  However, we can see from
-Eqs. \ref{eq:def-eps-1} that both
+$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a} and
+Supplementary Figure \ref{SI-fig:rho-profile}). When $L$ is large
+enough, the induced dipoles $\boldsymbol{u}$ from the periodic images
+do not interact mutually as the integral in Eq. \ref{eq:def-eps-2}
+depends only locally on the atomic charge density at the layer.
+However, we can see from Eqs. \ref{eq:def-eps-1} that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
@@
 $\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
-theory (DFT) using hybrid functionals (see {\it Methods} for details)
+theory (DFT) using hybrid functionals (see {\it Theoretical Methods} for details)
 as a function of $L$ for P$\bar{6}$m2 transitional metal
@@
 Simulations performed at higher levels of theory using many-body
-techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}),
-and also taking into account electron-hole excitations at the level of
-the Bethe-Salpeter equation (BSE) for the frequency-dependent
+techniques, G$_{\rm 0}$W$_{0}$, and also taking into account
+electron-hole excitations at the level of the Bethe-Salpeter equation
+(BSE) for the frequency-dependent
 $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
-results (Supplementary Figure \ref{fig:S2}). Moreover, due to the long
-range Coulomb interaction, variations of the quasi-particle energy
-(and corresponding peak positions) with lattice constant $L$ at the
-G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
-SXX). Such results implicate that several other related quantities,
-including the optical absorption and optical conductivity, suffer the
-same deficiencies, which should be avoided in a fully first principles
-theory.
+results(details see Supplementary Section \ref{SI-ssec:gw}).
+% Moreover, due to the long range Coulomb
+% interaction, variations of the quasi-particle energy (and
+% corresponding peak positions) with lattice constant $L$ at the
+% G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
+% SXX). Such results implicate that several other related quantities,
+% including the optical absorption and optical conductivity, suffer the
+% same deficiencies, which should be avoided in a fully first principles
+% theory.
 %
@@
 of the respective bulk materials (details see Supplementary Section
-\ref{sec:2D-3D-rescale}).
+\ref{SI-sec:2D-3D-rescale}).
 %
@@
 $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
+$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Section \ref{SI-ssec:gw}). 
 %
@@
 More discussions about the choice of the 2D polarizability
-and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.
+and comparison with other methods can be found in Supplementary Section \ref{SI-sec:2D-3D-rescale}.
 
@@
 formalism\cite{kittel_2005_introduction} (see Supplementary
-Section \ref{sssec:theory-1} and  \ref{ssec:theory-2} for details), 
+Section \ref{SI-sssec:theory-1} and  \ref{SI-ssec:theory-2} for details), 
 we can show that
@@
 $E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with
+\ref{SI-sec:pol-2D-Eg}). It is worth mentioning that materials with
 elements having large polarizabilities, such as Hf and Zr in
@@
 with that from Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
-(see Supplementary Section \ref{sec:pol-2D-Eg} and
+(see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
 Supplementary Figure \ref{fig:alpha-Eg-diff}) which suggests that higher levels 
@@
 experimentally accessible optical bandgap of 2D materials (details see
-Supplementary Section \ref{sec:gpaw-2} and Supplementary Figure
+Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
 \ref{fig:opt}).
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section \ref{sssec:theory-3}). Indeed, the
+material (see Supplementary Section \ref{SI-sssec:theory-3}). Indeed, the
 universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
@@
 \ref{fig-3}{\bf d} (see details in Supplementary Section
-\ref{sec:gpaw-1}). Although the dielectric properties may be
+\ref{SI-sec:gpaw-1}). Although the dielectric properties may be
 overestimated at PBE level due to underestimation of the bandgap
@@
 with the linear coefficient very close to the HSE06 results (see
-details in Supplementary Section \ref{sec:gpaw-2}).
+details in Supplementary Section \ref{SI-sec:gpaw-2}).
 
@@
 total atomic polarizabilities with no apparent correlations being
-found (Supplementary Section \ref{sec:gpaw-3}).  We found however that
+found (Supplementary Section \ref{SI-sec:gpaw-3}).  We found however that
 Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
@@
 index of corresponding 2D layer (see additional details in Supplementary Section
-\ref{sssec:aniso-2}), which is the basis for the separation of bulk
+\ref{SI-sssec:aniso-2}), which is the basis for the separation of bulk
 and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
@@
 $\eta$ of common semiconducting materials in other dimensions 
-(Supplementary Section \ref{sssec:aniso-1}) on the phase diagram in Figure
+(Supplementary Section \ref{SI-sssec:aniso-1}) on the phase diagram in Figure
 \ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)

### 2018-12-17 SI.tex
Correct x-references in manuscript and SI

@@
 
-1. Supplementary Figure \ref{fig:S1}:  Simulations of $\varepsilon_{\mathrm{SL}}$ using many-body $G_{\rm 0}W_{\rm 0}$   \\
-%
-%2. Supplementary Section \ref{epsilon-model}: $\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ dependence on $L$ \\ 
-%
-2. Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant \\
-%
-3. Supplementary Section \ref{ssec:theory-1}: Polarizability-Based Theoretical Model  \\ 
-%
-4. Supplementary Section \ref{sec:pol-2D-Eg}: Dependence of $\alpha_{\mathrm{2D}}$ on bandgap \\ 
-%
-5.
+\begin{itemize}
+\item Supplementary Section \ref{sec:polarizability-analysis}: Further analysis on the dielectric properties of 2D materials
+
+\item Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant
+
+\item Supplementary Section \ref{sec:theory-1}: Polarizability-Based Theoretical Model
+
+\item Supplementary Section \ref{sec:pol-2D-Eg}: Dependence of $\alpha_{\mathrm{2D}}$ on bandgap
+
+\item Supplementary Section \ref{sec:gpaw}: Validation on the C2DB 2D materials database
+
+\item Supplementary Section \ref{sec:2D-3D}: More discussion about the
+  relation between 2D and 3D properties
+
+  \item Supplementary Section \ref{sec:aniso}: More discussions about the dielectric anisotropy
+
+\item Supplementary Section \ref{sec:raw}: Raw data from first
+  principles calculations
+
+\end{itemize}
 
@@
 \section{Further analysis on the dielectric properties of 2D materials}
+\label{sec:polarizability-analysis}
 
@@
 $\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
-the 2H-MoS$_{2}$ slab in main text Figure 1a. The
+the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}. The
 density $\rho$ is calculated as the average value in the
@@
    MoS$_{2}$ layer, corresponding to main text Figure
-   \ref{main-fig-1}a. Green and red parts corresponding to negative and
+   \ref{main-fig-1}\textbf{a}. Green and red parts corresponding to negative and
    positive induced charges. The external electric field
@@
 removed using Eqs. \ref{main-eq:alpha-para-def} and
-\ref{main-eq:alpha-perp-ref}, yielding lattice-independent
+\ref{main-eq:alpha-perp-def}, yielding lattice-independent
 polarizabilities throughout the frequency domain.
@@
    $\alpha_{\mathrm{2D}}^{\parallel}$, \textbf{c} Imaginary part of
-   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part of
-   $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling is used
-   in all simulations with the only variable quantity being $L$. }
+   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part
+   of $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling
+   is used in all simulations with the only variable quantity being
+   $L$. Clearly, the $L$-dependency of the superlattice dielectric
+   function is removed using 2D polarizabilities.}
   \label{fig:PBE-omega-in}
@@
     $\alpha_{\mathrm{2D}}^{\perp}$.  The same {\bf k}-sampling is used
-   in all simulations with the only variable quantity being $L$. }
+    in all simulations with the only variable quantity being
+    $L$. Clearly, the $L$-dependency of the superlattice dielectric
+    function is removed using 2D polarizabilities.}
   \label{fig:PBE-omega-out}
@@
  \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
-  \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated using G$_{0}$W$_{0}$ method. Peak shift can be observed in the dielectric function spectra.
-}
+ \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated
+   using G$_{0}$W$_{0}$ method. A shift of peak position (frequency)
+   in the dielectric function spectra is observed, resulted from the
+   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
+   invloving the 2D slab.}
   \label{fig:GW-omega-in}
@@
  \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
-   using G$_{0}$W$_{0}$ method. Peak shift can be observed in the
-   dielectric function spectra.}
+   using G$_{0}$W$_{0}$ method.  A shift of peak position (frequency)
+   in the dielectric function spectra is observed, resulted from the
+   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
+   invloving the 2D slab.}
   \label{fig:GW-omega-out}
@@
  \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
-  \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into account electron-hole interactions at the level of 
-  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
-  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$.
-}
+ \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into
+   account electron-hole interactions at the level of the
+   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  The peak shift
+   in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$. As a
+   result the polarizabilities becomes almost independent of $L$,
+   consistent to results obtained by the PBE method.}
   \label{fig:BSE-omega-in}
@@
  \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
-  \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into account electron-hole interactions at the level of 
-  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
-  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
-}
+ \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into
+   account electron-hole interactions at the level of the
+   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  As a result
+   the polarizabilities becomes almost independent of $L$, consistent
+   to results obtained by the PBE method.  }
   \label{fig:BSE-omega-out}
@@
 \section{Polarizability-Based Theoretical Model}
-\label{ssec:theory-1}
+\label{sec:theory-1}
 The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
@@
 that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
-give rise to the main text Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}.
-
-{\bf ES:} There is something weird with the cross-referencing for the equations 3a and 3b between the main text and 
-SI. They changed to 2a and 2b in the SI.
-
-\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-para-def} 3a}  %
-\label{sssec:theory-1}
-
-In this section we show how main text Eq. \ref{eq:alpha-para-def}
+give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
+\ref{main-eq:2D-Moss-perp}.
+
+% {\bf ES:} There is something weird with the cross-referencing for the equations 3a and 3b between the main text and 
+% SI. They changed to 2a and 2b in the SI.
+
+\subsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-para}}  %
+\label{ssec:theory-1-para}
+
+In this section we show how main text Eq. \ref{main-eq:alpha-para-def}
 is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
@@
   {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
-  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
+  \frac{|<u_{\mathrm{c}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
   {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
 \end{equation}
-Present the summation of k-space into integral, and further combining
-with the Bloch wave representation and the
-$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
-at Eq. \ref{eq:alpha-para-def}. Note that from
-Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
-$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
-$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
-where $N$ is the degeneracy associated with the minimal bandgap. Such
-relation predicts the linear correlation coefficient between
+Following the method of $\mathbf{k} \cdot \mathbf{p}$ theory from
+Ref. \citenum{Jiang_2017_Eg_Eb}, the matrix element in the numerator
+of Eq. \ref{eq:alpha_para_RPA} is approximated by:
+
+\begin{equation}
+\label{eq:matrix-approx}
+|<u_{\mathrm{c}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}
+\approx {\displaystyle \frac{\hbar^{2}}{2 m^{*}}
+  \frac{1}{E_{\mathrm{g}} + \frac{\hbar^{2} k^{2}}{2 m^{*}}}}
+\end{equation}
+plug it into Eq.
+\ref{eq:alpha_para_RPA} and integrate within the 2D Brillouin Zone from $|k|=0$ to $|k|= k_{\mathrm{BZ}}$, where $k_{\mathrm{BZ}}$ is the wavevector at the boundary of the 2D Brillouin Zone, we get:
+\begin{equation}
+  \label{eq:derivation-2D-Moss-para}
+  \begin{aligned}
+\alpha_{\mathrm{2D}}^{\parallel} &= N\cdot -\frac{e^{2}}{2 \pi}
+\frac{1}{E_{g} + \beta} \Biggr\vert_{\beta=0}^{\beta=\frac{\hbar^{2} k^{2}_{\mathrm{BZ}}}{m^{*}}} \\
+&\approx N e^{2}/(2\pi E_{\mathrm{g}}) = C^{\parallel} E_{g}^{-1}
+\end{aligned}
+\end{equation}
+where $N$ is de degeneracy of bands associated with $E_{g}$. The
+approximation in Eq. \ref{eq:derivation-2D-Moss-para} is due to the
+fact that $\frac{\hbar^{2} k^{2}_{\mathrm{BZ}}}{m^{*}} \gg E_{g}$, and
+we arrive at main text Eq. \ref{main-eq:2D-Moss-para}.
+
+The coefficient of $C^{\parallel}$ adapted from
+Ref. \citenum{Jiang_2017_Eg_Eb} $C^{\parallel} = N e^{2}/(2\pi)$
+predicts linear correlation between $\alpha^{\parallel}_{\mathrm{2D}}$
+and $E_{\mathrm{g}}^{-1}$. We validate this by examining the
+DFT-calculated
 $(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
-\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
-$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From Figure 2{\bf c}, we have
-$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
-\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
-between 2 and 3, which is a reasonable result for the 2D materials
-studied.
-
-{\bf ES:} Tian, please include more details in this section on the derivations!
-
-\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-perp-def}}
-\label{ssec:theory-2}
-
-For main text Eq. \ref{eq:alpha-perp-def}, treating the in-plane
+\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) in main text
+Figure \ref{main-fig-3}\textbf{c}. The coefficient $C^{\parallel}$
+becomes
+$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N = 0.183$,
+corresponding to $N$ between 2 and 3, which is a reasonable result for
+the 2D materials studied.
+
+% {\bf ES:} Tian, please include more details in this section on the derivations!
+
+\subsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-perp}}
+\label{ssec:theory-1-perp}
+
+For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
 wave functions as plane wave with form
@@
 model for the confinement in z-direction than simple square potential
-well, which may be explored further. Nevertheless the simple model presented
-here still captures the bandgap-independent and thickness-related feature
-of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
-text. In the next section we will provide a simple explanation for the $\alpha \propto \delta$ relation from fundamental electrostatics theory.
+well, which may be explored further. Nevertheless the simple model
+presented here still captures the bandgap-independent and
+thickness-related feature of $\alpha_{\mathrm{2D}}^{\perp}$,
+supporting our findings in the main text. In the next section we will
+provide a simple explanation for the $\alpha \propto \delta$ relation
+from fundamental electrostatics theory.
+
+\subsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
+  from fundamental electrostatics}
+\label{ssec:theory-1-perp-fundamental}
+
+The dependency of $\alpha_{\mathrm{2D}}^{\perp}$ on the thickness
+$\delta$ of a 2D material, can also be regarded using fundamental
+electrostatic model. Consider the smallest repeating unit of the 2D
+material with xy-plane area $A$, under small perturbation field $E$
+along the z-direction.  Note that the surface bound charge
+$\sigma_{\mathrm{b}}=n e /A$, where $n$ is the number of unit charges
+contributes to the bound charges, comes only from the dipoles of the
+outer-most atoms, since the induced charges from inner atoms are
+cancel out (see Figure \ref{fig:classic-model}).
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\linewidth]{img/SI-classic.pdf}
+  \caption{Fundamental electrostatic model for the
+    thickness-dependency of $\alpha_{\mathrm{2D}}^{\perp}$, using 2H-MoS2 as an
+    example. Left: induced dipoles from individual atoms along the
+    z-direction. The positive and negative induced charges from inner
+    atoms cancel out. Right: simplified model for the thickness
+    dependency of $\alpha_{\mathrm{2D}}^{\perp}$, where the surface dipole density
+    $\boldsymbol{\mu}$ comes only from the outer-most atoms.}
+  \label{fig:classic-model}
+\end{figure}
+From the definition of
+$\alpha_{\mathrm{2D}}^{\perp}$, we have:
+\begin{equation}
+  \label{eq:alpha-classic}
+  \alpha_{\mathrm{2D}}^{\perp} = \frac{\boldsymbol{u}_{z}}{E_{\mathrm{loc}} A}
+  = \frac{(d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j}) \sigma_{\mathrm{b}}}{E}
+\end{equation}
+where $r_{\mathrm{cov}}^{i}$ and $r_{\mathrm{cov}}^{j}$ are the
+covalent radii of the outer-most atoms, the characteristic length of
+the dipole extension in z-direction, and $d_{\mathrm{max}}$ is the
+z-distance between the nuclei of such atoms.  The field $E$
+counterbalances the field from the surface bound charges and equals
+$E = \sigma_{\mathrm{b}}/\varepsilon_{0}$. Therefore we have:
+\begin{equation}
+  \label{eq:alpha-classic-2}
+  \alpha_{\mathrm{2D}}^{\perp} = (d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j})\varepsilon_{0}
+                = \delta_{\mathrm{cov}} \varepsilon_{0}
+\end{equation}
+which explains the linear relation seen in main text Figure
+\ref{main-fig-3}d. We can see that such simple model nicely captures
+the thickness feature of $\alpha_{\mathrm{2D}}^{\perp}$, and
+reproduces the right coefficient between $\delta_{\mathrm{cov}}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$.
 
@@
 \section{Validation on the C2DB 2D materials database}
+\label{sec:gpaw}
 \subsection{Validation of the universal description of 2D polarizabilities}
@@
 
-%%%%%%pasted in 12/05/2018
-
-\subsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
-  from fundamental electrostatics}
-\label{sssec:theory-3}
-
-The dependency of $\alpha_{\mathrm{2D}}^{\perp}$ on the thickness
-$\delta$ of a 2D material, can also be regarded using fundamental
-electrostatic model. Consider the smallest repeating unit of the 2D
-material with xy-plane area $A$, under small perturbation field $E$
-along the z-direction.  Note that the surface bound charge
-$\sigma_{\mathrm{b}}=n e /A$, where $n$ is the number of unit charges
-contributes to the bound charges, comes only from the dipoles of the
-outer-most atoms, since the induced charges from inner atoms are
-cancel out (see Figure \ref{fig:classic-model}).
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.7\linewidth]{img/SI-classic.pdf}
-  \caption{Fundamental electrostatic model for the
-    thickness-dependency of $\alpha_{\mathrm{2D}}^{\perp}$, using 2H-MoS2 as an
-    example. Left: induced dipoles from individual atoms along the
-    z-direction. The positive and negative induced charges from inner
-    atoms cancel out. Right: simplified model for the thickness
-    dependency of $\alpha_{\mathrm{2D}}^{\perp}$, where the surface dipole density
-    $\boldsymbol{\mu}$ comes only from the outer-most atoms.}
-  \label{fig:classic-model}
-\end{figure}
-From the definition of
-$\alpha_{\mathrm{2D}}^{\perp}$, we have:
-\begin{equation}
-  \label{eq:alpha-classic}
-  \alpha_{\mathrm{2D}}^{\perp} = \frac{\boldsymbol{u}_{z}}{E_{\mathrm{loc}} A}
-  = \frac{(d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j}) \sigma_{\mathrm{b}}}{E}
-\end{equation}
-where $r_{\mathrm{cov}}^{i}$ and $r_{\mathrm{cov}}^{j}$ are the
-covalent radii of the outer-most atoms, the characteristic length of
-the dipole extension in z-direction, and $d_{\mathrm{max}}$ is the
-z-distance between the nuclei of such atoms.  The field $E$
-counterbalances the field from the surface bound charges and equals
-$E = \sigma_{\mathrm{b}}/\varepsilon_{0}$. Therefore we have:
-\begin{equation}
-  \label{eq:alpha-classic-2}
-  \alpha_{\mathrm{2D}}^{\perp} = (d_{\mathrm{max}} + r_{\mathrm{cov}}^{i} + r_{\mathrm{cov}}^{j})\varepsilon_{0}
-                = \delta_{\mathrm{cov}} \varepsilon_{0}
-\end{equation}
-which explains the linear relation seen in main text Figure
-\ref{main-fig-3}d. We can see that such simple model nicely captures
-the thickness feature of $\alpha_{\mathrm{2D}}^{\perp}$, and
-reproduces the right coefficient between $\delta_{\mathrm{cov}}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$. Finally, the schematic drawing of the
-polarizability ellipsoid for a 2D material, is drawn in Figure
-\ref{fig:ellipsoid}.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.6\linewidth]{img/SI-ellipsoid.pdf}
-  \caption{Polarizability ellipsoid of a 2D material, the long axis
-    equals $\alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ and the short axis
-    equals  $\alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$}
-  \label{fig:ellipsoid}
-\end{figure}
+%%%%%% pasted in 12/05/2018
+\section{More discussion about the relation between 2D and 3D properties}
+\label{sec:2D-3D}
 
@@
 
-\subsection{Comparing dielectric anisotropy}
-\label{ssec:aniso}
-\subsubsection{Choice of materials}
-\label{sssec:aniso-1}
+\subsection{The relation between 2D and 3D physical quantities}
+As schematically shown in Figure \ref{fig-2D-3D}, the physical
+quantities related to the dielectric properties can be categorized
+into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
+(iii) valid both 2D and 3D.  $\alpha_{\mathrm{2D}}$ and $\varepsilon$ are the
+starting point for the strictly 2D and 3D quantities, which require
+distinct definitions when dimensionality changes. Such quantities
+include (but not limited to):
+\begin{enumerate}
+\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
+  charge, polarization, electronic states, etc.
+
+\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
+  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (see
+  Section \ref{ssec:omega-p} and Figure \ref{fig:plasma}).
+
+\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
+  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
+\end{enumerate}
+These quantities have distinct units in both dimensions, and related
+by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
+plasma frequency), which requires prudent interpretation of
+theoretical and experimental results. For instance, the experimentally
+observed ``dielectric constant'' of monolayer 2D materials
+\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
+without considering the effect of mix ted medium. Instead, the 2D slab
+polarizability, either transformed from the vacuum-containing
+macroscopic dielectric constant, or predicted from the bandgap and
+geometry as proposed here, will be a better descriptor for the true 2D
+dielectric nature. On the other hand, there are also
+dimension-independent quantities that valid for both 2D and 3D
+systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
+energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
+as well as the Hamaker constant of van der Waals interaction
+$A_{\mathrm{H}}$. All these quantities are well-defined and can be
+measured in both dimensions, while their relation with the dielectric
+property varies with dimensionality. The well-known examples are the
+different Wannier-Mott laws for exciton binding energy
+\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
+proposed here, and the distinct power laws for van der Waals
+interactions \cite{Gobre_2013}. To get a accuracy description of
+dielectric-related properties of the 2D materials and their
+heterostructures, one has to distinguish between the 2D and 3D
+properties, and choose a suitable relation with the
+dimension-dependent and dimension-independent quantities.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
+\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
+  both 2D (red circle) and 3D (cyan circle) systems. The
+  dimension-dependent quantities can be related with $\alpha_{\mathrm{2D}}$ and
+  $\varepsilon$, respectively. The intersection between the circles
+  present the quantities are well-defined in both dimensions, but may have a
+  different scaling relation with others quantities.}
+\end{figure}
+
+\section{More discussions about the dielectric anisotropy}
+\label{sec:aniso}
+\subsection{The 2D screening length}
+\label{ssec:2D-screening}
+Here we show a schematic drawing of the polarizability ellipsoid for a
+2D material in Figure \ref{fig:ellipsoid}. As can be seen the
+polarizability ellipsoid is ultraflat, with
+$r_{0}^{\parallel} \gg r_{0}^{\perp}$, which is the origin of the high
+dielectric anisotropy of 2D materials.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\linewidth]{img/SI-ellipsoid.pdf}
+  \caption{Polarizability ellipsoid of a 2D material, the long axis
+    equals $\alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ and the short axis
+    equals  $\alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$}
+  \label{fig:ellipsoid}
+\end{figure}
+
+\subsection{Choice of materials for main text Figure \ref{main-fig:aniso}}
+\label{ssec:aniso-materials}
 The dielectric anisotropy $\eta$ proposed in the main text is also
@@
 
-\subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
+\subsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
 \label{sssec:aniso-2}
@@
 
-\subsection{The relation between 2D and 3D physical quantities}
-As schematically shown in Figure \ref{fig-2D-3D}, the physical
-quantities related to the dielectric properties can be categorized
-into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
-(iii) valid both 2D and 3D.  $\alpha_{\mathrm{2D}}$ and $\varepsilon$ are the
-starting point for the strictly 2D and 3D quantities, which require
-distinct definitions when dimensionality changes. Such quantities
-include (but not limited to):
-\begin{enumerate}
-\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
-  charge, polarization, electronic states, etc.
-
-\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
-  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (see
-  Section \ref{ssec:omega-p} and Figure \ref{fig:plasma}).
-
-\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
-  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
-\end{enumerate}
-These quantities have distinct units in both dimensions, and related
-by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
-plasma frequency), which requires prudent interpretation of
-theoretical and experimental results. For instance, the experimentally
-observed ``dielectric constant'' of monolayer 2D materials
-\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
-without considering the effect of mix ted medium. Instead, the 2D slab
-polarizability, either transformed from the vacuum-containing
-macroscopic dielectric constant, or predicted from the bandgap and
-geometry as proposed here, will be a better descriptor for the true 2D
-dielectric nature. On the other hand, there are also
-dimension-independent quantities that valid for both 2D and 3D
-systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
-energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
-as well as the Hamaker constant of van der Waals interaction
-$A_{\mathrm{H}}$. All these quantities are well-defined and can be
-measured in both dimensions, while their relation with the dielectric
-property varies with dimensionality. The well-known examples are the
-different Wannier-Mott laws for exciton binding energy
-\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
-proposed here, and the distinct power laws for van der Waals
-interactions \cite{Gobre_2013}. To get a accuracy description of
-dielectric-related properties of the 2D materials and their
-heterostructures, one has to distinguish between the 2D and 3D
-properties, and choose a suitable relation with the
-dimension-dependent and dimension-independent quantities.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
-\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
-  both 2D (red circle) and 3D (cyan circle) systems. The
-  dimension-dependent quantities can be related with $\alpha_{\mathrm{2D}}$ and
-  $\varepsilon$, respectively. The intersection between the circles
-  present the quantities are well-defined in both dimensions, but may have a
-  different scaling relation with others quantities.}
-\end{figure}
-
 %%%%%%pasted!

### 2018-12-17 paper.tex
Correct x-references in manuscript and SI

@@
 finite electric fields
-($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
+($|\boldsymbol{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
 $\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a} and
@@
 formalism\cite{kittel_2005_introduction} (see Supplementary
-Section \ref{SI-sssec:theory-1} and  \ref{SI-ssec:theory-2} for details), 
+Section \ref{SI-sec:theory-1} for details), 
 we can show that
@@
 where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
-the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf
-  a}), and $C^{\parallel} = \frac{Ne^2}{2 \pi}$, where $N$ corresponds to
-the degeneracy of the bands associated with $E_{\mathrm{g}}$, and
-$C^{\perp} = {\varepsilon_{0}}$.  \todo[inline]{The previous
-  expressions for the coefficients are wrong. Please see the version
-  in SI.} Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
-\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
-the polarizability and the electronic and structural properties for
-any 2D material in a new framework.  We can show that these equations
-are valid for the current library of known layered materials involving
-different lattice symmetry, element composition, optical and
-electronic properties.
+the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf a}), and
+$C^{\parallel} = \frac{Ne^2}{2 \pi}$ \cite{Jiang_2017_Eg_Eb}, where
+$N$ corresponds to the degeneracy of the bands associated with
+$E_{\mathrm{g}}$, and $C^{\perp} = {\varepsilon_{0}}$.
+\todo[inline]{The previous expressions for the coefficients are
+  wrong. Please see the version in SI}
+Despite of the simplicity of
+Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, they generalize
+a direct relationship between the polarizability and the electronic
+and structural properties for any 2D material in a new framework.  We
+can show that these equations are valid for the current library of
+known layered materials involving different lattice symmetry, element
+composition, optical and electronic properties.
 %
@@
 % 
-We then examine Eqs. \ref{eq:2D-Moss-para}
-and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
-first-principle calculations. 
-Figure \ref{fig-3}{\bf c} shows
+We then examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
+using the polarizabilities by first-principle calculations.  Figure
+\ref{fig-3}{\bf c} shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
 \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
-materials investigated (circle dots).  
-A linear regression coefficient of $R^{2}=0.84$ indicates a 
-strong correlation between bandgaps and polarizabilities as predicted in 
-Eq. \ref{eq:2D-Moss-para}. 
-We also discover that
-the linearity between
+materials investigated (circle dots).  A linear regression coefficient
+of $R^{2}=0.84$ indicates a strong correlation between bandgaps and
+polarizabilities as predicted in Eq. \ref{eq:2D-Moss-para}.  We also
+discover that the linearity between
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
 $E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
-bandgap is calculated using the HSE06 hybrid functional\cite{Heyd_2005} compared
-with that from Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
-(see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
-Supplementary Figure \ref{fig:alpha-Eg-diff}) which suggests that higher levels 
-of theory are needed to predict bandgaps as it is normally the case.   
-We also show
-that the proposed Eq. \ref{eq:2D-Moss-para}
-behaves equivalently well when using the
-experimentally accessible optical bandgap of 2D materials (details see
-Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
-\ref{fig:opt}).
+bandgap is calculated using the HSE06 hybrid
+functional\cite{Heyd_2005} compared with that from
+Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
+(see Supplementary Section \ref{SI-sec:pol-2D-Eg} and Supplementary
+Figure \ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels
+of theory are needed to predict bandgaps.  We also show that the
+proposed Eq. \ref{eq:2D-Moss-para} behaves equivalently well when
+using the experimentally accessible optical bandgap of 2D materials (
+Supplementary Figure \ref{SI-fig:opt}).
 
@@
 is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section \ref{SI-sssec:theory-3}). Indeed, the
-universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
-Figure \ref{fig-3}{\bf d} indicates that the quantity
+material (see Supplementary Section
+\ref{SI-ssec:theory-1-perp-fundamental}). Indeed, the universal
+scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
+\ref{fig-3}{\bf d} indicates that the quantity
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
@@
 To rule out the possibility that our conclusion are limited by the
-number of materials used at HSE06, we further validate
+number of materials used at HSE06 level, we further validate
 Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
-database\cite{Haastrup_2018}, from which we extracted the dielectric
+database \cite{Haastrup_2018}, from which we extracted the dielectric
 properties of over 230 compounds calculated at the PBE level, and
@@
 molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
-Figure \ref{fig:ellipsoid}). The polarizability ellipsoid for a 2D
+Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
 material is in general ultra flat, with
@@
 %
-These approximations assume that the strong interactions 
-occur in-plane and the interlayer stacking is not a critical factor.
-\todo{??}
-The dielectric constant $\varepsilon$ although not well-defined for
-a monolayer 2D material becomes applicable when the 2D layers are
-put together. 
+Here we neglect the effect of the stacking order of the layers.  The
+dielectric constant $\varepsilon$ although not well-defined for a
+monolayer 2D material becomes applicable when the 2D layers are put
+together.
 %
@@
 \eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
-index of corresponding 2D layer (see additional details in Supplementary Section
-\ref{SI-sssec:aniso-2}), which is the basis for the separation of bulk
-and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For
-comparison, we also superimpose the dielectric anisotropy indices
-$\eta$ of common semiconducting materials in other dimensions 
-(Supplementary Section \ref{SI-sssec:aniso-1}) on the phase diagram in Figure
-\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
-semiconductors show isotropic dielectric properties, scattered on the
-line $\eta=1$. On the other hand, reduced dimensionality increases the
-dielectric anisotropy of materials such as planar organic
-semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
-linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
-most of these materials also scatter along the boundary line
-separating the bulk and 2D regimes, indicating the criteria
-distinguishing 2D (more anisotropic) and bulk layered materials (more
-isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
-to other dimensions. From the phase diagram, we can see that 2D and
-bulk layered materials (also including 2D van der Waals
-heterostructure (vdWH) \cite{Novoselov_2016}), provides more
-flexibility in controlling the dielectric and electronic properties,
-compared with semiconductors in other dimensions.
+index of corresponding 2D layer (see additional details in
+Supplementary Section \ref{SI-sec:aniso}), which is the basis for the
+separation of bulk and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase
+diagram.  For comparison, we also superimpose the dielectric
+anisotropy indices $\eta$ of common semiconducting materials in other
+dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
+the phase diagram in Figure \ref{fig:aniso}. Bulk covalent (3D,
+e.g. Si, GaN) and 0D (fullerenes) semiconductors show isotropic
+dielectric properties, scattered on the line $\eta=1$. On the other
+hand, reduced dimensionality increases the dielectric anisotropy of
+materials such as planar organic semiconductor (OSc, 1D-2D,
+e.g. CuPc), carbon nanotube (CNT, 1D), linear OSc (0D-1D,
+e.g. polyacene and polyacetylene). Interestingly, most of these
+materials also scatter along the boundary line separating the bulk and
+2D regimes, indicating the criteria distinguishing 2D (more
+anisotropic) and bulk layered materials (more isotropic) from the
+$\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
+dimensions. From the phase diagram, we can see that 2D and bulk
+layered materials (also including 2D van der Waals heterostructure
+(vdWH) \cite{Novoselov_2016}), provides more flexibility in
+controlling the dielectric and electronic properties, compared with
+semiconductors in other dimensions.
 
@@
 \centering
-\includegraphics[width=1.04\linewidth]{img/fig4.pdf}
+\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties
@@
   \centering
-  \includegraphics[width=1.05\linewidth]{img/fig5.pdf}
+  \includegraphics[width=0.9\linewidth]{img/fig5.pdf}
   \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as

### 2018-12-17 SI.tex
More minor changes to SI and manu

@@
 \ref{main-eq:alpha-perp-def}, yielding lattice-independent
-polarizabilities throughout the frequency domain.
-
-\begin{figure}[H]
+polarizabilities throughout the frequency domain. Note when extracting
+the frequency-dependent 2D polarizabilities from
+Eqs. \ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def},
+the peak position from $\varepsilon_{\mathrm{SL}}$ is preserved. This
+is explained by the fact that the local extrema from spectra of
+$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
+$\alpha_{\mathrm{2D}}$, since when
+$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
+we have
+\begin{subequations}
+\begin{eqnarray}
+  \label{eq:extrema-para}
+  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
+  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
+  \label{eq:extrema-perp}
+  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
+  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
+\end{eqnarray}
+\end{subequations}
+which indicates that the peak position is perserved when transforming
+$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
+
+We note that the result change slightly when G$_{0}$W$_{0}$ method
+is used. As shown in Figures \ref{fig:GW-omega-in} and
+\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
+functions change with $L$, but also the peak positions. As a result
+the obtained polarizabilities also show $L$-dependent peak shift. This
+can be explained by the long-range nature of Coulomb interactions. In
+fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
+\begin{equation}
+  \label{eq:GW-formula}
+  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
+\end{equation}
+where $G$ is the non-interacting Green function, and $\nu$ is the
+Coulomb interaction. Since the dielectric constant $\varepsilon$
+changes with $L$, the self energy as well quasi-particle energies of
+the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
+higher peak energy of the dielectric spectrum when $L$ increases. Such
+peculiar $L$-dependency can be minimized when adding electron-hole
+interaction through the Bethe-Salpethe equation (BSE), as shown in
+Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
+polarizabilities again becomes lattice-independent due to the
+localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.
+
+Combining the accuray of bandgap estimation, reproducible results of
+frequency-dependent dielectric properties and calculation efforts, the
+choice of HSE06 hybrid functional seems used in the main text provides
+best tradeoff between all aspects.
+
+\begin{figure}[htbp]
   \centering
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
@@
 
-We note that the result may change slightly when G$_{0}$W$_{0}$ method
-is used. As shown in Figures \ref{fig:GW-omega-in} and
-\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
-functions change with $L$, but also the peak positions. As a result
-the obtained polarizabilities also show $L$-dependent peak shift. This
-can be explained by the long-range nature of Coulomb interactions. In
-fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
-\begin{equation}
-  \label{eq:GW-formula}
-  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
-\end{equation}
-where $G$ is the non-interacting Green function, and $\nu$ is the
-Coulomb interaction. Since the dielectric constant $\varepsilon$
-changes with $L$, the self energy as well quasi-particle energies of
-the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
-higher peak energy of the dielectric spectrum when $L$ increases. Such
-peculiar $L$-dependency can be minimized when adding electron-hole
-interaction through the Bethe-Salpethe equation (BSE), as shown in
-Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
-polarizabilities again becomes lattice-independent due to the
-localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.
-
-Combining the accuray of bandgap estimation, reproducible results of
-frequency-dependent dielectric properties and calculation efforts, the
-choice of HSE06 hybrid functional seems used in the main text provides
-best tradeoff between all aspects.
-
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
@@
 when $\eta_{\mathrm{2D}}$ is much smaller than 1. Therefore the
-separation between the 2D and 3D regimes in the Figure
+separation between the 2D and 3D regimes in  main text Figure
 \ref{main-fig:aniso} is explained.
@@
 \label{sec:raw}
-\todo[inline]{I think showing the $\alpha$ values is enough since
-  whoever interested in calculating the $r_{0}$ values can simply
-  multiply them by $2 \pi$. }
+Table S2 shows the parameters and results from the
+first principles calculations for the 2D materials studied. The 2D
+screening lengthes $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ can be
+obtained by multiplying $2 \pi$ to the columns
+$\alpha_{\mathrm{2D}}^{\parallel}/(4\pi \varepsilon_{0})$ and
+$\alpha_{\mathrm{2D}}^{\perp}/(4\pi \varepsilon_{0})$, respectively.
+
 \input{raw_data}

### 2018-12-17 paper.tex
More minor changes to SI and manu

@@
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
-    dielectric nature of 2D
-    materials}. \textbf{a}. The structures of the 2D materials investigated in this study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
-  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
-  materials studied.  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
+    dielectric nature of 2D materials}. \textbf{a}. The structures of
+  the 2D materials investigated in this
+  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
+  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
+  (blue dots) for all the 2D materials studied.
+  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
   increasing $E_{\mathrm{g}}$, while no apparent relation between
   $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
-  observed. \textbf{c}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
-  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
+  observed. \textbf{c}.
+  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
+  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
   correlation between each other. The energy range of visible light is
-  shown in the
-  background. \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
-  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
-  schematically shown in the inset), showing a perfect linear relation
-  with slope very close to $1/4\pi$. The universal scaling relation is
-  also revealed using the C2DB database (squares), as superimposed on \textbf{c}
-  and \textbf{d}.}
+  shown in the background. \textbf{d}.
+  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
+  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
+  in the inset), showing a perfect linear relation with slope very
+  close to $1/4\pi$ (i.e.
+  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
+  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
+  revealed using the data from Ref. \citenum{Haastrup_2018} (squares),
+  as superimposed on \textbf{c} and \textbf{d}.}
 \end{figure}

### 2019-01-02 src/post_processing/compile_data.py
Fix error while compiling data for ABX3

@@ -101,11 +101,13 @@ for row in reader:
         e_xy = numpy.sqrt(ex * ey)
         ax = (e_xy - 1) / (4 * pi) * L
         az = (1 - 1/ez) * L / (4 * pi)
-        mol = list(db.select(formula=name, prototype=proto))[0]
+        
         if proto == "ABX3":     # perovskite?
             delta = 14.24
             n_2D = None
+            mol = None
         else:
+            mol = list(db.select(formula=name, prototype=proto))[0]
             delta, n_2D = get_thick(mol)
         # 3D
         try:

### 2019-01-04 paper.tex
Implement changes elton 20181224

@@
 
-The dielectric constant $\varepsilon$ (also known as the relative
-permittivity) plays a crucial role in bridging various fundamental
-material properties, such as bandgaps
-\cite{Moss_1950_relation,Moss_1985_n_Eg}, optical absorption
-\cite{kittel_2005_introduction}, and conductivities
-\cite{Dressel_2001_electrodynamics}. $\varepsilon$ characterizes the
-ability to screen an electric field $\boldsymbol{E}$ which classifies
-metals, semiconductors and insulators.  \todo[inline]{I shortened the
-  sentences. However, can we really "classify" the material only by
-  $\varepsilon$? For instance HfO2 has large $\varepsilon$ but also
-  large bandgap}
-% Such definitions determine a broad range of
-% condensed matter physics, as well as in related fields in chemistry
-% and materials science.
-The ability to compute and measure
-$\varepsilon$ in bulk materials is well established via different
-theoretical and experimental techniques of distinct flavors where the
-probe of the dielectric properties is made through an external
-electric field.
+The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
+plays a crucial role in bridging various fundamental material
+properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
+optical absorption\cite{kittel_2005_introduction} and 
+conductivities\cite{Dressel_2001_electrodynamics}   
+with elemental interactions, e.g. electron-electron. 
+The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
+where is common to classify a material accordingly to its ability to screen an 
+electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
+condensed matter physics, as well as in related fields in chemistry and materials science. 
+The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
+theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
+is made through an external electric field. 
 %
@@
 electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
-%
 %
@@
 have generated long-standing debates whether the dielectric constant 
-may represent their dielectric features or only an 
+may represent their dielectric features or it can be used only as an 
 additional parameter from the bulk-counterparts.
+
 %%
@@
 $\boldsymbol{P}$ comes from the displacement of electron cloud under
-external electric field. For the majority of 2D nonmetals, the
+external electric field. For the majority of the 2D nanosheets, the
 off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
-negligible \todo[inline]{why only nonmetals?  Could you cite one
-  reference?}.  Considering that the 2D material is placed in vacuum
+negligible.  Considering that the 2D material is placed in vacuum
 ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
-components, namely the in-plane
+components of $\kappa$, namely the in-plane
 ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
@@
 The absence of bonding perpendicular to the plane confines the induced
-dipoles along the \textit{z}-direction as the charge density
-difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$, at zero and
-finite electric fields
-($|\boldsymbol{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
-$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a} and
-Supplementary Figure \ref{SI-fig:rho-profile}). When $L$ is large
+dipoles along the \textit{z}-direction in a range of 
+$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\bf a} and
+Supplementary Figure \ref{SI-fig:rho-profile}). 
+%
+%
+When $L$ is large
 enough, the induced dipoles $\boldsymbol{u}$ from the periodic images
@@
 depends only locally on the atomic charge density at the layer.
-However, we can see from Eqs. \ref{eq:def-eps-1} that both
+However, we can see from Eq. \ref{eq:def-eps-1} that both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
-the cell $\Omega$.  Therefore, any calculation performed using such
+the cell $\Omega$. In the case of bulk materials such physical dependence 
+is well described given the periodicity of the 3D crystal throughout the space.  
+%
+%since this volume is used to represent the crystal 
+%periodically throughout the space.  
+%
+%
+In the case of 2D materials, however, such repetition is artificial along the direction 
+perpendicular to the plane. Despite of the simplicity of this argument,  
+any calculation performed using such
 definition will intrinsically depend on the magnitude of $L$ as an
@@
 theory (DFT) using hybrid functionals (see {\it Theoretical Methods} for details)
-as a function of $L$ for P$\bar{6}$m2 transitional metal
+as a function of $L$ for P$\bar{6}$m2 transition metal
 dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
 (top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c},
-respectively).  Despite of the magnitudes of $L$ both components of
-the dielectric constant change systematically without a clear
-convergence.
+respectively). Both components of the dielectric constant 
+change systematically with $L$ without a clear convergence. 
 %
 Simulations performed at higher levels of theory using many-body
-techniques, G$_{\rm 0}$W$_{0}$, and also taking into account
-electron-hole excitations at the level of the Bethe-Salpeter equation
-(BSE) for the frequency-dependent
-$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
-results(details see Supplementary Section \ref{SI-ssec:gw}).
+techniques, G$_{\rm 0}$W$_{0}$, invariably give alike
+results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}). 
+We have also undertaken similar analysis into the frequency regime 
+for $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where despite of the 
+method utilized from PBE, G$_{\rm 0}$W$_{0}$ up 
+to taking into account electron-hole excitations at the level of the 
+Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$--BSE) the dependence on $L$
+is still present (see Supplementary Section \ref{SI-ssec:gw} for a systematic study). 
+These results indicate that quantities that depend 
+on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, 
+the optical absorption, suffer the
+same deficiencies.  
+%
 % Moreover, due to the long range Coulomb
@@
 results as the thickness is normally chosen by the interlayer spacing
-of the respective bulk materials (details see Supplementary Section
+of the respective bulk materials (see Supplementary Section
 \ref{SI-sec:2D-3D-rescale}).
@@
 $\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
-Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
+Eq.~\ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
 $\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
@@
 % interlayer interactions.
-\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true.
+%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true.
 I think it is better not to explicitly mention this.}
@@
 present in the calculations.  
-More discussions about the choice of the 2D polarizability
-and comparison with other methods can be found in Supplementary Section \ref{SI-sec:2D-3D-rescale}.
+More discussions about the choice of the 2D polarizability,
+comparison with other methods, simulations at the frequency-dependent domain
+ can be found in Supplementary Section \ref{SI-ssec:gw}.
 
@@
 $E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{SI-sec:pol-2D-Eg}). It is worth mentioning that materials with
-elements having large polarizabilities, such as Hf and Zr in
-1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
-for the layers with slightly variations between 1T and 2H phases. The
-former normally shows larger values of
-$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
-\todo[inline]{sorry but I don't quite get the idea of this
-  sentence. In fact HfO2 and ZrO2 have quite low in-plane
-  polarizabilities compared with even TiO2. Shall we just remove these
-  sentenses? }
+\ref{SI-sec:pol-2D-Eg}). 
+%It is worth mentioning that materials with
+%elements having large polarizabilities, such as Hf and Zr in
+%1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
+%for the layers with slightly variations between 1T and 2H phases. The
+%former normally shows larger values of
+%$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
+%\todo[inline]{sorry but I don't quite get the idea of this
+%  sentence. In fact HfO2 and ZrO2 have quite low in-plane
+%  polarizabilities compared with even TiO2. Shall we just remove these
+%  sentenses? }
 %
@@
 Figure \ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels
-of theory are needed to predict bandgaps.  We also show that the
-proposed Eq. \ref{eq:2D-Moss-para} behaves equivalently well when
-using the experimentally accessible optical bandgap of 2D materials (
-Supplementary Figure \ref{SI-fig:opt}).
+of theory are needed to predict bandgaps. See Supplementary Section \ref{SI-sec:gpaw}
+for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
+using different bandgaps, databases, and levels of calculation.
 
@@
 \end{equation}
-where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
-is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
+where $i$, $j$ are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
+is the covalent radius of atom $i$ (Figure \ref{fig-3}{\bf d} inset). 
 %
@@
 \ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
-This results indicate that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
+This result indicates that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
 physical meaning through the geometry of the layer.  Similar to the
-molecular polarizability which characterizes the volume of electron
+molecular polarizability which characterizes the volume of the electron
 cloud of an isolated molecule \cite{Israelachvili_2011},
@@
 volume of the electron cloud per unit area (from its definition), and
-is naturally proportional to the electron cloud thickness of the 2D
-material (see Supplementary Section
-\ref{SI-ssec:theory-1-perp-fundamental}). Indeed, the universal
+is naturally proportional to the thickness of the 2D
+material. Supplementary Section
+\ref{SI-ssec:theory-1-perp-fundamental} shows an electrostatic model 
+of this behavior. Indeed, the universal
 scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
 \ref{fig-3}{\bf d} indicates that the quantity
-$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, measurable via
 electronic and optical approaches
@@
 with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
-(\textit{x}-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
+(\textit{x}-axis) as shown in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
 Both HSE06 and PBE datasets give almost identical results.  
@@
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
-predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
+predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
 regression slope of 1.01 and $R^2$ of 0.97. Conversely,
@@
 as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
-counterparts. Interestingly, the 2D materials (blue triangle) can be
-clearly distinguished from the bulk layered materials (orange square)
+counterparts. Interestingly, the 2D materials (blue triangles) can be
+clearly distinguished from the bulk layered materials (orange squares)
 with the boundary line determined to be
@@
 indicates a high dielectric anisotropy, which is responsible for the
-unique 2D optoelectronic properties, such as electrostatic
-transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
-binding energy
+unique 2D optoelectronic properties, such as the electrostatic
+transparency phenomena\cite{Liluhua_2014,Tian_2016,Li_2018} and the large exciton
+binding energies
 \cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
@@
 diagram.  For comparison, we also superimpose the dielectric
-anisotropy indices $\eta$ of common semiconducting materials in other
+anisotropy indices of common semiconducting materials in other
 dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
@@
 
-All results calculated for this paper were the result of \emph{ab
-  initio} simulations carried out using plane-wave Density Functional
-Theory (DFT) package VASP
-\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
-Augmented Wave (PAW) approach with Kresse's mainly GW Pseudopotentials
+Simulations were carried out using plane-wave density functional
+theory package VASP
+\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the projector
+augmented wave (PAW) approach with GW pseudopotentials
 \cite{Kresse_1999_pseudopotentials}. Band gaps were calculated using
 the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
-\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
+\cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
 included. The geometries were converged both in cell parameters and
 ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
-of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
+of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA~is
 used. A k-point grid of \(7\times7\times1\) was used to relax the
@@
 giving a plane wave kinetic energy cutoff of 30\% greater than the
-highest given in the pseudopotentials used in each material,
-guaranteeing that absolute energies were converged to a few meV and
-the stress tensor to within a few kBar.  Calculation of the
+highest given in the pseudopotentials used in each material. This 
+guarantees that absolute energies were converged to a few meV and
+the stress tensor to within 0.01 kBar.  Calculation of the
 macroscopic ion-clamped dielectric tensor were carried out with an
 18$\times$18$\times$1 k-grid and electric field strength of 0.001
-eV/\AA. The materials from Ref. \citenum{Haastrup_2018} for comparison
+eV/\AA. The materials from Ref.\citenum{Haastrup_2018} for comparison
 were choses with the GW bandgap larger than 0.05 eV. Bulk layered
@@
 18$\times$18$\times$6 k-grid with same parameter as for monolayer,
-while the dielectric properties of bulk counterparts of the C2DB
-database are calculated at PBE level with a k-point density of 10
-\AA$^{-1}$.
+while the dielectric properties of bulk counterparts of Ref.~\citenum{Haastrup_2018}
+are calculated at PBE level with a k-point density of 10~\AA$^{-1}$.
 
@@
 \centering
-\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
+\includegraphics[width=0.79\linewidth]{img/fig1.pdf}
 \caption{\label{fig-1} \textbf{2D polarizability as the true
@@
   and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
-  \ref{eq:alpha-perp-def}, respectively.}
+  \ref{eq:alpha-perp-def}, respectively. HSE06 functional is used in all plots.}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.70\linewidth]{img/fig2.pdf}
+\includegraphics[width=0.74\linewidth]{img/fig2.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
   $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
-  observed. \textbf{c}.
+  observed. HSE06 functional is used to obtain the data. \textbf{c}.
   $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
@@
   coupling. The comparisons in \textbf{b} and \textbf{c} are made
-  based on both HSE06 (circles) and PBE (squares) levels.}
+  based on both HSE06 (circles) and PBE (squares) functionals.}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/fig5.pdf}
+  \includegraphics[width=1.01\linewidth]{img/fig5.pdf}
   \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as

### 2019-01-04 SI.tex
Fix minor errors in the manuscript
Implement changes of SI from elton 20181224

@@
 
-\item Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant
-
-\item Supplementary Section \ref{sec:theory-1}: Polarizability-Based Theoretical Model
+\item Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from the 3D dielectric constant
+
+\item Supplementary Section \ref{sec:theory-1}: Polarizability-based theoretical model
 
@@
 
-\item Supplementary Section \ref{sec:gpaw}: Validation on the C2DB 2D materials database
+\item Supplementary Section \ref{sec:gpaw}: Validation of results using a larger 2D material database
 
@@
 In this section we provide more analysis on the dielectric properties
-of 2D materials, with focus on the dielectric properties calculated
-using many-body Green function method (G$_0$W$_0$) and the
-frequency-dependency of the superlattice dielectric functions and 2D
-polarizabilities.
+of 2D materials calculated using many-body Green function method 
+(G$_0$W$_0$), including electron-hole interactions at the level of the 
+Bethe-Salpeter equation (G$_0$W$_0$--BSE), and at the frequency-dependent regime.
 
@@
 Here we show in detail the
-$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
+$\Delta {\rho}=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
 the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}. The
-density $\rho$ is calculated as the average value in the
-\textit{xy}-plane, and the value is shown in Figure
-\ref{fig:rho-profile}. As can be seen the induced charges on the
-MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
+density $\Delta \rho$ is calculated via $\Delta \rho(z) = \frac{1}{S} \int_{S} \Delta \rho (x,y;z) dx dy $, 
+where $S$ is the surface of the unit cell perpendicular to the given direction, in this case $z$. 
+%
+As can be seen in Figure \ref{fig:rho-profile} the induced charges on the
+MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{} centered at the middle of the layer. This corresponds to about 6 \AA ~from each side. 
+When the
 SL size $L \gg$12 \AA{} as in the first principle calculations done in
 the main text, the induced dipoles from the periodic images do not
-interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
+interact, and thus give the converged values of $\alpha_{\mathrm{2D}}$.
 
@@
 Here we will show the results of dielectric properties calculated
-using higher level of many-body Green function method (G$_0$W$_{0}$)
-and with electron-hole interaction. We first compare the case of a
-layer of hBN within an superlattice with varying size with the
-dielectric properties calculated using PBE and G$_{0}$W$_{0}$ methods,
-as shown in Figure
-\ref{fig:GW-PBE-alpha}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$, shown in
-Figure \ref{fig:GW-PBE-alpha}a and \ref{fig:GW-PBE-alpha}b,
-respectively, do not converge with $L$, while the corresponding 2D
-polarizabilities in Figure \ref{fig:GW-PBE-alpha}c and
-\ref{fig:GW-PBE-alpha}d are almost $L$-independent. It is worthnoting
-that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than PBE method.
+using many-body Green function method (G$_0$W$_{0}$)
+and with electron-hole interactions at the level of the Bethe-Salpeter 
+equation (G$_0$W$_{0}$--BSE). We first compare the case of a
+monolayer of BN within a varying superlattice $L$ 
+calculated using PBE and G$_{0}$W$_{0}$ as shown in Figure \ref{fig:GW-PBE-alpha}. 
+%
+%
+Both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of $L$ 
+despite of the separation utilized in the simulations (Figure \ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}).
+However, corresponding 2D polarizabilities are almost $L$-independent (Figure \ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}).
+It is worth noting
+that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than in PBE functionals.
 \begin{figure}[htbp]
@@
  \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
- \caption{Variation of dielectric properties and
+ \caption{{\bf Variation of 
    $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
-   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.
-   \textbf{a}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ as function of
-   $L$. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as function of
-   $L$ corresponding to
-   \textbf{b}. \textbf{c}. $\varepsilon_{\mathrm{SL}}^{\perp}$ as
-   function of $L$.  \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}$ as
-   function of $L$. In all cases the values obtained using
+   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.}
+   \textbf{a}-{\bf b}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\parallel}$ as function of $L$, respectively.    
+  \textbf{c}-{\bf d}. $\varepsilon_{\mathrm{SL}}^{\perp}$ and 
+  $\alpha_{\mathrm{2D}}^{\perp}$ as
+   function of $L$. 
+   In all cases the values obtained using
    G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
@@
 
-We calculate the frequency-dependent dielectric properties of hBN with
-varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$
-with electron-hole interaction (G$_{0}$W$_{0}$+BSE). As shown in
-Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out}, the
-intensities of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
+We calculate the frequency-dependent dielectric properties of BN with
+varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
+Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show the
+magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
 $\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
-throughout the whole frequency range. The $L$-dependency can also be
+throughout the whole frequency range at PBE level. The $L$-dependency can also be
 removed using Eqs. \ref{main-eq:alpha-para-def} and
 \ref{main-eq:alpha-perp-def}, yielding lattice-independent
-polarizabilities throughout the frequency domain. Note when extracting
+polarizabilities throughout the frequency domain (Figure \ref{fig:PBE-omega-in}{\bf b}-{\bf d} and \ref{fig:PBE-omega-out}{\bf b}-{\bf d}). 
+%
+Note that when extracting
 the frequency-dependent 2D polarizabilities from
 Eqs. \ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def},
-the peak position from $\varepsilon_{\mathrm{SL}}$ is preserved. This
+the peak position in energy $\omega (eV)$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This
 is explained by the fact that the local extrema from spectra of
@@
 \end{subequations}
-which indicates that the peak position is perserved when transforming
+which indicates that no corrections in energy are present 
+when transforming
 $\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
+ \includegraphics[width=1.00\linewidth]{img/SI-PBE-omega-in_plane.pdf}
  \caption{Dependence of in-plane dielectric properties on $L$ for
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
+  \includegraphics[width=1.0\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
   \caption{Dependence of out-of-plane dielectric properties on $L$ for
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
+ \includegraphics[width=1.0\linewidth]{img/SI-GW-omega-in_plane.pdf}
  \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
+ \includegraphics[width=1.0\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
  \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
+ \includegraphics[width=1.0\linewidth]{img/SI-BSE-in_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into
    account electron-hole interactions at the level of the
-   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  The peak shift
+   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ + BSE).  The peak shift
    in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$. As a
@@
   \centering
- \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
+ \includegraphics[width=1.0\linewidth]{img/SI-BSE-out_of_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into
    account electron-hole interactions at the level of the
-   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  As a result
+   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ + BSE).  As a result
    the polarizabilities becomes almost independent of $L$, consistent
-   to results obtained by the PBE method.  }
+   to results obtained by the PBE method.}
   \label{fig:BSE-omega-out}
@@
 Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
-coincidence. Combining recent theoretical findings of the linear
+coincidental. Combining recent theoretical findings of the linear
 relation between exciton binding energy $E_{\mathrm{b}}$ and
@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
-to have a general Moss-like relation between
+to have a general relation between
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
@@
 an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
-in- and out-of-plane components, similar to the treatment of quantum
+in- and out-of-plane components ($\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$) 
+similar to the treatment of quantum
 wells (QW),\cite{davies_physics_1997} such that
-$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
 $\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
@@
 \end{equation}
-where $e$ is the unit charge, c, v are the conduction and valence
+where $e$ is the unit charge, $c$, $v$ are the conduction and valence
 bands, $E$ is the eigenenergy of individual bands, and $f$ is the
@@
 
-\subsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-para}}  %
+\subsection{Detailed derivations of Eq. \ref{main-eq:2D-Moss-para}}  %
 \label{ssec:theory-1-para}
 
-In this section we show how main text Eq. \ref{main-eq:alpha-para-def}
+In this section we show how Eq. \ref{main-eq:alpha-para-def}
 is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
@@
 plug it into Eq.
-\ref{eq:alpha_para_RPA} and integrate within the 2D Brillouin Zone from $|k|=0$ to $|k|= k_{\mathrm{BZ}}$, where $k_{\mathrm{BZ}}$ is the wavevector at the boundary of the 2D Brillouin Zone, we get:
+\ref{eq:alpha_para_RPA} and integrate within the 2D Brillouin zone from $|k|=0$ to $|k|= k_{\mathrm{BZ}}$, where $k_{\mathrm{BZ}}$ is the wavevector at the boundary of the 2D Brillouin Zone, we get:
 \begin{equation}
@@
 fact that $\frac{\hbar^{2} k^{2}_{\mathrm{BZ}}}{m^{*}} \gg E_{g}$, and
-we arrive at main text Eq. \ref{main-eq:2D-Moss-para}.
+we arrive at Eq. \ref{main-eq:2D-Moss-para}.
 
@@
 $(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
-\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) in main text
+\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) in
 Figure \ref{main-fig-3}\textbf{c}. The coefficient $C^{\parallel}$
@@
 
-\subsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-perp}}
+\subsection{Detailed derivation of Eq. \ref{main-eq:2D-Moss-perp}}
 \label{ssec:theory-1-perp}
 
-For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
+For Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
 wave functions as plane wave with form
@@
 a potential well of width $\delta$, which is the typical treatment for
-semiconductor QWs \cite{ihn_semiconductor_2009}. The allowed bound
+semiconductor QWs \cite{ihn_semiconductor_2009,Fowler_1984,Maize_2011}. 
+The allowed bound
 states inside the confined region generally have wave vector
@@
 the effective masses parallel and perpendicular to the 2D
-plane. Therefore the denominator of Eq. \ref{eq:alpha_perp_RPA} becomes independent of
+plane. Therefore, the denominator of Eq. \ref{eq:alpha_perp_RPA} becomes independent of
 $\mathbf{k}$, that
@@
 $<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
-is proportional to the confinement length $\delta$ which can be seen using
+is proportional to the confinement length $\delta$ which can be seen using the 
 particle-in-box solution\cite{davies_physics_1997}. In combination,
@@
 $\alpha_{\mathrm{2D}}^{\perp}$ is independent of the band gap.
-
-Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
-confinement length $\delta$, or equivalent the thickness of the 2D
-material. For simplicity we assume $\psi^{\parallel}$ is the solution
-of a particle confined inside an infinite potential well of width
-$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
-K, the only non-zero contribution for the transition between band
-$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
-vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
-$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
-\begin{equation}
-  \begin{aligned}
-    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
-    d^{2}\mathbf{k}_{\rho}
-    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
-      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
-      n_{\mathrm{v}}^{2}}\\
-    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
-      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
-        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
-        n_{\mathrm{v}}^{2}}
-  \end{aligned}
-\end{equation}
-Since the Fermi wave vector for band \textit{i} follows
-${\displaystyle
-  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
-{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
-    \delta^{2}}} = E_{\mathrm{F}}$, we have
-$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
-(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
-n_{\mathrm{v}}^{2}) {\displaystyle
-  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
-model, the energy levels for a sub-nm QW will be at the order of 10
-eV, which allows only few states inside the QW. Combine with the fact
-that the strongest transition mostly comes from the lowest bands
-\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
-be proportional to $\delta^{p}$, where the power index $p$ is 2. We
-note the different power law comes from the choice of the $V(z)$. The
-atomic polarizabilities of free particles inside a 1D infinite QW,
-finite QW or harmonic QW all show dependency with $\delta^{4}$, where
-$\delta$ is the length of confinement or effective harmonic length of
-the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
-the molecular polarizability divided by the area, such approach will
-always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
-accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
-model for the confinement in z-direction than simple square potential
-well, which may be explored further. Nevertheless the simple model
-presented here still captures the bandgap-independent and
-thickness-related feature of $\alpha_{\mathrm{2D}}^{\perp}$,
-supporting our findings in the main text. In the next section we will
+%
+%Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
+%confinement length $\delta$, or equivalently the thickness of the 2D
+%material. For simplicity we assume $\psi^{\parallel}$ is the solution
+%of a particle confined inside an infinite potential well of width
+%$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
+%K, the only non-zero contribution for the transition between band
+%$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
+%vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
+%$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
+%\begin{equation}
+%  \begin{aligned}
+%    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
+%    d^{2}\mathbf{k}_{\rho}
+%    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
+%      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
+%      n_{\mathrm{v}}^{2}}\\
+%    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
+%      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
+%        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
+%        n_{\mathrm{v}}^{2}}
+%  \end{aligned}
+%\end{equation}
+%Since the Fermi wave vector for band \textit{i} follows
+%${\displaystyle
+%  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
+%{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
+%    \delta^{2}}} = E_{\mathrm{F}}$, we have
+%$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
+%(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
+%n_{\mathrm{v}}^{2}) {\displaystyle
+%  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
+%model, the energy levels for a sub-nm QW will be at the order of 10
+%eV, which allows only few states inside the QW. Combine with the fact
+%that the strongest transition mostly comes from the lowest bands
+%\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
+%be proportional to $\delta^{p}$, where the power index $p$ is 2. We
+%note the different power law comes from the choice of the $V(z)$. The
+%atomic polarizabilities of free particles inside a 1D infinite QW,
+%finite QW or harmonic QW all show dependency with $\delta^{4}$, where
+%$\delta$ is the length of confinement or effective harmonic length of
+%the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
+%the molecular polarizability divided by the area, such approach will
+%always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
+%accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
+%model for the confinement in z-direction than simple square potential
+%well, which may be explored further. Nevertheless the simple model
+%presented here still captures the bandgap-independent and
+%thickness-related feature of $\alpha_{\mathrm{2D}}^{\perp}$,
+%supporting our findings in the main text. 
+In the next section we will
 provide a simple explanation for the $\alpha \propto \delta$ relation
@@
 
-\subsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
+\subsection{Explanation of Eq. \ref{main-eq:2D-Moss-perp}
   from fundamental electrostatics}
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{img/SI-classic.pdf}
+  \includegraphics[width=0.99\linewidth]{img/SI-classic.pdf}
   \caption{Fundamental electrostatic model for the
@@
 covalent radii of the outer-most atoms, the characteristic length of
-the dipole extension in z-direction, and $d_{\mathrm{max}}$ is the
+the dipole extension in z-direction, respectively, and $d_{\mathrm{max}}$ is the
 z-distance between the nuclei of such atoms.  The field $E$
@@
 \end{equation}
-which explains the linear relation seen in main text Figure
+which explains the linear relation seen in Figure
 \ref{main-fig-3}d. We can see that such simple model nicely captures
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
-  \caption{$E_{\mathrm{g}}$-dependence of \textbf{a} $\alpha_{\mathrm{2D}}^{\parallel}$ and
-    \textbf{b} $\alpha_{\mathrm{2D}}^{\perp}$ for the 2D materials investigated here.}
+  \includegraphics[width=0.99\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
+  \caption{$E_{\mathrm{g}}$-dependence of \textbf{a,} $\alpha_{\mathrm{2D}}^{\parallel}$ and
+    \textbf{b,} $\alpha_{\mathrm{2D}}^{\perp}$ for the 2D materials investigated here using HSE06.}
   \label{fig:SI-raw-HSE}
@@
 relation. We also examine the validity of such statement based on the
-analysis of the Computational 2D Materials Database (C2DB)
-\cite{Haastrup_2018}, as will be discussed in the following sections.
-
-\section{Validation on the C2DB 2D materials database}
+analysis of a different database\cite{Haastrup_2018} 
+as will be discussed in the following sections.
+
+\section{Using a different dataset of 2D materials}
 \label{sec:gpaw}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
-  \caption{Validation the linear relation between \textbf{a}
+  \includegraphics[width=1.05\linewidth]{img/SI-gpaw-data.pdf}
+  \caption{Validation of the linear relation between \textbf{a,}
     $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
-    and \textbf{b}
-    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB
-    2D material database, corresponding to Figure \ref{main-fig-3}c
-    and \ref{main-fig-3}d in main text.}
+    and \textbf{b,}
+    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ from 
+    Ref.\cite{Haastrup_2018} corresponding to Figure \ref{main-fig-3}{\bf c}
+    and \ref{main-fig-3}{\bf d}.}
   \label{fig:gpaw-alpha-relation}
@@
 
-Due to the high computation complexity of dielectric response
-calculations on the HSE level, our 2D material database is limited to
-about 50 types of materials. It is desirable to validate our proposed
+Due to time-consuming simulations and significant increment in 
+memory overload, high-accurate calculations at hybrid HSE06 level is limited 
+to about 56 compounds. 
+It is desirable to validate our proposed
 relations on an even larger scale database. We select over 230
-semiconducting 2D materials from the C2DB database with a GW bandgap
+semiconducting 2D materials from Ref.\cite{Haastrup_2018} 
+with a GW bandgap
 larger than 0.05 eV and extracted the 2D polarizabilities calculated
@@
 as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
-correlation is observed in both cases, with the $R^{2}$ coefficient
-larger than 0.9, indicating the existence of the universal description
+correlation is observed in both cases with the $R^{2}$ coefficient
+larger than 0.9 which indicates the existence of a universal description 
 of 2D dielectric nature through the proposed relations with the 2D
-polarizabilities. We note that the slope of linear regression is
-slightly different from the our proposed relation from the dielectric
-response on HSE06 level, due to the fact that the macroscopic
-dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated on the PBE
-level is about slightly difference. Despite the minor deviation of the
-slope of linear regression, the analysis on the C2DB database supports
-our understanding of the universal dielectric nature of 2D materials.
+polarizabilities. We note that the slope of the linear regression is
+slightly different from the one proposed from the dielectric
+response at the HSE06 level.
 
@@
 regression of $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation. Figure
-\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha_{\mathrm{2D}}^{\parallel}$ from the
-C2DB database as a function of minimal and direct bandgap calculated
+\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha_{\mathrm{2D}}^{\parallel}$ from 
+Ref.\cite{Haastrup_2018} as a function of minimal and direct bandgap calculated
 on PBE, HSE06 and GW levels. We observe,
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
+  \includegraphics[width=1.05\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
   \caption{$\alpha_{\mathrm{2D}}^{\parallel}$ as function of minimal and direct
     $E_{\mathrm{g}}$ calculated on different theoretical levels:
-    \textbf{a} PBE, \textbf{b} HSE and \textbf{c} GW of the C2DB
-    database.}
+    \textbf{a,} PBE, \textbf{b,} HSE and \textbf{c,} GW of Ref.\cite{Haastrup_2018}.}
   \label{fig:SI-gpaw-alpha-Eg-all}
@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{\mathrm{opt}}$
-from the C2DB database, with
+from Ref.\cite{Haastrup_2018} with
 $E_{\mathrm{g}}^{\mathrm{opt}}=E_{\mathrm{g}}^{\mathrm{dir,QP}}-E_{\mathrm{b}}^{\mathrm{BSE}}$,
 where $E_{\mathrm{g}}^{\mathrm{dir,QP}}$ is the direct quasi-particle
-bandgap calculated using G0W0 method and
+bandgap calculated using G$_0$W$_0$ method and
 $E_{\mathrm{b}}^{\mathrm{BSE}}$ is the exciton binding energy
@@
 between $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
-$E_{\mathrm{g}}^{\mathrm{opt}}$ is not coincidence: in fact,
+$E_{\mathrm{g}}^{\mathrm{opt}}$ is not coincidental: in fact,
 theoretical analysis shows that the binding energy $E_{\mathrm{b}}$ is
@@
   \centering
-  \includegraphics[width=0.55\linewidth]{img/SI-alphax-Eg-opt.pdf}
+  \includegraphics[width=0.70\linewidth]{img/SI-alphax-Eg-opt.pdf}
   \caption{$(4\pi\varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-    $E_{\mathrm{g}}^{\mathrm{opt}}$ from the C2DB database.}
+    $E_{\mathrm{g}}^{\mathrm{opt}}$ from Ref.\cite{Haastrup_2018}.}
   \label{fig:opt}
@@
 
-The relatively large size of the C2DB 2D materials database allows us
+The relatively large size of Ref.\cite{Haastrup_2018} database allows us
 to examine the relation between 2D polarizabilities and other physical
@@
   \centering
-  \includegraphics[width=0.75\linewidth]{img/SI-gpaw-alpha-emass.pdf}
+  \includegraphics[width=0.99\linewidth]{img/SI-gpaw-alpha-emass.pdf}
   \caption{Relation between 2D polarizabilities and the effective
-    carrier mass from the C2DB 2D material
-    database. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of the
+    carrier mass from Ref.\cite{Haastrup_2018}. 
+    \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of the
     electron mass $m_{e}^{*}$.  \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{img/SI-quantum-capacitance.pdf}
+  \includegraphics[width=0.95\linewidth]{img/SI-quantum-capacitance.pdf}
   \caption{Relation between the 2D polarizabilities with the quantum
@@
   \centering
-  \includegraphics[width=0.75\linewidth]{img/SI-gpaw-alpha-atomic-polarizability.pdf}
+  \includegraphics[width=1.07\linewidth]{img/SI-gpaw-alpha-atomic-polarizability.pdf}
   \caption{Relation between the 2D polarizabilities
@@
 $n_{\mathrm{3D}}$ is the 3D number density of valence
-electrons. Combine Eq. \ref{eq:eps-plas-3D} with main text
+electrons. Combine Eq. \ref{eq:eps-plas-3D} with 
 Eq. \ref{main-eq:alpha-para-def}, we get:
@@
 calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the C2DB database, as shown in Figure \ref{fig:plasma}.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.65\linewidth]{img/SI-lorentz-model.pdf}
-  \caption{Calculated$\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the
-    C2DB database. The broken line shows the theoretical prediction
+$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using Ref.\cite{Haastrup_2018} database, as shown in Figure \ref{fig:plasma}.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.85\linewidth]{img/SI-lorentz-model.pdf}
+  \caption{Calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
+    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using data from Ref.\cite{Haastrup_2018}. The broken line shows the theoretical prediction
     from single-oscillator model.}
@@
 \cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
-without considering the effect of mix ted medium. Instead, the 2D slab
+without considering the effect of mixed medium. Instead, the 2D slab
 polarizability, either transformed from the vacuum-containing
@@
 geometry as proposed here, will be a better descriptor for the true 2D
-dielectric nature. On the other hand, there are also
-dimension-independent quantities that valid for both 2D and 3D
+dielectric nature. There are also
+dimension-independent quantities that are valid for both 2D and 3D
 systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
@@
 \centering
-\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
+\includegraphics[width=0.85\linewidth]{img/fig-2D-vs-3D.pdf}
 \caption{\label{fig-2D-3D} Dielectric-related physical quantities in
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{img/SI-ellipsoid.pdf}
+  \includegraphics[width=0.9\linewidth]{img/SI-ellipsoid.pdf}
   \caption{Polarizability ellipsoid of a 2D material, the long axis
@@
 
-\subsection{Choice of materials for main text Figure \ref{main-fig:aniso}}
+\subsection{Choice of materials for Figure \ref{main-fig:aniso}}
 \label{ssec:aniso-materials}
@@
 
-\subsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
+\subsection{Explanation for the separation between 2D and 3D regimes in Figure \ref{main-fig:aniso}}
 \label{sssec:aniso-2}
@@
 between the dielectric anisotropy indices of 2D and their bulk
-counterparts. From main text Eqs. \ref{main-eq:alpha-para-def},
+counterparts. From Eqs. \ref{main-eq:alpha-para-def},
 \ref{main-eq:alpha-perp-def} and \ref{main-eq:anisotropy},
@@
 $\alpha_{\mathrm{Bulk}}^{\parallel} \approx
-\alpha^{\parallel}_{\mathrm{2D}}$ (main text Figure
+\alpha^{\parallel}_{\mathrm{2D}}$ (Figure
 \ref{main-fig-4}b), we name
@@
 when $\eta_{\mathrm{2D}}$ is much smaller than 1. Therefore the
-separation between the 2D and 3D regimes in  main text Figure
+separation between the 2D and 3D regimes in Figure
 \ref{main-fig:aniso} is explained.
@@
 \section{Raw data from first principles calculations}
+\label{sec:raw}
 \subsection{Quantities from first principles calculation}
-\label{sec:raw}
+
 Table S2 shows the parameters and results from the

### 2019-01-04 paper.tex
Add minor changed to paper.tex

@@
   the dielectric properties of two-dimensional (2D) materials due to
-  the locality of their electrostatic screening. We found instead that
-  the electric  polarizability correctly
-  captures the dielectric nature of a 2D material which is united to
-  other physical quantities in an atomically thin layer. We reveal a
-  long-sought universal formalism where electronic, geometrical and
-  dielectric properties are intrinsically correlated through the
-  polarizability opening the door to probe quantities yet not directly
-  measurable including the real covalent thickness of a layer. We
-  unify the concept of dielectric properties in any material dimension
-  finding a global dielectric anisotropy index defining their
-  controllability through dimensionality.  }
+  the locality of their electrostatic screening. Instead, the electric
+  polarizability correctly captures the dielectric nature of a 2D
+  material which is united to other physical quantities in an
+  atomically thin layer. We reveal a long-sought universal formalism
+  where electronic, geometrical and dielectric properties are
+  intrinsically correlated through the polarizability opening the door
+  to probe quantities yet not directly measurable including the real
+  covalent thickness of a layer. We unify the concept of dielectric
+  properties in any material dimension finding a global dielectric
+  anisotropy index defining their controllability through
+  dimensionality.  }
 
@@
 conductivities\cite{Dressel_2001_electrodynamics}   
-with elemental interactions, e.g. electron-electron. 
+with elemental interactions. 
 The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
@@
 ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
-components of $\kappa$, namely the in-plane
+components of $\varepsilon$, namely the in-plane
 ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
@@
 dipoles along the \textit{z}-direction in a range of 
-$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\bf a} and
+$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and
 Supplementary Figure \ref{SI-fig:rho-profile}). 
@@
 dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
-(top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c},
+(top panels of Figure \ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c},
 respectively). Both components of the dielectric constant 
@@
 Simulations performed at higher levels of theory using many-body
-techniques, G$_{\rm 0}$W$_{0}$, invariably give alike
-results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}). 
-We have also undertaken similar analysis into the frequency regime 
-for $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where despite of the 
-method utilized from PBE, G$_{\rm 0}$W$_{0}$ up 
-to taking into account electron-hole excitations at the level of the 
-Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$--BSE) the dependence on $L$
-is still present (see Supplementary Section \ref{SI-ssec:gw} for a systematic study). 
-These results indicate that quantities that depend 
-on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, 
-the optical absorption, suffer the
-same deficiencies.  
+techniques, G$_{\rm 0}$W$_{0}$, invariably give alike results (see
+Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).  We have also
+undertaken similar analysis into the frequency ($\omega$) regime for
+$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where the $L$-dependence
+remains present despite various methods utilized (see Supplementary
+Section \ref{SI-ssec:gw} for a systematic study).  These results
+indicate that quantities that depend on
+$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, the optical
+absorption, suffer the same deficiencies.
 %
@@
 %
-Similar to the definition of molecular
-polarizability \cite{Israelachvili_2011},
-$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
-polarizability $\alpha_{\mathrm{2D}}$ through:
-$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
-\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
-$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
-Using electrostatic boundary conditions, 
-the continuity of the electric field along the
-in-plane direction gives
+Similar to the definition of molecular polarizability
+\cite{Israelachvili_2011}, $\boldsymbol{\mu}_{\mathrm{2D}}$ is
+associated with the 2D polarizability $\alpha_{\mathrm{2D}}$ through:
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
+\alpha_{\mathrm{2D}}^{pq} \boldsymbol{E}_{\mathrm{loc}}^{q}$
+\cite{T_bik_2004}, where $\boldsymbol{E}_{\mathrm{loc}}$ is the local
+electric field.  Using electrostatic boundary conditions, the
+continuity of the electric field along the in-plane direction gives
 $\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
@@
 \cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
-Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
+Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D
+polarizabilities, $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ with
+$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
 %
@@
 %
-Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
-to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
-for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
-a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
-and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
+Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
+\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
+panels in Fig.\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
+$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
+centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$
+(Fig. \ref{fig-1}\textbf{d}-\textbf{e}}).
 % A similar curve profile is obtained in both components of the dielectric constant including the much 
@@
 % 
-These findings provide that the 2D polarizability captures the essence of the dielectric properties 
-of layered materials as the microscopic quantity in describing the 
-atomic interactions present in the layers. Its local nature removes any dependence on size effects 
-present in the calculations.  
-More discussions about the choice of the 2D polarizability,
-comparison with other methods, simulations at the frequency-dependent domain
- can be found in Supplementary Section \ref{SI-ssec:gw}.
+These findings provide that the 2D polarizability captures the essence
+of the dielectric properties of layered materials as the microscopic
+quantity in describing the atomic interactions present in the
+layers. Its local nature removes the dependence on size effects
+present in the calculations.  More discussions about the choice of the
+2D polarizability, comparison with other methods, simulations at the
+frequency-dependent domain can be found in Supplementary Section
+\ref{SI-ssec:gw}.
 
@@
 
-As a consequence of Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, we can demonstrate 
-that other quantities are intrinsically related to the polarizability. 
-Using random phase approximation (RPA)
-theory \cite{Adler_1962} within the $\mathbf{k} \cdot \mathbf{p}$
-formalism\cite{kittel_2005_introduction} (see Supplementary
-Section \ref{SI-sec:theory-1} for details), 
-we can show that
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-can be written as: 
-%
-%
-%
+As a consequence of Eqs. \ref{eq:alpha-para-def} and
+\ref{eq:alpha-perp-def}, we demonstrate that other quantities are
+intrinsically related to the polarizability.  Using random phase
+approximation (RPA) theory \cite{Adler_1962} within the
+$\mathbf{k} \cdot \mathbf{p}$ formalism\cite{kittel_2005_introduction}
+(see Supplementary Section \ref{SI-sec:theory-1} for details), we show
+that $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ can be written as:
 \begin{subequations}
@@
 \end{subequations}
-%
-%
-%
-%
 where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
-the intrinsic thickness of the layer (Fig. \ref{fig-1}{\bf a}), and
-$C^{\parallel} = \frac{Ne^2}{2 \pi}$ \cite{Jiang_2017_Eg_Eb}, where
+the intrinsic thickness of the layer (Fig. \ref{fig-1}{\textbf a}), and
+$C^{\parallel} = {\displaystyle \frac{Ne^2}{2 \pi}}$ \cite{Jiang_2017_Eg_Eb}, where
 $N$ corresponds to the degeneracy of the bands associated with
 $E_{\mathrm{g}}$, and $C^{\perp} = {\varepsilon_{0}}$.
-\todo[inline]{The previous expressions for the coefficients are
-  wrong. Please see the version in SI}
-Despite of the simplicity of
-Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, they generalize
-a direct relationship between the polarizability and the electronic
-and structural properties for any 2D material in a new framework.  We
-can show that these equations are valid for the current library of
-known layered materials involving different lattice symmetry, element
-composition, optical and electronic properties.
+% \todo[inline]{The previous expressions for the coefficients are
+  % wrong. Please see the version in SI}
+Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
+\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
+the polarizability and the electronic and structural properties for
+any 2D material in a new framework.  We show that these equations are
+valid for the current library of known layered materials involving
+different lattice symmetry, element composition, optical and
+electronic properties.
 %
-A high-throughput screening performed on 
-different families of TMDCs (MX\(_{\text{2}}\), where M is
-a metal in groups 4, 6, 10, and X=O, S, Se, Te) and phases (P\(\bar{6}\)m2, P3m1), 
-metal monochalcogenides
+A high-throughput screening performed on different families of TMDCs
+(MX\(_{\text{2}}\), where M is a metal in groups 4, 6, 10, and X=O, S,
+Se, Te) and phases (P\(\bar{6}\)m2, P3m1), metal monochalcogenides
 (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
@@
 (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
-and thin layer organic-inorganic perovskites (ABX$_{3}$) (Fig. \ref{fig-3}{\bf a}) 
-shows that our method enables full correlation between these disparate variables. 
-%%
-%
-%Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are the main conclusions of this work. 
-%
-% \todo[inline]{I not sure if we need to show the proportional coefficients
-%  here. $\alpha_{2D}^{\perp}$ is almost certain to be
-%  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
-%  a more complex coefficient.}
-%
-%
-%
-%The static 2D
-%polarizabilities are calculated from the static dielectric response of
-%the selected 2D materials (see {\it Methods}). 
-Figure \ref{fig-3}{\bf b} compares the calculated fundamental bandgap
+and thin layer organic-inorganic perovskites (ABX$_{3}$)
+(Fig. \ref{fig-3}{\textbf a}) shows that our method enables full
+correlation between these disparate variables.  Figure
+\ref{fig-3}{\textbf b} compares the calculated fundamental bandgap
 $E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar
@@
 $E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{SI-sec:pol-2D-Eg}). 
-%It is worth mentioning that materials with
-%elements having large polarizabilities, such as Hf and Zr in
-%1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
-%for the layers with slightly variations between 1T and 2H phases. The
-%former normally shows larger values of
-%$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
-%\todo[inline]{sorry but I don't quite get the idea of this
-%  sentence. In fact HfO2 and ZrO2 have quite low in-plane
-%  polarizabilities compared with even TiO2. Shall we just remove these
-%  sentenses? }
-%
-% 
-We then examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
-using the polarizabilities by first-principle calculations.  Figure
-\ref{fig-3}{\bf c} shows
+\ref{SI-sec:pol-2D-Eg}).  We then examine Eqs. \ref{eq:2D-Moss-para}
+and \ref{eq:2D-Moss-perp} using the polarizabilities by
+first-principle calculations.  Figure \ref{fig-3}{\textbf c} shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
@@
 functional\cite{Heyd_2005} compared with that from
-Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
+Perdew--Burk--Ernzerhof (PBE)
+functional%exchange correlation functional
 (see Supplementary Section \ref{SI-sec:pol-2D-Eg} and Supplementary
 Figure \ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels
-of theory are needed to predict bandgaps. See Supplementary Section \ref{SI-sec:gpaw}
-for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
-using different bandgaps, databases, and levels of calculation.
+of theory are needed to predict bandgaps. See Supplementary Section
+\ref{SI-sec:gpaw} for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and
+\ref{eq:2D-Moss-perp} using different bandgaps, databases, and levels
+of calculation.
 
@@
 where $i$, $j$ are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
-is the covalent radius of atom $i$ (Figure \ref{fig-3}{\bf d} inset). 
+is the covalent radius of atom $i$ (Figure \ref{fig-3}{\textbf d} inset). 
 %
@@
 $R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
-\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
-This result indicates that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
-physical meaning through the geometry of the layer.  Similar to the
-molecular polarizability which characterizes the volume of the electron
-cloud of an isolated molecule \cite{Israelachvili_2011},
+\ref{fig-3}{\textbf d}), which agrees well with Eq
+\ref{eq:2D-Moss-perp}.  This result indicates that
+$\alpha_{\mathrm{2D}}^{\perp}$ has a strong physical meaning through
+the geometry of the layer.  Similar to the molecular polarizability
+which characterizes the volume of the electron cloud of an isolated
+molecule \cite{Israelachvili_2011},
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
@@
 material. Supplementary Section
-\ref{SI-ssec:theory-1-perp-fundamental} shows an electrostatic model 
-of this behavior. Indeed, the universal
+\ref{SI-ssec:theory-1-perp-fundamental} shows an explanation of this
+behavior from fundamental electrostatics. Indeed, the universal
 scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
-\ref{fig-3}{\bf d} indicates that the quantity
+\ref{fig-3}{\textbf d} indicates that the quantity
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, measurable via
@@
 properties of over 230 compounds calculated at the PBE level, and
-superimpose with our results in Figure \ref{fig-3}{\bf c} and
-\ref{fig-3}{\bf d} (see details in Supplementary Section
+superimpose with our results in Figure \ref{fig-3}{\textbf c} and
+\ref{fig-3}{\textbf d} (see details in Supplementary Section
 \ref{SI-sec:gpaw-1}). Although the dielectric properties may be
@@
 %
-In merit of the unit analysis,
+In merit of the unit analysis, $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ both have unit of
+$4\pi\varepsilon_{0} \cdot$[Length]. In other words,
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-both have unit of $4\pi\varepsilon_{0} \cdot$[Length], that is, $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
-characteristic lengths, respectively. The in-plane screened
-electrostatic potential $V(r)$ from a point charge as
-a function of distance $r$: 
+represent in- and out-of-plane characteristic lengths,
+respectively. It is well-known that the in-plane screened
+electrostatic potential $V(r)$ from a point charge as a function of
+distance $r$:
 $V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
@@
 $r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
-respectively. This is analog to the polarizability ellipsoid picture of
-molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
-Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
-material is in general ultra flat, with
+respectively. This is analog to the polarizability ellipsoid picture
+of molecules used in spectroscopy \cite{Banwell_1994} (see
+Supplementary Figure \ref{SI-fig:ellipsoid}). The polarizability
+ellipsoid for a 2D material is in general ultra flat, with
 $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
-TMDCs in Table \ref{tbl:radii}.  Moreover,
-$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
-semiconductor, which qualitatively explains the inverse proportional
-relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$E_{\mathrm{g}}$ seen in Eq. \ref{eq:2D-Moss-para}. 
-This gives a geometrical interpretation of the bandgap in terms 
-of the screening radius of the layer.
+TMDCs in Table \ref{tbl:radii}.  Moreover, $r_{0}^{\parallel}$ is
+generally larger for a smaller bandgap semiconductor, which
+qualitatively explains the inverse proportional relation between
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$ seen in
+Eq. \ref{eq:2D-Moss-para}.  This gives a geometrical interpretation of
+the bandgap in terms of the screening radius of the layer.
 
@@
 be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
-$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\bf a}) as:
+$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
 %
@@
 with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
-(\textit{x}-axis) as shown in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
+(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
 Both HSE06 and PBE datasets give almost identical results.  
@@
 \centering
-\includegraphics[width=0.79\linewidth]{img/fig1.pdf}
+\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
 \caption{\label{fig-1} \textbf{2D polarizability as the true
@@
   and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
-  \ref{eq:alpha-perp-def}, respectively. HSE06 functional is used in all plots.}
+  \ref{eq:alpha-perp-def}, respectively.
+  % HSE06 functional is used in all plots.
+}
 \end{figure}
@@
   \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
-  revealed using the data from Ref. \citenum{Haastrup_2018} (squares),
+  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
   as superimposed on \textbf{c} and \textbf{d}.}

### 2019-01-04 SI.tex
Add changes to SI

@@
 In this section we provide more analysis on the dielectric properties
-of 2D materials calculated using many-body Green function method 
-(G$_0$W$_0$), including electron-hole interactions at the level of the 
-Bethe-Salpeter equation (G$_0$W$_0$--BSE), and at the frequency-dependent regime.
+of 2D materials calculated using many-body Green function
+method (G$_0$W$_0$), including electron-hole interactions at the level
+of the Bethe-Salpeter equation (G$_0$W$_0$--BSE), and at the
+frequency-dependent regime.
 
@@
 %
-As can be seen in Figure \ref{fig:rho-profile} the induced charges on the
-MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{} centered at the middle of the layer. This corresponds to about 6 \AA ~from each side. 
-When the
-SL size $L \gg$12 \AA{} as in the first principle calculations done in
-the main text, the induced dipoles from the periodic images do not
-interact, and thus give the converged values of $\alpha_{\mathrm{2D}}$.
+As can be seen in Figure \ref{fig:rho-profile} the induced charges on
+the MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}
+centered at the middle of the layer. This corresponds to about 5-6 \AA
+from each side.  When the SL size $L \gg$12 \AA{} as in the first
+principle calculations done in the main text, the induced dipoles from
+the periodic images do not interact, and thus give the converged
+values of $\alpha_{\mathrm{2D}}$.
 
@@
 throughout the whole frequency range at PBE level. The $L$-dependency can also be
-removed using Eqs. \ref{main-eq:alpha-para-def} and
+removed using main text Eqs. \ref{main-eq:alpha-para-def} and
 \ref{main-eq:alpha-perp-def}, yielding lattice-independent
@@
 %
-Note that when extracting
-the frequency-dependent 2D polarizabilities from
-Eqs. \ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def},
-the peak position in energy $\omega (eV)$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This
-is explained by the fact that the local extrema from spectra of
+Note that when extracting the frequency-dependent 2D polarizabilities
+from main text Eqs. \ref{main-eq:alpha-para-def} and
+\ref{main-eq:alpha-perp-def}, the peak position in energy
+$\hbar \omega$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This is
+explained by the fact that the local extrema from spectra of
 $\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
@@
 $\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
-
-We note that the result change slightly when G$_{0}$W$_{0}$ method
-is used. As shown in Figures \ref{fig:GW-omega-in} and
-\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
-functions change with $L$, but also the peak positions. As a result
-the obtained polarizabilities also show $L$-dependent peak shift. This
-can be explained by the long-range nature of Coulomb interactions. In
-fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
-\begin{equation}
-  \label{eq:GW-formula}
-  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
-\end{equation}
-where $G$ is the non-interacting Green function, and $\nu$ is the
-Coulomb interaction. Since the dielectric constant $\varepsilon$
-changes with $L$, the self energy as well quasi-particle energies of
-the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
-higher peak energy of the dielectric spectrum when $L$ increases. Such
-peculiar $L$-dependency can be minimized when adding electron-hole
-interaction through the Bethe-Salpethe equation (BSE), as shown in
-Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
-polarizabilities again becomes lattice-independent due to the
-localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.
+Performing the simulations at the level of G$_{0}$W$_{0}$
+we observe shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
+as a function of $L$. Figures \ref{fig:GW-omega-in} and
+\ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
+functions change with $L$ but also the peak positions. As a result
+the obtained polarizabilities also show $L$-dependent peak 
+shift (Figures \ref{fig:GW-omega-in} {\bf b}-{\bf d} and
+\ref{fig:GW-omega-out}{\bf b}-{\bf d}). This
+can be explained by the long-range nature of Coulomb interactions into the self-energy 
+$\Sigma=iGW$.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+The non-interacting Green's function can be constructed as:
+
+\begin{equation}
+    G^{(0)}(\mathbf{r},\mathbf{r}',\omega)=\sum_n\frac{\phi_{\mathrm{n}\mathbf{k}}^{(0)}(\mathbf{r})\phi_{\mathrm{n}\mathbf{k}}^{*(0)}(\mathbf{r'})}{\omega-\epsilon_\mathrm{n}-+i\eta\mathrm{sgn}(\epsilon_\mathrm{n}-\epsilon_\mathrm{F})}
+\end{equation}
+
+Here $\epsilon_n(\mathbf{k})$ are the DFT eigenenergies at \textbf{k}, $\epsilon_F$ the Fermi energy, $\omega$ the frequency, $\ket{u_{n\mathbf{k}}}$ the cell periodic Bloch functions, $\phi_{n\mathbf{k}}$ are the one-electron orbitals and $\eta$ is an infintesimal complex shift.
+It can be seen from equation \ref{eq:dft-dielectric} there is a clear volume dependence on $\Omega$ of the dielectric function from the preceding DFT calculation.
+Thus, when carrying out a calculation on a slab, the dielectric function will vary with the vacuum spacing used.
+
+Using the dielectric function we can calculate the screened Coulomb interaction:
+\begin{equation}
+    W=\epsilon^{-1}\nu
+\end{equation}
+where $\nu$ is the bare Coulomb interaction given by
+$e^2$/$|\mathbf{r}-\mathbf{r}'|$. Due to the
+1/$|\mathbf{r}-\mathbf{r}'|$ term, images in the non-periodic
+direction have a long-range spurious interaction which varies with
+vacuum spacing. From the screened Coulomb interaction and
+non-interacting Green's function it is possible to calculate the
+self-energy of the system:
+\begin{equation}\label{self}
+\Sigma=iGW
+\end{equation}
+and the quasi-particle eigenenergies are found using:
+\begin{equation}\label{quasi}
+E^{\mathrm{QP}}_{\mathrm{n}\mathbf{k}}=\Re\Big[\braket{\phi_{\mathrm{n}\mathbf{k}}|-\frac{1}{2}\Delta+V_{\mathrm{ext}}+V_\mathrm{H}+\Sigma(\epsilon_{\mathrm{n}\mathbf{k}}^{\mathrm{DFT}})|\phi_{\mathrm{n}\mathbf{k}}}\Big]
+\end{equation}
+Therefore a new set of eigenergies, E$_{n\mathbf{k}}^{QP}$ are found.
+Using E$_{n\mathbf{k}}^{QP}$ it is then possible to recalculate the dielectric function using the quasi-particle eigenergies as well as the DFT eigenfunctions.
+
+Due to the volume dependence of $\Sigma$ in equations \ref{self} and
+\ref{quasi}, increasing the vacuum spacing leads to a change in the
+calculated quasi-particle eigenergies. This, along with the volume
+dependence in the calculation of the dielectric function, leads to an
+increase in energy of the peak position and a decrease in its
+magnitude with increasing vacuum spacing.  Including excitonic effects
+on top of a G$_0$W$_0$ calculation through solving the Bethe--Salpeter
+equation corrects for this energy shift by localizing the exciton
+within the slab (Figures \ref{fig:BSE-omega-in} and
+\ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
+the dielectric function on both components of
+$\varepsilon_{\mathrm{SL}}(\omega)$ with increasing vacuum spacing is
+still observed.  Using main text Eqs. \ref{main-eq:alpha-para-def} and
+\ref{main-eq:alpha-perp-def} we can remove the dependence on $L$ as
+plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
+\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with few variations on
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% We note that the result change slightly when G$_{0}$W$_{0}$ method                                               %
+% is used. As shown in Figures \ref{fig:GW-omega-in} and                                                           %
+% \ref{fig:GW-omega-out}, not only do the intensity of the dielectric                                              %
+% functions change with $L$, but also the peak positions. As a result                                              %
+% the obtained polarizabilities also show $L$-dependent peak shift. This                                           %
+% can be explained by the long-range nature of Coulomb interactions. In                                            %
+% fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:                                    %
+% \begin{equation}                                                                                                 %
+%   \label{eq:GW-formula}                                                                                          %
+%   \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu                                                          %
+% \end{equation}                                                                                                   %
+% where $G$ is the non-interacting Green function, and $\nu$ is the                                                %
+% Coulomb interaction. Since the dielectric constant $\varepsilon$                                                 %
+% changes with $L$, the self energy as well quasi-particle energies of                                             %
+% the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get                                               %
+% higher peak energy of the dielectric spectrum when $L$ increases. Such                                           %
+% peculiar $L$-dependency can be minimized when adding electron-hole                                               %
+% interaction through the Bethe-Salpethe equation (BSE), as shown in                                               %
+% Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The                                                  %
+% polarizabilities again becomes lattice-independent due to the                                                    %
+% localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method. %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{Detailed derivations of Eq. \ref{main-eq:2D-Moss-para}}  %
+\subsection{Detailed derivations of main text Eq. \ref{main-eq:2D-Moss-para}}  %
 \label{ssec:theory-1-para}
@@
 Following the method of $\mathbf{k} \cdot \mathbf{p}$ theory from
-Ref. \citenum{Jiang_2017_Eg_Eb}, the matrix element in the numerator
+Ref.~\citenum{Jiang_2017_Eg_Eb}, the matrix element in the numerator
 of Eq. \ref{eq:alpha_para_RPA} is approximated by:
@@
 The coefficient of $C^{\parallel}$ adapted from
-Ref. \citenum{Jiang_2017_Eg_Eb} $C^{\parallel} = N e^{2}/(2\pi)$
+Ref.~\citenum{Jiang_2017_Eg_Eb} $C^{\parallel} = N e^{2}/(2\pi)$
 predicts linear correlation between $\alpha^{\parallel}_{\mathrm{2D}}$
@@
 
-\subsection{Detailed derivation of Eq. \ref{main-eq:2D-Moss-perp}}
+\subsection{Detailed derivation of main text Eq. \ref{main-eq:2D-Moss-perp}}
 \label{ssec:theory-1-perp}
 
-For Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
+For main text Eq. \ref{main-eq:2D-Moss-perp}, treating the in-plane
 wave functions as plane wave with form
@@
 
-\subsection{Explanation of Eq. \ref{main-eq:2D-Moss-perp}
+\subsection{Explanation of main text Eq. \ref{main-eq:2D-Moss-perp}
   from fundamental electrostatics}
@@
 \end{equation}
-which explains the linear relation seen in Figure
+which explains the linear relation seen in main text Figure
 \ref{main-fig-3}d. We can see that such simple model nicely captures
@@
     $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ from 
-    Ref.\cite{Haastrup_2018} corresponding to Figure \ref{main-fig-3}{\bf c}
+    Ref.~\citenum{Haastrup_2018} corresponding to main text Figure \ref{main-fig-3}{\bf c}
     and \ref{main-fig-3}{\bf d}.}
@@
 relations on an even larger scale database. We select over 230
-semiconducting 2D materials from Ref.\cite{Haastrup_2018} 
+semiconducting 2D materials from Ref.~\citenum{Haastrup_2018} 
 with a GW bandgap
@@
 \ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha_{\mathrm{2D}}^{\parallel}$ from 
-Ref.\cite{Haastrup_2018} as a function of minimal and direct bandgap calculated
+Ref.~\citenum{Haastrup_2018} as a function of minimal and direct bandgap calculated
 on PBE, HSE06 and GW levels. We observe,
@@
     $E_{\mathrm{g}}$ calculated on different theoretical levels:
-    \textbf{a,} PBE, \textbf{b,} HSE and \textbf{c,} GW of Ref.\cite{Haastrup_2018}.}
+    \textbf{a,} PBE, \textbf{b,} HSE and \textbf{c,} GW of Ref.~\citenum{Haastrup_2018}.}
   \label{fig:SI-gpaw-alpha-Eg-all}
@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{\mathrm{opt}}$
-from Ref.\cite{Haastrup_2018} with
+from Ref.~\citenum{Haastrup_2018} with
 $E_{\mathrm{g}}^{\mathrm{opt}}=E_{\mathrm{g}}^{\mathrm{dir,QP}}-E_{\mathrm{b}}^{\mathrm{BSE}}$,
@@
   \caption{$(4\pi\varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-    $E_{\mathrm{g}}^{\mathrm{opt}}$ from Ref.\cite{Haastrup_2018}.}
+    $E_{\mathrm{g}}^{\mathrm{opt}}$ from Ref.~\citenum{Haastrup_2018}.}
   \label{fig:opt}
@@
 
-The relatively large size of Ref.\cite{Haastrup_2018} database allows us
+The relatively large size of Ref.~\citenum{Haastrup_2018} database allows us
 to examine the relation between 2D polarizabilities and other physical
@@
   \caption{Relation between 2D polarizabilities and the effective
-    carrier mass from Ref.\cite{Haastrup_2018}. 
+    carrier mass from Ref.~\citenum{Haastrup_2018}. 
     \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of the
@@
 $n_{\mathrm{3D}}$ is the 3D number density of valence
-electrons. Combine Eq. \ref{eq:eps-plas-3D} with 
+electrons. Combine Eq. \ref{eq:eps-plas-3D} with main text
 Eq. \ref{main-eq:alpha-para-def}, we get:
@@
 calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using Ref.\cite{Haastrup_2018} database, as shown in Figure \ref{fig:plasma}.
+$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using Ref.~\citenum{Haastrup_2018} database, as shown in Figure \ref{fig:plasma}.
 \begin{figure}[htbp]
@@
   \caption{Calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
-    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using data from Ref.\cite{Haastrup_2018}. The broken line shows the theoretical prediction
+    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using data from Ref.~\citenum{Haastrup_2018}. The broken line shows the theoretical prediction
     from single-oscillator model.}
@@
 
-\subsection{Choice of materials for Figure \ref{main-fig:aniso}}
+\subsection{Choice of materials for main text Figure \ref{main-fig:aniso}}
 \label{ssec:aniso-materials}
@@
 
-\subsection{Explanation for the separation between 2D and 3D regimes in Figure \ref{main-fig:aniso}}
+\subsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
 \label{sssec:aniso-2}
@@
 between the dielectric anisotropy indices of 2D and their bulk
-counterparts. From Eqs. \ref{main-eq:alpha-para-def},
+counterparts. From main text Eqs. \ref{main-eq:alpha-para-def},
 \ref{main-eq:alpha-perp-def} and \ref{main-eq:anisotropy},
@@
 $\alpha_{\mathrm{Bulk}}^{\parallel} \approx
-\alpha^{\parallel}_{\mathrm{2D}}$ (Figure
+\alpha^{\parallel}_{\mathrm{2D}}$ (main text Figure
 \ref{main-fig-4}b), we name
@@
 when $\eta_{\mathrm{2D}}$ is much smaller than 1. Therefore the
-separation between the 2D and 3D regimes in Figure
+separation between the 2D and 3D regimes in main text Figure
 \ref{main-fig:aniso} is explained.

### 2019-01-04 SI.tex
Fix the number of materials

@@
 memory overload, high-accurate calculations at hybrid HSE06 level is limited 
-to about 56 compounds. 
+to about 55 compounds. 
 It is desirable to validate our proposed

### 2019-03-11 paper.tex
Minor fix
Add data availability
Add Matthes papaer

@@
 
-To solve this problem, we need to
-find the $L$-independent alternative of
-$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
-Eq.~\ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
+To solve this problem, we need to find the $L$-independent alternative
+of $\varepsilon_{\mathrm{SL}}$, which is related to both electrostatic
+and optical properties of a 2D material \cite{Matthes_2016}. As
+described before, by multiplying Eq.~\ref{eq:def-eps-2} with $L$ we
+obtain the sheet polarization density
 $\boldsymbol{\mu}_{\mathrm{2D}}$, that is,
-$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
-which is independent of $L$ due to the locality 
-of $\boldsymbol{u}$ and $A$. 
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, which is
+independent of $L$ due to the locality of $\boldsymbol{u}$ and $A$.
 %
@@
 $\alpha_{\mathrm{2D}}^{\perp}$
-(Fig. \ref{fig-1}\textbf{d}-\textbf{e}}).
+(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).
 % A similar curve profile is obtained in both components of the dielectric constant including the much 
@@
 
+\section{Data Availability}
+The data that support the findings of this study are available from
+the corresponding author upon reasonable request.
+
 \bibliography{ref}
@@
 \centering
-\includegraphics[width=0.74\linewidth]{img/fig2.pdf}
+\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the

### 2019-03-11 paper.tex
Fix electronic polarizabilities

@@
 \date{}
-\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
 %\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
@@
 \ref{fig-3}{\textbf b} compares the calculated fundamental bandgap
-$E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar
+$E_{\mathrm{g}}$ (blue dots) and 2D electronic polarizabilities (bar
 plots) of all the 2D materials investigated, covering a wide spectrum
@@
 
-Our results show that the 2D electric polarizability
+Our results show that the 2D electronic polarizability
 $\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric

### 2019-03-11 paper.tex
Add corrections for the polarizability

@@
 $\varepsilon_{0}$ is vacuum permittivity. Here we only study the
-electronic contribution to the dielectric constant where the dipole
-$\boldsymbol{P}$ comes from the displacement of electron cloud under
-external electric field. For the majority of the 2D nanosheets, the
+electronic contribution to the macroscopic dielectric constant where
+the dipole $\boldsymbol{P}$ comes from the displacement of electron
+cloud under external electric field, while the ionic contribution
+\cite{Laturia_2018} ($\boldsymbol{P}$ comes from the displacement of
+nuclei) to the static $\varepsilon$ is considered.
+For the majority of the 2D nanosheets, the
 off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
@@
 \end{subequations}
+Note due to the choice of $\varepsilon$ is limited to the electronic
+macroscopic dielectric constant, $\alpha_{\mathrm{2D}}$ naturally
+refers to the electronic polarizability (the polarizability of the
+electron cloud \cite{Israelachvili_2011}).
 %
@@
 Simulations were carried out using plane-wave density functional
-theory package VASP
-\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the projector
-augmented wave (PAW) approach with GW pseudopotentials
-\cite{Kresse_1999_pseudopotentials}. Band gaps were calculated using
-the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
+theory package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2}
+using the projector augmented wave (PAW) approach with GW
+pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
+calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
 \cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
@@
 highest given in the pseudopotentials used in each material. This
-guarantees that absolute energies were converged to a few meV and
-the stress tensor to within 0.01 kBar.  Calculation of the
-macroscopic ion-clamped dielectric tensor were carried out with an
+guarantees that absolute energies were converged to a few meV and the
+stress tensor to within 0.01 kBar.  Calculation of the macroscopic
+ion-clamped dielectric tensor were carried out with an
 18$\times$18$\times$1 k-grid and electric field strength of 0.001
-eV/\AA. The materials from Ref.\citenum{Haastrup_2018} for comparison
+eV/\AA.  Local field effect corrections are included at the
+exchange-correlation potential $V_{\mathrm{xc}}$ at both PBE and HSE06
+levels. The materials from Ref.\citenum{Haastrup_2018} for comparison
 were choses with the GW bandgap larger than 0.05 eV. Bulk layered
@@
 18$\times$18$\times$6 k-grid with same parameter as for monolayer,
-while the dielectric properties of bulk counterparts of Ref.~\citenum{Haastrup_2018}
-are calculated at PBE level with a k-point density of 10~\AA$^{-1}$.
+while the dielectric properties of bulk counterparts of
+Ref.~\citenum{Haastrup_2018} are calculated at PBE level with a
+k-point density of 10~\AA$^{-1}$. Local field effect corrections are
+also used for the dielectric properties of bulk systems.
 

### 2019-03-14 paper.tex
Correct minor typo
Apply changes locally

@@
 \cite{Laturia_2018} ($\boldsymbol{P}$ comes from the displacement of
-nuclei) to the static $\varepsilon$ is considered.
+nuclei) to the static $\varepsilon$ is not considered.
 For the majority of the 2D nanosheets, the
@@
 refers to the electronic polarizability (the polarizability of the
-electron cloud \cite{Israelachvili_2011}).
+electron cloud \cite{Israelachvili_2011}). We also note that such
+approach is essentially different from the effective medium theory
+(EMT) treatment\cite{Aspnes_1982} of 2D materials, in which the
+hypothetical effective dielectric constant of 2D materials
+$\varepsilon_{\mathrm{2D}}$ are extracted from the macroscopic
+dielectric constant \cite{Matthes_2016,Laturia_2018}, from
+pre-determined 2D layer thickness $\delta$. The 2D electronic
+polarizability approach solves the issue of overestimation in the EMT
+approach, and $\alpha_{\mathrm{2D}}$ has an umambiguous physical
+meaning. Detailed discussions can be found in Supplementary Section
+\ref{SI-sec:2D-3D-rescale}.
 %

### 2019-03-14 SI.tex
Modification on 20190314

@@
 Here we will show the results of dielectric properties calculated
-using many-body Green function method (G$_0$W$_{0}$)
-and with electron-hole interactions at the level of the Bethe-Salpeter 
-equation (G$_0$W$_{0}$--BSE). We first compare the case of a
-monolayer of BN within a varying superlattice $L$ 
-calculated using PBE and G$_{0}$W$_{0}$ as shown in Figure \ref{fig:GW-PBE-alpha}. 
-%
-%
-Both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of $L$ 
-despite of the separation utilized in the simulations (Figure \ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}).
-However, corresponding 2D polarizabilities are almost $L$-independent (Figure \ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}).
-It is worth noting
-that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than in PBE functionals.
+using many-body Green function method (G$_0$W$_{0}$) and with
+electron-hole interactions at the level of the Bethe-Salpeter equation
+(G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
+$\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
+are calculated using VASP, with a cutoff energy of XXX and k point
+density of YYY. Local field effect is included in both cases: local
+field correction is applied to independent-particle energies in G0W0
+at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
+polarizability is calculated using BSE in G0W0-BSE
+\todo[inline]{@Declan, could you help modify this part?}
+
+We first compare the case of a monolayer of BN within a varying
+superlattice $L$ calculated using PBE and G$_{0}$W$_{0}$ as shown in
+Figure \ref{fig:GW-PBE-alpha}.  Both
+$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of
+$L$ despite of the separation utilized in the simulations (Figure
+\ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}). However, corresponding 2D
+polarizabilities are almost $L$-independent (Figure
+\ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting that since
+the G$_{0}$W$_{0}$ method has better estimation of the bandgap,
+$\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller
+using G$_{0}$W$_{0}$ than in PBE functionals.
 \begin{figure}[htbp]
@@
 Performing the simulations at the level of G$_{0}$W$_{0}$
-we observe shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
-as a function of $L$. Figures \ref{fig:GW-omega-in} and
+we observe blue shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
+with increasing $L$. Figures \ref{fig:GW-omega-in} and
 \ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
@@
 increase in energy of the peak position and a decrease in its
-magnitude with increasing vacuum spacing.  Including excitonic effects
-on top of a G$_0$W$_0$ calculation through solving the Bethe--Salpeter
-equation corrects for this energy shift by localizing the exciton
-within the slab (Figures \ref{fig:BSE-omega-in} and
+magnitude with increasing vacuum spacing. Such effect is also
+discussed in several other studies
+\cite{Rozzi_2006,Hueser_2013_2Dvs3D}, when full Coulomb interaction is
+used in a supercell. Including excitonic effects on top of a
+G$_0$W$_0$ calculation through solving the Bethe--Salpeter equation
+corrects for this energy shift by localizing the exciton within the
+slab (Figures \ref{fig:BSE-omega-in} and
 \ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
@@
 plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
-\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with few variations on
+\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with fewer variations on
 $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.
@@
 \pagebreak{}
-\section{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
+\section{Comment on the hypothetical ``dielectric constant'' in the effective medium theory (EMT)}
 \label{sec:2D-3D-rescale}
@@
 x,y directions but separated by a vacuum layer between its images
-\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
-definition of the 2D ``dielectric constant'' (in particular, its
-in-plane components) is questionable, due to the locality of
-electrostatic screening of the 2D materials
-\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
+\cite{Matthes_2016,Laturia_2018}. Such method makes use of the
+effective medium theory (EMT), and as discussed in the main text, the
+definition of the 2D ``dielectric constant'' is questionable, due to
+the locality of electrostatic screening of the 2D materials
+\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Moreover, the
+EMT approach assumes that the 2D material has an effective thickness
+$\delta$ and effective dielectric constant
+$\varepsilon_{\mathrm{2D}}$, while the exact value of $\delta$ is
+unknown due to the ambiguity of the reference planes. Here we show
 that, in addition to the ambiguous definition of the 2D dielectric
 constant, such approach requires the precise determination of the 2D
-layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.
+layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical. On
+the contrary, the 2D polarizability approach presented in the main
+text is independent of the choice of the parameter $\delta$, as well
+as the volume fraction of the 2D material, and can correctly capture
+the dielectric properties of the 2D material.
 
@@
 $\varepsilon$ comes from the planar limit of the
-Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
+effective medium theory \cite{Markel_2016,Aspnes_1982}, and can be
 expressed by means of the macroscopic dielectric constant
@@
 
-Another drawback of the 2D dielectric constant approach is the
+Another drawback of the 2D EMT approach is the
 overestimation of the out-of-plane dielectric response. As can be seen
@@
 \item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
-\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
-\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
-\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.
-
-\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
+\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ in EMT requires calculation with varied superlattice length.
+\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
+\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
+
+\item The value of $\epsilon_{\mathrm{2D}}$ in EMT hugely depends on the
   choice of the thickness of 2D material, while such information is

### 2019-03-14 paper.tex
Modification on 20190314

@@
 approach is essentially different from the effective medium theory
-(EMT) treatment\cite{Aspnes_1982} of 2D materials, in which the
-hypothetical effective dielectric constant of 2D materials
+\cite{Aspnes_1982,Markel_2016} (EMT) treatment of 2D materials, in
+which the hypothetical effective dielectric constant of 2D materials
 $\varepsilon_{\mathrm{2D}}$ are extracted from the macroscopic
@@
 approach, and $\alpha_{\mathrm{2D}}$ has an umambiguous physical
-meaning. Detailed discussions can be found in Supplementary Section
-\ref{SI-sec:2D-3D-rescale}.
+meaning. Detailed discussions about the different between the 2D
+polarizability and the EMT approach, can be found in Supplementary
+Section \ref{SI-sec:2D-3D-rescale}.
 %

### 2019-03-14 convert.py
Make convert script handle transparency: svg-->png-->pdf

@@ -25,19 +25,32 @@ def convert_pdf(infile, outdir="./img"):
     base_name = os.path.basename(infile)
     infile = os.path.join(PATH, base_name)
     outfile = os.path.join(os.path.abspath(outdir), base_name)
-    outfile = outfile.replace(".svg", ".pdf")
+    outfile = outfile.replace(".svg", ".png")
     print(outfile)
-    program = "inkscape"
+    program = "/Applications/Inkscape.app/Contents/Resources/bin/inkscape"
     params = ["--without-gui", "--export-area-page",
     ]
     io = ["--file={}".format(infile),
-          "--export-pdf={}".format(outfile)]
+          "--export-png={}".format(outfile),
+          "--export-dpi=600"]
     success = subprocess.call([program, *params, *io])
+    
     if success != 0:
         warnings.warn(TColors.FAIL + "File {} cannot be converted!".format(infile) + TColors.ENDC)
     else:
         print(TColors.OKGREEN +
               "File {} converted successfully on thread {}.".format(infile, multiprocessing.current_process())
+              +TColors.ENDC)
+    program = "convert"
+    infile = outfile
+    outfile = infile.replace(".png", ".pdf")
+    io = [infile, outfile]
+    success = subprocess.call([program, *io])
+    if success != 0:
+        warnings.warn(TColors.FAIL + "File {} cannot be converted!".format(infile) + TColors.ENDC)
+    else:
+        print(TColors.OKGREEN +
+              "File {} converted to pdf on thread {}.".format(infile, multiprocessing.current_process())
               +TColors.ENDC)
 
 # Convert all the pdf files

### 2019-06-11 paper.tex
Submit to PNAS

@@
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
+% \documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
+\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
+
+\templatetype{pnasresearcharticle} % Choose template 
 \usepackage[utf8]{inputenc}
@@
 
-\author{Tian Tian}
-\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
-\altaffiliation{T. T. and D. S. contributed equally to this work}
-\author{Declan Scullion}
-\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
-\altaffiliation{T. T. and D. S. contributed equally to this work}
-\author{Dale Hughes}
-\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
-\author{Lu Hua Li}
-\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
-\author{Chih-Jen Shih}
-\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
-\author{Jonathan Coleman}
-\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
-\author{Manish Chhowalla}
+\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+
+\author[a,1]{Tian Tian}
+\author[b, 1]{Declan Scullion}
+\author[b]{Dale Hughes}
+\author[c]{Lu Hua Li}
+
+\author[a]{Chih-Jen Shih}
+\author[d]{Jonathan Coleman}
+\author[e]{Manish Chhowalla}
 %% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
-\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
-\author{Elton J. G. Santos}
-\email{e.santos@qub.ac.uk}
-\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
-\date{}
-\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
-%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
-% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
-\begin{document}
 
-\newpage{}
+\author[b, 2]{Elton J. G. Santos}
 
-% \section{Introduction}
-% \label{sec:org2ea169d}
-\linenumbers{}
+\leadauthor{Tian}
 
-{\bfseries The dielectric constant, which defines the polarization of
+\affil[a]{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\affil[b]{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
+\affil[c]{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
+\affil[d]{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
+\affil[e]{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
+
+\authorcontributions{E.J.G.S. designed the scope of research. T.T.,
+  D.S. and D.H. performed first-principles calculations. T.T. and
+  D.S. performed the analysis of data. T.T., D.S. and E.J.G.S. wrote
+  the paper. L.H.L., C.J.S., J.C. amd M.C. participated in discussion of manuscript.}
+\authordeclaration{The authors declare no conflict of interest.}
+\equalauthors{\textsuperscript{1}T.T. and D.S. contributed equally to this work}
+\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: e.santos@qub.ac.uk}
+
+% \significancestatement{
+
+% }
+
+\begin{abstract}
+  The dielectric constant, which defines the polarization of
   the media, is a key quantity in condensed matter. It determines
@@
   anisotropy index defining their controllability through
-  dimensionality.  }
+  dimensionality.  
+\end{abstract}
 
-The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
+\dates{This manuscript was compiled on \today}
+
+\begin{document}
+
+\maketitle
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+% \section{Introduction}
+% \label{sec:org2ea169d}
+% \linenumbers{}
+
+\dropcap{T}he dielectric constant $\varepsilon$ (also known as the relative permittivity) 
 plays a crucial role in bridging various fundamental material
@@
 %%
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\linewidth]{img/fig1.pdf}
+\caption{\label{fig-1} \textbf{2D polarizability as the true
+    descriptor of the dielectric nature of 2D materials.}
+  \textbf{a}. 3D illustration of the spatial distribution of the
+  charge density change $\Delta \rho(z)$ along the z-direction for
+  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
+  eletric field of 0.01 V/\AA{}.  The green and red regions represent
+  negative and positive induced charges, respectively. The macroscopic
+  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
+  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
+  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
+  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
+  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
+  constant when $L>$15 \AA{}, compared with the $L$-dependence of
+  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
+  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
+  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
+  \ref{eq:alpha-perp-def}, respectively.
+  % HSE06 functional is used in all plots.
+}
+\end{figure}
 We approach this problem showing that the current definition of
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=9cm]{img/fig2.pdf}
+\caption{\label{fig-3} \textbf{The universal scaling relation of the
+    dielectric nature of 2D materials}. \textbf{a}. The structures of
+  the 2D materials investigated in this
+  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
+  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
+  (blue dots) for all the 2D materials studied.
+  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
+  increasing $E_{\mathrm{g}}$, while no apparent relation between
+  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
+  observed. HSE06 functional is used to obtain the data. \textbf{c}.
+  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
+  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
+  correlation between each other. The energy range of visible light is
+  shown in the background. \textbf{d}.
+  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
+  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
+  in the inset), showing a perfect linear relation with slope very
+  close to $1/4\pi$ (i.e.
+  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
+  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
+  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
+  as superimposed on \textbf{c} and \textbf{d}.}
+\end{figure}
+
 We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
@@
 the bandgap in terms of the screening radius of the layer.
+\begin{table}
+  \centering
+  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
+    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
+    selected 2D materials calculated from first principles
+    simulations. $r_{0}^{\parallel}$ is in general much larger than
+    $r_{0}^{\perp}$, which accounts for the highly anisotropic
+    dielectric nature of 2D materials.}
+  \label{tbl:radii}  
+  \begin{tabular}{lcc}
+    \hline
+    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
+    \hline
+    2H-MoS$_{2}$ & 40.0 & 2.50 \\
+    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
+    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
+    2H-WS$_{2}$ & 35.7 & 2.46  \\
+    2H-WSe$_{2}$ & 41.0 & 2.71 \\
+    2H-WTe$_{2}$ & 53.5 &  3.17\\
+    \hline
+  \end{tabular}
+\end{table}
 
@@
 %\label{sec:2D-3D}
-
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\linewidth]{img/fig4.pdf}
+\caption{\label{fig-4} \textbf{Transition of dielectric properties
+    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
+  transition. $\alpha$ in the 2D material is essentially equivalent to
+  $\varepsilon$ in its bulk counterpart. \textbf{b}
+  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
+  (y-axis) compared with the predicted value from 2D
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
+  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
+  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
+  (x-axis). The predicted value is in good aggreement with the DFT
+  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
+  coupling. The comparisons in \textbf{b} and \textbf{c} are made
+  based on both HSE06 (circles) and PBE (squares) functionals.}
+\end{figure}
 We next show that the underlying physical mechanism linking 
@@
 their 3D bulk counterparts in a remarkable way. 
-%The dielectric constant $\varepsilon$, although not well-defined for
-%a monolayer 2D material, becomes applicable when the 2D layers are
-%stacked. 
-%
-%
-%
 In a bulk layered material stacked by layers with equilibrium
@@
 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=\linewidth]{img/fig5.pdf}
+  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
+      function of bandgap $E_{\mathrm{g}}$}. The
+    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
+    their bulk counterparts (orange square) can be distinguished by
+    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
+    semiconducting materials in other dimensions are also superimposed
+    for comparison. Isotropic dielectric property is observed for bulk
+    covalent materials (3D, red triangle) and fullerenes (0D, green
+    star), while reduced dimensional materials, including planar
+    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
+    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
+    scattered along the boundary line. The dimensionality and
+    structure of typical materials are shown along the axis on the
+    right. Compared with other materials, 2D materials and their bulk
+    counterparts provide more flexibility of controlling the
+    dielectric anisotropy.}
+  \label{fig:aniso}
+\end{figure}
 Finally, we show that a general picture of the dielectric properties in
@@
 
-\section{Theoretical Methods}
-\label{sec:org8457dbb}
-
+\matmethods{
 Simulations were carried out using plane-wave density functional
@@
 k-point density of 10~\AA$^{-1}$. Local field effect corrections are
-also used for the dielectric properties of bulk systems.
+also used for the dielectric properties of bulk systems.}
+\showmatmethods{}
 
-\section{Data Availability}
-The data that support the findings of this study are available from
-the corresponding author upon reasonable request.
+% FOR ES
+\acknow{T.T. and C.J. are thankful for the ETH start funding.}
+\showacknow{}
+
+% \subsection*{Data Availability}
+% The data that support the findings of this study are available from
+% the corresponding author upon reasonable request.
 
@@
 % \section{Figures}
-\label{sec:org34cbe74}
-\begin{figure}[H]
+
+\iffalse
+\begin{figure}
 \centering
-\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
+\includegraphics[width=\linewidth]{img/fig1.pdf}
 \caption{\label{fig-1} \textbf{2D polarizability as the true
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
+\includegraphics[width=\linewidth]{img/fig2.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
 
-\begin{table}[H]
+\begin{table}
   \centering
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
+\includegraphics[width=\linewidth]{img/fig4.pdf}
 \caption{\label{fig-4} \textbf{Transition of dielectric properties
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
-  \includegraphics[width=1.01\linewidth]{img/fig5.pdf}
+  \includegraphics[width=\linewidth]{img/fig5.pdf}
   \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
@@
 \end{figure}
+\fi
 

### 2019-10-02 src/VASP_HSE/epfl_data.py
Add new scripts for new figures

@@ -1,0 +1,193 @@
+import ase.db
+from ase.io import read, write
+import warnings
+import numpy
+import matplotlib.pyplot as plt
+from ase.data import covalent_radii
+from scipy.stats import linregress
+import os, os.path
+from scipy.constants import pi, epsilon_0
+import csv
+from glob import glob
+
+
+def get_thick(atom_row):
+    pos = atom_row.positions[:, -1]
+    diff = covalent_radii[atom_row.numbers]
+    zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
+    return zmax
+
+
+def get_data_epfl(exclude=[]):
+    # Read QE result
+    eps_x = []; eps_z = []
+    alpha_x = []; alpha_z = []
+    materials = []
+    Eg_QE = []
+    Eg_VASP = []
+    thick = []
+    reader = csv.reader(open("../../data/EPFL-data/eps_EPFL.csv", encoding="utf8"))
+    next(reader)                    # skip line1
+    for row in reader:
+        if row[0] != "":
+            name = row[0]
+            print(name)
+            if name in exclude:
+                continue
+            mol_file = glob(os.path.join("../../data/EPFL-data/structures/",
+                                         "{0}-*.json".format(name)))
+            if len(mol_file) == 0:
+                print(name + " Not correct!")
+                continue
+            L, ex, ey, ez, eg_qe, eg_vasp = map(float, row[1:])
+            if ez < ex:
+                eps_z.append(ez)
+                materials.append("-".join((name, "QE")))
+                e_xy = numpy.sqrt(ex * ey)
+                ax = (e_xy - 1) / (4 * pi) * L
+                az = (1 - 1/ez) * L / (4 * pi)
+                # ax = max(1 / 1.2, ax)
+                eps_x.append(e_xy); eps_z.append(ez)
+                alpha_x.append(ax); alpha_z.append(az)
+                Eg_QE.append(eg_qe)
+                Eg_VASP.append(eg_vasp)
+                # if proto == "ABX3":
+                # thick.append(8.0)
+                # else:
[…]

### 2019-10-02 src/VASP_HSE/relation_alpha.py

@@ -3,11 +3,13 @@ import warnings
 import numpy
 import matplotlib.pyplot as plt
 from ase.data import covalent_radii
+from ase.io import read, write
 from scipy.stats import linregress
 from scipy.optimize import curve_fit
 import os, os.path
 from scipy.constants import pi, epsilon_0
 from gpaw_data import get_data
+from epfl_data import get_data_epfl, get_data_epfl2
 import scipy
 import csv
 
@@ -37,6 +39,8 @@ def get_thick(atom_row):
     zmax = numpy.max(pos + diff) - numpy.min(pos - diff)
     return zmax
 
+
+# REad VASP result
 reader = csv.reader(open("../../data/HSE-data/2D_HSE.csv", encoding="utf8"))
 next(reader)                    # skip line1
 for row in reader:
@@ -60,17 +64,20 @@ for row in reader:
                 mol = list(db.select(formula=name, prototype=proto))[0]
                 thick.append(get_thick(mol))
 
+
+
 print(len(alpha_x))
 alpha_x = numpy.array(alpha_x)
 alpha_z = numpy.array(alpha_z)
 Eg_HSE = numpy.array(Eg_HSE)
 thick = numpy.array(thick)
 
-cond = numpy.where(Eg_HSE > 0.6)
-Eg_HSE = Eg_HSE[cond]
-alpha_x = alpha_x[cond]
-alpha_z = alpha_z[cond]
-thick = thick[cond]
+# cond = numpy.where(Eg_HSE > 0.6)
+# materials = materials[cond]
+# Eg_HSE = Eg_HSE[cond]
+# alpha_x = alpha_x[cond]
+# alpha_z = alpha_z[cond]
+# thick = thick[cond]
 
 colors = {"MoS2": "#AA0000", "CdI2": "#2C5AA0",
           "GaS": "#FFCC00", "BN": "#A05A2C",
@@ -89,87 +96,82 @@ plt.style.use("science")
 # plt.scatter(Eg_HSE, alpha_x, marker="o", alpha=0.5, c=cs)
 def fit_func(x, a,b):
     return b / x
-'''
-fit_param, cov = curve_fit(fit_func,
[…]

### 2019-10-02 src/distance/alpha_convergence.py

@@ -1,0 +1,107 @@
+import numpy
+from scipy.optimize import curve_fit
+import os, os.path
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+from scipy.constants import pi
+from model_eps import plot_eps_para, plot_eps_perp
+plt.style.use("science")
+
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+# print(g)
+names = next(g)[1]
+# print(names)
+# names = sorted(names)
+gs = GridSpec(7, 1, hspace=0.3)
+fig1 = plt.figure(figsize=(3, 3.2))
+fig2 = plt.figure(figsize=(3, 3.2))
+ax1_r = fig1.add_subplot(gs[5:])
+ax1 = fig1.add_subplot(gs[:5 ])
+ax2_r = fig2.add_subplot(gs[5:])
+ax2 = fig2.add_subplot(gs[:5 ])
+
+colors = {"mos2": "#1f77b4",
+          "mose2": "#ff7f0e",
+          "mote2": "#2ca02c",
+          "ws2": "#d62728",
+          "wse2": "#9467bd",
+          "wte2": "#8c564b",
+}
+
+# plot_eps_para(ax1, alpha_0=8.5, dev=4)
+# plot_eps_perp(ax2, alpha_0=0.47, dev=0.15)
+
+for i, item in enumerate(g):
+    if "old" in item:
+        continue
+    for f in item[2]:
+        f_path = os.path.join(item[0], f)
+        if "agr" not in f_path:
+            continue
+        print(f_path)
+        data = numpy.genfromtxt(f_path,
+                                delimiter=" "
+                                # skip_header=297,
+                                # skip_footer=2
+         )
+        # data = data[1: , :]
+        L = data[:, 0]
+        eps_SL = data[:, 1]
+        if "parallel.agr" in f_path:
+            alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
+            error_alpha = numpy.abs(alpha_SL - alpha_SL[-1]) / alpha_SL[-1] 
+            l, *_ = ax1.plot(L, eps_SL, "o",
[…]

### 2019-10-02 src/distance/compare_eps_bse.py

@@ -33,14 +33,14 @@ def main(method="BSE", direction="in_plane"):
         ax.set_xlabel("Energy (eV)")
     if method == "GW":
         if direction == "in_plane":
-            lim = [8, 12]
+            lim = [0, 12]
         else:
-            lim = [13, 17]
+            lim = [0, 17]
     else:
         if direction == "in_plane":
-            lim = [6, 10]
+            lim = [0, 10]
         else:
-            lim = [11, 15]
+            lim = [0, 15]
     # for ax in [ax3, ax4]:
         # ax.set_xlim(6, )
     # Set ylabel

### 2019-10-02 src/distance/compare_eps_freq.py

@@ -34,14 +34,18 @@ def main(method="PBE", direction="in_plane"):
         ax.set_xlabel("Energy (eV)")
     if method == "GW":
         if direction == "in_plane":
-            lim = [8, 12]
+            lim = [0, 15]
         else:
-            lim = [13, 17]
+            # lim = [13, 17]
+            # lim = [13, 17]
+            lim = [0, 20]
     else:
         if direction == "in_plane":
-            lim = [4, 8]
+            # lim = [4, 8]
+            lim = [0, 12]
         else:
-            lim = [8, 12]
+            # lim = [8, 12]
+            lim = [0, 12]
     # for ax in [ax3, ax4]:
         # ax.set_xlim(6, )
     # Set ylabel
@@ -67,7 +71,7 @@ def main(method="PBE", direction="in_plane"):
         ax3.plot(freq, eps.imag, linewidth=1.25)
         ax4.plot(freq, alpha.imag, linewidth=1.25)
     l = ax1.legend()
-    l.set_title("{} $L$".format(dict(GW="G0W0", PBE="PBE")[method]))
+    l.set_title("{} $L$".format(dict(GW="G$_{0}$W$_{0}$", PBE="PBE")[method]))
     fig.tight_layout()
     fig.savefig("../../tmp_img/comparison-{}-{}.svg".format(method, direction))
     return

### 2019-10-02 src/multi-mx2/extract.py

@@ -1,0 +1,93 @@
+import numpy
+from scipy.optimize import curve_fit
+from scipy.stats import linregress
+import os
+import os.path
+from os.path import exists, join, abspath, dirname
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+from scipy.constants import pi
+# from model_eps import plot_eps_para, plot_eps_perp
+import re
+import ase, ase.io
+plt.style.use("science")
+
+
+root = "../../data/multi-mx2/"
+
+colors = {"mos2": "#1f77b4",
+          "mose2": "#ff7f0e",
+          "mote2": "#2ca02c",
+          "ws2": "#d62728",
+          "wse2": "#9467bd",
+          "wte2": "#8c564b",
+          }
+
+
+def get_eps_matrix(mater, n):
+    work_dir = join(root, "{0}/{1}/eps".format(mater, n))
+    outcar = join(work_dir, "OUTCAR.COMPLETE")
+    assert exists(outcar)
+    pattern = "".join((r"MACROSCOPIC STATIC DIELECTRIC TENSOR ",
+                       r"\(including local field effects in DFT\)",
+                       r"[\s\n]+[-]{20,}\n(.+?)[-]{20,}"))
+    content = open(outcar, "r").read()
+    matches = re.findall(pattern, content, re.DOTALL)
+    assert(len(matches) > 0)    # At least one calculated!
+    eps_string = matches[-1]
+    eps_matrix = numpy.fromstring(eps_string.strip(),
+                                  dtype="float",
+                                  sep=" ")
+    assert eps_matrix.shape[0] == 9
+    eps_matrix = eps_matrix.reshape(3, 3)    # Reshape to Tensor
+    return eps_matrix
+
+
+def get_lattice_L(mater, n):
+    work_dir = join(root, "{0}/{1}/eps".format(mater, n))
+    poscar = join(work_dir, "POSCAR")
+    assert exists(poscar)
+    atoms = ase.io.read(poscar, format="vasp")
+    L = atoms.get_cell()[-1, -1]
+    return L
+
+
+fig = plt.figure(figsize=(5, 2.5))
+ax1 = fig.add_subplot(121)
+ax2 = fig.add_subplot(122)
+
+n_range = numpy.arange(1, 7)
[…]

### 2019-10-02 src/VASP_HSE/ellipsoid.py
Add ellipsoid figure

@@ -1,0 +1,74 @@
+import matplotlib.pyplot as plt
+import numpy
+import json
+from scipy.constants import pi, k, epsilon_0, e
+
+data = json.load(open("../../data/HSE-data/all_data.json", "r"))
+
+def model_alpha(x, ratio=0.1657):
+    return 1 / ( ratio * x - 0.0243)
+
+maters = []
+alpha = []
+Eg = []
+
+# for entry in data:
+#     if entry["gap_2D"] is not None:
+#         if entry["prototype"] == "MoS2":
+#             prefix = "2H-"
+#         elif entry["prototype"] == "CdI2":
+#             prefix = "1T-"
+#         else:
+#             prefix = ""
+#         maters.append("{0}{1}".format(prefix, entry["name"]))
+#         alpha.append([entry["alphax_2D"], entry["alphaz_2D"]])
+#         Eg.append(entry["gap_2D"])
+
+# alpha = numpy.array(alpha)
+# Eg = numpy.array(Eg)
+
+fig = plt.figure(figsize=(5.5, 2.5))
+plt.style.use("science")
+
+names = ["2H-MoS2", "2H-MoSe2", "2H-MoTe2",
+         "2H-WS2", "2H-WSe2", "2H-WTe2"]
+xx = numpy.arange(6)
+
+r_para = [40.0, 45.5, 58.1, 35.7, 41.0, 53.5]
+r_perp = [2.50, 2.72, 3.07, 2.46, 2.71, 3.17]
+
+
+ax1 = fig.add_subplot(121)
+ax2 = fig.add_subplot(122)
+
+# res = sorted(zip(Eg, alpha, maters))
+# maters = [n for e, a, n in res]
+# ax = [max(a[0], 1/1.2) for e, a, n in res]
+# az = [a[1] for e, a, n in res]
+# Eg = [e for e, a, n in res]
+
+# xx = numpy.arange(0, len(maters))
+
+# for r in numpy.linspace(0.12, 0.20, 100):
+    # a_model = model_alpha(numpy.array(Eg), r)
+    # ax1.plot(xx +0.5, a_model, color="cyan",
+             # alpha=0.2)
+
+ax1.bar(xx, r_para, width=0.5, color="#559dc9")
+ax2.bar(xx, r_perp, width=0.5, color="#d9ad66")
+
[…]

### 2019-10-02 src/multi-mx2/extract.py
Update Figure 4

@@ -52,7 +52,7 @@ def get_lattice_L(mater, n):
     return L
 
 
-fig = plt.figure(figsize=(5, 2.5))
+fig = plt.figure(figsize=(4.8, 2.4))
 ax1 = fig.add_subplot(121)
 ax2 = fig.add_subplot(122)
 
@@ -75,17 +75,22 @@ for m in ["Mo", "W"]:
             alpha_perp.append(alpha_perp_)
         alpha_para = numpy.array(alpha_para)
         alpha_perp = numpy.array(alpha_perp)
-        k_para, b_para, *_ = linregress(x=n_range, y=alpha_para)
-        k_perp, b_perp, *_  = linregress(x=n_range, y=alpha_perp)
-        l1, = ax1.plot(n_range, alpha_para, "o", markersize=4, label=mater)
-        l2, = ax2.plot(n_range, alpha_perp, "o", markersize=4, label=mater)
+        k_para, b_para, *_1 = linregress(x=n_range, y=alpha_para)
+        k_perp, b_perp, *_2  = linregress(x=n_range, y=alpha_perp)
+        print(b_para, _1, b_perp, _2)
+        l1, = ax1.plot(n_range, alpha_para, "o", markersize=5, label="2H-" + mater.replace("2", "$_{2}$"))
+        l2, = ax2.plot(n_range, alpha_perp, "o", markersize=5, label="2H-" + mater.replace("2", "$_{2}$"))
         ax1.plot(ext_n, k_para * ext_n + b_para, "--", color=l1.get_c())
         ax2.plot(ext_n, k_perp * ext_n + b_perp, "--", color=l2.get_c())
 
 ax1.set_xlabel("Number of Layers ($N$)")
-ax1.set_ylabel("$\\alpha_{\\rm{2D}}^{\\parallel}/(4 \\pi \\varepsilon_0)$ ($\\mathrm{\\AA}$)")
+ax1.set_ylabel("$\\alpha_{\\rm{NL}}^{\\parallel}/(4 \\pi \\varepsilon_0)$ ($\\mathrm{\\AA}$)")
 ax2.set_xlabel("Number of Layers ($N$)")
-ax2.set_ylabel("$\\alpha_{\\rm{2D}}^{\\perp} / (4 \\pi \\varepsilon_0)$ ($\\mathrm{\\AA}$)")
[…]

### 2019-10-02 SI.tex
Add figures up to figure 5

@@
 Here we will show the results of dielectric properties calculated
-using many-body Green function method (G$_0$W$_{0}$) and with
+using many-body Green function method (G$_{0}$W$_{0}$) and with
 electron-hole interactions at the level of the Bethe-Salpeter equation
-(G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
-$\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
-are calculated using VASP, with a cutoff energy of XXX and k point
-density of YYY. Local field effect is included in both cases: local
-field correction is applied to independent-particle energies in G0W0
-at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
-polarizability is calculated using BSE in G0W0-BSE
-\todo[inline]{@Declan, could you help modify this part?}
+(G$_{0}$W$_{0}$–BSE). Frequency-dependent dielectric functions,
+$\varepsilon_{\mathrm{SL}}(L)$, were calculated at the level of
+G$_{0}$W$_{0}$ and G$_{0}$W$_{0}$+BSE levels using VASP. For the
+calculations on G$_{0}$W$_{0}$, a 12$\times$12$\times$1 $\Gamma$-centered k-grid was
+used along with an 800 eV energy cutoff in the plane waves and in
+calculation of the response function. 120 bands (4 occupied and 116
+unoccupied) were used in the calculation of
+$\varepsilon_{\mathrm{SL}}(\omega)$ of monolayer BN, with local-field
+effects being included on the RPA level. For the calculation of the
+Bethe-Salpeter equation, the Tamm-Dancoff approximation was used with
+two occupied and two unoccupied bands being included in the
+calculation.
+
+% Here we will show the results of dielectric properties calculated
+% using many-body Green function method (G$_0$W$_{0}$) and with
+% electron-hole interactions at the level of the Bethe-Salpeter equation
+% (G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
+% $\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
+% are calculated using VASP, with a cutoff energy of XXX and k point
+% density of YYY. Local field effect is included in both cases: local
+% field correction is applied to independent-particle energies in G0W0
+% at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
+% polarizability is calculated using BSE in G0W0-BSE
+% \todo[inline]{@Declan, could you help modify this part?}
 

### 2019-10-02 paper.tex
Add figures up to figure 5

--- 2019-03-14 paper.tex
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
+  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
+      ``dielectric constant'' picture based on the effective medium
+      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
+    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
+    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
+    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
+    not well-defined. \textbf{b}.  Estimation error between
+    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
+    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
+    of /ab initio/ $\varepsilon_{\mathrm{SL}} - L$ data for selected
+    2D metal dichacolgenides. The uncertainty of
+    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
+    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
+    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
+\end{figure}
+
 % \begin{figure}[htbp]
@@
   revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
-  as superimposed on \textbf{c} and \textbf{d}.}
+  and Ref.~\cite{Mounet_2018} (triangles) as superimposed on
+  \textbf{c} and \textbf{d}.}
 \end{figure}
 
-\begin{table}[H]
-  \centering
-  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
-    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
-    selected 2D materials calculated from first principles
-    simulations. $r_{0}^{\parallel}$ is in general much larger than
-    $r_{0}^{\perp}$, which accounts for the highly anisotropic
-    dielectric nature of 2D materials.}
-  \label{tbl:radii}  
-  \begin{tabular}{lcc}
-    \hline
-    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
-    \hline
-    2H-MoS$_{2}$ & 40.0 & 2.50 \\
-    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
-    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
-    2H-WS$_{2}$ & 35.7 & 2.46  \\
-    2H-WSe$_{2}$ & 41.0 & 2.71 \\
-    2H-WTe$_{2}$ & 53.5 &  3.17\\
-    \hline
-  \end{tabular}
-\end{table}
+% \begin{table}[H]
+%   \centering
+%   \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
+%     ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
+%     selected 2D materials calculated from first principles
+%     simulations. $r_{0}^{\parallel}$ is in general much larger than
+%     $r_{0}^{\perp}$, which accounts for the highly anisotropic
+%     dielectric nature of 2D materials.}
+%   \label{tbl:radii}  
+%   \begin{tabular}{lcc}
+%     \hline
+%     Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
+%     \hline
+%     2H-MoS$_{2}$ & 40.0 & 2.50 \\
+%     2H-MoSe$_{2}$ & 45.5 & 2.72  \\
+%     2H-MoTe$_{2}$ & 58.1 & 3.07  \\
+%     2H-WS$_{2}$ & 35.7 & 2.46  \\
+%     2H-WSe$_{2}$ & 41.0 & 2.71 \\
+%     2H-WTe$_{2}$ & 53.5 &  3.17\\
+%     \hline
+%   \end{tabular}
+% \end{table}
 
@@
 \includegraphics[width=0.9\linewidth]{img/fig4.pdf}
-\caption{\label{fig-4} \textbf{Transition of dielectric properties
-    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
+\caption{\label{fig-4} \textbf{Application of 2D polarizability to
+    multilayer and 3D systems}.  \textbf{a}. Scheme for the 2D-3D
   transition. $\alpha$ in the 2D material is essentially equivalent to
-  $\varepsilon$ in its bulk counterpart. \textbf{b}
+  $\varepsilon$ in its bulk counterpart.  By applying the concept of
+  electronic polarizability to multilayer 2D materials, the multilayer
+  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
+  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal dichacolgenides
+  as functions of number of layers $N$ are shown in \textbf{a} and
+  \textbf{b}, respectively. Both $\alpha_{\mathrm{NL}}^{\parallel}$
+  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
+  electronic polarizabilities of monolayer, indicating that
+  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
+  interacting regime. The 2D to 3D transition is further studied in
+  \textbf{c} and \textbf{d}, where $\alpha_{\mathrm{2D}}$ of an
+  monolayer 2D material is compared with its bulk counterpart
+  $\varepsilon_{\mathrm{Bulk}}$. \textbf{c}
   $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
   (y-axis) compared with the predicted value from 2D
-  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
-  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
-  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
-  (x-axis). The predicted value is in good aggreement with the DFT
-  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
-  coupling. The comparisons in \textbf{b} and \textbf{c} are made
-  based on both HSE06 (circles) and PBE (squares) functionals.}
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good
+  correlation. \textbf{d} $\varepsilon_{\mathrm{bulk}}^{\perp}$
+  calculated from DFT (y-axis) compared with the predicted value from
+  2D $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis). The predicted value
+  is in good aggreement with the DFT calculation when
+  $E_{\mathrm{g}}>4$ eV, due to minimal interlayer coupling. The
+  comparisons in \textbf{b} and \textbf{c} are made based on both
+  HSE06 (circles) and PBE (squares) functionals.}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width-0.8\linewdith]{img/fig-ellipsoid.pdf}
+  \caption{\label{fig-ellip} \textbf{Geometric representation of the
+      2D polarizability}. \textbf{a}. Scheme of the polarizability
+    ellipsoid of a 2D material, with its in-plane
+    ($r_{0}^{\parallel}$) and out-of-plane radii
+    ($r_{\mathrm{0}}^{\perp}$) proportional to
+    $\alpha_{\mathrm{2D}}^{\parallel}$ and
+    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
+    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D metal
+    dichalcogenides are shown in \textbf{b} and \textbf{c},
+    respectively.  }
 \end{figure}

### 2019-10-02 src/distance/compare_emt.py

@@ -1,0 +1,199 @@
+import numpy
+from scipy.optimize import curve_fit, fsolve
+import os, os.path
+import matplotlib.pyplot as plt
+from scipy.constants import pi
+plt.style.use("science")
+
+def fit_para(L, d, eps_2D):
+    return (eps_2D - 1) * d / L  + 1
+
+def fit_vert(L, d, eps_2D):
+    return 1 / (d / L * (1 / eps_2D - 1) + 1)
+
+root = "../../data/distance/"
+g = os.walk(root)
+names = next(g)[1]
+tags = {
+    "mos2": "MoS$_{2}$",
+    "mose2": "MoSe$_{2}$",
+    "mote2": "MoTe$_{2}$",
+    "ws2": "WS$_{2}$",
+    "wse2": "WSe$_{2}$",
+    "wte2": "WTe$_{2}$",
+}
+
+limits = {
+    "mos2": (4.98, 6.15),
+    "mose2": (5.60, 6.46),
+    "mote2": (6.12, 6.98),
+    "ws2": (5.00, 6.15),
+    "wse2": (5.42, 6.49),
+    "wte2": (6.33, 7.06),
+}
+
+# limits = {
+    # "mos2": (5.22, 6.15),
+    # "mose2": (5.73, 6.46),
+    # "mote2": (6.37, 6.98),
+    # "ws2": (5.20, 6.15),
+    # "wse2": (5.75, 6.49),
+    # "wte2": (6.38, 7.06),
+# }
+
+raw_data_para = dict()
+raw_data_perp = dict()
+fit_all_para = dict()               # eps_2D, delta
+fit_all_perp = dict()               # eps_2D, delta
+
+def combine_data():
+    for i, item in enumerate(g):
+        if "old" in item:
+            continue
+        for f in item[2]:
+            f_path = os.path.join(item[0], f)
+            if "agr" not in f_path:
+                continue
+            print(f_path)
+            data = numpy.genfromtxt(f_path,
+                                    delimiter=" "
+                                    # skip_header=297,
+                                    # skip_footer=2
+             )
+            L = data[:, 0]
+            eps_SL = data[:, 1]
+            if "par" in f_path:
+                raw_data_para[names[i]] = (L, eps_SL)
+                param, _ = curve_fit(fit_para, L[1:], eps_SL[1:],
+                                     p0=(5, 10),
[…]

### 2019-10-02 paper.tex
Add captions for new figures

@@
 
+Add Mounet paper \cite{Mounet_2018}
+
 \section{Data Availability}
@@
     $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
-    of /ab initio/ $\varepsilon_{\mathrm{SL}} - L$ data for selected
-    2D metal dichacolgenides. The uncertainty of
+    of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
+    2D TMDCs. The uncertainty of
     $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
@@
   revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
-  and Ref.~\cite{Mounet_2018} (triangles) as superimposed on
+  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
   \textbf{c} and \textbf{d}.}
@@
 \caption{\label{fig-4} \textbf{Application of 2D polarizability to
-    multilayer and 3D systems}.  \textbf{a}. Scheme for the 2D-3D
+    multilayer and bulk systems}.  \textbf{a}. Scheme for the 2D-3D
   transition. $\alpha$ in the 2D material is essentially equivalent to
@@
   \centering
-  \includegraphics[width-0.8\linewdith]{img/fig-ellipsoid.pdf}
+  \includegraphics[width=0.8\linewidth]{img/fig-ellipsoid.pdf}
   \caption{\label{fig-ellip} \textbf{Geometric representation of the
@@
     $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
-    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D metal
-    dichalcogenides are shown in \textbf{b} and \textbf{c},
-    respectively.  }
+    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D TMDCs are
+    shown in \textbf{b} and \textbf{c}, respectively.  The
+    polarizability ellipsoid is highly anisotropic with screening much
+    larger at in-plane direction than out-of-plane direction.}
 \end{figure}
@@
 \end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-10-02 paper.tex
Update main and SI

@@
 % \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
+
+\keywords{Dielectric property, electronic polarizability, two-dimensional material, scaling relation, first principles simulations, dielectric anisotropy}
+
+\begin{tocentry}
+  \centering
+ \includegraphics[height=3.5cm]{img/toc.pdf}
+\end{tocentry}
+
 \begin{document}
@@
 
-{\bfseries The dielectric constant, which defines the polarization of
+\begin{abstract}
+  The dielectric constant, which defines the polarization of
   the media, is a key quantity in condensed matter. It determines
@@
   anisotropy index defining their controllability through
-  dimensionality.  }
+  dimensionality.
+\end{abstract}
 

### 2019-10-02 convert.py

@@ -32,7 +32,7 @@ def convert_pdf(infile, outdir="./img"):
     ]
     io = ["--file={}".format(infile),
           "--export-png={}".format(outfile),
-          "--export-dpi=600"]
+          "--export-dpi=150"]
     success = subprocess.call([program, *params, *io])
     
     if success != 0:

### 2019-10-03 paper.tex
Change up to subsection1

@@
 
-\keywords{Dielectric property, electronic polarizability, two-dimensional material, scaling relation, first principles simulations, dielectric anisotropy}
+\keywords{Dielectric screening, electronic polarizability, two-dimensional material, scaling relation, first principles simulations, dielectric anisotropy}
 
@@
   several electronic and optoelectronic properties important for a
-  plethora of modern technologies from computer memory to field effect
-  transistors and communication circuits. Moreover, the importance of
-  the dielectric constant in describing electromagnetic interactions
-  through screening plays a critical role in understanding fundamental
-  molecular interactions. Here we show that despite its fundamental
+  plethora of modern technologies, and its importance of 
+  % from computer memory to field effect
+  % transistors and communication circuits. Moreover, the importance of
+  % the dielectric constant in
+  describing electromagnetic interactions through screening plays a
+  critical role in understanding fundamental molecular
+  interactions. Here we show that despite its fundamental
   transcendence, the dielectric constant does not define unequivocally
   the dielectric properties of two-dimensional (2D) materials due to
-  the locality of their electrostatic screening. Instead, the electric
-  polarizability correctly captures the dielectric nature of a 2D
-  material which is united to other physical quantities in an
-  atomically thin layer. We reveal a long-sought universal formalism
-  where electronic, geometrical and dielectric properties are
-  intrinsically correlated through the polarizability opening the door
-  to probe quantities yet not directly measurable including the real
-  covalent thickness of a layer. We unify the concept of dielectric
-  properties in any material dimension finding a global dielectric
-  anisotropy index defining their controllability through
-  dimensionality.
+  the locality of their electrostatic screening. Instead, the
+  electronic polarizability correctly captures the dielectric nature
+  of a 2D material which is united to other physical quantities in an
+  atomically thin layer. Being a quantity with unique definition, the
+  electronic polarizability overcomes the disadvantage of uncertainty
+  posed by the effective dielectric constant model conventionally used
+  to described screening in 2D material systems.  Furthermore, we
+  reveal a long-sought universal formalism where electronic,
+  geometrical and dielectric properties are intrinsically correlated
+  through the polarizability opening the door to probe quantities yet
+  not directly measurable including the real covalent thickness of a
+  layer. Lastly, we unify the concept of dielectric properties in any
+  material dimension finding a global dielectric anisotropy index
+  defining their controllability through dimensionality.
 \end{abstract}
+
+\pagebreak{}
+
+\section{Introduction}
+\label{sec:introduction}
 
@@
 The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
-theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
-is made through an external electric field. 
+theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
+% where the probe of the dielectric properties 
+% is made through an external electric field. 
 %
 Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
-electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
+% electronic and
+dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
 %
-The confined nature of the electrons in such atomically thin space associated with the 
-attenuated and anisotropic character of the dielectric screening of 2D crystals 
+The confined nature of such atomically-thin 2D crystals associated
+with the attenuated and anisotropic character of the dielectric
+screening
 \cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
 have generated long-standing debates whether the dielectric constant
-may represent their dielectric features or it can be used only as an 
-additional parameter from the bulk-counterparts.
+truly represents dielectric features of such low-dimensional systems,
+% or it can be used only as an
+% additional parameter from the bulk-counterparts.
+The controversy of
+$\varepsilon$ values reported by both theoretical and experimental
+approaches can be widely seen throughput literature\cite{Li_2016},
+where the variation of $\varepsilon$ can be more than one order of
+magnitude. As a consequence, several key physical parameters that
+scales with $\varepsilon$, such as the exciton binding energy and
+Debye screening length, cannot be reliably estimated due to the
+discrepancy of reported $\varepsilon$ values. In this letter, we give
+a thorough study of the underlying issue. Using \textbf{ab initio}
+simulations of a model system, we demonstrate that the macroscopic
+dielectric constant strongly depends on the size of the superlattice,
+making it unsuitable to describe the screening of a 2D material. On
+the contrary, by analyzing the formalism of dielectric tensors, we
+propose that the electronic polarizability is the true descriptor
+which uniquely captures the dielectric nature of 2D materials. The 2D
+electronic polarizability has unique definition, which overcomes the
+disadvantage of ambiguity compared with the conventionally used
+effective dielectric medium model for 2D materials. Moreover, we show
+the universal scaling relations for in- and out-of-plane 2D electronic
+polarizabilities with the electronic and geometric information of the
+2D material. The concept of electronic polarizabilities bridges the
+gap between the dielectric properties of 2D and 3D systems, and can be
+extended to characterize the dielectric anisotropy for any material
+dimensions.
 
@@
 %%
-We approach this problem showing that the current definition of
-$\varepsilon$ used in layered materials is ill defined as illustrated
-in Figure \ref{fig-1}.  From the theoretical point of view, an
-isolated 2D material is placed in the \textit{xy}-plane of a
-periodically repeating superlattice (SL) with a length $L$ along the
-\textit{z}-direction separating the cell images. The static macroscopic
-dielectric tensor from the superlattice
+
+\section{Results and discussions}
+\label{sec:results-discussions}
+
+\subsection{Lattice-dependency of macroscopic dielectric constant}
+\label{sec:latt-depend-macr}
+
+We first approach the discrepancy of macroscopic dielectric constant
+of 2D materials, by showing that the current definition of
+$\varepsilon$ used in layered materials is ill defined.  This can be
+viewed in a model system as illustrated
+in Figure \ref{fig-1}, where an isolated 2D material is placed in
+the \textit{xy}-plane of a periodically repeating superlattice (SL)
+with a length $L$ along the \textit{z}-direction separating the cell
+images. The static macroscopic dielectric tensor from the superlattice
 $\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
@@
 polarization and electric field,
-respectively\cite{Dressel_2001_electrodynamics}:
+respectively~\cite{Dressel_2001_electrodynamics}:
 \begin{subequations}
@@
       \label{eq:def-eps-1}
-    &\varepsilon^{pq} &= \kappa^{pq} +
+    &\varepsilon_{\mathrm{SL}}^{pq} &= \kappa^{pq} +
                                  {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
@@
 where $\kappa$ is the dielectric tensor of the environment,
-$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is
+$\boldsymbol{u}$ is the total dipole moment within the SL, $\rho$ is
 the spatial charge density, $\Omega=AL$ is the volume of the
 supercell, $A$ is the \textit{xy}-plane area of the SL and
-$\varepsilon_{0}$ is vacuum permittivity. Here we only study the
-electronic contribution to the macroscopic dielectric constant where
-the dipole $\boldsymbol{P}$ comes from the displacement of electron
-cloud under external electric field, while the ionic contribution
-\cite{Laturia_2018} ($\boldsymbol{P}$ comes from the displacement of
-nuclei) to the static $\varepsilon$ is not considered.
-For the majority of the 2D nanosheets, the
-off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
-negligible.  Considering that the 2D material is placed in vacuum
-($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
-components of $\varepsilon$, namely the in-plane
-($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
+$\varepsilon_{0}$ is vacuum permittivity. Here we limit out study on
+the electronic contribution to the macroscopic dielectric constant
+where the dipole $\boldsymbol{P}$ comes from the displacement of
+electrons under external field.  On the other hand, the ionic
+contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
+displacement of atomic nuclei is not covered in this due to its
+complex dependency on several factors including phonon
+dispersion~\cite{Sohier_2017} as well as lattice
+symmetry~\cite{Laturia_2018}, which requires separated discussions.
+The symmetry of 2D materials lead to the negligible off-diagonal
+elements of the dielectric tensor ($p \neq q$), while and diagonal
+elements $\varepsilon_{\mathrm{SL}}^{xx}$,
+$\varepsilon_{\mathrm{SL}}^{yy}$ and $\varepsilon_{\mathrm{SL}}^{zz}$
+can be different \cite{Sohier_2016}.  Considering that the 2D material
+is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
+distinguish two components of $\varepsilon_{\mathrm{SL}}$, namely the
+in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
 ($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
@@
 The absence of bonding perpendicular to the plane confines the induced
-dipoles along the \textit{z}-direction in a range of 
-$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and
-Supplementary Figure \ref{SI-fig:rho-profile}). 
+dipoles along the \textit{z}-direction within a range of $\sim{}$5--6
+\AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and Supplementary
+Figure \ref{SI-fig:rho-profile}).
 %
 %
-When $L$ is large
-enough, the induced dipoles $\boldsymbol{u}$ from the periodic images
-do not interact mutually as the integral in Eq. \ref{eq:def-eps-2}
-depends only locally on the atomic charge density at the layer.
-However, we can see from Eq. \ref{eq:def-eps-1} that both
+Under a certain external field, when $L$ increases, the confinement of
+the induced dipole moment $\boldsymbol{u}$ causes the integral in the
+numerator of Eq.~\ref{eq:def-eps-2} to be saturated, when the
+separation is large enough such that dipole moment from periodic
+images do not mutually interfere. On the other hand, the increase of
+$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the polarization density, and in turn makes both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
-the cell $\Omega$. In the case of bulk materials such physical dependence 
-is well described given the periodicity of the 3D crystal throughout the space.  
+$\varepsilon^{\perp}_{\mathrm{SL}}$ dropping to
+unity when $L$ is infinitely large.
+% In the case of bulk materials
+% such physical dependence is well described given the periodicity of
+% the 3D crystal throughout the space.
 %
@@
 %
-In the case of 2D materials, however, such repetition is artificial along the direction 
-perpendicular to the plane. Despite of the simplicity of this argument,  
-any calculation performed using such
-definition will intrinsically depend on the magnitude of $L$ as an
-additional parameter. This dependence can be clearly demonstrated by
-plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
+% In the case of 2D materials, however, such repetition is artificial along the direction 
+% perpendicular to the plane.
+Despite of the simplicity of this argument, any calculation performed
+using such definition will intrinsically depend on the magnitude of
+$L$, an artificial parameter introduced by simulation system. This
+dependence can be clearly demonstrated by plotting
+$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
-theory (DFT) using hybrid functionals (see {\it Theoretical Methods} for details)
-as a function of $L$ for P$\bar{6}$m2 transition metal
-dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
-(top panels of Figure \ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c},
-respectively). Both components of the dielectric constant 
-change systematically with $L$ without a clear convergence. 
-%
-Simulations performed at higher levels of theory using many-body
-techniques, G$_{\rm 0}$W$_{0}$, invariably give alike results (see
-Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).  We have also
-undertaken similar analysis into the frequency ($\omega$) regime for
+theory (DFT) (see {\it Theoretical Methods} for details) as a function
+of $L$ for P\={6}m2 transition metal dichalcogenides (TMDCs),
+2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te (top panels of Figure
+\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c}, respectively). To
+get a better description of the electronic band structure, the
+calculations of dielectric properties were performed at the level of
+Heyd-Scuseria-Ernzerhof (HSE06) hybrid functional
+\cite{Heyd_2003,Heyd_2006}.  Both components of the dielectric
+constant decreases with $L$ as excepted. To rule out the possibility
+that the result is affected by the choice of \textbf{ab initio}
+methods, we also performed simulations at higher levels of theory
+using many-body techniques (G$_{0}$W$_{0}$), which invariably give
+alike results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).
+The lattice-size dependency also exists for dielectric function in the
+frequency ($\omega$) domain. We carried out similar analysis for
+frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
+and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, as seen in
+Supplementary Section \ref{SI-ssec:gw}. Despite the different levels
+of techniques used (Perdew-Burke-Ernzerhof (PBE) exchange-correlation
+functional \cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, HSE06 hybrid
+functionals or G\textsubscript{0}W\textsubscript{0} method), the
+magnitude of dielectric functions calculated universally decreases
+with $L$ over the frequency domain.  These results indicate that
+quantities that depend on
 $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where the $L$-dependence
-remains present despite various methods utilized (see Supplementary
-Section \ref{SI-ssec:gw} for a systematic study).  These results
-indicate that quantities that depend on
-$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, the optical
-absorption, suffer the same deficiencies.
-%
-% Moreover, due to the long range Coulomb
-% interaction, variations of the quasi-particle energy (and
-% corresponding peak positions) with lattice constant $L$ at the
-% G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
-% SXX). Such results implicate that several other related quantities,
-% including the optical absorption and optical conductivity, suffer the
-% same deficiencies, which should be avoided in a fully first principles
-% theory.
-%
-%
-%
-%as the computation of the dielectric function is based on alike formalism\cite{Ehrenreich-Cohen paper}
-% We can understand this behavior in terms of the electrostatic of the problem. 
-%
-%
-%
-%This result indicates that the use of the dielectric constant to represent 
-%dielectric properties at the static limit of a 2D material is 
-%ambiguous as the long-range correlations between the layers would only 
-%be negligible at the limit of $L \rightarrow \infty$, which incidentally modify the magnitudes of 
-%$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ in the convergence. 
-%
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
+absorption and electron energy loss spectrum (EELS), suffers the same
+deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
+simple model system explains the origin of the discrepancy of dielectric constant values reported in previous literature~\cite{Li_2016}.
+
+{\color{magenta}
 It is worth mentioning that experimental dielectric results of 2D
@@
 \ref{SI-sec:2D-3D-rescale}).
+}
 %
@@
 
-To solve this problem, we need to find the $L$-independent alternative
-of $\varepsilon_{\mathrm{SL}}$, which is related to both electrostatic
-and optical properties of a 2D material \cite{Matthes_2016}. As
-described before, by multiplying Eq.~\ref{eq:def-eps-2} with $L$ we
-obtain the sheet polarization density
-$\boldsymbol{\mu}_{\mathrm{2D}}$, that is,
-$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, which is
-independent of $L$ due to the locality of $\boldsymbol{u}$ and $A$.
+\subsection{The electronic polarizability of 2D materials}
+\label{sec:electr-polar-2d}
+
+To solve the problem described above, we need to find the
+$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
+related to both electrostatic and optical properties of a 2D
+material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
+with $L$, we obtain the sheet polarization density that is,
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, in
+direction $p$. Following the discussion in the previous section,
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of lattice
+size when $L$ is large enough, due to the saturation of
+$\boldsymbol{u}^{p}$.
 %
-Similar to the definition of molecular polarizability
-\cite{Israelachvili_2011}, $\boldsymbol{\mu}_{\mathrm{2D}}$ is
-associated with the 2D polarizability $\alpha_{\mathrm{2D}}$ through:
+Similar to the molecular polarizability \cite{Israelachvili_2011}, we
+can define a 2D electronic polarizability $\alpha_{\mathrm{2D}}$ which
+characterizes the ability to induce dipole moment of a 2D material. It
+is associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
 $\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
@@
 \cite{T_bik_2004}, where $\boldsymbol{E}_{\mathrm{loc}}$ is the local
-electric field. Using electrostatic boundary conditions, the
-continuity of the electric field along the in-plane direction gives
-$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
-\cite{Markel_2016}. For the out-of-plane component, the dipole
-screening yields
+electric field causing the polarization. At $L \rightarrow \infty$
+limit, $E_{\mathrm{loc}}$ can be solved using electrostatic boundary
+conditions of slab geometry \cite{Markel_2016}. The continuity of the
+electric field along the in-plane direction gives
+$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
+while for the out-of-plane component, the dipole screening yields
 $\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
-\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
-Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D
-polarizabilities, $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ with
-$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+\cite{Meyer_2001_dipole_slab,T_bik_2004}, where
+$\boldsymbol{E}^{\parallel}$ and $\boldsymbol{E}^{\perp}$ are the
+external field in the in-plane and out-of-plane directions,
+respectively. Combining with Eqs. \ref{eq:def-eps-1} and
+\ref{eq:def-eps-2},
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+can be related with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
 $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
@@
 \end{subequations}
-Note due to the choice of $\varepsilon$ is limited to the electronic
-macroscopic dielectric constant, $\alpha_{\mathrm{2D}}$ naturally
-refers to the electronic polarizability (the polarizability of the
-electron cloud \cite{Israelachvili_2011}). We also note that such
+% 20191003-16:00
+% As pointed before, as we limit the discussion on electronic contributions to the dielectric properties, $\alpha_{\mathrm{2D}}$ characterizes the polarizability of electron cloud of a 2D materials.
+% refers to the electronic polarizability (the polarizability of the
+% electron cloud \cite{Israelachvili_2011}).
+{\color{magenta} We also note that such
 approach is essentially different from the effective medium theory
@@
 Section \ref{SI-sec:2D-3D-rescale}.
+}
 %
 %
-The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
+Using these relations, we show the calculated
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-of the selected TMDCs as a function of $L$, calculated using
-Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
-that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
-convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
+of the selected TMDCs as a function of $L$ in the bottom panels of
+Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
+$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
+{\color{red} Convergence plot in SI} Such result is in good agreement
+with the spatially localized induced dipole moment of a 2D materials
+as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
 %
@@
 I think it is better not to explicitly mention this.}
-Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
-the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Section \ref{SI-ssec:gw}). 
+Such relations can also be used to remove the dependence on $L$ for
+frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
+and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
+lattice-independent electronic polarizability
+$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
+$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
+respectively (details see Supplementary Section \ref{SI-ssec:gw}).
 %
@@
 % 
-These findings provide that the 2D polarizability captures the essence
-of the dielectric properties of layered materials as the microscopic
-quantity in describing the atomic interactions present in the
-layers. Its local nature removes the dependence on size effects
-present in the calculations.  More discussions about the choice of the
+These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
+of the dielectric properties of 2D materials.
+In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
+More discussions about the choice of the
 2D polarizability, comparison with other methods, simulations at the

### 2019-10-03 paper.tex
Update until subpagraph 3

@@
 simple model system explains the origin of the discrepancy of dielectric constant values reported in previous literature~\cite{Li_2016}.
-
-{\color{magenta}
-It is worth mentioning that experimental dielectric results of 2D
-materials generally need to define an ``effective thickness'' of the sheet
-to interpret ellipsometry data
-\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
-transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
-extract information for the real part of the dielectric functions.  We
-argue that such procedure may induce inevitably variations of the
-results as the thickness is normally chosen by the interlayer spacing
-of the respective bulk materials (see Supplementary Section
-\ref{SI-sec:2D-3D-rescale}).
-}
 %
@@
 % electron cloud \cite{Israelachvili_2011}).
-{\color{magenta} We also note that such
-approach is essentially different from the effective medium theory
-\cite{Aspnes_1982,Markel_2016} (EMT) treatment of 2D materials, in
-which the hypothetical effective dielectric constant of 2D materials
-$\varepsilon_{\mathrm{2D}}$ are extracted from the macroscopic
-dielectric constant \cite{Matthes_2016,Laturia_2018}, from
-pre-determined 2D layer thickness $\delta$. The 2D electronic
-polarizability approach solves the issue of overestimation in the EMT
-approach, and $\alpha_{\mathrm{2D}}$ has an umambiguous physical
-meaning. Detailed discussions about the different between the 2D
-polarizability and the EMT approach, can be found in Supplementary
-Section \ref{SI-sec:2D-3D-rescale}.
-}
+
 %
@@
 
+\subsection{Comparison with effective dielectric model}
+\label{sec:comp-with-effect}
+
+Apart from the 2D electronic polarizability proposed here, it is worth
+mentioning that a widely-used approach in literature is to treat the
+2D material as a slab with an effective dielectric tensor
+$\varepsilon_{\mathrm{2D}}$ and thickness $\delta_{\mathrm{2D}}$. Such
+method can be found in both experimental and theoretical studies, such
+as to interpret ellipsometry data
+\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance /
+transmission spectra \cite{Li_2014, Yoffe-Wilson69}, optical
+conductance \cite{Matthes_2016} and many-body interactions
+\cite{Sohier_2016,Meckbach_2018} of 2D materials. The effective
+dielectric model allowing applying physical laws of bulk systems
+directly to 2D materials using $\varepsilon_{\mathrm{2D}}$. However,
+there are several drawbacks of such approach, first of all, the
+wavevector($q$)-dependency of dielectric screening in 2D
+sheets~\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Trolle_2017_eps_subst}
+is not captured. More severely, here we show that, due to the
+uncertainty of $\delta_{\mathrm{2D}}$, the calculated
+$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
+is extremely sensitive to the choice of $\delta_{\mathrm{2D}}$, making
+such model questionable.
+
+The basic assumption of the effective dielectric model (EDM) can be
+seen in Figure~\ref{fig-emt}\textbf{a}, where the macroscopic
+$\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
+2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
+and thickness $\delta_{\mathrm{2D}}$ and (ii) vacuum spacing with
+distance $L-\delta_{\mathrm{2D}}$. Using the effective medium theory
+(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
+$\varepsilon_{\mathrm{SL}}$ and $\varepsilon_{\mathrm{2D}}$ can be
+expressed using capacitance-like
+equations~\cite{Matthes_2016,Laturia_2018} :
+\begin{subequations}
+  \begin{eqnarray}
+    \label{eq:emt-1}
+    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}\\
+     \label{eq:emt-2}
+    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}
+  \end{eqnarray}
+\end{subequations}
+In principle, both the values of $\varepsilon_{\mathrm{2D}}$ and
+$\delta_{\mathrm{2D}}$ are unknown for a certain 2D material. To
+minimize the modeling error, we used non-linear least-square fitting
+to extract $\varepsilon_{\mathrm{2D}}$ and $\delta_{\mathrm{2D}}$ of
+selected 2H TMDCs simultaneously from \textit{ab initio}
+$\varepsilon_{\mathrm{SL}}$ -- $L$ data in
+Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{b} (details see
+Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
+the slab thickness, $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$
+and $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in-plane and
+out-of-plane data, respectively, are shown in Supplementary
+Table~\ref{SI-tab:delta-L-DFt}. As seen in Figure
+\ref{fig-emt}\textbf{b}, the estimation error of the thickness
+estimated from different directions is around 0.06$\sim{}$0.27
+\AA{}. Although such uncertainty only corresponds to about
+1$\sim{}$4\% of the interlayer spacing in the bulk counterparts of
+these 2D materials, its influence on the calculated values
+$\varepsilon_{\mathrm{2D}}^{\parallel}$ and
+$\varepsilon_{\mathrm{2D}}^{\perp}$ is significant. We estimated the
+dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
+$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta_{\mathrm{2D}}$ deviates
+from the best fitted value by $\pm{}$2.5 \AA{}, as shown in Figures
+\ref{fig-emt}\textbf{c} and \ref{fig-emt}\textbf{d},
+respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
+with $\delta_{\mathrm{2D}}$ with a uncertainty of $\sim{}$10\%, while
+strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans over
+more than one order of magnitude. The sensitivity of
+$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta_{\mathrm{2D}}$ explains
+the discrepancy in literature that both isotropic~\cite{Sohier_2016}
+and highly anisotropic~\cite{Matthes_2016,Laturia_2018}
+$\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
+reported. As a consequence, the estimated values of
+$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
+is highly questionable.
+
+On the contrary, the proposed $\alpha_{\mathrm{2D}}$ approach does not
+suffer from such deficiencies, despite its relatively simple
+formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
+generally at the order of 10\textsuperscript{-4} (Supplementary Figure
+{\color{red} XX}). In addition, the calculation of
+$\alpha_{\mathrm{2D}}$ technically simpler than
+$\varepsilon_{\mathrm{2D}}$: (i) $\alpha_{\mathrm{2D}}$ can be
+achieved using single-point calculation of macroscopic dielectric
+tensor, while $\varepsilon_{\mathrm{2D}}$ requires non-linear fitting
+of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; (ii) the
+values of $\alpha_{\mathrm{2D}}$ typically converge well for large $L$
+($>$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
+uncertainty as described above.
+
 %\subsection*{Polarizability as the fundamental variable}
@@
 %We consider
+
+\subsection{Universal scaling laws of $\alpha_{\mathrm{2D}}$}
+\label{sec:univ-scal-laws}
 

### 2019-10-03 paper.tex
modify until alpha-Eg relation

@@
 \ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
-panels in Fig.\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
+panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
 $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
@@
 $\alpha_{\mathrm{2D}}^{\perp}$
-(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).
+(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
 % A similar curve profile is obtained in both components of the dielectric constant including the much 
@@
 
-\subsection{Comparison with effective dielectric model}
+\subsection{Comparison with effective dielectric model (EDM)}
 \label{sec:comp-with-effect}
@@
 
-As a consequence of Eqs. \ref{eq:alpha-para-def} and
-\ref{eq:alpha-perp-def}, we demonstrate that other quantities are
-intrinsically related to the polarizability.  Using random phase
-approximation (RPA) theory \cite{Adler_1962} within the
-$\mathbf{k} \cdot \mathbf{p}$ formalism\cite{kittel_2005_introduction}
-(see Supplementary Section \ref{SI-sec:theory-1} for details), we show
-that $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ can be written as:
+For bulk materials, pioneering works from the 1950s have demonstrated
+empirical equations between $\varepsilon$ and the bandgap
+$E_{\mathrm{g}}$, including the
+Moss~\cite{Moss_1950_relation,Moss_1985_n_Eg,Finkenrath_1988} or
+Ravindra~\cite{Ravindra_1980_model,Ravindra_1979_eps_Eg} relations.
+Such universal relations, if exist in the context of
+$\alpha_{\mathrm{2D}}$, would be of high importance for studying and
+predicting the screening of 2D materials.  Inspired by the random
+phase approximation (RPA) theory \cite{Adler_1962} within the
+$\mathbf{k} \cdot \mathbf{p}$
+formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
+depending on the electronic and geometric information of a 2D material (see
+Supplementary Section \ref{SI-sec:theory-1} for details):
+% \begin{subequations}
+% \begin{eqnarray}
+% \label{eq:2D-Moss-para}
+  % &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
+  % \label{eq:2D-Moss-perp}
+  % &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \hat{\delta}_{\mathrm{2D}}
+% \end{eqnarray}
+% \end{subequations}
 \begin{subequations}
@@
 \label{eq:2D-Moss-para}
-  &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
+  &E_{\mathrm{g}} &= C^{\parallel} \alpha_{\mathrm{2D}}^{\parallel} \\
   \label{eq:2D-Moss-perp}
-  &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \delta
+  &\hat{\delta}_{\mathrm{2D}} & = C^{\perp} \alpha_{\mathrm{2D}}^{\perp} 
 \end{eqnarray}
 \end{subequations}
-where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
-the intrinsic thickness of the layer (Fig. \ref{fig-1}{\textbf a}), and
-$C^{\parallel} = {\displaystyle \frac{Ne^2}{2 \pi}}$ \cite{Jiang_2017_Eg_Eb}, where
-$N$ corresponds to the degeneracy of the bands associated with
-$E_{\mathrm{g}}$, and $C^{\perp} = {\varepsilon_{0}}$.
-% \todo[inline]{The previous expressions for the coefficients are
-  % wrong. Please see the version in SI}
-Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
-\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
-the polarizability and the electronic and structural properties for
-any 2D material in a new framework.  We show that these equations are
-valid for the current library of known layered materials involving
-different lattice symmetry, element composition, optical and
-electronic properties.
+where $E_{\mathrm{g}}$ is the fundamental electronic bandgap and
+$\hat{\delta}_{\mathrm{2D}}$ is the intrinsic thickness of the 2D
+layer, with coefficients
+$C^{\parallel} = {\displaystyle \frac{2 \pi}{Ne^2}}$
+\cite{Jiang_2017_Eg_Eb}, where $N$ is a pre-factor associated with the
+band degeneracy, and $C^{\perp} = {\varepsilon_{0}}^{-1}$. It is worth
+noting, unlike the parameter $\delta_{\mathrm{2D}}$ that is
+artificially assigned within the EDM picture (see previous section),
+$\hat{\delta_{\mathrm{2D}}}$ can be uniquely defined by
+$\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
+computationally and experimentally determined. Despite of the
+simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
+they generalize direct relationships between the electronic polarizability and
+the electronic / structural properties for any 2D material in a new
+framework.
+
+Next, we show that these equations are valid for the current
+library of known layered materials involving different lattice
+symmetry, element composition, optical and electronic properties.
 %
@@
 (MX\(_{\text{2}}\), where M is a metal in groups 4, 6, 10, and X=O, S,
-Se, Te) and phases (P\(\bar{6}\)m2, P3m1), metal monochalcogenides
-(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
-I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
-(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
-and thin layer organic-inorganic perovskites (ABX$_{3}$)
-(Fig. \ref{fig-3}{\textbf a}) shows that our method enables full
-correlation between these disparate variables.  Figure
-\ref{fig-3}{\textbf b} compares the calculated fundamental bandgap
-$E_{\mathrm{g}}$ (blue dots) and 2D electronic polarizabilities (bar
-plots) of all the 2D materials investigated, covering a wide spectrum
-range from far-infrared to ultraviolet.  Note from dimension analysis,
-it is more intuitive to express the polarizability as
-$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
-\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
-descending trend when $E_{\mathrm{g}}$ increases, while no apparent
-correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
-$E_{\mathrm{g}}$ is observed (see Supplementary Section
-\ref{SI-sec:pol-2D-Eg}).  We then examine Eqs. \ref{eq:2D-Moss-para}
-and \ref{eq:2D-Moss-perp} using the polarizabilities by
-first-principle calculations.  Figure \ref{fig-3}{\textbf c} shows
+Se, Te) and phases (P\={6}m2, P3m1), metal monochalcogenides
+(Ga\textsubscript{2}S\textsubscript{2},
+Ga\textsubscript{2}Se\textsubscript{2}), cadmium halides (CdX$_2$,
+X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
+(fluorographene (C\textsubscript{2}F\textsubscript{2}), graphane
+(C\textsubscript{2}H\textsubscript{2})), phosphorene
+(P\textsubscript{4}) and thin layer organic-inorganic perovskites
+(ABX\textsubscript{3}) (Figure \ref{fig-3}{\textbf a}) shows that our
+method enables full correlation between these disparate variables.
+Figure \ref{fig-3}{\textbf b} compares the calculated fundamental
+bandgap $E_{\mathrm{g}}$ (blue dots) and 2D electronic
+polarizabilities (bar plots) of all the 2D materials investigated,
+covering a wide spectrum range from far-infrared to ultraviolet.  Note
+from dimension analysis, it is more intuitive to express the
+polarizability as $\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$,
+which has unit of \AA{}. We find that
+$\alpha_{\mathrm{2D}}^{\parallel}$ has a general descending trend when
+$E_{\mathrm{g}}$ increases, while no apparent correlation between
+$\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
+Supplementary Section \ref{SI-sec:pol-2D-Eg}).  We then examine
+Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
+polarizabilities by first-principle calculations.  Figure
+\ref{fig-3}\textbf{c} shows
 $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
 \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
-materials investigated (circle dots).  A linear regression coefficient
-of $R^{2}=0.84$ indicates a strong correlation between bandgaps and
-polarizabilities as predicted in Eq. \ref{eq:2D-Moss-para}.  We also
-discover that the linearity between
-$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
+materials investigated (circle dots) at HSE06 level.  A linear
+regression coefficient of $R^{2}=0.84$ indicates a strong correlation
+between bandgaps and polarizabilities as predicted in
+Eq. \ref{eq:2D-Moss-para}.  We also discover that the linearity
+between $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
 $E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
-bandgap is calculated using the HSE06 hybrid
-functional\cite{Heyd_2005} compared with that from
-Perdew--Burk--Ernzerhof (PBE)
-functional%exchange correlation functional
-(see Supplementary Section \ref{SI-sec:pol-2D-Eg} and Supplementary
-Figure \ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels
-of theory are needed to predict bandgaps. See Supplementary Section
-\ref{SI-sec:gpaw} for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and
-\ref{eq:2D-Moss-perp} using different bandgaps, databases, and levels
-of calculation.
+bandgap is calculated using the HSE06 hybrid functional compared with
+that from PBE exchange-correlation functional (see Supplementary
+Section \ref{SI-sec:pol-2D-Eg} and Supplementary Figure
+\ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels of
+theory are needed to precisely predict bandgaps.  A detailed benchmark
+of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using
+different bandgaps, databases, and levels of calculation can be seen
+in Supplementary Section~\ref{SI-sec:gpaw}.
 
@@
   charge density change $\Delta \rho(z)$ along the z-direction for
-  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
+  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under external
   eletric field of 0.01 V/\AA{}.  The green and red regions represent

### 2019-10-03 SI.tex
Update main and SI
update until question 5

@@
 Using E$_{n\mathbf{k}}^{QP}$ it is then possible to recalculate the dielectric function using the quasi-particle eigenergies as well as the DFT eigenfunctions.
+
+For bulk systems, the accuracy of optical properties calculated
+generally ranks by PBE $<$ G\textsubscript{0}W\textsubscript{0} $<$
+BSE. This is because the calculation of the frequency-dependent
+optical properties of a material involves a summation over the valence
+and conduction states. Thus, the accuracy of these states determines
+the calculated optical properties. Within Kohn-Sham density functional
+theory (KS-DFT), the many-body effects are given by the
+exchange-correlation energy which is approximated by functionals based
+on the homogenous electron gas. This generally leads to an
+underestimation of the bandgap and results in the first optical peak
+being lower in energy in comparison to experiment. To go beyond
+KS-DFT, the G\textsubscript{0}W\textsubscript{0} approximation
+replaces the exchange-correlation energy with the self-energy in a bid
+to include many-body effects through the interacting Green's function,
+$G$, and the screened Coulomb potential, $W$. This generally leads to
+an overestimation of the first optical peak as electron-hole coupling
+is not taken into account. This can be remedied by solving the
+Bethe-Salpeter equation using the eigenvalues obtained from
+G\textsubscript{0}W\textsubscript{0}
+(G\textsubscript{0}W\textsubscript{0} + BSE) which generally gives
+good agreement with experiment.
 
@@
 
+\iffalse
 \subsection{Density of States (DOS) plots for the materials studied}
@@
 \input{BS_figures}
+\fi
 

### 2019-10-03 paper.tex
update until question 5

@@
 constant decreases with $L$ as excepted. To rule out the possibility
-that the result is affected by the choice of \textbf{ab initio}
+that the result is affected by the choice of \textit{ab initio}
 methods, we also performed simulations at higher levels of theory
@@
 frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
-and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, as seen in
-Supplementary Section \ref{SI-ssec:gw}. Despite the different levels
-of techniques used (Perdew-Burke-Ernzerhof (PBE) exchange-correlation
-functional \cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, HSE06 hybrid
-functionals or G\textsubscript{0}W\textsubscript{0} method), the
-magnitude of dielectric functions calculated universally decreases
+and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different levels
+of techniques, including Perdew-Burke-Ernzerhof (PBE)
+exchange-correlation functional
+\cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, many-body Green function
+method (G\textsubscript{0}W\textsubscript{0})~\cite{Hedin_1965} and
+Bethe-Salpethe equation (BSE)~\cite{Onida_2002}, with increasing
+accuracy of calculated optical properties (PBE $<$
+G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
+many-body screening and excitonic effects (details see Supplementary
+Section \ref{SI-ssec:gw}). Despite various levels of theory involved,
+the magnitude of dielectric functions calculated universally decreases
 with $L$ over the frequency domain.  These results indicate that
@@
 $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
-absorption and electron energy loss spectrum (EELS), suffers the same
+absorption and electron energy loss spectrum (EELS, equivalent to $1 / \mathrm{Im}(\varepsilon(\omega))$), suffers the same
 deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
-simple model system explains the origin of the discrepancy of dielectric constant values reported in previous literature~\cite{Li_2016}.
+simple model system explains the origin of the discrepancy of
+dielectric constant values reported in previous
+literature~\cite{Li_2016}.
 %
@@
 
-We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
-thickness of a 2D material proposed in
-Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
-$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
-longest distance along the z-direction between any two atom nuclei
-plus their covalent radii:
+We further examine the validity of Eq.~\ref{eq:2D-Moss-perp}, i.e.,
+the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the thickness
+of a 2D material. To test if the quantity $\hat{\delta_{\mathrm{2D}}}$
+is physical, we choose the ``covalent'' thickness
+$\delta_{\mathrm{cov}}$ of a 2D material as a
+comparison. $\delta_{\mathrm{cov}}$ is defined as the longest distance
+along the \textit{z}-direction between any two atom nuclei plus their covalent
+radii:
 %
@@
 \end{equation}
-where $i$, $j$ are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
-is the covalent radius of atom $i$ (Figure \ref{fig-3}{\textbf d} inset). 
-%
-%
-$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
-excellent linear correlation with $\delta_{\mathrm{cov}}$, with
-$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
-\ref{fig-3}{\textbf d}), which agrees well with Eq
-\ref{eq:2D-Moss-perp}.  This result indicates that
-$\alpha_{\mathrm{2D}}^{\perp}$ has a strong physical meaning through
-the geometry of the layer.  Similar to the molecular polarizability
-which characterizes the volume of the electron cloud of an isolated
-molecule \cite{Israelachvili_2011},
-$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
-volume of the electron cloud per unit area (from its definition), and
-is naturally proportional to the thickness of the 2D
+where $i$, $j$ are atomic indices in the 2D material and
+$r_{\mathrm{cov}}^{i}$ is the covalent radius of atom $i$ (Figure
+\ref{fig-3}{\textbf d} inset). As shown in Figure~\ref{fig-3}{\textbf
+  d}, $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ (or equivalently,
+$\hat{\delta}_{\mathrm{2D}}$) is very close to $\delta_{\mathrm{cov}}$
+with a good linear correlation of $R^{2}=0.98$. This result indicates
+a strong relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
+geometry of the 2D layer, which can be approximated by
+$\delta_{\mathrm{cov}}$. Similar to the molecular polarizability which
+characterizes the volume of the electron cloud of an isolated molecule
+\cite{Israelachvili_2011},
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also naturally
+related to the characteristic thickness of the electron cloud of 2D
 material. Supplementary Section
 \ref{SI-ssec:theory-1-perp-fundamental} shows an explanation of this
-behavior from fundamental electrostatics. Indeed, the universal
-scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
-\ref{fig-3}{\textbf d} indicates that the quantity
-$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, measurable via
-electronic and optical approaches
-\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
-is in reality the (dielectric) characteristic thickness of a 2D
-material, and can be used to resolve the long-existing controversy
-about the experimental thickness of 2D materials, such as graphene
-\cite{Shearer_2016}.
-%
+behavior from fundamental electrostatics and why
+$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is close to
+$\delta_{\mathrm{cov}}$. Our proposed definition of
+$\hat{\delta_{\mathrm{2D}}}$ of a 2D material based on
+Eq. \ref{eq:2D-Moss-perp} may have impact
+on some long-existing controversies about the experimental thickness
+of 2D materials~\cite{Shearer_2016}, through the
+measurable quantity $\alpha_{\mathrm{2D}}^{\perp}$
+\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}.
+% 
+%
+
 To rule out the possibility that our conclusion are limited by the
 number of materials used at HSE06 level, we further validate
-Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
-database \cite{Haastrup_2018}, from which we extracted the dielectric
-properties of over 230 compounds calculated at the PBE level, and
-superimpose with our results in Figure \ref{fig-3}{\textbf c} and
-\ref{fig-3}{\textbf d} (see details in Supplementary Section
-\ref{SI-sec:gpaw-1}). Although the dielectric properties may be
-overestimated at PBE level due to underestimation of the bandgap
+Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using two
+different 2D material databases \cite{Haastrup_2018,Mounet_2018}, from
+which we extracted the dielectric properties of over 300 compounds
+calculated at the PBE level, and superimpose with our results in
+Figure \ref{fig-3}{\textbf c} and \ref{fig-3}{\textbf d}. Although the
+calculated dielectric properties may be different due to different
+choice of functionals as well as underestimation of the bandgap
 compared with the more accurate HSE06 functionals
@@
 $\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-with the linear coefficient very close to the HSE06 results (see
-details in Supplementary Section \ref{SI-sec:gpaw-2}).
-
-We have also searched for additional relations between the 2D
-polarizabilities with other physical quantities, including the
-effective carrier mass, quantum capacitance (density of states) and
-total atomic polarizabilities with no apparent correlations being
-found (Supplementary Section \ref{SI-sec:gpaw-3}).  We found however that
-Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
-connection with the screening properties of the layer.
-%
-In merit of the unit analysis, $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ both have unit of
-$4\pi\varepsilon_{0} \cdot$[Length]. In other words,
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-represent in- and out-of-plane characteristic lengths,
-respectively. It is well-known that the in-plane screened
-electrostatic potential $V(r)$ from a point charge as a function of
-distance $r$:
-$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
-\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
-      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
-    \frac{2
-      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
-\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
-function and $Y_{0}$ is the Bessel function of second kind, is
-associated with the in-plane screening radius
-$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
-\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
-to the simple Coulomb potential in vacuum. Combining with the result
-that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
-thickness of a 2D material, we have drawn a generalized picture of the
-dielectric nature of 2D materials via the 2D polarizability: the
-dielectric screening of a point charge sitting in the middle of a 2D
-material can be viewed as an ellipsoid with the length of principle
-axes to be
-$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
-\varepsilon_{0})$ and
-$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
-respectively. This is analog to the polarizability ellipsoid picture
-of molecules used in spectroscopy \cite{Banwell_1994} (see
-Supplementary Figure \ref{SI-fig:ellipsoid}). The polarizability
-ellipsoid for a 2D material is in general ultra flat, with
-$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
-TMDCs in Table \ref{tbl:radii}.  Moreover, $r_{0}^{\parallel}$ is
-generally larger for a smaller bandgap semiconductor, which
-qualitatively explains the inverse proportional relation between
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$ seen in
-Eq. \ref{eq:2D-Moss-para}.  This gives a geometrical interpretation of
-the bandgap in terms of the screening radius of the layer.
-
-%\subsection{Bridging the 2D and 3D Dielectric Properties}
-%\label{sec:2D-3D}
-
-We next show that the underlying physical mechanism linking 
-polarizability to bandgaps allows us to further bridge 
-the dielectric properties between 2D materials and 
-their 3D bulk counterparts in a remarkable way. 
-%The dielectric constant $\varepsilon$, although not well-defined for
-%a monolayer 2D material, becomes applicable when the 2D layers are
-%stacked. 
-%
-%
-%
-In a bulk layered material stacked by layers with equilibrium
+with the linear coefficient very close to the HSE06 results, which
+further proves the validity of our proposed relations. We have also
+searched for additional relations between the 2D polarizabilities with
+other physical quantities, including the effective carrier mass,
+quantum capacitance (density of states) and total atomic
+polarizabilities with no apparent correlations being found
+(Supplementary Section \ref{SI-sec:gpaw-3}).
+
+\subsection{Application in multilayer and bulk systems}
+\label{sec:apply-electr-polar}
+The concept of electronic polarizability is not limited to monolayer
+materials, and can be applied to multilayer and bulk systems as
+well. For a 2D material stack composed of $N$ layers, we can define
+the electronic polarizability $\alpha_{\mathrm{NL}}$ similar to
+Eqs. \eqref{eq:alpha-para-def} and \eqref{eq:alpha-para-def}. Note
+$\alpha_{\mathrm{NL}}(N=1)$ is equivalent to $\alpha_{\mathrm{2D}}$.
+Figure \ref{fig-4}\textbf{a} and \ref{fig-4}\textbf{b} show
+$\alpha_{\mathrm{NL}}^{\parallel}$ and $\alpha_{\mathrm{NL}}^{\perp}$
+as functions of $N$ for the selected 2H TMDCs,
+respectively. Interestingly, we find that in all cases,
+$\alpha_{\mathrm{NL}}$ exhibits nearly ideal linear relation with
+$\alpha_{\mathrm{2D}}$, such that
+$\alpha_{\mathrm{NL}}^{\parallel}= N \alpha_{\mathrm{2D}}^{\parallel}$
+and $\alpha_{\mathrm{NL}}^{\perp}= N
+\alpha_{\mathrm{2D}}^{\perp}$. Due to the relatively small
+electric applied (0.01 eV/\AA{}), the interlayer interactions within
+the stack are negligible. Under such circumstances, $\alpha_{\mathrm{2D}}$ of individual layers is additive, which leads to the following general relation:
+\begin{equation}
+  \label{eq:alpha-nl}
+  \alpha_{\mathrm{NL}}^{p} = \sum_{i=1}^{N} \alpha_{\mathrm{2D, i}}^{p},\quad p=\parallel\ \mathrm{or}\ \perp
+\end{equation}
+where $\alpha_{\mathrm{2D, i}}$ is the electronic polarizability of
+layer $i$, and $p$ is the direction of polarization. This relation can
+be further used to calculate screening inside 2D heterostructures
+\cite{Kumar_2016_jpcc,Andersen_2015_dielec_vdWH}.
+%
+%
+%
+
+We further look into the bulk systems. In a bulk layered material stacked by layers with equilibrium
 inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
@@
   \varepsilon^{\parallel}_{\mathrm{Bulk}}
-  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
+  &= 1 + \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
   \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
@@
 
-Finally, we show that a general picture of the dielectric properties in
+\subsection{Unified geometric represenation of $\alpha_{\mathrm{2D}}$}
+\label{sec:unif-geom-repr}
+
+%
+Lastly, we demonstrate that both $\alpha_{\mathrm{2D}}^{\parallel}$
+and $\alpha_{\mathrm{2D}}^{\perp}$ can be unified using a geometric
+picture. In merit of the unit analysis,
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
+both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. In other words,
+they represent in- and out-of-plane characteristic lengths,
+respectively. It is well-known that the in-plane screened
+electrostatic potential (Keldysh potential) $V(r)$ from a point charge
+as a function of distance $r$:
+$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
+\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
+      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
+    \frac{2
+      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
+\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
+function and $Y_{0}$ is the Bessel function of second kind, is
+associated with the in-plane screening radius
+$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
+\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
+to the simple Coulomb potential in vacuum. Combining with the result
+that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
+thickness of a 2D material, we can view the dielectric screening of a
+point charge sitting in the middle of a 2D material as an ellipsoid
+with the radii of principle axes to be
+$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
+\varepsilon_{0})$ and
+$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
+respectively, as illustrated in Figure~\ref{fig-ellip}\textbf{a}.
+This is analog to the polarizability ellipsoid picture of molecules
+used in spectroscopy \cite{Banwell_1994}. The polarizability ellipsoid
+for a 2D material is in general ultra flat, with
+$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as demonstrated by the examples
+of group 6 2H TMDCs (Figure~\ref{fig-ellip}\textbf{a} and
+~\ref{fig-ellip}\textbf{b}). The polarizability ellipsoid picture
+provides further insights into the physical nature of
+$\alpha_{\mathrm{2D}}$: $r_{0}^{\parallel}$ is close to the exciton
+radius that confined within the 2D plane~\cite{Pulci_2014}, which is
+generally larger for a smaller bandgap semiconductor, and can be
+converted through the exciton binding energy as proposed in
+Refs. \citenum{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}
+Eq. \ref{eq:2D-Moss-para}. On the other hand, $r_{0}^{\perp}$ may be
+indirectly deduced from Stark effect
+\cite{Pedersen_2016,Klein_2016,Roch_2018}.
+% and the low-frequency Raman
+% scattering modes of 2D materials \cite{Tan_2012,Zhang_2013}.
+
+%\subsection{Bridging the 2D and 3D Dielectric Properties}
+%\label{sec:2D-3D}
+
+Inspired by the polarizability ellipsoid model, we show that a general picture of the dielectric properties in
 any dimension can be drawn by studying the dielectric
@@
 
-%\section{Conclusion}
+\section{Conclusion}
 %\label{sec:org5fd1f1a}
@@
 
-Add Mounet paper \cite{Mounet_2018}
-
 \section{Data Availability}

### 2019-10-04 paper.tex
ADd more scripts

@@
 discrepancy of reported $\varepsilon$ values. In this letter, we give
-a thorough study of the underlying issue. Using \textbf{ab initio}
+a thorough study of the underlying issue. Using \textit{ab initio}
 simulations of a model system, we demonstrate that the macroscopic
@@
 $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
-absorption and electron energy loss spectrum (EELS, equivalent to $1 / \mathrm{Im}(\varepsilon(\omega))$), suffers the same
+absorption (abs., equivalent to $\mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), refractive index ($n$,  $\sim{}\sqrt{\mathrm{Re}(\varepsilon_{\mathrm{SL}})}$) and electron energy loss spectrum (EELS, equivalent to $-1 / \mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), suffers the same
 deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
@@
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
-{\color{red} Convergence plot in SI} Such result is in good agreement
-with the spatially localized induced dipole moment of a 2D materials
-as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
+reach convergence when $L$ exceeds 10 \AA and 15 \AA,
+respectively. Such result is in good agreement with the spatially
+localized induced dipole moment of a 2D materials as shown in
+Supplementary Figure~\ref{SI-fig:rho-profile}.
 %

### 2019-10-04 src/VASP_HSE/relation_alpha.py

@@ -145,19 +145,19 @@ fig.savefig(os.path.join(img_path, "alpha_xx_1_Eg_HSE.svg"))
 fig = plt.figure(figsize=(2.5, 2.5))
 ax = fig.add_subplot(111)
 # gpaw
-ax.scatter(gp_data[3], gp_data[1], marker="s", alpha=0.1,
+ax.scatter(gp_data[3], gp_data[1] * 4 * pi, marker="s", alpha=0.1,
            c="#cca384", label="$\\alpha_{\\mathrm{2D}}^{\\perp}$ Ref. xx")
 
-ax.scatter(qe_data[-1], qe_data[1], marker="^", alpha=0.1,
+ax.scatter(qe_data[-1], qe_data[1] * 4 * pi, marker="^", alpha=0.1,
            c="#cca384", label="$\\alpha_{\\mathrm{2D}}^{\\perp}$ Ref. xx")
 # [ax.text(x=qe_data[-1][i], y=qe_data[1][i], s=materials_qe[i],
          # ha="left", va="top", size="x-small", alpha=0.5) \
          # for i in range(len(materials_qe)) if qe_data[1][i] < 0.8 * qe_data[-1][i] * 0.078]
 # hse
-ax.scatter(thick, alpha_z, marker="o",
+ax.scatter(thick, alpha_z * 4 * pi, marker="o",
             edgecolors=None,
             alpha=0.5, c=cs)
-res = linregress(x=thick, y=alpha_z)
+res = linregress(x=thick, y=alpha_z * 4 * pi)
 # res = linregress(x=numpy.hstack([thick, gp_data[3], qe_data[-1]]),
                  # y=numpy.hstack([alpha_z, gp_data[1], qe_data[1]]))
 # res = linregress(x=gp_data[3], y=gp_data[1])
@@ -165,12 +165,13 @@ print(res)
 xx = numpy.linspace(1.5, 10.5)
 yy = res.slope * xx + res.intercept
 ax.plot(xx, yy, "--")
+ax.plot(xx, xx, "--")
 # plt.colorbar()
 ax.set_xlim(1.5, 10.5)
-ax.set_ylim(0.08, numpy.max(yy))
+# ax.set_ylim(0.08, numpy.max(yy))
[…]

### 2019-10-04 src/distance/alpha_convergence.py

@@ -20,13 +20,11 @@ g = os.walk(root)
 names = next(g)[1]
 # print(names)
 # names = sorted(names)
-gs = GridSpec(7, 1, hspace=0.3)
-fig1 = plt.figure(figsize=(3, 3.2))
-fig2 = plt.figure(figsize=(3, 3.2))
-ax1_r = fig1.add_subplot(gs[5:])
-ax1 = fig1.add_subplot(gs[:5 ])
-ax2_r = fig2.add_subplot(gs[5:])
-ax2 = fig2.add_subplot(gs[:5 ])
+fig1 = plt.figure(figsize=(4.5, 2))
+ax1_r = fig1.add_subplot(121)
+# ax1 = fig1.add_subplot(gs[:5 ])
+ax2_r = fig1.add_subplot(122)
+# ax2 = fig2.add_subplot(gs[:5 ])
 
 colors = {"mos2": "#1f77b4",
           "mose2": "#ff7f0e",
@@ -58,50 +56,47 @@ for i, item in enumerate(g):
         if "parallel.agr" in f_path:
             alpha_SL = L * (data[:, 1] - 1)  / (4 * pi)
             error_alpha = numpy.abs(alpha_SL - alpha_SL[-1]) / alpha_SL[-1] 
-            l, *_ = ax1.plot(L, eps_SL, "o",
-                             label=names[i],
-                             markersize=4,
-                             color=colors[names[i]]
-            )
+            # l, *_ = ax1.plot(L, eps_SL, "o",
+            #                  label=names[i],
+            #                  markersize=4,
+            #                  color=colors[names[i]]
+            # )
             ax1_r.plot(L, error_alpha, "o",
-                       markersize=4,
-                       color=l.get_c())
+                       markersize=4,)
         elif "perpendicular.agr" in f_path:
             alpha_SL = L * (data[:, 1] - 1) / (data[:, 1]) / (4 * pi)
             error_alpha = numpy.abs(alpha_SL - alpha_SL[-1]) / alpha_SL[-1] / 10
-            l, *_ = ax2.plot(L, eps_SL, "o-",
-                             label=names[i],
-                             markersize=4,
-                             color=colors[names[i]]
-            )
[…]

### 2019-10-14 src/VASP_HSE/relation_alpha.py
update changes until 20191014

@@ -171,7 +171,7 @@ ax.set_xlim(1.5, 10.5)
 # ax.set_ylim(0.08, numpy.max(yy))
 # ax.set_title("$y={0:.2f}x+{1:.2f},\ R^2={2:.2f}$".format(res.slope, res.intercept, res.rvalue))
 ax.set_xlabel("$\\delta_{\\mathrm{cov}}$ ($\\mathrm{\\AA}$)")
-ax.set_ylabel("$\\alpha_{\\mathrm{2D}}^{\\perp} / \\varepsilon_0$ ($\\mathrm{\\AA}$)")
+ax.set_ylabel("$\\alpha_{\\mathrm{2D}}^{\\perp} / (4 \\pi \\varepsilon_0)$ ($\\mathrm{\\AA}$)")
 ax.legend()
 fig.tight_layout()
 fig.savefig(os.path.join(img_path, "alpha_zz_thick_HSE.svg"))

### 2019-10-14 src/distance/alpha_convergence.py
Update plots for fig1

@@ -34,6 +34,14 @@ colors = {"mos2": "#1f77b4",
           "wte2": "#8c564b",
 }
 
+symbs = {"mos2": "MoS$_{2}$",
+          "mose2": "MoSe$_{2}$",
+          "mote2": "MoTe$_{2}$",
+          "ws2": "WS$_{2}$",
+          "wse2": "WSe$_{2}$",
+          "wte2": "WTe$_{2}$",
+}
+
 # plot_eps_para(ax1, alpha_0=8.5, dev=4)
 # plot_eps_perp(ax2, alpha_0=0.47, dev=0.15)
 
@@ -65,7 +73,7 @@ for i, item in enumerate(g):
                        markersize=4,)
         elif "perpendicular.agr" in f_path:
             alpha_SL = L * (data[:, 1] - 1) / (data[:, 1]) / (4 * pi)
-            error_alpha = numpy.abs(alpha_SL - alpha_SL[-1]) / alpha_SL[-1] / 10
+            error_alpha = numpy.abs(alpha_SL - alpha_SL[-1]) / alpha_SL[-1]
             # l, *_ = ax2.plot(L, eps_SL, "o-",
             #                  label=names[i],
             #                  markersize=4,
@@ -73,7 +81,7 @@ for i, item in enumerate(g):
             # )
             ax2_r.plot(L, error_alpha, "o",
                        markersize=4,
-                       label=names[i])
+                       label=symbs[names[i]])
 
 ax1_r.set_xlabel("$L$ ($\\AA$)")
 ax1_r.set_title("parallel")

### 2019-10-14 src/distance/compare_emt.py

@@ -83,7 +83,7 @@ combine_data()
 
 print(fit_all_para, fit_all_perp)
 
-fig, ax = plt.subplots(1, 3, figsize=(8, 2.5))
+fig, ax = plt.subplots(1, 3, figsize=(8.5, 2.4))
 
 def plot_diff():
 # ax 0: diff
@@ -94,12 +94,13 @@ def plot_diff():
         delta_perp, _ = fit_all_perp[n]
         name_disp.append("2H-" + name)
         # diff.append(delta_para / delta_perp)
-        diff.append(delta_para - delta_perp)
+        diff.append((delta_para - delta_perp) / delta_perp * 100)
     ax[0].axhline(y=0, alpha=0.8)
     ax[0].bar(range(len(name_disp)), diff, width=0.6)
     ax[0].set_xticks(range(len(name_disp)))
     ax[0].set_xticklabels(name_disp, rotation=-30)
-    ax[0].set_ylabel("Estimation Error $\\delta_{\\mathrm{2D}}^{{\parallel}, \\mathrm{fit}}  - \\delta_{\\mathrm{2D}}^{\\perp, \\mathrm{fit}}$ ($\\mathrm{\\AA{}}$)")
+    ax[0].set_ylabel("Estimation Error (%) of $\\delta_{\\mathrm{2D}}$")
+# ""between $\\delta_{\\mathrm{2D}}^{{\parallel}, \\mathrm{fit}}$  and $\\delta_{\\mathrm{2D}}^{\\perp, \\mathrm{fit}}$ ($\\mathrm{\\AA{}}$)")
 
 
 def plot_type1():
@@ -153,12 +154,16 @@ def plot_type2():
         delta_perp, _ = fit_all_perp[n]
         delta_avg = (delta_para + delta_perp) / 2
         name_disp.append("2H-" + name)
-        xx = numpy.linspace(-0.25, 0.25, 256)
-        dd_ = xx + delta_avg
+        # xx = numpy.linspace(-0.25, 0.25, 256)
+        # dd_ = xx + delta_avg
+        diff = 7.5
+        xx = numpy.linspace(-diff / 100, diff / 100, 256)
+        dd_ = (1 + xx) * delta_avg
         f = dd_ / L
         eps_2D_para = (eps_para + f - 1) / f
 
-        ax[1].plot(xx, eps_2D_para, label="2H-" + name)
[…]

### 2019-10-14 SI.tex
update figures befor sending to Elton

@@
 \pagebreak{}
-\section{Comment on the hypothetical ``dielectric constant'' in the effective medium theory (EMT)}
+\section{Further Data Concerning the Comparison with EDM}
 \label{sec:2D-3D-rescale}
-From literatures, it is often desired to extract the ``dielectric
-constant'' of a 2D material from the 3D macroscopic dielectric
-constant of the superlattice, where the layers are periodic along of
-x,y directions but separated by a vacuum layer between its images
-\cite{Matthes_2016,Laturia_2018}. Such method makes use of the
-effective medium theory (EMT), and as discussed in the main text, the
-definition of the 2D ``dielectric constant'' is questionable, due to
-the locality of electrostatic screening of the 2D materials
-\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Moreover, the
-EMT approach assumes that the 2D material has an effective thickness
-$\delta$ and effective dielectric constant
-$\varepsilon_{\mathrm{2D}}$, while the exact value of $\delta$ is
-unknown due to the ambiguity of the reference planes. Here we show
-that, in addition to the ambiguous definition of the 2D dielectric
-constant, such approach requires the precise determination of the 2D
-layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical. On
-the contrary, the 2D polarizability approach presented in the main
-text is independent of the choice of the parameter $\delta$, as well
-as the volume fraction of the 2D material, and can correctly capture
-the dielectric properties of the 2D material.
-
-In brief, the hypothetical 2D dielectric constant
-$\varepsilon$ comes from the planar limit of the
-effective medium theory \cite{Markel_2016,Aspnes_1982}, and can be
-expressed by means of the macroscopic dielectric constant
-$\varepsilon_{\mathrm{SL}}$ of the superlattice:
-
-\begin{eqnarray}
-  \label{eq:MG-effect-1}
-  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
-  \label{eq:MG-effect-2}
-  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
-\end{eqnarray}
-where $f=\delta/L$ is the volume fraction of the 2D
-material in the superlattice and $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
-$\varepsilon_{\mathrm{2D}}^{\perp}$ are the corresponding dielectric constants for the 2D layer. 
+
 The major issue when using such rescale
-relations comes from the determination of $\delta_{\mathrm{2D}}$. To
+relations comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
 eliminate the modeling error caused by the \textit{a priori} parameter
@@
 Figure \ref{fig:rescale-prb}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.85\linewidth]{img/SI-alpha-convergence.pdf}
+  \caption{Convergence of electronic polarizabilities
+    $\Delta \varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{a}) and
+    $\Delta \varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{b}) as
+    functions of $L$ for the selected TMDCs, respectively. For both
+    in- and out-of-plane polarizabilities, convergence is achieved
+    when $L >$15 \AA{}}
+  \label{fig:alpha-converg}
+\end{figure}
 
@@
 As can be seen from the fitted results in Figure
-\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}$ extracted
+\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}^{*}$ extracted
 from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
 $\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
-{\AA}. Notably, the $\delta_{\mathrm{2D}}$ values are generally 10\%
+{\AA}. Notably, the $\delta_{\mathrm{2D}}^{*}$ values are generally 10\%
 smaller than the interlayer distance in corresponding bulk materials
 $L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
-other hand, the extracted $\delta_{\mathrm{2D}}$ values are closer to
-the covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ as
+other hand, the extracted $\delta_{\mathrm{2D}}^{*}$ values are closer to
+the covalent thickness $\delta_{cov}$ as
 described in the main text, with a difference generally smaller than
@@
   \hline{}
-  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
+  Material & $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$ (\AA) & $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ ({\AA})& $L_{\mathrm{Bulk}}$ ({\AA}) & $\delta_{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
   \hline{}
@@
 
-\caption{Calculated $\delta_{\mathrm{2D}}$ from
-  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-  $\varepsilon_{\mathrm{SL}}^{\perp}$, compared with the interlayer
-  distance of corresponding bulk material $L_{\mathrm{SL}}$, the
-  covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
-  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
+\caption{Fitted effective thickness
+  $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$ and
+  $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in- and
+  out-of-plane dielectric data, compared with the interlayer distance
+  of corresponding bulk material $L_{\mathrm{Bulk}}$, the covalent
+  thickness $\delta_{\mathrm{cov}}$, and
+  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC
+  materials.}
 \label{tab:delta-L-DFt}
@@
 
-Another drawback of the 2D EMT approach is the
+One main drawback of the EDM approach is the
 overestimation of the out-of-plane dielectric response. As can be seen
@@
   \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
-    function of the difference between $\delta_{\mathrm{2D}}$ and
+    function of the difference between $\delta_{\mathrm{2D}}^{*}$ and
     $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$. A small change of
@@
     the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
-    which is apparently unphysical}
+    which is apparently nonphysical.}
   \label{fig:eps-alpha-error}
@@
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
-than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
+than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
 if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
-Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
+Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
-$\delta_{\mathrm{2D}}$ chosen may lead to divergence of
+$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
 $\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
@@
 To conclude, based on theoretical and technical considerations, there are several
-advantages of using the polarizability $\alpha$ for describing the dielectric
+advantages of using the electronic polarizability for describing the dielectric
 nature of 2D materials, including
@@
 \label{sec:aniso}
-\subsection{The 2D screening length}
-\label{ssec:2D-screening}
-Here we show a schematic drawing of the polarizability ellipsoid for a
-2D material in Figure \ref{fig:ellipsoid}. As can be seen the
-polarizability ellipsoid is ultraflat, with
-$r_{0}^{\parallel} \gg r_{0}^{\perp}$, which is the origin of the high
-dielectric anisotropy of 2D materials.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.9\linewidth]{img/SI-ellipsoid.pdf}
-  \caption{Polarizability ellipsoid of a 2D material, the long axis
-    equals $\alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ and the short axis
-    equals  $\alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$}
-  \label{fig:ellipsoid}
-\end{figure}
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-10-14 paper.tex
update figures befor sending to Elton

@@
 %
-Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
-\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
-panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
-$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
-centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$
-(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
+% Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
+% \ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
+% panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
+% $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+% $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
+% centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
+% $\alpha_{\mathrm{2D}}^{\perp}$
+% (Figure \ref{fig-1}\textbf{d}-\textbf{e}).
 % A similar curve profile is obtained in both components of the dielectric constant including the much 
@@
 Apart from the 2D electronic polarizability proposed here, it is worth
-mentioning that a widely-used approach in literature is to treat the
-2D material as a slab with an effective dielectric tensor
-$\varepsilon_{\mathrm{2D}}$ and thickness $\delta_{\mathrm{2D}}$. Such
-method can be found in both experimental and theoretical studies, such
-as to interpret ellipsometry data
+mentioning that the effective dielectric model (EDM) is widely used in
+literature to treat the 2D material as a slab with an effective
+dielectric tensor $\varepsilon_{\mathrm{2D}}$ and thickness
+$\delta^{*}_{\mathrm{2D}}$. Such method can be found in both
+experimental and theoretical studies, such as to interpret
+ellipsometry data
 \cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance /
@@
 conductance \cite{Matthes_2016} and many-body interactions
-\cite{Sohier_2016,Meckbach_2018} of 2D materials. The effective
-dielectric model allowing applying physical laws of bulk systems
-directly to 2D materials using $\varepsilon_{\mathrm{2D}}$. However,
-there are several drawbacks of such approach, first of all, the
-wavevector($q$)-dependency of dielectric screening in 2D
+\cite{Sohier_2016,Meckbach_2018} of 2D materials. The EDM allows
+applying physical laws of bulk systems directly to 2D materials using
+$\varepsilon_{\mathrm{2D}}$. However, there are several drawbacks of
+such approach, first of all, the wavevector($q$)-dependency of
+dielectric screening in 2D
 sheets~\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Trolle_2017_eps_subst}
 is not captured. More severely, here we show that, due to the
-uncertainty of $\delta_{\mathrm{2D}}$, the calculated
+uncertainty of $\delta^{*}_{\mathrm{2D}}$, the calculated
 $\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
-is extremely sensitive to the choice of $\delta_{\mathrm{2D}}$, making
-such model questionable.
-
-The basic assumption of the effective dielectric model (EDM) can be
-seen in Figure~\ref{fig-emt}\textbf{a}, where the macroscopic
+is extremely sensitive to the choice of $\delta^{*}_{\mathrm{2D}}$,
+making such model questionable.
+
+The basic assumption of EDM can be
+seen in the inset of Figure~\ref{fig-1}\textbf{e}, where the macroscopic
 $\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
 2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
-and thickness $\delta_{\mathrm{2D}}$ and (ii) vacuum spacing with
-distance $L-\delta_{\mathrm{2D}}$. Using the effective medium theory
+and thickness $\delta^{*}_{\mathrm{2D}}$ and (ii) vacuum spacing with
+distance $L-\delta^{*}_{\mathrm{2D}}$. Using the effective medium theory
 (EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
@@
     \label{eq:emt-1}
-    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}\\
+    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta^{*}_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta^{*}_{\mathrm{2D}}}{L} \right)}\\
      \label{eq:emt-2}
-    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}
+    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta^{*}_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta^{*}_{\mathrm{2D}}}{L} \right)}
   \end{eqnarray}
@@
 In principle, both the values of $\varepsilon_{\mathrm{2D}}$ and
-$\delta_{\mathrm{2D}}$ are unknown for a certain 2D material. To
+$\delta^{*}_{\mathrm{2D}}$ are unknown for a certain 2D material. To
 minimize the modeling error, we used non-linear least-square fitting
-to extract $\varepsilon_{\mathrm{2D}}$ and $\delta_{\mathrm{2D}}$ of
+to extract $\varepsilon_{\mathrm{2D}}$ and $\delta^{*}_{\mathrm{2D}}$ of
 selected 2H TMDCs simultaneously from \textit{ab initio}
 $\varepsilon_{\mathrm{SL}}$ -- $L$ data in
-Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{b} (details see
+Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{c} (details see
 Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
@@
 out-of-plane data, respectively, are shown in Supplementary
-Table~\ref{SI-tab:delta-L-DFt}. As seen in Figure
-\ref{fig-emt}\textbf{b}, the estimation error of the thickness
-estimated from different directions is around 0.06$\sim{}$0.27
-\AA{}. Although such uncertainty only corresponds to about
-1$\sim{}$4\% of the interlayer spacing in the bulk counterparts of
-these 2D materials, its influence on the calculated values
+Table~\ref{SI-tab:delta-L-DFt}.
+%
+% As seen in Figure
+% \ref{fig-emt}\textbf{b}, the estimation error of the thickness
+% estimated from different directions is around 0.06$\sim{}$0.27
+% \AA{}.
+%
+Although the uncertainty only corresponds to several percent of the
+interlayer spacing in the bulk counterparts of these 2D materials, its
+influence on the calculated values
 $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
@@
 dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
-$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta_{\mathrm{2D}}$ deviates
-from the best fitted value by $\pm{}$2.5 \AA{}, as shown in Figures
-\ref{fig-emt}\textbf{c} and \ref{fig-emt}\textbf{d},
+$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta^{*}_{\mathrm{2D}}$
+deviates from the best fitted value by $\pm{}$2.5 \AA{}, as shown in
+Figures \ref{fig-1}\textbf{d} and \ref{fig-1}\textbf{e},
 respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
-with $\delta_{\mathrm{2D}}$ with a uncertainty of $\sim{}$10\%, while
-strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans over
-more than one order of magnitude. The sensitivity of
-$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta_{\mathrm{2D}}$ explains
-the discrepancy in literature that both isotropic~\cite{Sohier_2016}
-and highly anisotropic~\cite{Matthes_2016,Laturia_2018}
+with $\delta^{*}_{\mathrm{2D}}$,
+while strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans
+over more than one order of magnitude. The sensitivity of
+$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta^{*}_{\mathrm{2D}}$
+explains the discrepancy in literature that both
+isotropic~\cite{Sohier_2016} and highly
+anisotropic~\cite{Matthes_2016,Laturia_2018}
 $\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
@@
 formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
-generally at the order of 10\textsuperscript{-4} (Supplementary Figure
-{\color{red} XX}). In addition, the calculation of
+generally at the order of 10\textsuperscript{-4} (Supplementary
+Figure~\ref{SI-fig:alpha-converg}). In addition, the calculation of
 $\alpha_{\mathrm{2D}}$ technically simpler than
@@
 band degeneracy, and $C^{\perp} = {\varepsilon_{0}}^{-1}$. It is worth
-noting, unlike the parameter $\delta_{\mathrm{2D}}$ that is
+noting, unlike the parameter $\delta^{*}_{\mathrm{2D}}$ that is
 artificially assigned within the EDM picture (see previous section),
-$\hat{\delta_{\mathrm{2D}}}$ can be uniquely defined by
+$\hat{\delta^{*}_{\mathrm{2D}}}$ can be uniquely defined by
 $\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
@@
 \includegraphics[width=0.75\linewidth]{img/fig1.pdf}
-\caption{\label{fig-1} \textbf{2D polarizability as the true
-    descriptor of the dielectric nature of 2D materials.}
+\caption{\label{fig-1} \textbf{2D polarizability and the breakdown of
+    effective dielectric model
+    (EDM)} % \textbf{2D polarizability as the
+  % true descriptor of the dielectric nature of 2D materials.}
   \textbf{a}. 3D illustration of the spatial distribution of the
   charge density change $\Delta \rho(z)$ along the z-direction for
-  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under external
-  eletric field of 0.01 V/\AA{}.  The green and red regions represent
-  negative and positive induced charges, respectively. The macroscopic
-  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under
+  external eletric field of 0.01 V/\AA{}.  The green and red regions
+  represent negative and positive induced charges, respectively. The
+  macroscopic $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
   $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
-  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
-  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
-  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
+  size $L$, while the 2D polarizabilities
+  $\alpha_{\mathrm{2D}}^{\parallel}$ and
+  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size
+  \textbf{b}.  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
   $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
@@
   constant when $L>$15 \AA{}, compared with the $L$-dependence of
-  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
-  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
-  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
-  \ref{eq:alpha-perp-def}, respectively.
+  $\varepsilon_{\mathrm{SL}}$. On the other hand, the EDM approach
+  which usually used in literature to extract the effective 2D
+  dielectric constant $\varepsilon_{\mathrm{2D}}$, fails to produce
+  consistent results, estimation uncertainty of the effective layer
+  thickness $\delta^{*}_{\mathrm{2D}}$, causes huge variations of
+  $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{d}) and
+  $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{e}).
   % HSE06 functional is used in all plots.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
-  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
-      ``dielectric constant'' picture based on the effective medium
-      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
-    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
-    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
-    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
-    not well-defined. \textbf{b}.  Estimation error between
-    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
-    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
-    of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
-    2D TMDCs. The uncertainty of
-    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
-    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
-    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
-\end{figure}
+% \begin{figure}[H]
+%   \centering
+%   \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
+%   \caption{\label{fig-emt} \textbf{Failure of the effective 2D
+%       ``dielectric constant'' picture based on the effective medium
+%       theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
+%     effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
+%     is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
+%     the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
+%     not well-defined. \textbf{b}.  Estimation error between
+%     $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
+%     $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
+%     of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
+%     2D TMDCs. The uncertainty of
+%     $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
+%     $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
+%     particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
+% \end{figure}
 

### 2019-10-14 src/distance/alpha_convergence.py

@@ -86,7 +86,7 @@ for i, item in enumerate(g):
 ax1_r.set_xlabel("$L$ ($\\AA$)")
 ax1_r.set_title("parallel")
 # ax1.set_ylabel("$\\epsilon^{\\parallel}_{\mathrm{SL}}$")
-ax1_r.set_ylabel("$\\alpha^{\\parallel}/(4\\pi\\varepsilon_0) (\\AA)$")
+ax1_r.set_ylabel("$\\Delta \\alpha^{\\parallel}_{\\mathrm{2D}}/(4\\pi\\varepsilon_0) (\\AA)$")
 ax1_r.set_yscale("log")
 # ax1.set_xticklabels([])
 # ax1_r.set_ylim(min(alpha_SL) * 0.75, max(alpha_SL)* 1.25)
@@ -94,7 +94,7 @@ ax1_r.set_yscale("log")
     # ax.plot(LL, fit_vert(LL, *param), "--")
 ax2_r.set_xlabel("$L$ ($\\AA$)")
 # ax2.set_ylabel("$\\epsilon^{\\perp}_{\mathrm{SL}}$")
-ax2_r.set_ylabel("$\\alpha^{\\perp}/(4\\pi \\varepsilon_0) (\\AA)$")
+ax2_r.set_ylabel("$\\Delta \\alpha^{\\perp}_{\\mathrm{2D}}/(4\\pi \\varepsilon_0) (\\AA)$")
 ax2_r.set_title("perp")
 ax2_r.set_yscale("log")
 # ax2.set_ylim(1, 4)

### 2019-12-22 paper.tex
update toc & main

@@
 \author{Lu Hua Li}
-\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
+\affiliation{Institute for Frontier Materials, Deakin University, Victoria, VIC 3216, Australia}
 \author{Chih-Jen Shih}
@@
 \author{Jonathan Coleman}
-\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
+\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland}
 \author{Manish Chhowalla}
@@
 
-\begin{tocentry}
-  \centering
- \includegraphics[height=3.5cm]{img/toc.pdf}
-\end{tocentry}
+% \begin{tocentry}
+ % \centering
+% \includegraphics[width=0.70\linewidth]{img/toc_v121719.pdf}  %toc.pdf  
+% \end{tocentry}
+%
+%
+%  \includegraphics[width=0.70\linewidth]{img/fig1.pdf}
 
@@
   several electronic and optoelectronic properties important for a 
-  plethora of modern technologies, and its importance of 
-  % from computer memory to field effect
-  % transistors and communication circuits. Moreover, the importance of
-  % the dielectric constant in
+  plethora of modern technologies 
+  from computer memory to field effect
+  transistors and communication circuits. Moreover, the importance of
+  the dielectric constant in 
   describing electromagnetic interactions through screening plays a
@@
   of a 2D material which is united to other physical quantities in an
-  atomically thin layer. Being a quantity with unique definition, the
-  electronic polarizability overcomes the disadvantage of uncertainty
-  posed by the effective dielectric constant model conventionally used
-  to described screening in 2D material systems.  Furthermore, we
-  reveal a long-sought universal formalism where electronic,
+  atomically thin layer. 
+ %
+  %
+%  Being a quantity with unique definition, the
+%  electronic polarizability overcomes the disadvantage of uncertainty
+%  posed by the effective dielectric constant model conventionally used
+%  to described screening in 2D material systems.  
+  We reveal a long-sought universal formalism where electronic, 
   geometrical and dielectric properties are intrinsically correlated  
@@
   not directly measurable including the real covalent thickness of a 
-  layer. Lastly, we unify the concept of dielectric properties in any
+  layer. We unify the concept of dielectric properties in any 
   material dimension finding a global dielectric anisotropy index
@@
 plays a crucial role in bridging various fundamental material
-properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
+properties, such as bandgap \cite{Moss_1950_relation,Moss_1985_n_Eg}, 
 optical absorption\cite{kittel_2005_introduction} and 
-conductivities\cite{Dressel_2001_electrodynamics}   
+conductivity \cite{Dressel_2001_electrodynamics}   
 with elemental interactions. 
@@
 where is common to classify a material accordingly to its ability to screen an 
-electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
-condensed matter physics, as well as in related fields in chemistry and materials science. 
-The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
-theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
-% where the probe of the dielectric properties 
-% is made through an external electric field. 
-%
-Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
-% electronic and
-dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
+electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. 
+Such definitions determine a broad range of 
+condensed matter physics, as well as in related 
+fields in chemistry and materials science. 
+The ability to compute and measure $\varepsilon$ in 
+bulk materials is well established via different 
+theoretical \cite{Adler_1962,Hybertsen_1987} and 
+experimental techniques \cite{palik_1998handbook} of distinct flavors
+where the probe of the dielectric properties 
+is made through an external electric field. 
+%
+Despite its obvious appeal, however, it is 
+still unknown whether such quantity can determine the 
+electronic and dielectric properties of 
+two-dimensional (2D) materials \cite{Novoselov_2016}.  
 %
@@
 \cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
-have generated long-standing debates whether the dielectric constant
-truly represents dielectric features of such low-dimensional systems,
-% or it can be used only as an
-% additional parameter from the bulk-counterparts.
-The controversy of
-$\varepsilon$ values reported by both theoretical and experimental
-approaches can be widely seen throughput literature\cite{Li_2016},
+has generated long-standing debates whether the dielectric constant
+truly represents the dielectric features of such low-dimensional systems. 
+%or it can be used only as an
+%additional parameter from the bulk-counterparts.
+%
+%
+The controversy of values
+reported by both theoretical and experimental
+approaches can be widely seen throughout the specialized 
+literature, see Ref.\cite{Li_2016} for a summary,
 where the variation of $\varepsilon$ can be more than one order of
 magnitude. As a consequence, several key physical parameters that
-scales with $\varepsilon$, such as the exciton binding energy and
+scale with $\varepsilon$, such as the exciton binding energy and
 Debye screening length, cannot be reliably estimated due to the
-discrepancy of reported $\varepsilon$ values. In this letter, we give
-a thorough study of the underlying issue. Using \textit{ab initio}
-simulations of a model system, we demonstrate that the macroscopic
-dielectric constant strongly depends on the size of the superlattice,
-making it unsuitable to describe the screening of a 2D material. On
-the contrary, by analyzing the formalism of dielectric tensors, we
-propose that the electronic polarizability is the true descriptor
-which uniquely captures the dielectric nature of 2D materials. The 2D
-electronic polarizability has unique definition, which overcomes the
-disadvantage of ambiguity compared with the conventionally used
-effective dielectric medium model for 2D materials. Moreover, we show
-the universal scaling relations for in- and out-of-plane 2D electronic
-polarizabilities with the electronic and geometric information of the
-2D material. The concept of electronic polarizabilities bridges the
-gap between the dielectric properties of 2D and 3D systems, and can be
-extended to characterize the dielectric anisotropy for any material
-dimensions.
+discrepancy of the reported magnitudes of $\varepsilon$.
+
+Here, by using a combination of analytical and numerical models liaised with 
+highly-accurate first-principles methods involving high-throughput screening 
+techniques, we show that the dielectric constant does not provide a reliable
+description of the screening features of a 2D material. The interplay between local 
+electrostatic interactions in the monolayer and the volume dependence 
+in the definition of $\varepsilon$ makes such quantity questionable. 
+%
+%
+We propose however that the electronic polarizability that describes 
+the electron dipole in the 2D material as the true descriptor 
+of its dielectric nature. 
+%
+%
+We overcome several problems intrinsic to thin layers not achievable using conventional 
+effective dielectric medium models, such as the real thickness of a monolayer and 
+any dependence on the long-range Coulomb potential. 
+We unveil universal scaling relations between electronic and dielectric properties through 
+the electronic polarizability, such as band gaps, optical spectra and exciton radius, for the 
+current library of known 2D materials involving different lattice symmetries, 
+atomic elements and chemical and physical properties. 
+%
+Moreover, the concept of electronic polarizabilities bridges the
+gap between the dielectric properties of 2D and 3D systems through a novel 
+dielectric anisotropy index that generalized the concept of dielectric control 
+using dimensionality and bandgap. 
+Our results open a new avenue for the study of the 
+dielectric properties of 2D compounds using techniques yet to be explored.
+
+%and can be
+%extended to characterize the dielectric anisotropy for any material
+%dimensions.
 
@@
 of 2D materials, by showing that the current definition of
-$\varepsilon$ used in layered materials is ill defined.  This can be
+$\varepsilon$ used in layered materials is {ill-defined}.  This can be
 viewed in a model system as illustrated
@@
 $\boldsymbol{P}^{p}$ under small perturbative external field
-$\boldsymbol{E}^{q}$, where $p$, $q$ are the directions of
-polarization and electric field,
+$\boldsymbol{E}^{q}$, where $p$, $q$ determine their directions,
 respectively~\cite{Dressel_2001_electrodynamics}:
@@
     &\varepsilon_{\mathrm{SL}}^{pq} &= \kappa^{pq} +
-                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
-                                 {\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
+                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}{\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
           \label{eq:def-eps-2}
@@
                           = {\displaystyle \frac{{\displaystyle
-          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}
-                          {AL}}
+          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}{AL}}
   \end{eqnarray}
@@
 supercell, $A$ is the \textit{xy}-plane area of the SL and
-$\varepsilon_{0}$ is vacuum permittivity. Here we limit out study on
-the electronic contribution to the macroscopic dielectric constant
-where the dipole $\boldsymbol{P}$ comes from the displacement of
-electrons under external field.  On the other hand, the ionic
-contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
-displacement of atomic nuclei is not covered in this due to its
-complex dependency on several factors including phonon
-dispersion~\cite{Sohier_2017} as well as lattice
-symmetry~\cite{Laturia_2018}, which requires separated discussions.
-The symmetry of 2D materials lead to the negligible off-diagonal
-elements of the dielectric tensor ($p \neq q$), while and diagonal
+$\varepsilon_{0}$ is vacuum permittivity. Here we limit our study on
+the electronic contributions to the macroscopic dielectric constant
+where the dipole $\boldsymbol{P}$ results from the response 
+of the electron density under an external field.  
+Ionic contributions\cite{Sohier_2017} to $\varepsilon_{\mathrm{SL}}$ 
+have previously been shown to be negligible\cite{relax-epsilon} and 
+are not considered here.  
+%
+%On the other hand, the ionic
+%contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
+%displacement of atomic nuclei is not covered in this due to its
+%complex dependency on several factors including phonon
+%dispersion~\cite{Sohier_2017} as well as lattice
+%symmetry~\cite{Laturia_2018}, which requires separated discussions.
+The symmetry of 2D materials leads to inappreciable off-diagonal
+elements of the dielectric tensor ($p \neq q$), while the diagonal
 elements $\varepsilon_{\mathrm{SL}}^{xx}$,
 $\varepsilon_{\mathrm{SL}}^{yy}$ and $\varepsilon_{\mathrm{SL}}^{zz}$
-can be different \cite{Sohier_2016}.  Considering that the 2D material
+can be different \cite{Sohier_2016}.  
+%
+Considering that the 2D material
 is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
@@
 The absence of bonding perpendicular to the plane confines the induced
-dipoles along the \textit{z}-direction within a range of $\sim{}$5--6
+dipole moments along the \textit{z}-direction within a range of $\sim$5--6
 \AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and Supplementary
@@
 %
-Under a certain external field, when $L$ increases, the confinement of
+Under a given external field, the strong confinement of
 the induced dipole moment $\boldsymbol{u}$ causes the integral in the 
-numerator of Eq.~\ref{eq:def-eps-2} to be saturated, when the
-separation is large enough such that dipole moment from periodic
-images do not mutually interfere. On the other hand, the increase of
-$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the polarization density, and in turn makes both
+numerator of Eq.~\ref{eq:def-eps-2} to be converged within few \AA's 
+resulting that the dipole moment from the periodic supercell 
+images do not mutually interfere. 
+%
+
+Conversely, the increase of
+$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the 
+polarization density, and in turn makes both
 $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
 $\varepsilon^{\perp}_{\mathrm{SL}}$ dropping to
-unity when $L$ is infinitely large.
+unity when $L$ is infinitely large, which is not physical. 
 % In the case of bulk materials
@@
 % perpendicular to the plane.
-Despite of the simplicity of this argument, any calculation performed
+Despite the simplicity of this argument, any calculation performed
 using such definition will intrinsically depend on the magnitude of
-$L$, an artificial parameter introduced by simulation system. This
+$L$, an artificial parameter introduced by the simulation setup. This
 dependence can be clearly demonstrated by plotting
@@
 \ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c}, respectively). To
-get a better description of the electronic band structure, the
+obtain a better description of the electronic band structure, the
 calculations of dielectric properties were performed at the level of
 Heyd-Scuseria-Ernzerhof (HSE06) hybrid functional
-\cite{Heyd_2003,Heyd_2006}.  Both components of the dielectric
-constant decreases with $L$ as excepted. To rule out the possibility
-that the result is affected by the choice of \textit{ab initio}
-methods, we also performed simulations at higher levels of theory
+\cite{Heyd_2003,HSE_2006}.  Both components of the dielectric
+constant decrease with $L$ as excepted. To rule out the possibility
+that the result is affected by the choice of the functional, 
+we performed simulations at higher levels of theory
 using many-body techniques (G$_{0}$W$_{0}$), which invariably give
 alike results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).
-The lattice-size dependency also exists for dielectric function in the
-frequency ($\omega$) domain. We carried out similar analysis for
+The lattice-size dependency also exists for the dielectric function in the 
+frequency domain.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.70\linewidth]{img/fig1.pdf}
+\caption{\label{fig-1} \textbf{2D polarizability and the breakdown of
+    effective dielectric model
+    (EDM)} % \textbf{2D polarizability as the
+  % true descriptor of the dielectric nature of 2D materials.}
+  \textbf{a,} 3D illustration of the spatial distribution of the
+  charge density change $\Delta \rho(z)$ along the z-direction for
+  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under
+  external eletric field of 0.01 V/\AA{}.  The green and red regions
+  represent negative and positive induced charges, respectively. The
+  macroscopic $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
+  size $L$, while the 2D polarizabilities
+  $\alpha_{\mathrm{2D}}^{\parallel}$ and
+  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant to $L$.
+  \textbf{b,} $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
+  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. 
+  \textbf{c,} $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
+  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
+  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
+  constant when $L>$15 \AA{}, compared with the $L$-dependence of
+  $\varepsilon_{\mathrm{SL}}$. 
+  %
+  %
+  {\bf d-e,} Estimated $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
+  $\varepsilon_{\mathrm{2D}}^{\perp}$, respectively, using EDM  
+  as a function of the uncertainty of the effective layer
+  thickness $\delta^{*}_{\mathrm{2D}}$. The inset in {\bf e,} shows schematically the main parameters
+  utilized in EMD: the vacuum layer ($\varepsilon^{}_{\mathrm{0}}$), an approximate thickness of the layer   which is given by $\delta^{*}_{\mathrm{2D}}$, and the obtained $\varepsilon^{}_{\mathrm{2D}}$.
+The length of the box perpendicular to the surface of the layer is given by $L$ (not shown).
+  %
+  Overall, there is a large variation and associated errors
+  to both components of the dielectric constant for small changes of $\delta^{*}_{\mathrm{2D}}$ in the range of $\pm7.5$\%.  
+  %
+  % HSE06 functional is used in all plots.
+}
+\end{figure}
+
+We carried out similar analysis for
 frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
-and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different levels
-of techniques, including Perdew-Burke-Ernzerhof (PBE)
+and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different 
+approaches including Perdew-Burke-Ernzerhof (PBE)
 exchange-correlation functional
-\cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, many-body Green function
-method (G\textsubscript{0}W\textsubscript{0})~\cite{Hedin_1965} and
-Bethe-Salpethe equation (BSE)~\cite{Onida_2002}, with increasing
-accuracy of calculated optical properties (PBE $<$
-G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
-many-body screening and excitonic effects (details see Supplementary
-Section \ref{SI-ssec:gw}). Despite various levels of theory involved,
-the magnitude of dielectric functions calculated universally decreases
-with $L$ over the frequency domain.  These results indicate that
-quantities that depend on
+\cite{Perdew_1996,Ernzerhof99,Paier_2005_PBE}, 
+G\textsubscript{0}W\textsubscript{0}\cite{Hedin_1965} and
+Bethe-Salpeter equation (G\textsubscript{0}W\textsubscript{0}$-$BSE)\cite{Onida_2002} (see Supplementary Section \ref{SI-ssec:gw} and 
+Supplementary Figures \ref{SI-fig:PBE-omega-in}$-$\ref{SI-fig:BSE-omega-out}). 
+%
+%with increasing
+%accuracy of calculated optical properties (PBE $<$
+%G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
+%many-body screening and excitonic effects (details see Supplementary
+%Section \ref{SI-ssec:gw}). 
+%
+Despite the various levels of theory analyzed and the increased 
+accuracy of the calculated optical properties due to the inclusion of 
+many-body screening and excitonic effects, 
+the magnitude of the dielectric function universally decreases
+with $L$ over the frequency. The underlying physical reason for such 
+dependence can be noticed in the definition of the dielectric 
+function versus $\omega$ shown in Eqs. \ref{SI-eq:dft-dielectric}$-$\ref{SI-eq:dft-dielectric-real}, which also depend on the volume of the unit cell. 
+%
+These results indicate that any 
+quantity that depends on
 $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
-$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
-absorption (abs., equivalent to $\mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), refractive index ($n$,  $\sim{}\sqrt{\mathrm{Re}(\varepsilon_{\mathrm{SL}})}$) and electron energy loss spectrum (EELS, equivalent to $-1 / \mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), suffers the same
-deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
-simple model system explains the origin of the discrepancy of
-dielectric constant values reported in previous
-literature~\cite{Li_2016}.
-%
-%%%
-%
-% We observe that neither
-% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
-% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
-% that the long-range Coulomb interaction could not be completed
-% screened within the range of magnitudes computationally accessible
-%.
-%
-%
-%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
-%it impractical to represent the dielectric nature of a 2D material
-%both theoretically and experimentally, because the size of vacuum
-%layer must always be considered. 
-%
+$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, such as the optical
+absorption ($\mathrm{Im}\{\varepsilon_{\mathrm{SL}}(\omega)\}$), refractive index ($n=\sqrt{\mathrm{Re}\{\varepsilon_{\mathrm{SL}}\}}$) and electron energy loss spectrum (EELS, $\mathrm{Im}\{-1/\varepsilon_{\mathrm{SL}}(\omega)\}$), suffers the same deficiencies for 2D materials.
 
@@
 material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
-with $L$, we obtain the sheet polarization density that is,
-$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, in
+with $L$, we obtain the sheet polarization density, that is,
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, along the
 direction $p$. Following the discussion in the previous section,
-$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of lattice
-size when $L$ is large enough, due to the saturation of
-$\boldsymbol{u}^{p}$.
-%
-Similar to the molecular polarizability \cite{Israelachvili_2011}, we
-can define a 2D electronic polarizability $\alpha_{\mathrm{2D}}$ which
-characterizes the ability to induce dipole moment of a 2D material. It
-is associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
+$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of the
+lattice size when $L$ is large enough, due to the short decay of the 
+induced charge density $\Delta \rho$ into the vacuum (see
+Supplementary Figure \ref{SI-fig:rho-profile}).
+%
+Similar to the molecular polarizability\cite{Israelachvili_2011}, we
+utilize the concept of electronic polarizability
+$\alpha_{\mathrm{2D}}$, 
+which has been used previously to solve
+exciton-related problems in 2D materials
+\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. 
+%
+$\alpha_{\mathrm{2D}}$ is a macroscopic quantity that characterizes
+the ability to induce dipole moments in a 2D material, and is
+associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
 $\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
-\alpha_{\mathrm{2D}}^{pq} \boldsymbol{E}_{\mathrm{loc}}^{q}$
-\cite{T_bik_2004}, where $\boldsymbol{E}_{\mathrm{loc}}$ is the local
-electric field causing the polarization. At $L \rightarrow \infty$
-limit, $E_{\mathrm{loc}}$ can be solved using electrostatic boundary
-conditions of slab geometry \cite{Markel_2016}. The continuity of the
-electric field along the in-plane direction gives
-$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
+\alpha_{\mathrm{2D}}^{pq} \boldsymbol{\overline{E}}_{\mathrm{loc}}^{q}$\cite{T_bik_2004}, where
+$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is the cell-averaged
+``local'' electric field acting on the 2D material to induce
+polarization\cite{Wiser_1963}.
+% 
+Alike to $\mu_{\mathrm{2D}}$,
+$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is also a macroscopic
+quantity that excludes the fields generated by the dipoles of the 2D
+sheet from $\boldsymbol{E}$. Note the term ``local'' in
+$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is adapted to resemble the
+Lorentz model\cite{Wiser_1963} which has also been used for other
+low-dimensional materials (e.g. nanotube\cite{Benedict_1995} and
+molecules\cite{T_bik_2004}, and should be distinguished with the
+microscopic local field $\boldsymbol{E}_{\mathrm{loc}}(\boldsymbol{r})$ which is spatially
+changing.
+%
+
+Such macroscopic treatment of polarizability is valid when the length
+of the superlattice is significantly larger than the spatial
+distribution of induced charges.  At $L \rightarrow \infty$ limit,
+$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ can be solved using
+electrostatic boundary conditions of the slab geometry
+\cite{Markel_2016,Meyer_2001_dipole_slab}. The continuity of the electric field along the
+in-plane direction gives
+$\boldsymbol{\overline{E}}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
 while for the out-of-plane component, the dipole screening yields
-$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
+$\boldsymbol{\overline{E}}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
 \cite{Meyer_2001_dipole_slab,T_bik_2004}, where
 $\boldsymbol{E}^{\parallel}$ and $\boldsymbol{E}^{\perp}$ are the
-external field in the in-plane and out-of-plane directions,
+external field along the in-plane and out-of-plane directions,
 respectively. Combining with Eqs. \ref{eq:def-eps-1} and
-\ref{eq:def-eps-2},
-$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-can be related with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
+\ref{eq:def-eps-2}, $\alpha_{\mathrm{2D}}^{\parallel}$ and
+$\alpha_{\mathrm{2D}}^{\perp}$ can be related with
+$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
 $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
@@
 %
-Using these relations, we show the calculated
+Using these relations, we show that the calculated
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
@@
 $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
+$\varepsilon_{\mathrm{SL}}^{\perp}$, we observe that both
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-reach convergence when $L$ exceeds 10 \AA and 15 \AA,
-respectively. Such result is in good agreement with the spatially
-localized induced dipole moment of a 2D materials as shown in
+reach convergence when $L \sim$10 \AA $, ~$15 \AA,
+respectively. Such results are in good agreement with the spatially
+localized induced dipole moment of a 2D material as shown in
 Supplementary Figure~\ref{SI-fig:rho-profile}.
@@
 I think it is better not to explicitly mention this.}
-Such relations can also be used to remove the dependence on $L$ for
-frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
+Equations \ref{eq:alpha-para-def}$-$\ref{eq:alpha-perp-def} can 
+also be used to remove the dependence on $L$ for
+$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
 and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
@@
 $\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
-respectively (details see Supplementary Section \ref{SI-ssec:gw}).
+respectively (see details in Supplementary Section \ref{SI-ssec:gw}).
 %
@@
 These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
-of the dielectric properties of 2D materials.
-In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
-More discussions about the choice of the
+of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has 
+a unique definition, and does not suffer from the dependency on the lattice size.
+It is worthy mentioning that Eqs.\ref{eq:alpha-para-def}$-$\ref{eq:alpha-perp-def} were 
+obtained using purely electrostatic arguments without any assumption 
+regarding the medium where the 2D material is immersed or a capacitance 
+model where an effective dielectric response can be extracted. 
+More details about the choice of the
 2D polarizability, comparison with other methods, simulations at the
@@
 
-\subsection{Comparison with effective dielectric model (EDM)}
+\subsection{Comparison with the effective dielectric model (EDM)}
 \label{sec:comp-with-effect}
 
-Apart from the 2D electronic polarizability proposed here, it is worth
-mentioning that the effective dielectric model (EDM) is widely used in
+Apart from the 2D electronic polarizability proposed here,  
+the effective dielectric model (EDM) is commonly used in
 literature to treat the 2D material as a slab with an effective
@@
 \cite{Sohier_2016,Meckbach_2018} of 2D materials. The EDM allows
-applying physical laws of bulk systems directly to 2D materials using
+applying physical concepts of bulk systems directly to their 2D counterparts using
 $\varepsilon_{\mathrm{2D}}$. However, there are several drawbacks of
-such approach, first of all, the wavevector($q$)-dependency of
+such approach. For instance, the wavevector $q$-dependency of
 dielectric screening in 2D
@@
 seen in the inset of Figure~\ref{fig-1}\textbf{e}, where the macroscopic
-$\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
-2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
-and thickness $\delta^{*}_{\mathrm{2D}}$ and (ii) vacuum spacing with
+$\varepsilon_{\mathrm{SL}}$ is considered to be composed by ({\it i}) a
+2D slab with an effective dielectric constant $\varepsilon_{\mathrm{2D}}$
+and a thickness $\delta^{*}_{\mathrm{2D}}$, and ({\it ii}) a vacuum spacing with
 distance $L-\delta^{*}_{\mathrm{2D}}$. Using the effective medium theory
-(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
+(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between  %Tancogne_Dejean_2015 
 $\varepsilon_{\mathrm{SL}}$ and $\varepsilon_{\mathrm{2D}}$ can be
 expressed using capacitance-like
-equations~\cite{Matthes_2016,Laturia_2018} :
+equations~\cite{Matthes_2016,Laturia_2018,Tancogne_Dejean_2015}:
 \begin{subequations}
   \begin{eqnarray}
-    \label{eq:emt-1}
+    \label{Response:1}
     {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta^{*}_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta^{*}_{\mathrm{2D}}}{L} \right)}\\
@@
 $\varepsilon_{\mathrm{SL}}$ -- $L$ data in
-Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{c} (details see
+Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{c} (see details in 
 Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
@@
 %
-Although the uncertainty only corresponds to several percent of the
-interlayer spacing in the bulk counterparts of these 2D materials, its
+Although the uncertainty only corresponds to a few percent of the
+interlayer spacing in the bulk structure of these 2D materials, its
 influence on the calculated values
 $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
-$\varepsilon_{\mathrm{2D}}^{\perp}$ is significant. We estimated the
-dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
-$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta^{*}_{\mathrm{2D}}$
-deviates from the best fitted value by $\pm{}$2.5 \AA{}, as shown in
-Figures \ref{fig-1}\textbf{d} and \ref{fig-1}\textbf{e},
-respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
-with $\delta^{*}_{\mathrm{2D}}$,
-while strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans
-over more than one order of magnitude. The sensitivity of
+$\varepsilon_{\mathrm{2D}}^{\perp}$ is substantial. 
+We estimated the dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
+$\varepsilon_{\mathrm{2D}}^{\perp}$ considering slightly deviations of 
+$\delta^{*}_{\mathrm{2D}}$ from the best fitted value by $\pm{}$7.5\%{} 
+(Figures \ref{fig-1}\textbf{d} and \ref{fig-1}\textbf{e}). 
+%
+%
+Strikingly, $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
+with $\delta^{*}_{\mathrm{2D}}$, while $\varepsilon_{\mathrm{2D}}^{\perp}$ spans
+over more than one order of magnitude. 
+%
+The sensitivity of
 $\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta^{*}_{\mathrm{2D}}$
-explains the discrepancy in literature that both
+explains the discrepancy in literature for both
 isotropic~\cite{Sohier_2016} and highly
 anisotropic~\cite{Matthes_2016,Laturia_2018}
-$\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
-reported. As a consequence, the estimated values of
+$\varepsilon_{\mathrm{2D}}$ tensors on 2D materials extracted 
+using EDM. 
+%
+As a consequence, the estimated values of
 $\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
-is highly questionable.
+are highly controversial.
 
 On the contrary, the proposed $\alpha_{\mathrm{2D}}$ approach does not
-suffer from such deficiencies, despite its relatively simple
+suffer from such limitations, despite its relatively simple
 formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
@@
 Figure~\ref{SI-fig:alpha-converg}). In addition, the calculation of
-$\alpha_{\mathrm{2D}}$ technically simpler than
-$\varepsilon_{\mathrm{2D}}$: (i) $\alpha_{\mathrm{2D}}$ can be
+$\alpha_{\mathrm{2D}}$ is technically simpler than 
+$\varepsilon_{\mathrm{2D}}$: ({\it i}) $\alpha_{\mathrm{2D}}$ can be
 achieved using single-point calculation of macroscopic dielectric
 tensor, while $\varepsilon_{\mathrm{2D}}$ requires non-linear fitting
-of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; (ii) the
-values of $\alpha_{\mathrm{2D}}$ typically converge well for large $L$
-($>$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
-uncertainty as described above.
+of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; ({\it ii}) the
+values of $\alpha_{\mathrm{2D}}$ typically converge well for $L$
+($\sim$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
+uncertainties as described above.
 
@@
 
-For bulk materials, pioneering works from the 1950s have demonstrated
+For bulk materials, pioneering works from the 1950s had demonstrated
 empirical equations between $\varepsilon$ and the bandgap
@@
 $\mathbf{k} \cdot \mathbf{p}$
-formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
-depending on the electronic and geometric information of a 2D material (see
-Supplementary Section \ref{SI-sec:theory-1} for details):
+formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the following 
+universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
+for 2D materials (see Supplementary Section \ref{SI-sec:theory-1} for details): 
 % \begin{subequations}
@@
 \label{eq:2D-Moss-para}
-  &E_{\mathrm{g}} &= C^{\parallel} \alpha_{\mathrm{2D}}^{\parallel} \\
+  &E_{\mathrm{g}} &= C^{\parallel}/ \alpha_{\mathrm{2D}}^{\parallel} \\
   \label{eq:2D-Moss-perp}
@@
 layer, with coefficients
-$C^{\parallel} = {\displaystyle \frac{2 \pi}{Ne^2}}$
+$C^{\parallel} = {\displaystyle \frac{Ne^2}{2 \pi}}$
 \cite{Jiang_2017_Eg_Eb}, where $N$ is a pre-factor associated with the
@@
 artificially assigned within the EDM picture (see previous section),
-$\hat{\delta^{*}_{\mathrm{2D}}}$ can be uniquely defined by
+$\hat{\delta}_{\mathrm{2D}}$ can be uniquely defined by
 $\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
-computationally and experimentally determined. Despite of the
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
+\caption{\label{fig-3} \textbf{The universal scaling relation of the
+    dielectric nature of 2D materials}. 
+    %%
+    \textbf{a,} The structures of
+  the 2D materials investigated in this 
+  study. 
+  %%
+  \textbf{b,} $\alpha_{\mathrm{2D}}^{\parallel}$,
+  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
+  (blue dots) for all the 2D materials studied.
+  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
+  increasing $E_{\mathrm{g}}$, while no apparent relation between
+  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
+  observed. HSE06 functional is used to obtain the data. 
+  %%
+  \textbf{c,} $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
+  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
+  correlation between each other. The energy range of visible light is
+  shown in the background. 
+  %%
+  \textbf{d,} $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$ (in \AA{}) as a
+  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
+  in the inset), showing a perfect linear relation with a slope very
+  close to $1$ (i.e.
+  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
+  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
+  revealed using different databank from 
+  from Ref.~\citenum{Haastrup_2018} (squares),
+  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
+  \textbf{c} and \textbf{d}. Data corresponding to 2H-MX$_2$ 
+  (M=Mo, W; X=O, S, Se, Te) is highlighted in {\bf d}. The very tiny 
+  difference in $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$
+  between compounds with different metal atoms 
+  gives superposed magnitudes not distinguishable in the plot. 
+  }
+\end{figure}
+%
+%
+computationally and experimentally determined. Despite the
 simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
-they generalize direct relationships between the electronic polarizability and
-the electronic / structural properties for any 2D material in a new
+they generate direct relationships between the electronic polarizability and
+the electronic/structural properties for any 2D material in a new
 framework.
@@
 library of known layered materials involving different lattice
-symmetry, element composition, optical and electronic properties.
+symmetry, element composition, optical and electronic properties (Figure \ref{fig-3}{\textbf a}).
 %
@@
 (P\textsubscript{4}) and thin layer organic-inorganic perovskites
-(ABX\textsubscript{3}) (Figure \ref{fig-3}{\textbf a}) shows that our
-method enables full correlation between these disparate variables.
+(ABX\textsubscript{3}), shows that our method enables 
+full correlation between these disparate variables.
+%
+%
 Figure \ref{fig-3}{\textbf b} compares the calculated fundamental
@@
 polarizabilities (bar plots) of all the 2D materials investigated,
-covering a wide spectrum range from far-infrared to ultraviolet.  Note
+covering a wide spectrum range from far-infrared to ultraviolet.  Note that 
 from dimension analysis, it is more intuitive to express the
@@
 \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D 
-materials investigated (circle dots) at HSE06 level.  A linear
+materials investigated using HSE06 hybrid functional 
+(circular dots) and PBE (triangles and squares).  
+%
+A linear
 regression coefficient of $R^{2}=0.84$ indicates a strong correlation
 between bandgaps and polarizabilities as predicted in
-Eq. \ref{eq:2D-Moss-para}.  We also discover that the linearity
+Eq. \ref{eq:2D-Moss-para}.  We also discovered that the linearity
 between $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
@@
 Section \ref{SI-sec:pol-2D-Eg} and Supplementary Figure
-\ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels of
-theory are needed to precisely predict bandgaps.  A detailed benchmark
+\ref{SI-fig:alpha-Eg-diff}). 
+This is reasonable as the bandgaps for 2D materials 
+obtained at the PBE functional, 
+although may be close to experimental reported 
+optical transition energies, are an artifact of the simulation due to a 
+fortuitous error cancellation\cite{Heine15,Lee_2017}. Thus, the use of a 
+time-consuming hybrid functional in our study is justified. 
+A detailed benchmark
 of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using
-different bandgaps, databases, and levels of calculation can be seen
-in Supplementary Section~\ref{SI-sec:gpaw}.
-
-We further examine the validity of Eq.~\ref{eq:2D-Moss-perp}, i.e.,
+different bandgaps, databases, and levels of theory can be seen
+in Supplementary Sections~\ref{SI-sec:pol-2D-Eg}$-$\ref{SI-sec:gpaw}.
+
+We further examine the validity of Eq.~\ref{eq:2D-Moss-perp}, that is,
 the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the thickness 
-of a 2D material. To test if the quantity $\hat{\delta_{\mathrm{2D}}}$
+of a 2D material. To test if the quantity $\hat{\delta}_{\mathrm{2D}}$
 is physical, we choose the ``covalent'' thickness 
-$\delta_{\mathrm{cov}}$ of a 2D material as a
-comparison. $\delta_{\mathrm{cov}}$ is defined as the longest distance
+$\delta_{\mathrm{cov}}$ as a comparison.  
+$\delta_{\mathrm{cov}}$ is defined as the longest distance
 along the \textit{z}-direction between any two atom nuclei plus their covalent
@@
 \end{equation}
+%
 where $i$, $j$ are atomic indices in the 2D material and
-$r_{\mathrm{cov}}^{i}$ is the covalent radius of atom $i$ (Figure
-\ref{fig-3}{\textbf d} inset). As shown in Figure~\ref{fig-3}{\textbf
+$r_{\mathrm{cov}}^{i}$ is the covalent radius of atom $i$ (inset in Figure
+\ref{fig-3}{\textbf d}). As shown in Figure~\ref{fig-3}{\textbf
   d}, $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ (or equivalently,
@@
 $\delta_{\mathrm{cov}}$. Similar to the molecular polarizability which
-characterizes the volume of the electron cloud of an isolated molecule
+characterizes the volume of the electron distribution of an isolated molecule
 \cite{Israelachvili_2011},
 $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also naturally
-related to the characteristic thickness of the electron cloud of 2D
+related to the characteristic thickness of the electron density of a 2D
 material. Supplementary Section
@@
 $\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is close to
-$\delta_{\mathrm{cov}}$. Our proposed definition of
-$\hat{\delta_{\mathrm{2D}}}$ of a 2D material based on
-Eq. \ref{eq:2D-Moss-perp} may have impact
+$\delta_{\mathrm{cov}}$. 
+%
+%
+The geometric nature of $\alpha_{\mathrm{2D}}^{\perp}$ leads to
+several interesting properties. For instance, the points corresponding
+to 2H-TMDCs with same chalcogenide element (i.e. 2H-MO$_{2}$,
+2H-MS$_{2}$, 2H-MSe2$_{2}$ or 2H-MTe$_{2}$, where M= Mo, W) 
+lie very close in Figure
+\ref{fig-3}\textbf{b} (detailed values see Supplementary Table
+S2). This can be briefly explained by the fact that the difference
+between covalent radii of transition metals (e.g. $\sim$8 pm between
+Mo and W) is much smaller than that between group 16 elements
+(e.g. $\sim$40 pm between O and S).
+%
+%
+Our proposed definition of
+$\hat{\delta}_{\mathrm{2D}}$ which is based on
+Eq. \ref{eq:2D-Moss-perp} will provide insights 
 on some long-existing controversies about the experimental thickness
-of 2D materials~\cite{Shearer_2016}, through the
-measurable quantity $\alpha_{\mathrm{2D}}^{\perp}$
+of 2D materials~\cite{Shearer_2016} through a 
+measurable quantity, e.g. $\alpha_{\mathrm{2D}}^{\perp}$
 \cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}.
@@
 Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using two
-different 2D material databases \cite{Haastrup_2018,Mounet_2018}, from
-which we extracted the dielectric properties of over 300 compounds
+different 2D-material databases based on different codes\cite{Haastrup_2018,Mounet_2018}. 
+%
+We extracted the dielectric properties of over 300 compounds
 calculated at the PBE level, and superimpose with our results in
-Figure \ref{fig-3}{\textbf c} and \ref{fig-3}{\textbf d}. Although the
-calculated dielectric properties may be different due to different
-choice of functionals as well as underestimation of the bandgap
-compared with the more accurate HSE06 functionals
-\cite{Van_Dyck_2017}, similar linear trends can be observed for both
-$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-with the linear coefficient very close to the HSE06 results, which
-further proves the validity of our proposed relations. We have also
+Figure \ref{fig-3}{\textbf c} and \ref{fig-3}{\textbf d}. 
+%
+The high-throughput datasets also show linear trends for both
+$(4\pi\varepsilon_0)/\alpha_{\mathrm{2D}}^{\parallel}$ (in \AA{}) vs
+$E_{\mathrm{g}}$ (in eV) ($y=0.190x - 0.0619$, $R^{2}=0.842$) and
+$\alpha_{\mathrm{2D}}^{\perp}$ vs $\delta_{\mathrm{cov}}$ (both in
+\AA{}, $y=0.904x + 0.0551$, $R^{2} = 0.943$) relations. We notice that the
+linear coefficients are similar but not identical to those calculated
+at the HSE06 level. The discrepancies may be due to several factors
+resulted from different choice of functionals, such as the underestimation
+of the bandgap in PBE, and different description of the 
+exchange-correlation potentials. 
+%
+We note that a more accurate estimation of the
+coefficients should be performed with larger datasets and accurate
+functionals which requires further work. Nevertheless, 
+the validity of the linear trends observed for
+$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ 
+is undeniable. We have also
 searched for additional relations between the 2D polarizabilities with
@@
 \label{sec:apply-electr-polar}
+%
+%
 The concept of electronic polarizability is not limited to monolayer
 materials, and can be applied to multilayer and bulk systems as
-well. For a 2D material stack composed of $N$ layers, we can define
-the electronic polarizability $\alpha_{\mathrm{NL}}$ similar to
-Eqs. \eqref{eq:alpha-para-def} and \eqref{eq:alpha-para-def}. Note
-$\alpha_{\mathrm{NL}}(N=1)$ is equivalent to $\alpha_{\mathrm{2D}}$.
+well. For a 2D-material stack composed of $N$ layers, we can define
+the electronic polarizability $\alpha_{\mathrm{NL}}$ similarly to
+Eqs. \ref{eq:alpha-para-def}$-$\ref{eq:alpha-perp-def} by replacing 
+$\alpha_{\mathrm{2D}}^{\parallel,\perp}$ to $\alpha_{\mathrm{NL}}^{\parallel,\perp}$. 
+%We assumed however that interlayer interactions are weak and calculate each magnitude of 
+%$\alpha_{\mathrm{2D}}^{\parallel,\perp}$ for a given stacking. 
+%
+%Note $\alpha_{\mathrm{NL}}(N=1)$ is equivalent to $\alpha_{\mathrm{2D}}$.
+%
+To check whether such assumption is valid, 
 Figure \ref{fig-4}\textbf{a} and \ref{fig-4}\textbf{b} show
 $\alpha_{\mathrm{NL}}^{\parallel}$ and $\alpha_{\mathrm{NL}}^{\perp}$
-as functions of $N$ for the selected 2H TMDCs,
+as functions of $N$ for several TMDCs in 2H-phase, 
 respectively. Interestingly, we find that in all cases,
@@
 \alpha_{\mathrm{2D}}^{\perp}$. Due to the relatively small
-electric applied (0.01 eV/\AA{}), the interlayer interactions within
-the stack are negligible. Under such circumstances, $\alpha_{\mathrm{2D}}$ of individual layers is additive, which leads to the following general relation:
+applied electric field (0.01 eV/\AA{}), the interlayer interactions within
+the stack are negligible. Under such circumstances, 
+$\alpha_{\mathrm{2D}}$ of individual layers is additive, 
+which leads to the following general relation: 
+%
 \begin{equation}
@@
 where $\alpha_{\mathrm{2D, i}}$ is the electronic polarizability of
-layer $i$, and $p$ is the direction of polarization. This relation can
-be further used to calculate screening inside 2D heterostructures
+layer $i$, and $p$ is the direction of the polarization. This relation can
+be additionally utilized to calculate screening inside 2D heterostructures
 \cite{Kumar_2016_jpcc,Andersen_2015_dielec_vdWH}.
@@
 
-We further look into the bulk systems. In a bulk layered material stacked by layers with equilibrium
-inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
-of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
-$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.95\linewidth]{img/fig4.pdf}
+\caption{\label{fig-4} \textbf{Application of 2D polarizability to
+    few-layer and bulk systems}.  \textbf{a-b,} Multilayer
+  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
+  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal 
+  dichacolgenides (2H-MX$_2$, M=Mo, W; X=S, Se, Te)
+  as a function of number of layers $N$, respectively.  
+  Inset in {\bf a,} shows a 
+   scheme of the 2D-3D transition. 
+  $\alpha$ in the 2D material is essentially equivalent to
+  $\varepsilon$ in its bulk counterpart.  
+  %
+  %
+  Both $\alpha_{\mathrm{NL}}^{\parallel}$
+  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
+  electronic polarizability of the monolayer which indicate that
+  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
+  interacting regime. 
+  %
+  {\bf c-d,} DFT calculated $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and 
+  $\varepsilon_{\mathrm{Bulk}}^{\perp}$, respectively, as a function of 
+  their predicted values from the 2D polarizability model. A strong correlation 
+  is observed in both components with the linear regression slope reaching the 
+  unit for $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ but slightly deviating for 
+  $\varepsilon_{\mathrm{Bulk}}^{\perp}$ at higher magnitudes. 
+  A heat map showing the dependence of $\varepsilon_{\mathrm{Bulk}}^{\parallel,\perp}$
+   with the band gaps is included in {\bf d}. The model predicted values for $\varepsilon_{\mathrm{Bulk}}^{\perp}$ are in good aggreement with the DFT calculations when
+  $E_{\mathrm{g}}>4$ eV. Inset in {\bf c,} shows the definition 
+  of the interlayer distance in bulk $L_{\rm Bulk}$
+  utilized to calculate $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and 
+  $\varepsilon_{\mathrm{Bulk}}^{\perp}$ via Eqs. \ref{eq:3D-para}$-$\ref{eq:3D-para}.  %%%%  
+  Calculations at the level of HSE06 and PBE are shown in circles and 
+  squares, respectively, in all panels that apply. 
+  }
+\end{figure}
+
+%We further look into the bulk systems. 
+In a bulk material with an equilibrium
+inter-layer distance $L_{\mathrm{Bulk}}$, we can follow a similar procedure as in multilayer by 
+defining the polarizability as $\alpha_{\mathrm{Bulk}}$.  %of the individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$
+%
+Inspired by Eqs. \ref{eq:alpha-para-def} and
 \ref{eq:alpha-perp-def}, the dielectric constants
@@
 be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
-$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
+$\alpha_{\mathrm{Bulk}}^{\perp}$ as:
 %
@@
 %
-Here we neglect the effect of the stacking order of the layers.  The
-dielectric constant $\varepsilon$ although not well-defined for a
+Here we neglect the effect of the stacking order of the layers and hypothesized 
+that the basic building blocks for the dielectric response of the bulk are the polarizability of the 
+individual layers subject to vdW and electrostatic interactions. 
+The dielectric constant $\varepsilon$ although not well-defined for a
 monolayer 2D material becomes applicable when the 2D layers are put
-together.
+together as shown in the following. 
 %
@@
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
-$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
+$\varepsilon_{\mathrm{bulk}}^{\perp}$ computed from DFT simulations (\textit{y}-axis)
 with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
-(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
-Both HSE06 and PBE datasets give almost identical results.  
+(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf c} and \ref{fig-4}{\textbf d}. 
+Strikingly both HSE06 and PBE datasets give almost identical results which suggest 
+a non-method dependent behavior. 
 %
@@
 $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
-predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
+predicted by Eq. \ref{eq:3D-para} are in sound agreement with a linear
 regression slope of 1.01 and $R^2$ of 0.97. Conversely, 
 $\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
-Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
+Eq. \ref{eq:3D-perp} fairly agree with the DFT-calculated values when
 $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
 $E_{\mathrm{g}}$ reduces. The above results indicate that
-$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
-its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
+$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated with 
+high accuracy from its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
 to the interlayer coupling and overlap between induced
-dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
+dipole\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
+Nevertheless, as most of the optical response and electronic device properties rely on the 
+in-plane dielectric constant for practical applications, the possibility to handily
+estimate $\alpha_{\mathrm{2D}}^{\parallel}$ from well established magnitudes of 
+$\varepsilon_{\mathrm{bulk}}^{\parallel}$, for instance, from material databases,   
+using reverse engineering in Eq.\ref{eq:3D-para}, it is a step forward in the 
+design and understanding of the dielectric phenomena in 2D.
+
 %With a better model describing
@@
 
-\subsection{Unified geometric represenation of $\alpha_{\mathrm{2D}}$}
+\subsection{Unified geometric representation of $\alpha_{\mathrm{2D}}$}
 \label{sec:unif-geom-repr}
@@
 and $\alpha_{\mathrm{2D}}^{\perp}$ can be unified using a geometric
-picture. In merit of the unit analysis,
+approach. In merit of the unit analysis,
 $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
-both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. In other words,
+both have unit of $4\pi\varepsilon_{0} \times$[Length]. In other words,
 they represent in- and out-of-plane characteristic lengths,
-respectively. It is well-known that the in-plane screened
-electrostatic potential (Keldysh potential) $V(r)$ from a point charge
-as a function of distance $r$:
+respectively. 
+%
+It is well-known that the in-plane screened
+electrostatic potential 
 $V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
@@
       \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
-\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
-function and $Y_{0}$ is the Bessel function of second kind, is
-associated with the in-plane screening radius
+from a point charge as a function of distance $r$\cite{Keldysh_1979_eps_multi,Pulci_2014} 
+(where $H_{0}$ is the Struve
+function and $Y_{0}$ is the Bessel function of second kind) 
+is associated with the in-plane screening radius
 $r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
@@
 point charge sitting in the middle of a 2D material as an ellipsoid
-with the radii of principle axes to be
+with the radii of principal axes to be
 $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
@@
 for a 2D material is in general ultra flat, with
-$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as demonstrated by the examples
-of group 6 2H TMDCs (Figure~\ref{fig-ellip}\textbf{a} and
-~\ref{fig-ellip}\textbf{b}). The polarizability ellipsoid picture
+$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as demonstrated by layered materials 
+of group 6 of 2H-TMDCs (Figure~\ref{fig-ellip}\textbf{b} and
+~\ref{fig-ellip}\textbf{c}). 
+%
+The picture of the polarizability ellipsoid
 provides further insights into the physical nature of
 $\alpha_{\mathrm{2D}}$: $r_{0}^{\parallel}$ is close to the exciton
-radius that confined within the 2D plane~\cite{Pulci_2014}, which is
+radius that it is confined within the 2D plane~\cite{Pulci_2014}. This radius is
 generally larger for a smaller bandgap semiconductor, and can be
 converted through the exciton binding energy as proposed in
-Refs. \citenum{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}
-Eq. \ref{eq:2D-Moss-para}. On the other hand, $r_{0}^{\perp}$ may be
-indirectly deduced from Stark effect
-\cite{Pedersen_2016,Klein_2016,Roch_2018}.
-% and the low-frequency Raman
-% scattering modes of 2D materials \cite{Tan_2012,Zhang_2013}.
-
-%\subsection{Bridging the 2D and 3D Dielectric Properties}
-%\label{sec:2D-3D}
-
-Inspired by the polarizability ellipsoid model, we show that a general picture of the dielectric properties in
+Refs.\cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}.
+%Eq. \ref{eq:2D-Moss-para}. 
+%
+$r_{0}^{\perp}$ in its turn can be 
+indirectly deduced from Stark effect for perpendicular electric fields 
+\cite{Pedersen_2016,Klein_2016,Roch_2018}. A comparison with 
+available experimental data\cite{Verzhbitskiy19, Roch_2018} gives 
+close magnitudes with our predicted values.
+
+Inspired by the polarizability ellipsoid model, we will show that a general 
+picture of the dielectric properties in
 any dimension can be drawn by studying the dielectric
-anisotropy. We define the dielectric anisotropy index $\eta$ as:
+anisotropy. That is, the dielectric response of a material along 
+its different geometrical orientations. 
+%
+%
+We define the dielectric anisotropy index $\eta$ as:
 \begin{equation}
@@
 \end{equation}
-$\eta=1$ indicates the material has isotropic dielectric properties
-while $\eta \to 0$ means the dielectric property is highly
+%
+%
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/fig-ellipsoid.pdf}
+  \caption{\label{fig-ellip} \textbf{Geometric representation of the
+      2D polarizability}. 
+      \textbf{a,} Scheme of the polarizability
+    ellipsoid of a 2D material, with its in-plane
+    ($r_{0}^{\parallel}$) and out-of-plane radii
+    ($r_{\mathrm{0}}^{\perp}$) proportional to
+    $\alpha_{\mathrm{2D}}^{\parallel}$ and
+    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  
+    {\bf b-c,} Calculated magnitudes of 
+    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$, respectively, for selected 2D TMDCs. 
+    The polarizability ellipsoid is highly anisotropic with screening much
+    stronger at in-plane than out-of-plane directions. Comparison with available experimental 
+    results\cite{Roch_2018,Verzhbitskiy19} for 2H-MoS$_2$ and 2H-WSe$_2$ is included.} 
+\end{figure}
+%
+%
+%
+$\eta=1$ indicates that the material has isotropic dielectric properties
+while $\eta \to 0$ means that the dielectric property is highly
 anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
@@
 \ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
-$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
+$E_{\mathrm{g}} \times \delta$, which explains the observation that
 $\eta$ for 2D materials increase almost linearly with
@@
 \AA{}) of the 2D materials investigated varies much less than
-$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
-\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
+$E_{\mathrm{g}}$ in the range of 0.1--7 eV (Figure \ref{fig-3}b$-$\ref{fig-3}c). 
+Further analysis shows that the dielectric anisotropy
 index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
@@
 \eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
-index of corresponding 2D layer (see additional details in
-Supplementary Section \ref{SI-sec:aniso}), which is the basis for the
+index of corresponding 2D layer, which is the basis for the
 separation of bulk and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase
-diagram.  For comparison, we also superimpose the dielectric
+diagram (Supplementary Section \ref{SI-sec:aniso}).  
+%
+For comparison, we also superimpose the dielectric
 anisotropy indices of common semiconducting materials in other
-dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
-the phase diagram in Figure \ref{fig:aniso}. Bulk covalent (3D,
-e.g. Si, GaN) and 0D (fullerenes) semiconductors show isotropic
-dielectric properties, scattered on the line $\eta=1$. On the other
-hand, reduced dimensionality increases the dielectric anisotropy of
-materials such as planar organic semiconductor (OSc, 1D-2D,
-e.g. CuPc), carbon nanotube (CNT, 1D), linear OSc (0D-1D,
-e.g. polyacene and polyacetylene). Interestingly, most of these
+dimensions on
+the phase diagram in Figure \ref{fig:aniso}. Bulk covalent 3D (e.g. Si, GaN) and 0D (e.g. fullerenes) semiconductors show isotropic
+dielectric properties, scattered along the line $\eta=1$. 
+%
+Conversely, reduced dimensionality increases the dielectric anisotropy of
+materials such as planar organic semiconductor (OSc) in 1D-2D 
+(e.g. CuPc), carbon nanotube (CNT) in 1D, linear OSc in 0D-1D
+(e.g. polyacene and polyacetylene). 
+%
+Interestingly, most of these
 materials also scatter along the boundary line separating the bulk and
-2D regimes, indicating the criteria distinguishing 2D (more
-anisotropic) and bulk layered materials (more isotropic) from the
+2D regimes, indicating that the criteria distinguishing 2D (more 
+anisotropic) and bulk materials (more isotropic) from the
 $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
 dimensions. From the phase diagram, we can see that 2D and bulk
-layered materials (also including 2D van der Waals heterostructure
-(vdWH) \cite{Novoselov_2016}), provides more flexibility in
+layered materials, including 2D van der Waals heterostructure
+(vdWH)\cite{Novoselov_2016}, provides more flexibility in
 controlling the dielectric and electronic properties, compared with
-semiconductors in other dimensions.
-
-%
-%\subsection{Implications for Experiments}
-%\todo[inline]{Wait for comments from JC and MC.}
+covalent semiconductors (without vdW gaps) in other dimensions.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1.01\linewidth]{img/fig5.pdf}
+  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
+      function of bandgap $E_{\mathrm{g}}$}. The
+    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
+    their bulk counterparts (orange square) can be distinguished by
+    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
+    semiconducting materials in other dimensions are also superimposed
+    for comparison. Isotropic dielectric property is observed for bulk
+    covalent materials (3D, red triangle) and fullerenes (0D, green
+    star), while reduced dimensional materials, including planar
+    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
+    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
+    scattered along the boundary line. The dimensionality and
+    structure of typical materials are shown along the axis on the
+    right. Compared with other materials, 2D materials and their bulk
+    counterparts provide more flexibility of controlling the
+    dielectric anisotropy.}
+  \label{fig:aniso}
+\end{figure}
 
@@
 $\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
-properties of 2D materials.  There exist well defined relationships
+properties of 2D materials.  There exist well-defined relationships
 between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
 electronic properties.  According to our analysis, simple scaling
-equations involving bandgaps and layer thicknesses can be used to
+equations involving bandgap and layer thickness can be used to
 describe both dielectric and electronic features at the same
@@
 principles presented here will benefit both fundamental understanding
-of 2D materials as well as rational device design and optimization.
+of 2D materials as well as a rational device design and optimization.
 
@@
 
-\section{Data Availability}
-The data that support the findings of this study are available from
-the corresponding author upon reasonable request.
+\section*{Data Availability}
+The data that support the findings of this study 
+is available within the paper and its Supplementary Information.
+
+\subsubsection*{Competing interests}
+The Authors declare no conflict of interests.
+
+\subsubsection*{Acknowledgments}
+C.J.S. and T.T. are grateful for financial support from ETH startup funding. 
+L.H.L. thanks the financial support from Australian Research Council (ARC) 
+via Discovery Early Career Researcher Award (DE160100796). 
+E.J.G.S. acknowledges the use of computational resources from the UK 
+Materials and Molecular Modelling Hub for access to THOMAS 
+supercluster, which is partially funded by EPSRC (EP/P020194/1); and CIRRUS Tier-2 HPC 
+Service (ec019 Cirrus Project) at EPCC (http://www.cirrus.ac.uk) funded 
+by the University of Edinburgh and EPSRC (EP/P020267/1). 
+The Department for the Economy (USI 097) is acknowledged for funding support.
+
+\subsubsection*{Author Contributions}
+E.J.G.S. conceived the idea and supervised the project. 
+T.T., D.S., D.H. and E.J.G.S. performed the first-principles simulations 
+and data analytics. T.T. developed the analytical model with 
+inputs from E.J.G.S. and C.J.S. L.H.L. and J.N.C. 
+performed numerical analysis and contributed to the discussions together with M.C.
+E.J.G.S. and T.T. co-wrote the manuscript with inputs from all authors. 
+All authors contributed to this work, read the manuscript, discussed 
+the results, and all agree to the contents of the manuscript.
+
+\section*{Supporting Information}
+
+The Supporting Information contains detailed descriptions and
+discussions about dielectric properties of 2D materials, effective
+dielectric model, derivations of the 2D polarizability-based model,
+dependency of $\alpha_{\mathrm{2D}}$ on the choice of bandgap,
+relation between 2D and 3D properties, explanations of the dielectric
+anisotropy, as well as raw data sheet from first principles
+calculations.
 
@@
 \label{sec:org34cbe74}
-\begin{figure}[H]
+\clearpage
+
+\section*{TOC entry}
+\begin{figure}
   \centering
-\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
-\caption{\label{fig-1} \textbf{2D polarizability and the breakdown of
-    effective dielectric model
-    (EDM)} % \textbf{2D polarizability as the
-  % true descriptor of the dielectric nature of 2D materials.}
-  \textbf{a}. 3D illustration of the spatial distribution of the
-  charge density change $\Delta \rho(z)$ along the z-direction for
-  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under
-  external eletric field of 0.01 V/\AA{}.  The green and red regions
-  represent negative and positive induced charges, respectively. The
-  macroscopic $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
-  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
-  size $L$, while the 2D polarizabilities
-  $\alpha_{\mathrm{2D}}^{\parallel}$ and
-  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size
-  \textbf{b}.  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
-  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
-  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
-  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
-  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
-  constant when $L>$15 \AA{}, compared with the $L$-dependence of
-  $\varepsilon_{\mathrm{SL}}$. On the other hand, the EDM approach
-  which usually used in literature to extract the effective 2D
-  dielectric constant $\varepsilon_{\mathrm{2D}}$, fails to produce
-  consistent results, estimation uncertainty of the effective layer
-  thickness $\delta^{*}_{\mathrm{2D}}$, causes huge variations of
-  $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{d}) and
-  $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{e}).
-  % HSE06 functional is used in all plots.
-}
-\end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%   \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
-%   \caption{\label{fig-emt} \textbf{Failure of the effective 2D
-%       ``dielectric constant'' picture based on the effective medium
-%       theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
-%     effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
-%     is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
-%     the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
-%     not well-defined. \textbf{b}.  Estimation error between
-%     $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
-%     $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
-%     of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
-%     2D TMDCs. The uncertainty of
-%     $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
-%     $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
-%     particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
-% \end{figure}
-
-% \begin{figure}[htbp]
-% \centering
-% \includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
-% \caption{\label{fig-2} The elements and 3D structures of the 2D
-  % materials investigated in this study.}
-% \end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
-\caption{\label{fig-3} \textbf{The universal scaling relation of the
-    dielectric nature of 2D materials}. \textbf{a}. The structures of
-  the 2D materials investigated in this
-  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
-  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
-  (blue dots) for all the 2D materials studied.
-  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
-  increasing $E_{\mathrm{g}}$, while no apparent relation between
-  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
-  observed. HSE06 functional is used to obtain the data. \textbf{c}.
-  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
-  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
-  correlation between each other. The energy range of visible light is
-  shown in the background. \textbf{d}.
-  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
-  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
-  in the inset), showing a perfect linear relation with slope very
-  close to $1/4\pi$ (i.e.
-  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
-  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
-  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
-  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
-  \textbf{c} and \textbf{d}.}
-\end{figure}
-
-% \begin{table}[H]
-%   \centering
-%   \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
-%     ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
-%     selected 2D materials calculated from first principles
-%     simulations. $r_{0}^{\parallel}$ is in general much larger than
-%     $r_{0}^{\perp}$, which accounts for the highly anisotropic
-%     dielectric nature of 2D materials.}
-%   \label{tbl:radii}  
-%   \begin{tabular}{lcc}
-%     \hline
-%     Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
-%     \hline
-%     2H-MoS$_{2}$ & 40.0 & 2.50 \\
-%     2H-MoSe$_{2}$ & 45.5 & 2.72  \\
-%     2H-MoTe$_{2}$ & 58.1 & 3.07  \\
-%     2H-WS$_{2}$ & 35.7 & 2.46  \\
-%     2H-WSe$_{2}$ & 41.0 & 2.71 \\
-%     2H-WTe$_{2}$ & 53.5 &  3.17\\
-%     \hline
-%   \end{tabular}
-% \end{table}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
-\caption{\label{fig-4} \textbf{Application of 2D polarizability to
-    multilayer and bulk systems}.  \textbf{a}. Scheme for the 2D-3D
-  transition. $\alpha$ in the 2D material is essentially equivalent to
-  $\varepsilon$ in its bulk counterpart.  By applying the concept of
-  electronic polarizability to multilayer 2D materials, the multilayer
-  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
-  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal dichacolgenides
-  as functions of number of layers $N$ are shown in \textbf{a} and
-  \textbf{b}, respectively. Both $\alpha_{\mathrm{NL}}^{\parallel}$
-  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
-  electronic polarizabilities of monolayer, indicating that
-  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
-  interacting regime. The 2D to 3D transition is further studied in
-  \textbf{c} and \textbf{d}, where $\alpha_{\mathrm{2D}}$ of an
-  monolayer 2D material is compared with its bulk counterpart
-  $\varepsilon_{\mathrm{Bulk}}$. \textbf{c}
-  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
-  (y-axis) compared with the predicted value from 2D
-  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good
-  correlation. \textbf{d} $\varepsilon_{\mathrm{bulk}}^{\perp}$
-  calculated from DFT (y-axis) compared with the predicted value from
-  2D $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis). The predicted value
-  is in good aggreement with the DFT calculation when
-  $E_{\mathrm{g}}>4$ eV, due to minimal interlayer coupling. The
-  comparisons in \textbf{b} and \textbf{c} are made based on both
-  HSE06 (circles) and PBE (squares) functionals.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\linewidth]{img/fig-ellipsoid.pdf}
-  \caption{\label{fig-ellip} \textbf{Geometric representation of the
-      2D polarizability}. \textbf{a}. Scheme of the polarizability
-    ellipsoid of a 2D material, with its in-plane
-    ($r_{0}^{\parallel}$) and out-of-plane radii
-    ($r_{\mathrm{0}}^{\perp}$) proportional to
-    $\alpha_{\mathrm{2D}}^{\parallel}$ and
-    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
-    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D TMDCs are
-    shown in \textbf{b} and \textbf{c}, respectively.  The
-    polarizability ellipsoid is highly anisotropic with screening much
-    larger at in-plane direction than out-of-plane direction.}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1.01\linewidth]{img/fig5.pdf}
-  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
-      function of bandgap $E_{\mathrm{g}}$}. The
-    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
-    their bulk counterparts (orange square) can be distinguished by
-    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
-    semiconducting materials in other dimensions are also superimposed
-    for comparison. Isotropic dielectric property is observed for bulk
-    covalent materials (3D, red triangle) and fullerenes (0D, green
-    star), while reduced dimensional materials, including planar
-    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
-    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
-    scattered along the boundary line. The dimensionality and
-    structure of typical materials are shown along the axis on the
-    right. Compared with other materials, 2D materials and their bulk
-    counterparts provide more flexibility of controlling the
-    dielectric anisotropy.}
-  \label{fig:aniso}
+  \includegraphics[width=0.95\linewidth]{img/toc.pdf}  %toc.pdf  
 \end{figure}

### 2019-12-22 SI.tex
modify the SI file

@@
 % Intended LaTeX compiler: pdflatex
-\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
+\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false]{achemso}
+%manuscript=suppinfo 
 \usepackage{times}
@@
 
+%\usepackage{xr}
 \usepackage{xr-hyper} 
-%\usepackage{xr}
-\externaldocument[main-]{paper}
+\externaldocument[main-]{paper_v120719}
 
@@
 \author{Manish Chhowalla}
-% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
 \affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
@@
 
-\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+\title{Supplementary Information: \\ 
+Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
 %\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
@@
 density $\Delta \rho$ is calculated via $\Delta \rho(z) = \frac{1}{S} \int_{S} \Delta \rho (x,y;z) dx dy $, 
-where $S$ is the surface of the unit cell perpendicular to the given direction, in this case $z$. 
+where $S$ is the surface of the unit cell perpendicular to a given direction, in this case $z$. 
 %
@@
 the MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}
-centered at the middle of the layer. This corresponds to about 5-6 \AA
+centered at the middle of the layer. This corresponds to about 5-6 \AA~
 from each side.  When the SL size $L \gg$12 \AA{} as in the first
-principle calculations done in the main text, the induced dipoles from
-the periodic images do not interact, and thus give the converged
+principle calculations shown in the main text, the induced dipoles from
+the periodic images do not interact thus giving the converged
 values of $\alpha_{\mathrm{2D}}$.
@@
 electron-hole interactions at the level of the Bethe-Salpeter equation
-(G$_{0}$W$_{0}$–BSE). Frequency-dependent dielectric functions,
-$\varepsilon_{\mathrm{SL}}(L)$, were calculated at the level of
+(G$_{0}$W$_{0}$-BSE). Frequency-dependent dielectric functions,
+$\varepsilon_{\mathrm{SL}}(\omega)$, were calculated at the level of
 G$_{0}$W$_{0}$ and G$_{0}$W$_{0}$+BSE levels using VASP. For the
 calculations on G$_{0}$W$_{0}$, a 12$\times$12$\times$1 $\Gamma$-centered k-grid was
-used along with an 800 eV energy cutoff in the plane waves and in
+used along with a 800 eV energy cutoff in the plane waves and in
 calculation of the response function. 120 bands (4 occupied and 116
@@
 $\varepsilon_{\mathrm{SL}}(\omega)$ of monolayer BN, with local-field
-effects being included on the RPA level. For the calculation of the
+effects being included. For the calculation of the
 Bethe-Salpeter equation, the Tamm-Dancoff approximation was used with
-two occupied and two unoccupied bands being included in the
-calculation.
+two occupied and two unoccupied bands being included.
 
@@
 \ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting that since
-the G$_{0}$W$_{0}$ method has better estimation of the bandgap,
+the G$_{0}$W$_{0}$ method has better estimation of the electronic bandgap,
 $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller
 using G$_{0}$W$_{0}$ than in PBE functionals.
+%%%
 \begin{figure}[htbp]
@@
 Next we will investigate the frequency-dependent dielectric properties of the 2D materials using various methods.
-The imaginary part of the frequency-dependent dielectric function of an periodic system is calculated using the following relation:
+The imaginary part of the frequency-dependent dielectric function of a periodic system is calculated using the following relation:
 
@@
 \begin{equation}
+\label{eq:dft-dielectric-real}
   \varepsilon_{\alpha\beta}^{(1)}(\omega)=1+\frac{2}{\pi}\int_0^\infty\frac{\varepsilon_{\alpha\beta}^{(2)}(\omega')\omega'}{\omega'^2-\omega^2}d\omega'
@@
 We calculate the frequency-dependent dielectric properties of BN with
-varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
-Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show the
+varying superlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
+Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show that the
 magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
@@
 Note that when extracting the frequency-dependent 2D polarizabilities
-from main text Eqs. \ref{main-eq:alpha-para-def} and
+from Eqs. \ref{main-eq:alpha-para-def} and
 \ref{main-eq:alpha-perp-def}, the peak position in energy
@@
 with increasing $L$. Figures \ref{fig:GW-omega-in} and
-\ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
+\ref{fig:GW-omega-out} show that not only the magnitudes of the dielectric
 functions change with $L$ but also the peak positions. As a result
@@
 \ref{fig:GW-omega-out}{\bf b}-{\bf d}). This 
-can be explained by the long-range nature of Coulomb interactions into the self-energy 
+can be explained by the long-range nature of the 
+Coulomb interactions into the self-energy 
 $\Sigma=iGW$.
@@
 
-For bulk systems, the accuracy of optical properties calculated
-generally ranks by PBE $<$ G\textsubscript{0}W\textsubscript{0} $<$
-BSE. This is because the calculation of the frequency-dependent
-optical properties of a material involves a summation over the valence
-and conduction states. Thus, the accuracy of these states determines
-the calculated optical properties. Within Kohn-Sham density functional
-theory (KS-DFT), the many-body effects are given by the
-exchange-correlation energy which is approximated by functionals based
-on the homogenous electron gas. This generally leads to an
-underestimation of the bandgap and results in the first optical peak
-being lower in energy in comparison to experiment. To go beyond
-KS-DFT, the G\textsubscript{0}W\textsubscript{0} approximation
-replaces the exchange-correlation energy with the self-energy in a bid
+In general terms excitonic effects are not taken into account at the level of PBE or 
+G\textsubscript{0}W\textsubscript{0}. 
+%
+%
+%
+%For bulk systems, the most accurate simulations are based on BSE approach for 
+%the optical properties. As excitonic effects including electron-hole interactions are taken 
+%into account 
+% 
+%This is because the calculation of the frequency-dependent
+%optical properties of a material involves a summation over the valence
+%and conduction states. 
+%
+%Thus, the accuracy of these states determines
+%the calculated optical properties. 
+%
+%Within Kohn-Sham density functional
+%theory (KS-DFT), the many-body effects are given by the
+%exchange-correlation energy which is approximated by functionals based
+%on the homogenous electron gas. 
+%% 
+For the former, this generally leads to an 
+underestimation of the electronic bandgap and results in the first optical peak
+being lower in energy in comparison to more accurate methods. 
+To go beyond
+PBE, the G\textsubscript{0}W\textsubscript{0} approximation
+replaces the exchange-correlation energy by the self-energy 
 to include many-body effects through the interacting Green's function,
-$G$, and the screened Coulomb potential, $W$. This generally leads to
+$G$, and the screened Coulomb potential, $W$. 
+%
+This generally leads to
 an overestimation of the first optical peak as electron-hole coupling
@@
 G\textsubscript{0}W\textsubscript{0}
-(G\textsubscript{0}W\textsubscript{0} + BSE) which generally gives
+(G\textsubscript{0}W\textsubscript{0} - BSE) which generally gives
 good agreement with experiment.
@@
 G$_0$W$_0$ calculation through solving the Bethe--Salpeter equation
-corrects for this energy shift by localizing the exciton within the
+correct this energy shift by localizing the exciton within the
 slab (Figures \ref{fig:BSE-omega-in} and
@@
 frequency-dependent dielectric properties and calculation efforts, the
-choice of HSE06 hybrid functional seems used in the main text provides
-best tradeoff between all aspects.
+choice of HSE06 hybrid functional used in the main text provides
+best trade off between all aspects.
 
@@
 
-\pagebreak{}
-\section{Further Data Concerning the Comparison with EDM}
-\label{sec:2D-3D-rescale}
-
-The major issue when using such rescale
-relations comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
-eliminate the modeling error caused by the \textit{a priori} parameter
-selection of $\delta$, we perform the calculation of
-$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
-and use least-square fitting to extract both
-$\varepsilon$ and $\delta$, as shown in
-Figure \ref{fig:rescale-prb}.
-
 \begin{figure}[htbp]
@@
 
+\pagebreak{}
+\section{Further Data Concerning the Comparison with EDM}
+\label{sec:2D-3D-rescale}
+
+The major issue when using rescale
+relations \ref{main-Response:1}$-$\ref{main-eq:emt-2} comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
+eliminate the modeling error caused by the \textit{a priori} selection of this parameter, 
+we perform the calculation of
+$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
+and use least-square fitting to extract both
+$\varepsilon$ and $\delta$, as shown in
+Figure \ref{fig:rescale-prb}.
+%
 \begin{figure}[htbp]
@@
 \end{figure}
-
-As can be seen from the fitted results in Figure
-\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}^{*}$ extracted
+%
+The values of $\delta_{\mathrm{2D}}^{*}$ extracted
 from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
@@
 smaller than the interlayer distance in corresponding bulk materials
-$L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
+$L_{\mathrm{\rm Bulk}}$, as shown in Table \ref{tab:delta-L-DFt}. On the
 other hand, the extracted $\delta_{\mathrm{2D}}^{*}$ values are closer to
-the covalent thickness $\delta_{cov}$ as
+the covalent thickness $\delta_{\rm cov}$ as
 described in the main text, with a difference generally smaller than
@@
 overestimation. On the contrary, the out-of-plane polarizability
-$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness nature
+$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness 
 of 2D materials.
@@
 $\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
-are comparable or even larger than
+are comparable (within a range of 8-13\%) or even larger than
 $\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
@@
 smaller perpendicular to the 2D plane. In fact, combining
-Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
+Eq. \ref{main-eq:emt-2} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
 have:
@@
   \label{eq:eps-alpha-perp}
-  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
-\end{equation}
+  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta^{*}_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
+\end{equation}
+%
+%
+which indicates that the characteristic length
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
+than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
+if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
+Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
+$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
+$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
+$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
+\ref{fig:eps-alpha-error}. Therefore cautions must be taken when
+treating the dielectric response of the 2D material using effective
+medium theory. In comparison, the 2D polarizability does not require
+the initial guess of the thickness.
 
@@
 
-which indicate that the characteristic length
-$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
-than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
-if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
-Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
-$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
-$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
-$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
-\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
-treating the dielectric response of the 2D material using effective
-medium theory. In comparison, the 2D polarizability does not require
-the guess of the thickness, and therefore is the true descriptor of
-the 2D dielectric nature.
-
 To conclude, based on theoretical and technical considerations, there are several
 advantages of using the electronic polarizability for describing the dielectric
-nature of 2D materials, including
+nature of 2D materials, including:
+%
 \begin{enumerate}
-\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
-\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ in EMT requires calculation with varied superlattice length.
+\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ is unable.
+
+\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length at relative small $L$, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
+This is a big advantage on the computational side since the larger the supercell the larger the computational cost.
+
 \item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
-\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
-
-\item The value of $\epsilon_{\mathrm{2D}}$ in EMT hugely depends on the
+
+\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.
+
+\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
   choice of the thickness of 2D material, while such information is
@@
 \end{enumerate}
+%
+%
+
+%%%%%%%%%%%%%%%%
+
+\subsection{Derivation of Eqs.\ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def}}
+
+To show that Eqs.
+\ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def} do not use any arguments based on EMT but rather basic electrostatics, we show the derivation of both equations in the following.
+
+\subsubsection{Parallel to the surface}
+
+For in-plane electric field, the electrostatic boundary conditions gives the continuity of the applied electric field as  
+${E}^{\parallel}_{\mathrm{loc}}={E}^{\parallel}$\cite{Markel_2016}, which resulted in 
+${P}^{p}=\frac{1}{L} {\mu}^{p}_{\mathrm{2D}}$.
+Indeed, ${\mu}^{p}_{\mathrm{2D}}$ can be written in terms of the local electric field ${E}_{\mathrm{loc}}^{p}$ and the 2D polarizability $\alpha_{\mathrm{2D}}$ as:
+
+\begin{equation}
+{\mu}^{p}_{\mathrm{2D}} = \alpha^{\parallel}_{\mathrm{2D}} {E}^{\parallel}_{\mathrm{loc}} 
+\end{equation}
+%
+This gives for the in-plane polarization:
+
+\begin{equation}
+{P}^{p}=\frac{1}{L} \alpha^{\parallel}_{\mathrm{2D}} {E}^{\parallel}_{\mathrm{loc}} = \frac{1}{L} \alpha^{\parallel}_{\mathrm{2D}} {E}^{\parallel} 
+\end{equation}
+%
+The derivative of this equation relative to the external field ${E}^{\parallel}$ resulted in:
+
+\begin{equation}
+\frac{\partial {P}^{p}}{\partial {E}^{\parallel}} =\frac{1}{L} \alpha^{\parallel}_{\mathrm{2D}} 
+\label{parallel}
+\end{equation}
+%
+Inserting this equation \ref{parallel} into Eq.\ref{main-eq:def-eps-1} with $p=q=\parallel$:
+
+\begin{equation}
+\varepsilon_{\mathrm{SL}}^{\parallel} =  1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_0 L}
+\end{equation}
+
+\subsubsection{Perpendicular to the surface}
+
+The same procedure can be used along the out-of-plane component but using ${E}_{\mathrm{loc}}^{\perp}={E}^{\perp}+{\mu}_{\mathrm{2D}}^{\perp}/\varepsilon_0 L$ for the local field.
+We can write this field as:
+
+\begin{equation}
+{E}_{\mathrm{loc}}^{\perp}={E}^{\perp}+\frac{\alpha^{\perp}_{\mathrm{2D}} {E}_{\mathrm{loc}}^{\perp}}{\varepsilon_0 L}
+\end{equation}
+%
+If we re-arrange the terms for ${E}_{\mathrm{loc}}^{\perp}$, we can ended up with:
+
+\begin{equation}
+{E}_{\mathrm{loc}}^{\perp}= \frac{{E}^{\perp}}{ 1-\frac{\alpha^{\perp}_{\mathrm{2D}}}{\varepsilon_0 L} }
+\end{equation}
+%
+We can write the polarization ${P}^{\perp}$ as:
+
+\begin{equation}
+{P}^{\perp} = \frac{\alpha^{\perp}_{\mathrm{2D}}} {L}(\frac{{E}^{\perp}} {1-\alpha^{\perp}_{\mathrm{2D}}/\varepsilon_0 L})
+\end{equation} 
+%
+%
+Taking the derivative of this equation relative to ${E}^{\perp}$ and inserting in Eq.\ref{main-eq:def-eps-1} with $p=q=\perp$ resulted in: 
+%
+\begin{equation}
+\varepsilon_{\mathrm{SL}}^{\perp} = 1 +  \frac{\alpha^{\perp}_{\mathrm{2D}}} {\varepsilon_0 L}(\frac{1} {1-\alpha^{\perp}_{\mathrm{2D}}/\varepsilon_0 L})
+\end{equation}
+%
+Re-arranging the terms, it ended up as:
+
+\begin{equation}
+\varepsilon_{\mathrm{SL}}^{\perp} =\frac{\varepsilon_0 L - \alpha^{\perp}_{\mathrm{2D}} + \alpha^{\perp}_{\mathrm{2D}}}{  \varepsilon_0 L - \alpha^{\perp}_{\mathrm{2D}}} = (1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_0 L})^{-1}
+\end{equation}
 
@@
 \label{sec:theory-1}
+%
+%
 The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
-$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
+$\alpha_{\mathrm{2D}}^{\perp}$ revealed by 
 Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
@@
   \label{eq:alpha-RPA}
-  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
+  \alpha_{\rm 2D} = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
   \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
@@
 becomes independent of $\psi^{\perp}$, due to the orthogonality
-and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
+and normalization. The Bloch-wave form of $\psi^{\parallel}$ ensures that
 only the cell-function $u(\mathbf{k})$ contributes to the final result
@@
 \end{equation}
-where $N$ is de degeneracy of bands associated with $E_{g}$. The
+where $N$ is degeneracy of bands associated with $E_{g}$. The
 approximation in Eq. \ref{eq:derivation-2D-Moss-para} is due to the
@@
 It is desirable to validate our proposed
-relations on an even larger scale database. We select over 230
+relations on an even larger scale database. We select over 248
 semiconducting 2D materials from Ref.~\citenum{Haastrup_2018} 
@@
 determining the experimentally accessible bandgap
-\cite{Arnaud_2006_exc_hBN,Pulci_2014,Ramasubramaniam_2012,Chernikov_2014_EB_MoS2_2D3D}. The
-experimentally observed optical bandgap
+\cite{Arnaud_2006_exc_hBN,Pulci_2014,Ramasubramaniam_2012,Chernikov_2014_EB_MoS2_2D3D}. The experimentally observed optical bandgap
 $E_{\mathrm{g}}^{\mathrm{opt}}$, is usually lower than the direct

### 2019-12-22 paper.tex
modify the SI file
resolve issues with paper and SI

@@
 ``local'' electric field acting on the 2D material to induce
-polarization\cite{Wiser_1963}.
+polarization\cite{}.
 % 
@@
 \centering
-\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
+\includegraphics[width=0.7\linewidth]{img/fig2-with-MX2.pdf}
 \caption{\label{fig-3} \textbf{The universal scaling relation of the
@@
 Perdew-Burke-Ernzerhof
-(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
+(PBE)\cite{Perdew_1996,Ernzerhof99,Paier_2005_PBE}
 exchange-correlation functional level and a subsequent relaxation

### 2019-12-22 SI.tex
resolve issues with paper and SI
Update to arXiv format

@@
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false]{achemso}
+\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false,manuscript=suppinfo ]{achemso}
 %manuscript=suppinfo 
@@
 \usepackage{graphicx}
-\usepackage{hyperref}
 \usepackage[T1]{fontenc}
@@
 %\usepackage{xr}
-\usepackage{xr-hyper} 
-\externaldocument[main-]{paper_v120719}
+\usepackage{xr} 
+\externaldocument[main-]{paper}
 
@@
 \renewcommand{\theequation}{S\arabic{equation}}
+% \makeatletter
+% \renewcommand\@biblabel[1]{S#1}
+% \makeatother
 
@@
 
-\title{Supplementary Information: \\ 
-Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
+\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
 %\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
